### 2015-09-12 main.tex
Initial commit

\documentclass{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\usepackage{apacite}

\title{Thesis Draft}
\author{Mustafa İlhan}

\begin{document}
\maketitle

In this thesis usage of discarded materials in the process of art making and artwork itself is explored. How it is used by the artist? Is there any differences with the original items? (In other words using discarded materials or trash has specific (or special) meaning? What are the importance of it?) This is a work to explore the re-usage of trash in artworks. (place or the role in the art practice.)

Actually (It is questioned that) working with trash dictates a life practice, it is a convergence of life and art making. The process effects how one's lives and lifestyle. (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)

\section{Reality of trash}
\subsection{What is wrong with trash?}
Huge amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. Most of them packages that are used carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using package trash therefore it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a loosing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. live with trash. do not see it as trash actually. Then question is to how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

All these produced materials how much harmonious with the nature? How much animals and plant can be use these discarded items? (Because of complex production methods their recycling requires complex processes again. Some of them already produced to protect goods from natural factors (like decaying etc.). However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with the nature. However some artists turned to trash into site specific sculptures that are more than trash heap. not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it. (Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created. More likely idea will be we will live harmoniously with what we create.

The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why? and what are the other dimensions?)

Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.

\subsection{Throw away culture}
Continuously consuming things and disposing something. It is important concept to understand why trash is trash? (or how it become trash?) Behavioral pattern of throw away culture result trash. (this pattern does not think about the recycling of it.) artworks that are trying to raise awareness is related with this concept.

\subsubsection{How does it become trash?}
Here purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a road map (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find a way(methodology, approach) to add value to object using artistic methods?)

\subsubsection{Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

\subsubsection{Types of trashes}

\subsection{Collecting trash}
One of the most important part of the using trash in the artwork (or expressing something, or representation) is to collect them. What are the dynamics(considerations) of collecting them? (easily accessible materials or unique items.) Where to store them? Does it mean that live with trash? In other words collecting trash and using them is live with them? (making them part of life.) After the being part of the are they still trash? Can be thought that it is something that effects the lifestyle. (possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value. What is the driving force? You may collecting it to prevent object being lost. For archival things what you collect is something that has some sort of social use and meaning which is going to disappear. However trash is never disappears, even its amount increasing rapidly. For archival things people have memories with them, but does some applies for the trash? Who wants to keep trash? or who wants to re-see(re-visit) trash again (in a museum for example)?

\subsection{What might be meaning of using trash in the artworks? Questioning trash in the context of art}
\begin{itemize}
\item Some works try to raise awareness the problem of trash. (its threat to environment and nature.)
\item Some of them reflect people's lifestyle especially throw away culture. mirroring of current lifestyle.
\item Try to find new combination, meaning from the discarded material that are useless anymore and reached end in the specific lifestyle. to explore new approach, new way. subvert peoples ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
\item Using discarded item to represent other discarded things by the ruling ideology or approach. For example trash can be used to represent refugees. The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential. In other words refugees have potential but we see them as a players that will change our current system. Therefore it can be said that willing to transform trash to treasure is to requires change of current lifestyle. Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
\item One way is to not producing trash. zero trash philosophy. The other one is to transform trash into something else.
\item How does it feel that collecting and working on objects that are generally discarded? (experiencing out of common practice, it is open to new explorations...)
\item Instead of a world that produce trash, how could it be a world created from trash?
\end{itemize}

\section{Rubbish Theory}

\section{Collage, Assemblage and Found Object}

\bibliographystyle{apacite}
\bibliography{ref}

\end{document}

### 2015-09-12 main.tex
etimology

@@
 
-In this thesis usage of discarded materials in the process of art making and artwork itself is explored.
+In this thesis usage of discarded materials in the process of art making and artwork itself is explored (or researched).
 How it is used by the artist?
@@
 
+It can be thought that when the complexity of trashed increased to effort to repair, reuse and recycle is increase.
+Therefore for ones that has no such complex tools it is becoming harder to reuse them.
+In other words objects become more complex their re-usage becomes less likely.
+
 \subsubsection{Types of trashes}
+Different production process generates different types of trash.
 
@@
 \item Instead of a world that produce trash, how could it be a world created from trash?
+\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
+It also signifies that trash still has a good quality to used with new materials.
+Creating composite products from new and reused items.
+Using valuable thing with invaluable thing.
+It become more valuable or less valuable.
+depends on the idea.
+\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. trash portraits, sculptures.)
 \end{itemize}
+
+\section{Etymology}
+In this topic there are widely used keywords, it is important to clarify them.
+
+The concept of reuse is when a product that is newly purchased is put to another use after the first use is completed.
+In layman terms an item is reused for the same purpose or another purpose.
+Reuse is considered to have a massive impact on environment as an item which would have been thrown out, is being given a new purpose.
+It also eliminates the need to buy another new product, contributing to reduce.
+The concept of reuse includes anything object that can be used again maybe for a short term as well as long term.
+An example of reusing would be carrying a cloth bag while going shopping.
+Since the cloth bag can be used more than once, a person would not have to keep purchasing new paper or plastic bags, hence reducing amount of waste.
+Reusing can also include using older materials for decorating or other purposes.
+Plastic bottles can be reused in order to cut the top of and create pen holders.
+Milk crates can be made into storage compartments.
+Even donating is a form of re-use, where another person can make use of items that are no longer of use to the person donating them.
+Salvation Army, churches and various other places hold donation centers where people donate old clothes, shoes, toys, etc that are in turn given to less fortunate people.
+
+Recycling is processing of used materials (waste) into new products to prevent waste of potentially useful materials.
+The waste is converted into raw materials for a new product.
+Recycling helps reduce the consumption of fresh raw materials, energy usage, air pollution (from incineration) and water pollution (from landfilling) by reducing the need for "conventional" waste disposal, and lower greenhouse gas emissions as compared to virgin production.
+Material such as glass, metal, plastic, paper and cloth can be reprocessed and used to create brand new products.
+Plastic bottles are melted to create new plastic bottles.
+Even electronics, such as computers, cell phones, TVs, etc can be taken apart and the components can be upgraded and used for new electronics.
+A set back of recycling is that it has to be sorted and cleaned before it can be processed into new material.
+This can add extra costs on the part of the company.
+However, many companies are still turning to the concept of recycling as in the long run it is cheaper compared to purchasing new raw materials every time.
+In order to make it easier for recycling, people are usually asked separate plastic, glass and paper from other waste.
+
+The root of words waste, garbage, trash, rubbish, scrap, junk, refuse.
+
+Waste "squander, spend or consume uselessly".
+Garbage giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
+Garbology "study of waste as a social science".
+"In modern American usage garbage is generally restricted to mean kitchen and vegetable wastes".
 
@@
 
+\section{Artwork}
+\subsection{Why (package) paper?}
+
 \bibliographystyle{apacite}

### 2015-09-13 main.tex
rubbish theory

@@
 
-\subsection{What might be meaning of using trash in the artworks? Questioning trash in the context of art}
+\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
 \begin{itemize}
-\item Some works try to raise awareness the problem of trash. (its threat to environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. mirroring of current lifestyle.
+\item Some works try to raise awareness the problems that are result of trash. (it threats environment and nature.)
+\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
 \item Try to find new combination, meaning from the discarded material that are useless anymore and reached end in the specific lifestyle.
@@
 subvert peoples ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
+trash to treasure.
 \item Using discarded item to represent other discarded things by the ruling ideology or approach.
@@
 \section{Etymology}
-In this topic there are widely used keywords, it is important to clarify them.
-
+\subsection{The difference between reuse and recycle.}
 The concept of reuse is when a product that is newly purchased is put to another use after the first use is completed.
@@
 
-The root of words waste, garbage, trash, rubbish, scrap, junk, refuse.
+\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
+The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
 
-Waste "squander, spend or consume uselessly".
-Garbage giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology "study of waste as a social science".
-"In modern American usage garbage is generally restricted to mean kitchen and vegetable wastes".
+Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
+Garbology is study of waste as a social science.
+In modern American usage garbage is generally restricted to mean kitchen and vegetable wastes.
+
+Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
+German has retained the original meaning in wüste (desert).
+Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
+It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
 
 \section{Rubbish Theory}
+Objects have a lifetime and they don't remain same through that lifetime.
+Their value, usage, location change over time.
+During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
+Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
+Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
+This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
+Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts and ideas.
+He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
+The theory looks at how some of these objects then regain value, such as antiques or historic homes.
+It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
+The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
+Further there is a common idea/argument/motto that is "trash to treasure" among artists who uses trash as a medium.
+Rubbish theory presents a conceptual approach to this argument.
 
-\section{Collage, Assemblage and Found Object}
+Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
+Thompson label some transitions as possible and the others as impossible.
+"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
+Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
+Further he does not allow move from transient to durable.
+However Duchamp's fountain breaks this rule.
+Because urine used as fountain is still functional and have a place in the market.
+In other word it is not rubbish.
+This urine with the approach of Duchamp turned to be an artwork.
+It is one of most influential piece of modern art and one of the best examples of ready-made.
+After Duchamp's intervention to the urine, it becomes a durable object placed in museum.
+
+In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
+(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
+transforming them creates new a value system?
+or just finding place existing value system.
+by the way there is a value theory related with (or inside of) game theory.)
+
+Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
+
+\section{Collage, Assemblage and the Found Object}
 
@@
 \subsection{Why (package) paper?}
+Easy to collect. Found easily. Thrown out even if it is good quality. Packaging materials are very widespread.
 

### 2015-09-13 main.tex
Assamblage, proof reading.

@@
 \usepackage[utf8x]{inputenc}
-
 \usepackage{apacite}
@@
 
-In this thesis usage of discarded materials in the process of art making and artwork itself is explored (or researched).
-How it is used by the artist?
-Is there any differences with the original items?
+In this thesis usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
+How is it used by the artist?
+Are there any differences with the original items?
 (In other words using discarded materials or trash has specific (or special) meaning?
-What are the importance of it?) This is a work to explore the re-usage of trash in artworks.
+What is the importance of it?) This is a work to explore the re-usage of trash in artworks.
 (place or the role in the art practice.)
@@
 \subsection{What is wrong with trash?}
-Huge amount of industrial discarded items spread through the landfills to oceans.
+The vast amount of industrial discarded items spread through the landfills to oceans.
 They are the result of highly complex industrial production methods.
@@
 After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using package trash therefore it is more important.) How manage the all this increasing trash that damaging nature?
+(types of trash can be mentioned here, but currently in the artwork I'm using package trash, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
 This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a loosing the ability to transform new things, alternative behaviors etc.
+(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
 (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-live with trash.
-do not see it as trash actually.
-Then question is to how to love trash?
+Live with trash.
+Do not see it as trash actually.
+Then the question is how to love trash?
 how to live with trash?
@@
 
-All these produced materials how much harmonious with the nature?
-How much animals and plant can be use these discarded items?
+All these produced materials how much harmonious with nature?
+How many animals and the plant can use these discarded items?
 (Because of complex production methods their recycling requires complex processes again.
 Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with the nature.
-However some artists turned to trash into site specific sculptures that are more than trash heap.
+However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
+However, some artists turned to trash into site-specific sculptures that are more than trash heap.
 not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
 (Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-More likely idea will be we will live harmoniously with what we create.
+The more likely idea will be we will live harmoniously with what we create.
 
@@
 \subsection{Throw away culture}
-Continuously consuming things and disposing something.
-It is important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture result trash.
-(this pattern does not think about the recycling of it.) artworks that are trying to raise awareness is related with this concept.
+Continuously consuming things and disposing of something.
+It is an important concept to understand why trash is trash?
+(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
+(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
 
 \subsubsection{How does it become trash?}
-Here purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a road map (or ideas) how to turn trash to something valuable?
+Here the purpose is to understand the dynamics that turn objects to trash.
+By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
 (The purpose of this thesis is to find a way(methodology, approach) to add value to object using artistic methods?)
@@
 The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for environment is never exist previous societies.
+For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
 Think batteries and so on.
@@
 
-It can be thought that when the complexity of trashed increased to effort to repair, reuse and recycle is increase.
-Therefore for ones that has no such complex tools it is becoming harder to reuse them.
+It can be thought that when the complexity of trashed increased to the effort to repair, reuse and recycle is increase.
+Therefore for ones that have no such complex tools it is becoming harder to reuse them.
 In other words objects become more complex their re-usage becomes less likely.
@@
 \subsection{Collecting trash}
-One of the most important part of the using trash in the artwork (or expressing something, or representation) is to collect them.
+One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
 What are the dynamics(considerations) of collecting them?
@@
 (making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that effects the lifestyle.
+Can be thought that it is something that affects the lifestyle.
 (possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
 What is the driving force?
-You may collecting it to prevent object being lost.
+You may collect it to prevent object being lost.
 For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However trash is never disappears, even its amount increasing rapidly.
+However, trash is never disappearing, even its amount increasing rapidly.
 For archival things people have memories with them, but does some applies for the trash?
@@
 \begin{itemize}
-\item Some works try to raise awareness the problems that are result of trash. (it threats environment and nature.)
+\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
 \item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find new combination, meaning from the discarded material that are useless anymore and reached end in the specific lifestyle.
-to explore new approach, new way.
-subvert peoples ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-trash to treasure.
+\item Try to find a new value and meaning from the discarded material that are useless anymore.
+To explore a new approach, new way.
+Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
+Trash to treasure.
 \item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example trash can be used to represent refugees.
+For example, trash can be used to represent refugees.
 The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words refugees have potential but we see them as a players that will change our current system.
-Therefore it can be said that willing to transform trash to treasure is to requires change of current lifestyle.
+In other words, refugees have potential but we see them as players that will change our current system.
+Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
 Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is to not producing trash. zero trash philosophy. The other one is to transform trash into something else.
-\item How does it feel that collecting and working on objects that are generally discarded? (experiencing out of common practice, it is open to new explorations...)
+\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
+\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
 \item Instead of a world that produce trash, how could it be a world created from trash?
@@
 Creating composite products from new and reused items.
-Using valuable thing with invaluable thing.
-It become more valuable or less valuable.
-depends on the idea.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. trash portraits, sculptures.)
+Using the valuable thing with the invaluable thing.
+It becomes more valuable or less valuable.
+Depends on the perception.
+\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
 \end{itemize}
@@
 \section{Etymology}
-\subsection{The difference between reuse and recycle.}
-The concept of reuse is when a product that is newly purchased is put to another use after the first use is completed.
-In layman terms an item is reused for the same purpose or another purpose.
-Reuse is considered to have a massive impact on environment as an item which would have been thrown out, is being given a new purpose.
-It also eliminates the need to buy another new product, contributing to reduce.
-The concept of reuse includes anything object that can be used again maybe for a short term as well as long term.
-An example of reusing would be carrying a cloth bag while going shopping.
-Since the cloth bag can be used more than once, a person would not have to keep purchasing new paper or plastic bags, hence reducing amount of waste.
-Reusing can also include using older materials for decorating or other purposes.
-Plastic bottles can be reused in order to cut the top of and create pen holders.
-Milk crates can be made into storage compartments.
-Even donating is a form of re-use, where another person can make use of items that are no longer of use to the person donating them.
-Salvation Army, churches and various other places hold donation centers where people donate old clothes, shoes, toys, etc that are in turn given to less fortunate people.
+\subsection{The difference between reuse and recycle}
+According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+If any item is used again and again over time, it is said to be reused.
+The main purpose of reusing is to lengthen the life of the item or material.
+We give out used clothes for charity which results in reusing.
+Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
+The main purpose is to make the item last as long as it can.
+To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
+Why throw something away when you can give it another life?
+Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
+Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
+For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
 
-Recycling is processing of used materials (waste) into new products to prevent waste of potentially useful materials.
-The waste is converted into raw materials for a new product.
-Recycling helps reduce the consumption of fresh raw materials, energy usage, air pollution (from incineration) and water pollution (from landfilling) by reducing the need for "conventional" waste disposal, and lower greenhouse gas emissions as compared to virgin production.
-Material such as glass, metal, plastic, paper and cloth can be reprocessed and used to create brand new products.
-Plastic bottles are melted to create new plastic bottles.
-Even electronics, such as computers, cell phones, TVs, etc can be taken apart and the components can be upgraded and used for new electronics.
-A set back of recycling is that it has to be sorted and cleaned before it can be processed into new material.
-This can add extra costs on the part of the company.
-However, many companies are still turning to the concept of recycling as in the long run it is cheaper compared to purchasing new raw materials every time.
-In order to make it easier for recycling, people are usually asked separate plastic, glass and paper from other waste.
+According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
+It is an energy consuming process.
+For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
+In this process, energy is required which depends upon the stages of transformation.
 
@@
 Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is study of waste as a social science.
-In modern American usage garbage is generally restricted to mean kitchen and vegetable wastes.
+Garbology is a study of waste as a social science.
+In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
 
@@
 This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts and ideas.
+Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
 He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
@@
 The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further there is a common idea/argument/motto that is "trash to treasure" among artists who uses trash as a medium.
+Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
 Rubbish theory presents a conceptual approach to this argument.
@@
 Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
-Further he does not allow move from transient to durable.
-However Duchamp's fountain breaks this rule.
-Because urine used as fountain is still functional and have a place in the market.
-In other word it is not rubbish.
+Further, he does not allow move from transient to durable.
+However, Duchamp's fountain breaks this rule.
+Because urine used as a fountain is still functional and have a place in the market.
+In another word, it is not rubbish.
 This urine with the approach of Duchamp turned to be an artwork.
-It is one of most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in museum.
+It is one of the most influential piece of modern art and one of the best examples of ready-made.
+After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
 
@@
 \section{Collage, Assemblage and the Found Object}
+In this chapter root of using objects in the artworks is examined.
+Using objects on artworks beyond their intended purpose.
+Developing artworks not only painting but also using paper and other stuff by pasting them together.
 
-\section{Artwork}
+\subsection{Collage}
+Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
+In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
+Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
+
+\subsection{Assemblage}
+Assemblage work produced by the incorporation of everyday objects into a composition.
+It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
+Diverse range of things can be used production of work.
+In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
+William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
+
+\subsection{the Found Object (Ready-mades)}
+Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
+Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).
+Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
+The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+
+\subsection{\textit{Bricolage}}
+Something constructed using whatever was available at the time.
+
+\subsection{Discussion}
+Are artworks made from trash just examples of collage and assemblage or more than from them?
+What about the experience and interaction with other people?
+Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
+But all of them work in fragments, combine many objects together.
+
+\section{Artwork, Project}
 \subsection{Why (package) paper?}
-Easy to collect. Found easily. Thrown out even if it is good quality. Packaging materials are very widespread.
+Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
 

### 2015-09-20 main.tex
theory of trashed/garbage extended

@@
-\documentclass{article}
+\documentclass[a4paper]{article}
 \usepackage[english]{babel}
@@
 \usepackage{apacite}
+
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
 
@@
 
-In this thesis usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
-How is it used by the artist?
-Are there any differences with the original items?
-(In other words using discarded materials or trash has specific (or special) meaning?
-What is the importance of it?) This is a work to explore the re-usage of trash in artworks.
-(place or the role in the art practice.)
+\begin{abstract}
+In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
+Why and how are they used by the artist?
+Are there any differences with the original items compared to discarded items?
+(In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
+(and also in which scope?
+medium, message, life practice\ldots)
 
-Actually (It is questioned that) working with trash dictates a life practice, it is a convergence of life and art making.
+Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
 The process effects how one's lives and lifestyle.
 (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
+\end{abstract}
+\keywords{trash, art}
 
-\section{Reality of trash}
-\subsection{What is wrong with trash?}
-The vast amount of industrial discarded items spread through the landfills to oceans.
+\section{Reality of trash (other side of production)}
+\subsection{Trash is everywhere and, produced every time}
+Modern (developed) societies are continuously generating trash and, pile them on landfills.
+It's a common object category that all people share its possession.
+During daily activities trash is generated and people get rid of them by throwing away.
+(Various objects become trash after their primary functions daily.
+Who defined the primary function?
+Primary function is the only function.
+People cares the package of the objects that they buy.
+They buy the coffee not the cup of it.
+After coffee finished the life of cup also finishes.
+There is a lifetime defined (or forecast) by the producer of objects.
+However it is not bound to the producer, also consumer play an important role.
+There are different choices.
+Throw it away.
+Keep it.
+Give it.
+Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
 They are the result of highly complex industrial production methods.
@@
 They live in the nature thousands of years.
-Most of them packages that are used carry or protect other materials.
+Most of them packages that are used to carry or protect other materials.
 After real material used these packages became valueless (or useless).
@@
 
-All these produced materials how much harmonious with nature?
+(Zizek part: talks about ecology at garbage dump in London, and starts with the words "This is where we should start feeling at home." to the ecologist.
+how ecology turns to ideology and mentions the our wrong perception about the ecology.
+Draw attention to the event if trash disappears from our world but not world.
+He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing.
+He claims that it is ideological in the sense that wrong thinking important problems.
+nature contains unimaginable catastrophes.
+think oil and distinct animals and plants.
+we profit balance part of the nature but it is created from catastrophe.
+Are we aware of this catastrophe.
+he asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
+It would be too much." its voice is like "Don't mess with D.N.A.
+Don't mess with nature.
+Don't do it" etc.
+we should not forget that we are part of the ecology.
+we must more alienated from the nature.
+we must find poetry and spirituality in the dimension of trash.
+thats the true love of world.
+Love is not idealization.
+This part can be extended.)
+
+How much harmonious all these produced materials with nature?
 How many animals and the plant can use these discarded items?
@@
 
+Getting rid of it is not the significant reaction.
+It still waits us.
+Maybe the first thing to do is accept the waste, to accept that there are things out there that serve nothing.
+To break out of this eternal cycle of functioning.
+
 The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
@@
 Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
+
+trash of developed societies has higher recycling period in the nature. higher damage to the nature. hard to reuse. hard to transform. sometimes not to safe to keep them.
+
+\subsubsection{Perspectives of trash from different disciplines}
+Trash is ecological problems and it is treats the balance of it. Animals do not aware of plastics materials and eat them. Management problem of municipals.
 
@@
 (This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
+
+(Our trash generating behavioral patterns reveals what it is wrong? You are walking outside and entered an coffee shop. buy a coffee inside a paper cup. carried with paper package.)
 
@@
 
+\subsection{What is wrong with trash?}
+Relationship between entropy (second law of thermodynamics) and waste.
+Resources of nature turns to waste that it can revert it.
+Creating that are reversible again is problematic through the nature of sustainability.
+What is produced after it is consumed become worthless.
+
 \subsection{Collecting trash}
@@
 or who wants to re-see(re-visit) trash again (in a museum for example)?
+
+Agnes varda, the gleaner and I
 
@@
 
+Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
+Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
+
 According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
@@
 In this process, energy is required which depends upon the stages of transformation.
+
+Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
+Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
+
+Reusing is possible with re seeing (rethinking).
+Reusing is possible meet the needs of the human itself.
+Using creativity and personal approach can change objects functions.
+It is possible to use objects for different purposes.
 
@@
 
+"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18thcentury Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
+
+\subsection{Implications of Rubbish Theory}
+
 \section{Collage, Assemblage and the Found Object}
@@
 
+Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
+\cite{levi1966savage}
+
+\subsection{Folk Art}
+
+\subsection{History of Consumption and Waste}
+"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
+Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
+A.
+Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
+
 \subsection{Discussion}
@@
 
+Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
+
+In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
+
+\section{Artworks and trash}
+Types of artworks are created from trash.
+
 \section{Artwork, Project}
+
+\subsection{Paper}
+"Paper is an indispensable product throughout the world.
+Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
+In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
+Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
+Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
+
+\subsubsection{Environmental Impact}
+Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
+However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
+In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
+Further, forest resources are not always as renewable as one may like to think.
+These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
+
+Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
+Recycling paper can greatly diminish demand for virgin fiber from wood.
+However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
+It can only be recycled four to six times, as the fibers get shorter and weaker each time.
+In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
+
+\subsubsection{History}
+The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
+
+\subsubsection{Production}
+All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
+
+\subsubsection{Uses}
+Paper has become the most ubiquitous product in the age of information.
+Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+
 \subsection{Why (package) paper?}
 Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
+
+\section{Uncategorized ideas, references}
+Trash art is not collage (assemblage or found object) or fragments.
+it is more than that.
+The carried messages through the medium have different meaning.
+It has relationship with activism, craftivism.
+It refuses consumption based life cycle.
+It suggests a life practice.
+
+"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
+The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
+Worthless.
+Rejected and useless matter of any kind.
+Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
+Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
+
+\subsection{Culture, Values, and Garbage}
+"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
+In terms of their relationship to garbage, all people interact with it on two levels.
+One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
+In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
+Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
+The second connection that people maintain with garbage is an ideational one.
+Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
+The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
+Instead, humans determine whether the object is of value or whether it is considered trash.
+The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
+The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
+
+\subsection{Garbage Art}
+"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
+
+\subsection{Garbage in Modern Thought}
+"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
+It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
+Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
+
+\subsubsection{Categorization and Value}
+"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
+Consumers have become accustomed to the categories that are often applied to garbage.
+Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
+Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
+
+"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
+Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
+While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
+Many non-Western societies attach a much greater value to items after they are discarded.
+In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
+Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
+People define what is trash and what is valuable." \cite{lukas2012garbage}
+
+\subsubsection{Semiotic Context}
+"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
+
+\section{Archaeology of Garbage}
+\subsection{Garbology}
+"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
+
+"The field of garbology involves the study of refuse and waste.
+It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
+According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
+A.
+J.
+Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
+
+\subsection{Trash as History/Memory}
+\cite{bullock2012trash}
 

### 2015-09-21 main.tex
The Gleaners and I

@@
 \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+\providecommand{\quotes}[1]{``#1''}
 
@@
 After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using package trash, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
+(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
 This is the common approach to trash and the main problem.
@@
 
-(Zizek part: talks about ecology at garbage dump in London, and starts with the words "This is where we should start feeling at home." to the ecologist.
-how ecology turns to ideology and mentions the our wrong perception about the ecology.
-Draw attention to the event if trash disappears from our world but not world.
+\subsubsection{The Case of Zizek}
+(In documentary film, Examined-life, Zizek talks about ecology at a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
+He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
+Draw attention to notion of even if trash disappears from our world but not world.
 He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing.
 He claims that it is ideological in the sense that wrong thinking important problems.
-nature contains unimaginable catastrophes.
+Nature contains unimaginable catastrophes.
 think oil and distinct animals and plants.
@@
 Are we aware of this catastrophe.
-he asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
+He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
 It would be too much." its voice is like "Don't mess with D.N.A.
@@
 Don't do it" etc.
-we should not forget that we are part of the ecology.
-we must more alienated from the nature.
-we must find poetry and spirituality in the dimension of trash.
-thats the true love of world.
-Love is not idealization.
-This part can be extended.)
+We should not forget that we are part of the ecology.
+We must more alienated from the nature.
+We must find poetry and spirituality in the dimension of trash.
+That's the true love of world.
+Love is not about idealization.
+This part will be extended later.)
 
@@
 
-Getting rid of it is not the significant reaction.
-It still waits us.
-Maybe the first thing to do is accept the waste, to accept that there are things out there that serve nothing.
+Getting rid of it is not the significant action.
+It still waits us at somewhere else or the next generations have to cope with it.
+(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
 To break out of this eternal cycle of functioning.
@@
 
-trash of developed societies has higher recycling period in the nature. higher damage to the nature. hard to reuse. hard to transform. sometimes not to safe to keep them.
+Trash of developed societies has higher decomposing period in the nature.
+Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
 
-\subsubsection{Perspectives of trash from different disciplines}
+\subsubsection{Perspectives related with trash from different disciplines}
 Trash is ecological problems and it is treats the balance of it. Animals do not aware of plastics materials and eat them. Management problem of municipals.
@@
 
-(Our trash generating behavioral patterns reveals what it is wrong? You are walking outside and entered an coffee shop. buy a coffee inside a paper cup. carried with paper package.)
+(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?)
 
@@
 By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find a way(methodology, approach) to add value to object using artistic methods?)
+(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
+Therefore first question is why they are less-valued, and ignored.
+How to make them valuable?
+How to make them part of our life again?)
 
@@
 
-It can be thought that when the complexity of trashed increased to the effort to repair, reuse and recycle is increase.
-Therefore for ones that have no such complex tools it is becoming harder to reuse them.
+It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
+Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
 In other words objects become more complex their re-usage becomes less likely.
@@
 \subsubsection{Types of trashes}
-Different production process generates different types of trash.
+Different production process generates different types of trash. According to production process, decomposition process\ldots
 
@@
 
-Agnes varda, the gleaner and I
+\subsubsection{The case of \quotes{The Gleaners and I}}
+The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
+The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
+This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
+
+It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
+Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
+
+\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
+Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
+However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
+Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
+She is gleaning images.
+The Gleaners and I far more than document the lives of gleaners.
+It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
+
+The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
+As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
+More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
+And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
+
+Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
+There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
+Seeing the value in what someone else has defined as trash is an art in itself.
+
+Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
+She keeps light to the modern life gleaners that are not visible every time.
+One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
+In other word we can be subject of the refusal.
+At some point she become the subject of the thing that she track.
+
+There are many aspects of this documentary film.
+First draw attention the practice of gleaning.
+The discarded items that are not fit in the industrial standards because of their shape, color etc.
+Even if these items are discarded and we are not aware of them, there is also another life for them.
+Modern life gleaners feed from them.
+In another words someones trash becomes another trash.
+There are people live the boundaries of consumption societies.
+They create their life from the unwanted items.
+what the society refuses, they find a life or create a life from them.
+Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
+(as also Zizek mentions that love is not idealization.
+But the industrial processes has some standards and beyond that standards there is not a place for everyone.
+Life is being lived in the cites is somehow idealized life or tried to be idealized life.
+beyond the border of the urban there is new life generated.
+What is not succeed in the cities succeed outside of it.)
+
+She uses unconsciously recorded pieces in the film.
+\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
+It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
+She sets this scene to a jazz soundtrack.
+While watching the scene I was certainly confused.
+Why is this in here?
+What does this have to do with gleaning?
+And certainly why did the scene last so long?
+But there was also something lovely about it.
+Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
+I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
+Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
+Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
+Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
+Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
+The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
+
+Refused is not only foods and trash.
+there are a lot of things that are pushed outside border of the society.
+She talks and investigates artist that are using discarded items in the artworks.
+What people not found anything the artist see countless possibilities from them.
+There is always alternative ways to see something different.
+Giving life or finding life from discarded life.
+
+The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
+
+Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
+Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
+There should reason for this?
+For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
+They require it to sustain their life.
+Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
+What gleaning means become more open (or powerful).
+It draws a picture of body combination of different parts (connected, dependent to the each other).
+The reason of gleaning varies but the fact that gleaning is continues in different forms.
+
+She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
+One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
+
+The Gleaners And I is not an environmental film.
+Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
+
+The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
+Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
+The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
+One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
+
+Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
+Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
+He specializes in reliefs and assemblages made entirely from discarded objects and junk.
+In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
 
@@
 
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18thcentury Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
+"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
 

### 2015-09-24 main.tex
- Zizek extended. - Artist part started. - Adding images started. - Comments added.
Former-commit-id: 3420ed906adc98026e01af91572067f733dc606e

@@
 \usepackage{apacite}
+%\usepackage{setspace}
+%\doublespacing
+\usepackage{graphicx}
+%\graphicspath{ {graphics/} }
 
+% Keywords command
 \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+% Quotation command
 \providecommand{\quotes}[1]{``#1''}
+\providecommand{\singlequotes}[1]{`#1'}
 
@@
 
+%%%
+%%%
+%%%
 \begin{abstract}
@@
 
+%%%
+%%%
+%%%
 \section{Reality of trash (other side of production)}
+%%
+%%
 \subsection{Trash is everywhere and, produced every time}
@@
 
+Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
+The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD countries produce almost half of the world’s waste.
+Africa and South Asia produce the least waste.
+High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
+Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
+(Trash as Treasure, BY WILLIAM L.
+FASH AND E.
+WYLLYS ANDREWS)
+
+Literature is recycled material, a pretext for making more art.
+I learned this distillation of lots of literary criticism in workshops with children.
+I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
+For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
+(Recycle the Classics, BY DORIS SOMMER)
+
+%
+\subsubsection{Cycle of trash}
+Trash moves, objects moves from place to place.
+From homes to garbage trucks.
+From streets to land fills.
+From garbage baskets to sculptures.
+[REF.
+MIT Garbage project] Lots of different people touches to trash.
+With the trash what moves?
+
+% <Part from "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
+Below part Explains journey of trash, its different steps.
+Object moves and also trash also moves.
+How is it life of trash?
+This part explains life of trash.
+How does it intersect with other people in which places?
+This part also can be understand by pointing out different part of it with detailed explanation.
+For example an artist collect from trash from streets and the other one goes to the [for Vik Muniz] landfill.
+In other words there are different places to touch on trash.
+Every place generates different story?
+Or to understand it more deeply it covers different part of it.
+Or provides ideas about it.
+Lots of people touches it from philosophers to artist.
+Also in the later parts it draws attention to them.
+
+Trash moves, all the time.
+It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or compostable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
+Even in the landfill, it does not remain still.
+Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
+More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
+When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
+This is how trash moves.
+But\ldots who moves on trash?
+In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
+In Latin America, it is mostly people.
+People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
+In many of the garbage dumps around the world, scavenging becomes a steady job.
+\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
+thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
+(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
+% >
+
+%
 \subsubsection{The Case of Zizek}
-(In documentary film, Examined-life, Zizek talks about ecology at a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
+(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
+In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
 He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
 Draw attention to notion of even if trash disappears from our world but not world.
+It seems as though the thrown out garbage disappears from
+our world.
+However, it disappears only from the world of illusions, but still exists in reality.
 He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing.
@@
 This part will be extended later.)
+
+\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
+Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
+Such interpretation makes life easier.
+However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
+Nature is a series of unthinkable disasters.
+Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
+Do not touch DNA!
+Do not develop new medicines!
+Do not invent new technologies!” How one should react to these reproaches?
+Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
+
+His basic argument is that the modern eco movement is a conservative ideology.
+It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
+Basically he says the eco movement has it's head in the clouds.
+If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
+
+\begin{itemize}
+\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
+\item Ideology addresses real problems but mystifies them.
+\item We search for meaning when a horrible event happens to make it easier to accept.
+\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
+\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
+\item Ecology is becoming more like religion with dogmas.
+\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
+\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
+\item Learn to love our trash as a part of ecology.
+\end{itemize}
 
@@
 
+%
 \subsubsection{Perspectives related with trash from different disciplines}
@@
 
-\subsection{Throw away culture}
+\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
+In other word the problem is our technology which is not perfect.
+(and I'm not sure that at some point that technology will reach to the perfection or not.)
+
+\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
+Yes and no.
+After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
+Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
+No one called it recycling.
+Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
+They can not handle their trash.
+There is no place for trash in their life.
+
+\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
+\quotes{What is happening to trash is what is going to happen to us.
+We’re all going to end up in a dump, and we’re going to decompose.
+That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
+Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
+But when the same student went to Beverly Hills to go through trash, the police were nearly called.
+\quotes{Who decides what is public and what is private?
+How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{}
+
+Wall-e resembles to giant dozers that moves and piles trash in the landfills.
+WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
+A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
+
+%
+\subsubsection{Throw away culture}
 Continuously consuming things and disposing of something.
@@
 
+%
 \subsubsection{How does it become trash?}
@@
 
+%
 \subsubsection{Comparison of trashes}
@@
 
+%
 \subsubsection{Types of trashes}
@@
 
-\subsection{What is wrong with trash?}
+%
+\subsubsection{What is wrong with trash?}
 Relationship between entropy (second law of thermodynamics) and waste.
@@
 
+From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
+Even if they are excluded, there is also life for them.
+
+% TODO Reference
+John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
+
+% TODO motivations of artists. their ideas about them.
+
+%%
+%%
 \subsection{Collecting trash}
@@
 
+%
 \subsubsection{The case of \quotes{The Gleaners and I}}
@@
 
+%%
+%%
 \subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
@@
 
+%%%
+%%%
+%%%
 \section{Etymology}
+%%
+%%
 \subsection{The difference between reuse and recycle}
@@
 
+Recycling can be viewed as down-cycling.
+The object smashed to the small particles to be used later in the production of something else.
+Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
+Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
+
+%%
+%%
 \subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
+Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.
+
 The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
@@
 
+%%%
+%%%
+%%%
 \section{Rubbish Theory}
@@
 
-\subsection{Implications of Rubbish Theory}
+%%
+%%
+\subsection{Rubbish Theory in Practice}
+% TODO paper analysis
 
+%%
+%%
+\subsection{Theoretical Analysis of Found Object}
+% TODO paper analysis
+
+%%%
+%%%
+%%%
 \section{Collage, Assemblage and the Found Object}
@@
 
+%%
+%%
 \subsection{Collage}
@@
 
+%%
+%%
 \subsection{Assemblage}
@@
 
+%%
+%%
 \subsection{the Found Object (Ready-mades)}
@@
 
+%%
+%%
 \subsection{\textit{Bricolage}}
@@
 
+%%
+%%
 \subsection{Folk Art}
+In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic.
+The nature of folk art is specific to its particular culture.
 
+%%
+%%
 \subsection{History of Consumption and Waste}
@@
 
+%%
+%%
 \subsection{Discussion}
@@
 
-\section{Artworks and trash}
-Types of artworks are created from trash.
+%%%
+%%%
+%%%
+\section{Artworks}
+Artist and artworks related with trash and their analysis. Stages of their works and methods.
 
-\section{Artwork, Project}
+Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond. \cite{}
 
+\begin{itemize}
+% From Maite Zubiaurre, ReVista Garbage
+\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
+It is that particular type of trash meet in the public places.
+trash left behind, trash on the sidewalk, squished, squashed, and weathered.
+Filomena Cruz sees trash that we don’t want to see.
+A
+piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
+    \caption{Road Kill by Filomena Cruz}
+    \label{fig:FilomenaCruz_RoadKill_ReVista}
+\end{figure}
+
+\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
+
+% https://www.youtube.com/watch?v=sJxxdQox7n0
+\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.
+
+% http://www.eloisacartonera.com.ar/ENGversion.html
+\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
+urban pickers (\textit{cartoneros}) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.}
+\end{itemize}
+
+%%
+%%
+\subsection{Their statements}
+
+%%%
+%%%
+%%%
+\section{My Artwork/Project}
+
+%%
+%%
+\subsection{Functionality and Art Debate}
+From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
+Duchamp's works kills the functionality.
+It works beyond the functional perception.
+Moves the debate to the conceptual frame.
+However it is not every time case.
+Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value.
+Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else.
+\quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}.
+Therefore anything can be turned to art with a good idea.
+
+%%
+%%
 \subsection{Paper}
@@
 
+%
 \subsubsection{Environmental Impact}
@@
 
+%
 \subsubsection{History}
@@
 
+%
 \subsubsection{Production}
@@
 
+%
 \subsubsection{Uses}
@@
 
+%%
+%%
 \subsection{Why (package) paper?}
@@
 
-\section{Uncategorized ideas, references}
+%%
+%%
+\subsection{Why covering notebooks and books?}
+
+%%
+%%
+\subsection{Artistic tactics}
+Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.
+
+%%%
+%%%
+%%%
+\section{Literature review, discussions, ideas\ldots}
 Trash art is not collage (assemblage or found object) or fragments.
@@
 
+%%
+%%
 \subsection{Culture, Values, and Garbage}
@@
 
+%%
+%%
 \subsection{Garbage Art}
@@
 
+%%
+%%
 \subsection{Garbage in Modern Thought}
@@
 
+%
 \subsubsection{Categorization and Value}
@@
 
+%
 \subsubsection{Semiotic Context}
@@
 
+%%%
+%%%
+%%%
 \section{Archaeology of Garbage}
+
+%%
+%%
 \subsection{Garbology}
@@
 
+In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
+
+%%
+%%
 \subsection{Trash as History/Memory}
-\cite{bullock2012trash}
+Walter Benjamin's trash aesthetics and Adornos reflection. \cite{bullock2012trash}
+
+%%
+%%
+\subsection{Trash Aesthetics}
 

### 2015-09-24 main.tex
Artworks are extended.
Former-commit-id: 0a5682e5eee2b3b04844cb9c65fd504bc8ae5c4b

@@
 
+% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
+We relate to garbage daily.
+We use it, produce it and dispose of it.
+Endlessly.
+The most obsessive of us get rid of it as fast as we can.
+The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
+We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
+Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
+Particularly in the connection between
+garbage and the arts, I am interested in two questions.
+First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
+
 %
@@
 
-% <Part from "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
+% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
 Below part Explains journey of trash, its different steps.
@@
 
+Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest.
+
 %%
@@
 It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
+
+\subsection{In the context of Art}
+Many scholar used the word recycling when mentioning works uses trash and the concept of it.
+However they are not mentioning the meaning that is decomposing things to the their particles.
+What they is actually is reusing and combining things, concepts, creating new mixtures.
+
+% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
+Recycling has always been a common practice in the arts at least at a nonmaterial level.
+From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
+Take and put.
+De-contextualize and re-contextualize.
+In that sense, art, as a system, is an act of recycling.
 
@@
 
+\cite{greenberg1984collage}
+
 %%
@@
 
-Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond. \cite{}
+% FROM ReVista
+Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.
+
+% FROM Paola Ibarra ReVista
+Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
+Is there a limit to recycling and representation?
+Or is there a point at which waste cannot become art (or anything else)?
 
 \begin{itemize}
-% From Maite Zubiaurre, ReVista Garbage
+% FROM Maite Zubiaurre, ReVista Garbage
 \item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
@@
 piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
-\begin{figure}[h]
+  \begin{figure}[ht]
       \centering
@@
 \item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
-urban pickers (\textit{cartoneros}) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.}
+urban pickers (\textit{cartoneros}) who pick it from the streets.
+Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
+  \begin{figure}[ht]
+      \centering
+      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
+      \caption{Books covered by Eloisa Cartonera}
+      \label{fig:EloisaCartonera_Books}
+  \end{figure}
+
+% FROM Paola Ibarra, ReVista
+% Forever; Blue Yonder by artist Kyle Huffman
+% Too Too---Much Much by Thomas Hirschhorn
+% Autoconstrucción by Abraham Cruzvillegas
+% Pictures of Garbage by Vik Muniz
+
+% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
+
+% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
+% https://www.youtube.com/watch?v=v6IoEF_Tsrw
+\item Nick Quijano has some rules to create assemblages.
+\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
+As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
+Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
+
+% FROM Burning Messages BY MICHAEL WELLEN, ReVista
+%\item Antonio Berni
+
+% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
+\item Haiti case.
+When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
+It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
+When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
+When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
+It shows that working with trash and being clean healthy is not a contradiction.
+Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
+
+% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
+% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
+In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
+These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
+The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
+Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
+It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
+
 \end{itemize}
+
+Childs can enjoy with trash.
+I remember from my childhood, we collect crown cap and play with them.
+Some caps are found less and they worth more.
+We are looking everywhere for them.
+To make them flat we put them on the railways.
+After train passed we get perfect plat cap.
+At that time it is not trash for us.
+It has a value and part of our games and enjoy.
+To have fun a bunch of trash can be enough for us.
+
+In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life.
+By the artist or other parts are give them a new life.
+They can reborn as a different things.
+Do people collect them aware of it?
+Discarded items unites together with the hands of a artist.
+
+Trash is global topic men. When you talk about trash, everyone have ideas about it.
+
+Think a city that has trash monument in the every corner.
+created from their trash.
+merged with the city life and gaining unique cityscapes and aesthetics.
+or think that a museum a trash museum.
+Exhibits works of art embracing the trash in all aspects.
+Maybe done by the artist or the visitors from all around world.
+A place for garbage other than a landfill.
+Waiting their creator to meet again.
+What a great idea isn't it?
+Meeting their creators again.
+But this time their creator can recognize their trash.
+They transformed to totally new thing.
+Reborn.
+Transformed (Kafka, Gregor Samsa).
 

### 2015-09-25 main.tex
Practice of Value Creation
Former-commit-id: 7190b8dea9e5ade147aa31cec2ca0949b006407d

@@
-\documentclass[a4paper]{article}
+\documentclass[12pt]{article}
 \usepackage[english]{babel}
@@
 \usepackage{apacite}
+\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
 %\usepackage{setspace}
@@
 (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
+
+With the help of art discarded thing can be find a place in the society.
+This issue is examined through the trash which is discarded by the society.
+By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life.
+The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.
+
+From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
+Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
+In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
+Stages and expression of this practice is examined with my artwork in the context of art.
+
+Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
 \end{abstract}
-\keywords{trash, art}
+\keywords{trash, art, value creation}
 
@@
 %%%
-\section{Reality of trash (other side of production)}
+\section{What is trash?}
+In this thesis work to understand the different aspects of trash is a key element.
+Because as scholars agreed on it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
+Sometimes it is accepted as a problem that is need to carefully and seriously manged.
+On the other hand it is accepted as a source of diversity.
+(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
+Therefore we should ask these questions: What is trash?
+How does it became trash?
+Is it a end product or a source material?
+How much is it valuable?
+How much is it dangerous?
+
 %%
@@
 
+% TODO PRAP. REF.
 Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
@@
 However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(Trash as Treasure, BY WILLIAM L.
+(FROM Trash as Treasure, BY WILLIAM L.
 FASH AND E.
@@
 
+% TODO PRAP. REF.
 Literature is recycled material, a pretext for making more art.
@@
 For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(Recycle the Classics, BY DORIS SOMMER)
+(FROM Recycle the Classics, BY DORIS SOMMER)
 
 % From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
+% TODO PRAP. REF.
 We relate to garbage daily.
@@
 First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
+(BY PAOLA IBARRA)
 
@@
 This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the [for Vik Muniz] landfill.
+For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
 In other words there are different places to touch on trash.
@@
 Also in the later parts it draws attention to them.
+[PRAP, REF Maite Zubiaurre]
 
@@
 %
-\subsubsection{The Case of Zizek}
+\subsubsection{Examined-life, Zizek}
 (There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
@@
 However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing.
+He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
 He claims that it is ideological in the sense that wrong thinking important problems.
@@
 \subsubsection{Perspectives related with trash from different disciplines}
-Trash is ecological problems and it is treats the balance of it. Animals do not aware of plastics materials and eat them. Management problem of municipals.
+\begin{itemize}
+\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
+\item Management of it handled by generally by the municipals. 
+\end{itemize}
 
@@
 
-Wall-e resembles to giant dozers that moves and piles trash in the landfills.
 WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
 A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
+WALL-E resembles to giant dozers that moves and piles trash in the landfills.
 
@@
 
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?)
+(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
+Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
 
@@
 
-% TODO motivations of artists. their ideas about them.
+% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions that
 
@@
 
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest.
+Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
 
@@
 
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-Recycling has always been a common practice in the arts at least at a nonmaterial level.
+% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+Recycling has always been a common practice in the arts at least at a non-material level.
 From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
@@
 
+The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
+It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
+Finally the theory suggests that value emerges through our ways of seeing and placing objects.
+(From Liz Parsons)
+
 %%
@@
 \subsection{Rubbish Theory in Practice}
-% TODO paper analysis
+% TODO PRAP. REF.
+A key critique of the rubbish theory is its neglect of the practices of value creation.
+Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
+
+Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
+Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
+McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
+He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
+He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
+These rituals include those of possession, exchange, grooming and divestment.
+The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
+However he is not clear as to the practices which constitute these rituals.
+In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
+There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
+
+In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
+Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
+He focuses on the ‘commodity potential’ of things.
+‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
+However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
+This is where Thompson’s Rubbish Theory comes in.
+
+\subsubsection{Transients, Rubbish and Durables}
+The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
+The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
+Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
+Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
+He further observes that their category membership determines the way we act towards them.
+
+Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
+Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
+Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
+
+Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
+(Further there is similar analogy at Waste and Want.
+The author give the example of shoe and claim that thrash is relative.
+The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
+Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
+
+\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
+disappear into dust.
+But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
+
+\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
+Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
+It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
+
+\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
+Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
+Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
+The find may not involve objects which are new to us, it is possible to find some of ones own items if they have been hidden away long enough in an attic and thus made strange to us.
+The concept of the find also suggests that the found object has some qualities that others (or indeed ourselves) have in the past overlooked, as such it is closely related to ‘bringing to light’.
+The find may be extended to embrace features of objects as well as objects themselves.
+This directs us to their ‘potentialities’, objects may have been there all along but we’ve suddenly found them to be useful, likeable or beautiful.
+It might be that some aspect of them has simply been brought to our attention.
+Equally, as discussed below in relation to transforming objects, we may make alterations to objects which bring out their potential.
+The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
+
+\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
+
+\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
+Transformations may also involve the modification or updating of objects through painting, alteration or repair.
+Transformations may not only be based around creating new uses but also creating new looks.
+The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
 
@@
 % FROM Paola Ibarra, ReVista
-% Forever; Blue Yonder by artist Kyle Huffman
-% Too Too---Much Much by Thomas Hirschhorn
-% Autoconstrucción by Abraham Cruzvillegas
-% Pictures of Garbage by Vik Muniz
+%\item Forever; Blue Yonder by artist Kyle Huffman
+%\item Too Too---Much Much by Thomas Hirschhorn
+%\item Autoconstrucción by Abraham Cruzvillegas
+%\item Pictures of Garbage by Vik Muniz
 
 % FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
+%\item Daniel Lind-Ramos
 

### 2015-09-25 main.tex
Theoratical and Practical Analysis of Found Object
Former-commit-id: 4c90a5afefc2842693c8e9ab4c052900ba3a4928

@@
 \subsection{Theoretical Analysis of Found Object}
-% TODO paper analysis
+% TODO PRAP. REF.
+\subsubsection{Seeking Objects}
+As a species Homo sapiens has been gathering and collecting objects for thousands of years.
+Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
+The search for “things,” collecting them (Humphrey, 1979), and the need to embellish and make the ordinary special (Dissanayake, 1988) have been essential parts of the evolutionary process of human development (Bettinger, 1991; Dissanayake, 1992).
+For example, many early cave drawings occur around a natural feature within the cave such as a projection or indentation (Bahn, 1998; Lewis-Williams, 2004), making these natural features potentially comparable to found objects in modern and contemporary art (Read, 1930).
+When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
+Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
+
+In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
+Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
+Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
+Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, & Sherry, 1989).
+These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
+A form of cultural reuse, the process
+of salvaging and using found and second-hand objects has potential implications for \ldots
+
+% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
+
+% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
+To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
+This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
+
+\subsubsection{Found Objects in Art}
+The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
+It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
+The junk object becomes transformed into the valued found object.
+Objet trouve ́ , translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
+His earliest known application for an objet trouve ́ was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
+97) and labeled it a work of art.
+A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
+These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
+
+Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
+169), referred to as objets trouve ́s in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
+170).
+The finder discovers an unrealised significance in the object.
+A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
+He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi & Rochberg-Halton, 1981).
+
+How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
+(Important points a gap in the literature.
+Although Parsons article analyze practices, it is not very broad and detailed.
+Further what is the importance of it is missing.)
+
+Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
+
+\textbf{Motivations and found object practice:}
+\begin{itemize}
+\item Discovery and engagement
+  \begin{itemize}
+  \item Seeking out: The adventure of hunting
+  \item Finding the unexpected
+  \item The location of discovery
+  \item Metamorphosis and transformation: Imagining a use for the object
+  \item Creative action
+  \end{itemize}
+\item History and time past
+  \begin{itemize}
+  \item Trigger of personal memories
+  \item The object’s story: Reflection about earlier “life” of object and previous owner
+  \item Capturing something elusive: Making sense of an unknown past
+  \end{itemize}
+\item The symbolic and functional object
+  \begin{itemize}
+  \item Aesthetic properties: Visual, tactile, original
+  \item Cost: The thrill of a free find
+  \item Evocative: More interesting than something new
+  \item Useable solutions for practical problems
+  \end{itemize}
+\item Psychological processes
+  \begin{itemize}
+  \item Personal resourcefulness
+  \item Impact on memory, emotion, cognition
+  \item Meaningfulness of object
+  \item Arouses interest: Motivates
+  \item Social engagement
+  \end{itemize}
+\item Ecological affirmation
+  \begin{itemize}
+  \item Environmental concerns
+  \item Against the cult of the new: Slowing down consumption
+  \item Transforming rubbish
+  \end{itemize}
+\end{itemize}
+
+The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
+The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
+
+[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
 
@@
 
+\item Joseph Cornell
+
 \end{itemize}

### 2015-09-26 main.tex
Motivations extended.
Former-commit-id: 076efc0c931d41d0faa74070b6afb169b332adf2

@@
 Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
-Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, & Sherry, 1989).
+Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, \& Sherry, 1989).
 These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
@@
 The junk object becomes transformed into the valued found object.
-Objet trouve ́ , translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve ́ was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
+Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
+His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
 97) and labeled it a work of art.
@@
 Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve ́s in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
+169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
 170).
@@
 He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi & Rochberg-Halton, 1981).
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
 
@@
 
+Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
+The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
+When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
+Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
+This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
+
+An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
+Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
+
+Results of this study also support consideration of found objects as important artifacts that are signifiers of cultural meaning.
+
 [TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
@@
 
+\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
+
 \end{itemize}
@@
 
+% TODO PRAP.
+Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing.
+To me art is communication of an idea or an emotion, while craft is the physical manipulation of material.
+An object can easily be both, either, or neither.
+A sculpture, for example, may communicate, but it was constructed using craft.
+Likewise a teapot can communicate an idea, but it was crafted.
+Function is misleading and no distinction.
+Functional objects can still communicate ideas, so art can be functional.
+One object could be viewed two ways: if you look at the way it was made and the materials used, you are looking at its craft, if you think about its ideas, you are viewing it as art.
+An object could have been crafted, but contain no art.
+Even a painting can be crafted but artless.
+A ready-made might be art with no craft.
+I very much like the idea of a spectrum.
+One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.
+
 %%

### 2015-09-27 main.tex
My artwork steps
Former-commit-id: e225a9e56867b09d4de3dd644880c1f53142a1fb

@@
 
-Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
+\textbf{Driving questions} Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again.
+
+\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
+
+\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims.
+Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
 \end{abstract}
-\keywords{trash, art, value creation}
+\keywords{trash, art, value creation, transformation}
 
@@
 Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or compostable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
+It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
 Even in the landfill, it does not remain still.
@@
 %%
+\subsection{Art and activism}
+
+%%
+%%
 \subsection{History of Consumption and Waste}
@@
 %%
-\subsection{Their statements}
+\subsection{Artist statements}
 
@@
 \section{My Artwork/Project}
+Here stages of my artwork are listed:
+\begin{itemize}
+\item \textbf{Memories.} As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
+One of these (First of them) is from my primary school teacher.
+When I was third class my teacher give us a homework to bring colorful paper to make something(whatever it is I don't remember).
+The day after we bring some colorful paper but she did not.
+Instead of this she bring paper cut out from packages that are colorful, shinny and qualify.
+And I remember clearly that she suggest that same for us.
+Do not throw out packages, look for the useful parts and keep them to use later.
+\item \textbf{Motivation.} I can not throw them away.
+When I throw them I became sad for them.
+I have to find something useful for it.
+Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
+We are humans that can produce, transform items.
+One of most developed species in the earth that produce and use tools.
+There is a lot of effort to produce thrown away and it seems that all this efforts are wasted.
+What I mention is not related about ultimate productivity.
+It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using.
+Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.
+\item \textbf{Collecting.} One of the most found trash in my habitat is paper.
+I work at METU Technopolis, live at 100.
+yil which is the nearest settlement to METU and study at Bilkent.
+People live there commonly use paper and needs paper.
+Paper is nearly everywhere.
+Reusing the paper is not limited with recycling of it.
+There is a another ways of it.
+When we recycle them actually we again send away them and use it as we all know.
+(industrial papers and notebooks.) There is no richness here.
+Same type of paper.
+Produced after a industrial process.
+I collected them from my friends (people that have communicate often).
+Sometimes I collect them from trash bins and roads.
+\item \textbf{Transforming.} I turned them to notebooks.
+Actually I use it for my self.
+And while I was using of it I am very proud of it.
+I am studying nearly more 20 twenty years and I have always need for notebooks and use them.
+It is some sort of passion for me notebooks.
+Because I always admire notebook beautifully design or uniquely designed.
+I collect them whenever I find and most of the time I only save them for later use.
+\end{itemize}
 
@@
 %%
+\subsection{Why giving away?}
+Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
+
+%%
+%%
+\subsection{Why in the public space?}
+To reach more audience.
+Actually the audience is out of the art galleries.
+They are walking in the streets.
+Putting them to next to people is much more effective.
+It is not visible and nearly it is hided from society.
+It is dirty.
+Removed from the society.
+There is a effort to hide them away.
+However in this project it is again showed to the society.
+Because it is revisited and reclaimed.
+
+%%
+%%
 \subsection{Artistic tactics}
-Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.
+Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+
+\subsection{Why is it art?}
+Uses artistic methods?
+Does it represent anything?
+The idea is transforming things.
+Anything can be transformed and re-contextualized again.
+The limitation is our imagination and approach.
+It has a claim.
+In can be analyzed and examined in the context of art.
+It is hard to say that something is art or not.
+However it can be examined in the context of art.
+There are artworks reject art galleries.
+There are artworks also reject commodities.
+It has purpose that.
+spread out the idea in different manner.
+Subverts peoples ideas.
+
+The work aims to liberate the imagination and change the way people see the trash.
 
@@
 \subsection{Trash as History/Memory}
-Walter Benjamin's trash aesthetics and Adornos reflection. \cite{bullock2012trash}
+% TODO From encylopedia
+\cite{bullock2012trash}
 
@@
 \subsection{Trash Aesthetics}
+Walter Benjamin's trash aesthetics and Adornos reflection.
+
+%%%
+%%%
+%%%
+\section{Sample Phrases}
 

### 2015-09-28 chapter2.tex
format changed.
Former-commit-id: 268481e7bc2309b7a723363c8a58ad53557d090a

--- 2015-09-26 main.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage{apacite}
-\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
-%\usepackage{setspace}
-%\doublespacing
-\usepackage{graphicx}
-%\graphicspath{ {graphics/} }
-
-% Keywords command
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
-% Quotation command
-\providecommand{\quotes}[1]{``#1''}
-\providecommand{\singlequotes}[1]{`#1'}
-
-\title{Thesis Draft}
-\author{Mustafa İlhan}
-
-\begin{document}
-\maketitle
-
-%%%
-%%%
-%%%
-\begin{abstract}
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
-Why and how are they used by the artist?
-Are there any differences with the original items compared to discarded items?
-(In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
-(and also in which scope?
-medium, message, life practice\ldots)
-
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects how one's lives and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
-
-With the help of art discarded thing can be find a place in the society.
-This issue is examined through the trash which is discarded by the society.
-By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life.
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.
-
-From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
-Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
-In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
-Stages and expression of this practice is examined with my artwork in the context of art.
-
-Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
-\end{abstract}
-\keywords{trash, art, value creation}
+\chapter{Theory of Trash}
 
@@
 \item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it handled by generally by the municipals. 
+\item Management of it handled by the municipals generally.
+\item Technological perspectives
 \end{itemize}
@@
 %
-\subsubsection{Comparison of trashes}
+\subsubsection{How does it become(turn to) art?}
+How does it draw attention of artist, and also mine?
+
+%
+\subsubsection{Types and Comparison of trashes}
 The complexity of produced trashes of societies is increasing.
@@
 
-%
-\subsubsection{Types of trashes}
 Different production process generates different types of trash. According to production process, decomposition process\ldots
@@
 In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
-
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
 
@@
 %%%
-\section{Collage, Assemblage and the Found Object}
-In this chapter root of using objects in the artworks is examined.
-Using objects on artworks beyond their intended purpose.
-Developing artworks not only painting but also using paper and other stuff by pasting them together.
-
-%%
-%%
-\subsection{Collage}
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
-
-\cite{greenberg1984collage}
-
-%%
-%%
-\subsection{Assemblage}
-Assemblage work produced by the incorporation of everyday objects into a composition.
-It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
-Diverse range of things can be used production of work.
-In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
-William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
-
-%%
-%%
-\subsection{the Found Object (Ready-mades)}
-Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
-Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).
-Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
-The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
-
-%%
-%%
-\subsection{\textit{Bricolage}}
-Something constructed using whatever was available at the time.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-%%
-%%
-\subsection{Folk Art}
-In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic.
-The nature of folk art is specific to its particular culture.
-
-%%
-%%
-\subsection{History of Consumption and Waste}
-"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
-Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
-Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
-A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Discussion}
-Are artworks made from trash just examples of collage and assemblage or more than from them?
-What about the experience and interaction with other people?
-Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
-But all of them work in fragments, combine many objects together.
-
-Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
-
-In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
-
-%%%
-%%%
-%%%
-\section{Artworks}
-Artist and artworks related with trash and their analysis. Stages of their works and methods.
-
-% FROM ReVista
-Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.
-
-% FROM Paola Ibarra ReVista
-Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
-Is there a limit to recycling and representation?
-Or is there a point at which waste cannot become art (or anything else)?
-
-\begin{itemize}
-% FROM Maite Zubiaurre, ReVista Garbage
-\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
-It is that particular type of trash meet in the public places.
-trash left behind, trash on the sidewalk, squished, squashed, and weathered.
-Filomena Cruz sees trash that we don’t want to see.
-A
-piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-      \caption{Road Kill by Filomena Cruz}
-      \label{fig:FilomenaCruz_RoadKill_ReVista}
-  \end{figure}
-
-\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
-
-% https://www.youtube.com/watch?v=sJxxdQox7n0
-\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.
-
-% http://www.eloisacartonera.com.ar/ENGversion.html
-\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
-urban pickers (\textit{cartoneros}) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
-      \caption{Books covered by Eloisa Cartonera}
-      \label{fig:EloisaCartonera_Books}
-  \end{figure}
-
-% FROM Paola Ibarra, ReVista
-%\item Forever; Blue Yonder by artist Kyle Huffman
-%\item Too Too---Much Much by Thomas Hirschhorn
-%\item Autoconstrucción by Abraham Cruzvillegas
-%\item Pictures of Garbage by Vik Muniz
-
-% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
-%\item Daniel Lind-Ramos
-
-% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
-% https://www.youtube.com/watch?v=v6IoEF_Tsrw
-\item Nick Quijano has some rules to create assemblages.
-\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
-As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
-Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
-
-% FROM Burning Messages BY MICHAEL WELLEN, ReVista
-%\item Antonio Berni
-
-% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
-\item Haiti case.
-When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
-It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
-When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
-When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
-It shows that working with trash and being clean healthy is not a contradiction.
-Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
-
-% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
-% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
-In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
-These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
-The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
-Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
-It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
-
-\item Joseph Cornell
-
-\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
-
-\end{itemize}
-
-Childs can enjoy with trash.
-I remember from my childhood, we collect crown cap and play with them.
-Some caps are found less and they worth more.
-We are looking everywhere for them.
-To make them flat we put them on the railways.
-After train passed we get perfect plat cap.
-At that time it is not trash for us.
-It has a value and part of our games and enjoy.
-To have fun a bunch of trash can be enough for us.
-
-In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life.
-By the artist or other parts are give them a new life.
-They can reborn as a different things.
-Do people collect them aware of it?
-Discarded items unites together with the hands of a artist.
-
-Trash is global topic men. When you talk about trash, everyone have ideas about it.
-
-Think a city that has trash monument in the every corner.
-created from their trash.
-merged with the city life and gaining unique cityscapes and aesthetics.
-or think that a museum a trash museum.
-Exhibits works of art embracing the trash in all aspects.
-Maybe done by the artist or the visitors from all around world.
-A place for garbage other than a landfill.
-Waiting their creator to meet again.
-What a great idea isn't it?
-Meeting their creators again.
-But this time their creator can recognize their trash.
-They transformed to totally new thing.
-Reborn.
-Transformed (Kafka, Gregor Samsa).
-
-%%
-%%
-\subsection{Their statements}
-
-%%%
-%%%
-%%%
-\section{My Artwork/Project}
-
-%%
-%%
-\subsection{Functionality and Art Debate}
-From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
-Duchamp's works kills the functionality.
-It works beyond the functional perception.
-Moves the debate to the conceptual frame.
-However it is not every time case.
-Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value.
-Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else.
-\quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}.
-Therefore anything can be turned to art with a good idea.
-
-% TODO PRAP.
-Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing.
-To me art is communication of an idea or an emotion, while craft is the physical manipulation of material.
-An object can easily be both, either, or neither.
-A sculpture, for example, may communicate, but it was constructed using craft.
-Likewise a teapot can communicate an idea, but it was crafted.
-Function is misleading and no distinction.
-Functional objects can still communicate ideas, so art can be functional.
-One object could be viewed two ways: if you look at the way it was made and the materials used, you are looking at its craft, if you think about its ideas, you are viewing it as art.
-An object could have been crafted, but contain no art.
-Even a painting can be crafted but artless.
-A ready-made might be art with no craft.
-I very much like the idea of a spectrum.
-One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.
-
-%%
-%%
-\subsection{Paper}
-"Paper is an indispensable product throughout the world.
-Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
-In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
-Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
-
-%
-\subsubsection{Environmental Impact}
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
-
-Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
-Recycling paper can greatly diminish demand for virgin fiber from wood.
-However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
-It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
-
-%
-\subsubsection{History}
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
-
-%
-\subsubsection{Production}
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
-
-%
-\subsubsection{Uses}
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
-
-%%
-%%
-\subsection{Why (package) paper?}
-Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
-
-%%
-%%
-\subsection{Why covering notebooks and books?}
-
-%%
-%%
-\subsection{Artistic tactics}
-Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.
-
-%%%
-%%%
-%%%
 \section{Literature review, discussions, ideas\ldots}
@@
 \subsection{Trash Aesthetics}
+%Walter Benjamin's trash aesthetics and Adornos reflection. 
+\quotes{Benjamin’s approach to history is through ‘trash’---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
+Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
+In the face of the endless proliferation of trash, Benjamin potentially suggests a ‘trash aesthetics’ that could be used radically and critically to attend to the everyday.
+The method might be thought of in terms of ‘recycling’ – an ecology of everyday experience.
 
-\bibliographystyle{apacite}
-\bibliography{ref}
+% HERE Same sample phrases are listed you can use them:
 
-\end{document}
+% The artist thinks, acts, performs music, and writes outside the framework that society has created.
+
+% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
+
+% Outline:
+% Weak points:
+% Where to study next.

### 2015-09-28 chapter3.tex
format changed.
Former-commit-id: 268481e7bc2309b7a723363c8a58ad53557d090a

--- 2015-09-25 main.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage{apacite}
-\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
-%\usepackage{setspace}
-%\doublespacing
-\usepackage{graphicx}
-%\graphicspath{ {graphics/} }
-
-% Keywords command
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
-% Quotation command
-\providecommand{\quotes}[1]{``#1''}
-\providecommand{\singlequotes}[1]{`#1'}
-
-\title{Thesis Draft}
-\author{Mustafa İlhan}
-
-\begin{document}
-\maketitle
-
-%%%
-%%%
-%%%
-\begin{abstract}
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
-Why and how are they used by the artist?
-Are there any differences with the original items compared to discarded items?
-(In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
-(and also in which scope?
-medium, message, life practice\ldots)
-
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects how one's lives and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
-
-With the help of art discarded thing can be find a place in the society.
-This issue is examined through the trash which is discarded by the society.
-By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life.
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.
-
-From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
-Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
-In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
-Stages and expression of this practice is examined with my artwork in the context of art.
-
-Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
-\end{abstract}
-\keywords{trash, art, value creation}
-
-%%%
-%%%
-%%%
-\section{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
-% TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
-Literature is recycled material, a pretext for making more art.
-I learned this distillation of lots of literary criticism in workshops with children.
-I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
-For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between
-garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
-%
-\subsubsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
-
-% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
-Object moves and also trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
-
-Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or compostable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
-% >
-
-%
-\subsubsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from
-our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-%
-\subsubsection{Perspectives related with trash from different disciplines}
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it handled by generally by the municipals. 
-\end{itemize}
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
-In other word the problem is our technology which is not perfect.
-(and I'm not sure that at some point that technology will reach to the perfection or not.)
-
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
-\quotes{What is happening to trash is what is going to happen to us.
-We’re all going to end up in a dump, and we’re going to decompose.
-That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-\quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{}
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-
-%
-\subsubsection{Throw away culture}
-Continuously consuming things and disposing of something.
-It is an important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
-(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
-
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
-
-%
-\subsubsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
-
-%
-\subsubsection{Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-
-%
-\subsubsection{Types of trashes}
-Different production process generates different types of trash. According to production process, decomposition process\ldots
-
-%
-\subsubsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
-There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
-Even if they are excluded, there is also life for them.
-
-% TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
-
-% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions that
-
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
-
-%
-\subsubsection{The case of \quotes{The Gleaners and I}}
-The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
-The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
-This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
-
-It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
-Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
-
-\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
-Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
-However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
-Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
-She is gleaning images.
-The Gleaners and I far more than document the lives of gleaners.
-It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
-
-The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
-And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
-
-Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
-There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-Seeing the value in what someone else has defined as trash is an art in itself.
-
-Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
-She keeps light to the modern life gleaners that are not visible every time.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
-In other word we can be subject of the refusal.
-At some point she become the subject of the thing that she track.
-
-There are many aspects of this documentary film.
-First draw attention the practice of gleaning.
-The discarded items that are not fit in the industrial standards because of their shape, color etc.
-Even if these items are discarded and we are not aware of them, there is also another life for them.
-Modern life gleaners feed from them.
-In another words someones trash becomes another trash.
-There are people live the boundaries of consumption societies.
-They create their life from the unwanted items.
-what the society refuses, they find a life or create a life from them.
-Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
-(as also Zizek mentions that love is not idealization.
-But the industrial processes has some standards and beyond that standards there is not a place for everyone.
-Life is being lived in the cites is somehow idealized life or tried to be idealized life.
-beyond the border of the urban there is new life generated.
-What is not succeed in the cities succeed outside of it.)
-
-She uses unconsciously recorded pieces in the film.
-\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
-It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
-She sets this scene to a jazz soundtrack.
-While watching the scene I was certainly confused.
-Why is this in here?
-What does this have to do with gleaning?
-And certainly why did the scene last so long?
-But there was also something lovely about it.
-Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
-I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
-Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
-Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
-Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
-Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
-Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
-The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
-
-Refused is not only foods and trash.
-there are a lot of things that are pushed outside border of the society.
-She talks and investigates artist that are using discarded items in the artworks.
-What people not found anything the artist see countless possibilities from them.
-There is always alternative ways to see something different.
-Giving life or finding life from discarded life.
-
-The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
-
-Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
-There should reason for this?
-For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
-They require it to sustain their life.
-Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
-What gleaning means become more open (or powerful).
-It draws a picture of body combination of different parts (connected, dependent to the each other).
-The reason of gleaning varies but the fact that gleaning is continues in different forms.
-
-She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
-One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
-
-The Gleaners And I is not an environmental film.
-Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
-
-The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
-Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
-The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
-One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-
-Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
-Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
-He specializes in reliefs and assemblages made entirely from discarded objects and junk.
-In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
-
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
-
-%%%
-%%%
-%%%
-\section{Etymology}
-%%
-%%
-\subsection{The difference between reuse and recycle}
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
-Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-%%
-%%
-\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
-Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.
-
-The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
-
-Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is a study of waste as a social science.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
-
-Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-
-\subsection{In the context of Art}
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling.
-
-%%%
-%%%
-%%%
-\section{Rubbish Theory}
-Objects have a lifetime and they don't remain same through that lifetime.
-Their value, usage, location change over time.
-During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
-Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
-Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
-This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
-The theory looks at how some of these objects then regain value, such as antiques or historic homes.
-It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
-The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.
-
-Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
-Thompson label some transitions as possible and the others as impossible.
-"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
-Further, he does not allow move from transient to durable.
-However, Duchamp's fountain breaks this rule.
-Because urine used as a fountain is still functional and have a place in the market.
-In another word, it is not rubbish.
-This urine with the approach of Duchamp turned to be an artwork.
-It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
-
-In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
-(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
-transforming them creates new a value system?
-or just finding place existing value system.
-by the way there is a value theory related with (or inside of) game theory.)
-
-Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
-
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
-
-The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
-It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
-Finally the theory suggests that value emerges through our ways of seeing and placing objects.
-(From Liz Parsons)
-
-%%
-%%
-\subsection{Rubbish Theory in Practice}
-% TODO PRAP. REF.
-A key critique of the rubbish theory is its neglect of the practices of value creation.
-Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
-
-Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
-Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
-McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
-He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
-He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
-These rituals include those of possession, exchange, grooming and divestment.
-The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
-However he is not clear as to the practices which constitute these rituals.
-In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
-There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
-
-In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
-Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
-He focuses on the ‘commodity potential’ of things.
-‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
-However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
-This is where Thompson’s Rubbish Theory comes in.
-
-\subsubsection{Transients, Rubbish and Durables}
-The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
-The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
-Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
-Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
-He further observes that their category membership determines the way we act towards them.
-
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-
-Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
-(Further there is similar analogy at Waste and Want.
-The author give the example of shoe and claim that thrash is relative.
-The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
-Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
-
-\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
-disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
-
-\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
-Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
-It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
-
-\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
-Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
-Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
-The find may not involve objects which are new to us, it is possible to find some of ones own items if they have been hidden away long enough in an attic and thus made strange to us.
-The concept of the find also suggests that the found object has some qualities that others (or indeed ourselves) have in the past overlooked, as such it is closely related to ‘bringing to light’.
-The find may be extended to embrace features of objects as well as objects themselves.
-This directs us to their ‘potentialities’, objects may have been there all along but we’ve suddenly found them to be useful, likeable or beautiful.
-It might be that some aspect of them has simply been brought to our attention.
-Equally, as discussed below in relation to transforming objects, we may make alterations to objects which bring out their potential.
-The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
-
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
-
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
-Transformations may also involve the modification or updating of objects through painting, alteration or repair.
-Transformations may not only be based around creating new uses but also creating new looks.
-The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
-
-%%
-%%
-\subsection{Theoretical Analysis of Found Object}
-% TODO PRAP. REF.
-\subsubsection{Seeking Objects}
-As a species Homo sapiens has been gathering and collecting objects for thousands of years.
-Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
-The search for “things,” collecting them (Humphrey, 1979), and the need to embellish and make the ordinary special (Dissanayake, 1988) have been essential parts of the evolutionary process of human development (Bettinger, 1991; Dissanayake, 1992).
-For example, many early cave drawings occur around a natural feature within the cave such as a projection or indentation (Bahn, 1998; Lewis-Williams, 2004), making these natural features potentially comparable to found objects in modern and contemporary art (Read, 1930).
-When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
-Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
-
-In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
-Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
-Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
-Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, & Sherry, 1989).
-These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
-A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots
-
-% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
-
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
-
-\subsubsection{Found Objects in Art}
-The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve ́ , translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve ́ was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve ́s in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi & Rochberg-Halton, 1981).
-
-How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
-
-\textbf{Motivations and found object practice:}
-\begin{itemize}
-\item Discovery and engagement
-  \begin{itemize}
-  \item Seeking out: The adventure of hunting
-  \item Finding the unexpected
-  \item The location of discovery
-  \item Metamorphosis and transformation: Imagining a use for the object
-  \item Creative action
-  \end{itemize}
-\item History and time past
-  \begin{itemize}
-  \item Trigger of personal memories
-  \item The object’s story: Reflection about earlier “life” of object and previous owner
-  \item Capturing something elusive: Making sense of an unknown past
-  \end{itemize}
-\item The symbolic and functional object
-  \begin{itemize}
-  \item Aesthetic properties: Visual, tactile, original
-  \item Cost: The thrill of a free find
-  \item Evocative: More interesting than something new
-  \item Useable solutions for practical problems
-  \end{itemize}
-\item Psychological processes
-  \begin{itemize}
-  \item Personal resourcefulness
-  \item Impact on memory, emotion, cognition
-  \item Meaningfulness of object
-  \item Arouses interest: Motivates
-  \item Social engagement
-  \end{itemize}
-\item Ecological affirmation
-  \begin{itemize}
-  \item Environmental concerns
-  \item Against the cult of the new: Slowing down consumption
-  \item Transforming rubbish
-  \end{itemize}
-\end{itemize}
-
-The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
+\chapter{Artworks}
 
@@
 %%
-\subsection{the Found Object (Ready-mades)}
+\subsection{Found Object (Ready-mades)}
 Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
@@
 %%
-\subsection{\textit{Bricolage}}
+\subsection{Bricolage}
 Something constructed using whatever was available at the time.
@@
 \cite{levi1966savage}
+
+\cite{strasser1999waste}
 
@@
 %%
+\subsection{Art and activism}
+
+%%
+%% TODO change here
 \subsection{History of Consumption and Waste}
@@
 %%
-%%
+%% TODO change here
 \subsection{Discussion}
@@
 
+\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
+
+\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning}
+
 \end{itemize}
@@
 %%
-\subsection{Their statements}
-
-%%%
-%%%
-%%%
-\section{My Artwork/Project}
+\subsection{Artist statements}
 
@@
 %%
-\subsection{Functionality and Art Debate}
-From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
-Duchamp's works kills the functionality.
-It works beyond the functional perception.
-Moves the debate to the conceptual frame.
-However it is not every time case.
-Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value.
-Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else.
-\quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}.
-Therefore anything can be turned to art with a good idea.
+\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
+\begin{itemize}
+\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
+\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
+\item Try to find a new value and meaning from the discarded material that are useless anymore.
+To explore a new approach, new way.
+Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
+Trash to treasure.
+\item Using discarded item to represent other discarded things by the ruling ideology or approach.
+For example, trash can be used to represent refugees.
+The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
+In other words, refugees have potential but we see them as players that will change our current system.
+Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
+Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
+\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
+\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
+\item Instead of a world that produce trash, how could it be a world created from trash?
+\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
+It also signifies that trash still has a good quality to used with new materials.
+Creating composite products from new and reused items.
+Using the valuable thing with the invaluable thing.
+It becomes more valuable or less valuable.
+Depends on the perception.
+\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
+\end{itemize}
 
-%%
-%%
-\subsection{Paper}
-"Paper is an indispensable product throughout the world.
-Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
-In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
-Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
-
-%
-\subsubsection{Environmental Impact}
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
-
-Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
-Recycling paper can greatly diminish demand for virgin fiber from wood.
-However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
-It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
-
-%
-\subsubsection{History}
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
-
-%
-\subsubsection{Production}
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
-
-%
-\subsubsection{Uses}
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
-
-%%
-%%
-\subsection{Why (package) paper?}
-Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
-
-%%
-%%
-\subsection{Why covering notebooks and books?}
-
-%%
-%%
 \subsection{Artistic tactics}
-Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.
-
-%%%
-%%%
-%%%
-\section{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
-
-%%
-%%
-\subsection{Garbage Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
-
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
-
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
-
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%%
-%%%
-%%%
-\section{Archaeology of Garbage}
-
-%%
-%%
-\subsection{Garbology}
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
-
-%%
-%%
-\subsection{Trash as History/Memory}
-Walter Benjamin's trash aesthetics and Adornos reflection. \cite{bullock2012trash}
-
-%%
-%%
-\subsection{Trash Aesthetics}
-
-\bibliographystyle{apacite}
-\bibliography{ref}
-
-\end{document}

### 2015-09-28 chapter4.tex
format changed.
Former-commit-id: 268481e7bc2309b7a723363c8a58ad53557d090a

--- 2015-09-27 main.tex
@@
-\documentclass[12pt]{article}
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage{apacite}
-\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
-%\usepackage{setspace}
-%\doublespacing
-\usepackage{graphicx}
-%\graphicspath{ {graphics/} }
-
-% Keywords command
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
-% Quotation command
-\providecommand{\quotes}[1]{``#1''}
-\providecommand{\singlequotes}[1]{`#1'}
-
-\title{Thesis Draft}
-\author{Mustafa İlhan}
-
-\begin{document}
-\maketitle
-
-%%%
-%%%
-%%%
-\begin{abstract}
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
-Why and how are they used by the artist?
-Are there any differences with the original items compared to discarded items?
-(In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
-(and also in which scope?
-medium, message, life practice\ldots)
-
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects how one's lives and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
-
-With the help of art discarded thing can be find a place in the society.
-This issue is examined through the trash which is discarded by the society.
-By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life.
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.
-
-From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
-Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
-In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
-Stages and expression of this practice is examined with my artwork in the context of art.
-
-\textbf{Driving questions} Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again.
-
-\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
-
-\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims.
-Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
-\end{abstract}
-\keywords{trash, art, value creation, transformation}
-
-%%%
-%%%
-%%%
-\section{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
-% TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
-Literature is recycled material, a pretext for making more art.
-I learned this distillation of lots of literary criticism in workshops with children.
-I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
-For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between
-garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
-%
-\subsubsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
-
-% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
-Object moves and also trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
-
-Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
-% >
-
-%
-\subsubsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from
-our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-%
-\subsubsection{Perspectives related with trash from different disciplines}
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it handled by generally by the municipals. 
-\end{itemize}
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
-In other word the problem is our technology which is not perfect.
-(and I'm not sure that at some point that technology will reach to the perfection or not.)
-
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
-\quotes{What is happening to trash is what is going to happen to us.
-We’re all going to end up in a dump, and we’re going to decompose.
-That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-\quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{}
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-
-%
-\subsubsection{Throw away culture}
-Continuously consuming things and disposing of something.
-It is an important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
-(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
-
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
-
-%
-\subsubsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
-
-%
-\subsubsection{Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-
-%
-\subsubsection{Types of trashes}
-Different production process generates different types of trash. According to production process, decomposition process\ldots
-
-%
-\subsubsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
-There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
-Even if they are excluded, there is also life for them.
-
-% TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
-
-% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions that
-
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
-
-%
-\subsubsection{The case of \quotes{The Gleaners and I}}
-The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
-The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
-This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
-
-It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
-Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
-
-\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
-Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
-However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
-Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
-She is gleaning images.
-The Gleaners and I far more than document the lives of gleaners.
-It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
-
-The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
-And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
-
-Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
-There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-Seeing the value in what someone else has defined as trash is an art in itself.
-
-Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
-She keeps light to the modern life gleaners that are not visible every time.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
-In other word we can be subject of the refusal.
-At some point she become the subject of the thing that she track.
-
-There are many aspects of this documentary film.
-First draw attention the practice of gleaning.
-The discarded items that are not fit in the industrial standards because of their shape, color etc.
-Even if these items are discarded and we are not aware of them, there is also another life for them.
-Modern life gleaners feed from them.
-In another words someones trash becomes another trash.
-There are people live the boundaries of consumption societies.
-They create their life from the unwanted items.
-what the society refuses, they find a life or create a life from them.
-Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
-(as also Zizek mentions that love is not idealization.
-But the industrial processes has some standards and beyond that standards there is not a place for everyone.
-Life is being lived in the cites is somehow idealized life or tried to be idealized life.
-beyond the border of the urban there is new life generated.
-What is not succeed in the cities succeed outside of it.)
-
-She uses unconsciously recorded pieces in the film.
-\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
-It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
-She sets this scene to a jazz soundtrack.
-While watching the scene I was certainly confused.
-Why is this in here?
-What does this have to do with gleaning?
-And certainly why did the scene last so long?
-But there was also something lovely about it.
-Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
-I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
-Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
-Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
-Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
-Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
-Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
-The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
-
-Refused is not only foods and trash.
-there are a lot of things that are pushed outside border of the society.
-She talks and investigates artist that are using discarded items in the artworks.
-What people not found anything the artist see countless possibilities from them.
-There is always alternative ways to see something different.
-Giving life or finding life from discarded life.
-
-The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
-
-Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
-There should reason for this?
-For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
-They require it to sustain their life.
-Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
-What gleaning means become more open (or powerful).
-It draws a picture of body combination of different parts (connected, dependent to the each other).
-The reason of gleaning varies but the fact that gleaning is continues in different forms.
-
-She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
-One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
-
-The Gleaners And I is not an environmental film.
-Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
-
-The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
-Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
-The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
-One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-
-Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
-Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
-He specializes in reliefs and assemblages made entirely from discarded objects and junk.
-In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
-
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
-
-%%%
-%%%
-%%%
-\section{Etymology}
-%%
-%%
-\subsection{The difference between reuse and recycle}
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
-Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-%%
-%%
-\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
-Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.
-
-The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
-
-Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is a study of waste as a social science.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
-
-Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-
-\subsection{In the context of Art}
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling.
-
-%%%
-%%%
-%%%
-\section{Rubbish Theory}
-Objects have a lifetime and they don't remain same through that lifetime.
-Their value, usage, location change over time.
-During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
-Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
-Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
-This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
-The theory looks at how some of these objects then regain value, such as antiques or historic homes.
-It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
-The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.
-
-Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
-Thompson label some transitions as possible and the others as impossible.
-"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
-Further, he does not allow move from transient to durable.
-However, Duchamp's fountain breaks this rule.
-Because urine used as a fountain is still functional and have a place in the market.
-In another word, it is not rubbish.
-This urine with the approach of Duchamp turned to be an artwork.
-It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
-
-In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
-(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
-transforming them creates new a value system?
-or just finding place existing value system.
-by the way there is a value theory related with (or inside of) game theory.)
-
-Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
-
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
-
-The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
-It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
-Finally the theory suggests that value emerges through our ways of seeing and placing objects.
-(From Liz Parsons)
-
-%%
-%%
-\subsection{Rubbish Theory in Practice}
-% TODO PRAP. REF.
-A key critique of the rubbish theory is its neglect of the practices of value creation.
-Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
-
-Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
-Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
-McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
-He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
-He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
-These rituals include those of possession, exchange, grooming and divestment.
-The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
-However he is not clear as to the practices which constitute these rituals.
-In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
-There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
-
-In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
-Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
-He focuses on the ‘commodity potential’ of things.
-‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
-However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
-This is where Thompson’s Rubbish Theory comes in.
-
-\subsubsection{Transients, Rubbish and Durables}
-The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
-The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
-Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
-Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
-He further observes that their category membership determines the way we act towards them.
-
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-
-Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
-(Further there is similar analogy at Waste and Want.
-The author give the example of shoe and claim that thrash is relative.
-The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
-Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
-
-\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
-disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
-
-\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
-Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
-It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
-
-\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
-Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
-Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
-The find may not involve objects which are new to us, it is possible to find some of ones own items if they have been hidden away long enough in an attic and thus made strange to us.
-The concept of the find also suggests that the found object has some qualities that others (or indeed ourselves) have in the past overlooked, as such it is closely related to ‘bringing to light’.
-The find may be extended to embrace features of objects as well as objects themselves.
-This directs us to their ‘potentialities’, objects may have been there all along but we’ve suddenly found them to be useful, likeable or beautiful.
-It might be that some aspect of them has simply been brought to our attention.
-Equally, as discussed below in relation to transforming objects, we may make alterations to objects which bring out their potential.
-The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
-
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
-
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
-Transformations may also involve the modification or updating of objects through painting, alteration or repair.
-Transformations may not only be based around creating new uses but also creating new looks.
-The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
-
-%%
-%%
-\subsection{Theoretical Analysis of Found Object}
-% TODO PRAP. REF.
-\subsubsection{Seeking Objects}
-As a species Homo sapiens has been gathering and collecting objects for thousands of years.
-Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
-The search for “things,” collecting them (Humphrey, 1979), and the need to embellish and make the ordinary special (Dissanayake, 1988) have been essential parts of the evolutionary process of human development (Bettinger, 1991; Dissanayake, 1992).
-For example, many early cave drawings occur around a natural feature within the cave such as a projection or indentation (Bahn, 1998; Lewis-Williams, 2004), making these natural features potentially comparable to found objects in modern and contemporary art (Read, 1930).
-When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
-Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
-
-In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
-Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
-Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
-Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, \& Sherry, 1989).
-These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
-A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots
-
-% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
-
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
-
-\subsubsection{Found Objects in Art}
-The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
-
-How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
-
-\textbf{Motivations and found object practice:}
-\begin{itemize}
-\item Discovery and engagement
-  \begin{itemize}
-  \item Seeking out: The adventure of hunting
-  \item Finding the unexpected
-  \item The location of discovery
-  \item Metamorphosis and transformation: Imagining a use for the object
-  \item Creative action
-  \end{itemize}
-\item History and time past
-  \begin{itemize}
-  \item Trigger of personal memories
-  \item The object’s story: Reflection about earlier “life” of object and previous owner
-  \item Capturing something elusive: Making sense of an unknown past
-  \end{itemize}
-\item The symbolic and functional object
-  \begin{itemize}
-  \item Aesthetic properties: Visual, tactile, original
-  \item Cost: The thrill of a free find
-  \item Evocative: More interesting than something new
-  \item Useable solutions for practical problems
-  \end{itemize}
-\item Psychological processes
-  \begin{itemize}
-  \item Personal resourcefulness
-  \item Impact on memory, emotion, cognition
-  \item Meaningfulness of object
-  \item Arouses interest: Motivates
-  \item Social engagement
-  \end{itemize}
-\item Ecological affirmation
-  \begin{itemize}
-  \item Environmental concerns
-  \item Against the cult of the new: Slowing down consumption
-  \item Transforming rubbish
-  \end{itemize}
-\end{itemize}
-
-The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
-The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
-When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
-Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
-This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
-
-An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
-Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
-
-Results of this study also support consideration of found objects as important artifacts that are signifiers of cultural meaning.
-
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
-
-%%%
-%%%
-%%%
-\section{Collage, Assemblage and the Found Object}
-In this chapter root of using objects in the artworks is examined.
-Using objects on artworks beyond their intended purpose.
-Developing artworks not only painting but also using paper and other stuff by pasting them together.
-
-%%
-%%
-\subsection{Collage}
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
-
-\cite{greenberg1984collage}
-
-%%
-%%
-\subsection{Assemblage}
-Assemblage work produced by the incorporation of everyday objects into a composition.
-It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
-Diverse range of things can be used production of work.
-In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
-William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
-
-%%
-%%
-\subsection{the Found Object (Ready-mades)}
-Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
-Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).
-Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
-The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
-
-%%
-%%
-\subsection{\textit{Bricolage}}
-Something constructed using whatever was available at the time.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-%%
-%%
-\subsection{Folk Art}
-In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic.
-The nature of folk art is specific to its particular culture.
-
-%%
-%%
-\subsection{Art and activism}
-
-%%
-%%
-\subsection{History of Consumption and Waste}
-"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
-Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
-Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
-A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Discussion}
-Are artworks made from trash just examples of collage and assemblage or more than from them?
-What about the experience and interaction with other people?
-Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
-But all of them work in fragments, combine many objects together.
-
-Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
-
-In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
-
-%%%
-%%%
-%%%
-\section{Artworks}
-Artist and artworks related with trash and their analysis. Stages of their works and methods.
-
-% FROM ReVista
-Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.
-
-% FROM Paola Ibarra ReVista
-Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
-Is there a limit to recycling and representation?
-Or is there a point at which waste cannot become art (or anything else)?
-
-\begin{itemize}
-% FROM Maite Zubiaurre, ReVista Garbage
-\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
-It is that particular type of trash meet in the public places.
-trash left behind, trash on the sidewalk, squished, squashed, and weathered.
-Filomena Cruz sees trash that we don’t want to see.
-A
-piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-      \caption{Road Kill by Filomena Cruz}
-      \label{fig:FilomenaCruz_RoadKill_ReVista}
-  \end{figure}
-
-\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
-
-% https://www.youtube.com/watch?v=sJxxdQox7n0
-\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.
-
-% http://www.eloisacartonera.com.ar/ENGversion.html
-\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
-urban pickers (\textit{cartoneros}) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
-      \caption{Books covered by Eloisa Cartonera}
-      \label{fig:EloisaCartonera_Books}
-  \end{figure}
-
-% FROM Paola Ibarra, ReVista
-%\item Forever; Blue Yonder by artist Kyle Huffman
-%\item Too Too---Much Much by Thomas Hirschhorn
-%\item Autoconstrucción by Abraham Cruzvillegas
-%\item Pictures of Garbage by Vik Muniz
-
-% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
-%\item Daniel Lind-Ramos
-
-% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
-% https://www.youtube.com/watch?v=v6IoEF_Tsrw
-\item Nick Quijano has some rules to create assemblages.
-\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
-As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
-Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
-
-% FROM Burning Messages BY MICHAEL WELLEN, ReVista
-%\item Antonio Berni
-
-% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
-\item Haiti case.
-When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
-It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
-When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
-When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
-It shows that working with trash and being clean healthy is not a contradiction.
-Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
-
-% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
-% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
-In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
-These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
-The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
-Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
-It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
-
-\item Joseph Cornell
-
-\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
-
-\end{itemize}
-
-Childs can enjoy with trash.
-I remember from my childhood, we collect crown cap and play with them.
-Some caps are found less and they worth more.
-We are looking everywhere for them.
-To make them flat we put them on the railways.
-After train passed we get perfect plat cap.
-At that time it is not trash for us.
-It has a value and part of our games and enjoy.
-To have fun a bunch of trash can be enough for us.
-
-In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life.
-By the artist or other parts are give them a new life.
-They can reborn as a different things.
-Do people collect them aware of it?
-Discarded items unites together with the hands of a artist.
-
-Trash is global topic men. When you talk about trash, everyone have ideas about it.
-
-Think a city that has trash monument in the every corner.
-created from their trash.
-merged with the city life and gaining unique cityscapes and aesthetics.
-or think that a museum a trash museum.
-Exhibits works of art embracing the trash in all aspects.
-Maybe done by the artist or the visitors from all around world.
-A place for garbage other than a landfill.
-Waiting their creator to meet again.
-What a great idea isn't it?
-Meeting their creators again.
-But this time their creator can recognize their trash.
-They transformed to totally new thing.
-Reborn.
-Transformed (Kafka, Gregor Samsa).
-
-%%
-%%
-\subsection{Artist statements}
+\chapter{My work}
 
@@
 \subsection{Why (package) paper?}
-Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
+Easy to collect.
+Easy to find.
+Thrown out even if it is good quality.
+Packaging materials are very widespread.
+Appropriate for painting and writing.
+Has a very short life time.
+Disposable, there are a lot of package outside.
+No need to carry it.
+Every place gives you package paper.
 
@@
 \subsection{Why covering notebooks and books?}
+They are all package paper, already used as carry things and this work it has used again for the same purpose (but in different connection, this time trash is bound to the notebook).
+Trash is used to cover the papers.
+Cover is the most visible part of the notebook and book.
+Therefore trash becomes most visible part of the produced item.
+What is the function of cover?
+It gives ideas about what is inside, distinguishes from other things, protect it.
 
@@
 The work aims to liberate the imagination and change the way people see the trash.
-
-%%%
-%%%
-%%%
-\section{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
-
-%%
-%%
-\subsection{Garbage Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
-
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
-
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
-
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%%
-%%%
-%%%
-\section{Archaeology of Garbage}
-
-%%
-%%
-\subsection{Garbology}
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
-
-%%
-%%
-\subsection{Trash as History/Memory}
-% TODO From encylopedia
-\cite{bullock2012trash}
-
-%%
-%%
-\subsection{Trash Aesthetics}
-Walter Benjamin's trash aesthetics and Adornos reflection.
-
-%%%
-%%%
-%%%
-\section{Sample Phrases}
-
-\bibliographystyle{apacite}
-\bibliography{ref}
-
-\end{document}

### 2015-09-28 main.tex
format changed.
Former-commit-id: 268481e7bc2309b7a723363c8a58ad53557d090a

--- 2015-09-25 main.tex
@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{report}
 \usepackage[english]{babel}
@@
 
-% Keywords command
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
 % Quotation command
@@
 
+\begin{document}
 \title{Thesis Draft}
 \author{Mustafa İlhan}
+\maketitle
+\pagenumbering{roman}
+\tableofcontents
+%\listoffigures
+%\listoftables
 
-\begin{document}
-\maketitle
-
-%%%
-%%%
-%%%
 \begin{abstract}
@@
 
-Driving questions: Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. 
+\textbf{Questions.} Do she/he want to take back (or revisit) the trash once thrown away?
+People do not want to think of what they throw away.
+Turning them to a things that worth to look again.
+How do artists reflect garbage and what are their tactics?
+What is the thing that add value to trash and what is the role of art in that?
+
+\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
+
+\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims.
+Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
+
+\vfill\noindent\textbf{\textit{Keywords:}} trash(discarded things), art, value creation, transformation.
 \end{abstract}
-\keywords{trash, art, value creation}
 
-%%%
-%%%
-%%%
-\section{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
-% TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
-Literature is recycled material, a pretext for making more art.
-I learned this distillation of lots of literary criticism in workshops with children.
-I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
-For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between
-garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
-%
-\subsubsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
-
-% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
-Object moves and also trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
-
-Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or compostable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
-% >
-
-%
-\subsubsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from
-our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-%
-\subsubsection{Perspectives related with trash from different disciplines}
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it handled by generally by the municipals. 
-\end{itemize}
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
-In other word the problem is our technology which is not perfect.
-(and I'm not sure that at some point that technology will reach to the perfection or not.)
-
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
-\quotes{What is happening to trash is what is going to happen to us.
-We’re all going to end up in a dump, and we’re going to decompose.
-That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-\quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{}
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-
-%
-\subsubsection{Throw away culture}
-Continuously consuming things and disposing of something.
-It is an important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
-(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
-
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
-
-%
-\subsubsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
-
-%
-\subsubsection{Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-
-%
-\subsubsection{Types of trashes}
-Different production process generates different types of trash. According to production process, decomposition process\ldots
-
-%
-\subsubsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
-There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
-Even if they are excluded, there is also life for them.
-
-% TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
-
-% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions that
-
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
-
-%
-\subsubsection{The case of \quotes{The Gleaners and I}}
-The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
-The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
-This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
-
-It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
-Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
-
-\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
-Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
-However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
-Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
-She is gleaning images.
-The Gleaners and I far more than document the lives of gleaners.
-It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
-
-The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
-And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
-
-Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
-There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-Seeing the value in what someone else has defined as trash is an art in itself.
-
-Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
-She keeps light to the modern life gleaners that are not visible every time.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
-In other word we can be subject of the refusal.
-At some point she become the subject of the thing that she track.
-
-There are many aspects of this documentary film.
-First draw attention the practice of gleaning.
-The discarded items that are not fit in the industrial standards because of their shape, color etc.
-Even if these items are discarded and we are not aware of them, there is also another life for them.
-Modern life gleaners feed from them.
-In another words someones trash becomes another trash.
-There are people live the boundaries of consumption societies.
-They create their life from the unwanted items.
-what the society refuses, they find a life or create a life from them.
-Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
-(as also Zizek mentions that love is not idealization.
-But the industrial processes has some standards and beyond that standards there is not a place for everyone.
-Life is being lived in the cites is somehow idealized life or tried to be idealized life.
-beyond the border of the urban there is new life generated.
-What is not succeed in the cities succeed outside of it.)
-
-She uses unconsciously recorded pieces in the film.
-\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
-It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
-She sets this scene to a jazz soundtrack.
-While watching the scene I was certainly confused.
-Why is this in here?
-What does this have to do with gleaning?
-And certainly why did the scene last so long?
-But there was also something lovely about it.
-Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
-I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
-Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
-Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
-Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
-Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
-Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
-The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
-
-Refused is not only foods and trash.
-there are a lot of things that are pushed outside border of the society.
-She talks and investigates artist that are using discarded items in the artworks.
-What people not found anything the artist see countless possibilities from them.
-There is always alternative ways to see something different.
-Giving life or finding life from discarded life.
-
-The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
-
-Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
-There should reason for this?
-For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
-They require it to sustain their life.
-Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
-What gleaning means become more open (or powerful).
-It draws a picture of body combination of different parts (connected, dependent to the each other).
-The reason of gleaning varies but the fact that gleaning is continues in different forms.
-
-She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
-One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
-
-The Gleaners And I is not an environmental film.
-Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
-
-The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
-Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
-The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
-One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-
-Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
-Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
-He specializes in reliefs and assemblages made entirely from discarded objects and junk.
-In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
-
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
-
-%%%
-%%%
-%%%
-\section{Etymology}
-%%
-%%
-\subsection{The difference between reuse and recycle}
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
-Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-%%
-%%
-\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
-Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.
-
-The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
-
-Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is a study of waste as a social science.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
-
-Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-
-\subsection{In the context of Art}
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling.
-
-%%%
-%%%
-%%%
-\section{Rubbish Theory}
-Objects have a lifetime and they don't remain same through that lifetime.
-Their value, usage, location change over time.
-During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
-Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
-Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
-This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
-The theory looks at how some of these objects then regain value, such as antiques or historic homes.
-It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
-The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.
-
-Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
-Thompson label some transitions as possible and the others as impossible.
-"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
-Further, he does not allow move from transient to durable.
-However, Duchamp's fountain breaks this rule.
-Because urine used as a fountain is still functional and have a place in the market.
-In another word, it is not rubbish.
-This urine with the approach of Duchamp turned to be an artwork.
-It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
-
-In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
-(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
-transforming them creates new a value system?
-or just finding place existing value system.
-by the way there is a value theory related with (or inside of) game theory.)
-
-Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
-
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
-
-The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
-It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
-Finally the theory suggests that value emerges through our ways of seeing and placing objects.
-(From Liz Parsons)
-
-%%
-%%
-\subsection{Rubbish Theory in Practice}
-% TODO PRAP. REF.
-A key critique of the rubbish theory is its neglect of the practices of value creation.
-Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
-
-Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
-Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
-McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
-He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
-He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
-These rituals include those of possession, exchange, grooming and divestment.
-The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
-However he is not clear as to the practices which constitute these rituals.
-In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
-There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
-
-In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
-Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
-He focuses on the ‘commodity potential’ of things.
-‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
-However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
-This is where Thompson’s Rubbish Theory comes in.
-
-\subsubsection{Transients, Rubbish and Durables}
-The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
-The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
-Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
-Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
-He further observes that their category membership determines the way we act towards them.
-
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-
-Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
-(Further there is similar analogy at Waste and Want.
-The author give the example of shoe and claim that thrash is relative.
-The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
-Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
-
-\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
-disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
-
-\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
-Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
-It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
-
-\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
-Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
-Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
-The find may not involve objects which are new to us, it is possible to find some of ones own items if they have been hidden away long enough in an attic and thus made strange to us.
-The concept of the find also suggests that the found object has some qualities that others (or indeed ourselves) have in the past overlooked, as such it is closely related to ‘bringing to light’.
-The find may be extended to embrace features of objects as well as objects themselves.
-This directs us to their ‘potentialities’, objects may have been there all along but we’ve suddenly found them to be useful, likeable or beautiful.
-It might be that some aspect of them has simply been brought to our attention.
-Equally, as discussed below in relation to transforming objects, we may make alterations to objects which bring out their potential.
-The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
-
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
-
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
-Transformations may also involve the modification or updating of objects through painting, alteration or repair.
-Transformations may not only be based around creating new uses but also creating new looks.
-The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
-
-%%
-%%
-\subsection{Theoretical Analysis of Found Object}
-% TODO PRAP. REF.
-\subsubsection{Seeking Objects}
-As a species Homo sapiens has been gathering and collecting objects for thousands of years.
-Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
-The search for “things,” collecting them (Humphrey, 1979), and the need to embellish and make the ordinary special (Dissanayake, 1988) have been essential parts of the evolutionary process of human development (Bettinger, 1991; Dissanayake, 1992).
-For example, many early cave drawings occur around a natural feature within the cave such as a projection or indentation (Bahn, 1998; Lewis-Williams, 2004), making these natural features potentially comparable to found objects in modern and contemporary art (Read, 1930).
-When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
-Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
-
-In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
-Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
-Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
-Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, & Sherry, 1989).
-These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
-A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots
-
-% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
-
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
-
-\subsubsection{Found Objects in Art}
-The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve ́ , translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve ́ was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve ́s in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi & Rochberg-Halton, 1981).
-
-How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
-
-\textbf{Motivations and found object practice:}
-\begin{itemize}
-\item Discovery and engagement
-  \begin{itemize}
-  \item Seeking out: The adventure of hunting
-  \item Finding the unexpected
-  \item The location of discovery
-  \item Metamorphosis and transformation: Imagining a use for the object
-  \item Creative action
-  \end{itemize}
-\item History and time past
-  \begin{itemize}
-  \item Trigger of personal memories
-  \item The object’s story: Reflection about earlier “life” of object and previous owner
-  \item Capturing something elusive: Making sense of an unknown past
-  \end{itemize}
-\item The symbolic and functional object
-  \begin{itemize}
-  \item Aesthetic properties: Visual, tactile, original
-  \item Cost: The thrill of a free find
-  \item Evocative: More interesting than something new
-  \item Useable solutions for practical problems
-  \end{itemize}
-\item Psychological processes
-  \begin{itemize}
-  \item Personal resourcefulness
-  \item Impact on memory, emotion, cognition
-  \item Meaningfulness of object
-  \item Arouses interest: Motivates
-  \item Social engagement
-  \end{itemize}
-\item Ecological affirmation
-  \begin{itemize}
-  \item Environmental concerns
-  \item Against the cult of the new: Slowing down consumption
-  \item Transforming rubbish
-  \end{itemize}
-\end{itemize}
-
-The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
-
-%%%
-%%%
-%%%
-\section{Collage, Assemblage and the Found Object}
-In this chapter root of using objects in the artworks is examined.
-Using objects on artworks beyond their intended purpose.
-Developing artworks not only painting but also using paper and other stuff by pasting them together.
-
-%%
-%%
-\subsection{Collage}
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
-
-\cite{greenberg1984collage}
-
-%%
-%%
-\subsection{Assemblage}
-Assemblage work produced by the incorporation of everyday objects into a composition.
-It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
-Diverse range of things can be used production of work.
-In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
-William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
-
-%%
-%%
-\subsection{the Found Object (Ready-mades)}
-Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
-Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).
-Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
-The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
-
-%%
-%%
-\subsection{\textit{Bricolage}}
-Something constructed using whatever was available at the time.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-%%
-%%
-\subsection{Folk Art}
-In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic.
-The nature of folk art is specific to its particular culture.
-
-%%
-%%
-\subsection{History of Consumption and Waste}
-"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
-Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
-Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
-A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Discussion}
-Are artworks made from trash just examples of collage and assemblage or more than from them?
-What about the experience and interaction with other people?
-Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
-But all of them work in fragments, combine many objects together.
-
-Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
-
-In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
-
-%%%
-%%%
-%%%
-\section{Artworks}
-Artist and artworks related with trash and their analysis. Stages of their works and methods.
-
-% FROM ReVista
-Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.
-
-% FROM Paola Ibarra ReVista
-Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
-Is there a limit to recycling and representation?
-Or is there a point at which waste cannot become art (or anything else)?
-
-\begin{itemize}
-% FROM Maite Zubiaurre, ReVista Garbage
-\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
-It is that particular type of trash meet in the public places.
-trash left behind, trash on the sidewalk, squished, squashed, and weathered.
-Filomena Cruz sees trash that we don’t want to see.
-A
-piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-      \caption{Road Kill by Filomena Cruz}
-      \label{fig:FilomenaCruz_RoadKill_ReVista}
-  \end{figure}
-
-\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
-
-% https://www.youtube.com/watch?v=sJxxdQox7n0
-\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.
-
-% http://www.eloisacartonera.com.ar/ENGversion.html
-\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
-urban pickers (\textit{cartoneros}) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
-      \caption{Books covered by Eloisa Cartonera}
-      \label{fig:EloisaCartonera_Books}
-  \end{figure}
-
-% FROM Paola Ibarra, ReVista
-%\item Forever; Blue Yonder by artist Kyle Huffman
-%\item Too Too---Much Much by Thomas Hirschhorn
-%\item Autoconstrucción by Abraham Cruzvillegas
-%\item Pictures of Garbage by Vik Muniz
-
-% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
-%\item Daniel Lind-Ramos
-
-% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
-% https://www.youtube.com/watch?v=v6IoEF_Tsrw
-\item Nick Quijano has some rules to create assemblages.
-\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
-As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
-Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
-
-% FROM Burning Messages BY MICHAEL WELLEN, ReVista
-%\item Antonio Berni
-
-% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
-\item Haiti case.
-When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
-It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
-When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
-When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
-It shows that working with trash and being clean healthy is not a contradiction.
-Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
-
-% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
-% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
-In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
-These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
-The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
-Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
-It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
-
-\item Joseph Cornell
-
-\end{itemize}
-
-Childs can enjoy with trash.
-I remember from my childhood, we collect crown cap and play with them.
-Some caps are found less and they worth more.
-We are looking everywhere for them.
-To make them flat we put them on the railways.
-After train passed we get perfect plat cap.
-At that time it is not trash for us.
-It has a value and part of our games and enjoy.
-To have fun a bunch of trash can be enough for us.
-
-In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life.
-By the artist or other parts are give them a new life.
-They can reborn as a different things.
-Do people collect them aware of it?
-Discarded items unites together with the hands of a artist.
-
-Trash is global topic men. When you talk about trash, everyone have ideas about it.
-
-Think a city that has trash monument in the every corner.
-created from their trash.
-merged with the city life and gaining unique cityscapes and aesthetics.
-or think that a museum a trash museum.
-Exhibits works of art embracing the trash in all aspects.
-Maybe done by the artist or the visitors from all around world.
-A place for garbage other than a landfill.
-Waiting their creator to meet again.
-What a great idea isn't it?
-Meeting their creators again.
-But this time their creator can recognize their trash.
-They transformed to totally new thing.
-Reborn.
-Transformed (Kafka, Gregor Samsa).
-
-%%
-%%
-\subsection{Their statements}
-
-%%%
-%%%
-%%%
-\section{My Artwork/Project}
-
-%%
-%%
-\subsection{Functionality and Art Debate}
-From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
-Duchamp's works kills the functionality.
-It works beyond the functional perception.
-Moves the debate to the conceptual frame.
-However it is not every time case.
-Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value.
-Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else.
-\quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}.
-Therefore anything can be turned to art with a good idea.
-
-%%
-%%
-\subsection{Paper}
-"Paper is an indispensable product throughout the world.
-Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
-In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
-Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
-
-%
-\subsubsection{Environmental Impact}
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
-
-Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
-Recycling paper can greatly diminish demand for virgin fiber from wood.
-However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
-It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
-
-%
-\subsubsection{History}
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
-
-%
-\subsubsection{Production}
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
-
-%
-\subsubsection{Uses}
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
-
-%%
-%%
-\subsection{Why (package) paper?}
-Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.
-
-%%
-%%
-\subsection{Why covering notebooks and books?}
-
-%%
-%%
-\subsection{Artistic tactics}
-Spreading the idea by making something useful and easy to carry while traveling. Small notebooks.
-
-%%%
-%%%
-%%%
-\section{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
-
-%%
-%%
-\subsection{Garbage Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
-
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
-
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
-
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%%
-%%%
-%%%
-\section{Archaeology of Garbage}
-
-%%
-%%
-\subsection{Garbology}
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
-
-%%
-%%
-\subsection{Trash as History/Memory}
-Walter Benjamin's trash aesthetics and Adornos reflection. \cite{bullock2012trash}
-
-%%
-%%
-\subsection{Trash Aesthetics}
-
+\pagenumbering{arabic}
+\include{chapter1}
+\include{chapter2}
+\include{chapter3}
+\include{chapter4}
+\include{chapter5}
 \bibliographystyle{apacite}
-\bibliography{ref}
+\bibliography{literature}
 

### 2015-09-29 chapter2.tex
Layout & Header organization updated.
Former-commit-id: 497c876eefc8a79803afe4223ecd39f1c07e4b62

@@
 \chapter{Theory of Trash}
+In this chapter trash is examined in theoretical (and conceptual) aspect. Theoretical foundations of trash are discussed. (Further benefited from historical and social aspect of trash.)
+
+%%%
+%%%
+%%%
+\section{Etymology}
+(Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
+There are slight differences between these words but sometimes they are used to signify same concept.
+
+%%
+%%
+\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
+The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
+
+Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
+Garbology is a study of waste as a social science.
+In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
+
+Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
+German has retained the original meaning in wüste (desert).
+Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
+It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
+
+%%
+%%
+\subsection{The difference between reuse and recycle}
+According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+If any item is used again and again over time, it is said to be reused.
+The main purpose of reusing is to lengthen the life of the item or material.
+We give out used clothes for charity which results in reusing.
+Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
+The main purpose is to make the item last as long as it can.
+To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
+Why throw something away when you can give it another life?
+Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
+Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
+For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
+
+Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
+Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
+
+According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
+It is an energy consuming process.
+For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
+In this process, energy is required which depends upon the stages of transformation.
+
+Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
+Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
+
+Reusing is possible with re seeing (rethinking).
+Reusing is possible meet the needs of the human itself.
+Using creativity and personal approach can change objects functions.
+It is possible to use objects for different purposes.
+
+Recycling can be viewed as down-cycling.
+The object smashed to the small particles to be used later in the production of something else.
+Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
+Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
+
+Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
+
+Many scholar used the word recycling when mentioning works uses trash and the concept of it.
+However they are not mentioning the meaning that is decomposing things to the their particles.
+What they is actually is reusing and combining things, concepts, creating new mixtures.
+
+% TODO not sure for this section, maybe mentioned above...
+\subsection{My terminology selection}
+(I use this word for this and that?)
 
@@
 %
-\subsubsection{How does it become(turn to) art?}
-How does it draw attention of artist, and also mine?
-
-%
 \subsubsection{Types and Comparison of trashes}
@@
 
-% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions that
-
 %%
@@
 
-%
-\subsubsection{The case of \quotes{The Gleaners and I}}
-The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
-The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
-This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
-
-It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
-Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
-
-\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
-Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
-However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
-Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
-She is gleaning images.
-The Gleaners and I far more than document the lives of gleaners.
-It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
-
-The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
-And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
-
-Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
-There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-Seeing the value in what someone else has defined as trash is an art in itself.
-
-Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
-She keeps light to the modern life gleaners that are not visible every time.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
-In other word we can be subject of the refusal.
-At some point she become the subject of the thing that she track.
-
-There are many aspects of this documentary film.
-First draw attention the practice of gleaning.
-The discarded items that are not fit in the industrial standards because of their shape, color etc.
-Even if these items are discarded and we are not aware of them, there is also another life for them.
-Modern life gleaners feed from them.
-In another words someones trash becomes another trash.
-There are people live the boundaries of consumption societies.
-They create their life from the unwanted items.
-what the society refuses, they find a life or create a life from them.
-Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
-(as also Zizek mentions that love is not idealization.
-But the industrial processes has some standards and beyond that standards there is not a place for everyone.
-Life is being lived in the cites is somehow idealized life or tried to be idealized life.
-beyond the border of the urban there is new life generated.
-What is not succeed in the cities succeed outside of it.)
-
-She uses unconsciously recorded pieces in the film.
-\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
-It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
-She sets this scene to a jazz soundtrack.
-While watching the scene I was certainly confused.
-Why is this in here?
-What does this have to do with gleaning?
-And certainly why did the scene last so long?
-But there was also something lovely about it.
-Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
-I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
-Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
-Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
-Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
-Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
-Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
-The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
-
-Refused is not only foods and trash.
-there are a lot of things that are pushed outside border of the society.
-She talks and investigates artist that are using discarded items in the artworks.
-What people not found anything the artist see countless possibilities from them.
-There is always alternative ways to see something different.
-Giving life or finding life from discarded life.
-
-The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
-
-Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
-There should reason for this?
-For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
-They require it to sustain their life.
-Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
-What gleaning means become more open (or powerful).
-It draws a picture of body combination of different parts (connected, dependent to the each other).
-The reason of gleaning varies but the fact that gleaning is continues in different forms.
-
-She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
-One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
-
-The Gleaners And I is not an environmental film.
-Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
-
-The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
-Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
-The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
-One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-
-Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
-Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
-He specializes in reliefs and assemblages made entirely from discarded objects and junk.
-In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
-
-%%%
-%%%
-%%%
-\section{Etymology}
-%%
-%%
-\subsection{The difference between reuse and recycle}
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
-Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-%%
-%%
-\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
-Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.
-
-The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
-
-Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is a study of waste as a social science.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
-
-Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-
-\subsection{In the context of Art}
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling.
+% TODO: ragpickers from benjamin and archades project.
 
@@
 %%
-\subsection{Garbage Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%%
-%%
 \subsection{Garbage in Modern Thought}

### 2015-09-29 chapter3.tex
Layout & Header organization updated.
Former-commit-id: 497c876eefc8a79803afe4223ecd39f1c07e4b62

@@
-\chapter{Artworks}
+\chapter{Trash as Medium (Trash in the Art)}
+How does trash draw attention of artist(, and also mine)?
+In this chapter how artist approached to the trash and their techniques are discussed in the context of art.
+(Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?).
+How does it turn to medium?
+
+% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions.
 
@@
 
+% TODO reading...
 \cite{greenberg1984collage}
@@
 
+% TODO reading...
 \cite{strasser1999waste}
@@
 
+Some scholars think that the roots of collage is folk art.
+(Find resource.) It's methodologies used in this art.
+The same exist for craft.
+Some works(for example sculptures from trash) are highly requires craft skills.
+
+%%
+%% TODO reading...
+\subsection{Art and activism}
+Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.
+
+\subsection{Recycling in the context of Art}
+% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+Recycling has always been a common practice in the arts at least at a non-material level.
+From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
+Take and put.
+De-contextualize and re-contextualize.
+In that sense, art, as a system, is an act of recycling.
+
 %%
 %%
-\subsection{Art and activism}
+\subsection{Garbage Art}
+"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
 
@@
 
-%%
-%% TODO change here
-\subsection{Discussion}
-Are artworks made from trash just examples of collage and assemblage or more than from them?
-What about the experience and interaction with other people?
-Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
-But all of them work in fragments, combine many objects together.
+%%%
+%%%
+%%%
+\section{The case of \quotes{The Gleaners and I}}
+The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
+The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
+This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
 
-Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
+It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
+Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
 
-In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
+\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
+Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
+However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
+Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
+She is gleaning images.
+The Gleaners and I far more than document the lives of gleaners.
+It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
+
+The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
+As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
+More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
+And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
+
+Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
+There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
+Seeing the value in what someone else has defined as trash is an art in itself.
+
+Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
+She keeps light to the modern life gleaners that are not visible every time.
+One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
+In other word we can be subject of the refusal.
+At some point she become the subject of the thing that she track.
+
+There are many aspects of this documentary film.
+First draw attention the practice of gleaning.
+The discarded items that are not fit in the industrial standards because of their shape, color etc.
+Even if these items are discarded and we are not aware of them, there is also another life for them.
+Modern life gleaners feed from them.
+In another words someones trash becomes another trash.
+There are people live the boundaries of consumption societies.
+They create their life from the unwanted items.
+what the society refuses, they find a life or create a life from them.
+Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
+(as also Zizek mentions that love is not idealization.
+But the industrial processes has some standards and beyond that standards there is not a place for everyone.
+Life is being lived in the cites is somehow idealized life or tried to be idealized life.
+beyond the border of the urban there is new life generated.
+What is not succeed in the cities succeed outside of it.)
+
+She uses unconsciously recorded pieces in the film.
+\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
+It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
+She sets this scene to a jazz soundtrack.
+While watching the scene I was certainly confused.
+Why is this in here?
+What does this have to do with gleaning?
+And certainly why did the scene last so long?
+But there was also something lovely about it.
+Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
+I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
+Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
+Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
+Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
+Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
+The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
+
+Refused is not only foods and trash.
+there are a lot of things that are pushed outside border of the society.
+She talks and investigates artist that are using discarded items in the artworks.
+What people not found anything the artist see countless possibilities from them.
+There is always alternative ways to see something different.
+Giving life or finding life from discarded life.
+
+The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
+
+Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
+Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
+There should reason for this?
+For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
+They require it to sustain their life.
+Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary.
+What gleaning means become more open (or powerful).
+It draws a picture of body combination of different parts (connected, dependent to the each other).
+The reason of gleaning varies but the fact that gleaning is continues in different forms.
+
+She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
+One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
+
+The Gleaners And I is not an environmental film.
+Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
+
+The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
+Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
+The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
+One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
+
+Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
+Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
+He specializes in reliefs and assemblages made entirely from discarded objects and junk.
+In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
 
@@
 %%%
-\section{Artworks}
+\section{Example Artworks}
 Artist and artworks related with trash and their analysis. Stages of their works and methods.
@@
 %%
-%%
+%% TODO sample statements here.
 \subsection{Artist statements}
@@
 
+%%
+%%
 \subsection{Artistic tactics}
+
+%%%
+%%%
+%%%
+\section{Discussions}
+Are artworks made from trash just examples of collage and assemblage or more than from them?
+What about the experience and interaction with other people?
+Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
+But all of them work in fragments, combine many objects together.
+
+Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
+
+In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.

### 2015-09-29 chapter4.tex
Layout & Header organization updated.
Former-commit-id: 497c876eefc8a79803afe4223ecd39f1c07e4b62

@@
 \chapter{My work}
+In this chapter the artwork explained in detail.
+
+%%%
+%%%
+%%% TODO extend this part
+\section{Artist Statement}
+Collect(Rescue), Store, Transform, Spread.
 
@@
 %%%
-\section{My Artwork/Project}
-Here stages of my artwork are listed:
+\section{Progress}
+Here stages(progress) of my artwork are listed:
 \begin{itemize}
@@
 %%
-\subsection{Functionality and Art Debate}
+\subsection{(Overcomed) Problems}
+There are a lot of questions and problems that I have to overcome while development of my work. 
+\begin{itemize}
+\item First one is that my art work can be considered as design and has functional purposes.
+(It is not just a design, it is uses design to reach its goal like many artworks use other disciplines to reach their goals and expression.
+Purpose is not design and functionality.)
+\item Using unused industrial paper. (Mixed trash and virgin material, \textbf{to show that discarded and desired object can live together.})
+\item Collecting them.
+\item Giving them to people, but people should take them voluntarily.
+\end{itemize}
+
+%
+\subsubsection{Functionality and Art Debate}
 From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
@@
 %
-\subsubsection{History}
+\subsubsection{History of paper}
 The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
@@
 %
-\subsubsection{Production}
+\subsubsection{Production of paper}
 All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
@@
 %
-\subsubsection{Uses}
+\subsubsection{Uses of paper}
 Paper has become the most ubiquitous product in the age of information.
@@
 %%
-\subsection{Artistic tactics}
-Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
-
 \subsection{Why is it art?}
@@
 The work aims to liberate the imagination and change the way people see the trash.
+
+%%
+%%
+\subsection{Artistic tactics}
+Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.

### 2015-09-30 chapter4.tex
artwork notebook.
Former-commit-id: c386004a5bc2735f3aa04da477cbb77fd36c6831

@@
 Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+
+\subsection{How I reached to notebook?}
+Actually I have been collecting same materials that are used in my project before the thesis work.
+In my mind there is always belief that I can I find something useful for them.
+(In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork.
+Before the thesis I also produce the notebooks for myself.
+However what is changed in thesis.
+First my approach to the trash is a little bit deeper.
+What is added to the notebooks.
+I started to use also used papers.
+for the cover of the notebook, I use more different materials.
+more close to collage.
+production method changed.
+and I started to collect different things, from different places.
+My realization increased.
+I organized my close friends and others to collect or save their trash for me.
+I discovered some points.
+their differences.
+
+\textbf{Why notebook?} Because I already do it.
+So What I didn't change it.
+It is the best one or no to change it.
+I love idea of carrying notebook with near of you.
+I have also save my notebooks.
+I don't throw away them.
+A notebook is actually is a work of you.
+It carries your signature.
+It is one of best gift to give someone.
+Because it is a combination of your work and the other peoples works.
+It is co-authored work.
+Actually there is also a part of people who throw away this peace.
+Actually the best part of it the transformation is not finishes after my creation of notebook.
+It continues with the usage of it.
+How it turned to is not actually uncertain.
+Therefore it is very appropriate of my idea that transforming trash is increases the diversity.
+
+\textbf{What is different from industrial notebooks?} Handmade, from trash.
+an alternative to other versions.
+every one have different stories, they are different in visuals (but the others are also different.) What makes them different is not clear actually.
+Does it have to be different?
+Yes.
+The production method is different.
+You pay no money.
+There is different with gift notebooks from companies.
+This notebooks call to you change the destiny of trash together.

### 2015-10-01 chapter3.tex
something related with art.
Former-commit-id: 3b77bc5731346177b00b1b67ea14f54413ae066b

@@
 
-\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning}
+\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was
+drawn to recycled art because of one simple factor---the price. "Free is certainly great, and that was a driving force for me early on in my career," he said.
 
@@
 In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
+
+(Trash has a history. They have different stories. But same destiny?)
+
+Lets make clear the motto: "trash to treasure".
+What is treasure here.
+What does it signify?
+Treasure---something very valuable.
+from trash.
+Then it is trash.
+Not once it is trash.
+What type of treasure.
+Who can get value from it.
+Who creates this treasure?
+How does it created?
+Trash is actually is opposite of treasure and then it is switched.
+In other words trash become treasure and treasure become trash?
+
+Lets consider the practice of working with trash.
+Why someone believes that discarded objects of people \ldots Looking things that people are refused.
+Transforming is the one of the most common practice of whole history of man and nature.
+This practice is forgotten or it is still alive.
+Agnes Varda actually shows that it is still exist but in different forms.
+They use it what ruling lifestyle throw out.
+They are everywhere actually but you should look them carefully.
+They live in the borders.
+But live.
+Event if they are refused they live.
+Actually it is hard to say that they want to integrate to the system.
+They want to change it?
+
+ability of transform, well actually it is very easy to throw away. hard thing is to keep it. force the material. the dimension of trash.
+
+\begin{itemize}
+\item Where do you think this object came from?
+\item Why do you think that someone labeled this object as waste?
+\item How can you transform this object to tell the story that you thought of before?
+\item What story does it tell you?
+\item Does it remind you of an event, a specific time in history or in your life, a place, or a state of mind?
+\item How can you bring that story to life? (Taylor, 2006, p. 9).
+\end{itemize}
+
+%junkyard art
+
+% TODO PRAP. from rethink, reimagine, reinvent
+Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
+Assemblage art involves the creation of new and innovative objects from what were once considered objects of waste; that is.
+through their use in assemblage pieces, reclaimed objects are endowed with a new.
+sometimes paradoxical meaning.
+The transformations of the objects used in assemblage pieces ask viewers to reconsider the notion of "valuable" as they are challenged to look at everyday objects with a new perspective (Taylor, 2006).
+Viewers confront issues relating to the functionality of objects during modern processes of production, consumption and distribution.
+
+Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs & McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
+Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).

### 2015-10-04 chapter2.tex
literature
Former-commit-id: 10106d6d6d4b83530ba518d170c02132441efb0d

@@
 \subsubsection{Perspectives related with trash from different disciplines}
+This is very important because the problem of trash is being tried to be handled by different disciplines.
+In other words there different approaches to the trash.
+Different problems, different solutions.
+Which perspective that I have.
+In what ways my project differs from them.
+The purpose is to participate people in this work, by collecting them etc.
+And also offer to transform it.
+Rescue it and than later transform it.
+In short, the difference between the other disciplines must be clear.
 \begin{itemize}
@@
 \end{itemize}
+
+% Sample sentence:
+% Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture
 
@@
 
-% Outline:
-% Weak points:
-% Where to study next.
+% FROM The Ruin and the Ruined in the Work of Kurt Schwitters.
+% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality
+
+\subsection{Discussions}
+Objects moves around and their values change constantly.
+(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
+The Social Life of Things: Commodities in Cultural Perspective)
+
+Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)
+
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
+This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trashcan in the form of waste.
+In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
+
+Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”
+
+% Prap. same source...
+% On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” 9 Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
+The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
+10 Waste now became evil.
+If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
+11 Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” 12 Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
+Upcycling...
+On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
+Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
+16 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
+In short, there is a whole sector of upcycling now.
+
+% Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
+
+% There is commodity aspect of it and also the process of accommodation.
+In this process design plays a significant role.
+Trash is waiting to be discovered.
+At the same time forgotten styles are also used in works.
+Therefore actually trash and forgotten styles can be considered in the same status.
+
+% This can be sample thesis statement sentence:
+% This article is about those objects that are recreated from trash through the process of upcycling.
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” 4 I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of.
+
+% From The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
+% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
+% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
+\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
+The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
+As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.

### 2015-10-04 chapter3.tex
literature
Former-commit-id: 10106d6d6d4b83530ba518d170c02132441efb0d

@@
 
+\begin{itemize}
+\item I am an artist living in New York City, and my experience of daily life here is both the catalyst for and the subject of my art.
+Working from the local, the personal and the ordinary - the paper take-out coffee cup in the palm of my hand, the view from my studio window in the Garment District, friends and their children, the community garden around the corner from my apartment in Hell's Kitchen - my drawings, paintings and installations are about what happens when the familiar suddenly undergoes a perspective shift and is revealed in all its wonder and infinite possibility.
+With this shift, mundane things become extraordinary, as nodes of rapidly expanding sets of connections, relationships and new artworks.
+
+My approach to art-making is both observational and process-oriented.
+A fascination with cultural, physical and temporal change combined with the possibility of infinite variation unify projects as diverse as drawing and painting on my used coffee cups each day, repeatedly recording the view from my studio in paint and photography over the course of six years, depicting in two and three dimensions the incursion of human activity on the fractal meanders of salt marshes along the New Jersey coast, and painting portraits of alternative families in my New York City neighborhood.
+(from http://gwynethleech.com/)
+\end{itemize}
+
 %%
@@
 
+% FROM drink UP, author: Werthan, Sarah, artist: Leech, Gwyneth. A Year in Cups. http://gwynethleech.com/
+% trash and art collided. Paper and art, actually paper already medium of art, but is there anything different here. Itself is a part of a work, not the drawing, or painting.
+% Documenting via a blog or a website. (what type of dimension it brings the work? maybe connect them, leave message.)
+% Buying a beverage is a daily event for \ldots
+% Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives.
+% “People see that an artist can make work anywhere, and make creative spaces anywhere,” she asserts.
+
+% Trash is as a material or a subject
+
 \begin{itemize}
@@
 Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).
+
+% Phrases...
+% What specific social issues are you trying to address through Labyrinth?

### 2015-10-11 chapter1.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

\chapter{Introduction}
Some text...

% This written portion was to evaluate the project in terms of a justificatory theoretical framework.

% So what is the issue here?

% Title: Trash as a Medium.

% Subsection: the purpose of this study
% Subsection: overview of chapters

% This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.

% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda.

% The project aims to what? and what needs to justify what it questions?

### 2015-10-11 chapter2.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % HERE Same sample phrases are listed you can use them:
 
+% The work that follows is divided into three sections
+
 % The artist thinks, acts, performs music, and writes outside the framework that society has created.
+
+% this thesis takes a rather different approach to the resonant possibilities of discarded things.
+It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
+
+% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
+
+% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
 
@@
 As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
+
+% FROM Waste by William Viney
+Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+(Think that the transformation process.
+Previous argument support that the transformation of trash is possible by changing the place of them.
+In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
+For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.
+
+% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.
+
+%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
+But it is very strange that the fat on the paper is previously what they are eat.
+
+% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.
+
+% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
+Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
+Remember the example given: shoes  on the dinner table.
+
+% King Lear, feeling of waste
+
+% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.
+
+% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
+
+% https://narratingwaste.wordpress.com/tag/king-lear/
+% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.
+
+% Binding things together and separating things from each other.
+
+% Cornelia Parker's work, narrate an absent event of waste
+% There is also strong relationship with the collecting discarded stuff and archeologies of waste.

### 2015-10-11 chapter3.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

@@
 
-Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs & McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
+Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
 Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).

### 2015-10-11 chapter4.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

@@
 \chapter{My work}
-In this chapter the artwork explained in detail.
+In this chapter the artwork(thesis project) will be explained in detail. Final work and it's progress will be explained.
 
@@
 \item Using unused industrial paper. (Mixed trash and virgin material, \textbf{to show that discarded and desired object can live together.})
-\item Collecting them.
+\item Collecting them with help of people, and asking other people to give the unused papers.
+(Collected from my close friends, from supervisor, from office where I work, from modshifters and varuna gezgin and from bcc labs(hopefully)?)
 \item Giving them to people, but people should take them voluntarily.
@@
 This notebooks call to you change the destiny of trash together.
+
+\subsection{What do I think about trash?}
+I need to clarify my approach to the trash, wasting and discarding.
+First point is that I am very uncomfortable to the action of discarding thing.
+I always think that by discarding this think I am missing something rather than getting rid of something.
+Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on.
+However almost it is never ending loop.
+(I believe that sometimes we need to break the loops to realize different meanings.
+To think outside the box, we need to behave outside of common habits.
+As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on.
+But for what?
+and also ought to be like that?
+(throw away them to same bin.
+(Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it.
+At that times I become very sad and feel very comfortable.
+I must have find to another place for it more suitable than a waste bin.
+At least I can give them someone else who can use it for own purposes.
+Do I really luxury of discard?
+
+Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}
+
+\textbf{Making exploration.} One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
+Because it is discarded and undiscovered.
+Wait us to be discarded.
+and possible (as picasso mentioned) discovered again and again.
+
+\section{Parts of project (or final work)}
+The project introduced in this thesis have different parts.
+Each of them are connected to have relation with and support the other.
+Different parts also enable us that different level of integration to the project.
+
+\subsection{Notebooks}
+Mixing materials is main method in the production process.
+I combine different papers and packages.
+I try to generate every possible combination.
+For some of them I establish the connection but for the others the connection is not obvious but it is not obligatory.
+Because trash is state where you can find meaning through the trash or material later.
+
+All package papers are cleaned up. Because it is important that it needs to be safe to use. With mix of water and little bleach they are swabbed.
+
+\subsubsection{Name of notebooks}
+\begin{itemize}
+\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU). Every piece was a part of bigger banner. 
+\item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+\item ... because 
+\item 08.00 am/gevrek, breakfast time. 
+\end{itemize}
+
+\subsubsection{Collected materials}
+There are different papers and objects are used to produce papers
+\begin{itemize}
+\item Burger King packages, from office at launch time
+\item Starbucks packages, from supervisor, office and my friend.
+Especially my supervisor and friend collect them from their friends and their own uses.
+They save them for me and later I take them later.
+\item Modshifters papers, that are covered on table and at the end of the day they are cut out and throw away.
+I go this place many times and every time questioned what they are doing to the papers.
+One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
+I ask him to give me and he kindly accepted.
+From this paper I covered [x] notebooks.
+All of them contains track of people who sit down there.
+I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
+\item Varuna Gezgin
+\item Graduation banner
+\end{itemize}
+
+\subsection{Website}
+As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place peoples life again, it also finds another place in the digital space. ()
+
+Mainly websites displays the story(History) of notebooks.
+Also it is a place to track the journey the notebooks.
+As I claimed that it is not a finished work.
+It does not completed transformation.
+It always continues.
+Therefore a website that anyone can reach share their progress via website.
+Anyone can later discover how they turned to new things etc.
+
+Collect peoples comment with this notebooks.
+As I leave notebooks different places I do not have connection with people who take them.
+This website also will help to collect/share peoples ideas about the notebooks.
+
+It will contains a section for how notebooks are produced and the story behind it.
+The purpose is to record the creative process and share with the others.
+Revealing the process is significant to demystifiying the truth about the project.
+It makes it more clear that the object used here is actually transformed from something else.
+
+\textbf{Why website?} Maybe you can think that there are different methods to accomplish recording and sharing the process.
+In a gallery on a single table or a room it can be succeed.
+However it like the idea that website can evolve by time as this work evolve in time.
+I think it matches perfectly.
+This is not a finished work, it continues and so the website also.
+
+% Meaning of stories behind the process
+There are different stories behind the objects.
+I try to record their stories (by photography and taking notes) but some of them were not possible.
+However I still use them in the work because even if I missed their story, with their materiality reveals their history.
+It still has a history but needs to rewritten.
+Maybe forgetting all the history maybe creates different notebook.
+
+It is also co-authored work.
+Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them.
+After production of papers I also want them to continue as co-authored process.
+In other words many people will be part of this project.
+As people see different things on objects and bring them to me.
+the variety of things is increased in time.
+Because people sad me that \quotes{I thought that you can use it.
+Do you collect also these?}.
+After that time I want to continue as so.
+
+% Documenting the progress.
+
+% It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing photography

### 2015-10-13 chapter4.tex
puzzle notebook.
Former-commit-id: 9d9397215989fa8018a50262946fbe342928ce75

@@
+% Structure of chapter:
+% 
+% Artist Statement
+% Work
+% Exhibition
+
+% \ldots is the concern of this study which aims to \ldots
+
+% The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
+
 \chapter{My work}
@@
 \begin{itemize}
-\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU). Every piece was a part of bigger banner. 
+\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
+Every piece was a part of bigger banner.
+At that time there are serious debates about freedom on the internet.
+Most of the website are banned from the decision to the courts and they were not accessible.
+(Access to this banner is blocked by a court decision.) In Middle East Technical University there is a tradition that in graduation ceremony people walk through in the stadium and greet to the tribunes.
+With this event they carry some banners to express their feelings and criticize some realities in the country.
+This one of them.
+It is carried by students (new grads of Computer Engineering) The slogan decided by among the students and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.
+After the ceremony I could not throw away this banner.
+I do not know what to do it, it is very big actually to store but I could not.
+I think that I will figure out later.
+Maybe I can use it as a draft paper.
+But is it worth to cut out this all long banner etc.
+Also to strengthen the banner and to prevent to tear while carried by the many people we are tape it from its boundaries.
+In other words some of the areas can not approiate for writing.
+When I decided to this topic I remembered to this banner.
+It is stands in a corner in a dusty way.
+Now it is time use it.
+It waited very log time and it is time to revive again.
+Currently In turkey the problem of banning web-sites continues.
+Event it can said that people do not surprises when a website is blocked by the courts.
+It can be turn be a paper that people can freely express their ideas and feeling onto the it.
+Cut out them to the smaller pieces and make them as notebooks.
+They are part of puzzle.
+for the smaller parts what is written on them can not easily understandable.
+To realize what is the message is you have to bring together all of them again.
+But It is not possible, therefore website is a very good solution for them.
+All pages have unique patterns.
+Remaining parts of letter and tape.
+It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
 \item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
-\item ... because 
-\item 08.00 am/gevrek, breakfast time. 
+\item 08.00 am/gevrek, breakfast time. I think that these packages are used at the morning, very the beginning of the day.
 \end{itemize}
@@
 % It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing photography
+
+% Counter Argument:
+% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
+Here there are available different answers to the question.
+Firstly they are different once they are designed.
+Turned to different thing.
+I suggest that them to consider in different context like Duchamp.
+
+% I resurrect things that have been killed off...
+My work is all about the potential of materials — even when it looks like they've lost all possibilities.
+(Cornelia Parker) https://en.wikipedia.org/wiki/Cornelia_Parker
+
+% These all memories and collected materials related with the my history.
+So why is it important for the other people.
+What can they found my memories.
+This is not theirs.
+How other people connect to the topic.
+They important for me but also I need to find something important for the other people.
+For example modshifter and varuna gezgin is one of them.
+This not only my experience.
+Some kind of shared memories and histories.
+What will find people in these notebooks.
+
+% Is it important that the place where people access them? How to design the experience here.

### 2015-10-14 chapter4.tex
thesis project section.
Former-commit-id: 2826821b4d261faf7b7ffdfe932d2c2d879534d3

@@
 \begin{itemize}
-\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
+\item \textbf{Puzzle.} Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
 Every piece was a part of bigger banner.
@@
 Also to strengthen the banner and to prevent to tear while carried by the many people we are tape it from its boundaries.
-In other words some of the areas can not approiate for writing.
+In other words some of the areas can not appropriate for writing.
 When I decided to this topic I remembered to this banner.
@@
 It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
-\item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
-\item 08.00 am/gevrek, breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+\item \textbf{12:00 pm.} Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+\item \textbf{08:00 am.} Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+\item \textbf{Friday Night.} (Maybe there can be another option related with traveling, or union).
+These notebook's pages are collected from restaurant "Varuna Gezgin".
+We go there to meet some friends after long time.
+One of them is coming from Australia, the other one is coming from Norway.
+they are my friends from the university.
+We united again at varuna gezgin.
+The place also interesting story.
+It is a place of travelers.
+It supports them.
+and the decoration of that place contains a lot of items collected from different sides of the world.
+The concept of the place and our meeting perfectly matched.
+I'm collecting the paper that are under the plates.
+When we are leaving this place, I ask the guy at the desk, I am making small notebooks and is it possible to exhibit there.
+I said that is it possible to give them to people.
+Firstly he asked me that selling them but I said no they are free and part of my thesis project.
+and later he offered me there are a lot of unused papers.
+I can give you.
+they are not used and waiting to be recycling.
+I took some of the papers, and that papers are part the sheets of these papers.
+% Name of the paper can be related with this place and related with the meaning. 
+\item \textbf{Modsifters.} 
+% Again I need some memory from here. 
+% They are all my memories actually and I also turn my memories something different. Changing and constructing memories. And also others' memories... These project also contains others memories.
+
+% Ersan hoca's packages.
+Elgins' papers etc.
+I do not know actually their stories.
+Maybe I can dream up stories for them.
+Creating histories from some of the trashes.
+They do not have proper memory with me, but I tried to construct memories, (fake memories can be said that.)
+
 \end{itemize}
@@
 \item Graduation banner
+\item Tea bags.
+% It is also realization of materials. Establishing different connection to them. Why is important? Identity construction.
 \end{itemize}
@@
 
-% Is it important that the place where people access them? How to design the experience here.
+% important question: herkes neye ihtiyacı var ise onu toplar.
+ben neden niçin topluyorum.
+toplama sebepleri.
+dönüştürme sebepleri.
+neden sadece toplamakla yetinmiyorum.
+yani toplamak ile ayrıldığı noktalar nelerdir.
+
+%
+% EXHIBITION
+% Where people access them? How to design the experience here. The relationship with the location? 
+% Pizza box, with l shape box. I need to find a place to put them. 
+%
+%
+
+%
+%% Move to the other sections:
+%
+% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
+The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.

### 2015-10-16 chapter4.tex
artwork, statement, questions and debates
Former-commit-id: 9897c39b89687a410855e37f69f9464f07e3199e

@@
-% Structure of chapter:
+% Structure of Chapter:
 % 
@@
 % Work
-% Exhibition
+%  - Development of it.
+%  - Parts of it. (Collecting, Transforming, Spreading them)
+% Exhibition?
 
+% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
+The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Relationship between my project and theoretical aspects:
+% - First one is actually is to analyze what is trash?
+Because I am using trash material and what is point of view of scholars to the trash.
+Realizing the potentials of it.
+Also the difference comes from the working on virgin object and trash object.
+Understanding the difference between the bricolouer and engineer.
+If trash has multiple life than these research will somehow reveal it.
+It is actually research on trash but what purposes.
+I guess it is missing?
+I need to set a purpose for the theory chapter.
+Or it is a just a background chapter?
+% - Roots in the art history. (Also roots on the social life can be researched?)
+% - Inspiration from the other artist and also 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Sample Phrases
 % \ldots is the concern of this study which aims to \ldots
-
 % The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \chapter{My work}
-In this chapter the artwork(thesis project) will be explained in detail. Final work and it's progress will be explained.
+In this chapter the artwork(thesis project) will be explained in detail.
+Final work and it's progress will be explained.
+Connection will be established with the previous chapters.
+Stages of work and concerns will be explained.
+%(Also the result of project is explained.
+But is there any result?
+I don't think so?
+I did not see discussions about the results of the works.
+but I try to collect peoples reflection and comments on it.
+Because I believe that it is not transforming the object.)
 
@@
 
+% Converting disposal things to multiple time usage. Realizing the alternative lives of trash beyond their defined one shot life. Giving attention to the things.
+
 %%%
@@
 Here stages(progress) of my artwork are listed:
+
 \begin{itemize}
@@
 There are a lot of questions and problems that I have to overcome while development of my work.
+
+% Yani aslında bir derdim ve yapmak istediğim bir şey var.
+Ama bunu gerçekleştirmek için yapmam gereken şeyler var.
+Ve bunların bazılarının nasıl yapılacağı çok belli değil.
+Ben bunlara bir çözüm buluyorum.
+Bir yöntem üretiyorum.
+Bu kısımda aslında bunlardan bahsediyorum.
+
 \begin{itemize}
@@
 One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.
+
+\textbf{Why is it not a design?} Because the considerations and priorities are different?
+Functionality is not my primary concern.
+I do not increase the functionality or searching best functionality?
+(Considerations of design and art can be compared and what are my priorities in this work.
+I'm not trying to finish the garbage problem.
+Is it a problem for me?
+Do I problematize it?)
 
@@
 their differences.
+
+% What I tried during this progress: Wrap out the trees, because I think that most of the materials that I collected are package papers.
+Well I somehow package the trees again.
+not to carry them but to raise awareness.
+Yani benim amacımı en iyi anlatacak olan şey nedir?
+Aslında ben burada defterden gidip bunu anlamlandırmaya çalıştım.
+Dolayısıyla deneyerek deftere nasıl ulaştım da ziyade defterden başlayıp nasıl tekrar defterde karar kıldığımı anlatan bir hikaye olabilir?
+Yani bu çok da şart olmayabilir bir diğer yandan da?
+Developlement of work?
+Nasıldı nereye geldi?
+How my project evolved?
+And this also explains how it is relates with the research.
+Because the reasearch is shaped the project also.
+Which part of the project shaped by the project?
+Not thinking in the ecological perspective.
+Raised questions also mature the project?
+For example zizek suggest that to find spirutuality and aesthetics to the trash, and for me?
 
@@
 
+% Refer to 9 canlı. Never dies, revives again and again. Because trash moves in the community, even if thrown away can be find another use.
+
 \end{itemize}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% EXHIBITION
+% Where people access them? How to design the experience here. The relationship with the location? 
+% Pizza box, with l shape box. I need to find a place to put them. 
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Move to the other sections:
+%
+% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
+The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TODO Find a solution for this problem:
+% Bu işin olması için ben insanlardan bir şeyler yapmalarını istiyorum.
+Yani aslında kendimde yapabilirim ama neden insanları da dahil ediyorum?
+Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de deönüştürmek gerekmek.
+ve bu bir süreç işi (şart mı tek bir yöntem bu mu?) İnsanlar nasıl değişir diye sormak gerekir o zaman.
+İnsanların değiştiğini dönüştüğünü gerçekten nasıl ölçeceğim ki?
+
 % important question: herkes neye ihtiyacı var ise onu toplar.
@@
 yani toplamak ile ayrıldığı noktalar nelerdir.
+Ben bir mana mı arıyorum?
+Yoksa kaybetmekten mi korkuyorum?
+Yeni kompozisyonlar oluşturmak istiyorum.
+Farklı karşımlar elde etmek istiyorum.
+Bir tür şaşırtmak durumu...
+Beklenmeyeni yapmak...
+En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
 
-%
-% EXHIBITION
-% Where people access them? How to design the experience here. The relationship with the location? 
-% Pizza box, with l shape box. I need to find a place to put them. 
-%
-%
+% Problem:
+% In theoratical part I am focusing on actually the trash.
+But should I focus on paper trash?
+Is there any difference?
+Ya da ben oradaki bir farklılıktan besleniyor muyum?
+It is not totally paper, actually they are package.
+Examples can be given related with package material.
+It has a very short life.
+Not short actually.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%
-%% Move to the other sections:
-%
-% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
-The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Explain your project that I am like and child: 
+% Collecting things means actually searching things. I'm searching for materials and also 
+% What is the main focus in my work? Participation? Transformation? Composite of them? Trash? What else? 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-21 chapter2.tex
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d

@@
 \chapter{Theory of Trash}
-In this chapter trash is examined in theoretical (and conceptual) aspect. Theoretical foundations of trash are discussed. (Further benefited from historical and social aspect of trash.)
+
+% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych
+\epigraph{\textit{\quotes{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}}}{\hfill --- Priscilla Uppal}
+
+In this chapter trash is examined in theoretical (and conceptual) aspect.
+Theoretical foundations of trash are discussed.
+(Further benefited from historical and social aspect of trash.) How do scholars conceptualized the trash?
+What do they say about it?
+In this chapter it will presented.
+It draws attention of many scholars and people who are professional in different areas.
+Further trash is a topic that common for the all ages through the human history.
+In other word this topic is not a new one.
+It always part of the human practice.
+It can be thought that it is refused, discarded thing as soon as possible there are people also carefully observing the concept giving attention to the discarding things.
 
@@
 %%%
-\section{Etymology}
-(Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
-There are slight differences between these words but sometimes they are used to signify same concept.
+\section{Etymology/Terminology}
+(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
+Although there are slight differences between these words, sometimes they are used to signify same concept.
+It is important to understand vocabulary of this topic before dive into the theory.
+It is very important to choose right terminology, because ...
+and also make more clearer the border of the work.
+As mentioned it very diverse vocabulary to define the practice and there is no agreed terminology.
+Some scholars uses junk art, other recycling art.
+Sometimes it makes difficult to research on this topic.
+And also I must point out that this topic is not limited with the English language.
+The topic is broad and it is not limited with english literature and vocabulary.
+% TODO reference for other languages and societies.
 
@@
 %%
-\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
+\subsection{Origins of Words}
 The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
@@
 %%
-\subsection{The difference between reuse and recycle}
+\subsection{Reuse and Recycle}
+One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used to signify the concept.
+
 According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
@@
 It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
+For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
 In this process, energy is required which depends upon the stages of transformation.
@@
 With the trash what moves?
+
+% Here is important thing is moving nature of trash.
+Objects moves and gains different meanings through this movement.
+Sometimes it becomes artwork, sometimes it becomes archelogical part, waits in the dumpsite or wait to be recycle.
+It also signifies that it is relative and result of a classification issue.
+All of them are creates a harmony.
+supports each other with different words and conceptualization.
 
@@
 Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
+
+%%% Reference from Identity, mobility and the throwaway society
+we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
+\quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
+In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
+Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
+The thesis, however, lacks depth and provenance.
+It is, actually, glib.
+Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
+% In this paper criticized the perception of throw away culture and arguments. They show the weak points of the arguments. What I understand from trow away culture?
 
@@
 % There is also strong relationship with the collecting discarded stuff and archeologies of waste.
+
+%%% Reference
+% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
+% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
+In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
+Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
+The thesis, however, lacks depth and provenance.
+It is, actually, glib.
+Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.
+
+\section{Summary}
+What can be extracted from all these words?
+
+\begin{itemize}
+\item Shared practice through the different ages of humanity and different societies. 
+\item Moving nature of trash.
+\item Classification, not the related with the object property. 
+\item Value creation, shifts in the society. 
+\end{itemize}
+
+Thompson thinks that the switch only occurs from losing all the value given the object.
+He refers that to gain new value previous systems ruins must be cleaned.
+Changing the context by first rubbishing them.

### 2015-10-21 chapter3.tex
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d

@@
 \chapter{Trash as Medium (Trash in the Art)}
+
+\epigraph{\textit{\quotes{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together.
+I assembled these two objects, which everyone then recognized as a bull’s head.
+The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense.
+If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \singlequotes{Here’s something that would make a good handlebar for my bicycle!} }}}{\hfill ---Pablo Picasso}
+
 How does trash draw attention of artist(, and also mine)?
@@
 
-\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was
-drawn to recycled art because of one simple factor---the price. "Free is certainly great, and that was a driving force for me early on in my career," he said.
+\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
+"Free is certainly great, and that was a driving force for me early on in my career," he said.
+
+\item Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London.
+The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says.
+(It is very corralate between Ages Varda's work.
+She shows at the side of human practice, Nelson looks the topic from object side.)
 
@@
 
-%junkyard art
+% junkyard art
 
@@
 
+%*************************************
 % Phrases...
 % What specific social issues are you trying to address through Labyrinth?
+% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art.
+Table 1 organizes this classification according to a set of multiple criteria.
+(But this one can be used at introduction, but it is too long to fit on introduction.
+Maybe select works by giving prominence to some of the features.
+So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art.
+Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.)
+\section{Crowdsourcing, Participation}
+% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
+In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}.
+The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers.
+Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing.
+Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.
+
+The value of crowdsourcing lies in the collective intelligence of the contributors.
+Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p.
+13).
+The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism.
+Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004).
+Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?
+
+All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks.
+They are not bought, not gift.
+They are found.
+They are accepted.
+One of the most creative medium is paper and pencil.
+Chance given to the people through this work.
+
+However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment.
+It is well studied area.
+Pick a method here.
+Transforming trash with collaboration.
+
+As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).
+
+Here this question can be raised about why this type collaboration.
+Another option can be working together with people on a table.
+Creating things at that time and transforming the objects here.
+Possibly the connection to the people will more realistic and intense.
+However same things can be succeed on the internet at some level.
+
+While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers.
+(This totally a new area to discuss, I'm going to summarize and introduce concepts and debates.
+How are they support my work and how they are give way to me?)
+
+% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories.
+Principally, my interest is in answering two key questions.
+What is crowdsourced art and how can it be classified?
+And how does the structure of the artwork determine the degree or significance of participation?
+
+% discussion is not collaboration, collaboration is used.
+
+% Umberto Eco's Open Work
+
+% SketchBook Project.
+Inspires me a lot.
+Lots of works from all over the world.
+Full of creativity and showcase of richness of people's expressions on the small notebooks.
+My work can be considered as a sketch book project through trash.
+Sketches or only creative progress is not the only consideration.
+You can send your lecture notes.
+
+% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
+% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
+Reveal all his possessions.
+and loosing them while you are alive.
+Turning them to rubbish making them unusable.
+breaking down the all the meaning.
+breaking down the connections.
+% Michael Landy's Art Bin uses a art gallery to create his dust bin.
+Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
+Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
+"There's no hierarchy once they are in the bin" All of them are accepted as same.
+Ultimate equality.
+Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
+Nothing's too good for the art bin.
+Everything can fit into the art bin.
+Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
+As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
+It is a very big glass bin and isolates people.
+There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
+There is no limitation of throwing away even if art.
+
+% In this thesis project case the issue is not the nature of art and its methods.

### 2015-10-21 chapter1.tex
puzzle notebook.
Former-commit-id: 9d9397215989fa8018a50262946fbe342928ce75
artwork, statement, questions and debates
Former-commit-id: 9897c39b89687a410855e37f69f9464f07e3199e
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

@@
 \chapter{Introduction}
-Some text...
 
+%****************************************
+% Structure of this chapter
+% Section: topic and its significance
+% Section: the purpose of this study
+% Section: overview of chapters
+
+The topic and its significance \ldots
+
+\section{Purpose of this study}
+The aim of this study is \ldots
+
+\section{Overview of Chapters}
+Following chapter focuses on trash in theoretical aspects.
+
+Third chapter seeks the root of using trash in the artworks and looks through the sample artworks.
+
+Fourth chapter explains the project that supports this thesis. It's stages, approach to the topic mentioned here.
+
+Finally last chapter offer an overall conclusion of this thesis.
+
+%****************************************
+% About the thesis statement and focus:
+% Is it too broad?
+% Is it debatable? Is is fact? (Trash is not a end point of objects, there is a life waiting for them?)
+% What is my side? throwing away is required for society to go further? or omitting the tons of possibilities... 
+% Supporting claims?
+% What is my thesis statement? Again same topic... It needs to be solved...
+
+%****************************************
+% Examples from other thesis.
+% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology.
+// The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
+It is questioned the role of art in transformation of discarded items.
+This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
+Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.
+
+%****************************************
+% Sample phrases:
+% The discussions (mentioned discussion are also formed the thesis project entitled ... )
+% Aim of this thesis is ...
+% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
+% as a reaction to the consumerist society.
+
+%****************************************
+% Some comments
 % This written portion was to evaluate the project in terms of a justificatory theoretical framework.
-
-% So what is the issue here?
-
-% Title: Trash as a Medium.
-
-% Subsection: the purpose of this study
-% Subsection: overview of chapters
-
 % This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.
-
 % Burada önemli olan şey soru veya sorgulanan şey.
@@
 Tartışmalar ne üzerine olmalı bu durumda.
+% The project aims to what? and what needs to justify what it questions? 
+% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.
 
-% The project aims to what? and what needs to justify what it questions?
+% Tipografi ve ideoloji arasında bir ilişki vardır.
+Fotoğrafın geleceği?
+Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir?
+kelime ve imaj arasında bir problme olduğundan bahsediyor.
+Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir.
+Toplum ve çöp nispeten bir problemli bir durum.
+Burada bir dert var.
+Atılan tüketilen manalar var.
+Sanat bunları provoke mi ediyor.
+Peki ya ben ne öneriyorum, yani aslında bir şey önermem mi gerekiyor?
+Sanat ve çöp arasında nasıl bir ilişki vardır?
+Çöp ile diğer nesneler arasında nasıl bir ilişki vardır?
+
+% Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor.
+iş neyi soruyor ise aslında tez de onu soruyor.
+Yapılan işlerle sorulan sorular arasında bir bağlantı var.
+Bu noktada aslında benim işin neyi sorguladığını bulmam gerekli.
+Çöp dönüştürülebilir, sanatsal bağlamda.
+(Çok geniş değil mi abi sanatsal bağlamda demek?
+Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli.
+
+% çöpe yeni bir alternatif yaşam üretmek gerekli.
+Aslında hepimiz bir şeyleri dönüştürüyoruz.
+Agnes varda aslında neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında snatçıları da geziyor, çünkü onlar da topluyorlar.
+Onlar da o çöplerde farklı şeyler görüyorlar.
+Kendi de mesela çöpe atılmış bir şeye anlam yüklüyor.
+Kendisininde aslında bir toplayıcı olduğunun farkına varıyor.
+
+% Çöp ve dönüşüm, dönüşümün aşamaları... Başka sanatçıların methodlarını incelemek pek mantılı değil, onun dışında başka bir şey bulmam gerekli.

### 2015-10-21 chapter2.tex
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

@@
 %%
-\subsection{Origins of Words}
+\subsection{Origins of Vocabulary}
 The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
@@
 It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
+
+% TODO other words, relation, comparasition etc.
 
@@
 % TODO not sure for this section, maybe mentioned above...
-\subsection{My terminology selection}
-(I use this word for this and that?)
+I use word 'x' because \ldots (not sure for this.)
 
@@
 
-%
-\subsubsection{Cycle of trash}
+%%
+%%
+\subsection{Cycle of trash}
 Trash moves, objects moves from place to place.
@@
 
-%
-\subsubsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from
-our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-%
-\subsubsection{Perspectives related with trash from different disciplines}
+%%
+%%
+\subsection{Perspectives related with trash from different disciplines}
 This is very important because the problem of trash is being tried to be handled by different disciplines.
@@
 
-%
-\subsubsection{Throw away culture}
+%%
+%%
+\subsection{Throw away culture}
 Continuously consuming things and disposing of something.
@@
 
-%
-\subsubsection{How does it become trash?}
+In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this.
+Always needed to keep in my mind that the practice of discard is not belongs to only current society.
+
+%%
+%%
+\subsection{How does it become trash?}
 Here the purpose is to understand the dynamics that turn objects to trash.
@@
 
-%
-\subsubsection{Types and Comparison of trashes}
+%%
+%%
+\subsection{Types and Comparison of trashes}
 The complexity of produced trashes of societies is increasing.
@@
 
-%
-\subsubsection{What is wrong with trash?}
+The approach to the different type of trash will be different.
+In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
+There are some trashes that are more close to the people.
+More easy to convert them.
+more easy to regain to the society.
+
+%%
+%%
+\subsection{What is wrong with trash?}
 Relationship between entropy (second law of thermodynamics) and waste.
@@
 %%
+\subsection{Examined-life, Zizek}
+(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
+In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
+He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
+Draw attention to notion of even if trash disappears from our world but not world.
+It seems as though the thrown out garbage disappears from
+our world.
+However, it disappears only from the world of illusions, but still exists in reality.
+He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
+He claims that it is ideological in the sense that wrong thinking important problems.
+Nature contains unimaginable catastrophes.
+think oil and distinct animals and plants.
+we profit balance part of the nature but it is created from catastrophe.
+Are we aware of this catastrophe.
+He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
+It would be too much." its voice is like "Don't mess with D.N.A.
+Don't mess with nature.
+Don't do it" etc.
+We should not forget that we are part of the ecology.
+We must more alienated from the nature.
+We must find poetry and spirituality in the dimension of trash.
+That's the true love of world.
+Love is not about idealization.
+This part will be extended later.)
+
+\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
+Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
+Such interpretation makes life easier.
+However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
+Nature is a series of unthinkable disasters.
+Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
+Do not touch DNA!
+Do not develop new medicines!
+Do not invent new technologies!” How one should react to these reproaches?
+Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
+
+His basic argument is that the modern eco movement is a conservative ideology.
+It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
+Basically he says the eco movement has it's head in the clouds.
+If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
+
+\begin{itemize}
+\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
+\item Ideology addresses real problems but mystifies them.
+\item We search for meaning when a horrible event happens to make it easier to accept.
+\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
+\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
+\item Ecology is becoming more like religion with dogmas.
+\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
+\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
+\item Learn to love our trash as a part of ecology.
+\end{itemize}
+
+How much harmonious all these produced materials with nature?
+How many animals and the plant can use these discarded items?
+(Because of complex production methods their recycling requires complex processes again.
+Some of them already produced to protect goods from natural factors (like decaying etc.).
+However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
+However, some artists turned to trash into site-specific sculptures that are more than trash heap.
+not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
+(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
+The more likely idea will be we will live harmoniously with what we create.
+
+Getting rid of it is not the significant action.
+It still waits us at somewhere else or the next generations have to cope with it.
+(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
+To break out of this eternal cycle of functioning.
+
+The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
+and what are the other dimensions?)
+
+Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
+
+Trash of developed societies has higher decomposing period in the nature.
+Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
+
+%%
+%%
 \subsection{Culture, Values, and Garbage}
@@
 
+%%%
+%%%
+%%%
 \section{Summary}
-What can be extracted from all these words?
-
 \begin{itemize}
 \item Shared practice through the different ages of humanity and different societies. 
-\item Moving nature of trash.
-\item Classification, not the related with the object property. 
+\item Moving nature of trash/objects.
+\item Classification is the main key, trash is not related with the object property. 
 \item Value creation, shifts in the society. 
+\item Trash has archaeological value.
+\item Trash has potential to be used again.
 \end{itemize}

### 2015-10-21 chapter3.tex
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

@@
-\chapter{Trash as Medium (Trash in the Art)}
+\chapter{Trash in Art}
 
@@
 %%%
-\section{Collage, Assemblage and the Found Object}
+\section{Root in the Art History}
 In this chapter root of using objects in the artworks is examined.
@@
 Developing artworks not only painting but also using paper and other stuff by pasting them together.
+
+% TODO praphase
+\textbf{[TODO praphrase]} "The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
+Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
+A.
+Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
 
@@
 %%
-%% TODO reading...
-\subsection{Art and activism}
-Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.
+%% junkyard art
+\subsection{Garbage Art, Recycling Art}
+"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
 
-\subsection{Recycling in the context of Art}
 % From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
@@
 In that sense, art, as a system, is an act of recycling.
-
-%%
-%%
-\subsection{Garbage Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%%
-%% TODO change here
-\subsection{History of Consumption and Waste}
-"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
-Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
-Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
-A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
 
@@
 %% TODO sample statements here.
-\subsection{Artist statements}
+%\subsection{Artist statements}
 
@@
 
-%%
-%%
-\subsection{Artistic tactics}
+%*****************************************
+% Maybe...
+% Artistic tactics
+% Topology of artworks
+%*****************************************
 
@@
 
-% junkyard art
-
 % TODO PRAP. from rethink, reimagine, reinvent
@@
 Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).
+
+%%
+%% ACTIVISM as a methodology 
+%% TODO reading...
+\section{Art and activism}
+Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.
 
@@
 
-% discussion is not collaboration, collaboration is used.
+% why collaboration, is it really collaboration?
 
@@
 
+%************************
+% inspirational work.
 % SketchBook Project.
@@
 
-% In this thesis project case the issue is not the nature of art and its methods.
+% In this thesis project case the issue is not the language of art and its methods.

### 2015-10-23 chapter2.tex
reorganization
Former-commit-id: 6fac98764f44817919a9acf6bd80803b5ab13dcd

@@
 It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
+
+%From http://dictionary.reference.com/
+\textbf{Waste.}
+\begin{itemize}
+\item v. to consume, spend, or employ uselessly or without adequate return; use to no avail or profit; squander:to waste money; to waste words.
+\item v. to fail or neglect to use: to waste an opportunity.
+\item n. An unusable or unwanted substance or material, such as a waste product. See also hazardous waste, landfill. 
+\item Antonyms: save
+\end{itemize}
+
+\textbf{Trash.}
+\begin{itemize}
+\item n. anything worthless, useless, or discarded; rubbish.
+\item n. foolish or pointless ideas, talk, or writing; nonsense.
+\item n. literary or artistic material of poor or inferior quality. a literary or artistic production of poor quality.
+\item Garbage collector.
+\end{itemize}
+
+\textbf{Garbage.}
+\begin{itemize}
+\item n. discarded animal and vegetable matter, as from a kitchen; refuse.
+\item n. any matter that is no longer wanted or needed; trash.
+\item Synonyms: litter, refuse, junk, rubbish.
+\item Origin.
+early 15c., "giblets of a fowl, waste parts of an animal," later confused with garble in its sense of "siftings, refuse." Perhaps some senses derive from Old French garbe "a bundle of sheaves, entrails," from Proto-Germanic *garba- (cf.
+Dutch garf, German garbe "sheaf"), from PIE *ghrebh- "a handful, a grasp." Sense of "refuse, filth" is first attested 1580s; used figuratively for "worthless stuff" from 1590s.
+Garbology "study of waste as a social science" is from 1976.
+\end{itemize}
+
+\textbf{Rubbish.}
+\begin{itemize}
+\item n. worthless, unwanted material that is rejected or thrown out; debris; litter; trash.
+\item n. nonsense, as in writing or art.
+\end{itemize}
+
+\textbf{Junk.}
+\begin{itemize}
+\item n. any old or discarded material, as metal, paper, or rags.
+\item n. anything that is regarded as worthless, meaningless, or contemptible; trash.
+\item v. to cast aside as junk; discard as no longer of use; scrap.
+\item adj. cheap, worthless, unwanted, or trashy.
+\end{itemize}
+
+\textbf{Refuse.}
+\begin{itemize}
+\item n. something that is discarded as worthless or useless; rubbish; trash; garbage.
+\item Antonyms: accept, welcome.
+\end{itemize}
 
@@
 
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials.]
+[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials. So what is value?]
+\textbf{Value.}
+\begin{itemize}
+\item n. relative worth, merit, or importance: the value of a college education; the value of a queen in chess.
+\item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
+\item n. estimated or assigned worth; valuation: a painting with a current value of $500,000.
+\item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books.
+Worth implies especially spiritual qualities of mind and character, or moral excellence: Few knew her true worth.
+\item the desirability of a thing, often in respect of some property such as usefulness or exchangeability; worth, merit, or importance
+\end{itemize}
 
@@
 
+\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic.
+Show the problematic understanding thought to the garbage.
+Suggest another thing, and point out the need for the new approach.
+Beyond the ecological problem there are different sides of it.
+Different readings can be added to the topic.
+Adding spirituality and new aesthetics dimension to the topic.
+
 %%
@@
 "In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%%
-%%%
-%%%
-\section{Archaeology of Garbage}
 

### 2015-10-23 chapter4.tex
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d
reorganization
Former-commit-id: 6fac98764f44817919a9acf6bd80803b5ab13dcd

@@
 % Converting disposal things to multiple time usage. Realizing the alternative lives of trash beyond their defined one shot life. Giving attention to the things.
+
+%%%
+%%%
+%%%
+\section{Inspired Works}
+There are some works that inspire me a lot when developing the work.
+They are not actually trash related works therefore I put them in different section and here before the details of my work.
+However the previous chapter has also very inspirational contributions to the my work.
+They helped the understand the topic and develop an approach to the topic.
+In this section some projects are mentioned and their methodologies are explained.
+How are these works effected my work.
+What is the relationship between them?
+(Maybe all of them can be explained only the related part of it.)
+\begin{itemize}
+\item SketchBook Project.
+Inspires me a lot.
+Lots of works from all over the world.
+Full of creativity and showcase of richness of people's expressions on the small notebooks.
+My work can be considered as a sketch book project through trash.
+Sketches or only creative progress is not the only consideration.
+You can send your lecture notes.
+\end{itemize}
 
@@
 Not short actually.
+
+% How to establish the relationship between the collaboration and the trash?
+transforming them with the help of people.
+However, main discussion is not about collaboration.
+Here collaboration is a method to reach the aim of the project.
+In other words it is a methodology.
+There are different methodologies applied by artist to transform them.
+My methodology is to collaborate with the other people.
+My aim is to transform trash with people.
+Also make them to engage with trash.
+Trash is only one of the things discarded by the society.
+What is the importance of co-authored work?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-23 chapter3.tex
reorganization
Former-commit-id: 6fac98764f44817919a9acf6bd80803b5ab13dcd
new artwork
Former-commit-id: e9247e54386b522d9f8b64f65f9dc058b1befa5b

@@
 
+% From http://www.thisiscolossal.com/2014/06/historical-fine-oil-portraits-on-crumpled-trash-by-kim-alsbrooks/, http://www.thisiscolossal.com/2015/05/new-historical-portraits-on-flattened-cans-by-kim-alsbrooks/, http://kimalsbrookswhitetrash.blogspot.com.tr/
+\item
+\parbox[t]{
+	\dimexpr\textwidth-\leftmargin}{%
+      \vspace{-2.5mm}
+      \begin{wrapfigure}[22]{r}{0.4\textwidth}
+        \centering
+        \vspace{-\baselineskip}
+        \includegraphics[width=\linewidth]{graphics/Alsbrooks.jpg}
+        \caption{The White Trash Series by Kim Alsbrooks}
+      \end{wrapfigure}
+Kim Alsbrooks, historical oil portraits on flattened beers cans and fast food containers.
+\quotes{The White Trash Series was developed while living in the South out of frustration with some of the prevailing ideologies, in particular, class distinction.
+This ideology seems to be based on a combination of myth, biased history and a bizarre sentimentality about old wars and social structures.
+With the juxtaposition of the portraits from museums, once painted on ivory, now on flattened trash like beer cans and fast food containers, the artist sets out to even the playing field, challenging the perception of the social elite in today’s society.} \quotes{On technique: The trash is found flat, on the street.
+One cannot flatten the trash.
+It just doesn't work.
+It must be found so that there are no wrinkles in the middle and the graphic should be well centered.
+Then the portraits are found that are complimentary to the particular trash.
+Generally I depict miniature portraits from the watercolor on ivory era (17th-18th century more or less).
+The trash is gessoed in the oval shape, image drawn in graphite, painted in oils and varnished.} I need to mention that this images are very subversing to the perception of us about these images.
+It is unexpected way of presenting images.
+There is a relationship with the image and painting.
+At least this work questioned this relation.
+With tihs work one can ask that with the painting trashed can become valueable thing or with this can this paintiing became valueless.
+Artsist combines two thing that can be never thought together.
+New combination, new meaning.}
+
 \end{itemize}
@@
 
+% TODO 
 % Umberto Eco's Open Work
-
-%************************
-% inspirational work.
-% SketchBook Project.
-Inspires me a lot.
-Lots of works from all over the world.
-Full of creativity and showcase of richness of people's expressions on the small notebooks.
-My work can be considered as a sketch book project through trash.
-Sketches or only creative progress is not the only consideration.
-You can send your lecture notes.
 

### 2015-10-25 chapter3.tex
chapter 3 organization.
Former-commit-id: fcd9c8bc8fd426f8392128fbd8fee0972cb7998e

@@
 
-How does trash draw attention of artist(, and also mine)?
+How and why does trash draw attention of artists(, and also mine)?
 In this chapter how artist approached to the trash and their techniques are discussed in the context of art.
@@
 
-% TODO motivations of artists. their ideas about them, because they also point what is wrong with it? or their perceptions.
+% TODO List motivations of artists and their ideas about junk. Because it reveals the different dimensions of this topic.
 
@@
 \section{Root in the Art History}
-In this chapter root of using objects in the artworks is examined.
-Using objects on artworks beyond their intended purpose.
+In this chapter root of using ---(non-art)--- objects in the artworks is examined.
+In other words using objects in artworks beyond their intended purpose or intended meaning and function.
 Developing artworks not only painting but also using paper and other stuff by pasting them together.
+(Foundations of trash in art.) Using object apart from their proposed meaning is not a new thing[ref required, using jewelry by African tribes], through the ages people used objects and tools for different purposes.
+However it is not discussed in the context of (western)art and not accepted method for art making.
+Therefore who and which work introduces this concept and how it is developed and evolved in time.
+(of course it is a brief overview by some remarkable pieces.)
 
@@
 % TODO reading...
-\cite{greenberg1984collage}
+[TODO read this resource]\cite{greenberg1984collage}
 
@@
 % TODO reading...
-\cite{strasser1999waste}
+[TODO read this resource]\cite{strasser1999waste}
 
@@
 
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
 Recycling has always been a common practice in the arts at least at a non-material level.
@@
 In that sense, art, as a system, is an act of recycling.
+[TODO ref]
 
@@
 \section{Example Artworks}
-Artist and artworks related with trash and their analysis. Stages of their works and methods.
+Artist and artworks related with trash and their analysis.
+Stages of their works and methods.
+(Keep in mind that what can be extracted from these works?) There are a lot of work that needs to mentioned here but to stay focused and not to move away from the scope of the thesis only the works are selected with relation to the theory chapter.
+(is it really like that?)
+
+This section is more focused on trash.
 
@@
 Or is there a point at which waste cannot become art (or anything else)?
+
+% TODO Naive debate??
+All that can be seen as naive act because of little impact and outside of the system(which system?).
+As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill.
+However this very argumentative that having no impact or little impact.
+It might be true that this practices solve all problems of landfill or etc.
+But changes individuals and communities life.
+It recreate and rebuilds the community.
+Even if it is one simple object worth look and see the opportunities of it.
 
@@
 
+%\item Pictures of Garbage by Vik Muniz
 \item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
@@
 % https://www.youtube.com/watch?v=sJxxdQox7n0
-\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.
+\item \textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra”.
+``The world send us garbage.
+We send back music''.
+
+Cateura, Paraguay is a small city that has grown atop a massive dump.
+It is regarded as one of the poorest slums in Latin America, a village where people live among a sea of garbage.
+Incredibly, the landfill itself is the primary form of subsistence for many residents, who pick through waste for items that can be used or sold.
+Prospects for most of the children born in Cateura is bleak as gangs and drugs await many of them.
+But then one day, something amazing happened.
+A garbage picker named Nicolás Gómez (known as “Cola”) found a piece of trash that resembled a violin and brought it to musician Favio Chávez.
+Using other objects collected from the dump, the pair constructed a functional violin in a place where a real violin is worth more a house.
+Using items gleaned completely from the dump, the pair then built a cello, a flute, a drum, and suddenly had a wild idea: could a children’s orchestra be born in one of the most depressed areas in the world?
+As you can guess, the answer was yes.
+
+To view scenes from the landfill slum of Cateura in Paraguay is to look into the depths of extreme poverty.
+But within the contents of the landfill are glimmers of hope in the form of cardboard, utensils and other discarded materials that can be crafted into imperfect but usable musical instruments.
+These makeshift violins, flutes and cellos, combined with instruction from a local music teacher, have given birth to the Recycled Orchestra of Cateura.
+Through the music of Mozart, Beethoven and Vivaldi, this orchestra allows the young musicians to transcend their identity as children of poverty.
+
+"A violin is worth more than a house here," says Favio Chavez, the orchestra's director and founder.
+In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
+"My life would be worthless without music." says one girl in pigtails.
+A young man named Juan Manuel Chavez, nicknamed Bebi, has a cello fashioned out of an oil can and old cooking tools.
+For the camera, he plays the Prelude to Bach's Cello Suite No.
+1 — beautifully.
+
+"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either."
+
+This project can be seen as a bricolage practice. They build their musical instruments from what is available around.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
+        \caption{Sax}
+        \label{fig:gull}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
+        \caption{Violin}
+        \label{fig:tiger}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+    %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic_drum2.png}
+        \caption{Drum}
+        \label{fig:mouse}
+    \end{subfigure}
+    \caption{Pictures of animals}\label{fig:animals}
+\end{figure}
+
+% Beni bu projede etkileyen en öenmli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
+yokluk içinden bir şeyler üretmeleri.
+Her ne kadar üretilen müzik aletleri mükemmel olmasalarda onlar için bulunmayacak bir nimet.
+Üretilen ürünün kalitesi gerçekten de endüstriyel standartların altında.
+Müziğin kalitesi diğer kadar olmasa bile farklı bir yaklaşım sunuyor olması önemli.
+Nasıl oluyor da bu aletten bu ses çıkıyor.
+Amatör ruhun getirdiği bambaşka bir algı var.
+Müziğin ötesi, düşündürdüğü bambaşka şeyler var, olaya yeni bir boyut getiriyor.
+Başka bir alanla diğerinin buluştuğunun bir göstergesi.
+
+% Peki bu iş neden sanat işi olsun ki?
+
+% Bambaşka şeylere dönüşen ürünler.
+Üretim amaçlarının dışında.
+Yeni linkler bağlantılar kuran müzik aletleri.
+Kendilerinden beklenmeyeni başarmak vs.
+Daha önce görülmeyen şeyler, görülmeyen ilişkiler.
 
@@
 %\item Autoconstrucción by Abraham Cruzvillegas
-%\item Pictures of Garbage by Vik Muniz
 
@@
 
+% Yav biraz da tarihsel fotoğraflara ihtiyaç var mı? aslında bu artworkleri anlatiştaki sıra nasıl olmalı.
+
+\item Martin Kaltwasser \& Folke Föbberling: City As a Resource.
+One Man's Trash Is Another Man's Treasure.
+Garbage dump or gold mine?
+The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource.
+Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear.
+In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization.
+For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden.
+In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.
+
+Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
+Pavilions, villages of huts and even whole houses are appearing over night.
+Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources.
+In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation.
+Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning.
+Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible.
+Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.
+
+% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
+Public space is under siege.
+The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities.
+In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation.
+Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.
+
+Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
+Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures.
+The work will be an act of resistance to occupy and reclaim a space and change its meaning.
+At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.
+
+For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
+
+Public space and transformed materials.
+
+% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
+Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
+The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.
+
+They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
+In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces.
+And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.
+
+% Sample phrases
+% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
+Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
+With recycled objects, one can build anti-seismic and energy efficient houses.
+Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
+There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
+Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
+Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
+David Hertz reused the wings of a 747 as roof for a villa in Malibu.
+TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
+Yatin Pandya and Footprints E.A.R.T.H.
+built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
+James & Mau and Infiniski designed fashion homes with recycled containers.
+The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
+The GAD.
+In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
+The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
+All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.
+
 \end{itemize}
@@
 %% TODO sample statements here.
-%\subsection{Artist statements}
-
+\subsection{Artist statements}
 \begin{itemize}
@@
 
-% why collaboration, is it really collaboration?
+% why collaboration, is it really a collaboration?
 
@@
 % In this thesis project case the issue is not the language of art and its methods.
+
+\section{Summary}
+Artists works and the place of the trash in the art can be summarized as follow:
+\begin{itemize}
+\item Artist see them as potential.
+But what type potential it haves.
+In which areas.
+They are already thrown away, if it was value or has a place in the current system they are not thrown away.
+There is an alternative life and outside of the ruling system.
+\item Visual uniqueness, aesthetics dimension.
+\end{itemize}

### 2015-10-25 main.tex
Layout & Header organization updated.
Former-commit-id: 497c876eefc8a79803afe4223ecd39f1c07e4b62
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103
puzzle notebook.
Former-commit-id: 9d9397215989fa8018a50262946fbe342928ce75
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab
new artwork
Former-commit-id: e9247e54386b522d9f8b64f65f9dc058b1befa5b
chapter 3 organization.
Former-commit-id: fcd9c8bc8fd426f8392128fbd8fee0972cb7998e

@@
 \documentclass[12pt]{report}
+\usepackage[hidelinks]{hyperref}
 \usepackage[english]{babel}
@@
 \usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
+\usepackage{epigraph}
 %\usepackage{setspace}
@@
 %\graphicspath{ {graphics/} }
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{wrapfig}
+
+\setlength{\epigraphwidth}{.6\textwidth}
+\setlength{\epigraphrule}{0pt}
+
+\hypersetup{
+    pdftitle			= {Thesis Draft},
+    pdfauthor			= {Mustafa ilhan},
+    pdfsubject			= {Trash, Art},
+    pdfkeywords			= {mfa, thesis, trash, art},
+    colorlinks			= false,
+    pdfborder			= {0 0 0},
+    pdfpagemode			= UseOutlines
+}
 
@@
 \pagenumbering{roman}
+\setcounter{secnumdepth}{3}
+\setcounter{tocdepth}{3}
 \tableofcontents
@@
 %\listoftables
+
+%****************************************
+% Title Ideas for Thesis 
+% - Trash as an Artistic Medium.
+% - Trash Notebooks: Trash in the Context of Art
+% - Trash Notebooks: Exploring the potential of trash through art practice
+%****************************************
+
+%****************************************
+% Abstract ideas
+% You can add shortly definition of trash and discard. Any object can be art in 19th century.
+% Structure of this thesis: written part of it and the project support each other.
+%****************************************
 
@@
 Are there any differences with the original items compared to discarded items?
-(In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
+(In other words has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
 (and also in which scope?
@@
 The process effects how one's lives and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)
+(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose do not build a thing that is produced from discarded material to watch it from a distance.
+The important thing is to interact with it.
+Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it.
+It must call the viewer to interact with it.
+(not only watch.)
 
-With the help of art discarded thing can be find a place in the society.
-This issue is examined through the trash which is discarded by the society.
-By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life.
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.
+% Olay sadece böyle çöpten bir şeyler yapıp insanların seyretmesi değil, mühim olan onunla iletişime, ilişkeye geçmek.
+Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki?
+İnsanların bu işin aşamalarının bir parçası olmalılar.
+
+With the help of art discarded things can be find a place in the society.
+(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.
 
@@
 
-\textbf{Questions.} Do she/he want to take back (or revisit) the trash once thrown away?
+Do she/he want to take back (or revisit) the trash once thrown away?
 People do not want to think of what they throw away.
@@
 
-\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
+With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
 
-\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims.
+Using trash can not only understand in ecological perceptions, it also have powerful political claims.
 Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
 
-\vfill\noindent\textbf{\textit{Keywords:}} trash(discarded things), art, value creation, transformation.
+Junk(or trash) can be seen as a resource that is fertile to new meanings, creations and aesthetics.
+Ignored and discarded nature of garbage when rethought becomes fertile resource.
+Trash as a resource (as a artistic material.)
+
+\vfill\noindent\textbf{\textit{Keywords:}} trash(discarded objects), art, value creation, transformation.
 \end{abstract}
+
+%****************************************
+% Sample abstract from a thesis:
+% Bu çalışmada, ne kadar itici bir kavram olsa da, çöplük olgusunun çirkinlikten güzelliğe ulaşarak estetik bir haz uyandırması amaç edinilmiştir.
+Iticici gözüken bir konunun resim diliyle anlatımı ile tersine çekici ilginç bir sanat konusu olabileceğinin somutlaştırılması amaçlanmıştır.
+Sanatçı bir anlamda doğada yaşamda bulunan küçük ayrıntıları, sanatsal bir gözle yaklaşarak gösterebilendir.
+Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.
+Oysa önemsiz gibi gözüken itici karmaşık konular bile sanatsal kaygılarla ele ahnabilmelidir.
+Önemli olan, bu konalara estetik yaklaşım ve izlenen anlatım yol ve teknikleridir.
+Özgün baskı dallarından kazı resim (gravür) tekniğinin ele alınan konunun görselleştirilmesinde, anlatımında en uygun teknik olmasıdır.
+Çünkü her sanatçı kendi doğasına en uygun olan teknik ve malzemelerin olanaklarıyla kendini en rahat biçimde ifade etme olanağı bulur.
+Kendine özgü bir biçim ve anlatım diliyle dile getirmek gerçekleştirmek çabalan özgünlüğü yakalamak içindir.
+Bu çalışmada özgünlüğü yakalamak, çöplük olgusunun oluşturduğu dinamik yapı, objelerin biçimlerine bağlı kalmadan plastik dille görselleştirilmiştir.
+Seçilen teknik doğası gereği raslantısal tadlarada olanak vermektedir.
+Oluşturulan resimlerde durağan bir dengeden çok dinamik biçim ilişkilerine dayanan gerilimli bir etkinin yakalanması amaçlanmıştır.
 

### 2015-10-25 chapter2.tex
new artwork
Former-commit-id: e9247e54386b522d9f8b64f65f9dc058b1befa5b
reorganization and compilation.
Former-commit-id: f9b8dcf47704fea0ad54949bca9599f5d2407301

@@
 
-In this chapter trash is examined in theoretical (and conceptual) aspect.
+In this chapter trash (and the practice of transforming trash) is examined in theoretical (and conceptual) aspect.
 Theoretical foundations of trash are discussed.
-(Further benefited from historical and social aspect of trash.) How do scholars conceptualized the trash?
+(Further benefited from historical and social aspect of trash.
+(?)) How do scholars conceptualized the trash?
 What do they say about it?
-In this chapter it will presented.
-It draws attention of many scholars and people who are professional in different areas.
-Further trash is a topic that common for the all ages through the human history.
-In other word this topic is not a new one.
-It always part of the human practice.
-It can be thought that it is refused, discarded thing as soon as possible there are people also carefully observing the concept giving attention to the discarding things.
+
+Trash draws attention of many scholars and people who are professional in different areas.
+Further trash is a common topic(problem?) of the all ages through the human history.
+In other words this topic is not introduced in recent years (or ages).
+It always part of the human practice and life.
+Even if trash is refused and discarded thing, there are people giving attention to them.
 
@@
 \section{Etymology/Terminology}
-(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
-Although there are slight differences between these words, sometimes they are used to signify same concept.
-It is important to understand vocabulary of this topic before dive into the theory.
+(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
+Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
+It is important to understand diverse vocabulary of this topic before dive into the theory.
 It is very important to choose right terminology, because ...
-and also make more clearer the border of the work.
-As mentioned it very diverse vocabulary to define the practice and there is no agreed terminology.
-Some scholars uses junk art, other recycling art.
-Sometimes it makes difficult to research on this topic.
+and also make more clearer the borders of the work.
+There is no agreed (or specific) terminology.
+Some scholars uses junk art, others recycling art.
+Sometimes this make difficult to research on this topic.
 And also I must point out that this topic is not limited with the English language.
-The topic is broad and it is not limited with english literature and vocabulary.
+The topic is broad and it is not limited with english literature and vocabulary (ref required).
 % TODO reference for other languages and societies.
@@
 \subsection{Origins of Vocabulary}
-The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?
+The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
+What were people throwing out when these words were coined?
 
-Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-Garbology is a study of waste as a social science.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.
-
-Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-
-%From http://dictionary.reference.com/
+%From http://dictionary.reference.com/, http://www.etymonline.com/
 \textbf{Waste.}
@@
 \item n. An unusable or unwanted substance or material, such as a waste product. See also hazardous waste, landfill. 
+\item Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
+German has retained the original meaning in wüste (desert).
+Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
+It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
 \item Antonyms: save
@@
 Dutch garf, German garbe "sheaf"), from PIE *ghrebh- "a handful, a grasp." Sense of "refuse, filth" is first attested 1580s; used figuratively for "worthless stuff" from 1590s.
-Garbology "study of waste as a social science" is from 1976.
+(Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
+In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.)
 \end{itemize}
@@
 
-% TODO other words, relation, comparasition etc.
+% TODO other words, relation, comparison etc.
 
@@
 \subsection{Reuse and Recycle}
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used to signify the concept.
+One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).
 
@@
 Why throw something away when you can give it another life?
-Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
+Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
 Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
 For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-Reuse occurs when waste in an unchanged chemical form is used in a process that did not create the original product.
-Examples include crushed glass containers (cullet) used to manufacture glass wool insulation or manufactured sand, and various forms of waste polypropylene used to make clothing.
 
@@
 
-% TODO not sure for this section, maybe mentioned above...
-I use word 'x' because \ldots (not sure for this.)
-
 %%%
@@
 In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
+Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
 Sometimes it is accepted as a problem that is need to carefully and seriously manged.
@@
 Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between
-garbage and the arts, I am interested in two questions.
+Particularly in the connection between garbage and the arts, I am interested in two questions.
 First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
@@
 
-% Here is important thing is moving nature of trash.
+% Like a summary sentence
+Here the important thing is moving nature of trash.
 Objects moves and gains different meanings through this movement.
-Sometimes it becomes artwork, sometimes it becomes archelogical part, waits in the dumpsite or wait to be recycle.
+Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
 It also signifies that it is relative and result of a classification issue.
@@
 \item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it handled by the municipals generally.
-\item Technological perspectives
+\item Management of it (handled by the municipals generally).
+\item Technological perspectives.
+(seeing trash as a design problem.
+developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
+development in what sense?)
 \end{itemize}
@@
 \quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{}
+How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
 
@@
 %%% Reference from Identity, mobility and the throwaway society
-we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
+we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)
+
 \quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
@@
 In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this.
-Always needed to keep in my mind that the practice of discard is not belongs to only current society.
+Always needed to keep in my mind that the practice of discard does not exist on only current societies.
 
@@
 
-% TODO: ragpickers from benjamin and archades project.
+[TODO: ragpickers from benjamin and archades project.]
 
@@
 % TODO PRAP. REF.
+(Summary From Liz Parsons.)
+
 A key critique of the rubbish theory is its neglect of the practices of value creation.
@@
 \subsection{Theoretical Analysis of Found Object}
+(Summary From Paul M Camic.)
+
 % TODO PRAP. REF.
@@
 \item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
-\item n. estimated or assigned worth; valuation: a painting with a current value of $500,000.
+\item n. estimated or assigned worth; valuation: a painting with a current value of \$500,000.
 \item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books.
@@
 \end{itemize}
+
+%%%
+%%%
+%%%
+\section{Bricolage}
+Dictionary meaning; something constructed using whatever was available at the time.
+
+% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;
+
+% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime.
+bunu yapan kişiye de bricoleur deniyormuş.
+lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş.
+kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.
+
+Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
+\cite{levi1966savage}
+
+the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
+
+\begin{blockquote}
+[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
+His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
+\end{blockquote}
+
+\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.
+
+\begin{blockquote}
+The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
+There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
+\end{blockquote}
+
+\begin{blockquote}
+The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
+In this sense the engineer is a myth.
+A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
+The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
+\end{blockquote}
+
+% TODO reading...
+[TODO use this ref]\cite{strasser1999waste}
+
+Bricolage is different than collage.
+Bricolage > collage.
+Because it is more general understanding of human practice.
+Collage is just only gluing paper together and it can be only a subset of bricolage.
+Same applicable for assemblage.
+Transforming trash can be examined within bricolage.
 
@@
 Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from
-our world.
+It seems as though the thrown out garbage disappears from our world.
 However, it disappears only from the world of illusions, but still exists in reality.
@@
 \subsection{Garbology}
+Garbology is a study of waste as a social science.
+
 "Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
@@
 %Walter Benjamin's trash aesthetics and Adornos reflection. 
-\quotes{Benjamin’s approach to history is through ‘trash’---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
+\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
 Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
-In the face of the endless proliferation of trash, Benjamin potentially suggests a ‘trash aesthetics’ that could be used radically and critically to attend to the everyday.
-The method might be thought of in terms of ‘recycling’ – an ecology of everyday experience.
+In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday.
+The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%**************************************
 % HERE Same sample phrases are listed you can use them:
@@
 % Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
+
 % Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
@@
 For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.
+(from William Viney)
 

### 2015-10-25 chapter3.tex
reorganization and compilation.
Former-commit-id: f9b8dcf47704fea0ad54949bca9599f5d2407301

@@
 %%
-\subsection{Bricolage}
-Something constructed using whatever was available at the time.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-% TODO reading...
-[TODO read this resource]\cite{strasser1999waste}
-
-%%
-%%
 \subsection{Folk Art}
@@
 
-Some scholars think that the roots of collage is folk art.
-(Find resource.) It's methodologies used in this art.
+Some scholars think that the roots of collage is folk art (ref required).
+It's methodologies used in this art.
 The same exist for craft.
@@
 De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling.
-[TODO ref]
+In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].
 
@@
 % FROM Maite Zubiaurre, ReVista Garbage
-\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
+\item \textbf{Road Kill.} Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
 It is that particular type of trash meet in the public places.
@@
 Filomena Cruz sees trash that we don’t want to see.
-A
-piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
+A piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
+
+% They are continously changing. Unrecognized things. Created unintentionaly. Part of the streets roads. It can be seen as a archieve.
+
   \begin{figure}[ht]
@@
 %\item Pictures of Garbage by Vik Muniz
-\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)
+\item \textbf{Pictures of Garbage.} Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010) Waste Land, directed by Lucy Walker  tracks the development of a series of monumental photographic portraits made from trash.
+Called “Pictures of Garbage,” they were created by Mr.
+Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America.
+(Important point is here collaboration with the pickers.
+Listening their stories and capturing their portraits.
+What is specific about trash here?)
 
-% https://www.youtube.com/watch?v=sJxxdQox7n0
+  \begin{figure}[ht]
+      \centering
+      \includegraphics[width=0.5\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
+      \caption{Pictures of Garbage by Vic Muniz}
+      \label{fig:VicMuniz_PicturesOfGarbage}
+  \end{figure}
+
 \item \textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra”.
@@
     \end{subfigure}
-    \caption{Pictures of animals}\label{fig:animals}
+    \caption{Pictures of instruments}\label{fig:animals}
 \end{figure}
@@
       \centering
-      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
+      \includegraphics[width=0.5\textwidth]{graphics/EloisaCartonera_Books.jpg}
       \caption{Books covered by Eloisa Cartonera}
@@
 
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
-
 %*****************************************
@@
 Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).
+
+%%
+%%
+\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
+\begin{itemize}
+\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
+\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
+\item Try to find a new value and meaning from the discarded material that are useless anymore.
+To explore a new approach, new way.
+Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
+Trash to treasure.
+\item Using discarded item to represent other discarded things by the ruling ideology or approach.
+For example, trash can be used to represent refugees.
+The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
+In other words, refugees have potential but we see them as players that will change our current system.
+Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
+Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
+\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
+\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
+\item Instead of a world that produce trash, how could it be a world created from trash?
+\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
+It also signifies that trash still has a good quality to used with new materials.
+Creating composite products from new and reused items.
+Using the valuable thing with the invaluable thing.
+It becomes more valuable or less valuable.
+Depends on the perception.
+\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
+\end{itemize}
 

### 2015-10-26 chapter2.tex
reorganization
Former-commit-id: c8f73de447b8554d6ab2083ae746442981971ac8

@@
-\chapter{Theory of Trash}
+\chapter{Trash in Theory}
 
@@
 
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
+(WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
 A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
 WALL-E resembles to giant dozers that moves and piles trash in the landfills.
+This robot creates squeezed trash blocks that has no meaning and interpretation.
+All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.)
 
@@
 Changing the context by first rubbishing them.
+
+Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.

### 2015-10-26 chapter3.tex
reorganization
Former-commit-id: c8f73de447b8554d6ab2083ae746442981971ac8

@@
 % TODO praphase
-\textbf{[TODO praphrase]} "The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+[TODO praphrase] \quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
 Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
@@
 A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}
+Schuldt’s famous “Trash People,” which has traveled around the world since 1996}  \cite{tauxe2012encyclopedia}.
 
@@
     \end{subfigure}
-    \caption{Pictures of instruments}\label{fig:animals}
+    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
 \end{figure}

### 2015-11-08 chapter1.tex
reorganization and compilation.
Former-commit-id: f9b8dcf47704fea0ad54949bca9599f5d2407301
reorganization
Former-commit-id: c8f73de447b8554d6ab2083ae746442981971ac8
Comments on structure of thesis.
Former-commit-id: 2c7e98676b898811224687b90240e6cc22125bff

@@
 \chapter{Introduction}
+
+% How to cite epigraph http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
+% Epigraph:
+% FROM Wild Art
+% The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful?
+And very shortly you discover that there is no reason.
+If we can conquer that dislike, or begin to like what we did dislike, then the world is more open.
+That path --- of increasing one's enjoyment of life --- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.
+--- John Cage, quote taken from the televison series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
+
+% FROM http://stanforddailyarchive.com/cgi-bin/stanford?a=d&d=stanford19920130-01.2.5&e=-------en-20--1--txt-txIN-------#
+% The thing to do is to find some way --- and it can be done, I think, through art --- to enjoy life in its vast multiplicity. --- John Cage
+
+% FROM Wild Art
+% Bu epigraphta aslında şöyle bir sıkıntı var, bir şeyin miktarı artınca daha fazla insanın onun üzerinde düşeceğini varsaymak biraz sıkıntı olabilir.
+% We are going to make a lot more junk, and there is going to be a lot more junk art.
+I think people are going to have a lot to say about it, and more people need to think about it.
+--- Jeremy Mayer, quote taken from American Craft Magazine, December/January 2011.
 
@@
 
-The topic and its significance \ldots
+% Konunun dikkat çekici ilginç kısımları: ?
 
+% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir?
+% Meaning of words here. move reuse and recycle here.
+
+% Belki direk bir sanat işiyle girebilirsin.
+Etkileyici olması açısından.
+Hangi iş olabilir?
+Çöpün ne olduğunu ele alan hem de ona karşı bir yaklaşım geliştiren bir örnek belki de benim işine çok benzeyen bir şey olabilir.
+Starbucks bardaklarından bir şeyler yapan insan olabilir.
+
+% Amelie olabilir.
+Orada fotoğraf toplayan çocuk olabilir.
+Onları itinayla toplayan bir adam.
+Tren garındaki fotoğraf kulubesi.
+Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
+Bir birinden farklı bir sürü insan.
+Filmde neden böyle bir eyleme yer veriliyor?
+Film fotoğraflar üzerinden defter üzerinden ilerliyor.
+Onun çevresinden bir hikaye kurgulanıyor.
+İnsanların artıklarını topluyor.
+Bunlar baya baya aslında o insanlar.
+Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
+Çok iyi bir örnek mi bilmiyorum.
+Burada niyet nedir ki?
+Ben buna şöyle bir okuma getireceğim diyebilirim.
+
+% Wall-E belki olabilir.
+Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
+Çöp dağları, çöp denizleri.
+Atılmış binbir türlü nesne.
+ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
+Bundan basetmişken aslında pressleme işi yapan şu cesar.
+Bu şekilde olmak zorunda mı?
+Bunun alternatifi yok mu?
+Aslında bu tezde bunlara cevap bulunabilir.
+Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
+Ya da başka neler var?
+Bunları araştıran inceleyen bir yazı.
+Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
+İnsanlık buna mı dönüşücek?
+Başka bir ihtimal yok mu?
+Gerçekten de dünyayı bekleyen şey bu mu?
+Bir çöp yığını olması mı?
+Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?
+
+% Bu trash in every sıralamasını neden yapıyorum?
+Genel bir çerçeve çizmekten çok aslında evrensel bir konu olduğuna değinmiş oluyorum.
+Peki bu çok açık bir şey mi?
+Yani aslında çok da açık olmayan bilgilerek vererek yaparsam olmayabilir.
+Evrensel olmasının benim için ne önemi var.
+Yaşamımızın bir parçası demek.
+Tamam da buna karşı bir şey mi var.
+Ben göremiyorum açıkcası.
+Herkes bunu biliyor.
+Farkında mıyız.
+Ama farkında olmak istemediğimiz bir şey ki sürekli kendimizden uzaklaştırıyoruz.
+O zaman bu gerçekleri aslında ne kadar biliyoruz.
+Ama bunları bilmek böyle davranmamız gerektiği anlamına mı gelmektedir?
+Aslında yabancı olmadığımız ama uzak durduğumuz bir konu.
+Belki de sırf bu yüzden kaçırdığımız bir sürü şey olabilir.
+Trash in every age.
+In other words it is part of human activity.
+It exists early ages of human to now.
+Trash is part of the early days of human production / or activity.
+Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human.
+Legs, bones etc.
+[TODO etymology reference, see appendix] Archaeologist find things from people throw away.
+
+Trash in every society. Some of them called as trash the others don't. [TODO introduction of revista]
+
+% TODO Life time of objects.
+% Nesnelerin yaşam süreleri, Bu yaşam sürelerinin ne kadar olduğu.
+Burada ilginç bilgiler olabilir.
+Aslında ne kadar çok üretip ne kadar kısa sürede tükettiğimi görüyoruz.
+Ama eskiden ürünler daha uzun sürelerde kullanılıyordı.
+Sonrasında ise bu kısa sürede tüketilen ürünlerden nasıl dağlar oluşuyor.
+Çöpçü kaç günde bir ziyaret ediyor.
+Çöp kutuları ne kadar sürede bir doluyor.
+Çöp kovalarının içlerinde neler var.
+
+% Background information about the thesis. Inspirational points. The fact of trash.
+
+% Firstly as a part of art making.
+Changes in art making?
+// Sanatın köklerine inme abi.
+Sen sanat bağlamında anlatacaksın bunları.
+Zaten ilerisinde değineceğin şeyleri neden şimdi tekrardan anlatıyorsun.
+In the beginning of the 20th century non-art objects enter the scope of art making.
+This is a revolutionary change in the making of art.
+Production of art and the approach to the art changed dramatically.
+This changes actually started at the end of the 19th century with impressionist.
+(But not related with non-art objects.) Picasso is the first artist that used non-art object in his works.
+Later many of them followed him.
+First works are collage and then collage.
+
+% Aga çöpe farklı yaklaşımlar var.
+O yüzden background information olarak burada verilebilir ve scope belirlenebilir.
+Tam da bu noktada ise purpose kısmına geçilebilir.
+Çöpe nasıl yaklaşıyorlar falan filan.
+İşte ben tam da bu noktada sanatta nasıl yaklaşılmıştır dicem.
+Hatta basitçe sanatta bu tür işlere
+
+%%%
+%%%
+%%%
 \section{Purpose of this study}
-The aim of this study is \ldots
 
+% Bu söylemeden önce insana böyle bir şeyin mümkün olduğunu anlatmak gerekli.
+Yani aslında transformation of trash diye bir şey var aga demeli.
+Kimler bunu nasıl yapmış.
+Neler var ortalıkta bunlara bakmak gerekli.
+Pres makineleri falan.
+Ama bunu aynı zamanda sanatsal açıdan inceleyenler, sanatsal amaçlarla yapanlar bulunmakta demek gerekli.
+The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.
+
+%%%
+%%%
+%%% Bu kısım aslında yukarda bahsedilen purposın nasıl yapılacağını anlatacak.
 \section{Overview of Chapters}
-Following chapter focuses on trash in theoretical aspects.
+Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash.
+The aim is (better) to understand the trash in cultural and theoretical aspects.
+(to better realization the notion of trash.)
 
@@
 
-Fourth chapter explains the project that supports this thesis. It's stages, approach to the topic mentioned here.
+Fourth chapter explains the project that supports this thesis. Its stages and approaches to the topic mentioned here.
 
-Finally last chapter offer an overall conclusion of this thesis.
+Finally last chapter offers an overall conclusion of this thesis and project.
 
@@
 Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek.
-Tartışmalar ne üzerine olmalı bu durumda.
+Tartışmalar ne üzerine olmalı bu durumda?
 % The project aims to what? and what needs to justify what it questions? 
@@
 Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir?
-kelime ve imaj arasında bir problme olduğundan bahsediyor.
+kelime ve imaj arasında bir problem olduğundan bahsediyor.
 Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir.
@@
 % Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor.
-iş neyi soruyor ise aslında tez de onu soruyor.
+İş neyi soruyor ise aslında tez de onu soruyor.
 Yapılan işlerle sorulan sorular arasında bir bağlantı var.
@@
 Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli.
+Çöp sanat işlerine girmiştir.
+Çöp dönüştürmek aslında bir artistic acte dönüşüyor.
+Tezde bunu anlatıyor.
+Aga bu artisctic act dediğin şey de ne oluyor.
+Çöp dönüştürmek ne oluyor?
 
-% çöpe yeni bir alternatif yaşam üretmek gerekli.
-Aslında hepimiz bir şeyleri dönüştürüyoruz.
-Agnes varda aslında neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında snatçıları da geziyor, çünkü onlar da topluyorlar.
+% Çöpe yeni bir alternatif yaşam üretmek gerekli! Neden böyle düşünüyorsun? Çünkü sürekli çöp üretiyorsun ama bir yandan da bundan dert yanıyorsun. Zizek işte bu konuya el basıyor.
+
+% Aslında hepimiz bir şeyleri dönüştürüyoruz!
+Neden böyle düşüyorsun?
+Örnekleri nelerdir?
+Bricologe bu iddayı destekler mi?
+Nesnleri üretim amaçlarından farklı amaçlar için kullanmak yeni bir şey değil.
+(Ama zaten ben sanat amacıyla kullanılmasından bahsedeceğim.) Belki bunu belirtmek için mantıklı olabilir.
+Ama burada bir farklılık var olamalı.
+Diğerinden ayıran diyeceğim ama öyle bir fark aramamak gerekli bence.
+Sanat o farkı yıkmak için uğraşıp duruyor.
+Belki de bu uğraşa katkısı bu olabilir bu işin.
+Bir şeyleri dönüştürme potansiyellerimiz olduğunu düşünebiliriz.
+Dönüştürme dediğimiz şey aslında hangi noktada açığa çıkıyor.
+Bir ihtiyaç anında, kaçış anında, ya da yeni alternatifler ararken mi?
+
+% Çöpün dönüştürülmesi ne olaki?
+Buna bir şekilde girişte yer vermek gerekli.
+Çöpün market içindeki hareketi mi?
+Ya da aslında çöpün yaşamı.
+Belki de bu olabilir.
+Çöpün nasıl oluştuğu vs.
+Fabrikada üretilmesi.
+İnsanlara dağıtılması.
+Ve sonra çöp olması.
+Çöp dağları oluşması.
+Çöp kutusunda yer alması.
+Neler yok ki çöp kutusunda.
+Bir sanatçı çöp kovasına attığı sanat işleri.
+Sanat işleri çöplükleri vs.
+Çöp kavramı aslında o kadar çok şey için geçerli ki?
+İşte bu çok çeşitli çöp kavramını ele almak gerekli.
+Yani objeler bir şekilde farklı konumlarda mekanlarda yer değiştiriyorlar.
+Bazen çöp oluyorlar bazen değerli vs.
+
+% Bir bir çeşit çöp var.
+Bunlar binbir çeşit davranış sonucunda oluşuyorlar.
+Bir işlemin sonunda ortaya çıkan son ürün.
+Çöp konumuna gelmesi vs.
+Kime göre çöp neye göre çöp.
+Ama işte ortada bir konsensus yok.
+Başkaları da farklı şekilde görüyor.
+Birine göre çöp diğerine göre ise bir hazine.
+
+% Dönüşmek ne oluyor peki bu durumda.
+Bir durumdan başka bir duruma geçmesi.
+Farklı bir anlam, amaç kazanması olabilir mi?
+Mesela pisuvar dönüşmüş müydü?
+Gazeteyi kolajda kullandığım zaman gazeteyi dönüştürmüş mü oluyorum?
+Hangisi dönüştü?
+Zaten buradaki açık bir şekilde açığa çıkıyor aslında.
+Her ikisi de dönüşmüş oluyor.
+Farklı bir kullanım alanı bulmak.
+Farklı niyetlerle kullanmak olabilir belki de.
+Bir şeyin ne zaman dönüştüğünü iddia edebilirsin.
+
+% Çöpün dönüşmesi diye bir şeyin olduğunu aslında kullanıcıya aktarmak gerekli introductionda.
+
+% Agnes varda neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında sanatçıları da geziyor, çünkü onlar da topluyorlar.
 Onlar da o çöplerde farklı şeyler görüyorlar.
@@
 
-% Çöp ve dönüşüm, dönüşümün aşamaları... Başka sanatçıların methodlarını incelemek pek mantılı değil, onun dışında başka bir şey bulmam gerekli.
+%****************************************
+% JUSTIFICATION (Gerekçesi)
+% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
+% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
+% - Peki neden bu işi yapıyorsun.
+Alternatifi aramak.
+Değer bulmak, değer bulunabilceğine inanmam aslında.
+Belki de değer üretmek için o değerleri yıkmak gerekli.
+Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur.
+Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman.
+O yüzden çöpe atılması önemli.
+Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir.
+Çöplüğün bir başlangıç olması.
+Batırdığımız bitridiğimiz yerden yeni bir başlangıç.
+Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek.
+Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin.
+% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
+% - Çöp bu sanat işlerinde dönüşmüştür. 
+% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
+
+%****************************************
+% ARGUMENTS:
+%
+
+%****************************************
+% SANATTAKİ KÖKLERİ ÜZERİNE:
+% picasso falan gibi adamların derdi sanata farklı objeleri sokarken ki amaçları ya da değerlendirildikleri nokta farklı bir şeyler yapmaları.
+O dönemki anlayışı yıkmaları.
+Onun yerine daha geniş bir alan imkanı sunmaları.
+Biz şu anda onların açtıkları alandan top koşturuyoruz bir nebze.
+Onların buna yaklaşımları ile bizimkiler arasındaki bazı farklılıklar olacak.
+En azından biz onların yıkları şeyi yıktığımız iddia edemeyiz.
+Çünkü o kalıplar, yaklaşımlar açıldı ve yeni bir üretim alanı insanlara sunulmuş oldu.
+Sorulacak yeni sorular, yapılacak yeni tartışmalar vardı.
+% Yani farklı dönemlerde farklı amaçlarla kullanılmıştır.
+Farklı şekillerde okumak mümkündür.
+Ama benim işime yarayanları seçmek gerekli bunları.
+Bir kısmı için bu sanatın diline yeni bir şey sokması, sanatın alanını genişletmesi, yeni tartışma alanları açması şekilde işime yarayacak.
+Diğerleri ise çöpe ele almaları
+
+%****************************************
+% It is a justification of the work. 
+% What is trash? Who does call it trash? 
+% Is it possible to transform it? How? Which methods?
+%

### 2015-11-08 chapter2.tex
Comments on structure of thesis.
Former-commit-id: 2c7e98676b898811224687b90240e6cc22125bff

@@
 % TODO reference for other languages and societies.
+
+% FROM Rubbish! The Archaeology of Garbage, p.9
+A note on terminology.
+Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings.
+\textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on.
+\textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal.
+Refuse is an inclusive term for both the wet discards and the dry.
+Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris.
+The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrevelant, but may see a revival if the idea of composting food and yard waste catches on.
+We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech.
+The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.
 
@@
 
+% Rubbish: The Archeology of Garbage, p.24
+As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
+THe Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
+(example of Medical researches)
+
 %%
@@
 
+% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.
+
+%*******************************************************************
 % FROM The Ruin and the Ruined in the Work of Kurt Schwitters.

### 2015-11-08 main.tex
reorganization and compilation.
Former-commit-id: f9b8dcf47704fea0ad54949bca9599f5d2407301
Comments on structure of thesis.
Former-commit-id: 2c7e98676b898811224687b90240e6cc22125bff

@@
     pdfsubject			= {Trash, Art},
-    pdfkeywords			= {mfa, thesis, trash, art},
+    pdfkeywords			= {mfa thesis, trash, art},
     colorlinks			= false,
@@
 
+\newenvironment{blockquote}{%
+  \par%
+  \medskip
+  \leftskip=4em\rightskip=2em%
+  \noindent\ignorespaces}{%
+  \par\medskip}
+
 \begin{document}
-\title{Thesis Draft}
+\title{Transforming Trash as an Artistic Act}
 \author{Mustafa İlhan}
@@
 % Title Ideas for Thesis 
-% - Trash as an Artistic Medium.
+% - Trash as an Artistic Medium
 % - Trash Notebooks: Trash in the Context of Art
 % - Trash Notebooks: Exploring the potential of trash through art practice
+% - Notebooks from trash.
+% - Transforming Trash as an Artistic Act
 %****************************************
@@
 % Abstract ideas
-% You can add shortly definition of trash and discard. Any object can be art in 19th century.
+% You can add short definition of trash. Any object can be art in 20th century. Society generated trash and a culture that do not reuse and throws away.
 % Structure of this thesis: written part of it and the project support each other.
@@
 
+%****************************************
+% Structure of abstract
+% What is this study?
+% What is questioned/examined/investigated?
+% How is it investigated?
+% What is the outcome?
+
 \begin{abstract}
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched).
+In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
 Why and how are they used by the artist?
 Are there any differences with the original items compared to discarded items?
-(In other words has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
+Has using discarded material or trash specific (or special) meaning and message?
+This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
 (and also in which scope?
@@
 
+% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir.
+
 Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects how one's lives and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose do not build a thing that is produced from discarded material to watch it from a distance.
+The process effects one's life and lifestyle.
+(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
 The important thing is to interact with it.
@@
 It must call the viewer to interact with it.
-(not only watch.)
+
+% Ersan hoca uzak seyretmek yerine etkileşime geçilmesini auranın kırılması olarak bakıyor.
+Performatif olması veya bir act olması zaten bunu kıran bir şey olabilir.
+Sanatsal eylem, performans kavramlarını araştırmak gerekli.
+Uzaktan seyredip hayranlık duymak yerine ilişkiye geçilen bir hale getirmek çöpü.
+Amaç bu aslında.
+Çöpü tekrar tanımak, onunla barışmak, onunla yaşamak.
+İşte bu yüzden bir eylem olabilir.
+Ya da yaşam pratiği.
 
@@
 
-With the help of art discarded things can be find a place in the society.
+With the help of art discarded things can find a place in the society.
 (By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.
 
-From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
+Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
 Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
@@
 Stages and expression of this practice is examined with my artwork in the context of art.
+
+% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.
 
@@
 
-With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.
+With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods.
 
@@
 
-Junk(or trash) can be seen as a resource that is fertile to new meanings, creations and aesthetics.
+Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
 Ignored and discarded nature of garbage when rethought becomes fertile resource.
-Trash as a resource (as a artistic material.)
+Trash as a resource (as an artistic material).
 
-\vfill\noindent\textbf{\textit{Keywords:}} trash(discarded objects), art, value creation, transformation.
+% Ne, Nasıl, Sonuç.
+
+% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir.
+Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
+Hem sanatın dili genişledi hem de objelerin sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı.
+Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır.
+Çöpü daha iyi anlayabilmek için throw away.
+Çöpün nasıl sanatta yer bulduğu incelenmiştir.
+ve aynı zamanda aslında çöpün ne olduğu sorgulanmıştır.
+The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act.
+
+% Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
+% Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır. 
+% Projeyle şunu sorgulanmıştır.
+
+\vfill\noindent\textbf{Keywords:} Trash, Art, Transformation.
 \end{abstract}
@@
 
+% ON THE RELATIONSHIP BETWEEN IMAGES AND WORDS AND THEIR RELATION TO BODY AND PERCEPTION
+% Prehistoric man created a mark and throughout the history this mark evolved and bifurcated into two: a word and an image. While images were cherished, words were set apart from images. 
+% This thesis attempts to look at the relationship between images and words through seeking their connection to perception and body.
+It investigates how image-word dichotomy occurred and how this dichotomy obscured the connection between writing and body.
+The thesis also examines different approaches to overcome this phenomenon in the context of Modern Art.
+% By examining my artwork within this framework, it argues that it is possible to embody the inseparable relationship between images and words through reconnecting with the body’s primordial existence.
+
+% ALTERNATIVE PHOTOGRAPHY IN THE DIGITAL AGE: PERFECT PHOTOGRAPHS IN AN IMPERFECT WAY
+% This thesis explores the possibility of an alternative future of photography from the union of digital and chemical domains of the photographic medium.
+The historical photographic processes known as Cyanotype, Salt print and Vandyke Brown are employed for this project in conjunction with the modern inkjet printer produced digital negatives.
+% As being highly sensitive to the variables during the process, each alternative photographic print exhibits a visual uniqueness.
+In this aspect, there is conceptual correlation with the visual uniqueness of alternative photographic processes and the visual uniqueness of albinism.
+Emphasizing the human element in subject, vision and craft of making photographs, this project aims to produce unique photographs of a visually unique subject.
+
 \pagenumbering{arabic}

### 2015-11-09 appendix_glossary.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

--- 2015-10-25 chapter2.tex
@@
-\chapter{Theory of Trash}
-
-% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych
-\epigraph{\textit{\quotes{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}}}{\hfill --- Priscilla Uppal}
-
-In this chapter trash (and the practice of transforming trash) is examined in theoretical (and conceptual) aspect.
-Theoretical foundations of trash are discussed.
-(Further benefited from historical and social aspect of trash.
-(?)) How do scholars conceptualized the trash?
-What do they say about it?
-
-Trash draws attention of many scholars and people who are professional in different areas.
-Further trash is a common topic(problem?) of the all ages through the human history.
-In other words this topic is not introduced in recent years (or ages).
-It always part of the human practice and life.
-Even if trash is refused and discarded thing, there are people giving attention to them.
-
-%%%
-%%%
-%%%
-\section{Etymology/Terminology}
-(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
-Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
-It is important to understand diverse vocabulary of this topic before dive into the theory.
-It is very important to choose right terminology, because ...
-and also make more clearer the borders of the work.
-There is no agreed (or specific) terminology.
-Some scholars uses junk art, others recycling art.
-Sometimes this make difficult to research on this topic.
-And also I must point out that this topic is not limited with the English language.
-The topic is broad and it is not limited with english literature and vocabulary (ref required).
-% TODO reference for other languages and societies.
-
-%%
-%%
-\subsection{Origins of Vocabulary}
-The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
-What were people throwing out when these words were coined?
+\appendix
+\chapter{Glossary}
 
@@
 \end{itemize}
-
-% TODO other words, relation, comparison etc.
-
-%%
-%%
-\subsection{Reuse and Recycle}
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).
-
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-%%%
-%%%
-%%%
-\section{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
-% TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
-Literature is recycled material, a pretext for making more art.
-I learned this distillation of lots of literary criticism in workshops with children.
-I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
-For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
-%%
-%%
-\subsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
-
-% Like a summary sentence
-Here the important thing is moving nature of trash.
-Objects moves and gains different meanings through this movement.
-Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
-It also signifies that it is relative and result of a classification issue.
-All of them are creates a harmony.
-supports each other with different words and conceptualization.
-
-% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
-Object moves and also trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
-
-Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
-% >
-
-%%
-%%
-\subsection{Perspectives related with trash from different disciplines}
-This is very important because the problem of trash is being tried to be handled by different disciplines.
-In other words there different approaches to the trash.
-Different problems, different solutions.
-Which perspective that I have.
-In what ways my project differs from them.
-The purpose is to participate people in this work, by collecting them etc.
-And also offer to transform it.
-Rescue it and than later transform it.
-In short, the difference between the other disciplines must be clear.
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it (handled by the municipals generally).
-\item Technological perspectives.
-(seeing trash as a design problem.
-developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-development in what sense?)
-\end{itemize}
-
-% Sample sentence:
-% Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
-In other word the problem is our technology which is not perfect.
-(and I'm not sure that at some point that technology will reach to the perfection or not.)
-
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
-\quotes{What is happening to trash is what is going to happen to us.
-We’re all going to end up in a dump, and we’re going to decompose.
-That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-\quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-
-%%
-%%
-\subsection{Throw away culture}
-Continuously consuming things and disposing of something.
-It is an important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
-(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
-
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
-
-%%% Reference from Identity, mobility and the throwaway society
-we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)
-
-\quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
-In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
-Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
-The thesis, however, lacks depth and provenance.
-It is, actually, glib.
-Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
-% In this paper criticized the perception of throw away culture and arguments. They show the weak points of the arguments. What I understand from trow away culture?
-
-In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this.
-Always needed to keep in my mind that the practice of discard does not exist on only current societies.
-
-%%
-%%
-\subsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
-
-%%
-%%
-\subsection{Types and Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-
-Different production process generates different types of trash. According to production process, decomposition process\ldots
-
-The approach to the different type of trash will be different.
-In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
-There are some trashes that are more close to the people.
-More easy to convert them.
-more easy to regain to the society.
-
-%%
-%%
-\subsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
-There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
-Even if they are excluded, there is also life for them.
-
-% TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
-
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
-
-[TODO: ragpickers from benjamin and archades project.]
-
-%%%
-%%%
-%%%
-\section{Rubbish Theory}
-Objects have a lifetime and they don't remain same through that lifetime.
-Their value, usage, location change over time.
-During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
-Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
-Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
-This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
-The theory looks at how some of these objects then regain value, such as antiques or historic homes.
-It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
-The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.
-
-Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
-Thompson label some transitions as possible and the others as impossible.
-"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
-Further, he does not allow move from transient to durable.
-However, Duchamp's fountain breaks this rule.
-Because urine used as a fountain is still functional and have a place in the market.
-In another word, it is not rubbish.
-This urine with the approach of Duchamp turned to be an artwork.
-It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
-
-In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
-(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
-transforming them creates new a value system?
-or just finding place existing value system.
-by the way there is a value theory related with (or inside of) game theory.)
-
-Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
-
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
-
-The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
-It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
-Finally the theory suggests that value emerges through our ways of seeing and placing objects.
-(From Liz Parsons)
-
-%%
-%%
-\subsection{Rubbish Theory in Practice}
-% TODO PRAP. REF.
-(Summary From Liz Parsons.)
-
-A key critique of the rubbish theory is its neglect of the practices of value creation.
-Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
-
-Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
-Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
-McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
-He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
-He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
-These rituals include those of possession, exchange, grooming and divestment.
-The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
-However he is not clear as to the practices which constitute these rituals.
-In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
-There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
-
-In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
-Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
-He focuses on the ‘commodity potential’ of things.
-‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
-However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
-This is where Thompson’s Rubbish Theory comes in.
-
-\subsubsection{Transients, Rubbish and Durables}
-The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
-The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
-Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
-Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
-He further observes that their category membership determines the way we act towards them.
-
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-
-Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
-(Further there is similar analogy at Waste and Want.
-The author give the example of shoe and claim that thrash is relative.
-The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
-Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
-
-\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
-disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
-
-\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
-Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
-It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
-
-\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
-Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
-Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
-The find may not involve objects which are new to us, it is possible to find some of ones own items if they have been hidden away long enough in an attic and thus made strange to us.
-The concept of the find also suggests that the found object has some qualities that others (or indeed ourselves) have in the past overlooked, as such it is closely related to ‘bringing to light’.
-The find may be extended to embrace features of objects as well as objects themselves.
-This directs us to their ‘potentialities’, objects may have been there all along but we’ve suddenly found them to be useful, likeable or beautiful.
-It might be that some aspect of them has simply been brought to our attention.
-Equally, as discussed below in relation to transforming objects, we may make alterations to objects which bring out their potential.
-The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
-
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
-
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
-Transformations may also involve the modification or updating of objects through painting, alteration or repair.
-Transformations may not only be based around creating new uses but also creating new looks.
-The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
-
-%%
-%%
-\subsection{Theoretical Analysis of Found Object}
-(Summary From Paul M Camic.)
-
-% TODO PRAP. REF.
-\subsubsection{Seeking Objects}
-As a species Homo sapiens has been gathering and collecting objects for thousands of years.
-Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
-The search for “things,” collecting them (Humphrey, 1979), and the need to embellish and make the ordinary special (Dissanayake, 1988) have been essential parts of the evolutionary process of human development (Bettinger, 1991; Dissanayake, 1992).
-For example, many early cave drawings occur around a natural feature within the cave such as a projection or indentation (Bahn, 1998; Lewis-Williams, 2004), making these natural features potentially comparable to found objects in modern and contemporary art (Read, 1930).
-When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
-Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
-
-In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
-Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
-Although most of these objects are purchased new in shops or online, many others are preused items, castoffs, or trash found in back alleys and country lanes, dumpsters, and rubbish bins or purchased cheaply in flea markets, garage and boot sales, and in shops catering in previously owned goods.
-Some individuals have chosen to salvage objects out of economic necessity, as depicted in Jean-Francois Millet’s 1857 painting The Gleaners and by Agne`s Verga’s 2002 documentary film Les Glaneurs et la glaneuse, whereas others have done it for a range of other reasons, including a desire to rescue them (Belk, Wallendorf, \& Sherry, 1989).
-These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
-A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots
-
-% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
-
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
-
-\subsubsection{Found Objects in Art}
-The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
-
-How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
-
-\textbf{Motivations and found object practice:}
-\begin{itemize}
-\item Discovery and engagement
-  \begin{itemize}
-  \item Seeking out: The adventure of hunting
-  \item Finding the unexpected
-  \item The location of discovery
-  \item Metamorphosis and transformation: Imagining a use for the object
-  \item Creative action
-  \end{itemize}
-\item History and time past
-  \begin{itemize}
-  \item Trigger of personal memories
-  \item The object’s story: Reflection about earlier “life” of object and previous owner
-  \item Capturing something elusive: Making sense of an unknown past
-  \end{itemize}
-\item The symbolic and functional object
-  \begin{itemize}
-  \item Aesthetic properties: Visual, tactile, original
-  \item Cost: The thrill of a free find
-  \item Evocative: More interesting than something new
-  \item Useable solutions for practical problems
-  \end{itemize}
-\item Psychological processes
-  \begin{itemize}
-  \item Personal resourcefulness
-  \item Impact on memory, emotion, cognition
-  \item Meaningfulness of object
-  \item Arouses interest: Motivates
-  \item Social engagement
-  \end{itemize}
-\item Ecological affirmation
-  \begin{itemize}
-  \item Environmental concerns
-  \item Against the cult of the new: Slowing down consumption
-  \item Transforming rubbish
-  \end{itemize}
-\end{itemize}
-
-The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
-The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
-When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
-Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
-This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
-
-An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
-Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
-
-Results of this study also support consideration of found objects as important artifacts that are signifiers of cultural meaning.
-
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials. So what is value?]
-\textbf{Value.}
-\begin{itemize}
-\item n. relative worth, merit, or importance: the value of a college education; the value of a queen in chess.
-\item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
-\item n. estimated or assigned worth; valuation: a painting with a current value of \$500,000.
-\item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books.
-Worth implies especially spiritual qualities of mind and character, or moral excellence: Few knew her true worth.
-\item the desirability of a thing, often in respect of some property such as usefulness or exchangeability; worth, merit, or importance
-\end{itemize}
-
-%%%
-%%%
-%%%
-\section{Bricolage}
-Dictionary meaning; something constructed using whatever was available at the time.
-
-% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;
-
-% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime.
-bunu yapan kişiye de bricoleur deniyormuş.
-lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş.
-kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
-
-\begin{blockquote}
-[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
-His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
-\end{blockquote}
-
-\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.
-
-\begin{blockquote}
-The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
-There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-\end{blockquote}
-
-\begin{blockquote}
-The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
-In this sense the engineer is a myth.
-A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
-The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-\end{blockquote}
-
-% TODO reading...
-[TODO use this ref]\cite{strasser1999waste}
-
-Bricolage is different than collage.
-Bricolage > collage.
-Because it is more general understanding of human practice.
-Collage is just only gluing paper together and it can be only a subset of bricolage.
-Same applicable for assemblage.
-Transforming trash can be examined within bricolage.
-
-%%%
-%%%
-%%%
-\section{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic.
-Show the problematic understanding thought to the garbage.
-Suggest another thing, and point out the need for the new approach.
-Beyond the ecological problem there are different sides of it.
-Different readings can be added to the topic.
-Adding spirituality and new aesthetics dimension to the topic.
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
-
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
-
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
-
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
-
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%
-%%
-\subsection{Garbology}
-Garbology is a study of waste as a social science.
-
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
-
-%%
-%%
-\subsection{Trash as History/Memory}
-% TODO From encylopedia
-\cite{bullock2012trash}
-
-%%
-%%
-\subsection{Trash Aesthetics}
-%Walter Benjamin's trash aesthetics and Adornos reflection. 
-\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
-Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
-In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday.
-The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.
-
-%**************************************
-% HERE Same sample phrases are listed you can use them:
-
-% The work that follows is divided into three sections
-
-% The artist thinks, acts, performs music, and writes outside the framework that society has created.
-
-% this thesis takes a rather different approach to the resonant possibilities of discarded things.
-It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
-
-% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
-
-% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
-
-% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
-
-% FROM The Ruin and the Ruined in the Work of Kurt Schwitters.
-% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality
-
-\subsection{Discussions}
-Objects moves around and their values change constantly.
-(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
-The Social Life of Things: Commodities in Cultural Perspective)
-
-Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)
-
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
-This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trashcan in the form of waste.
-In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
-
-Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”
-
-% Prap. same source...
-% On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” 9 Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
-The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
-10 Waste now became evil.
-If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
-11 Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” 12 Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
-Upcycling...
-On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
-Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
-16 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
-In short, there is a whole sector of upcycling now.
-
-% Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
-People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
-
-% There is commodity aspect of it and also the process of accommodation.
-In this process design plays a significant role.
-Trash is waiting to be discovered.
-At the same time forgotten styles are also used in works.
-Therefore actually trash and forgotten styles can be considered in the same status.
-
-% This can be sample thesis statement sentence:
-% This article is about those objects that are recreated from trash through the process of upcycling.
-Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” 4 I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of.
-
-% From The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
-
-% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
-\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
-As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
-
-% FROM Waste by William Viney
-Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
-(Think that the transformation process.
-Previous argument support that the transformation of trash is possible by changing the place of them.
-In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
-For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.
-(from William Viney)
-
-% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
-Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.
-
-%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.
-
-% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.
-
-% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
-Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
-Remember the example given: shoes  on the dinner table.
-
-% King Lear, feeling of waste
-
-% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.
-
-% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
-
-% https://narratingwaste.wordpress.com/tag/king-lear/
-% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.
-
-% Binding things together and separating things from each other.
-
-% Cornelia Parker's work, narrate an absent event of waste
-% There is also strong relationship with the collecting discarded stuff and archeologies of waste.
-
-%%% Reference
-% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
-% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
-In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
-Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
-The thesis, however, lacks depth and provenance.
-It is, actually, glib.
-Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.
-
-%%%
-%%%
-%%%
-\section{Summary}
-\begin{itemize}
-\item Shared practice through the different ages of humanity and different societies. 
-\item Moving nature of trash/objects.
-\item Classification is the main key, trash is not related with the object property. 
-\item Value creation, shifts in the society. 
-\item Trash has archaeological value.
-\item Trash has potential to be used again.
-\end{itemize}
-
-Thompson thinks that the switch only occurs from losing all the value given the object.
-He refers that to gain new value previous systems ruins must be cleaned.
-Changing the context by first rubbishing them.

### 2015-11-09 chapter1.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

@@
 \chapter{Introduction}
-
-% How to cite epigraph http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
-% Epigraph:
-% FROM Wild Art
-% The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful?
-And very shortly you discover that there is no reason.
-If we can conquer that dislike, or begin to like what we did dislike, then the world is more open.
-That path --- of increasing one's enjoyment of life --- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.
---- John Cage, quote taken from the televison series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
-
-% FROM http://stanforddailyarchive.com/cgi-bin/stanford?a=d&d=stanford19920130-01.2.5&e=-------en-20--1--txt-txIN-------#
-% The thing to do is to find some way --- and it can be done, I think, through art --- to enjoy life in its vast multiplicity. --- John Cage
-
-% FROM Wild Art
-% Bu epigraphta aslında şöyle bir sıkıntı var, bir şeyin miktarı artınca daha fazla insanın onun üzerinde düşeceğini varsaymak biraz sıkıntı olabilir.
-% We are going to make a lot more junk, and there is going to be a lot more junk art.
-I think people are going to have a lot to say about it, and more people need to think about it.
---- Jeremy Mayer, quote taken from American Craft Magazine, December/January 2011.
 
@@
 
-% Konunun dikkat çekici ilginç kısımları: ?
+% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time. Changes through the time.
+% Konu hakkındaki temel bilgiler.
+% Konunun ele alınan kısmı.
+%
 
@@
 
+WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
+A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
+WALL-E resembles to giant dozers that moves and piles trash in the landfills.
+This robot creates squeezed trash blocks that has no meaning and interpretation.
+All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
+
 % Bu trash in every sıralamasını neden yapıyorum?
@@
 Belki de sırf bu yüzden kaçırdığımız bir sürü şey olabilir.
+
 Trash in every age.
@@
 
-Trash in every society. Some of them called as trash the others don't. [TODO introduction of revista]
+Trash in every society. Some of them called as trash the others don't.  
+% TODO look introduction of revista, there is a related reference above it.
+
+Trash is everywhere.
+% Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.
+
+% Gene aslında sürekli tükettiği şeylerin fotoğrafını çken sanatçı.
+
+% Intoductionua bir sanatçı fikriyle girip konuyu oradan açabilirim. Bir hikayesi yaklaşımı olabilir.
 
@@
 %%%
-\section{Purpose of this study}
+\section{Purpose of the Study}
 
@@
 %%%
-%%% Bu kısım aslında yukarda bahsedilen purposın nasıl yapılacağını anlatacak.
+%%% 
+% Bu kısım aslında yukarda bahsedilen amacın nasıl yapılacağını anlatacak.
 \section{Overview of Chapters}
@@
 % What is my thesis statement? Again same topic... It needs to be solved...
+%........................................
 
@@
 Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.
+%........................................
 
@@
 % as a reaction to the consumerist society.
+%........................................
 
@@
 % 
+%........................................
 
@@
 Diğerleri ise çöpe ele almaları
+%........................................
 
@@
 % Is it possible to transform it? How? Which methods?
-%
+%........................................
+
+%%%
+%%%
+%%%
+\section{A Note on Terminology}
+(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
+Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
+It is important to understand diverse vocabulary of this topic before dive into the theory.
+It is very important to choose right terminology, because ...
+and also make more clearer the borders of the work.
+There is no agreed (or specific) terminology.
+Some scholars uses junk art, others recycling art.
+Sometimes this make difficult to research on this topic.
+And also I must point out that this topic is not limited with the English language.
+The topic is broad and it is not limited with English literature and vocabulary (ref required).
+
+% FROM Rubbish! The Archaeology of Garbage, p.9
+Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings.
+\textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on.
+\textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal.
+Refuse is an inclusive term for both the wet discards and the dry.
+Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris.
+The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrevelant, but may see a revival if the idea of composting food and yard waste catches on.
+We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech.
+The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.
+
+The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
+What were people throwing out when these words were coined?
+
+%****************************************
+% Reuse and Recycle
+One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).
+
+According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+If any item is used again and again over time, it is said to be reused.
+The main purpose of reusing is to lengthen the life of the item or material.
+We give out used clothes for charity which results in reusing.
+Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
+The main purpose is to make the item last as long as it can.
+To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
+Why throw something away when you can give it another life?
+Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
+Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
+For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
+
+According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
+It is an energy consuming process.
+For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
+In this process, energy is required which depends upon the stages of transformation.
+
+Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
+Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
+
+Reusing is possible with re seeing (rethinking).
+Reusing is possible meet the needs of the human itself.
+Using creativity and personal approach can change objects functions.
+It is possible to use objects for different purposes.
+
+Recycling can be viewed as down-cycling.
+The object smashed to the small particles to be used later in the production of something else.
+Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
+Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
+
+Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
+
+Many scholar used the word recycling when mentioning works use trash and the concept of it.
+However they are not mentioning the meaning that is decomposing things to the their particles.
+What they is actually is reusing and combining things, concepts, creating new mixtures.

### 2015-11-09 chapter2.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

--- 2015-10-25 chapter2.tex
@@
-\chapter{Theory of Trash}
+\chapter{Trash in Culture and Theory}
 
 % FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych
-\epigraph{\textit{\quotes{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}}}{\hfill --- Priscilla Uppal}
+% http://priscilauppal.ca/books/alphabet-city/
+\epigraph{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
 
@@
 %%%
-\section{Etymology/Terminology}
-(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
-Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
-It is important to understand diverse vocabulary of this topic before dive into the theory.
-It is very important to choose right terminology, because ...
-and also make more clearer the borders of the work.
-There is no agreed (or specific) terminology.
-Some scholars uses junk art, others recycling art.
-Sometimes this make difficult to research on this topic.
-And also I must point out that this topic is not limited with the English language.
-The topic is broad and it is not limited with english literature and vocabulary (ref required).
-% TODO reference for other languages and societies.
-
-%%
-%%
-\subsection{Origins of Vocabulary}
-The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
-What were people throwing out when these words were coined?
-
-%From http://dictionary.reference.com/, http://www.etymonline.com/
-\textbf{Waste.}
-\begin{itemize}
-\item v. to consume, spend, or employ uselessly or without adequate return; use to no avail or profit; squander:to waste money; to waste words.
-\item v. to fail or neglect to use: to waste an opportunity.
-\item n. An unusable or unwanted substance or material, such as a waste product. See also hazardous waste, landfill. 
-\item Waste comes from the Latin vastus, meaning empty, desolate, desert, or wilderness, and it’s interesting how the Romans called desert any wilderness that wasn’t settled, including forests.
-German has retained the original meaning in wüste (desert).
-Vastus, which also gave us vast, vain, and devastate, came to mean a waste of money and ultimately garbage.
-It is tempting to see a relation with the word west – the ancients didn’t like the west, where the sun “dies”, and associated the west side with death (the Egyptian tombs and pyramids are always on the west bank of the Nile, for instance)\cite{paul2013garbage}.
-\item Antonyms: save
-\end{itemize}
-
-\textbf{Trash.}
-\begin{itemize}
-\item n. anything worthless, useless, or discarded; rubbish.
-\item n. foolish or pointless ideas, talk, or writing; nonsense.
-\item n. literary or artistic material of poor or inferior quality. a literary or artistic production of poor quality.
-\item Garbage collector.
-\end{itemize}
-
-\textbf{Garbage.}
-\begin{itemize}
-\item n. discarded animal and vegetable matter, as from a kitchen; refuse.
-\item n. any matter that is no longer wanted or needed; trash.
-\item Synonyms: litter, refuse, junk, rubbish.
-\item Origin.
-early 15c., "giblets of a fowl, waste parts of an animal," later confused with garble in its sense of "siftings, refuse." Perhaps some senses derive from Old French garbe "a bundle of sheaves, entrails," from Proto-Germanic *garba- (cf.
-Dutch garf, German garbe "sheaf"), from PIE *ghrebh- "a handful, a grasp." Sense of "refuse, filth" is first attested 1580s; used figuratively for "worthless stuff" from 1590s.
-(Garbage is giblets, refuse of a fowl, waste parts of an animal (head, feet, etc.) used for human food.
-In modern American usage, garbage is generally restricted to mean kitchen and vegetable wastes.)
-\end{itemize}
-
-\textbf{Rubbish.}
-\begin{itemize}
-\item n. worthless, unwanted material that is rejected or thrown out; debris; litter; trash.
-\item n. nonsense, as in writing or art.
-\end{itemize}
-
-\textbf{Junk.}
-\begin{itemize}
-\item n. any old or discarded material, as metal, paper, or rags.
-\item n. anything that is regarded as worthless, meaningless, or contemptible; trash.
-\item v. to cast aside as junk; discard as no longer of use; scrap.
-\item adj. cheap, worthless, unwanted, or trashy.
-\end{itemize}
-
-\textbf{Refuse.}
-\begin{itemize}
-\item n. something that is discarded as worthless or useless; rubbish; trash; garbage.
-\item Antonyms: accept, welcome.
-\end{itemize}
-
-% TODO other words, relation, comparison etc.
-
-%%
-%%
-\subsection{Reuse and Recycle}
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).
-
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
-The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
-
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
-For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
-
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
-
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
-
-Recycling can be viewed as down-cycling.
-The object smashed to the small particles to be used later in the production of something else.
-Although reuse can be viewed as up-cycling that gives another (or more) value to the discarded products.
-Down-cycling does not generates new meanings it tries to convert the product to already known state to process.
-
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
-Many scholar used the word recycling when mentioning works uses trash and the concept of it.
-However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
-
-%%%
-%%%
-%%%
-\section{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
-% TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
-Literature is recycled material, a pretext for making more art.
-I learned this distillation of lots of literary criticism in workshops with children.
-I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
-For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
-
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
-%%
-%%
-\subsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
-
-% Like a summary sentence
-Here the important thing is moving nature of trash.
-Objects moves and gains different meanings through this movement.
-Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
-It also signifies that it is relative and result of a classification issue.
-All of them are creates a harmony.
-supports each other with different words and conceptualization.
-
-% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
-Object moves and also trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
-
-Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
-% >
-
-%%
-%%
-\subsection{Perspectives related with trash from different disciplines}
-This is very important because the problem of trash is being tried to be handled by different disciplines.
-In other words there different approaches to the trash.
-Different problems, different solutions.
-Which perspective that I have.
-In what ways my project differs from them.
-The purpose is to participate people in this work, by collecting them etc.
-And also offer to transform it.
-Rescue it and than later transform it.
-In short, the difference between the other disciplines must be clear.
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it (handled by the municipals generally).
-\item Technological perspectives.
-(seeing trash as a design problem.
-developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-development in what sense?)
-\end{itemize}
-
-% Sample sentence:
-% Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
-In other word the problem is our technology which is not perfect.
-(and I'm not sure that at some point that technology will reach to the perfection or not.)
-
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
-\quotes{What is happening to trash is what is going to happen to us.
-We’re all going to end up in a dump, and we’re going to decompose.
-That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-\quotes{Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-
-%%
-%%
-\subsection{Throw away culture}
+\section{Throw away culture}
 Continuously consuming things and disposing of something.
@@
 
-%%
-%%
-\subsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
+% Resource is here: mmmacleo2005.pdf (throw away culture ile ilgili.) (Çünkü ben bunun ürününü kullanıyorum.)
 
-%%
-%%
-\subsection{Types and Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
+%%%
+%%%
+%%%
+% FROM Examined Life
+\section{Zizek on Garbage}
+(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
+In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
+He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
+Draw attention to notion of even if trash disappears from our world but not world.
+It seems as though the thrown out garbage disappears from our world.
+However, it disappears only from the world of illusions, but still exists in reality.
+He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
+He claims that it is ideological in the sense that wrong thinking important problems.
+Nature contains unimaginable catastrophes.
+think oil and distinct animals and plants.
+we profit balance part of the nature but it is created from catastrophe.
+Are we aware of this catastrophe.
+He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
+It would be too much." its voice is like "Don't mess with D.N.A.
+Don't mess with nature.
+Don't do it" etc.
+We should not forget that we are part of the ecology.
+We must more alienated from the nature.
+We must find poetry and spirituality in the dimension of trash.
+That's the true love of world.
+Love is not about idealization.
+This part will be extended later.)
 
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
+\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
+Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
+Such interpretation makes life easier.
+However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
+Nature is a series of unthinkable disasters.
+Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
+Do not touch DNA!
+Do not develop new medicines!
+Do not invent new technologies!” How one should react to these reproaches?
+Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
 
-Different production process generates different types of trash. According to production process, decomposition process\ldots
+His basic argument is that the modern eco movement is a conservative ideology.
+It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
+Basically he says the eco movement has it's head in the clouds.
+If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
 
-The approach to the different type of trash will be different.
-In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
-There are some trashes that are more close to the people.
-More easy to convert them.
-more easy to regain to the society.
+\begin{itemize}
+\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
+\item Ideology addresses real problems but mystifies them.
+\item We search for meaning when a horrible event happens to make it easier to accept.
+\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
+\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
+\item Ecology is becoming more like religion with dogmas.
+\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
+\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
+\item Learn to love our trash as a part of ecology.
+\end{itemize}
 
-%%
-%%
-\subsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
+How much harmonious all these produced materials with nature?
+How many animals and the plant can use these discarded items?
+(Because of complex production methods their recycling requires complex processes again.
+Some of them already produced to protect goods from natural factors (like decaying etc.).
+However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
+However, some artists turned to trash into site-specific sculptures that are more than trash heap.
+not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
+(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
+The more likely idea will be we will live harmoniously with what we create.
 
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
-There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
-Even if they are excluded, there is also life for them.
+Getting rid of it is not the significant action.
+It still waits us at somewhere else or the next generations have to cope with it.
+(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
+To break out of this eternal cycle of functioning.
 
-% TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
+The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
+and what are the other dimensions?)
 
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
+Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
 
-[TODO: ragpickers from benjamin and archades project.]
+Trash of developed societies has higher decomposing period in the nature.
+Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
+
+\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic.
+Show the problematic understanding thought to the garbage.
+Suggest another thing, and point out the need for the new approach.
+Beyond the ecological problem there are different sides of it.
+Different readings can be added to the topic.
+Adding spirituality and new aesthetics dimension to the topic.
 
@@
 %%%
-\section{Bricolage}
-Dictionary meaning; something constructed using whatever was available at the time.
-
-% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;
-
-% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime.
-bunu yapan kişiye de bricoleur deniyormuş.
-lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş.
-kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
-
-\begin{blockquote}
-[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
-His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
-\end{blockquote}
-
-\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.
-
-\begin{blockquote}
-The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
-There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-\end{blockquote}
-
-\begin{blockquote}
-The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
-In this sense the engineer is a myth.
-A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
-The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-\end{blockquote}
-
-% TODO reading...
-[TODO use this ref]\cite{strasser1999waste}
-
-Bricolage is different than collage.
-Bricolage > collage.
-Because it is more general understanding of human practice.
-Collage is just only gluing paper together and it can be only a subset of bricolage.
-Same applicable for assemblage.
-Transforming trash can be examined within bricolage.
-
-%%%
-%%%
-%%%
-\section{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Examined-life, Zizek}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-This part will be extended later.)
-
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
-
-His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
-
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
-
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
-
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
-
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
-
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
-
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic.
-Show the problematic understanding thought to the garbage.
-Suggest another thing, and point out the need for the new approach.
-Beyond the ecological problem there are different sides of it.
-Different readings can be added to the topic.
-Adding spirituality and new aesthetics dimension to the topic.
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
-
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
-
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
-
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
-
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
-
-%%
-%%
-\subsection{Garbology}
-Garbology is a study of waste as a social science.
-
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
-
-%%
-%%
-\subsection{Trash as History/Memory}
-% TODO From encylopedia
-\cite{bullock2012trash}
-
-%%
-%%
-\subsection{Trash Aesthetics}
-%Walter Benjamin's trash aesthetics and Adornos reflection. 
-\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
-Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
-In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday.
-The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.
-
-%**************************************
-% HERE Same sample phrases are listed you can use them:
-
-% The work that follows is divided into three sections
-
-% The artist thinks, acts, performs music, and writes outside the framework that society has created.
-
-% this thesis takes a rather different approach to the resonant possibilities of discarded things.
-It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
-
-% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
-
-% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
-
-% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
-
-% FROM The Ruin and the Ruined in the Work of Kurt Schwitters.
-% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality
-
-\subsection{Discussions}
-Objects moves around and their values change constantly.
-(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
-The Social Life of Things: Commodities in Cultural Perspective)
-
-Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)
-
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
-This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trashcan in the form of waste.
-In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
-
-Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”
-
-% Prap. same source...
-% On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” 9 Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
-The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
-10 Waste now became evil.
-If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
-11 Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” 12 Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
-Upcycling...
-On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
-Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
-16 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
-In short, there is a whole sector of upcycling now.
-
-% Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
-People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
-
-% There is commodity aspect of it and also the process of accommodation.
-In this process design plays a significant role.
-Trash is waiting to be discovered.
-At the same time forgotten styles are also used in works.
-Therefore actually trash and forgotten styles can be considered in the same status.
-
-% This can be sample thesis statement sentence:
-% This article is about those objects that are recreated from trash through the process of upcycling.
-Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” 4 I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of.
-
-% From The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
-
-% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
-\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
-As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
-
-% FROM Waste by William Viney
-Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
-(Think that the transformation process.
-Previous argument support that the transformation of trash is possible by changing the place of them.
-In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
-For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.
-(from William Viney)
-
-% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
-Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.
-
-%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.
-
-% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.
-
-% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
-Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
-Remember the example given: shoes  on the dinner table.
-
-% King Lear, feeling of waste
-
-% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.
-
-% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
-
-% https://narratingwaste.wordpress.com/tag/king-lear/
-% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.
-
-% Binding things together and separating things from each other.
-
-% Cornelia Parker's work, narrate an absent event of waste
-% There is also strong relationship with the collecting discarded stuff and archeologies of waste.
-
-%%% Reference
-% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
-% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
-In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
-Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
-The thesis, however, lacks depth and provenance.
-It is, actually, glib.
-Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.
-
-%%%
-%%%
-%%%
 \section{Summary}
@@
 Changing the context by first rubbishing them.
+
+Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.
+
+Firstly trash is created (by the throw away culture).
+Even if there is counter argument about it, the focus is disposable items and their amount is very high.
+After generating mountains of garbage the approach of zizek introduced.
+What to do this garbage see.
+He claims that we need to find a way to handle it.
+Find aesthetics and other things.
+Learn to live with the trash.
+
+% Burada zizekten rubbish theorye geçerken aslında bir bağlantı bulmalı.
+İkisi arasında bir ilişki kurmalı.
+Ya da aslında static değildir çöp arkadaş bak bunu ileriki kısımda rubbish theory ile sana anlatacağım diyeceğim  mesela.
+
+Later rubbish theory and relative approach to the trash.
+Trash is not static.
+Objects are not static.
+It related with the perception.
+Classification of them.
+It is possible to change shift.
+Practices of it.
+
+% Aslında burda bazı pratikler veriliyor. Ama daha detaylısı bir sonraki bölümde verilecek. Sanat bağlamına yoğunlaşılarak.
+
+Then next chapter practices in art world. Trash in the context of art. Which purpose and which method.
+
+% Bu bölümün faydası ne oldu bana. Neleri çıkartmış oldum. Tüm bunlara göz atmak gerekli.
+% - ilk olarak throw away culture denilen bir şey var.
+belli çeşit üretim ve tüketim yöntemleri var.
+ve sanatçılar bunu karşı eleştirel yaklaşmışlar.
+hatta bir şeyin alternatifi olduğunu söylerken bunun neyin alternetifi olduğunu göstermem gerektiği için kullanıyorum.
+Konu çok geniş olabilir.
+kapitalizm, endüstrileşme faktörler olabilir.
+Aslında ben bu kültürün nasıl oluştuğundan değil nasıl şeyler ürettiğiyle ilgileniyorum.
+Büyük çöp yığınları oluşturuyorlar.
+(Benim kimin çöpüyle uğraşıyorum.
+Yani aslında bir sürü çöp var.
+Biraz da bunu netleştirmek için buna ihtiyaç var.)
+
+% - Sonrasında ise bu çöp yığınlarını ne yapacağız.
+Dert bu.
+Nasıl yaklaşmak gerekli bu çöp yığınlarına.
+Burada belki bir kaç yaklaşım verilebilir.
+Ama ben zizekin yaklaşımını ele alıyorum.
+Çünkü adam demiş ki çöpünüzle birlikte yaşayın.
+Ben de zaten bunu yapmaya çalışıyorum işimde.
+
+% - Çöp ile birlikte yaşa diyorsun ama bu nasıl olacak.
+en azından mümkün mü?
+Burada aslında çöp dediğin şeyin aslında bir şeyin bir sınıflandırma sorunu olduğu ve farklı stateler arasında geçişler yaptığını görebiliriz.
+
+% Sonra bu iş pratikte nasıl oluyor ona bakılabilir.
+
+% Yeri gelmişken pisuvarı da bu rubbish theorynin sınıflandırmasına sokabilirim.
+
+% Daha detaylısı için ise aslında diğer bölüme yönlendirilebilir.

### 2015-11-09 chapter3.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

@@
-\chapter{Trash in Art}
+\chapter{Trash (in) Art}
 
-\epigraph{\textit{\quotes{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together.
+\epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together.
 I assembled these two objects, which everyone then recognized as a bull’s head.
 The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense.
-If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \singlequotes{Here’s something that would make a good handlebar for my bicycle!} }}}{\hfill ---Pablo Picasso}
+If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}}
 
@@
 
-% TODO praphase
-[TODO praphrase] \quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+% TODO paraphrase
+\quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
 Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
@@
 % TODO reading...
-[TODO read this resource]\cite{greenberg1984collage}
+\cite{greenberg1984collage}
 
@@
 William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
+
+%%
+%%
+\subsection{Bricolage}
+Dictionary meaning; something constructed using whatever was available at the time.
+
+% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;
+
+% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime.
+bunu yapan kişiye de bricoleur deniyormuş.
+lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş.
+kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.
+
+Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
+\cite{levi1966savage}
+
+the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
+
+\begin{blockquote}
+[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
+His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
+\end{blockquote}
+
+\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.
+
+\begin{blockquote}
+The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
+There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
+\end{blockquote}
+
+\begin{blockquote}
+The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
+In this sense the engineer is a myth.
+A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
+The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
+\end{blockquote}
+
+% TODO reading...
+[TODO use this ref]\cite{strasser1999waste}
+
+Bricolage is different than collage.
+Bricolage > collage.
+Because it is more general understanding of human practice.
+Collage is just only gluing paper together and it can be only a subset of bricolage.
+Same applicable for assemblage.
+Transforming trash can be examined within bricolage.
 
@@
 %%%
-\section{Example Artworks}
+\section{List of Artworks}
 Artist and artworks related with trash and their analysis.
@@
 
-%%
-%% TODO sample statements here.
-\subsection{Artist statements}
-\begin{itemize}
-\item I am an artist living in New York City, and my experience of daily life here is both the catalyst for and the subject of my art.
-Working from the local, the personal and the ordinary - the paper take-out coffee cup in the palm of my hand, the view from my studio window in the Garment District, friends and their children, the community garden around the corner from my apartment in Hell's Kitchen - my drawings, paintings and installations are about what happens when the familiar suddenly undergoes a perspective shift and is revealed in all its wonder and infinite possibility.
-With this shift, mundane things become extraordinary, as nodes of rapidly expanding sets of connections, relationships and new artworks.
-
-My approach to art-making is both observational and process-oriented.
-A fascination with cultural, physical and temporal change combined with the possibility of infinite variation unify projects as diverse as drawing and painting on my used coffee cups each day, repeatedly recording the view from my studio in paint and photography over the course of six years, depicting in two and three dimensions the incursion of human activity on the fractal meanders of salt marshes along the New Jersey coast, and painting portraits of alternative families in my New York City neighborhood.
-(from http://gwynethleech.com/)
-\end{itemize}
-
 %*****************************************
@@
 
-%%
-%% ACTIVISM as a methodology 
-%% TODO reading...
-\section{Art and activism}
-Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.
-
-%*************************************
-% Phrases...
-% What specific social issues are you trying to address through Labyrinth?
-% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art.
-Table 1 organizes this classification according to a set of multiple criteria.
-(But this one can be used at introduction, but it is too long to fit on introduction.
-Maybe select works by giving prominence to some of the features.
-So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art.
-Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.)
-\section{Crowdsourcing, Participation}
-% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
-In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}.
-The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers.
-Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing.
-Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.
-
-The value of crowdsourcing lies in the collective intelligence of the contributors.
-Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p.
-13).
-The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism.
-Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004).
-Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?
-
-All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks.
-They are not bought, not gift.
-They are found.
-They are accepted.
-One of the most creative medium is paper and pencil.
-Chance given to the people through this work.
-
-However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment.
-It is well studied area.
-Pick a method here.
-Transforming trash with collaboration.
-
-As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).
-
-Here this question can be raised about why this type collaboration.
-Another option can be working together with people on a table.
-Creating things at that time and transforming the objects here.
-Possibly the connection to the people will more realistic and intense.
-However same things can be succeed on the internet at some level.
-
-While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers.
-(This totally a new area to discuss, I'm going to summarize and introduce concepts and debates.
-How are they support my work and how they are give way to me?)
-
-% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories.
-Principally, my interest is in answering two key questions.
-What is crowdsourced art and how can it be classified?
-And how does the structure of the artwork determine the degree or significance of participation?
-
-% why collaboration, is it really a collaboration?
-
-% TODO 
-% Umberto Eco's Open Work
-
-% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
-% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
-Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
-Reveal all his possessions.
-and loosing them while you are alive.
-Turning them to rubbish making them unusable.
-breaking down the all the meaning.
-breaking down the connections.
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
-
-% In this thesis project case the issue is not the language of art and its methods.
-
 \section{Summary}
@@
 \end{itemize}
+
+% Ben bölümde aslında çöpün sanatta nasıl yer aldığına bakıyor olacağım. İlk kim kullanmış nasıl kullanmış. Sonrasında hangi anlamlarda kullanılmış.
+
+% Aslında ben uygun her yerde çöpe olan yaklaşımlarla ilgili örnekler verdim. Peki ya bu bölümde ne yapacağım. Belki gene değineceğim. Ya da ne anlamlara geldiklerini özetleyeceğim.
+
+% Hangi sonuçlar çıkacak aslında bu bölümden benim için kıymetli olan o. Özellikle caselerden. Bu nasıl bir artistict act oluyor.
+
+% Her sanatçı bu arada çöpü dönüştürmüyor. Bazıları ise onu oldukları gibi kullanıyorlar. Yani farklı kullanım seneryoları var. Ama ben dönüştürmeye dair ne çıkaracağım bu bölümde.
+
+% aslında dönüştüğünü nereden iddia edebilirim.
+Rubbish theory?
+Durable state.
+Ya da onun tekrar hayata geçtiği.
+Benimkiler de belli noktalarda fösterilecekler.
+İnsanlar o defterleri saklıyorlar ne de olsa.
+Zaten dönüşme işlemi direk müzeye çıkmasıyla oluyor.
+İllaha onun materyal olarak dönüşmesi gerekmiyor.
+Bu yüzden her iş aslında bir şekilde dönüştürüyor.
+Sanatsal pratikler çöpü dönüştürüyorlar.
+
+% Sanatsal bir eylem olduğuna nasıl varacağım peki?
+Çünkü topluyorsun, belli bir yaklaşım geliştiriyorsun.
+Bu eyleme insanları davet ediyorsun.
+Sanatın eylem olma olayı...
+Buna burda değinip, kendi işime geçmeliyim.
+
+% Ne topladım buradan.
+Bu işin sanatsal bağlamdaki yerini öğrendik, yaklaşımları öğrendik.
+Yeni ihtimaller görme, hayatta var olma, alternatif oluşturma gibi.
+Ben de bu tür şeyleri kendi işimde kullanacağım.

### 2015-11-09 chapter4.tex
new artwork
Former-commit-id: e9247e54386b522d9f8b64f65f9dc058b1befa5b
chapter 3 organization.
Former-commit-id: fcd9c8bc8fd426f8392128fbd8fee0972cb7998e
reorganization and compilation.
Former-commit-id: f9b8dcf47704fea0ad54949bca9599f5d2407301
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

@@
+\chapter{Thesis Project: Notebooks from Trashed Papers}
+
+%****************************************
 % Structure of Chapter:
@@
 %  - Parts of it. (Collecting, Transforming, Spreading them)
-% Exhibition?
+% Exhibition
+%........................................
 
-% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
-The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 % Relationship between my project and theoretical aspects:
@@
 % - Inspiration from the other artist and also 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%........................................
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 % Sample Phrases
@@
 % The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
+The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
+%........................................
 
-\chapter{My work}
+% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
+\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful?
+And very shortly you discover that there is no reason.
+If we can conquer that dislike, or begin to like what we did dislike, then the world is more open.
+That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}}
+
 In this chapter the artwork(thesis project) will be explained in detail.
@@
 
+% What I have write is here to cover the project can not be sufficient.
+Because it is not possible to say everything about this project.
+I wish that this work would allow different interpretation and readings.
+
 %%%
 %%%
-%%% TODO extend this part
+%%% 
+% TODO
 \section{Artist Statement}
-Collect(Rescue), Store, Transform, Spread.
+(Collect, Save, Transform, Spread.)(Rescue, Revive)
 
@@
 %%
-\subsection{(Overcomed) Problems}
+\subsection{Problems}
 There are a lot of questions and problems that I have to overcome while development of my work.
@@
 
+\textbf{Why is it art?} Uses artistic methods?
+Does it represent anything?
+The idea is transforming things.
+Anything can be transformed and re-contextualized again.
+The limitation is our imagination and approach.
+It has a claim.
+In can be analyzed and examined in the context of art.
+It is hard to say that something is art or not.
+However it can be examined in the context of art.
+There are artworks reject art galleries.
+There are artworks also reject commodities.
+It has purpose that.
+spread out the idea in different manner.
+Subverts peoples ideas.
+
+The work aims to liberate the imagination and change the way people see the trash.
+
 %%
@@
 
-%
-\subsubsection{History of paper}
+% History of Paper
 The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
 
-%
-\subsubsection{Production of paper}
+% Production of Paper
 All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
 
-%
-\subsubsection{Uses of paper}
+% Uses of Paper
 Paper has become the most ubiquitous product in the age of information.
@@
 Because it is revisited and reclaimed.
-
-%%
-%%
-\subsection{Why is it art?}
-Uses artistic methods?
-Does it represent anything?
-The idea is transforming things.
-Anything can be transformed and re-contextualized again.
-The limitation is our imagination and approach.
-It has a claim.
-In can be analyzed and examined in the context of art.
-It is hard to say that something is art or not.
-However it can be examined in the context of art.
-There are artworks reject art galleries.
-There are artworks also reject commodities.
-It has purpose that.
-spread out the idea in different manner.
-Subverts peoples ideas.
-
-The work aims to liberate the imagination and change the way people see the trash.
 
@@
 \subsubsection{Name of notebooks}
+  \begin{figure}[ht]
+      \centering
+      \includegraphics[width=0.8\textwidth]{project_graphics/banner1.jpg}
+      \caption{Banner}
+      \label{fig:Banner_1}
+  \end{figure}
 \begin{itemize}
@@
 
+% I add the screenshoots of website. Also the development of it. Sketches of website. Navigation of it. User interaction. Use cases and actions. Functionalities.
+
 % Documenting the progress.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 % EXHIBITION
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%........................................
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 %% Move to the other sections:
@@
 The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%........................................
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 % TODO Find a solution for this problem:
@@
 
-% Problem:
+%
+% PROBLEM:
 % In theoratical part I am focusing on actually the trash.
@@
 What is the importance of co-authored work?
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%........................................
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%****************************************
 % Explain your project that I am like and child: 
@@
 % What is the main focus in my work? Participation? Transformation? Composite of them? Trash? What else? 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%........................................

### 2015-11-09 chapter5.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

\chapter{Conclusion}

Many artworks are introduced. They have differences in terms of purpose and approached to the trash. Some of them only valued from its plastics effects. Some of them turned to the performative act.

\textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)

There is also discard is being generated during the production process of papers. as an production process how to use them? need to find a way because varda uses this discard items. etc. even if work is generated from discard items. again always new discard items are generated.

% Bu bölümde gene toplu bir özet yapılacak. Teker teker argumanlardan bahsedilecek. ve bu argumanlerın yeri belirtilecek.

% O zaman yarın gene tüm yazdıklarımı okuyorum, nasıl birleşeceğine karar veriyorum.

### 2015-11-09 uncategorized.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2

\chapter{Uncategorized}

%****************************************
% EPIGRAPH:
% How to cite epigraph http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html

% FROM http://stanforddailyarchive.com/cgi-bin/stanford?a=d&d=stanford19920130-01.2.5&e=-------en-20--1--txt-txIN-------#
% The thing to do is to find some way --- and it can be done, I think, through art --- to enjoy life in its vast multiplicity. --- John Cage

% FROM Wild Art
% Bu epigraphta aslında şöyle bir sıkıntı var, bir şeyin miktarı artınca daha fazla insanın onun üzerinde düşeceğini varsaymak biraz sıkıntı olabilir.
% We are going to make a lot more junk, and there is going to be a lot more junk art. I think people are going to have a lot to say about it, and more people need to think about it. --- Jeremy Mayer, quote taken from American Craft Magazine, December/January 2011.

%%%
%%%
%%%
\section{In Theory}

%%
%%
\subsection{What is trash?}
In this thesis work to understand the different aspects of trash is a key element. Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here). Sometimes it is accepted as a problem that is need to carefully and seriously manged. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

%%
%%
\subsection{Trash is everywhere and, produced every time}
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession. During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

% TODO PRAP. REF.
Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever. The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment. (FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS)

% TODO PRAP. REF.
Literature is recycled material, a pretext for making more art. I learned this distillation of lots of literary criticism in workshops with children. I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation. For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress. (FROM Recycle the Classics, BY DORIS SOMMER)

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
% TODO PRAP. REF.
We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can. The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material. (BY PAOLA IBARRA)

%%
%%
\subsection{Cycle of trash}
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

% Like a summary sentence
Here the important thing is moving nature of trash. Objects moves and gains different meanings through this movement. Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle. It also signifies that it is relative and result of a classification issue. All of them are creates a harmony. supports each other with different words and conceptualization.

% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
Below part Explains journey of trash, its different steps. Object moves and also trash also moves. How is it life of trash? This part explains life of trash. How does it intersect with other people in which places? This part also can be understand by pointing out different part of it with detailed explanation. For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill. In other words there are different places to touch on trash. Every place generates different story? Or to understand it more deeply it covers different part of it. Or provides ideas about it. Lots of people touches it from philosophers to artist. Also in the later parts it draws attention to them. [PRAP, REF Maite Zubiaurre]

Trash moves, all the time. It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill. Even in the landfill, it does not remain still. Monster "waste handling dozers" move rubbish around, compact it and press it against the soil. More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche. When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement. This is how trash moves. But\ldots who moves on trash? In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish. In Latin America, it is mostly people. People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks. In many of the garbage dumps around the world, scavenging becomes a steady job. \quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is. (through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
% >

%%
%%
\subsection{Perspectives related with trash from different disciplines}
This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it (handled by the municipals generally).
\item Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)
\end{itemize}

% Sample sentence:
% Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture

\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}. In other word the problem is our technology which is not perfect. (and I'm not sure that at some point that technology will reach to the perfection or not.)

\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme. Yes and no.  After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast. Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects. No one called it recycling. Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash. They can not handle their trash. There is no place for trash in their life.

\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained. \quotes{What is happening to trash is what is going to happen to us. We’re all going to end up in a dump, and we’re going to decompose. That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live. Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said. But when the same student went to Beverly Hills to go through trash, the police were nearly called. \quotes{Who decides what is public and what is private? How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}

%%
%%
\subsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%
%%
\subsection{Types and Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase. Therefore for the ones that have no complex tools it is becoming harder to reuse objects. In other words objects become more complex their re-usage becomes less likely.

Different production process generates different types of trash. According to production process, decomposition process\ldots

The approach to the different type of trash will be different. In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it. There are some trashes that are more close to the people. More easy to convert them. more easy to regain to the society.

%%
%%
\subsection{What is wrong with trash?}
Relationship between entropy (second law of thermodynamics) and waste. Resources of nature turns to waste that it can revert it. Creating that are reversible again is problematic through the nature of sustainability. What is produced after it is consumed become worthless.

From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities. There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc. Even if they are excluded, there is also life for them.

% TODO Reference
John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge. He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.

%%
%%
\subsection{Collecting trash}
One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them. What are the dynamics(considerations) of collecting them? (easily accessible materials or unique items.) Where to store them? Does it mean that live with trash? In other words collecting trash and using them is live with them? (making them part of life.) After the being part of the are they still trash? Can be thought that it is something that affects the lifestyle. (possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value. What is the driving force? You may collect it to prevent object being lost. For archival things what you collect is something that has some sort of social use and meaning which is going to disappear. However, trash is never disappearing, even its amount increasing rapidly. For archival things people have memories with them, but does some applies for the trash? Who wants to keep trash? or who wants to re-see(re-visit) trash again (in a museum for example)?

[TODO: ragpickers from benjamin and archades project.]

%%%
%%%
%%%
\subsection{Literature review, discussions, ideas\ldots}
Trash art is not collage (assemblage or found object) or fragments. it is more than that. The carried messages through the medium have different meaning. It has relationship with activism, craftivism. It refuses consumption based life cycle. It suggests a life practice.

"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others. The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions. Worthless. Rejected and useless matter of any kind. Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}

%%
%%
\subsection{Culture, Values, and Garbage}
"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share. In terms of their relationship to garbage, all people interact with it on two levels. One is a material connection, indicative of the physical and sensory contacts that people have with garbage. In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends. Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside. The second connection that people maintain with garbage is an ideational one. Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition. The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object. Instead, humans determine whether the object is of value or whether it is considered trash. The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package. The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}

%%
%%
\subsection{Garbage in Modern Thought}
"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash. It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions. Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}

%
\subsubsection{Categorization and Value}
"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay. Consumers have become accustomed to the categories that are often applied to garbage. Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03). Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}

"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted. Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value. While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined. Many non-Western societies attach a much greater value to items after they are discarded. In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value. Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture. People define what is trash and what is valuable." \cite{lukas2012garbage}

%
\subsubsection{Semiotic Context}
"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}

%%
%%
\subsection{Garbology}
Garbology is a study of waste as a social science.

"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}

"The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. A. J. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."

In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.

% Rubbish: The Archeology of Garbage, p.24
As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades. THe Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life. (example of Medical researches)

%%
%%
\subsection{Trash as History/Memory}
% TODO From encylopedia
\cite{bullock2012trash}

%%
%%
\subsection{Trash Aesthetics}
%Walter Benjamin's trash aesthetics and Adornos reflection. 
\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}. Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity. In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday. The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.

%**************************************
% HERE Same sample phrases are listed you can use them:

% The work that follows is divided into three sections

% The artist thinks, acts, performs music, and writes outside the framework that society has created.

% this thesis takes a rather different approach to the resonant possibilities of discarded things. It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.

% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.

% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.

% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.

% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.

%*******************************************************************
% FROM The Ruin and the Ruined in the Work of Kurt Schwitters.
% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality

\subsection{Discussions}
Objects moves around and their values change constantly. (The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.). The Social Life of Things: Commodities in Cultural Perspective)

Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed. (Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)

% FROM Trashion: The Return of the Disposed by Bahar Emgin
In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of. This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trashcan in the form of waste. In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.

Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”

% Prap. same source...
% On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” 9 Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework. The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society. 10 Waste now became evil. If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts. 11 Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” 12 Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world. Upcycling... On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit. Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste. 16 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home. In short, there is a whole sector of upcycling now.

% Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless. People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.

% There is commodity aspect of it and also the process of accommodation. In this process design plays a significant role. Trash is waiting to be discovered. At the same time forgotten styles are also used in works. Therefore actually trash and forgotten styles can be considered in the same status.

% This can be sample thesis statement sentence:
% This article is about those objects that are recreated from trash through the process of upcycling. Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” 4 I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste. This theory counters the argument that an object is dead once it is disposed of.

% From The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.

% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin. As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.

% FROM Waste by William Viney
Douglas argues that our classification of dirt lies not with what objects are but where those objects are. (Think that the transformation process. Previous argument support that the transformation of trash is possible by changing the place of them. In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’. For Douglas dirt is a spatial problem, a question of not what stuff is but where it is. (from William Viney)

% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position. Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.

%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty. But it is very strange that the fat on the paper is previously what they are eat.

% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.

% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte. Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda. Remember the example given: shoes  on the dinner table.

% King Lear, feeling of waste

% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.

% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.

% https://narratingwaste.wordpress.com/tag/king-lear/
% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.

% Binding things together and separating things from each other.

% Cornelia Parker's work, narrate an absent event of waste
% There is also strong relationship with the collecting discarded stuff and archeologies of waste.  
%%% Reference
% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society. In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.

%%%
%%%
%%%
\section{In Art}

%%
%% TODO sample statements here.
\subsection{Artist statements}
\begin{itemize}
\item I am an artist living in New York City, and my experience of daily life here is both the catalyst for and the subject of my art. Working from the local, the personal and the ordinary - the paper take-out coffee cup in the palm of my hand, the view from my studio window in the Garment District, friends and their children, the community garden around the corner from my apartment in Hell's Kitchen - my drawings, paintings and installations are about what happens when the familiar suddenly undergoes a perspective shift and is revealed in all its wonder and infinite possibility. With this shift, mundane things become extraordinary, as nodes of rapidly expanding sets of connections, relationships and new artworks.

My approach to art-making is both observational and process-oriented. A fascination with cultural, physical and temporal change combined with the possibility of infinite variation unify projects as diverse as drawing and painting on my used coffee cups each day, repeatedly recording the view from my studio in paint and photography over the course of six years, depicting in two and three dimensions the incursion of human activity on the fractal meanders of salt marshes along the New Jersey coast, and painting portraits of alternative families in my New York City neighborhood. (from http://gwynethleech.com/)
\end{itemize}

%%
%% ACTIVISM as a methodology 
%% TODO reading...
\subsection{Art and activism}
Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.

%*************************************
% Phrases...
% What specific social issues are you trying to address through Labyrinth?
% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art. Table 1 organizes this classification according to a set of multiple criteria. (But this one can be used at introduction, but it is too long to fit on introduction. Maybe select works by giving prominence to some of the features. So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art. Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.) 
\subsection{Crowdsourcing, Participation}
% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}. The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers. Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing. Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.

The value of crowdsourcing lies in the collective intelligence of the contributors. Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p. 13). The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism. Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004). Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?

All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks. They are not bought, not gift. They are found. They are accepted. One of the most creative medium is paper and pencil. Chance given to the people through this work.

However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment. It is well studied area. Pick a method here. Transforming trash with collaboration.

As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).

Here this question can be raised about why this type collaboration. Another option can be working together with people on a table. Creating things at that time and transforming the objects here. Possibly the connection to the people will more realistic and intense. However same things can be succeed on the internet at some level.

While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers. (This totally a new area to discuss, I'm going to summarize and introduce concepts and debates. How are they support my work and how they are give way to me?)

% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories. Principally, my interest is in answering two key questions. What is crowdsourced art and how can it be classified? And how does the structure of the artwork determine the degree or significance of participation?

% why collaboration, is it really a collaboration?

% TODO 
% Umberto Eco's Open Work

% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% In this thesis project case the issue is not the language of art and its methods.

### 2015-11-09 chapter1.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

@@
 % Section: overview of chapters
+% Section: a note on terminology
 
-% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time. Changes through the time.
+Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
+Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
+In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
+Stages and expression of this practice is examined with my artwork in the context of art.
+
+% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
 % Konu hakkındaki temel bilgiler.
@@
 
-Trash in every age.
-In other words it is part of human activity.
+Trash is global, and shared concept for all societies throughout the ages. 
+\textbf{Trash in every age.} In other words it is part of human activity of every historic age.
 It exists early ages of human to now.
@@
 [TODO etymology reference, see appendix] Archaeologist find things from people throw away.
-
-Trash in every society. Some of them called as trash the others don't.  
+\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
 % TODO look introduction of revista, there is a related reference above it.
-
-Trash is everywhere.
+\textbf{Trash is everywhere.}
 % Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.
@@
 
+There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.
+
+Yes using non art objects in the art is introduced and opened new dimensions for the language of art.
+But some of them treated as sculptures from trash.
+Reflects our world.
+But it is not limited with this.
+It also evoke it.
+And offers an alternative.
+
+% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash.
+
+% Çöp hakkındaki genel geçer bilgileri sıralamak aslında iyi olabilir. Ya da bunun hakkındaki yanlış bilinmeyen şeyleri.
+
+% Aslında sadece bir heykel işi olan şeylerden bahsedebilirim, ya da aslında belki de içine girip dokunabildiğin bir şey olabilir.
+
+% Çöpe dair araştırmalar falan.
+
+% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti.
+
+% Savunma.
+% Yani aslında bu chapterdaki fikirler vs.'ler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar.
+
 %%%
@@
 The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.
+
+In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
+Why and how are they used by the artist?
+Are there any differences with the original items compared to discarded items?
+Has using discarded material or trash specific (or special) meaning and message?
+This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
+(and also in which scope?
+medium, message, life practice\ldots)
+
+% Çöpün sanat işlerinde kullanılmasının önemi ne?
+Bunun karşısındaki şey nedir?
+Diğer alanlardaki yaklaşımlar bir şey üretemiyor mu?
+Bu tezin önemi ne?
+Birilerinin bıraktığı boşluğu doldurmak mı?
+Ya da benim yaptığım işin önemi ne?
+
+% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili.
+
+% Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.
 
@@
 What they is actually is reusing and combining things, concepts, creating new mixtures.
+
+% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended

### 2015-11-09 chapter2.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

@@
 
+% Bu endüstriye yaklaşım günlük kişisel kullanım eşyarından dağlar yapıyor. Hepsi birisinin aynısı, steril, vs
+
+% COFFEE CUP / Transforming them and invite other people, reveals its process.
+% FROM http://www.gwynethleech.com/public-drawing/cup-windows/statement
+  \begin{figure}[h!]
+      \centering
+      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup5.jpg}
+      \caption[Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions Variable]{I began to save all of my coffee cups to use as "canvases" for making art.
+Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture.
+I like my coffee or tea in a paper take-out cup.
+Even better than the contents, I like the used cup as a surface on which to draw and paint.
+And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
+For ArtPrize I am showing 1001 of my cup artworks, each representing a daily caffeine break.
+The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
+It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill.
+But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.}
+      \label{fig:GwynethLeech_TheCup}
+  \end{figure}
+
+  \begin{figure}[h!]
+      \centering
+      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup3.jpg}
+      \caption[Gwyneth Leech while painting in the public]{There are different versions of it.
+paintings on paper coffee cups displayed as installation in public window spaces.
+She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many placas and date.
+During public drawing projects she draw with other people.
+and so.
+Buying a beverage is a daily event for Leech (and also many people.
+These coffee shops all around the world.}
+      \label{fig:GwynethLeech_InAction}
+  \end{figure}
+
+% Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.
+
+% TEA BAGS
+% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
+  \begin{figure}[h!]
+      \centering
+      \includegraphics[width=0.5\textwidth]{graphics/rubysilvious-teabag-Day237.jpg}
+      \caption[Ruby Silvious, 363 Days of Tea, Day 237, 2015, Mixed media on upcycled paper tea bags, Dimensions Variable]{In the beginning of this year, visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
+She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
+The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags.
+This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers.
+Every day she creates a new piece that reflects her impressions in that moment.
+Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.}
+      \label{fig:RubySilvious_TeaBag}
+  \end{figure}
+
+% Potraits of Global Mass culture from Chris Jordan.
+In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
+“There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says.
+“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.”
+
+% Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.
+
+% He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
+Here he draw attention to the our consumerism and express them numbers that are very big to understand.
+All the material that we have is trash to create this pictures.
+
+% HAKAN GÜRSU
+% Buraya aslında bir de Hakan Gürsu koymak gerekli olabilir.
+Yani aslında kendisi pek de sanatla ilgili bir laf etmiyor.
+Ama aslında tükettiğimiz onlarca şeye karşı bir tavır yaklaşım sergiliyor.
+Bu yüzden theory kısmında yer alabilir.
+Bu çöpün içinde boğulacağımızdan bahsediyor.
+Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.
+
+% Chris jordan hem bir gerçeği açığa çıkarıyor. 
+% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.
+
+% TEZ STATEMENT.
+% Ya gerçekten çöpü dönüştürüyorlar ya da çöpe dair düşünceleri dönüştürüyorlar, ve bunu ele alırken aslında heykel, kolaj, fotoğraf gibi şeylerden yararlanıyorlar ama aslında ortaya koydukları şey bir sanatsal eylem.
+veya bunu sanatsal eylem bağlamında ele alabiliriz.
+
+% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı.
+Çöpün de bu tekrar eden yapısı buna uyum sağlıyor.
+Çünkü zaten hatayın sürekli bir parçası.
+Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.
+
+% Sanat işleri
+% Her çöpünü fotoğraflayan adam.
+
+% Tracy emin mesela.
+Yani aslında bir şekilde bir yandan aslında teoriye mi değiniyorum yoksa sanatçıların işlerine mi değiniyorum, bunların teorideki karşılıklarını mı buluyorum emin olamadım.
+Bunların ikisi paslaşarak ilerliyor aslında.
+Aslında çöplerin bize ait çok şeyler söylediğini ünlülerin çöplerini karıştıran yaklaşım ortaya çıkarıyor.
+Bu işde bununla ilgili aslında.
+
+% Sanatçıların işlerine bir de bu güzel bakarsak ne görürüz.
+
 %%%
@@
 % FROM Examined Life
-\section{Zizek on Garbage}
+\section{Zizek's Approach to Garbage}
 (There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
@@
 This part will be extended later.)
+
+% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
+  \begin{figure}[h!]
+      \centering
+      \includegraphics[width=0.5\textwidth]{graphics/ChrisJordan-Albatross.jpg}
+      \caption[Chris Jordan, Albatross at Midway Atoll Refuge, 2009]{The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.}
+      \label{fig:ChrisJordan_Albatross}
+  \end{figure}
+
+Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash.
+Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.
+
+Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures
+
+% Effect of plastic on wildlife in Antartica.
+% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor.
+Sadece başka bir yerlere gidiyor.
+Mesela kuşların midelerine.
+Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor.
+Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar.
+Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor.
+Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız.
+Karşı durduğum nokta ise tam olarak burası.
 

### 2015-11-09 chapter4.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

@@
 
+% TODO
+% Felix Gonzales Torres'in untitled işi benim yapmaya çalıştığım ile ilgili.
+
 %%%
@@
 % Converting disposal things to multiple time usage. Realizing the alternative lives of trash beyond their defined one shot life. Giving attention to the things.
+
+% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir.
+Zaten toplama sürecinde bunu insanlarla ilişki kurarak yapıyorum.
+O insanlarda diğerleriyle konuşarak yapıyorlar.
+
+% At this stage it is claimed that the process of transformation of trash can be treated as artistic act.
+In the production of notebooks people collected papers from different places and location.
+During the collection phase they also collect them from other people.
+In other words there is human communication during this process.
+
+Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
+The process effects one's life and lifestyle.
+(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
+The important thing is to interact with it.
+Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it.
+It must call the viewer to interact with it.
+
+% Ersan hoca uzak seyretmek yerine etkileşime geçilmesini auranın kırılması olarak bakıyor.
+Performatif olması veya bir act olması zaten bunu kıran bir şey olabilir.
+Sanatsal eylem, performans kavramlarını araştırmak gerekli.
+Uzaktan seyredip hayranlık duymak yerine ilişkiye geçilen bir hale getirmek çöpü.
+Amaç bu aslında.
+Çöpü tekrar tanımak, onunla barışmak, onunla yaşamak.
+İşte bu yüzden bir eylem olabilir.
+Ya da yaşam pratiği.
+
+% Olay sadece böyle çöpten bir şeyler yapıp insanların seyretmesi değil, mühim olan onunla iletişime, ilişkeye geçmek.
+Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki?
+İnsanların bu işin aşamalarının bir parçası olmalılar.
+
+With the help of art (and artistic practices) discarded things can find a place in the society.
+(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).
+The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.)
+
+% Using trash can not only understand in ecological perceptions, it also have powerful political claims.
+Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
+
+% SEEING IT AS A RESOURCE.
+Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
+Ignored and discarded nature of garbage when rethought becomes fertile resource.
+Trash as a resource (as an artistic material).
+(City as a resource.
+Seeing the discarded items as a resource.
+Many artist approach to trash as resource.
+It is a shared approach.
+Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)
+
+% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.
+
+Do she/he want to take back (or revisit) the trash once thrown away?
+People do not want to think of what they throw away.
+Turning them to a things that worth to look again.
+How do artists reflect garbage and what are their tactics?
+What is the thing that add value to trash and what is the role of art in that?
+
+With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods.
+In other words autistics practices generates applies different methods.
 

### 2015-11-09 main.tex
reorganization of chapters
Former-commit-id: fe6bfec7060411e5ac72d1de83c27de435929cb2
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[turkish,english,shorthands=:!]{babel}
 \usepackage{apacite}
@@
 %\graphicspath{ {graphics/} }
+\usepackage{float}
 \usepackage{caption}
@@
 \usepackage{wrapfig}
+\usepackage[titletoc]{appendix}
+%\usepackage{chngcntr}
+
+%\counterwithout{figure}{chapter}
 
@@
 
-\begin{document}
-\title{Transforming Trash as an Artistic Act}
-\author{Mustafa İlhan}
-\maketitle
-\pagenumbering{roman}
-\setcounter{secnumdepth}{3}
-\setcounter{tocdepth}{3}
-\tableofcontents
-%\listoffigures
-%\listoftables
+\renewcommand*\bibname{Bibliography}
 
@@
 % - Trash Notebooks: Exploring the potential of trash through art practice
-% - Notebooks from trash.
+% - Notebooks from Trash
 % - Transforming Trash as an Artistic Act
-%****************************************
+%........................................
+
+\begin{document}
+\selectlanguage{english}
+\begin{titlepage}
+    \begin{center}
+
+        \Huge
+        Transforming Trash as an Artistic Act
+
+        \vfill
+        \Large
+        A Master’s Thesis\\
+        by\\
+        Mustafa İlhan
+
+        \vfill
+        Department of\\
+        Communication and Design\\
+        İhsan Doğramacı Bilkent University\\
+        Ankara\\
+        November 2015
+
+    \end{center}
+\end{titlepage}
+
+%\title{Transforming Trash as an Artistic Act}
+%\author{Mustafa İlhan}
+%\maketitle
+
+\pagenumbering{roman}
 
 %****************************************
-% Abstract ideas
+% Ideas for Abstract
 % You can add short definition of trash. Any object can be art in 20th century. Society generated trash and a culture that do not reuse and throws away.
 % Structure of this thesis: written part of it and the project support each other.
-%****************************************
+%........................................
 
 %****************************************
-% Structure of abstract
+% Structure of Abstract
 % What is this study?
@@
 % What is the outcome?
+%........................................
 
+%****************************************
+% ENGLISH
 \begin{abstract}
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
-Why and how are they used by the artist?
-Are there any differences with the original items compared to discarded items?
-Has using discarded material or trash specific (or special) meaning and message?
-This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
-(and also in which scope?
-medium, message, life practice\ldots)
+The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act.
+Approach of artists who uses discarded material in their works treated in detail.
+It is questioned that why and how they use discarded materials and investigated in terms of theoretical and cultural aspects.
 
-% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir.
+Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act.
 
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects one's life and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
-The important thing is to interact with it.
-Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it.
-It must call the viewer to interact with it.
+\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory, Throw Away Culture, Handmade Notebooks.
+\end{abstract}
+%........................................
 
-% Ersan hoca uzak seyretmek yerine etkileşime geçilmesini auranın kırılması olarak bakıyor.
-Performatif olması veya bir act olması zaten bunu kıran bir şey olabilir.
-Sanatsal eylem, performans kavramlarını araştırmak gerekli.
-Uzaktan seyredip hayranlık duymak yerine ilişkiye geçilen bir hale getirmek çöpü.
-Amaç bu aslında.
-Çöpü tekrar tanımak, onunla barışmak, onunla yaşamak.
-İşte bu yüzden bir eylem olabilir.
-Ya da yaşam pratiği.
-
-% Olay sadece böyle çöpten bir şeyler yapıp insanların seyretmesi değil, mühim olan onunla iletişime, ilişkeye geçmek.
-Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki?
-İnsanların bu işin aşamalarının bir parçası olmalılar.
-
-With the help of art discarded things can find a place in the society.
-(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.
-
-Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
-Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
-In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
-Stages and expression of this practice is examined with my artwork in the context of art.
-
-% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.
-
-Do she/he want to take back (or revisit) the trash once thrown away?
-People do not want to think of what they throw away.
-Turning them to a things that worth to look again.
-How do artists reflect garbage and what are their tactics?
-What is the thing that add value to trash and what is the role of art in that?
-
-With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods.
-
-Using trash can not only understand in ecological perceptions, it also have powerful political claims.
-Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
-
-Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
-Ignored and discarded nature of garbage when rethought becomes fertile resource.
-Trash as a resource (as an artistic material).
+\selectlanguage{turkish}
+%****************************************
+% TURKISH
+\begin{abstract}
 
 % Ne, Nasıl, Sonuç.
+
+% Sanatta çöpün yeri inceleniyor, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
+Ya da en azından proje kapsamında üretilen işin.
+Ya da bu bağlamda ele alınabileceği iddia edilmektedir.
+
+Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır.
+Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır.
+Çöpü dönüştürmenin nasıl ne ne şekilde mümkün olduğu incelenmiştir.
+Sanatsal üretim yöntemi olarak çöpü (tercih etmiş)kullanan sanatçıların yaklaşımları ele alınmıştır.
+Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.
+
+% Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
+Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
+Aynı zamanda bu defter hakim sistemin dışındaki mekanlarda bulunarak (kamusal ortak alan)
 
@@
 ve aynı zamanda aslında çöpün ne olduğu sorgulanmıştır.
-The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act.
 
-% Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
-% Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır. 
-% Projeyle şunu sorgulanmıştır.
+Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
+Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
+Teoriler ve methodlar ele alınmıştır.
+Çöpün ne olduğu sorgulanmaktadır.
 
-\vfill\noindent\textbf{Keywords:} Trash, Art, Transformation.
+Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
+Bu atık maddeler dönüştürülerek defter yapılmıştır.
+Renk, doku, biçim ve üretim yöntemi ile endüstriyel defterlere alternatif bir yaklaşım olması amaçlanmıştır.
+Bu defterler insanların ulaşabileceği belirli mekanlara dağıtılmıştır (yerleştirilmiştir).
+Mekanlar da aynı şekilde eleştirel bakış açısına açık yerler arasından seçilmiştir.
+Alternatif bir ortam sunan mekanlar seçilmiştir.
+Bu proje sonunda dönüştürülen şeylerin aynı zamanda dönüşütüğü şeyi de başka bir şeye dönüştürdüğü anlaşılmaktadır.
+Çöpe olan bakış açısının dönüştürülmesi amaç edilmiştir.
+
+\vfill\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
 \end{abstract}
+%........................................
+\selectlanguage{english}
 
 %****************************************
-% Sample abstract from a thesis:
+% SAMPLE ABSTRACTS
+
 % Bu çalışmada, ne kadar itici bir kavram olsa da, çöplük olgusunun çirkinlikten güzelliğe ulaşarak estetik bir haz uyandırması amaç edinilmiştir.
@@
 
+% LAND ART ON THE BORDER BETWEEN TOPOLOGY AND ATOPOLOGY
+% The purpose of this study is to discuss the Land Art movement from a topological and atopological perspective.
+In order to establish an extensive understanding of the matters of topology and atopology, Arkady Plotnitsky’s formalization of quasi- mathematical thinking, which is derived from Jacques Derrida’s philosophy, is treated in detail.
+The artistic stance, Robert Smithson, as a major figure of Land Art movement is analyzed both from the artistic and the theoretical perspectives.
+Thereafter, an algebraic reading of the Smithsonian conceptualization is executed in order to illuminate the liaison between the Land Art movement and the matters of topology and atopology.
+Finally, the thesis project, Nonlocalizable Displaced Mirrors depicts the whole attitude, which is taken throughout the study, towards the issue of Land Art on the Border between Topology and Atopology.
+
+%........................................
+
+\setcounter{secnumdepth}{3}
+\setcounter{tocdepth}{3}
+\tableofcontents
+\listoffigures
+%{%
+%\let\oldnumberline\numberline%
+%\renewcommand{\numberline}{\figurename~\oldnumberline}%
+%\listoffigures%
+%}
+%\listoftables
+
 \pagenumbering{arabic}
@@
 \include{chapter5}
+\include{uncategorized}
 \bibliographystyle{apacite}
 \bibliography{literature}
+\begin{appendices}
+\include{appendix_glossary}
+\end{appendices}
 

### 2015-11-10 chapter1.tex
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

@@
 % Structure of this chapter
-% Section: topic and its significance
-% Section: the purpose of this study
-% Section: overview of chapters
-% Section: a note on terminology
+% Section: explain the topic and its significance, raise curiosity, give same facts about it.
+% Section: state the the purpose of this study, specify the focus of it.
+% Section: overview of chapters and structure of thesis.
+% Section: a note on terminology, clarification about the comprehensive terminology.
+
+\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces.
+I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects.
+My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower.
+But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}
+
+% Bence introductionda çöpün farklı şekillerde ele alınabileceğini bir şekilde göstermek gerekli. Burdaki genel geçer yaklaşımdan bahsetmek gerekli.
+
+% Ele aldığımız çöp insanların çöpleri, günlük kullanımdaki çöpler. Çok da değerli olmayan yerine yenisi koyabileceğimiz çöpler.
+
+In this thesis work to understand the different aspects of trash is a key element.
+Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
+Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
+On the other hand it is accepted as a source of diversity.
+(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
+Therefore we should ask these questions: What is trash?
+How does it became trash?
+Is it a end product or a source material?
+How much is it valuable?
+How much is it dangerous?
 
@@
 
+In previous ages (pre industrial ages?
+which age?) objects and resources are used again and again.
+Production of objects are hard and laborious.
+\comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur.
+Mendillere bunlara örnek olabilir.
+Aslında tam benim konumla ilgili çünkü tek kullanımlık.
+Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}
+
+% Trash is everywhere and, produced every time
+Modern (developed) societies are continuously generating trash and, pile them on landfills.
+It's a common object category that all people share its possession (It is experienced by everybody.).
+During daily activities trash is generated and people get rid of them by throwing away.
+(Various objects become trash after their primary functions daily.
+Who defined the primary function?
+Primary function is the only function.
+People cares the package of the objects that they buy.
+They buy the coffee not the cup of it.
+After coffee finished the life of cup also finishes.
+There is a lifetime defined (or forecast) by the producer of objects.
+However it is not bound to the producer, also consumer play an important role.
+There are different choices.
+Throw it away.
+Keep it.
+Give it.
+Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
+They are the result of highly complex industrial production methods.
+They are not easily disposable items.
+They live in the nature thousands of years.
+They are durable(in terms of resistant to natural affects) products.
+Most of them packages that are used to carry or protect other materials.
+After real material used these packages became valueless (or useless).
+(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
+This is the common approach to trash and the main problem.
+(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
+(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
+Live with trash.
+Do not see it as trash actually.
+Then the question is how to love trash?
+how to live with trash?
+can living with our trash enrich (our perceptions, abilities)?
+how not to see them as trash and useless?
+Can it be possible with art?)
+
+% FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
+% TODO PRAP. REF.
+\todo{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
+The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD countries produce almost half of the world’s waste.
+Africa and South Asia produce the least waste.
+High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
+Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.}
+
+% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+% TODO PRAP. REF.
+\paraphrase{We relate to garbage daily.
+We use it, produce it and dispose of it.
+Endlessly.
+The most obsessive of us get rid of it as fast as we can.
+The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
+We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
+Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
+Particularly in the connection between garbage and the arts, I am interested in two questions.
+First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.}
+
 % Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
@@
 % Konunun ele alınan kısmı.
-%
 
 % Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir? 
-% Meaning of words here. move reuse and recycle here.
+% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash. 
+People tend to think that trash is values because it is trashed no longer needed or not wanted anymore.
+However is it really values?
+What does make it valueless?
+They do not think what happens after they throw it away.
+It exits from your life but not the world.
+What happens when you throw away a It is stacked from another place.
+Value of objects are not static.
+Trash is not static also It has a long journey.
+A project conducted by MIT researches journey of trash by placing trackers onto the trash.
+The results are surprising.
+Trashes spread away across the country and this journey takes month.
+\todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}.
+In other worlds Americans trash is not only their trash.
+As commodities spread to the every corner of the world, trash also.
+What happens when it is traveled to the other countries, how they approaches these items.
+\comment{They find new uses and meanings on them.} \todo{consider Papua genen people}
 
-% Belki direk bir sanat işiyle girebilirsin.
-Etkileyici olması açısından.
-Hangi iş olabilir?
-Çöpün ne olduğunu ele alan hem de ona karşı bir yaklaşım geliştiren bir örnek belki de benim işine çok benzeyen bir şey olabilir.
-Starbucks bardaklarından bir şeyler yapan insan olabilir.
+% Cycle of trash
+Trash moves, objects moves from place to place.
+From homes to garbage trucks.
+From streets to land fills.
+From garbage baskets to sculptures.
+[REF.
+MIT Garbage project] Lots of different people touches to trash.
+With the trash what moves?
 
-% Amelie olabilir.
-Orada fotoğraf toplayan çocuk olabilir.
-Onları itinayla toplayan bir adam.
-Tren garındaki fotoğraf kulubesi.
-Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
-Bir birinden farklı bir sürü insan.
-Filmde neden böyle bir eyleme yer veriliyor?
-Film fotoğraflar üzerinden defter üzerinden ilerliyor.
-Onun çevresinden bir hikaye kurgulanıyor.
-İnsanların artıklarını topluyor.
-Bunlar baya baya aslında o insanlar.
-Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
-Çok iyi bir örnek mi bilmiyorum.
-Burada niyet nedir ki?
-Ben buna şöyle bir okuma getireceğim diyebilirim.
-
-% Wall-E belki olabilir.
-Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
-Çöp dağları, çöp denizleri.
-Atılmış binbir türlü nesne.
-ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
-Bundan basetmişken aslında pressleme işi yapan şu cesar.
-Bu şekilde olmak zorunda mı?
-Bunun alternatifi yok mu?
-Aslında bu tezde bunlara cevap bulunabilir.
-Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
-Ya da başka neler var?
-Bunları araştıran inceleyen bir yazı.
-Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
-İnsanlık buna mı dönüşücek?
-Başka bir ihtimal yok mu?
-Gerçekten de dünyayı bekleyen şey bu mu?
-Bir çöp yığını olması mı?
-Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?
-
-WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles to giant dozers that moves and piles trash in the landfills.
-This robot creates squeezed trash blocks that has no meaning and interpretation.
-All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
+Even if people pay little attention, everybody do not.
+An artist takes photos of his every trash, like people take photos of their faces.
+He focuses on the thing that paid little attention, that is trash.
+At the end he exhibits all the photos by covering all the walls of room.
+It can seen as record of his activities, record of commodities.
+Most of them we are not aware of them.
+Draw the attention of is being thrown away and everytime and everywhere.
+They are too much and can only fit covering all the walls.
+\todo{artist}
 
@@
 \textbf{Trash is everywhere.}
-% Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.
 
-% Gene aslında sürekli tükettiği şeylerin fotoğrafını çken sanatçı.
+% ARTWORK
+% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuous
 
-% Intoductionua bir sanatçı fikriyle girip konuyu oradan açabilirim. Bir hikayesi yaklaşımı olabilir.
+Why people are interested in rubbish.
+Some of the artist also interested in others trash.
+\comment{O çöplerde ne bulmayı umuyorlar ki?
+Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor.
+ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor.
+Bazen de olduğu gibi kullanıyorlar.
+bu açıdan önemli.
+Çöpü çöp şekliden sunan sanatçılar.
+Ama bu nasıl mümkün ki?
+fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar.
+Bence değil?
+bir şekilde müdahele var gene orada.
+o fotoğraflarda artık dikkatin objesi haline geliyor.
+çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.
+
+% Amelie olabilir.
+Orada fotoğraf toplayan çocuk olabilir.
+Onları itinayla toplayan bir adam.
+Tren garındaki fotoğraf kulubesi.
+Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
+Bir birinden farklı bir sürü insan.
+Filmde neden böyle bir eyleme yer veriliyor?
+Film fotoğraflar üzerinden defter üzerinden ilerliyor.
+Onun çevresinden bir hikaye kurgulanıyor.
+İnsanların artıklarını topluyor.
+Onların değer vermedikleri şeyleri topluyor.
+Bunlar baya baya aslında o insanlar.
+Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
+Çok iyi bir örnek mi bilmiyorum.
+Burada niyet nedir ki?
+Ben buna şöyle bir okuma getireceğim diyebilirim.
+Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
+Bu arada bu fotoğraf toplama işi ilk değil.
+Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
+Ama benim işime yarayan kısmı ne?
+Neden o fotoğrafları ya da bunun filmini yapıyor.
+Aslında puzzlelar üretiyor.
+Belirli tekrar olacaktır.
+insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
+Tekrar bir kitap haline geliyor.
+Tanınmayan insanların fotoğrafları.
+Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
+Aslında tam da amelie bunu yapmıyor mu?
+Hikayeler üretiyor bu fotoğraflardan.
+Yeni karşılaşmalar üretmesi.
+Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
+Bin bir türlü şey vardır aralarında.
+Nereye yerleşmeli.
+Başkasının çöpünü toplama.
+O dönemin o eşyasını arşivini tutma.
+ve herkes sunuluyor sonrasında bu.
+
+% Wall-E belki olabilir.
+Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
+Çöp dağları, çöp denizleri.
+Atılmış binbir türlü nesne.
+ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
+Bundan basetmişken aslında pressleme işi yapan şu cesar.
+Bu şekilde olmak zorunda mı?
+Bunun alternatifi yok mu?
+Aslında bu tezde bunlara cevap bulunabilir.
+Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
+Ya da başka neler var?
+Bunları araştıran inceleyen bir yazı.
+Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
+İnsanlık buna mı dönüşücek?
+Başka bir ihtimal yok mu?
+Gerçekten de dünyayı bekleyen şey bu mu?
+Bir çöp yığını olması mı?
+Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?
+
+WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
+A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
+WALL-E resembles giant dozers that moves and piles trash in the landfills.
+This robot creates squeezed trash blocks that have no meaning and interpretation.
+All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
+There are mountains of trash and place is very limited.
+By squeezing them, WALL-E saves space.
+\todo{What is the context of it?
+Which part is related with my topic?} What are we going to do with all these mountains of trash?
+\todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.
 
@@
 
-% Background information about the thesis. Inspirational points. The fact of trash.
+\todo{Background information about the thesis. Inspirational points. The fact of trash.}
 
-% Firstly as a part of art making.
-Changes in art making?
-// Sanatın köklerine inme abi.
-Sen sanat bağlamında anlatacaksın bunları.
-Zaten ilerisinde değineceğin şeyleri neden şimdi tekrardan anlatıyorsun.
-In the beginning of the 20th century non-art objects enter the scope of art making.
+% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti. 
+\comment{In the beginning of the 20th century non-art objects enter the scope of art making.
 This is a revolutionary change in the making of art.
@@
 Later many of them followed him.
-First works are collage and then collage.
+First works are collage which gluing different papers together.
+Yes using non art objects in the art is introduced and opened new dimensions for the language of art.
+But some of them treated as sculptures from trash.
+Reflects our world.
+But it is not limited with this.
+Some of the works are provokes the consumption habits of society and offers an alternative perception.}
 
@@
 
+\comment{Trash draws attention different peoples and disciplines.
+In other words there are different studies related with trash.
+Different approaches to the trash and son on.
+However in this thesis study trash }
+
 There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.
-
-Yes using non art objects in the art is introduced and opened new dimensions for the language of art.
-But some of them treated as sculptures from trash.
-Reflects our world.
-But it is not limited with this.
-It also evoke it.
-And offers an alternative.
-
-% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash.
-
-% Çöp hakkındaki genel geçer bilgileri sıralamak aslında iyi olabilir. Ya da bunun hakkındaki yanlış bilinmeyen şeyleri.
 
@@
 
-% Çöpe dair araştırmalar falan.
-
-% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti.
-
 % Savunma.
 % Yani aslında bu chapterdaki fikirler vs.'ler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar.
+
+This trash pheomanan catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Many type of it?
+
+% Idea of everthing can be trash. Act of trashing. not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
+% Michael Landy's Art Bin uses a art gallery to create his dust bin.
+Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
+Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
+"There's no hierarchy once they are in the bin" All of them are accepted as same.
+Ultimate equality.
+Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
+Nothing's too good for the art bin.
+Everything can fit into the art bin.
+Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
+As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
+It is a very big glass bin and isolates people.
+There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
+There is no limitation of throwing away even if art.
 
@@
 \section{Purpose of the Study}
+
+%****************************************
+% It is a justification of the work. 
+% What is trash? Who does call it trash? 
+% Is it possible to transform it? How? Which methods?
+%........................................
+
+\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
 
@@
 
-% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili.
+% Önceki işlere değinmek gerekli.
+Bu alanla ilgili yapılmış.
+Mesela ne var.
+İki tane tez buldum aslında tam da bu konuyla ilgili.
+Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.
 
-% Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.
+As many people are inside the business of transforming trash through craft and so on.
+People on the streets looking for aliminu cans, glass bottles, plastic.
+They collect and sell them to survive.
+There are companies that are collect waste materials to regain them again the industry.
+In thesis they are not in the scope.
+People that give attention to the trash and behave artistic act is in the scope of this thesis.
+
+% How does it become trash?
+Here the purpose is to understand the dynamics that turn objects to trash.
+By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
+(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
+Therefore first question is why they are less-valued, and ignored.
+How to make them valuable?
+How to make them part of our life again?)
 
@@
 %%% 
-% Bu kısım aslında yukarda bahsedilen amacın nasıl yapılacağını anlatacak.
 \section{Overview of Chapters}
+This study is structured many examples of artworks in different part of the thesis.
+As the related topic or argument is presented example artwork is given at this moment.
+Immediately how artist replies this issue is illustrated.
+Thereby artworks are examined in the theoretical and cultural context.
+Art works are used as a supportive elements for the stated arguments.
+\comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.}
+
 Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash.
 The aim is (better) to understand the trash in cultural and theoretical aspects.
-(to better realization the notion of trash.)
+(to better realization the notion of trash.) It is explored the trash is being worked is whose trash.
+Or what type of society genarete this trash.
+Also in the project I collect the paper trash.
+What type of approach generate it and what are the dynamics of it?
+What type of trash we are talking about?
+It is understood through the patters of consumption patterns.
+And to reflect this cultural phenomena what phylosphers and scholars say.
+Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system.
+How explained the transient nature of trash?
+
+\comment{First chapter will be about the conceptual framework that I have been working through
+which includes historical and theoretical background.}
 
 Third chapter seeks the root of using trash in the artworks and looks through the sample artworks.
+As already artworks are mentioned in the different part of the thesis, in this chapter focused on art (historical )
 
 Fourth chapter explains the project that supports this thesis. Its stages and approaches to the topic mentioned here.
+
+\comment{The second chapter will consist of the overview of my work.
+I will start with the development process of the work.
+I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied.
+Development process of my work shaped the way I think on the subject of my thesis.
+Therefore, I will explain my process as detailed as possible.
+Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level.
+At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}
 
@@
 %****************************************
-% Examples from other thesis.
-% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology.
-// The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
-It is questioned the role of art in transformation of discarded items.
-This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
-Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.
-%........................................
-
-%****************************************
 % Sample phrases:
@@
 % Some comments
-% This written portion was to evaluate the project in terms of a justificatory theoretical framework.
-% This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.
 % Burada önemli olan şey soru veya sorgulanan şey.
@@
 
-% Çöpün dönüşmesi diye bir şeyin olduğunu aslında kullanıcıya aktarmak gerekli introductionda.
-
 % Agnes varda neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında sanatçıları da geziyor, çünkü onlar da topluyorlar.
@@
 % - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
-
-%****************************************
-% ARGUMENTS:
-% 
 %........................................
@@
 Diğerleri ise çöpe ele almaları
-%........................................
-
-%****************************************
-% It is a justification of the work. 
-% What is trash? Who does call it trash? 
-% Is it possible to transform it? How? Which methods?
+% Ben picassonun sahip olduğu kaygılarla sanat yapmıyorum. Yani ondan bahsetmek ya da sanatın bu işlerdeki köklerinden konuşmak benim için yeterli değil. DAha da fazlasına ihtiyacım var. 
+% Benim kaygılarım ne peki? Ben kime hitap ediyorum, bence burada bir ayrım söz konusu.
 %........................................
@@
 % Reuse and Recycle
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars (ref required).
+One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars \todo{ref}
 
@@
 The main purpose of reusing is to lengthen the life of the item or material.
-We give out used clothes for charity which results in reusing.
 Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
@@
 
+%****************************************
+% UPCYCLING TERİMİNİ KULLANANLAR.
 % Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended
+% Raw+Matrial=Art burda da upcycling deniliyor.
+%........................................

### 2015-11-10 main.tex
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

@@
 \usepackage{epigraph}
-%\usepackage{setspace}
-%\doublespacing
 \usepackage{graphicx}
@@
 \usepackage{wrapfig}
+\usepackage[usenames, dvipsnames]{color}
 \usepackage[titletoc]{appendix}
+
 %\usepackage{chngcntr}
+%\counterwithout{figure}{chapter}
 
-%\counterwithout{figure}{chapter}
+%\usepackage{setspace}
+%\doublespacing
 
@@
 
-% Quotation command
 \providecommand{\quotes}[1]{``#1''}
 \providecommand{\singlequotes}[1]{`#1'}
+\providecommand{\todo}[1]{\textcolor{red}{#1}}
+\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
+\providecommand{\paraphrase}[1]{\textcolor{magenta}{#1}}
 
@@
 % - Trash as an Artistic Medium
-% - Trash Notebooks: Trash in the Context of Art
-% - Trash Notebooks: Exploring the potential of trash through art practice
-% - Notebooks from Trash
+% - Notebooks from Trash: Trash in the Context of Art
+% - Notebooks from Trash: Exploring the potential of trash through art practice
 % - Transforming Trash as an Artistic Act
+% - Act of Transforming Trash in the Context of Art
 %........................................
@@
 
-%\title{Transforming Trash as an Artistic Act}
-%\author{Mustafa İlhan}
-%\maketitle
-
 \pagenumbering{roman}
@@
 
+% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology.
+// The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
+It is questioned the role of art in transformation of discarded items.
+This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
+Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.
+
 \vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory, Throw Away Culture, Handmade Notebooks.
@@
 \begin{abstract}
-
-% Ne, Nasıl, Sonuç.
-
-% Sanatta çöpün yeri inceleniyor, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
+\comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
 Ya da en azından proje kapsamında üretilen işin.
-Ya da bu bağlamda ele alınabileceği iddia edilmektedir.
+Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}
 
@@
 Çöpü dönüştürmenin nasıl ne ne şekilde mümkün olduğu incelenmiştir.
-Sanatsal üretim yöntemi olarak çöpü (tercih etmiş)kullanan sanatçıların yaklaşımları ele alınmıştır.
+Sanatsal üretim yöntemi olarak çöpü (tercih eden) kullanan sanatçıların yaklaşımları ele alınmıştır.
 Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.
 
-% Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
+\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
 Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
-Aynı zamanda bu defter hakim sistemin dışındaki mekanlarda bulunarak (kamusal ortak alan)
+Bu defter hakim sistemin dışındaki mekanlarda konulmuştur.
+(kamusal ortak alan)}
 
-% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir.
+\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir.
 Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
-Hem sanatın dili genişledi hem de objelerin sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı.
+Hem sanatın dili genişledi hem de objeler sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı.
 Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır.
-Çöpü daha iyi anlayabilmek için throw away.
-Çöpün nasıl sanatta yer bulduğu incelenmiştir.
-ve aynı zamanda aslında çöpün ne olduğu sorgulanmıştır.
+Çöpün nasıl sanatta yer bulduğu incelenmiştir.}
 
@@
 Teoriler ve methodlar ele alınmıştır.
-Çöpün ne olduğu sorgulanmaktadır.
+Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kandırılmak amaçlandırılmaktadır.
 

### 2015-11-10 uncategorized.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

@@
 
-% FROM http://stanforddailyarchive.com/cgi-bin/stanford?a=d&d=stanford19920130-01.2.5&e=-------en-20--1--txt-txIN-------#
-% The thing to do is to find some way --- and it can be done, I think, through art --- to enjoy life in its vast multiplicity. --- John Cage
-
-% FROM Wild Art
-% Bu epigraphta aslında şöyle bir sıkıntı var, bir şeyin miktarı artınca daha fazla insanın onun üzerinde düşeceğini varsaymak biraz sıkıntı olabilir.
-% We are going to make a lot more junk, and there is going to be a lot more junk art.
-I think people are going to have a lot to say about it, and more people need to think about it.
---- Jeremy Mayer, quote taken from American Craft Magazine, December/January 2011.
-
 %%%
@@
 
-%%
-%%
-\subsection{What is trash?}
-In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
-Sometimes it is accepted as a problem that is need to carefully and seriously manged.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%%
-%%
-\subsection{Trash is everywhere and, produced every time}
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession.
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
-People cares the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
-
 % TODO PRAP. REF.
-Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-(FROM Trash as Treasure, BY WILLIAM L.
-FASH AND E.
-WYLLYS ANDREWS)
-
-% TODO PRAP. REF.
+% Ne diyor?
 Literature is recycled material, a pretext for making more art.
@@
 
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
-% TODO PRAP. REF.
-We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.
-(BY PAOLA IBARRA)
-
 %%
@@
 \subsection{Cycle of trash}
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
-With the trash what moves?
 
@@
 How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
-
-%%
-%%
-\subsection{How does it become trash?}
-Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
 
@@
 \subsection{Garbology}
-Garbology is a study of waste as a social science.
+Garbology is a study of waste as a social science. applying methodologies of archeology to the human debris.
 
@@
 
-% Binding things together and separating things from each other.
-
 % Cornelia Parker's work, narrate an absent event of waste
@@
 
-%%
-%% TODO sample statements here.
-\subsection{Artist statements}
-\begin{itemize}
-\item I am an artist living in New York City, and my experience of daily life here is both the catalyst for and the subject of my art.
-Working from the local, the personal and the ordinary - the paper take-out coffee cup in the palm of my hand, the view from my studio window in the Garment District, friends and their children, the community garden around the corner from my apartment in Hell's Kitchen - my drawings, paintings and installations are about what happens when the familiar suddenly undergoes a perspective shift and is revealed in all its wonder and infinite possibility.
-With this shift, mundane things become extraordinary, as nodes of rapidly expanding sets of connections, relationships and new artworks.
-
-My approach to art-making is both observational and process-oriented.
-A fascination with cultural, physical and temporal change combined with the possibility of infinite variation unify projects as diverse as drawing and painting on my used coffee cups each day, repeatedly recording the view from my studio in paint and photography over the course of six years, depicting in two and three dimensions the incursion of human activity on the fractal meanders of salt marshes along the New Jersey coast, and painting portraits of alternative families in my New York City neighborhood.
-(from http://gwynethleech.com/)
-\end{itemize}
-
-%%
-%% ACTIVISM as a methodology 
-%% TODO reading...
-\subsection{Art and activism}
-Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.
-
 %*************************************
@@
 Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.)
-\subsection{Crowdsourcing, Participation}
+\subsection{Crowdsourcing, Participation, Open Work}
 % TODO needs reference, FROM Crowdsourced Art and Collective Creativity
@@
 
-% why collaboration, is it really a collaboration?
+% why collaboration, is it really a collaboration? It is methodology used in my practice.
 
-% TODO 
-% Umberto Eco's Open Work
+% TODO: Umberto Eco's Open Work
 
-% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
-% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+%*************************************
+% ARTWORKS:
+% Not all artist transform trash although some deconstruct them.
+Michael Landy is one of them.
+Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
 Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
@@
 breaking down the connections.
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
+%.....................................
 
-% In this thesis project case the issue is not the language of art and its methods.
+%*************************************
+% Solid claims about its cultural aspect.
+\subsection{Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap}
+
+All of them must be paraphrased. Establish connection with the other sections.
+
+\comment{Notes from the book.} They also choose the word recycle.
+(It is hard to say that they use it wrongly, but what they refer is actually upcycling.
+Creative reuse, inventing new things from discard.)
+
+They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
+From western trash to tribal treasure.
+\paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods.
+A disposable item becomes imminent desire and profound social consequence.
+(Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}
+
+They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple tehcnologies, histories and temporalities.
+
+\quote{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance towrd time --- between the past nad the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)}
+
+\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaninf for another.
+Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
+It is story of people abour the women, men, children etc.
+one person's trash into another's treasure.}
+
+\paraphrase{the process of refabrication explored here is not to be confused with the kind of industrial stregth recycling to which we in the West are most accustomed.
+When we think of recycling in America and other industrialized nations we imagine an autometed sequence begining with the curbside disposal of aluminum cans, plastic bottles, and old newspapers.
+returned to the industrial process.
+solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and postconsumer waste recycling.
+}
+
+There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ...
+For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
+It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders
+
+(buraya yerlinin fotoğrafını koymak gerekli.)
+“Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.
+
+\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these essays are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}
+
+While consumption has provided a foundation for the transnatioal captitalist system adntheus has much longer history than the last fifty years this thesis focused on the more recent history.
+because it is during the history of consumption.
+comsumption can be though that as gloabal not to a western or first world countires.
+
+It is not limited with geography, ethinicity, gender, nationaltiy.
+The process of of retrieving and trasnforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban america as well as the remotest corners of amazonian rain forest.
+
+To frame a discussion that incorporates an understanding of such diverse locaions, objects, and peoples is to claim links between material process that originate under vastly different socail, economic, environmental, and political circumstances.
+
+The most obvious link are the raw materials the raw materials themselves: the packaging, broken pieces.
+becomes raw materials for other things.
+these consumer items.
+and it is spreated globally.
+It can be seen remotest corner of the world.
+the indigenization of western objects.
+(sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"?
+Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves.
+They do not necessarily despise our commodities.
+But they are selective in their demands and transformative of their uses of such things.
+(sahlins, 13)"
+
+human manufactured never envisioned possibilieties seen by people.
+It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
+
+This misuse the detritus of the industrial age has been described by western theorist as ironic.
+the irony is often embodied visually and conceptually.
+opposite of natural use, expected perception.
+for example making something from nothing or turning trash into treasure.
+By juxtaposing different materials changing context and place.
+
+\quote{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
+
+when an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown aout as trash.
+.
+
+Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
+The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.
+
+The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifially designed to end up on the garbage heap.
+They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
+This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
+themselves.
+(Waste and wantta bununla ilgili bir bölüm olmalı.)
+
+throwaway spirit (vance packard) Stephen jay gould has observed: "in our world of material wealth where so many broken items are thrown away "
+
+The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
+America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourt world countires.
+(bu ülkeler hangileri onları foot notte açıklayabilirsin.)
+
+while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and trasnformed back into an object of greater or lesser durability.
+
+If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experiencei and they can do so only according to their own principles of existence.
+(sahlins 1992, 16)"
+
+each recycled object contains within it a reference to two or more distinct times.
+
+Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)
+
+recycling as an economic strategy of survival in develoing countries throughout the world.
+creative production that is motivated, primarily, by adverse conditions of economic necessity.
+(lanfill orchestra here.
+bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised.
+(p25)
+
+\subsection{Statistics:}
+The United nations estimates that two percent of the people in cities in nonindustrialized countries make a living from the refuse discarded by the richest ten to twenty percent (germer 1991)

### 2015-11-11 chapter1.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 % Structure of this chapter
-% Section: explain the topic and its significance, raise curiosity, give same facts about it.
+% Section: explain the topic and its significance, raise curiosity, give some facts about it.
 % Section: state the the purpose of this study, specify the focus of it.
@@
 % Section: a note on terminology, clarification about the comprehensive terminology.
+%........................................
 
-\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces.
-I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects.
-My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower.
-But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}
+%****************************************
+% Sample phrases:
+% The discussions (mentioned discussion are also formed the thesis project entitled ... )
+% Aim of this thesis is ...
+% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
+% as a reaction to the consumerist society.
+%........................................
 
-% Bence introductionda çöpün farklı şekillerde ele alınabileceğini bir şekilde göstermek gerekli. Burdaki genel geçer yaklaşımdan bahsetmek gerekli.
+\epigraph{One can even shout out through refuse \ldots}{\hfill---Kurt Schwitters, \textit{Kurt Schwitters}, 1985}
 
-% Ele aldığımız çöp insanların çöpleri, günlük kullanımdaki çöpler. Çok da değerli olmayan yerine yenisi koyabileceğimiz çöpler.
+%****************************************
+% Rubbish: the archaeology of garbage. rathje1992rubbish
+% Garbage project's findings have supplied a fresh perspective on what we know --- and what we think we know --- about certain aspects of our lives. p.24
+
+% The basic methods of garbage disposal are four: dumping it, burning it, turning it into something that can be useful (recycling), and minimizing the volume of material goods.(p.33)
+
+%ancient peoples p.33
+
+%human behavior p.55 can you tell a lot about the customers from their garbage?
+
+%p191-192 people tend to think of "recycling" as a relatively modern conceit that has only recently gained broad public acceptance, and whose practical benefits have only just began to be realized.
+Recycling itself is probably as old as --- indeed, seems to be a fundamental characteristic of --- human species.
+
+%p.209 The reuse of paper, for example, involves processes that generated a considerable amount of hazardous waste.
+In order to recycle newspapers, magazines, and, indeed, any printed paper, the paper must first be de-inked.
+At the end of the de-inking process one is left with essentially two products: on the one hand, de-inked fiber that will be turned into new paper; and on th other, a large quantity of toxic sludge.
+%........................................
+
+%****************************************
+% fast food packaging. p97
+
+%trasformations during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8
+
+% p11. for decades we've taken for granted used cars and old houses. Is there anyone alive who has always lived in new houses or driven only new cars?
+
+% p.11 Economics has always been a factor in recycling.
+
+% p.12 recycling is not limited to folk art.
+
+% Bicycle wheel duchamp 1913.
+
+% Use of recycled materials is not new, not is it exclusive to the united states. p.18
+
+% p.22 Material, meaning, and memory --- these are artists' reasons for using found objects.
+
+% p.48 recycling may be the most wasteful activity in modern America --- a waste of time and money, a waste of human and anutral resources. john tierney, "What a Waste," seattle postintelligencer...
+%........................................
+
+\comment{not shared thing, perception of waste is not static.} \paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
+The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
+Worthless.
+Rejected and useless matter of any kind.
+Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
+Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}}
 
@@
 
-Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible.
-Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them.
-In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated.
-Stages and expression of this practice is examined with my artwork in the context of art.
-
-In previous ages (pre industrial ages?
-which age?) objects and resources are used again and again.
+In previous ages (which age?
+pre industrial ages?) objects and resources are used again and again.
 Production of objects are hard and laborious.
@@
 Primary function is the only function.
-People cares the package of the objects that they buy.
+People do not care the package of the objects that they buy.
 They buy the coffee not the cup of it.
@@
 (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash.
-Live with trash.
-Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
-Can it be possible with art?)
+(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.)
+
+Trash is global, and shared concept for all societies throughout the ages. 
+\textbf{Trash in every age.} In other words it is part of human activity of every historic age.
+It exists early ages of human to now.
+Trash is part of the early days of human production / or activity.
+Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human.
+Legs, bones etc.
+[TODO etymology reference, see appendix] Archaeologist find things from people throw away.
+\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
+\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe(footnotes, satellite discard covers the atmosphere.).
+
+% Introduction of ReVista
+\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
+Yes and no.
+After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
+Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
+No one called it recycling.
+Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
+They can not handle their trash.
+There is no place for trash in their life.
 
@@
 
-% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
-% Konu hakkındaki temel bilgiler.
-% Konunun ele alınan kısmı.
-
-% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir? 
-% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash. 
-People tend to think that trash is values because it is trashed no longer needed or not wanted anymore.
+People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore.
 However is it really values?
@@
 
-% Bu trash in every sıralamasını neden yapıyorum?
-Genel bir çerçeve çizmekten çok aslında evrensel bir konu olduğuna değinmiş oluyorum.
-Peki bu çok açık bir şey mi?
-Yani aslında çok da açık olmayan bilgilerek vererek yaparsam olmayabilir.
-Evrensel olmasının benim için ne önemi var.
-Yaşamımızın bir parçası demek.
-Tamam da buna karşı bir şey mi var.
-Ben göremiyorum açıkcası.
-Herkes bunu biliyor.
-Farkında mıyız.
-Ama farkında olmak istemediğimiz bir şey ki sürekli kendimizden uzaklaştırıyoruz.
-O zaman bu gerçekleri aslında ne kadar biliyoruz.
-Ama bunları bilmek böyle davranmamız gerektiği anlamına mı gelmektedir?
-Aslında yabancı olmadığımız ama uzak durduğumuz bir konu.
-Belki de sırf bu yüzden kaçırdığımız bir sürü şey olabilir.
-
-Trash is global, and shared concept for all societies throughout the ages. 
-\textbf{Trash in every age.} In other words it is part of human activity of every historic age.
-It exists early ages of human to now.
-Trash is part of the early days of human production / or activity.
-Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human.
-Legs, bones etc.
-[TODO etymology reference, see appendix] Archaeologist find things from people throw away.
-\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
-% TODO look introduction of revista, there is a related reference above it.
-\textbf{Trash is everywhere.}
-
 % ARTWORK
-% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuous
+% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.
 
@@
 o fotoğraflarda artık dikkatin objesi haline geliyor.
-çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.
+çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.}
 
@@
 
-% Wall-E belki olabilir.
-Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
-Çöp dağları, çöp denizleri.
-Atılmış binbir türlü nesne.
-ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
-Bundan basetmişken aslında pressleme işi yapan şu cesar.
-Bu şekilde olmak zorunda mı?
-Bunun alternatifi yok mu?
-Aslında bu tezde bunlara cevap bulunabilir.
-Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
-Ya da başka neler var?
-Bunları araştıran inceleyen bir yazı.
-Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
-İnsanlık buna mı dönüşücek?
-Başka bir ihtimal yok mu?
-Gerçekten de dünyayı bekleyen şey bu mu?
-Bir çöp yığını olması mı?
-Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?
-
-WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles giant dozers that moves and piles trash in the landfills.
-This robot creates squeezed trash blocks that have no meaning and interpretation.
-All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
-There are mountains of trash and place is very limited.
-By squeezing them, WALL-E saves space.
-\todo{What is the context of it?
-Which part is related with my topic?} What are we going to do with all these mountains of trash?
-\todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.
-
 % TODO Life time of objects.
@@
 Çöp kovalarının içlerinde neler var.
+Neler yok ki?
+Sanat işleri bile var.
+/ çok hızlı tükettiğimizi aslında chris jordan gösteriyor bize.
+Can you imagine how much plastic cup is being consumed every hour?
 
-\todo{Background information about the thesis. Inspirational points. The fact of trash.}
+\todo{Background information about the thesis. Inspirational points. facts of trash\ldots}
 
@@
 
-% Aga çöpe farklı yaklaşımlar var.
-O yüzden background information olarak burada verilebilir ve scope belirlenebilir.
-Tam da bu noktada ise purpose kısmına geçilebilir.
-Çöpe nasıl yaklaşıyorlar falan filan.
-İşte ben tam da bu noktada sanatta nasıl yaklaşılmıştır dicem.
-Hatta basitçe sanatta bu tür işlere
+This trash phenomena catches the attention of artist.
+It is very human activity.
+In this context which trash?
+What type of discard.
+Human discard.
+trashes of human activity.
+items that belongs to human.
+commodities etc.
 
-\comment{Trash draws attention different peoples and disciplines.
-In other words there are different studies related with trash.
-Different approaches to the trash and son on.
-However in this thesis study trash }
-
-There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.
-
-% Aslında sadece bir heykel işi olan şeylerden bahsedebilirim, ya da aslında belki de içine girip dokunabildiğin bir şey olabilir.
-
-% Savunma.
-% Yani aslında bu chapterdaki fikirler vs.'ler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar.
-
-This trash pheomanan catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Many type of it?
-
-% Idea of everthing can be trash. Act of trashing. not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
+%****************************************
+% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
 % Michael Landy's Art Bin uses a art gallery to create his dust bin.
@@
 
+% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
+%........................................
+
+\todo{ArtBin, trashing things?}
+
+%****************************************
+% Different types of trash
+\todo{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}
+
+The complexity of produced trashes of societies is increasing.
+For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
+Think batteries and so on.
+Every society generates different types of wastes.
+Differs from country to country, society to society, ages to ages.
+It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
+Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
+In other words objects become more complex their re-usage becomes less likely.
+Different production process generates different types of trash.
+According to production process, decomposition process\ldots The approach to the different type of trash will be different.
+In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
+There are some trashes that are more close to the people.
+More easy to convert them.
+more easy to regain to the society.
+%........................................
+
+%****************************************
+% Different disciplines, Perspectives related with trash from different disciplines
+\todo{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines.
+In other words there are different studies related with trash.
+Different approaches to the trash and son on.}
+
+% From Trashion: The Return of Disposed, Bahar Emgin.
+\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.}
+
+This is very important because the problem of trash is being tried to be handled by different disciplines.
+In other words there different approaches to the trash.
+Different problems, different solutions.
+Which perspective that I have.
+In what ways my project differs from them.
+The purpose is to participate people in this work, by collecting them etc.
+And also offer to transform it.
+Rescue it and than later transform it.
+In short, the difference between the other disciplines must be clear.
+\begin{itemize}
+\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
+\item Management of it (handled by the municipals generally).
+\item Technological perspectives.
+(seeing trash as a design problem.
+developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
+development in what sense?)
+\end{itemize}
+%........................................
+
 %%%
@@
 \section{Purpose of the Study}
-
-%****************************************
-% It is a justification of the work. 
-% What is trash? Who does call it trash? 
-% Is it possible to transform it? How? Which methods?
-%........................................
-
 \todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
 
-% Bu söylemeden önce insana böyle bir şeyin mümkün olduğunu anlatmak gerekli.
-Yani aslında transformation of trash diye bir şey var aga demeli.
-Kimler bunu nasıl yapmış.
-Neler var ortalıkta bunlara bakmak gerekli.
-Pres makineleri falan.
-Ama bunu aynı zamanda sanatsal açıdan inceleyenler, sanatsal amaçlarla yapanlar bulunmakta demek gerekli.
 The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.
@@
 
-% Çöpün sanat işlerinde kullanılmasının önemi ne?
-Bunun karşısındaki şey nedir?
-Diğer alanlardaki yaklaşımlar bir şey üretemiyor mu?
-Bu tezin önemi ne?
-Birilerinin bıraktığı boşluğu doldurmak mı?
-Ya da benim yaptığım işin önemi ne?
-
-% Önceki işlere değinmek gerekli.
-Bu alanla ilgili yapılmış.
-Mesela ne var.
-İki tane tez buldum aslında tam da bu konuyla ilgili.
-Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.
-
 As many people are inside the business of transforming trash through craft and so on.
-People on the streets looking for aliminu cans, glass bottles, plastic.
+People on the streets looking for aluminum cans, glass bottles, plastic.
 They collect and sell them to survive.
@@
 
-% How does it become trash?
-Here the purpose is to understand the dynamics that turn objects to trash.
+\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash.
 By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
@@
 Art works are used as a supportive elements for the stated arguments.
-\comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.}
+\comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.} \comment{Sanat eserlerinin tümüyle bir çözümlemesi her yerde yapılamamıştır, konuyla ilgili kısımlarına değinilmiştir.}
 
@@
 
-\comment{First chapter will be about the conceptual framework that I have been working through
-which includes historical and theoretical background.}
+\comment{First chapter will be about the conceptual framework that I have been working through which includes historical and theoretical background.}
 
@@
 
-%****************************************
-% About the thesis statement and focus:
-% Is it too broad?
-% Is it debatable? Is is fact? (Trash is not a end point of objects, there is a life waiting for them?)
-% What is my side? throwing away is required for society to go further? or omitting the tons of possibilities... 
-% Supporting claims?
-% What is my thesis statement? Again same topic... It needs to be solved...
-%........................................
-
-%****************************************
-% Sample phrases:
-% The discussions (mentioned discussion are also formed the thesis project entitled ... )
-% Aim of this thesis is ...
-% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
-% as a reaction to the consumerist society.
-%........................................
-
-%****************************************
-% Some comments
-% Burada önemli olan şey soru veya sorgulanan şey.
-Bu soru projeye yön verecek.
-Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek.
-Tartışmalar ne üzerine olmalı bu durumda?
-% The project aims to what? and what needs to justify what it questions? 
-% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.
-
-% Tipografi ve ideoloji arasında bir ilişki vardır.
-Fotoğrafın geleceği?
-Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir?
-kelime ve imaj arasında bir problem olduğundan bahsediyor.
-Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir.
-Toplum ve çöp nispeten bir problemli bir durum.
-Burada bir dert var.
-Atılan tüketilen manalar var.
-Sanat bunları provoke mi ediyor.
-Peki ya ben ne öneriyorum, yani aslında bir şey önermem mi gerekiyor?
-Sanat ve çöp arasında nasıl bir ilişki vardır?
-Çöp ile diğer nesneler arasında nasıl bir ilişki vardır?
-
-% Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor.
-İş neyi soruyor ise aslında tez de onu soruyor.
-Yapılan işlerle sorulan sorular arasında bir bağlantı var.
-Bu noktada aslında benim işin neyi sorguladığını bulmam gerekli.
-Çöp dönüştürülebilir, sanatsal bağlamda.
-(Çok geniş değil mi abi sanatsal bağlamda demek?
-Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli.
-Çöp sanat işlerine girmiştir.
-Çöp dönüştürmek aslında bir artistic acte dönüşüyor.
-Tezde bunu anlatıyor.
-Aga bu artisctic act dediğin şey de ne oluyor.
-Çöp dönüştürmek ne oluyor?
-
-% Çöpe yeni bir alternatif yaşam üretmek gerekli! Neden böyle düşünüyorsun? Çünkü sürekli çöp üretiyorsun ama bir yandan da bundan dert yanıyorsun. Zizek işte bu konuya el basıyor.
-
-% Aslında hepimiz bir şeyleri dönüştürüyoruz!
-Neden böyle düşüyorsun?
-Örnekleri nelerdir?
-Bricologe bu iddayı destekler mi?
-Nesnleri üretim amaçlarından farklı amaçlar için kullanmak yeni bir şey değil.
-(Ama zaten ben sanat amacıyla kullanılmasından bahsedeceğim.) Belki bunu belirtmek için mantıklı olabilir.
-Ama burada bir farklılık var olamalı.
-Diğerinden ayıran diyeceğim ama öyle bir fark aramamak gerekli bence.
-Sanat o farkı yıkmak için uğraşıp duruyor.
-Belki de bu uğraşa katkısı bu olabilir bu işin.
-Bir şeyleri dönüştürme potansiyellerimiz olduğunu düşünebiliriz.
-Dönüştürme dediğimiz şey aslında hangi noktada açığa çıkıyor.
-Bir ihtiyaç anında, kaçış anında, ya da yeni alternatifler ararken mi?
-
-% Çöpün dönüştürülmesi ne olaki?
-Buna bir şekilde girişte yer vermek gerekli.
-Çöpün market içindeki hareketi mi?
-Ya da aslında çöpün yaşamı.
-Belki de bu olabilir.
-Çöpün nasıl oluştuğu vs.
-Fabrikada üretilmesi.
-İnsanlara dağıtılması.
-Ve sonra çöp olması.
-Çöp dağları oluşması.
-Çöp kutusunda yer alması.
-Neler yok ki çöp kutusunda.
-Bir sanatçı çöp kovasına attığı sanat işleri.
-Sanat işleri çöplükleri vs.
-Çöp kavramı aslında o kadar çok şey için geçerli ki?
-İşte bu çok çeşitli çöp kavramını ele almak gerekli.
-Yani objeler bir şekilde farklı konumlarda mekanlarda yer değiştiriyorlar.
-Bazen çöp oluyorlar bazen değerli vs.
-
-% Bir bir çeşit çöp var.
-Bunlar binbir çeşit davranış sonucunda oluşuyorlar.
-Bir işlemin sonunda ortaya çıkan son ürün.
-Çöp konumuna gelmesi vs.
-Kime göre çöp neye göre çöp.
-Ama işte ortada bir konsensus yok.
-Başkaları da farklı şekilde görüyor.
-Birine göre çöp diğerine göre ise bir hazine.
-
-% Dönüşmek ne oluyor peki bu durumda.
-Bir durumdan başka bir duruma geçmesi.
-Farklı bir anlam, amaç kazanması olabilir mi?
-Mesela pisuvar dönüşmüş müydü?
-Gazeteyi kolajda kullandığım zaman gazeteyi dönüştürmüş mü oluyorum?
-Hangisi dönüştü?
-Zaten buradaki açık bir şekilde açığa çıkıyor aslında.
-Her ikisi de dönüşmüş oluyor.
-Farklı bir kullanım alanı bulmak.
-Farklı niyetlerle kullanmak olabilir belki de.
-Bir şeyin ne zaman dönüştüğünü iddia edebilirsin.
-
-% Agnes varda neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında sanatçıları da geziyor, çünkü onlar da topluyorlar.
-Onlar da o çöplerde farklı şeyler görüyorlar.
-Kendi de mesela çöpe atılmış bir şeye anlam yüklüyor.
-Kendisininde aslında bir toplayıcı olduğunun farkına varıyor.
-
-%****************************************
-% JUSTIFICATION (Gerekçesi)
-% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
-% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
-% - Peki neden bu işi yapıyorsun.
-Alternatifi aramak.
-Değer bulmak, değer bulunabilceğine inanmam aslında.
-Belki de değer üretmek için o değerleri yıkmak gerekli.
-Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur.
-Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman.
-O yüzden çöpe atılması önemli.
-Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir.
-Çöplüğün bir başlangıç olması.
-Batırdığımız bitridiğimiz yerden yeni bir başlangıç.
-Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek.
-Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin.
-% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
-% - Çöp bu sanat işlerinde dönüşmüştür. 
-% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
-%........................................
-
-%****************************************
-% SANATTAKİ KÖKLERİ ÜZERİNE:
-% picasso falan gibi adamların derdi sanata farklı objeleri sokarken ki amaçları ya da değerlendirildikleri nokta farklı bir şeyler yapmaları.
-O dönemki anlayışı yıkmaları.
-Onun yerine daha geniş bir alan imkanı sunmaları.
-Biz şu anda onların açtıkları alandan top koşturuyoruz bir nebze.
-Onların buna yaklaşımları ile bizimkiler arasındaki bazı farklılıklar olacak.
-En azından biz onların yıkları şeyi yıktığımız iddia edemeyiz.
-Çünkü o kalıplar, yaklaşımlar açıldı ve yeni bir üretim alanı insanlara sunulmuş oldu.
-Sorulacak yeni sorular, yapılacak yeni tartışmalar vardı.
-% Yani farklı dönemlerde farklı amaçlarla kullanılmıştır.
-Farklı şekillerde okumak mümkündür.
-Ama benim işime yarayanları seçmek gerekli bunları.
-Bir kısmı için bu sanatın diline yeni bir şey sokması, sanatın alanını genişletmesi, yeni tartışma alanları açması şekilde işime yarayacak.
-Diğerleri ise çöpe ele almaları
-% Ben picassonun sahip olduğu kaygılarla sanat yapmıyorum. Yani ondan bahsetmek ya da sanatın bu işlerdeki köklerinden konuşmak benim için yeterli değil. DAha da fazlasına ihtiyacım var. 
-% Benim kaygılarım ne peki? Ben kime hitap ediyorum, bence burada bir ayrım söz konusu.
-%........................................
+\comment{The final section, procedural description, covers the process of the project from beginning to end.
+The final chapter is reserved for conclusion.
+The overall project is summed up and the significance and the purpose of the project is re-emphasized.}
 
@@
 
+It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard.
+
+% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
+
+\paraphrase{Not all artist transform trash although some deconstruct them.
+Michael Landy is one of them.
+Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
+Reveal all his possessions.
+and loosing them while you are alive.
+Turning them to rubbish making them unusable.
+breaking down the all the meaning.
+breaking down the connections.} It can be an example of downcycling process.
+It is prefered to decompse all the complex link and relationships between the objects.
+They are not just ordinary things they are possessions of artist.
+Break Down 2001, in which he systematically destroyed all his personal possessions.
+His work examines what we value and what we discard, consumerism and waste, and human labour and its worth.
+It happens in public space.
+People can see the process.
+This process last 2 weeks.
+Places where people buy things actually.
+
+\comment{Yıktığı şeyler aslında bir noktada hepimizin yaşayacağı şeyler. Bunu yaşarken yapıyor. Tüm sahip olduklarını yaşarken kendi isteği ile bunların hepsini yok ediyor.}
+
 %****************************************
-% UPCYCLING TERİMİNİ KULLANANLAR.
+% UPCYCLING:
 % Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended
 % Raw+Matrial=Art burda da upcycling deniliyor.
+%
+% RECYCLING:
+% recycled, re-seen book.
 %........................................

### 2015-11-11 chapter2.tex
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 
-% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych
-% http://priscilauppal.ca/books/alphabet-city/
+% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych, http://priscilauppal.ca/books/alphabet-city/
 \epigraph{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
@@
 \section{Throw away culture}
+We need to ask what is the source of trash.
+
 Continuously consuming things and disposing of something.
@@
 %%% Reference from Identity, mobility and the throwaway society
-we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)
+\todo{we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)}
 
@@
 
+Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
+1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ...
+was supplying the customer with hundereds of disposible containers and materials bt the end of the nineteenth century.
+the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."
+
+\todo{throw away sprit}
+
+Industrial age played significant role (engine of the mountains of rubbish.)
+
 % Resource is here: mmmacleo2005.pdf (throw away culture ile ilgili.) (Çünkü ben bunun ürününü kullanıyorum.)
 
-% Bu endüstriye yaklaşım günlük kişisel kullanım eşyarından dağlar yapıyor. Hepsi birisinin aynısı, steril, vs
+% Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.
 
@@
 
+%****************************************
+% Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels. Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+
 % Potraits of Global Mass culture from Chris Jordan.
@@
 “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.”
+
+% Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
+His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits
 
@@
 
+% Chris jordan hem bir gerçeği açığa çıkarıyor. 
+% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.
+%........................................
+
+%****************************************
 % HAKAN GÜRSU
@@
 Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.
-
-% Chris jordan hem bir gerçeği açığa çıkarıyor. 
-% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.
 
@@
 Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.
+%........................................
 
-% Sanat işleri
-% Her çöpünü fotoğraflayan adam.
-
+%****************************************
 % Tracy emin mesela.
@@
 Bu işde bununla ilgili aslında.
-
-% Sanatçıların işlerine bir de bu güzel bakarsak ne görürüz.
+%........................................
 
@@
 Adding spirituality and new aesthetics dimension to the topic.
+
+% Her şey çöpe dönüyor. 
+% En fazla ürettiğimiz şey çöp. Böyle giderse her şey her yer çöp olur mu? Aslında tezin konusu bu değil ve buna cevap verilmeyecektir? Ama WALL_E denilen dizi böyle bir alternatifte geçen bir dizi.
+% İki tane yöntem var birisi bu çöp dağları...
+ve dağlardan ne görüleceği.
+Gerçi vik munizde o dağlara gidenlerden birisi ve oradaki insanlardan portreler yapıyor.
+Çöp dağlarını nasıl görmek gerek, nasıl farklı bir şekilde görebiliriz.
+\comment{Zizekin çizdiği potreden aslında çöp dağlarınan oluşan bir dünya tasavvur edebiliriz.
+Ve bun noktada wall-e'ye bakabiliriz.
+Bir an için çöpümüzün içinde buğulacağımızı düşünürüz.
+Ya da bu çöp dağlarının bizleri sınırladığını düşünebiliriz.}
+
+\comment{WALL-E belki olabilir.
+Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
+Çöp dağları, çöp denizleri.
+Atılmış binbir türlü nesne.
+ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
+Bundan basetmişken aslında pressleme işi yapan şu cesar.
+Bu şekilde olmak zorunda mı?
+Bunun alternatifi yok mu?
+Aslında bu tezde bunlara cevap bulunabilir.
+Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
+Ya da başka neler var?
+Bunları araştıran inceleyen bir yazı.
+Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
+İnsanlık buna mı dönüşücek?
+Başka bir ihtimal yok mu?
+Gerçekten de dünyayı bekleyen şey bu mu?
+Bir çöp yığını olması mı?
+Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?}
+
+\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
+A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
+WALL-E resembles giant dozers that moves and piles trash in the landfills.
+This robot creates squeezed trash blocks that have no meaning and interpretation.
+All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
+There are mountains of trash and place is very limited.
+By squeezing them, WALL-E saves space.
+\todo{What is the context of it?
+Which part is related with my topic?} What are we going to do with all these mountains of trash?
+\todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.}
+
+% HERŞEY ÇÖPE DÖNÜYOR.
+Relationship between entropy (second law of thermodynamics) and waste.
+Resources of nature turns to waste that it can revert it.
+Creating that are reversible again is problematic through the nature of sustainability.
+What is produced after it is consumed become worthless.
+
+% Yani bir çözüm bulmaktan bahsediliyor ama sanat çözüm bulur mu bilmiyorum.
+Zaten derdim de benim aslında tüm bu çöp sorununu ele almak çözmek değil.
+Çöpe olan bakış açısındaki problemi göstermek olabilir.
+Burda beni destekleyen şey zizekin sözleri olacak.
+
+idealization of nature, to love nature is to love trash.
+Live with trash.
+Do not see it as trash actually.
+Then the question is how to love trash?
+how to live with trash?
+can living with our trash enrich (our perceptions, abilities)?
+how not to see them as trash and useless?
+Can it be possible with art?
 
@@
 
-Then next chapter practices in art world. Trash in the context of art. Which purpose and which method.
+Then next chapter discusses the practices in art world in more detail. Trash in the context of art. Which purpose and which method? Approaches of artist.
 
@@
 Burada aslında çöp dediğin şeyin aslında bir şeyin bir sınıflandırma sorunu olduğu ve farklı stateler arasında geçişler yaptığını görebiliriz.
+Çöp evlere değinmek gerekebilir.
 
@@
 
-% Daha detaylısı için ise aslında diğer bölüme yönlendirilebilir.
+Zizek points out wrong opinion about ecology among the society.

### 2015-11-11 chapter3.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 % TODO List motivations of artists and their ideas about junk. Because it reveals the different dimensions of this topic.
+
+% Diğer tezlerde ne diyordu. Bu nasıl bir anlatış biçimi be mustafa. doğru düzgün bir şey yok. Anlatcak olsan birisine böyle mi anlatırsın ha?
 
@@
 
+%****************************************
+% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
+% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
+% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
+\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
+The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
+As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
+%........................................
+
 %%
@@
 Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
+
+% Works of picasso baraque.
 
@@
 
-\begin{blockquote}
+\begin{quote}
 [He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
 His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
-\end{blockquote}
+\end{quote}
 
@@
 
-\begin{blockquote}
+\begin{quote}
 The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
 There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-\end{blockquote}
+\end{quote}
 
-\begin{blockquote}
+\begin{quote}
 The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
@@
 The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-\end{blockquote}
+\end{quote}
 
@@
 The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+
+% Duchamp falan.
 
@@
 \begin{itemize}
-% FROM Maite Zubiaurre, ReVista Garbage
+% FROM Maite Zubiaurre, Re Vista Garbage
 \item \textbf{Road Kill.} Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
@@
 
-% They are continously changing. Unrecognized things. Created unintentionaly. Part of the streets roads. It can be seen as a archieve.
+% They are continuously changing. Unrecognized things. Created unintentionally. Part of the streets roads. It can be seen as a archive.
 
@@
 
-%\item Pictures of Garbage by Vik Muniz
+%\item Pictures of Garbage by Vic Muniz
 \item \textbf{Pictures of Garbage.} Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010) Waste Land, directed by Lucy Walker  tracks the development of a series of monumental photographic portraits made from trash.
@@
 What is specific about trash here?)
+
+% Talking with people picks up trash. Goes to landfill?
 
@@
 
-% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
-%\item Daniel Lind-Ramos
-
 % FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
@@
 
-\item Joseph Cornell
+\item Joseph Cornell, assemblage artist.
 
@@
 %%%
-\section{Discussions}
+\section{Summary}
 Are artworks made from trash just examples of collage and assemblage or more than from them?
@@
 % Buying a beverage is a daily event for \ldots
-% Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives.
+% Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives. The reason of website.
 % “People see that an artist can make work anywhere, and make creative spaces anywhere,” she asserts.
 
-% Trash is as a material or a subject
+% Trash is as a material or a subject. Both of them. Can be traced examples of artworks.
 
@@
 % TODO PRAP. from rethink, reimagine, reinvent
-Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
+\paraphrase{Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
 Assemblage art involves the creation of new and innovative objects from what were once considered objects of waste; that is.
@@
 The transformations of the objects used in assemblage pieces ask viewers to reconsider the notion of "valuable" as they are challenged to look at everyday objects with a new perspective (Taylor, 2006).
-Viewers confront issues relating to the functionality of objects during modern processes of production, consumption and distribution.
+Viewers confront issues relating to the functionality of objects during modern processes of production, consumption and distribution.}
 
-Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
-Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).
+\todo{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
+Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}
 
@@
 
-\section{Summary}
 Artists works and the place of the trash in the art can be summarized as follow:
@@
 Ben de bu tür şeyleri kendi işimde kullanacağım.
+
+\todo{Overview of all artworks. How do they differ from each other in terms of transformation(conceptually, physically), methodology, collecting, composition and so on.}
+
+\todo{a chart here.}

### 2015-11-11 chapter4.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 (Collect, Save, Transform, Spread.)(Rescue, Revive)
+
+% Closest waste bin is actually my own pocket.
 
@@
 Sometimes I collect them from trash bins and roads.
+
+\comment{COLLECTING TRASH.} One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
+What are the dynamics(considerations) of collecting them?
+(easily accessible materials or unique items.) Where to store them?
+Does it mean that live with trash?
+In other words collecting trash and using them is live with them?
+(making them part of life.) After the being part of the are they still trash?
+Can be thought that it is something that affects the lifestyle.
+(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
+What is the driving force?
+You may collect it to prevent object being lost.
+For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
+However, trash is never disappearing, even its amount increasing rapidly.
+For archival things people have memories with them, but does some applies for the trash?
+Who wants to keep trash?
+or who wants to re-see(re-visit) trash again (in a museum for example)?
+
+\todo{What type of collecting? How differs from the others? ragpickers from benjamin and archades project.}
+
 \item \textbf{Transforming.} I turned them to notebooks.
@@
 Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
+
+%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
+But it is very strange that the fat on the paper is previously what they are eat.
 

### 2015-11-11 chapter5.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 \chapter{Conclusion}
+
+%****************************************
+% Savunma.
+% Yani aslında bu tezdeki fikirler, işler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar. 
+%........................................
+
+\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces.
+I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects.
+My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower.
+But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}
 
@@
 again always new discard items are generated.
-
-% Bu bölümde gene toplu bir özet yapılacak. Teker teker argumanlardan bahsedilecek. ve bu argumanlerın yeri belirtilecek.
-
-% O zaman yarın gene tüm yazdıklarımı okuyorum, nasıl birleşeceğine karar veriyorum.

### 2015-11-11 drafts.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

INTRODUCTION

% Bence introductionda çöpün farklı şekillerde ele alınabileceğini bir şekilde göstermek gerekli. Burdaki genel geçer yaklaşımdan bahsetmek gerekli.
% Ele aldığımız çöp insanların çöpleri, günlük kullanımdaki çöpler. Çok da değerli olmayan yerine yenisi koyabileceğimiz çöpler.

% Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible. Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them. In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated. Stages and expression of this practice is examined with my artwork in the context of art.

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.

% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir? 
% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash.

% Bu trash in every sıralamasını neden yapıyorum? Genel bir çerçeve çizmekten çok aslında evrensel bir konu olduğuna değinmiş oluyorum. Peki bu çok açık bir şey mi? Yani aslında çok da açık olmayan bilgilerek vererek yaparsam olmayabilir. Evrensel olmasının benim için ne önemi var. Yaşamımızın bir parçası demek. Tamam da buna karşı bir şey mi var. Ben göremiyorum açıkcası. Herkes bunu biliyor. Farkında mıyız. Ama farkında olmak istemediğimiz bir şey ki sürekli kendimizden uzaklaştırıyoruz. O zaman bu gerçekleri aslında ne kadar biliyoruz. Ama bunları bilmek böyle davranmamız gerektiği anlamına mı gelmektedir? Aslında yabancı olmadığımız ama uzak durduğumuz bir konu. Belki de sırf bu yüzden kaçırdığımız bir sürü şey olabilir.

% Aga çöpe farklı yaklaşımlar var. O yüzden background information olarak burada verilebilir ve scope belirlenebilir. Tam da bu noktada ise purpose kısmına geçilebilir. Çöpe nasıl yaklaşıyorlar falan filan. İşte ben tam da bu noktada sanatta nasıl yaklaşılmıştır dicem. Hatta basitçe sanatta bu tür işlere

%****************************************
% It is a justification of the work. 
% What is trash? Who does call it trash? 
% Is it possible to transform it? How? Which methods?
%........................................

% Çöpün sanat işlerinde kullanılmasının önemi ne? Bunun karşısındaki şey nedir? Diğer alanlardaki yaklaşımlar bir şey üretemiyor mu? Bu tezin önemi ne? Birilerinin bıraktığı boşluğu doldurmak mı? Ya da benim yaptığım işin önemi ne?

% ben bunu konuyu bir eylem olarak mı ele alıyorum.

% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili. Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.

%****************************************
% Some comments
% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda? 
% The project aims to what? and what needs to justify what it questions? 
% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.

% Tipografi ve ideoloji arasında bir ilişki vardır. Fotoğrafın geleceği? Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir? kelime ve imaj arasında bir problem olduğundan bahsediyor. Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir. Toplum ve çöp nispeten bir problemli bir durum. Burada bir dert var. Atılan tüketilen manalar var. Sanat bunları provoke mi ediyor. Peki ya ben ne öneriyorum, yani aslında bir şey önermem mi gerekiyor? Sanat ve çöp arasında nasıl bir ilişki vardır? Çöp ile diğer nesneler arasında nasıl bir ilişki vardır?

% Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor. İş neyi soruyor ise aslında tez de onu soruyor. Yapılan işlerle sorulan sorular arasında bir bağlantı var. Bu noktada aslında benim işin neyi sorguladığını bulmam gerekli. Çöp dönüştürülebilir, sanatsal bağlamda. (Çok geniş değil mi abi sanatsal bağlamda demek? Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli. Çöp sanat işlerine girmiştir. Çöp dönüştürmek aslında bir artistic acte dönüşüyor. Tezde bunu anlatıyor. Aga bu artisctic act dediğin şey de ne oluyor. Çöp dönüştürmek ne oluyor?

% Çöpe yeni bir alternatif yaşam üretmek gerekli! Neden böyle düşünüyorsun? Çünkü sürekli çöp üretiyorsun ama bir yandan da bundan dert yanıyorsun. Zizek işte bu konuya el basıyor.

% Aslında hepimiz bir şeyleri dönüştürüyoruz! Neden böyle düşüyorsun? Örnekleri nelerdir? Bricologe bu iddayı destekler mi? Nesnleri üretim amaçlarından farklı amaçlar için kullanmak yeni bir şey değil. (Ama zaten ben sanat amacıyla kullanılmasından bahsedeceğim.) Belki bunu belirtmek için mantıklı olabilir. Ama burada bir farklılık var olamalı. Diğerinden ayıran diyeceğim ama öyle bir fark aramamak gerekli bence. Sanat o farkı yıkmak için uğraşıp duruyor. Belki de bu uğraşa katkısı bu olabilir bu işin. Bir şeyleri dönüştürme potansiyellerimiz olduğunu düşünebiliriz. Dönüştürme dediğimiz şey aslında hangi noktada açığa çıkıyor. Bir ihtiyaç anında, kaçış anında, ya da yeni alternatifler ararken mi?

% Çöpün dönüştürülmesi ne olaki? Buna bir şekilde girişte yer vermek gerekli. Çöpün market içindeki hareketi mi? Ya da aslında çöpün yaşamı. Belki de bu olabilir. Çöpün nasıl oluştuğu vs. Fabrikada üretilmesi. İnsanlara dağıtılması. Ve sonra çöp olması. Çöp dağları oluşması. Çöp kutusunda yer alması. Neler yok ki çöp kutusunda. Bir sanatçı çöp kovasına attığı sanat işleri. Sanat işleri çöplükleri vs. Çöp kavramı aslında o kadar çok şey için geçerli ki? İşte bu çok çeşitli çöp kavramını ele almak gerekli. Yani objeler bir şekilde farklı konumlarda mekanlarda yer değiştiriyorlar. Bazen çöp oluyorlar bazen değerli vs.

% Bir bir çeşit çöp var. Bunlar binbir çeşit davranış sonucunda oluşuyorlar. Bir işlemin sonunda ortaya çıkan son ürün. Çöp konumuna gelmesi vs. Kime göre çöp neye göre çöp. Ama işte ortada bir konsensus yok. Başkaları da farklı şekilde görüyor. Birine göre çöp diğerine göre ise bir hazine.

% Dönüşmek ne oluyor peki bu durumda. Bir durumdan başka bir duruma geçmesi. Farklı bir anlam, amaç kazanması olabilir mi? Mesela pisuvar dönüşmüş müydü? Gazeteyi kolajda kullandığım zaman gazeteyi dönüştürmüş mü oluyorum? Hangisi dönüştü? Zaten buradaki açık bir şekilde açığa çıkıyor aslında. Her ikisi de dönüşmüş oluyor. Farklı bir kullanım alanı bulmak. Farklı niyetlerle kullanmak olabilir belki de. Bir şeyin ne zaman dönüştüğünü iddia edebilirsin.

% Agnes varda neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında sanatçıları da geziyor, çünkü onlar da topluyorlar. Onlar da o çöplerde farklı şeyler görüyorlar. Kendi de mesela çöpe atılmış bir şeye anlam yüklüyor. Kendisininde aslında bir toplayıcı olduğunun farkına varıyor.

%****************************************
% JUSTIFICATION (Gerekçesi)
% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
% - Peki neden bu işi yapıyorsun. Alternatifi aramak. Değer bulmak, değer bulunabilceğine inanmam aslında. Belki de değer üretmek için o değerleri yıkmak gerekli. Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur. Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman. O yüzden çöpe atılması önemli. Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir. Çöplüğün bir başlangıç olması. Batırdığımız bitridiğimiz yerden yeni bir başlangıç. Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek. Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin. 
% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
% - Çöp bu sanat işlerinde dönüşmüştür. 
% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
%........................................

%****************************************
% SANATTAKİ KÖKLERİ ÜZERİNE:
% picasso falan gibi adamların derdi sanata farklı objeleri sokarken ki amaçları ya da değerlendirildikleri nokta farklı bir şeyler yapmaları. O dönemki anlayışı yıkmaları. Onun yerine daha geniş bir alan imkanı sunmaları. Biz şu anda onların açtıkları alandan top koşturuyoruz bir nebze. Onların buna yaklaşımları ile bizimkiler arasındaki bazı farklılıklar olacak. En azından biz onların yıkları şeyi yıktığımız iddia edemeyiz. Çünkü o kalıplar, yaklaşımlar açıldı ve yeni bir üretim alanı insanlara sunulmuş oldu. Sorulacak yeni sorular, yapılacak yeni tartışmalar vardı. 
% Yani farklı dönemlerde farklı amaçlarla kullanılmıştır. Farklı şekillerde okumak mümkündür. Ama benim işime yarayanları seçmek gerekli bunları. Bir kısmı için bu sanatın diline yeni bir şey sokması, sanatın alanını genişletmesi, yeni tartışma alanları açması şekilde işime yarayacak. Diğerleri ise çöpe ele almaları 
% Ben picassonun sahip olduğu kaygılarla sanat yapmıyorum. Yani ondan bahsetmek ya da sanatın bu işlerdeki köklerinden konuşmak benim için yeterli değil. DAha da fazlasına ihtiyacım var. 
% Benim kaygılarım ne peki? Ben kime hitap ediyorum, bence burada bir ayrım söz konusu.
%........................................

%****************************************
% About the thesis statement and focus:
% Is it too broad?
% Is it debatable? Is is fact? (Trash is not a end point of objects, there is a life waiting for them?)
% What is my side? throwing away is required for society to go further? or omitting the tons of possibilities... 
% Supporting claims?
% What is my thesis statement? Again same topic... It needs to be solved...
%........................................

### 2015-11-11 todo.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

TODO:
- Susan Strasser, Waste and Want
- TODO life time of objects
- TODO Grammarly ile tüm cümleleri ve kelimeleri gözden geçir.
- artworks???

cerny1996recycled, herman1998trashformations, rathje1992rubbish

Amaç belirsiz olan şeyleri olabildiğince belirgin hale getirmek. Bir düzen oturtmaya çalışmak.
En azından neler yazılmalı, neler eklenecek onları belirlemeli. Hangi artworkler hangi işler olmalı.

Today's TODO:
- Anotate all pharagraphs. (Konuya dair tüm fikirler bir ortaya serilsin. İlişkiler kurmanın yolu açılsın.) (öğlene kadar.)
- Diğer bölümlerde neler eksikse onlar not edilmeli. Notlar alınmalı. Nasıl bir düzen olacağı belirlenmeli.
- Referansları elden geçirmeli. Tüm yazarlar kitaplar belirlenmeli, sıkıntılı olanlar not alınmalı.
- Sanatçı işlerinin eklenmesi (akşama kadar.)
- (Çıktı almalı. Kütüphaneden kitap alınacaktı daha!)

Tomorrow's TODO:
- Tüm yazıların üzerinden geçme, olabildiğince paraphrase etmeli. Eksik bölümler doldurulmalı.
- Hocaya yazı göndermeli...

Çarşamba, Perşembe, Cuma, Cumartesi, Pazar...

ARTWORK için:
- Bilkentten kağıt alınacak? iş bankasından kağıt alınacak?
- Defterlerin içine ne yazmak gerek?
- Milli Kütüphane? Torun?
- Torun gibi bir mekana defterleri nasıl yerleştirebilirsin?

--------
- Siteye bir göz at, belki lorem ipsumlar yerine bir şeyler yazarsın.
- Torun'a, Tatbikat Sahnesine mail at.
- Jüri üyesi aramak gerekli.

TODO:
- Çöple ilgilenen disiplinler nelerdir? Konuya nasıl yaklaşmışlar. Birer cümle gerekli.
- Çöp hakkında istatiski verilere ihtiyaç var.
- Farklı türde çöpler nelerdir? Birer cümle gene.
- Waste and Technology relationship.
- John Scanlan's book, On Garbage.
- Artistic Act.
- Garbology: Our Dirty Love Affair With Trash, Edward Humes
- Hawkins and Muecke, Culture and Waste

### 2015-11-11 uncategorized.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

@@
 %****************************************
-% EPIGRAPH:
-% How to cite epigraph http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
+% RESOURCES:
+%
+% Plagiarism check: http://mashable.com/2012/08/29/plagiarism-online-services/
+% What is Plagiarism: http://www.plagiarism.org/plagiarism-101/what-is-plagiarism
+%
+% How to cite epigraph: http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
+%
+% Artist ve artist statementlar için kaynak:
+% - http://www.amandadonahue.com/artist-statement/
+% - http://www.smfa.edu/cyclo-show
+% - http://www.gwynethleech.com/statement
+%........................................
+
+%**************************************
+% HERE Same sample phrases are listed you can use them:
+
+% The work that follows is divided into three sections
+
+% The artist thinks, acts, performs music, and writes outside the framework that society has created.
+
+% This thesis takes a rather different approach to the resonant possibilities of discarded things.
+It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
+
+% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
+
+% I’d like to criticize a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
+
+% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
+
+% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.
+%........................................
 
@@
 % TODO PRAP. REF.
-% Ne diyor?
-Literature is recycled material, a pretext for making more art.
+% FROM Recycle the Classics, BY DORIS SOMMER
+% Her alanda recycling var olabilir, literatürde de vardır?
+\todo{WHAT, WHERE?} Literature is recycled material, a pretext for making more art.
 I learned this distillation of lots of literary criticism in workshops with children.
@@
 For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
-(FROM Recycle the Classics, BY DORIS SOMMER)
 
-%%
-%%
-\subsection{Cycle of trash}
+\comment{MOVES} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{reference}
+
+\comment{MOVES} \paraphrase{Objects moves around and their values change constantly.
+(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
+The Social Life of Things: Commodities in Cultural Perspective)}\todo{reference, resource?}
 
 % Like a summary sentence
-Here the important thing is moving nature of trash.
+\comment{TRASH MOVES.} Here the important thing is moving nature of trash.
 Objects moves and gains different meanings through this movement.
@@
 % <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-Below part Explains journey of trash, its different steps.
+\comment{TRASH MOVES.} \paraphrase{Below part Explains journey of trash, its different steps.
 Object moves and also trash also moves.
@@
 Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.
-[PRAP, REF Maite Zubiaurre]
+Also in the later parts it draws attention to them.}
 
-Trash moves, all the time.
+% Ama çöp olarak zaten kalmıyor bu trash bir şekilde hayatımıza tekrar giriyor.
+Ne kadar itise de...
+Trashion: the return of disposed.
+trash moves.
+Peki geri dönüşü nasıl bir değişiklik yaratıyor.
+Ya da gerçekten geri geliyor mu?
+Kullandığımız ürünlerin ne kadarı tek kullanımlık.
+Tek kullanımlıklarla nerede karşılaşıyoruz.
+Evet belki hayatımızda çok kullanılan şeyler var fakat.
+daha tek kullanımlıklar da var denilebilir.
+\comment{TRASH MOVES.} \paraphrase{Trash moves, all the time.
 It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
@@
 In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And
-thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”) [PRAP, REF Maite Zubiaurre]
+\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
+(through the works of Filomena Cruz's photographic series “Road Kill”)}
 % >
 
-%%
-%%
-\subsection{Perspectives related with trash from different disciplines}
-This is very important because the problem of trash is being tried to be handled by different disciplines.
-In other words there different approaches to the trash.
-Different problems, different solutions.
-Which perspective that I have.
-In what ways my project differs from them.
-The purpose is to participate people in this work, by collecting them etc.
-And also offer to transform it.
-Rescue it and than later transform it.
-In short, the difference between the other disciplines must be clear.
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it (handled by the municipals generally).
-\item Technological perspectives.
-(seeing trash as a design problem.
-developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-development in what sense?)
-\end{itemize}
-
-% Sample sentence:
-% Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture
-
-\quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
+\todo{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
 In other word the problem is our technology which is not perfect.
@@
 
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
-There is no place for trash in their life.
-
-\quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
+% WHO OWNS TRASH?
+kısmı benim işimde sorgulanabilir, ya da ünlülerin trashlerini inceleyen adam kısmında ele alınabilir.
+Orada aslında başkalarının trashlerinin insanlar hakkında neler anlattığını çok güzel anlıyoruz.
+\todo{ANALOGY Between landfill and graveyards.
+WHOSE TRASH?} \quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
 \quotes{What is happening to trash is what is going to happen to us.
@@
 
-%%
-%%
-\subsection{Types and Comparison of trashes}
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-
-Different production process generates different types of trash. According to production process, decomposition process\ldots
-
-The approach to the different type of trash will be different.
-In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
-There are some trashes that are more close to the people.
-More easy to convert them.
-more easy to regain to the society.
-
-%%
-%%
-\subsection{What is wrong with trash?}
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+\todo{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
 There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
@@
 % TODO Reference
-John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+\todo{WHAT?} John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
 He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
 
-%%
-%%
-\subsection{Collecting trash}
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
-
-[TODO: ragpickers from benjamin and archades project.]
-
-%%%
-%%%
-%%%
-\subsection{Literature review, discussions, ideas\ldots}
-Trash art is not collage (assemblage or found object) or fragments.
-it is more than that.
-The carried messages through the medium have different meaning.
-It has relationship with activism, craftivism.
-It refuses consumption based life cycle.
-It suggests a life practice.
-
-"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}
-
-%%
-%%
-\subsection{Culture, Values, and Garbage}
-"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
+% FROM Culture, Values, and Garbage, Encyclopedia 
+\comment{INTERACTION WITH GARBAGE.
+VALUE SYSTEM, DECIDING TO GARBAGE.} \paraphrase{"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
 In terms of their relationship to garbage, all people interact with it on two levels.
@@
 The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}
+The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}
 
-%%
-%%
-\subsection{Garbage in Modern Thought}
-"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
+% FROM Garbage in Modern Thought, Encyclopedia
+\comment{THROW AWAY CULTURE.} \paraphrase{"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
 It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}
+Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
 
-%
-\subsubsection{Categorization and Value}
-"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
+% FROM Garbage in Modern Thought, Encyclopedia
+\comment{CATEGORIZATION.} \paraphrase{"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
 Consumers have become accustomed to the categories that are often applied to garbage.
 Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}
+Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}}
 
-"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
+% Garbage is universal, reference
+\comment{NO VALUE, UNIVERSAL} \paraphrase{"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
 Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
@@
 Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}
+People define what is trash and what is valuable." \cite{lukas2012garbage}}
 
-%
-\subsubsection{Semiotic Context}
-"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}
+% Hepsinin ayrı bir manası olması falan.
+\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
 
-%%
-%%
-\subsection{Garbology}
-Garbology is a study of waste as a social science. applying methodologies of archeology to the human debris.
+% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
+\comment{GARBOLOGY} Garbology is a study of waste as a social science.
+Applying methodologies of archeology to the human debris.
+\todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
 
-"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}
-
-"The field of garbology involves the study of refuse and waste.
+% Garbology, from Encyclopedia, Abhijit Roy
+\paraphrase{"The field of garbology involves the study of refuse and waste.
 It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
@@
 Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."
-
-In his book “Garbology: Our Dirty Love Affair With Trash”, the Pulitzer prize-winning author Edward Humes notes that other wealthy countries with high living standards have rejected the disposable products that make up much of America's rubbish.
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}
 
 % Rubbish: The Archeology of Garbage, p.24
-As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
-THe Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
-(example of Medical researches)
+\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
+The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
+(example of Medical researches)} \todo{reference}
 
-%%
-%%
-\subsection{Trash as History/Memory}
-% TODO From encylopedia
-\cite{bullock2012trash}
+\todo{read resource (Trash as History/Memory) \cite{bullock2012trash}}
 
-%%
-%%
-\subsection{Trash Aesthetics}
-%Walter Benjamin's trash aesthetics and Adornos reflection. 
-\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
+% Walter Benjamin's trash aesthetics and Adornos reflection? Bu konudan ben hiç bir şey anlamadım açıkcası. Çünkü ne dedikleri ne yaptıkları hiç belli değil.
+\todo{BU NE OLACAK?
+NEREYE BAGLANACAK, GARBOLOGY??}\paraphrase{\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
 Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
 In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday.
-The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.
-
-%**************************************
-% HERE Same sample phrases are listed you can use them:
-
-% The work that follows is divided into three sections
-
-% The artist thinks, acts, performs music, and writes outside the framework that society has created.
-
-% this thesis takes a rather different approach to the resonant possibilities of discarded things.
-It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
-
-% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
-
-% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
-
-% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
-
-% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.
-
-%*******************************************************************
-% FROM The Ruin and the Ruined in the Work of Kurt Schwitters.
-% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality
-
-\subsection{Discussions}
-Objects moves around and their values change constantly.
-(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
-The Social Life of Things: Commodities in Cultural Perspective)
-
-Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)
+The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.}
 
 % FROM Trashion: The Return of the Disposed by Bahar Emgin
-In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
-This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trashcan in the form of waste.
-In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
+\comment{LIFE AN OBJECT} \paraphrase{In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
+This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
+In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
-Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
-% Prap. same source...
-% On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” 9 Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
+\comment{TECHNICAL PROBLEM, NEED TO MANAGED, RECYCLING (CAPITALISM), UPCYCLING} \paraphrase{On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
 The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
-10 Waste now became evil.
+Waste now became evil.
 If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
-11 Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” 12 Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
+Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
 Upcycling...
@@
 Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
-16 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
-In short, there is a whole sector of upcycling now.
+In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
+In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
-% Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
-People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
+\comment{DESIGN, ALTERNATIVE DICIPLINE.} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
-% There is commodity aspect of it and also the process of accommodation.
-In this process design plays a significant role.
-Trash is waiting to be discovered.
-At the same time forgotten styles are also used in works.
-Therefore actually trash and forgotten styles can be considered in the same status.
+% Trash is waiting to be discovered. At the same time forgotten styles are also used in works. Therefore actually trash and forgotten styles can be considered in the same status.
 
-% This can be sample thesis statement sentence:
-% This article is about those objects that are recreated from trash through the process of upcycling.
-Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” 4 I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of.
+\comment{UPCYCLING, sample thesis statement sentence} \paraphrase{This article is about those objects that are recreated from trash through the process of upcycling.
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of.} \todo{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}
 
-% From The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
-
-% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
-\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
-As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
-
-% FROM Waste by William Viney
-Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+\comment{CATEGORIZATION OF WASTE} \paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
 (Think that the transformation process.
@@
 In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
-For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.
-(from William Viney)
+For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.} \todo{Reference, (Waste by William Viney).}
 
-% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
-Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.
+\comment{CATEGORIZATION OF WASTE} \paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
 
-%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.
+\comment{CATEGORIZATION OF WASTE} \comment{susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
+Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
+Remember the example given: shoes  on the dinner table.}
 
-% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.
-
-% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
-Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
-Remember the example given: shoes  on the dinner table.
-
-% King Lear, feeling of waste
-
-% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.
-
-% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
+\comment{CATEGORIZATION OF WASTE} \paraphrase{waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
 
@@
 % There is also strong relationship with the collecting discarded stuff and archeologies of waste.
-%%% Reference
-% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
-% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
-In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
-Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
-The thesis, however, lacks depth and provenance.
-It is, actually, glib.
-Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.
+
+% King Lear, feeling of waste ???
 
@@
 \section{In Art}
+
+% Crowdsourcing artworkümde neden insanlardan topladığımı, neden onları kullanıdığımı anlatacağım yer ile ilgili olabilir.
 
@@
 % ARTWORKS:
-% Not all artist transform trash although some deconstruct them.
-Michael Landy is one of them.
-Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
-Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
-Reveal all his possessions.
-and loosing them while you are alive.
-Turning them to rubbish making them unusable.
-breaking down the all the meaning.
-breaking down the connections.
+
+% Dark Matter: Explosive View.
+
 %.....................................
@@
 \subsection{Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap}
-
-All of them must be paraphrased. Establish connection with the other sections.
-
-\comment{Notes from the book.} They also choose the word recycle.
-(It is hard to say that they use it wrongly, but what they refer is actually upcycling.
-Creative reuse, inventing new things from discard.)
-
-They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
+\todo{Reference.}
+\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
 From western trash to tribal treasure.
@@
 
-They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple tehcnologies, histories and temporalities.
+\comment{HYBRIDITY} They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
 
-\quote{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
-Recycling always implies a stance towrd time --- between the past nad the present --- and often a perspective on cultures --- one's own and others.
-(Jacknis 1992)}
+\comment{SEMIOTIC CONTEXT} \quotes{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)} \todo{reference}
 
-\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaninf for another.
+\comment{HYBRIDITY} \paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another.
 Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
-It is story of people abour the women, men, children etc.
+It is story of people --- the women, men, children etc.
 one person's trash into another's treasure.}
 
-\paraphrase{the process of refabrication explored here is not to be confused with the kind of industrial stregth recycling to which we in the West are most accustomed.
-When we think of recycling in America and other industrialized nations we imagine an autometed sequence begining with the curbside disposal of aluminum cans, plastic bottles, and old newspapers.
+\comment{OTHER DICIPLINE, INDUSTRY} \paraphrase{the process of re fabrication explored here is not to be confused with the kind of industrial strength recycling to which we in the West are most accustomed.
+When we think of recycling in America and other industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers.
 returned to the industrial process.
-solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and postconsumer waste recycling.
-}
+solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.}
 
-There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ...
+\comment{DIFFERENT SCALES OF RECYCLING} There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ...
 For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
@@
 
-(buraya yerlinin fotoğrafını koymak gerekli.)
-“Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
-In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.
+\todo{yerlinin fotoğrafı}
+\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{reference}
 
-\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these essays are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+\comment{CONSUMER CULTURE} \paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these essays are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
 In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}
 
-While consumption has provided a foundation for the transnatioal captitalist system adntheus has much longer history than the last fifty years this thesis focused on the more recent history.
+\comment{CONSUMER CULTURE, SORUCE OF TRASH} While consumption has provided a foundation for the transnational capitalist system adntheus has much longer history than the last fifty years this thesis focused on the more recent history.
 because it is during the history of consumption.
-comsumption can be though that as gloabal not to a western or first world countires.
+consumption can be though that as global not to a western or first world countries.
 
-It is not limited with geography, ethinicity, gender, nationaltiy.
-The process of of retrieving and trasnforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban america as well as the remotest corners of amazonian rain forest.
+\comment{GLOBAL} It is not limited with geography, ethnicity, gender, nationality.
+The process of of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of amazonian rain forest.
 
-To frame a discussion that incorporates an understanding of such diverse locaions, objects, and peoples is to claim links between material process that originate under vastly different socail, economic, environmental, and political circumstances.
-
-The most obvious link are the raw materials the raw materials themselves: the packaging, broken pieces.
+\comment{GLOBAL, SELECTING COMMODOTIES, } To frame a discussion that incorporates an understanding of such diverse locations, objects, and peoples is to claim links between material process that originate under vastly different social, economic, environmental, and political circumstances.
+\ldots The most obvious link are the raw materials the raw materials themselves: the packaging, broken pieces.
 becomes raw materials for other things.
@@
 
-human manufactured never envisioned possibilieties seen by people.
+\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
 It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
 
-This misuse the detritus of the industrial age has been described by western theorist as ironic.
+\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
 the irony is often embodied visually and conceptually.
@@
 
-\quote{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
+\quotes{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
 
-when an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
-Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown aout as trash.
-.
+\comment{Karşı çıktığım şeylerden birisi objelerin ilk manaları, ilk kullanım alanları.
+many scholar stated the general attitude in the society.
+It is key ingredients of throw away society.
+initial function is fulfilled by }
 
-Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+\comment{How does it become trash?, initial function.} when an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
+
+\comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
 As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
@@
 
-The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifially designed to end up on the garbage heap.
+\comment{Capitalism, market.} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
 They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
@@
 themselves.
-(Waste and wantta bununla ilgili bir bölüm olmalı.)
+\todo{Waste and wantta bununla ilgili bir bölüm olmalı.}
 
-throwaway spirit (vance packard) Stephen jay gould has observed: "in our world of material wealth where so many broken items are thrown away "
+\comment{throwaway culture} throwaway spirit (vance packard) Stephen jay gould has observed: "in our world of material wealth where so many broken items are thrown away "
 
-The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
-America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourt world countires.
+\comment{Social classification, throw away culture, place in society.} The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
+America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.
 (bu ülkeler hangileri onları foot notte açıklayabilirsin.)
 
-while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
-Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and trasnformed back into an object of greater or lesser durability.
+\comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.
 
-If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experiencei and they can do so only according to their own principles of existence.
+\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
 (sahlins 1992, 16)"
 
-each recycled object contains within it a reference to two or more distinct times.
+\comment{hybrid} each recycled object contains within it a reference to two or more distinct times.
+\comment{not every time actually, if you transfor ok.
+it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{reference}
 
-Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)
-
-recycling as an economic strategy of survival in develoing countries throughout the world.
+\comment{Economic conditions forces to people recycle and reuse.
+but even if they have no economical struggle, they continue recycle.
+what is the reason of it.} Recycling as an economic strategy of survival in develoing countries throughout the world.
 creative production that is motivated, primarily, by adverse conditions of economic necessity.

### 2015-11-22 appendix_materials.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

\appendix
\chapter{Examples of collected materials}

### 2015-11-22 chapter1.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 
-\comment{not shared thing, perception of waste is not static.} \paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
+Common perception to the trash is to get rid of it as soon as possible.
+People want to depose trash from their lives most of time not thinking beyond.
+However to establish solid understanding of trash, we have to give attention to the trash and ask why it is trash?
+How does it become trash?
+
+\paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
 The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
@@
 Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}}
+Our trash is part of us, whether or not we choose to acknowledge it.
+\todo{ref for tracey emin et al.}" \cite{zimring2012encyclopedia}}
 
 In this thesis work to understand the different aspects of trash is a key element.
-Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here).
+\todo[inline]{This aspects are \ldots} As scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
 Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
 On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)).
+(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?) or aspects).
 Therefore we should ask these questions: What is trash?
@@
 
-In previous ages (which age?
+%\comment{In previous ages (which age?
 pre industrial ages?) objects and resources are used again and again.
 Production of objects are hard and laborious.
-\comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur.
+Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur.
 Mendillere bunlara örnek olabilir.
 Aslında tam benim konumla ilgili çünkü tek kullanımlık.
-Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}
+Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.
+Peki burda illaha geçmişe falan girmek gerek var mı?
+çok mu derdimde benim?}
+
+%\comment{Dört bir yanımız metalarla çevrilmş durumda, istediğimiz şeylere çok kolay bir şekilde ulaşabiliyoruz.
+Yemek siparişi veriyoruz ayağımıza geliyor.
+İki blok ötedeki kahveciden istediğimiz zaman kahvemizi alıyoruz.
+Ama tüm bunların bir bedeli var.
+Bir yandan da sürekli olarak çöp üretiyoruz.
+Her ne kadar son derece sistemli bir şekilde çöpler toplanıyor ve belki de ne kadar tüketildiğini hiçbir zaman farkına var mıyoruz?}
 
@@
 Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It's a common object category that all people share its possession (It is experienced by everybody.).
-During daily activities trash is generated and people get rid of them by throwing away.
-(Various objects become trash after their primary functions daily.
-Who defined the primary function?
-Primary function is the only function.
+It is experienced by everybody, part of the production of garbage.
+During daily activities trash is generated and people get rid of them by throwing away as quickly as possible.
+(Various objects become trash after their primary functions consumed.
 People do not care the package of the objects that they buy.
@@
 After coffee finished the life of cup also finishes.
-There is a lifetime defined (or forecast) by the producer of objects.
+Very small life.
+But is that really so?
+Is that really life of an object ends after tossed on the waste bin?
+\todo[inline]{No.
+Rubbish theory says opposite of it.} (some of the garbage live more from us.
+we use it 5minutes it will still exist years.) There is a lifetime defined (or forecast) by the producer of objects.
 However it is not bound to the producer, also consumer play an important role.
@@
 % Introduction of ReVista
-\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme.
-Yes and no.
-After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
+\paraphrase{After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
 Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
 No one called it recycling.
-Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
+Trash was to be used and used again.} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
 They can not handle their trash.
 There is no place for trash in their life.
+\todo[inline]{herkes için bu geçerli değil yani o zaman ilk baştaki yere referans veriyoruz.}
 
@@
 % TODO PRAP. REF.
-\todo{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+\todo[inline]{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
+\textbf{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.} The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
 OECD countries produce almost half of the world’s waste.
@@
 % TODO PRAP. REF.
-\paraphrase{We relate to garbage daily.
+\paraphrase{\textbf{We relate to garbage daily.
 We use it, produce it and dispose of it.
 Endlessly.
-The most obsessive of us get rid of it as fast as we can.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
+The most obsessive of us get rid of it as fast as we can.} The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
 We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
@@
 It exits from your life but not the world.
-What happens when you throw away a It is stacked from another place.
+What happens when you throw it away?
+It is stacked from another place.
 Value of objects are not static.
-Trash is not static also It has a long journey.
-A project conducted by MIT researches journey of trash by placing trackers onto the trash.
+Trash is not static \todo[inline]{ilk paragrafa referans} also it has a long journey.
+A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}.
 The results are surprising.
 Trashes spread away across the country and this journey takes month.
-\todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}.
+\todo[inline]{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
 In other worlds Americans trash is not only their trash.
@@
 What happens when it is traveled to the other countries, how they approaches these items.
-\comment{They find new uses and meanings on them.} \todo{consider Papua genen people}
+\comment{They find new uses and meanings on them.} \todo[inline]{consider Papua genen people}
+
+\begin{quote}
+\paraphrase{“Nobody wonders where, each day, they carry their load of refuse.
+Outside the city, surely; but each year the city expands, and the street cleaners have to fall farther back.
+The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter” – Italo Calvino, Invisible Cities} The project is an initial investigation into understanding the 'removal-chain' in urban areas and it represents a type of change that is taking place in cities: a bottom-up approach to managing resources and promoting behavioral change through pervasive technologies.
+TrashTrack builds on previous work of the SENSEable City Lab in its exploration of how the increasing deployment of sensors and mobile technologies radically transforms how we understand and describe cities.
+“People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.”
+\end{quote}
 
@@
 From garbage baskets to sculptures.
-[REF.
-MIT Garbage project] Lots of different people touches to trash.
+\todo[inline]{REF.
+MIT Garbage project} Lots of different people touches to trash.
 With the trash what moves?
 
-Even if people pay little attention, everybody do not.
+%http://timgaudreau.com/2012/trash/trash.html
+\comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not.
 An artist takes photos of his every trash, like people take photos of their faces.
@@
 Most of them we are not aware of them.
-Draw the attention of is being thrown away and everytime and everywhere.
+Draw the attention of is being thrown away and every time and everywhere.
 They are too much and can only fit covering all the walls.
-\todo{artist}
+\todo[inline]{Tim Gaudreau “Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006”} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
+These collections of grids represent my first experiments with using those images.
+This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
 
-% ARTWORK
-% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.
+% ARTWORK http://www.keaggy.com/chairs/sad/12/
+\todo[inline]{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
 
@@
 
-\todo{Background information about the thesis. Inspirational points. facts of trash\ldots}
-
 % Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti. 
@@
 
-\todo{ArtBin, trashing things?}
+\todo[inline]{ArtBin, trashing things?, squuezzing, wall-e}
+
+%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
+\todo[inline]{showing them as they are, Barry Rosenthal}
 
@@
 % Different types of trash
-\todo{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}
+\todo[inline]{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}
 
@@
 % Different disciplines, Perspectives related with trash from different disciplines
-\todo{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines.
+\todo[inline]{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines.
 In other words there are different studies related with trash.
@@
 \end{itemize}
+
+\comment{Trash draws attention of many scholars and people who are professional in different areas.
+Further trash is a common subject of the all ages through the human history.
+In other words this topic is not introduced in recent years (or ages).
+It always part of the human practice and life.
+Even if trash is refused and discarded thing, there are people giving attention to them.}
 %........................................
@@
 \section{Purpose of the Study}
-\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
+\todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
 
@@
 \comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable?
+By understanding them is provide a road map (or ideas) how to turn trash to something valuable?
 (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
@@
 %%% 
-\section{Overview of Chapters}
-This study is structured many examples of artworks in different part of the thesis.
-As the related topic or argument is presented example artwork is given at this moment.
-Immediately how artist replies this issue is illustrated.
+\section{Structure of the Study}
+This study is structured by many examples of artworks in different part of the thesis.
+When a topic or argument is presented, immediately example artwork is given at this moment and how artist replies this issue is illustrated.
 Thereby artworks are examined in the theoretical and cultural context.
-Art works are used as a supportive elements for the stated arguments.
-\comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.} \comment{Sanat eserlerinin tümüyle bir çözümlemesi her yerde yapılamamıştır, konuyla ilgili kısımlarına değinilmiştir.}
+Artworks are used as a supportive elements for the stated arguments.
+However, not every time artworks are discussed in detail.
+Only basic information is given and how it is related with this topic explained.
+\comment{By the way} it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
 
-Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash.
+Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on trash.
 The aim is (better) to understand the trash in cultural and theoretical aspects.
-(to better realization the notion of trash.) It is explored the trash is being worked is whose trash.
-Or what type of society genarete this trash.
+(to better realization the notion of trash.) Provides theoretical and cultural background.
+It is explored the trash is being worked is whose trash.
+Or what type of society generate this trash.
 Also in the project I collect the paper trash.
@@
 It is understood through the patters of consumption patterns.
-And to reflect this cultural phenomena what phylosphers and scholars say.
+And to reflect this cultural phenomena what philosophers and scholars say.
 Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system.
@@
 
-\comment{First chapter will be about the conceptual framework that I have been working through which includes historical and theoretical background.}
+Third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and looks through the sample artworks and artists.
+As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply.
+Artists methods and approaches to the subject are stated.
 
-Third chapter seeks the root of using trash in the artworks and looks through the sample artworks.
-As already artworks are mentioned in the different part of the thesis, in this chapter focused on art (historical )
-
-Fourth chapter explains the project that supports this thesis. Its stages and approaches to the topic mentioned here.
-
-\comment{The second chapter will consist of the overview of my work.
+\comment{Fourth chapter consists of the overview of the project.
+Stated the approach to topic clearly.
+Development process of the work is presented in detail.
 I will start with the development process of the work.
@@
 
-Finally last chapter offers an overall conclusion of this thesis and project.
-
-\comment{The final section, procedural description, covers the process of the project from beginning to end.
-The final chapter is reserved for conclusion.
-The overall project is summed up and the significance and the purpose of the project is re-emphasized.}
+\comment{Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.}
 
@@
 \section{A Note on Terminology}
+Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
+Analysis of them may be subject of another thesis.
 (Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
 Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
-It is important to understand diverse vocabulary of this topic before dive into the theory.
-It is very important to choose right terminology, because ...
-and also make more clearer the borders of the work.
-There is no agreed (or specific) terminology.
+Understanding diverse vocabulary of this topic before dive into the theory makes more clearer the borders of the work.
+There is no consensus on terminology.
 Some scholars uses junk art, others recycling art.
-Sometimes this make difficult to research on this topic.
-And also I must point out that this topic is not limited with the English language.
-The topic is broad and it is not limited with English literature and vocabulary (ref required).
+The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
+What were people throwing out when these words were coined?
+From the rubbish: the archeology of garbage gives clearer definition of some these words.
 
@@
 Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris.
-The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrevelant, but may see a revival if the idea of composting food and yard waste catches on.
+The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on.
 We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech.
@@
 
-The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
-What were people throwing out when these words were coined?
+Some notes on methods:
 
@@
 According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
-If any item is used again and again over time, it is said to be reused.
-The main purpose of reusing is to lengthen the life of the item or material.
+Reusing lengthens the life of the item or material.
 Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
@@
 To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-Why throw something away when you can give it another life?
-Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
+\textbf{Why throw something away when you can give it another life?} Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
 Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
@@
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
+  \caption{Chris Jordan, Break Down}
+  \label{fig:ChrisJordan_BreakDown}
+\end{figure}
+
 \paraphrase{Not all artist transform trash although some deconstruct them.
@@
 breaking down the connections.} It can be an example of downcycling process.
-It is prefered to decompse all the complex link and relationships between the objects.
+It is preferred to decompose all the complex link and relationships between the objects.
 They are not just ordinary things they are possessions of artist.
@@
 
+In this thesis scope mainly \comment{tek kullanımlık} objects are considered generally.
+Nearly half of the material used in the project is disposable packets.
+Therefore as well as other words used but mainly trash is used to refer the material.
+
+Some of the scholar uses recycling\cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it. Some of the scholars and artist uses upcycling for their process.
+
 %****************************************

### 2015-11-22 chapter2.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 
-In this chapter trash (and the practice of transforming trash) is examined in theoretical (and conceptual) aspect.
+In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect.
 Theoretical foundations of trash are discussed.
-(Further benefited from historical and social aspect of trash.
-(?)) How do scholars conceptualized the trash?
-What do they say about it?
+Further benefited from historical and social aspect of trash.
+It is questioned that how do scholars conceptualized the trash, what do they say about it?
 
-Trash draws attention of many scholars and people who are professional in different areas.
-Further trash is a common topic(problem?) of the all ages through the human history.
-In other words this topic is not introduced in recent years (or ages).
-It always part of the human practice and life.
-Even if trash is refused and discarded thing, there are people giving attention to them.
+Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots
 
@@
 \section{Throw away culture}
-We need to ask what is the source of trash.
+%%% Reference from Identity, mobility and the throwaway society
+The term is actually a criticism of over consumption of short-live disposable objects.
+\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
+O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere.
+Even if conducted a qualitative research people are really do not throw away their things.
+\paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
+They analyzed the things like television, furniture and toys like that.
 
-Continuously consuming things and disposing of something.
-It is an important concept to understand why trash is trash?
-(or how it become trash?) Behavioral pattern of throw away culture results in the trash.
-(This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.
+\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}
 
@@
 
-%%% Reference from Identity, mobility and the throwaway society
-\todo{we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)}
-
-\quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society.
-In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
+\paraphrase{In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
 Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
@@
 Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
-% In this paper criticized the perception of throw away culture and arguments. They show the weak points of the arguments. What I understand from trow away culture?
 
-In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this.
-Always needed to keep in my mind that the practice of discard does not exist on only current societies.
+\comment{zaten zengin olanın atma lüksü var.}
 
-Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
+\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ...
-was supplying the customer with hundereds of disposible containers and materials bt the end of the nineteenth century.
-the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."
-
-\todo{throw away sprit}
-
-Industrial age played significant role (engine of the mountains of rubbish.)
+was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century.
+the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)
 
@@
 
-% Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.
+\comment{All around of us filled with the things that are disposable. They are part of our daily activities.}
 
-% COFFEE CUP / Transforming them and invite other people, reveals its process.
-% FROM http://www.gwynethleech.com/public-drawing/cup-windows/statement
+% not easily understandable with the entering non-art objects in art.
+artist are responding the current societies habits in a different ways.
+what they are doing here is to see other possibliteis and show actually what is going on.
+what does it mean all of these things.
+
+\todo[inline]{Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.
+Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.
+Bir anlamda çöplerin sanatçıların günlüklerine dönüştüklerini görüyoruz.
+Yani bir dönüşüm var.
+Benzer bir şey her gün yapılan işin fotoğrafını çeken insanda da var.
+Günlük rutinleri çöp üzerinden yakalayanlar var.}
+
+\todo{need to elaborate}
+
+% ARTWORK
+% COFFEE CUP
+% FROM http://www.gwynethleech.com/
 \begin{figure}[h!]
 \centering
-      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup5.jpg}
-      \caption[Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions Variable]{I began to save all of my coffee cups to use as "canvases" for making art.
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
+  \caption{Installation view}
+  \label{fig:GwynethLeech_Installation}
+\end{subfigure}
+\hfill
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
+  \caption{Painting in the public}
+  \label{fig:GwynethLeech_Public}
+\end{subfigure}
+\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
+\label{fig:GwynethLeech_CoffeeCups}
+\end{figure}
+
+I began to save all of my coffee cups to use as "canvases" for making art.
 Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture.
@@
 And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
-For ArtPrize I am showing 1001 of my cup artworks, each representing a daily caffeine break.
+Each cup representing a daily caffeine break.
 The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
 It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill.
-But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.}
-      \label{fig:GwynethLeech_TheCup}
-  \end{figure}
-
-  \begin{figure}[h!]
-      \centering
-      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup3.jpg}
-      \caption[Gwyneth Leech while painting in the public]{There are different versions of it.
+But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.
+There are different versions of it.
 paintings on paper coffee cups displayed as installation in public window spaces.
-She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many placas and date.
+She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date.
 During public drawing projects she draw with other people.
@@
 Buying a beverage is a daily event for Leech (and also many people.
-These coffee shops all around the world.}
-      \label{fig:GwynethLeech_InAction}
-  \end{figure}
-
-% Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.
+These coffee shops all around the world.
+As she drinks her coffee in the public, she also publicly transform its cup.
 
@@
   \centering
-      \includegraphics[width=0.5\textwidth]{graphics/rubysilvious-teabag-Day237.jpg}
-      \caption[Ruby Silvious, 363 Days of Tea, Day 237, 2015, Mixed media on upcycled paper tea bags, Dimensions Variable]{In the beginning of this year, visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
+  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
+  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
+  \label{fig:RubySilvious_TeaBag}
+\end{figure}
+
+Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
 She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
@@
 Every day she creates a new piece that reflects her impressions in that moment.
-Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.}
-      \label{fig:RubySilvious_TeaBag}
+Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.
+
+\begin{figure}[h!]
+\centering
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
+  \caption{Original view}
+  \label{fig:ChrisJordan_Numbers_CloseView}
+\end{subfigure}
+\hfill
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
+  \caption{Close view}
+  \label{fig:ChrisJordan_Numbers_OriginalView}
+\end{subfigure}
+\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
+\label{fig:ChrisJordan_Numbers_CapsSeurat}
 \end{figure}
 
-%****************************************
-% Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels. Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
-
-% Potraits of Global Mass culture from Chris Jordan.
+Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+Portraits of Global Mass culture from Chris Jordan.
 In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
 “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says.
-“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.”
-
-% Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
-His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits
-
-% Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.
-
-% He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
+“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
+His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits.
+He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
 Here he draw attention to the our consumerism and express them numbers that are very big to understand.
 All the material that we have is trash to create this pictures.
-
-% Chris jordan hem bir gerçeği açığa çıkarıyor. 
-% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.
-%........................................
+\todo[inline]{Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.
+Chris jordan hem bir gerçeği açığa çıkarıyor.
+Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor.
+Bize konuya farklı bir açıdan bakmaya davet ediyor.}
 
@@
 Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.
+
+% Sanatçıların işlerine bir de bu açıdan baktığımızda ne görüyoruz.
 %........................................
 
-%****************************************
-% Tracy emin mesela.
-Yani aslında bir şekilde bir yandan aslında teoriye mi değiniyorum yoksa sanatçıların işlerine mi değiniyorum, bunların teorideki karşılıklarını mı buluyorum emin olamadım.
-Bunların ikisi paslaşarak ilerliyor aslında.
-Aslında çöplerin bize ait çok şeyler söylediğini ünlülerin çöplerini karıştıran yaklaşım ortaya çıkarıyor.
-Bu işde bununla ilgili aslında.
-%........................................
+\comment{Things that are thrown away are one side of it.
+Actually all of our waste tells about us.
+ref required.
+Meaning of waste and what it tells about us.
+Understanding people through their wastes.
+REF.
+Tracey Emin's work.
+She opens up her wastes and also her life.}
+
+% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
+\comment{GARBOLOGY} Garbology is a study of waste as a social science.
+Applying methodologies of archeology to the human debris.
+\todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
+
+% Garbology, from Encyclopedia, Abhijit Roy
+\paraphrase{"The field of garbology involves the study of refuse and waste.
+It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
+According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
+A.
+J.
+Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."}\todo{ref.}
+
+% Rubbish: The Archeology of Garbage, p.24
+\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
+The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
+(example of Medical researches)} \todo{ref.}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
+  \caption{Tracey Emin, My Bed, 1998}
+  \label{fig:TraceyEmin_MyBed}
+\end{figure}
+
+\paraphrase{Tracey Emin puts her private life to the public.
+The work, which Emin now describes as a portrait of a young woman.
+It is a time capsule.
+The cigarettes that litter the floor will one day no longer exist; neither will the newspapers.
+Around her there are pieces of junks speared all over the room.
+We can understand from her junk what type of life her has.
+We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış.
+İşte o sürede birikenler.}
 
@@
   \centering
-      \includegraphics[width=0.5\textwidth]{graphics/ChrisJordan-Albatross.jpg}
-      \caption[Chris Jordan, Albatross at Midway Atoll Refuge, 2009]{The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.}
+  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
+  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
   \label{fig:ChrisJordan_Albatross}
 \end{figure}
+
+The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.
 
@@
 
-\comment{WALL-E belki olabilir.
+%\comment{WALL-E belki olabilir.
 Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
@@
 
-\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
+%\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
 A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
@@
 
-\subsubsection{The Practices of Value Creation: From Rubbish to Durable}
+\subsubsection{The Practices: From Rubbish to Durable}
 Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
@@
 
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.)
+\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.
 
@@
 
-\textbf{Motivations and found object practice:}
-\begin{itemize}
-\item Discovery and engagement
-  \begin{itemize}
-  \item Seeking out: The adventure of hunting
-  \item Finding the unexpected
-  \item The location of discovery
-  \item Metamorphosis and transformation: Imagining a use for the object
-  \item Creative action
-  \end{itemize}
-\item History and time past
-  \begin{itemize}
-  \item Trigger of personal memories
-  \item The object’s story: Reflection about earlier “life” of object and previous owner
-  \item Capturing something elusive: Making sense of an unknown past
-  \end{itemize}
-\item The symbolic and functional object
-  \begin{itemize}
-  \item Aesthetic properties: Visual, tactile, original
-  \item Cost: The thrill of a free find
-  \item Evocative: More interesting than something new
-  \item Useable solutions for practical problems
-  \end{itemize}
-\item Psychological processes
-  \begin{itemize}
-  \item Personal resourcefulness
-  \item Impact on memory, emotion, cognition
-  \item Meaningfulness of object
-  \item Arouses interest: Motivates
-  \item Social engagement
-  \end{itemize}
-\item Ecological affirmation
-  \begin{itemize}
-  \item Environmental concerns
-  \item Against the cult of the new: Slowing down consumption
-  \item Transforming rubbish
-  \end{itemize}
-\end{itemize}
+\todo[inline]{table moved to drafts.}
 
@@
 
-Results of this study also support consideration of found objects as important artifacts that are signifiers of cultural meaning.
-
-[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials. So what is value?]
-\textbf{Value.}
-\begin{itemize}
-\item n. relative worth, merit, or importance: the value of a college education; the value of a queen in chess.
-\item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
-\item n. estimated or assigned worth; valuation: a painting with a current value of \$500,000.
-\item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books.
-Worth implies especially spiritual qualities of mind and character, or moral excellence: Few knew her true worth.
-\item the desirability of a thing, often in respect of some property such as usefulness or exchangeability; worth, merit, or importance
-\end{itemize}
+Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.
 
@@
 \begin{itemize}
-\item Shared practice through the different ages of humanity and different societies. 
 \item Moving nature of trash/objects.

### 2015-11-22 chapter3.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}}
+
+Its roots go all the way back to the 1800s in Europe.
 
@@
 Schuldt’s famous “Trash People,” which has traveled around the world since 1996}  \cite{tauxe2012encyclopedia}.
+
+\todo[inline]{örnek bulduğum tezlerin izlediği yolu burda izleyebilirim.}
 
@@
 William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
+
+\todo{Joseph Cornell, assemblage artist.}
 
@@
 
-%%
-%%
-\subsection{Folk Art}
-In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic.
-The nature of folk art is specific to its particular culture.
-
-Some scholars think that the roots of collage is folk art (ref required).
-It's methodologies used in this art.
-The same exist for craft.
-Some works(for example sculptures from trash) are highly requires craft skills.
+\todo[inline]{place in the folk art.}
 
@@
 %%%
-\section{List of Artworks}
+\section{Examples from contemporary artists}
 Artist and artworks related with trash and their analysis.
@@
 (is it really like that?)
-
-This section is more focused on trash.
 
@@
     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
         \caption{Sax}
-        \label{fig:gull}
+        \label{fig:landfill_harmonic-sax}
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
         \caption{Violin}
-        \label{fig:tiger}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic_drum2.png}
-        \caption{Drum}
-        \label{fig:mouse}
+        \label{fig:landfill_harmonic-violin}
     \end{subfigure}
@@
 
-% Beni bu projede etkileyen en öenmli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
+% Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
+% Beni bu projede etkileyen en önemli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
 yokluk içinden bir şeyler üretmeleri.
@@
 
+% Bunu bir okuyabilirsin.
+% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
 % http://www.eloisacartonera.com.ar/ENGversion.html
@@
 Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
+
+It reminds me that litreary is also a reuse concept.
+Because to create meanings we reuse words and idioms again again with different combination.
+\comment{tüm kelimeler vs hepsi sıralanıyor.
+Arka arkaya getiriliyor.
+Kelimeler harflerin hepsi tekrar tekrar kullanılıyor.
+Reused cartbord reminds all of these and as an object all of it...}
+
+\todo[inline]{Bu ne anlama geliyor onu bulmak gerekli. nereye bağlamalı bilemiyorum. Bu ileri dağıtmak gerekiyor ama gene de burada kalanlar var. Ne yapsam ki?}
+
   \begin{figure}[ht]
       \centering
-      \includegraphics[width=0.5\textwidth]{graphics/EloisaCartonera_Books.jpg}
+      \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
       \caption{Books covered by Eloisa Cartonera}
@@
 
+% Bu adamın ilkeleri var. Benim de var aslında.
 % FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
 % https://www.youtube.com/watch?v=v6IoEF_Tsrw
-\item Nick Quijano has some rules to create assemblages.
+%\item Nick Quijano has some rules to create assemblages.
 \quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
@@
 
-\item Joseph Cornell, assemblage artist.
-
 \item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
 
-\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
+% Recycled art.
+%\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
 "Free is certainly great, and that was a driving force for me early on in my career," he said.
 
+% http://www.tate.org.uk/art/artworks/nelson-the-coral-reef-t12859/text-summary
 \item Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London.
@@
 She shows at the side of human practice, Nelson looks the topic from object side.)
+
+\todo[inline]{very important maybe the second case will this one.}
 
@@
 In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.
+
+\todo[inline]{One Man's Trash Is Another Man's Treasure. bu kısım rubbish theorydede geçiyordu. bunu bir şekikde sonra kullabilirsin.}
 
@@
 \end{itemize}
-
-Childs can enjoy with trash.
-I remember from my childhood, we collect crown cap and play with them.
-Some caps are found less and they worth more.
-We are looking everywhere for them.
-To make them flat we put them on the railways.
-After train passed we get perfect plat cap.
-At that time it is not trash for us.
-It has a value and part of our games and enjoy.
-To have fun a bunch of trash can be enough for us.
-
-In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life.
-By the artist or other parts are give them a new life.
-They can reborn as a different things.
-Do people collect them aware of it?
-Discarded items unites together with the hands of a artist.
-
-Trash is global topic men. When you talk about trash, everyone have ideas about it.
-
-Think a city that has trash monument in the every corner.
-created from their trash.
-merged with the city life and gaining unique cityscapes and aesthetics.
-or think that a museum a trash museum.
-Exhibits works of art embracing the trash in all aspects.
-Maybe done by the artist or the visitors from all around world.
-A place for garbage other than a landfill.
-Waiting their creator to meet again.
-What a great idea isn't it?
-Meeting their creators again.
-But this time their creator can recognize their trash.
-They transformed to totally new thing.
-Reborn.
-Transformed (Kafka, Gregor Samsa).
 
@@
 
-\todo{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
+\todo[inline]{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
 Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}
@@
 
-\todo{Overview of all artworks. How do they differ from each other in terms of transformation(conceptually, physically), methodology, collecting, composition and so on.}
+Childs can enjoy with trash.
+I remember from my childhood, we collect crown cap and play with them.
+Some caps are found less and they worth more.
+We are looking everywhere for them.
+To make them flat we put them on the railways.
+After train passed we get perfect plat cap.
+At that time it is not trash for us.
+It has a value and part of our games and enjoy.
+To have fun a bunch of trash can be enough for us.
+
+Think a city that has trash monument in the every corner.
+created from their trash.
+merged with the city life and gaining unique cityscapes and aesthetics.
+or think that a museum a trash museum.
+Exhibits works of art embracing the trash in all aspects.
+Maybe done by the artist or the visitors from all around world.
+A place for garbage other than a landfill.
+Waiting their creator to meet again.
+What a great idea isn't it?
+Meeting their creators again.
+But this time their creator can recognize their trash.
+They transformed to totally new thing.
+Reborn.
+Transformed (Kafka, Gregor Samsa).
+
+\todo[inline]{Overview of all artworks. How do they differ from each other in terms of transformation(conceptually, physically), methodology, collecting, composition and so on.}
 
 \todo{a chart here.}
+
+\textbf{Resim tahtası.} Bazı işler çöpleri kendi işleri için bir kanvasa dönüştürmüşler.
+Çay poşetlerini boyayan kadın, Kitapları boyayanlar, teneke kutuları boyayanlar.
+Hepsi aslında kullandığı ürünle farklı bir ilişki kuruyor.
+Onları farklı bir hale getiriyor.
+
+toplumun davranışlarına karşı bir cevap, görülmeyen, veya farkedilemeyen unutulup giden bir hale getiriyor.

### 2015-11-22 chapter4.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 % Artist Statement
-% Work
-%  - Development of it.
-%  - Parts of it. (Collecting, Transforming, Spreading them)
-% Exhibition
+% Development of Work
+%  Collecting, Transforming, Tests...
+%
+% Final Work
+%  - Notebooks
+%  - Website
+%  - Exhibition
 %........................................
@@
 %%%
-\section{Inspired Works}
-There are some works that inspire me a lot when developing the work.
+%\section{Inspired Works}
+%There are some works that inspire me a lot when developing the work.
 They are not actually trash related works therefore I put them in different section and here before the details of my work.
@@
 (Maybe all of them can be explained only the related part of it.)
-\begin{itemize}
-\item SketchBook Project.
+%SketchBook Project.
 Inspires me a lot.
@@
 You can send your lecture notes.
-\end{itemize}
 
@@
 %%%
-\section{Progress}
+\section{Development of Work}
 Here stages(progress) of my artwork are listed:
@@
 
-\todo{What type of collecting? How differs from the others? ragpickers from benjamin and archades project.}
+\todo[inline]{What type of collecting? How differs from the others? ragpickers from benjamin and archades project.}
+
+\todo[inline]{yaptığım işten diğerlerine referans vermek gerekli.}
 
@@
 \end{itemize}
+
+\subsection{Collected materials}
+There are different papers and objects are used to produce papers
+\begin{itemize}
+\item Burger King packages, from office at launch time
+\item Starbucks packages, from supervisor, office and my friend.
+Especially my supervisor and friend collect them from their friends and their own uses.
+They save them for me and later I take them later.
+\item Modshifters papers, that are covered on table and at the end of the day they are cut out and throw away.
+I go this place many times and every time questioned what they are doing to the papers.
+One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
+I ask him to give me and he kindly accepted.
+From this paper I covered [x] notebooks.
+All of them contains track of people who sit down there.
+I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
+\item Varuna Gezgin
+\item Graduation banner
+\item Tea bags.
+\item Banka sıra fişleri.
+\item Elginden gelen kağıtlar.
+\item Bilent kağıtları?
+% It is also realization of materials. Establishing different connection to them. Why is important? Identity construction.
+\end{itemize}
+
+\subsection{How I organize people?}
+Well I  actually follow very simple methods. I just talk them all. I explain what I did, ask for their help. Everyone actually approached positively and somehow they contributed the project.
+
+\subsection{Exhibition Experiments}
+Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
+Again the purpose is to find a way that to shock people, surprise them.
+After ward somehow they should understand that these notebooks can be taken.
+\comment{I set up makets and try some installations of it.
+Take photo it.
+listed them here.}
+
+\todo{images are here.}
+
+I imagine a exhibition environment and place notebooks \comment{üst üste.} Different placement are tried.
+All of them are look like sculptural.
+I have insert no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
+which I do not want.
+
+\todo[inline]{bir de aynı zamanda işin süreci, defterlerin yapımları hakkında bilgi vermem gerekli.}
 
@@
 
-%
 \subsubsection{Functionality and Art Debate}
@@
 
-% TODO PRAP.
-Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing.
+\comment{Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing.
 To me art is communication of an idea or an emotion, while craft is the physical manipulation of material.
@@
 I very much like the idea of a spectrum.
-One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.
+One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.}
 
@@
 
-%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.
+\comment{My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
+But it is very strange that the fat on the paper is previously what they are eat.}
 
-%
-\subsubsection{Environmental Impact}
 Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
@@
 % Name of the paper can be related with this place and related with the meaning. 
-\item \textbf{Modsifters.} 
 % Again I need some memory from here. 
@@
 
-\subsubsection{Collected materials}
-There are different papers and objects are used to produce papers
+\subsection{Exhibition spaces}
+Especially it is the most hard topic in the development of the thesis. To find a place for the notebooks is great issue for me?
+
 \begin{itemize}
-\item Burger King packages, from office at launch time
-\item Starbucks packages, from supervisor, office and my friend.
-Especially my supervisor and friend collect them from their friends and their own uses.
-They save them for me and later I take them later.
-\item Modshifters papers, that are covered on table and at the end of the day they are cut out and throw away.
-I go this place many times and every time questioned what they are doing to the papers.
-One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
-I ask him to give me and he kindly accepted.
-From this paper I covered [x] notebooks.
-All of them contains track of people who sit down there.
-I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
-\item Varuna Gezgin
-\item Graduation banner
-\item Tea bags.
-% It is also realization of materials. Establishing different connection to them. Why is important? Identity construction.
+\item Library.
+The reason why select library is there are small papers to write down the location of books.
+Libraries are places that things are reused.
+Books are used by many people.
+It is place of sharing culture.
+Books are shared by all the other peoples.
+\todo[inline]{problematic because of resusing. actually is sharing.}
+Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor. 
+\item Torun. as an alternative place?
 \end{itemize}

### 2015-11-22 drafts.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 %........................................
+
+THEORY IN CULTURE AND THEORY
+
+\textbf{Motivations and found object practice:}
+\begin{itemize}
+\item Discovery and engagement
+  \begin{itemize}
+  \item Seeking out: The adventure of hunting
+  \item Finding the unexpected
+  \item The location of discovery
+  \item Metamorphosis and transformation: Imagining a use for the object
+  \item Creative action
+  \end{itemize}
+\item History and time past
+  \begin{itemize}
+  \item Trigger of personal memories
+  \item The object’s story: Reflection about earlier “life” of object and previous owner
+  \item Capturing something elusive: Making sense of an unknown past
+  \end{itemize}
+\item The symbolic and functional object
+  \begin{itemize}
+  \item Aesthetic properties: Visual, tactile, original
+  \item Cost: The thrill of a free find
+  \item Evocative: More interesting than something new
+  \item Useable solutions for practical problems
+  \end{itemize}
+\item Psychological processes
+  \begin{itemize}
+  \item Personal resourcefulness
+  \item Impact on memory, emotion, cognition
+  \item Meaningfulness of object
+  \item Arouses interest: Motivates
+  \item Social engagement
+  \end{itemize}
+\item Ecological affirmation
+  \begin{itemize}
+  \item Environmental concerns
+  \item Against the cult of the new: Slowing down consumption
+  \item Transforming rubbish
+  \end{itemize}
+\end{itemize}
+
+[TODO need to focus on dynamics of value creation, and to do that analyzes of values bound to materials. So what is value?]
+\textbf{Value.}
+\begin{itemize}
+\item n. relative worth, merit, or importance: the value of a college education; the value of a queen in chess.
+\item n. monetary or material worth, as in commerce or trade: This piece of land has greatly increased in value.
+\item n. estimated or assigned worth; valuation: a painting with a current value of \$500,000.
+\item Value is that quality of anything which renders it desirable or useful: the value of sunlight or good books.
+Worth implies especially spiritual qualities of mind and character, or moral excellence: Few knew her true worth.
+\item the desirability of a thing, often in respect of some property such as usefulness or exchangeability; worth, merit, or importance
+\end{itemize}
+
+% not sure??
+
+% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
+\comment{GARBOLOGY} Garbology is a study of waste as a social science.
+Applying methodologies of archeology to the human debris.
+\todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
+
+% Garbology, from Encyclopedia, Abhijit Roy
+\paraphrase{"The field of garbology involves the study of refuse and waste.
+It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
+According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
+A.
+J.
+Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}
+
+% Rubbish: The Archeology of Garbage, p.24
+\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
+The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
+(example of Medical researches)} \todo{reference}

### 2015-11-22 main.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 \usepackage[titletoc]{appendix}
+\usepackage[colorinlistoftodos]{todonotes}
 
@@
 \providecommand{\singlequotes}[1]{`#1'}
-\providecommand{\todo}[1]{\textcolor{red}{#1}}
+%\providecommand{\todo}[1]{\textcolor{red}{#1}}
 \providecommand{\comment}[1]{\textcolor{cyan}{#1}}
@@
         Ankara\\
-        November 2015
+        \today
 
@@
 The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act.
-Approach of artists who uses discarded material in their works treated in detail.
-It is questioned that why and how they use discarded materials and investigated in terms of theoretical and cultural aspects.
+Approach and methodologies of artists who uses discarded materials in their works are explored.
+It is questioned that why and how they use discarded materials.
+How can artworks be understood in terms of theoretical and cultural aspects?
+
+\comment{The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
+It is questioned that the role of art in transformation of discarded items.
+This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
+Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.}
+
+Artists has used trash to reproduce artwork since the first ready-made introduced.
+\comment{first examples are not actually made of trash.
+not considered as trash, but entering non-art object traced back to beginning of 20th century.}
+
+\comment{First ready-made (or using non-art) object in the art making has extended the language of art and opened new playground for artist.}
 
 Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act.
+Notebooks are made from trash/discarded papers by the help of people.
+Process and notebooks are recorded on a website.
+Notebooks are distributed in different locations.
 
-% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology.
-// The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
-It is questioned the role of art in transformation of discarded items.
-This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
-Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.
+%\todo[inline]{Does trash can be seen as a (new) resource for artist.}
 
-\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory, Throw Away Culture, Handmade Notebooks.
+\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory?, Throw Away Culture?, Handmade Notebooks.
 \end{abstract}
@@
 Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır.
-Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır.
-Çöpü dönüştürmenin nasıl ne ne şekilde mümkün olduğu incelenmiştir.
-Sanatsal üretim yöntemi olarak çöpü (tercih eden) kullanan sanatçıların yaklaşımları ele alınmıştır.
+Çöpün kültürel ve kuramsal olarak nasıl ele alındığı(alınabileceği) araştırılmıştır.
+Çöpü dönüştürmenin nasıl ve ne şekilde mümkün olduğu incelenmiştir.
+Sanatsal üretim yöntemi olarak çöpü (tercih eden)/(kullanan) sanatçıların yaklaşımları ele alınmıştır.
 Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.
 
-\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
+\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
 Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
@@
 
-\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir.
+\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
 Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
@@
 Teoriler ve methodlar ele alınmıştır.
-Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kandırılmak amaçlandırılmaktadır.
+Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kazandırmak amaçlanmaktadır.
 
@@
 Alternatif bir ortam sunan mekanlar seçilmiştir.
+Defterlerin mekanla belirli bir anlamsal ilişki içine girmesi amaçlanmıştır.
 Bu proje sonunda dönüştürülen şeylerin aynı zamanda dönüşütüğü şeyi de başka bir şeye dönüştürdüğü anlaşılmaktadır.
@@
 \tableofcontents
+
 \listoffigures
@@
 %}
+
 %\listoftables
+\listoftodos
 

### 2015-11-22 todo.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 - Susan Strasser, Waste and Want
-- TODO life time of objects
+- TODO life time of objects, which are very short because of disposables.
 - TODO Grammarly ile tüm cümleleri ve kelimeleri gözden geçir.
-- artworks???
+- artworks?
 
+REFERANSLAR:
 cerny1996recycled, herman1998trashformations, rathje1992rubbish
 
-Amaç belirsiz olan şeyleri olabildiğince belirgin hale getirmek. Bir düzen oturtmaya çalışmak.
-En azından neler yazılmalı, neler eklenecek onları belirlemeli. Hangi artworkler hangi işler olmalı.
+KALAN GÜNLER:
+Perşembe, Cuma, Cumartesi, Pazar...
 
 Today's TODO:
-- Anotate all pharagraphs. (Konuya dair tüm fikirler bir ortaya serilsin. İlişkiler kurmanın yolu açılsın.) (öğlene kadar.)
-- Diğer bölümlerde neler eksikse onlar not edilmeli. Notlar alınmalı. Nasıl bir düzen olacağı belirlenmeli.
-- Referansları elden geçirmeli. Tüm yazarlar kitaplar belirlenmeli, sıkıntılı olanlar not alınmalı.
-- Sanatçı işlerinin eklenmesi (akşama kadar.)
-- (Çıktı almalı. Kütüphaneden kitap alınacaktı daha!)
+- Paraphrase gerekli.
+- İlişkiler kurulmalı.
+- Her şey yerli yerine oturtulmalı.
 
 Tomorrow's TODO:
-- Tüm yazıların üzerinden geçme, olabildiğince paraphrase etmeli. Eksik bölümler doldurulmalı.
-- Hocaya yazı göndermeli...
+- Defterler...
+- Phraphrase
 
-Çarşamba, Perşembe, Cuma, Cumartesi, Pazar...
+Amaç Hocaya gönderilecek hale getirmek tezi.
 

### 2015-11-22 uncategorized.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

@@
 % Her alanda recycling var olabilir, literatürde de vardır?
-\todo{WHAT, WHERE?} Literature is recycled material, a pretext for making more art.
+\comment{WHAT, WHERE?} Literature is recycled material, a pretext for making more art.
 I learned this distillation of lots of literary criticism in workshops with children.
@@
 \comment{MOVES} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{reference}
+(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}
 
@@
 (The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
-The Social Life of Things: Commodities in Cultural Perspective)}\todo{reference, resource?}
+The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}
 
@@
 
-\todo{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
+\comment{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
 In other word the problem is our technology which is not perfect.
@@
 Orada aslında başkalarının trashlerinin insanlar hakkında neler anlattığını çok güzel anlıyoruz.
-\todo{ANALOGY Between landfill and graveyards.
+\comment{ANALOGY Between landfill and graveyards.
 WHOSE TRASH?} \quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
@@
 
-\todo{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+\comment{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
 There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
@@
 % TODO Reference
-\todo{WHAT?} John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+\comment{WHAT?} John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
 He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
@@
 
-% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
-\comment{GARBOLOGY} Garbology is a study of waste as a social science.
-Applying methodologies of archeology to the human debris.
-\todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
-
-% Garbology, from Encyclopedia, Abhijit Roy
-\paraphrase{"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}
-
-% Rubbish: The Archeology of Garbage, p.24
-\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
-The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
-(example of Medical researches)} \todo{reference}
-
-\todo{read resource (Trash as History/Memory) \cite{bullock2012trash}}
+\comment{read resource (Trash as History/Memory) \cite{bullock2012trash}}
 
 % Walter Benjamin's trash aesthetics and Adornos reflection? Bu konudan ben hiç bir şey anlamadım açıkcası. Çünkü ne dedikleri ne yaptıkları hiç belli değil.
-\todo{BU NE OLACAK?
+\todo[inline]{BU NE OLACAK?
 NEREYE BAGLANACAK, GARBOLOGY??}\paraphrase{\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
@@
 This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
-In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
@@
 \comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
@@
 In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
-In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+In short, there is a whole sector of upcycling now.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
 \comment{DESIGN, ALTERNATIVE DICIPLINE.} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
-People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
-
-% Trash is waiting to be discovered. At the same time forgotten styles are also used in works. Therefore actually trash and forgotten styles can be considered in the same status.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
@@
 Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of.} \todo{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}
+This theory counters the argument that an object is dead once it is disposed of.} \todo[inline]{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}
 
@@
 
-% King Lear, feeling of waste ???
-
 %%%
@@
 
-% Crowdsourcing artworkümde neden insanlardan topladığımı, neden onları kullanıdığımı anlatacağım yer ile ilgili olabilir.
+\comment{Crowdsourcing artworkümde neden insanlardan topladığımı, neden onları kullanıdığımı anlatacağım yer ile ilgili olabilir.}
 
@@
 \subsection{Crowdsourcing, Participation, Open Work}
-% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
+\todo[inline]{TODO needs reference, FROM Crowdsourced Art and Collective Creativity}
 In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}.
@@
 \subsection{Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap}
-\todo{Reference.}
 \comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
@@
 Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
-(Jacknis 1992)} \todo{reference}
+(Jacknis 1992)} \todo{ref.}
 
@@
 
-\todo{yerlinin fotoğrafı}
+\todo[inline]{yerlinin fotoğrafı}
 \quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
-In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{reference}
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}
 
@@
 themselves.
-\todo{Waste and wantta bununla ilgili bir bölüm olmalı.}
+\todo[inline]{Waste and wantta bununla ilgili bir bölüm olmalı.}
 
@@
 \comment{not every time actually, if you transfor ok.
-it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{reference}
+it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{ref.}
 
@@
 (p25)
-
-\subsection{Statistics:}
-The United nations estimates that two percent of the people in cities in nonindustrialized countries make a living from the refuse discarded by the richest ten to twenty percent (germer 1991)

### 2015-11-22 chapter1.tex
re organization
Former-commit-id: f7f7ca407330448c19799f535ba2ea18fbe043ee

@@
 
-%ancient peoples p.33
+% ancient peoples p.33
 
-%human behavior p.55 can you tell a lot about the customers from their garbage?
+% fast food packaging. p97
+
+% human behavior p.55 can you tell a lot about the customers from their garbage?
 
@@
 %****************************************
-% fast food packaging. p97
+% trasformations
 
-%trasformations during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8
+% during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8
 
@@
 
-\paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
+\paraphrase{Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
+The names we give this material ---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
 Worthless.
 Rejected and useless matter of any kind.
-Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it.
-\todo{ref for tracey emin et al.}" \cite{zimring2012encyclopedia}}
+Unimportant.
+Our trash is a testament; what we throw away says much about our values, our habits, and our lives.
+While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared.
+\ldots the question of who owns these discards is not trivial.
+The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
+Our trash is part of us, whether or not we choose to acknowledge it \todo{ref for tracey emin et al.} \cite{zimring2012encyclopedia}}.
 
 In this thesis work to understand the different aspects of trash is a key element.
-\todo[inline]{This aspects are \ldots} As scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
+\todo[inline]{This aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
 Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
@@
 (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.)
+(Instead of creating new opportunities or alternatives, it is a consuming all of them (which?) and producing huge pile of trash.)
 
@@
 \textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
-\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe(footnotes, satellite discard covers the atmosphere.).
+\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe(footnotes, satellite discard covers the atmosphere).
 
-% Introduction of ReVista
-\paraphrase{After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast.
-Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects.
-No one called it recycling.
-Trash was to be used and used again.} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash.
-They can not handle their trash.
+[RELATIVE] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
+She realized that any of them called the practice as recycling.
+For them using trash again and again is very natural and it is part of their life.
+On the contrary for the developed countries trash considered as a thing that must be avoided.
 There is no place for trash in their life.
-\todo[inline]{herkes için bu geçerli değil yani o zaman ilk baştaki yere referans veriyoruz.}
+It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.
 
-% FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-% TODO PRAP. REF.
-\todo[inline]{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever.
-\textbf{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.} The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD countries produce almost half of the world’s waste.
+% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
+% TODO PRAP.
+[FACTS] \paraphrase{\textbf{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.} The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD\footnote{Organisation for Economic Co-operation and Development(OECD) is an international economic organization of 34 countries.
+Turkey is member of this organization.} countries produce almost half of the world’s waste.
 Africa and South Asia produce the least waste.
@@
 Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.}
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}
 
-% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-% TODO PRAP. REF.
+% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+% TODO PRAP.
 \paraphrase{\textbf{We relate to garbage daily.
@@
 Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between garbage and the arts, I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.}
+Particularly in the connection between garbage and the arts, \textbf{I am interested in two questions.
+First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material} \cite{ibarra2015beautiful}.}
 
-People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore.
-However is it really values?
-What does make it valueless?
-They do not think what happens after they throw it away.
+People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless?
+
+People do not think what happens after they throw it away.
 It exits from your life but not the world.
@@
 Value of objects are not static.
-Trash is not static \todo[inline]{ilk paragrafa referans} also it has a long journey.
+Trash is not static \todo{ref.
+first paragraph.} also it has a long journey.
 A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}.
@@
 
-%http://timgaudreau.com/2012/trash/trash.html
-\comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not.
+% ARTWORK http://timgaudreau.com/2012/trash/trash.html
+[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not.
 An artist takes photos of his every trash, like people take photos of their faces.
@@
 
-% Amelie olabilir.
-Orada fotoğraf toplayan çocuk olabilir.
-Onları itinayla toplayan bir adam.
-Tren garındaki fotoğraf kulubesi.
-Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
-Bir birinden farklı bir sürü insan.
-Filmde neden böyle bir eyleme yer veriliyor?
-Film fotoğraflar üzerinden defter üzerinden ilerliyor.
-Onun çevresinden bir hikaye kurgulanıyor.
-İnsanların artıklarını topluyor.
-Onların değer vermedikleri şeyleri topluyor.
-Bunlar baya baya aslında o insanlar.
-Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
-Çok iyi bir örnek mi bilmiyorum.
-Burada niyet nedir ki?
-Ben buna şöyle bir okuma getireceğim diyebilirim.
-Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
-Bu arada bu fotoğraf toplama işi ilk değil.
-Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
-Ama benim işime yarayan kısmı ne?
-Neden o fotoğrafları ya da bunun filmini yapıyor.
-Aslında puzzlelar üretiyor.
-Belirli tekrar olacaktır.
-insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
-Tekrar bir kitap haline geliyor.
-Tanınmayan insanların fotoğrafları.
-Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
-Aslında tam da amelie bunu yapmıyor mu?
-Hikayeler üretiyor bu fotoğraflardan.
-Yeni karşılaşmalar üretmesi.
-Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
-Bin bir türlü şey vardır aralarında.
-Nereye yerleşmeli.
-Başkasının çöpünü toplama.
-O dönemin o eşyasını arşivini tutma.
-ve herkes sunuluyor sonrasında bu.
-
 % TODO Life time of objects.
-% Nesnelerin yaşam süreleri, Bu yaşam sürelerinin ne kadar olduğu.
-Burada ilginç bilgiler olabilir.
-Aslında ne kadar çok üretip ne kadar kısa sürede tükettiğimi görüyoruz.
-Ama eskiden ürünler daha uzun sürelerde kullanılıyordı.
-Sonrasında ise bu kısa sürede tüketilen ürünlerden nasıl dağlar oluşuyor.
-Çöpçü kaç günde bir ziyaret ediyor.
-Çöp kutuları ne kadar sürede bir doluyor.
-Çöp kovalarının içlerinde neler var.
-Neler yok ki?
-Sanat işleri bile var.
-/ çok hızlı tükettiğimizi aslında chris jordan gösteriyor bize.
-Can you imagine how much plastic cup is being consumed every hour?
+% Nesnelerin yaşam süreleri... Can you imagine how much plastic cup is being consumed every hour?
 
@@
 
-\todo[inline]{ArtBin, trashing things?, squuezzing, wall-e}
+\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}
 
 %http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
-\todo[inline]{showing them as they are, Barry Rosenthal}
+\todo[inline]{showing trash as they are... [Artwork] by Barry Rosenthal}
 
@@
 What were people throwing out when these words were coined?
-From the rubbish: the archeology of garbage gives clearer definition of some these words.
+From the rubbish: the archeology of garbage gives clearer definition of some these words:
 
-% FROM Rubbish! The Archaeology of Garbage, p.9
+% FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
+\begin{quote}
 Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings.
@@
 The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.
+\end{quote}
 
@@
 
-In this thesis scope mainly \comment{tek kullanımlık} objects are considered generally.
+In this thesis scope mainly single use, disposable objects are considered generally.
 Nearly half of the material used in the project is disposable packets.

### 2015-11-22 chapter4.tex
re organization
Former-commit-id: f7f7ca407330448c19799f535ba2ea18fbe043ee

@@
 Stages of work and concerns will be explained.
-%(Also the result of project is explained.
-But is there any result?
-I don't think so?
-I did not see discussions about the results of the works.
-but I try to collect peoples reflection and comments on it.
-Because I believe that it is not transforming the object.)
 
@@
 
-\subsection{Collected materials}
+\subsection{Collecting}
+
+[Organazing People] Well I  actually follow very simple methods.
+I just talk them all.
+I explain what I did, ask for their help.
+Everyone actually approached positively and somehow they contributed the project.
+
+\subsubsection{Collected Materials}
 There are different papers and objects are used to produce papers
@@
 
-\subsection{How I organize people?}
-Well I  actually follow very simple methods. I just talk them all. I explain what I did, ask for their help. Everyone actually approached positively and somehow they contributed the project.
+\subsection{Experiments}
+\todo[inline]{experiments with paper.}
 
-\subsection{Exhibition Experiments}
-Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
+[EXHIBITION] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
 Again the purpose is to find a way that to shock people, surprise them.

### 2015-11-22 chapter4.tex
Reorganization
Former-commit-id: b58919e746aeeabe8ff71eb80518033739c43617

@@
 If we can conquer that dislike, or begin to like what we did dislike, then the world is more open.
-That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}}
+That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
 
-In this chapter the artwork(thesis project) will be explained in detail.
-Final work and it's progress will be explained.
-Connection will be established with the previous chapters.
-Stages of work and concerns will be explained.
+In this chapter thesis project with the development progress of it will be explained in detail in the light of what has been discussed in previous chapters.
 
@@
 (Collect, Save, Transform, Spread.)(Rescue, Revive)
+
+The work aims to liberate the imagination and change the way people see the trash.
 
@@
 
+% Daha öncesinden ne yaptığımı biliyor olmalı insanlar.
+% Benim kriterlerim nedir?
+% Benim kurallarım nelerdir?
+
 %%%
@@
 %%%
-\section{Development of Work}
-Here stages(progress) of my artwork are listed:
+\section{Development Progress of Work}
+How does it evolve in time?
+Important points.
+This progress also reveals the how this work can be positioned among the other works.
+Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?
 
-\begin{itemize}
-\item \textbf{Memories.} As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
+\begin{description}
+
+%%
+%%
+\item[How is it started?]
+
+%%
+%%
+\item[Memories.] As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
 One of these (First of them) is from my primary school teacher.
@@
 Do not throw out packages, look for the useful parts and keep them to use later.
-\item \textbf{Motivation.} I can not throw them away.
+
+%%
+%%
+\item[Motivation.] I can not throw them away.
 When I throw them I became sad for them.
@@
 Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.
-\item \textbf{Collecting.} One of the most found trash in my habitat is paper.
+
+%%
+%%
+\item[Collecting.] One of the most found trash in my habitat is paper.
 I work at METU Technopolis, live at 100.
@@
 
-\comment{COLLECTING TRASH.} One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
+One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
 What are the dynamics(considerations) of collecting them?
@@
 
-\todo[inline]{What type of collecting? How differs from the others? ragpickers from benjamin and archades project.}
+[Organizing People] Well I  actually follow very simple methods.
+I just talk them all.
+I explain what I did, ask for their help.
+Everyone actually approached positively and somehow they contributed the project.
+How does it differ from asking for their help?
+What type of meaning I add here?
 
-\todo[inline]{yaptığım işten diğerlerine referans vermek gerekli.}
+%%
+%%
+\item[Collected Materials.] There are different papers and objects are used to produce papers.
 
-\item \textbf{Transforming.} I turned them to notebooks.
+  \begin{description}
+  \item[Burger King packages] from office at launch time
+  \item[Starbucks packages] from supervisor, office and my friend.
+Especially my supervisor and friend collect them from their friends and their own uses.
+They save them for me and later I take them later.
+  \item[Modshifters papers] that are covered on table and at the end of the day they are cut out and throw away.
+I go this place many times and every time questioned what they are doing to the papers.
+One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
+I ask him to give me and he kindly accepted.
+From this paper I covered [x] notebooks.
+All of them contains track of people who sit down there.
+I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
+  \item[Varuna Gezgin]
+  \item[Graduation banner]
+  \item[Tea bags]
+  \item[Banka sıra fişleri]
+  \item[Elginden gelen kağıtlar]
+  \item[Bilkent kağıtları]
+  \end{description}
+
+%%
+%%
+\item[Transforming.] I turned them to notebooks.
 Actually I use it for my self.
@@
 I collect them whenever I find and most of the time I only save them for later use.
-\end{itemize}
 
-\subsection{Collecting}
-
-[Organazing People] Well I  actually follow very simple methods.
-I just talk them all.
-I explain what I did, ask for their help.
-Everyone actually approached positively and somehow they contributed the project.
-
-\subsubsection{Collected Materials}
-There are different papers and objects are used to produce papers
-\begin{itemize}
-\item Burger King packages, from office at launch time
-\item Starbucks packages, from supervisor, office and my friend.
-Especially my supervisor and friend collect them from their friends and their own uses.
-They save them for me and later I take them later.
-\item Modshifters papers, that are covered on table and at the end of the day they are cut out and throw away.
-I go this place many times and every time questioned what they are doing to the papers.
-One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
-I ask him to give me and he kindly accepted.
-From this paper I covered [x] notebooks.
-All of them contains track of people who sit down there.
-I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
-\item Varuna Gezgin
-\item Graduation banner
-\item Tea bags.
-\item Banka sıra fişleri.
-\item Elginden gelen kağıtlar.
-\item Bilent kağıtları?
-% It is also realization of materials. Establishing different connection to them. Why is important? Identity construction.
-\end{itemize}
-
-\subsection{Experiments}
-\todo[inline]{experiments with paper.}
-
-[EXHIBITION] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
+%%
+%%
+\item[Experiments.] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
 Again the purpose is to find a way that to shock people, surprise them.
@@
 
-I imagine a exhibition environment and place notebooks \comment{üst üste.} Different placement are tried.
+I imagine a exhibition environment and place notebooks at that place.
+Different placement are tried.
 All of them are look like sculptural.
@@
 
-\todo[inline]{bir de aynı zamanda işin süreci, defterlerin yapımları hakkında bilgi vermem gerekli.}
+% What I tried during this progress: Wrap out the trees, because I think that most of the materials that I collected are package papers.
+Well I somehow package the trees again.
+not to carry them but to raise awareness.
+Yani benim amacımı en iyi anlatacak olan şey nedir?
+Aslında ben burada defterden gidip bunu anlamlandırmaya çalıştım.
+Dolayısıyla deneyerek deftere nasıl ulaştım da ziyade defterden başlayıp nasıl tekrar defterde karar kıldığımı anlatan bir hikaye olabilir?
+Yani bu çok da şart olmayabilir bir diğer yandan da?
+Developlement of work?
+Nasıldı nereye geldi?
+How my project evolved?
+And this also explains how it is relates with the research.
+Because the reasearch is shaped the project also.
+Which part of the project shaped by the project?
+Not thinking in the ecological perspective.
+Raised questions also mature the project?
+For example zizek suggest that to find spirutuality and aesthetics to the trash, and for me?
 
@@
 %%
-\subsection{Problems}
-There are a lot of questions and problems that I have to overcome while development of my work.
+\item[Notebooks.] Actually I have been collecting same materials that are used in my project before the thesis work.
+In my mind there is always belief that I can I find something useful for them.
+(In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork.
+Before the thesis I also produce the notebooks for myself.
+However what is changed in thesis.
+First my approach to the trash is a little bit deeper.
+What is added to the notebooks.
+I started to use also used papers.
+for the cover of the notebook, I use more different materials.
+more close to collage.
+production method changed.
+and I started to collect different things, from different places.
+My realization increased.
+I organized my close friends and others to collect or save their trash for me.
+I discovered some points.
+their differences.
 
-% Yani aslında bir derdim ve yapmak istediğim bir şey var.
-Ama bunu gerçekleştirmek için yapmam gereken şeyler var.
-Ve bunların bazılarının nasıl yapılacağı çok belli değil.
-Ben bunlara bir çözüm buluyorum.
-Bir yöntem üretiyorum.
-Bu kısımda aslında bunlardan bahsediyorum.
+Because I already do it.
+So What I didn't change it.
+It is the best one or no to change it.
+I love idea of carrying notebook with near of you.
+I have also save my notebooks.
+I don't throw away them.
+A notebook is actually is a work of you.
+It carries your signature.
+It is one of best gift to give someone.
+Because it is a combination of your work and the other peoples works.
+It is co-authored work.
+Actually there is also a part of people who throw away this peace.
+Actually the best part of it the transformation is not finishes after my creation of notebook.
+It continues with the usage of it.
+How it turned to is not actually uncertain.
+Therefore it is very appropriate of my idea that transforming trash is increases the diversity.
 
-\begin{itemize}
-\item First one is that my art work can be considered as design and has functional purposes.
-(It is not just a design, it is uses design to reach its goal like many artworks use other disciplines to reach their goals and expression.
-Purpose is not design and functionality.)
-\item Using unused industrial paper. (Mixed trash and virgin material, \textbf{to show that discarded and desired object can live together.})
-\item Collecting them with help of people, and asking other people to give the unused papers.
-(Collected from my close friends, from supervisor, from office where I work, from modshifters and varuna gezgin and from bcc labs(hopefully)?)
-\item Giving them to people, but people should take them voluntarily.
-\end{itemize}
-
-\subsubsection{Functionality and Art Debate}
-From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was.
-Duchamp's works kills the functionality.
-It works beyond the functional perception.
-Moves the debate to the conceptual frame.
-However it is not every time case.
-Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value.
-Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else.
-\quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}.
-Therefore anything can be turned to art with a good idea.
-
-\comment{Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing.
-To me art is communication of an idea or an emotion, while craft is the physical manipulation of material.
-An object can easily be both, either, or neither.
-A sculpture, for example, may communicate, but it was constructed using craft.
-Likewise a teapot can communicate an idea, but it was crafted.
-Function is misleading and no distinction.
-Functional objects can still communicate ideas, so art can be functional.
-One object could be viewed two ways: if you look at the way it was made and the materials used, you are looking at its craft, if you think about its ideas, you are viewing it as art.
-An object could have been crafted, but contain no art.
-Even a painting can be crafted but artless.
-A ready-made might be art with no craft.
-I very much like the idea of a spectrum.
-One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.}
-
-\textbf{Why is it not a design?} Because the considerations and priorities are different?
-Functionality is not my primary concern.
-I do not increase the functionality or searching best functionality?
-(Considerations of design and art can be compared and what are my priorities in this work.
-I'm not trying to finish the garbage problem.
-Is it a problem for me?
-Do I problematize it?)
-
-\textbf{Why is it art?} Uses artistic methods?
-Does it represent anything?
-The idea is transforming things.
-Anything can be transformed and re-contextualized again.
-The limitation is our imagination and approach.
-It has a claim.
-In can be analyzed and examined in the context of art.
-It is hard to say that something is art or not.
-However it can be examined in the context of art.
-There are artworks reject art galleries.
-There are artworks also reject commodities.
-It has purpose that.
-spread out the idea in different manner.
-Subverts peoples ideas.
-
-The work aims to liberate the imagination and change the way people see the trash.
+[What is different from industrial notebooks?] Handmade, from trash.
+an alternative to other versions.
+every one have different stories, they are different in visuals (but the others are also different.) What makes them different is not clear actually.
+Does it have to be different?
+Yes.
+The production method is different.
+You pay no money.
+There is different with gift notebooks from companies.
+This notebooks call to you change the destiny of trash together.
 
@@
 %%
-\subsection{Paper}
+\item[Paper]
 "Paper is an indispensable product throughout the world.
@@
 %%
-\subsection{Why (package) paper?}
+\item[Why (package) paper?]
 Easy to collect.
@@
 %%
-\subsection{Why covering notebooks and books?}
+\item[Why covering notebooks?]
 They are all package paper, already used as carry things and this work it has used again for the same purpose (but in different connection, this time trash is bound to the notebook).
@@
 %%
-\subsection{Why giving away?}
+\item[Why giving away?]
 Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
@@
 %%
-\subsection{Why in the public space?}
+\item[Why in the public space?]
 To reach more audience.
@@
 %%
-\subsection{Artistic tactics}
+\item[Artistic tactics]
 Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
 
-\subsection{How I reached to notebook?}
-Actually I have been collecting same materials that are used in my project before the thesis work.
-In my mind there is always belief that I can I find something useful for them.
-(In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork.
-Before the thesis I also produce the notebooks for myself.
-However what is changed in thesis.
-First my approach to the trash is a little bit deeper.
-What is added to the notebooks.
-I started to use also used papers.
-for the cover of the notebook, I use more different materials.
-more close to collage.
-production method changed.
-and I started to collect different things, from different places.
-My realization increased.
-I organized my close friends and others to collect or save their trash for me.
-I discovered some points.
-their differences.
-
-% What I tried during this progress: Wrap out the trees, because I think that most of the materials that I collected are package papers.
-Well I somehow package the trees again.
-not to carry them but to raise awareness.
-Yani benim amacımı en iyi anlatacak olan şey nedir?
-Aslında ben burada defterden gidip bunu anlamlandırmaya çalıştım.
-Dolayısıyla deneyerek deftere nasıl ulaştım da ziyade defterden başlayıp nasıl tekrar defterde karar kıldığımı anlatan bir hikaye olabilir?
-Yani bu çok da şart olmayabilir bir diğer yandan da?
-Developlement of work?
-Nasıldı nereye geldi?
-How my project evolved?
-And this also explains how it is relates with the research.
-Because the reasearch is shaped the project also.
-Which part of the project shaped by the project?
-Not thinking in the ecological perspective.
-Raised questions also mature the project?
-For example zizek suggest that to find spirutuality and aesthetics to the trash, and for me?
-
-\textbf{Why notebook?} Because I already do it.
-So What I didn't change it.
-It is the best one or no to change it.
-I love idea of carrying notebook with near of you.
-I have also save my notebooks.
-I don't throw away them.
-A notebook is actually is a work of you.
-It carries your signature.
-It is one of best gift to give someone.
-Because it is a combination of your work and the other peoples works.
-It is co-authored work.
-Actually there is also a part of people who throw away this peace.
-Actually the best part of it the transformation is not finishes after my creation of notebook.
-It continues with the usage of it.
-How it turned to is not actually uncertain.
-Therefore it is very appropriate of my idea that transforming trash is increases the diversity.
-
-\textbf{What is different from industrial notebooks?} Handmade, from trash.
-an alternative to other versions.
-every one have different stories, they are different in visuals (but the others are also different.) What makes them different is not clear actually.
-Does it have to be different?
-Yes.
-The production method is different.
-You pay no money.
-There is different with gift notebooks from companies.
-This notebooks call to you change the destiny of trash together.
-
-\subsection{What do I think about trash?}
-I need to clarify my approach to the trash, wasting and discarding.
+\item[What do I think about trash?] I need to clarify my approach to the trash, wasting and discarding.
 First point is that I am very uncomfortable to the action of discarding thing.
@@
 
-\textbf{Making exploration.} One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
+[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
 Because it is discarded and undiscovered.
@@
 and possible (as picasso mentioned) discovered again and again.
+
+\end{description}
 
@@
 
-\subsubsection{Name of notebooks}
+Here are the name of notebooks and their story:
+
   \begin{figure}[ht]
@@
   \end{figure}
-\begin{itemize}
-\item \textbf{Puzzle.} Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
+
+\begin{description}
+\item[Puzzle.] Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
 Every piece was a part of bigger banner.
@@
 It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
-\item \textbf{12:00 pm.} Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
-\item \textbf{08:00 am.} Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
-\item \textbf{Friday Night.} (Maybe there can be another option related with traveling, or union).
+\item[12:00 pm.] Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+\item[08:00 am.] Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+\item[Friday Night.] (Maybe there can be another option related with traveling, or union).
 These notebook's pages are collected from restaurant "Varuna Gezgin".
@@
 
-\end{itemize}
+\end{description}
 
-\subsection{Exhibition spaces}
+\subsection{Exhibition}
 Especially it is the most hard topic in the development of the thesis. To find a place for the notebooks is great issue for me?
 
-\begin{itemize}
-\item Library.
-The reason why select library is there are small papers to write down the location of books.
+\begin{description}
+\item[Library.] The reason why select library is there are small papers to write down the location of books.
 Libraries are places that things are reused.
@@
 Books are shared by all the other peoples.
+Public space.
 \todo[inline]{problematic because of resusing. actually is sharing.}
 Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor. 
-\item Torun. as an alternative place?
-\end{itemize}
+\item[Torun.] as an alternative place?
+\end{description}
 
@@
 %****************************************
-% EXHIBITION
-% Where people access them? How to design the experience here. The relationship with the location? 
-% Pizza box, with l shape box. I need to find a place to put them. 
-%
-%........................................
-
-%****************************************
-%% Move to the other sections:
-%
-% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
-The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
-%........................................
-
-%****************************************
 % TODO Find a solution for this problem:
@@
 %........................................
-
-%****************************************
-% Explain your project that I am like and child: 
-% Collecting things means actually searching things. I'm searching for materials and also 
-% What is the main focus in my work? Participation? Transformation? Composite of them? Trash? What else? 
-%........................................

### 2015-11-22 chapter1.tex
Reorganization
Former-commit-id: a93107f6f668119865293f13739ec9e51133f88f

@@
 The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it \todo{ref for tracey emin et al.} \cite{zimring2012encyclopedia}}.
+Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}}.
+\todo{ref for tracey emin et al.}
 
 In this thesis work to understand the different aspects of trash is a key element.
-\todo[inline]{This aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
+\todo[inline]{These aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
 Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
@@
 Modern (developed) societies are continuously generating trash and, pile them on landfills.
-It is experienced by everybody, part of the production of garbage.
-During daily activities trash is generated and people get rid of them by throwing away as quickly as possible.
+During daily activities (drinking, eating, waiting in the bank?) trash is generated and people get rid of them as quickly as possible.
 (Various objects become trash after their primary functions consumed.
@@
 Is that really life of an object ends after tossed on the waste bin?
-\todo[inline]{No.
-Rubbish theory says opposite of it.} (some of the garbage live more from us.
-we use it 5minutes it will still exist years.) There is a lifetime defined (or forecast) by the producer of objects.
-However it is not bound to the producer, also consumer play an important role.
-There are different choices.
-Throw it away.
-Keep it.
-Give it.
-Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans.
+\todo{Rubbish Theory, Zizek} (Objects life time in the nature is more than human being.
+People use them for just 5minutes, however they will exist years on the nature.) The vast amount of industrial discarded items spread through the landfills to oceans.
 They are the result of highly complex industrial production methods.
-They are not easily disposable items.
-They live in the nature thousands of years.
+\comment{They are not easily disposable items in the nature.} They live in the nature thousands of years.
 They are durable(in terms of resistant to natural affects) products.
@@
 
-Trash is global, and shared concept for all societies throughout the ages. 
+\textbf{Trash is global}, and shared concept for all societies throughout the ages. 
 \textbf{Trash in every age.} In other words it is part of human activity of every historic age.
@@
 Trash is part of the early days of human production / or activity.
-Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human.
-Legs, bones etc.
-[TODO etymology reference, see appendix] Archaeologist find things from people throw away.
+Archaeologist find things from people throw away.
 \textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
-\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe(footnotes, satellite discard covers the atmosphere).
+\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe \todo{satellite discard covers the atmosphere}.
+Even if trash is isolated by people, it is close as closest waste bin.
 
@@
 % TODO PRAP.
-[FACTS] \paraphrase{\textbf{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.} The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{Organisation for Economic Co-operation and Development(OECD) is an international economic organization of 34 countries.
+[FACTS] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
 Turkey is member of this organization.} countries produce almost half of the world’s waste.
@@
 Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}
 

### 2015-11-22 chapter4.tex
Reorganization
Former-commit-id: a93107f6f668119865293f13739ec9e51133f88f

@@
 This progress also reveals the how this work can be positioned among the other works.
-Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?
+\comment{Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?}
 
@@
 
+\item[What do I think about trash?] I need to clarify my approach to the trash, wasting and discarding.
+First point is that I am very uncomfortable to the action of discarding thing.
+I always think that by discarding this think I am missing something rather than getting rid of something.
+Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on.
+However almost it is never ending loop.
+(I believe that sometimes we need to break the loops to realize different meanings.
+To think outside the box, we need to behave outside of common habits.
+As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on.
+But for what?
+and also ought to be like that?
+(throw away them to same bin.
+(Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it.
+At that times I become very sad and feel very comfortable.
+I must have find to another place for it more suitable than a waste bin.
+At least I can give them someone else who can use it for own purposes.
+Do I really luxury of discard?
+
+Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}
+
+[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
+Because it is discarded and undiscovered.
+Wait us to be discarded.
+and possible (as picasso mentioned) discovered again and again.
+
 %%
@@
 Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.
+
+%%
+%%
+\item[Paper]
+"Paper is an indispensable product throughout the world.
+Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
+In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
+Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
+Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
+
+\comment{My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
+But it is very strange that the fat on the paper is previously what they are eat.}
+
+Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
+However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
+In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
+Further, forest resources are not always as renewable as one may like to think.
+These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
+
+Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
+Recycling paper can greatly diminish demand for virgin fiber from wood.
+However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
+It can only be recycled four to six times, as the fibers get shorter and weaker each time.
+In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
+
+% History of Paper
+The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
+
+% Production of Paper
+All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
+
+% Uses of Paper
+Paper has become the most ubiquitous product in the age of information.
+Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+
+[Why (package) paper?] Easy to collect.
+Easy to find.
+Thrown out even if it is good quality.
+Packaging materials are very widespread.
+Appropriate for painting and writing.
+Has a very short life time.
+Disposable, there are a lot of package outside.
+No need to carry it.
+Every place gives you package paper.
 
@@
 %%
-\item[Transforming.] I turned them to notebooks.
-Actually I use it for my self.
-And while I was using of it I am very proud of it.
-I am studying nearly more 20 twenty years and I have always need for notebooks and use them.
-It is some sort of passion for me notebooks.
-Because I always admire notebook beautifully design or uniquely designed.
-I collect them whenever I find and most of the time I only save them for later use.
-
-%%
-%%
 \item[Experiments.] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
@@
 For example zizek suggest that to find spirutuality and aesthetics to the trash, and for me?
+
+%%
+%%
+\item[Transforming.] I turned them to notebooks.
+Actually I use it for my self.
+And while I was using of it I am very proud of it.
+I am studying nearly more 20 twenty years and I have always need for notebooks and use them.
+It is some sort of passion for me notebooks.
+Because I always admire notebook beautifully design or uniquely designed.
+I collect them whenever I find and most of the time I only save them for later use.
 
@@
 
-%%
-%%
-\item[Paper]
-"Paper is an indispensable product throughout the world.
-Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
-In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
-Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
-
-\comment{My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.}
-
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
-
-Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
-Recycling paper can greatly diminish demand for virgin fiber from wood.
-However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
-It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
-
-% History of Paper
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
-
-% Production of Paper
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
-
-% Uses of Paper
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
-
-%%
-%%
-\item[Why (package) paper?]
-Easy to collect.
-Easy to find.
-Thrown out even if it is good quality.
-Packaging materials are very widespread.
-Appropriate for painting and writing.
-Has a very short life time.
-Disposable, there are a lot of package outside.
-No need to carry it.
-Every place gives you package paper.
-
-%%
-%%
-\item[Why covering notebooks?]
-They are all package paper, already used as carry things and this work it has used again for the same purpose (but in different connection, this time trash is bound to the notebook).
+[Why covering notebooks?] They are all package paper, already used as carry things and this work it has used again for the same purpose (but in different connection, this time trash is bound to the notebook).
 Trash is used to cover the papers.
@@
 %%
-\item[Why giving away?]
-Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
+\item[Exhibition] Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
 
-%%
-%%
-\item[Why in the public space?]
-To reach more audience.
+[Why in the public space?] To reach more audience.
 Actually the audience is out of the art galleries.
@@
 Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
-
-\item[What do I think about trash?] I need to clarify my approach to the trash, wasting and discarding.
-First point is that I am very uncomfortable to the action of discarding thing.
-I always think that by discarding this think I am missing something rather than getting rid of something.
-Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on.
-However almost it is never ending loop.
-(I believe that sometimes we need to break the loops to realize different meanings.
-To think outside the box, we need to behave outside of common habits.
-As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on.
-But for what?
-and also ought to be like that?
-(throw away them to same bin.
-(Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it.
-At that times I become very sad and feel very comfortable.
-I must have find to another place for it more suitable than a waste bin.
-At least I can give them someone else who can use it for own purposes.
-Do I really luxury of discard?
-
-Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}
-
-[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
-Because it is discarded and undiscovered.
-Wait us to be discarded.
-and possible (as picasso mentioned) discovered again and again.
 

### 2015-11-22 chapter3.tex
Reorganization
Former-commit-id: b58919e746aeeabe8ff71eb80518033739c43617
Reorganization
Former-commit-id: a93107f6f668119865293f13739ec9e51133f88f
Reorganization
Former-commit-id: d2f4ba3d6ef984f2a64e4a3f955bf472f7cb7cc7

@@
 
+Resistance'a bir örnek. Çünkü müzik yapmak para isteyen bir şey mi? ya da bir senfoni orkestrası kurmak?
+
 \begin{figure}
@@
 
+% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
+The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
+
+% http://www.keaggy.com/chairs/sad/12/
+\item{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
+
 \item Martin Kaltwasser \& Folke Föbberling: City As a Resource.
@@
 \end{itemize}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
+  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
+  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+\end{figure}
+
+% ARTWORK http://timgaudreau.com/2012/trash/trash.html
+[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if most of people pay little attention to the trash, everybody do not.
+An artist takes photos of his every trash, like a popular habit that is taking photos of face everyday.
+He focuses on the thing that paid little attention.
+At the end he exhibits all the photos by covering all the walls of room.
+It can seen as record of his activities, record of commodities.
+Most of them we are not aware of them.
+Draw the attention of is being thrown away and every time and everywhere.
+They are too much and can only fit covering all the walls.
+\todo[inline]{Tim Gaudreau Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
+These collections of grids represent my first experiments with using those images.
+This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
+
+% act of taking a picture of every single item that I threw out became something else that I can't quite put my finger on.
+It became more than a chore; it became part of my life (albeit, a bit awkward on first dates).
+
+%  Did this project change your behavior?
+Yes!
+At the beginning of this project, on an average day, I would consume: (1) cup of iced coffee, (2) bottles of water, (1) bottle of iced tea and (1) bottle of a sports drink.
+After photographing so many plastic bottles, there came a point when I couldn't bear to admit throwing out another one.
+As I came to understand the flow of my plastic trash, I started by cutting back everywhere I could.
+I stopped using plastic and foil wrap in my kitchen; I started mixing my own iced tea from concentrate; Drinking water came from gallon jugs rather than pint bottles, then ultimately just tap water.
+Then I switched my morning coffee to a rather beautiful reusable ceramic mug and to mixing my own sports drink from powder.
+
+%****************************************
+% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
+% Michael Landy's Art Bin uses a art gallery to create his dust bin.
+Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
+Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
+"There's no hierarchy once they are in the bin" All of them are accepted as same.
+Ultimate equality.
+Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
+Nothing's too good for the art bin.
+Everything can fit into the art bin.
+Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
+As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
+It is a very big glass bin and isolates people.
+There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
+There is no limitation of throwing away even if art.
+
+% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
+%........................................
+
+\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}
+
+%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
+\todo[inline]{Showing trash as they are, or a database\ldots [Artwork] by Barry Rosenthal}
+
+[Çöpleştirme, heykelleştirme.] not all artist transform, some of them use them as they are.
+further some of them trashes things.
+[squeezing, artbin.] As we can think that trash is valuess.
+But the works of cesar claims that opposite of it.
+In his work he sequuzes objects and commodities.
+Makes them useless and functionless.
+But they earn great value in different value systems.
+
+In the literature generally focused topic is to analysis of transformation of trash to treasure (trash->treasure) but at the same time the opposite way is also exist.
 

### 2015-11-22 drafts.tex
Reorganization
Former-commit-id: d2f4ba3d6ef984f2a64e4a3f955bf472f7cb7cc7

@@
+ABSTRACT
+
+%****************************************
+% SAMPLE ABSTRACTS
+
+% Bu çalışmada, ne kadar itici bir kavram olsa da, çöplük olgusunun çirkinlikten güzelliğe ulaşarak estetik bir haz uyandırması amaç edinilmiştir.
+Iticici gözüken bir konunun resim diliyle anlatımı ile tersine çekici ilginç bir sanat konusu olabileceğinin somutlaştırılması amaçlanmıştır.
+Sanatçı bir anlamda doğada yaşamda bulunan küçük ayrıntıları, sanatsal bir gözle yaklaşarak gösterebilendir.
+Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.
+Oysa önemsiz gibi gözüken itici karmaşık konular bile sanatsal kaygılarla ele ahnabilmelidir.
+Önemli olan, bu konalara estetik yaklaşım ve izlenen anlatım yol ve teknikleridir.
+Özgün baskı dallarından kazı resim (gravür) tekniğinin ele alınan konunun görselleştirilmesinde, anlatımında en uygun teknik olmasıdır.
+Çünkü her sanatçı kendi doğasına en uygun olan teknik ve malzemelerin olanaklarıyla kendini en rahat biçimde ifade etme olanağı bulur.
+Kendine özgü bir biçim ve anlatım diliyle dile getirmek gerçekleştirmek çabalan özgünlüğü yakalamak içindir.
+Bu çalışmada özgünlüğü yakalamak, çöplük olgusunun oluşturduğu dinamik yapı, objelerin biçimlerine bağlı kalmadan plastik dille görselleştirilmiştir.
+Seçilen teknik doğası gereği raslantısal tadlarada olanak vermektedir.
+Oluşturulan resimlerde durağan bir dengeden çok dinamik biçim ilişkilerine dayanan gerilimli bir etkinin yakalanması amaçlanmıştır.
+
+% ON THE RELATIONSHIP BETWEEN IMAGES AND WORDS AND THEIR RELATION TO BODY AND PERCEPTION
+% Prehistoric man created a mark and throughout the history this mark evolved and bifurcated into two: a word and an image. While images were cherished, words were set apart from images. 
+% This thesis attempts to look at the relationship between images and words through seeking their connection to perception and body.
+It investigates how image-word dichotomy occurred and how this dichotomy obscured the connection between writing and body.
+The thesis also examines different approaches to overcome this phenomenon in the context of Modern Art.
+% By examining my artwork within this framework, it argues that it is possible to embody the inseparable relationship between images and words through reconnecting with the body’s primordial existence.
+
+% ALTERNATIVE PHOTOGRAPHY IN THE DIGITAL AGE: PERFECT PHOTOGRAPHS IN AN IMPERFECT WAY
+% This thesis explores the possibility of an alternative future of photography from the union of digital and chemical domains of the photographic medium.
+The historical photographic processes known as Cyanotype, Salt print and Vandyke Brown are employed for this project in conjunction with the modern inkjet printer produced digital negatives.
+% As being highly sensitive to the variables during the process, each alternative photographic print exhibits a visual uniqueness.
+In this aspect, there is conceptual correlation with the visual uniqueness of alternative photographic processes and the visual uniqueness of albinism.
+Emphasizing the human element in subject, vision and craft of making photographs, this project aims to produce unique photographs of a visually unique subject.
+
+% LAND ART ON THE BORDER BETWEEN TOPOLOGY AND ATOPOLOGY
+% The purpose of this study is to discuss the Land Art movement from a topological and atopological perspective.
+In order to establish an extensive understanding of the matters of topology and atopology, Arkady Plotnitsky’s formalization of quasi- mathematical thinking, which is derived from Jacques Derrida’s philosophy, is treated in detail.
+The artistic stance, Robert Smithson, as a major figure of Land Art movement is analyzed both from the artistic and the theoretical perspectives.
+Thereafter, an algebraic reading of the Smithsonian conceptualization is executed in order to illuminate the liaison between the Land Art movement and the matters of topology and atopology.
+Finally, the thesis project, Nonlocalizable Displaced Mirrors depicts the whole attitude, which is taken throughout the study, towards the issue of Land Art on the Border between Topology and Atopology.
+
+%........................................
+
 INTRODUCTION
@@
 
-% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
-\comment{GARBOLOGY} Garbology is a study of waste as a social science.
-Applying methodologies of archeology to the human debris.
-\todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
+% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
+  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
+  \label{fig:ChrisJordan_Albatross}
+\end{figure}
 
-% Garbology, from Encyclopedia, Abhijit Roy
-\paraphrase{"The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
-According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
-Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}
+The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.
 
-% Rubbish: The Archeology of Garbage, p.24
-\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
-The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
-(example of Medical researches)} \todo{reference}
+Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash.
+Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.
+
+Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures
+
+% Effect of plastic on wildlife in Antartica.
+% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor.
+Sadece başka bir yerlere gidiyor.
+Mesela kuşların midelerine.
+Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor.
+Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar.
+Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor.
+Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız.
+Karşı durduğum nokta ise tam olarak burası.

### 2015-11-22 uncategorized.tex
Reorganization
Former-commit-id: d2f4ba3d6ef984f2a64e4a3f955bf472f7cb7cc7

@@
 \comment{DIFFERENT SCALES OF RECYCLING} There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ...
-For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
+
+[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
 It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders
@@
 
-\comment{Karşı çıktığım şeylerden birisi objelerin ilk manaları, ilk kullanım alanları.
+[initial function throw away society] \comment{Karşı çıktığım şeylerden birisi objelerin ilk manaları, ilk kullanım alanları.
 many scholar stated the general attitude in the society.
@@
 
-\comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+[Chapter 2] rubbish Theory \comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
 As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
@@
 
-\comment{Capitalism, market.} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+[Chapter 2] \comment{Capitalism, market.} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
 They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
@@
 
-\comment{throwaway culture} throwaway spirit (vance packard) Stephen jay gould has observed: "in our world of material wealth where so many broken items are thrown away "
-
-\comment{Social classification, throw away culture, place in society.} The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
-America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.
-(bu ülkeler hangileri onları foot notte açıklayabilirsin.)
-
-\comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+[building new things from ruin] \comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
 Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.
 
-\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+[Resistance] \comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
 (sahlins 1992, 16)"
@@
 
-\comment{Economic conditions forces to people recycle and reuse.
+[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse.
 but even if they have no economical struggle, they continue recycle.
-what is the reason of it.} Recycling as an economic strategy of survival in develoing countries throughout the world.
+what is the reason of it.} Recycling as an economic strategy of survival in developing countries throughout the world.
 creative production that is motivated, primarily, by adverse conditions of economic necessity.

### 2015-12-06 chapter1_reduced.tex
Reduction
Former-commit-id: c287ed58ed0af64082641437043495694a05ba72

--- 2015-11-22 chapter1.tex
@@
 \chapter{Introduction}
-
-%****************************************
-% Structure of this chapter
-% Section: explain the topic and its significance, raise curiosity, give some facts about it.
-% Section: state the the purpose of this study, specify the focus of it.
-% Section: overview of chapters and structure of thesis.
-% Section: a note on terminology, clarification about the comprehensive terminology.
-%........................................
-
-%****************************************
-% Sample phrases:
-% The discussions (mentioned discussion are also formed the thesis project entitled ... )
-% Aim of this thesis is ...
-% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
-% as a reaction to the consumerist society.
-%........................................
 
@@
 
-%****************************************
-% Rubbish: the archaeology of garbage. rathje1992rubbish
-% Garbage project's findings have supplied a fresh perspective on what we know --- and what we think we know --- about certain aspects of our lives. p.24
+%
+%
+[Every.] \paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others \cite{zimring2012encyclopedia}.}
 
-% The basic methods of garbage disposal are four: dumping it, burning it, turning it into something that can be useful (recycling), and minimizing the volume of material goods.(p.33)
+Trash in every age and every society.
+Refuse is part of people's consumption practices and it is very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}.
+For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.
 
-% ancient peoples p.33
+Trash is everywhere and, produced every time.
+During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated.
+The pattern is spread to the all day and different places.
+It is hard to say that any location(place) is waste free.
+Nearly every place people require waste bin.
+If we do not find a waste bin, people often leave it (to the ground?).
+Production of trash never stops.
 
-% fast food packaging. p97
+Trash is everywhere.
+Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}.
+Even if trash is tried to be moved away from people life, it is close as closest waste bin.
 
-% human behavior p.55 can you tell a lot about the customers from their garbage?
-
-%p191-192 people tend to think of "recycling" as a relatively modern conceit that has only recently gained broad public acceptance, and whose practical benefits have only just began to be realized.
-Recycling itself is probably as old as --- indeed, seems to be a fundamental characteristic of --- human species.
-
-%p.209 The reuse of paper, for example, involves processes that generated a considerable amount of hazardous waste.
-In order to recycle newspapers, magazines, and, indeed, any printed paper, the paper must first be de-inked.
-At the end of the de-inking process one is left with essentially two products: on the one hand, de-inked fiber that will be turned into new paper; and on th other, a large quantity of toxic sludge.
-%........................................
-
-%****************************************
-% trasformations
-
-% during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8
-
-% p11. for decades we've taken for granted used cars and old houses. Is there anyone alive who has always lived in new houses or driven only new cars?
-
-% p.11 Economics has always been a factor in recycling.
-
-% p.12 recycling is not limited to folk art.
-
-% Bicycle wheel duchamp 1913.
-
-% Use of recycled materials is not new, not is it exclusive to the united states. p.18
-
-% p.22 Material, meaning, and memory --- these are artists' reasons for using found objects.
-
-% p.48 recycling may be the most wasteful activity in modern America --- a waste of time and money, a waste of human and anutral resources. john tierney, "What a Waste," seattle postintelligencer...
-%........................................
-
-Common perception to the trash is to get rid of it as soon as possible.
-People want to depose trash from their lives most of time not thinking beyond.
-However to establish solid understanding of trash, we have to give attention to the trash and ask why it is trash?
-How does it become trash?
-
-\paraphrase{Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others.
-The names we give this material ---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
-Worthless.
-Rejected and useless matter of any kind.
-Unimportant.
-Our trash is a testament; what we throw away says much about our values, our habits, and our lives.
-While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared.
-\ldots the question of who owns these discards is not trivial.
-The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}}.
-\todo{ref for tracey emin et al.}
-
-In this thesis work to understand the different aspects of trash is a key element.
-\todo[inline]{These aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
-Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
-On the other hand it is accepted as a source of diversity.
-(To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?) or aspects).
-Therefore we should ask these questions: What is trash?
-How does it became trash?
-Is it a end product or a source material?
-How much is it valuable?
-How much is it dangerous?
-
-%\comment{In previous ages (which age?
-pre industrial ages?) objects and resources are used again and again.
-Production of objects are hard and laborious.
-Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur.
-Mendillere bunlara örnek olabilir.
-Aslında tam benim konumla ilgili çünkü tek kullanımlık.
-Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.
-Peki burda illaha geçmişe falan girmek gerek var mı?
-çok mu derdimde benim?}
-
-%\comment{Dört bir yanımız metalarla çevrilmş durumda, istediğimiz şeylere çok kolay bir şekilde ulaşabiliyoruz.
-Yemek siparişi veriyoruz ayağımıza geliyor.
-İki blok ötedeki kahveciden istediğimiz zaman kahvemizi alıyoruz.
-Ama tüm bunların bir bedeli var.
-Bir yandan da sürekli olarak çöp üretiyoruz.
-Her ne kadar son derece sistemli bir şekilde çöpler toplanıyor ve belki de ne kadar tüketildiğini hiçbir zaman farkına var mıyoruz?}
-
-% Trash is everywhere and, produced every time
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
-During daily activities (drinking, eating, waiting in the bank?) trash is generated and people get rid of them as quickly as possible.
-(Various objects become trash after their primary functions consumed.
-People do not care the package of the objects that they buy.
-They buy the coffee not the cup of it.
-After coffee finished the life of cup also finishes.
-Very small life.
-But is that really so?
-Is that really life of an object ends after tossed on the waste bin?
-\todo{Rubbish Theory, Zizek} (Objects life time in the nature is more than human being.
-People use them for just 5minutes, however they will exist years on the nature.) The vast amount of industrial discarded items spread through the landfills to oceans.
-They are the result of highly complex industrial production methods.
-\comment{They are not easily disposable items in the nature.} They live in the nature thousands of years.
-They are durable(in terms of resistant to natural affects) products.
-Most of them packages that are used to carry or protect other materials.
-After real material used these packages became valueless (or useless).
-(types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?
-This is the common approach to trash and the main problem.
-(actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc.
-(Instead of creating new opportunities or alternatives, it is a consuming all of them (which?) and producing huge pile of trash.)
-
-\textbf{Trash is global}, and shared concept for all societies throughout the ages. 
-\textbf{Trash in every age.} In other words it is part of human activity of every historic age.
-It exists early ages of human to now.
-Trash is part of the early days of human production / or activity.
-Archaeologist find things from people throw away.
-\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
-\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe \todo{satellite discard covers the atmosphere}.
-Even if trash is isolated by people, it is close as closest waste bin.
-
-[RELATIVE] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
-She realized that any of them called the practice as recycling.
-For them using trash again and again is very natural and it is part of their life.
-On the contrary for the developed countries trash considered as a thing that must be avoided.
-There is no place for trash in their life.
-It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.
-
+%
+%
 % FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-% TODO PRAP.
-[FACTS] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+[Facts.] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
 The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
@@
 
-% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-% TODO PRAP.
-\paraphrase{\textbf{We relate to garbage daily.
-We use it, produce it and dispose of it.
-Endlessly.
-The most obsessive of us get rid of it as fast as we can.} The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes.
-We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations).
-Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding.
-Particularly in the connection between garbage and the arts, \textbf{I am interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material} \cite{ibarra2015beautiful}.}
+\comment{Bunu neden diyorsun? Teze nasıl bir katkı sağlıyor?}
 
-People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless?
+%
+%
+[Common.] (In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded.
+In parallel to this definition, common perception is to get rid of them as soon as possible.
+People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore.
+People want to refuse them from their lives most of the time not thinking beyond (or alternative).
+However to establish solid understanding of trash (or trashing things), we have to give attention to the trash (and ask why it is trash).
+\comment{(To understand the beyond common perception we have to ask...)} How does it become trash?
+\comment{Is it possible to do something other than refusing them?}
 
-People do not think what happens after they throw it away.
-It exits from your life but not the world.
-What happens when you throw it away?
-It is stacked from another place.
-Value of objects are not static.
-Trash is not static \todo{ref.
-first paragraph.} also it has a long journey.
-A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}.
-The results are surprising.
-Trashes spread away across the country and this journey takes month.
-\todo[inline]{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
-In other worlds Americans trash is not only their trash.
-As commodities spread to the every corner of the world, trash also.
-What happens when it is traveled to the other countries, how they approaches these items.
-\comment{They find new uses and meanings on them.} \todo[inline]{consider Papua genen people}
+Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash. People do not see beyond the primary function.
 
-\begin{quote}
-\paraphrase{“Nobody wonders where, each day, they carry their load of refuse.
-Outside the city, surely; but each year the city expands, and the street cleaners have to fall farther back.
-The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter” – Italo Calvino, Invisible Cities} The project is an initial investigation into understanding the 'removal-chain' in urban areas and it represents a type of change that is taking place in cities: a bottom-up approach to managing resources and promoting behavioral change through pervasive technologies.
-TrashTrack builds on previous work of the SENSEable City Lab in its exploration of how the increasing deployment of sensors and mobile technologies radically transforms how we understand and describe cities.
-“People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.”
-\end{quote}
+%
+%
+[Moves.] The vast amount of industrial discarded items spread through the landfills to oceans.
 
-% Cycle of trash
 Trash moves, objects moves from place to place.
@@
 From garbage baskets to sculptures.
-\todo[inline]{REF.
-MIT Garbage project} Lots of different people touches to trash.
+Lots of different people touches to trash.
 With the trash what moves?
+Trash moves around.
+Travels like humans.
+Travels like commodities.
+When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.
 
-% ARTWORK http://timgaudreau.com/2012/trash/trash.html
-[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not.
-An artist takes photos of his every trash, like people take photos of their faces.
-He focuses on the thing that paid little attention, that is trash.
-At the end he exhibits all the photos by covering all the walls of room.
-It can seen as record of his activities, record of commodities.
-Most of them we are not aware of them.
-Draw the attention of is being thrown away and every time and everywhere.
-They are too much and can only fit covering all the walls.
-\todo[inline]{Tim Gaudreau “Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006”} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
-These collections of grids represent my first experiments with using those images.
-This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
+People do not think what happens after they throw trash away.
+\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not the world.
+It is stacked to another place.
 
-% ARTWORK http://www.keaggy.com/chairs/sad/12/
-\todo[inline]{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
+A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}.
+The results are surprising.
+Trashes spread away across the country and this journey takes month.
+Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
+In other words American's trash is not only their trash.
+As commodities spread to the every corner of the world, trash also.
+What happens when it is traveled to the other countries, how they approaches these items.
+\comment{They find new uses and meanings on them.} \todo[inline]{consider African native}
 
-Why people are interested in rubbish.
-Some of the artist also interested in others trash.
-\comment{O çöplerde ne bulmayı umuyorlar ki?
-Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor.
-ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor.
-Bazen de olduğu gibi kullanıyorlar.
-bu açıdan önemli.
-Çöpü çöp şekliden sunan sanatçılar.
-Ama bu nasıl mümkün ki?
-fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar.
-Bence değil?
-bir şekilde müdahele var gene orada.
-o fotoğraflarda artık dikkatin objesi haline geliyor.
-çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.}
+%
+%
+[Aspects.
+Approaches.] In this thesis study to understand the different aspects of trash is a key element.
+Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed.
+On the other hand it is accepted as a source of diversity.
+Further for the recyclers it is a source of income.
+The economical aspect of trash can not ignored.
+There are people who collects plastics, scraps and papers from waste bins and landfills.
+By collecting and selling them they endure their life.
+Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes.
+As it can be seen clearly there are different aspects and approaches to the trash.
+For some people it is disgusting thing and moved away from living space and for the others source of their life.
+\paraphrase{While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
 
-% TODO Life time of objects.
-% Nesnelerin yaşam süreleri... Can you imagine how much plastic cup is being consumed every hour?
+[Relative.] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
+She realized that any of them called the practice as recycling.
+For them using trash again and again is very natural and it is part of their life.
+On the contrary for the developed countries trash considered as a thing that must be avoided.
+There is no place for trash in their life.
+It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.
+
+% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+\paraphrase{We use it, produce it and dispose of it \cite{ibarra2015beautiful}.
+The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes \cite{ibarra2015beautiful}.}
+
+[Production of trash and removal of trash.] For example a project conducted by MIT Sensible City Lab.
+reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.
+
+%
+%
+[Parts of us.] \paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
+Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}.
+The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}
+
+%
+%
+[Change in the production and consumption practices.] \paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced.
+Things once reused again and again, now thrown away because it is more affordable to replace \todo{daha uygun bir kelime bul} with new one.
+\paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production.
+(FROM Collage Culture)} As the production increased its by-product material waste is also increased.
+\paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption.
+(Trash Culture)} \todo{Ref: Trash Culture}
+
+%
+%
+[Current] During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste.
+
+% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+\paraphrase{Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding \cite{ibarra2015beautiful}.}
+
+%
+%
+[Art] \paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}
 
@@
 
-This trash phenomena catches the attention of artist.
-It is very human activity.
-In this context which trash?
-What type of discard.
-Human discard.
-trashes of human activity.
-items that belongs to human.
-commodities etc.
+%
+%****************************************
+\section{Purpose of the Study}
+% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+\paraphrase{Particularly in the connection between garbage and the arts, I am interested in two questions.
+First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material \cite{ibarra2015beautiful}.}
 
-%****************************************
-% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
+Some of the artist also interested in others trash. Why people are interested in rubbish?
 
-% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
-%........................................
-
-\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}
-
-%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
-\todo[inline]{showing trash as they are... [Artwork] by Barry Rosenthal}
-
-%****************************************
-% Different types of trash
-\todo[inline]{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}
-
-The complexity of produced trashes of societies is increasing.
-For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
-Think batteries and so on.
-Every society generates different types of wastes.
-Differs from country to country, society to society, ages to ages.
-It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
-Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
-In other words objects become more complex their re-usage becomes less likely.
-Different production process generates different types of trash.
-According to production process, decomposition process\ldots The approach to the different type of trash will be different.
-In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
-There are some trashes that are more close to the people.
-More easy to convert them.
-more easy to regain to the society.
-%........................................
-
-%****************************************
-% Different disciplines, Perspectives related with trash from different disciplines
-\todo[inline]{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines.
-In other words there are different studies related with trash.
-Different approaches to the trash and son on.}
-
-% From Trashion: The Return of Disposed, Bahar Emgin.
-\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.}
-
-This is very important because the problem of trash is being tried to be handled by different disciplines.
-In other words there different approaches to the trash.
-Different problems, different solutions.
-Which perspective that I have.
-In what ways my project differs from them.
-The purpose is to participate people in this work, by collecting them etc.
-And also offer to transform it.
-Rescue it and than later transform it.
-In short, the difference between the other disciplines must be clear.
-\begin{itemize}
-\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
-\item Management of it (handled by the municipals generally).
-\item Technological perspectives.
-(seeing trash as a design problem.
-developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-development in what sense?)
-\end{itemize}
-
-\comment{Trash draws attention of many scholars and people who are professional in different areas.
-Further trash is a common subject of the all ages through the human history.
-In other words this topic is not introduced in recent years (or ages).
-It always part of the human practice and life.
-Even if trash is refused and discarded thing, there are people giving attention to them.}
-%........................................
-
-%%%
-%%%
-%%%
-\section{Purpose of the Study}
 \todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
@@
 Has using discarded material or trash specific (or special) meaning and message?
-This is a work to explore the re-usage of trash in artworks (place or the role in the art practice).
-(and also in which scope?
-medium, message, life practice\ldots)
+
+\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.}
+
+%
+%
+[Different types of trash] There are different types of trashes.
+Result of different production and consumption practices different trashes are generated.
+For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}.
+Electronic waste (e-waste), Construction and demolition waste, Medical waste are one of them.
+As it can be seen that there are lots of different types and as various as activities of human.
+In this scope of thesis \ldots \todo{Ben hangisini kullanacağım.
+Buna burada değinmek gerekli mi?}
+
+%
+%
+[Different disciplines of trash] Trash draws attention different peoples and disciplines.
+
+% From Trashion: The Return of Disposed, Bahar Emgin.
+\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.} \todo{ref.}
+
+Increasing ecological concerns is one of the aspects of trash. As most of trash last decades are not easily decomposable. Relases toxics and other things.
+
+Technological perspectives.
+(seeing trash as a design problem.
+developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
+development in what sense?)
+
+Management of it (handled by the municipals generally). Removal from the life spaces of human.
 
@@
 
-\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a road map (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
+%
+%
+[Scope] Human discard. In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.
 
-%%%
-%%%
-%%% 
+%
+%****************************************
 \section{Structure of the Study}
+Theory and artworks are not strictly separated from each other.
+Artworks are explained with the help of theories.
 This study is structured by many examples of artworks in different part of the thesis.
@@
 Only basic information is given and how it is related with this topic explained.
-\comment{By the way} it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
+By the way it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
 
-Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on trash.
-The aim is (better) to understand the trash in cultural and theoretical aspects.
-(to better realization the notion of trash.) Provides theoretical and cultural background.
+% TODO Move to chapter 4.
+\comment{Research and the found samples of works helped a lot to shape my work.
+They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}
+
+Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on(of?) trash.
+The aim is to understand the trash in cultural and theoretical aspects.
+(Better realization the notion of trash) Chapter 2 provides theoretical and cultural background.
 It is explored the trash is being worked is whose trash.
 Or what type of society generate this trash.
-Also in the project I collect the paper trash.
 What type of approach generate it and what are the dynamics of it?
@@
 
-\comment{Fourth chapter consists of the overview of the project.
+Fourth chapter consists of the overview of the project.
 Stated the approach to topic clearly.
 Development process of the work is presented in detail.
-I will start with the development process of the work.
+It will start with the development process of the work.
 I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied.
@@
 Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level.
-At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}
+At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.
+\todo{rewrite, copy paste from another thesis.}
 
-\comment{Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.}
+Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.
 
-%%%
-%%%
-%%%
+%
+%****************************************
 \section{A Note on Terminology}
-Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
-Analysis of them may be subject of another thesis.
-(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash.
-Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes).
-Understanding diverse vocabulary of this topic before dive into the theory makes more clearer the borders of the work.
-There is no consensus on terminology.
-Some scholars uses junk art, others recycling art.
-The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages.
-What were people throwing out when these words were coined?
-From the rubbish: the archeology of garbage gives clearer definition of some these words:
+Many scholars and authors have used different words (or terminology) to define trash\todo{bunun yerine başka bir şey demek gerekir mi?}.
+Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them.
+Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes).
+It signifies that the topic is so broad and there is no consensus on terminology.
+Words are used interchangeably.
+From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:
 
@@
 
-Some notes on methods:
+From another book (Trash Culture):
+\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand.
+Many of these terms --- such as ‘trash’, ‘garbage’ and ‘rubbish’ --- are frequently used interchangeably.
+This is not least because the variety of terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of this volume.
+Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.
+Again, these usages have been retained to reflect the focus of individual studies.}
 
-%****************************************
-% Reuse and Recycle
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars \todo{ref}
+In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods transforming trash to the another thing. Both of them are used widely by scholars.
 
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+\paraphrase{According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
 Reusing lengthens the life of the item or material.
@@
 To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
-\textbf{Why throw something away when you can give it another life?} Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product.
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
+\textbf{Why throw something away when you can give it another life?} Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
+For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.} Reusing is possible with re seeing (rethinking).
+Reusing is possible meet the needs of the human itself.
+Using creativity and personal approach can change objects functions.
+It is possible to use objects for different purposes.
 
@@
 In this process, energy is required which depends upon the stages of transformation.
-
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
@@
 
-Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
+Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
 
@@
 
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
-
 Many scholar used the word recycling when mentioning works use trash and the concept of it.
@@
 What they is actually is reusing and combining things, concepts, creating new mixtures.
+It is hard to say that they use it wrongly, but what they refer is actually upcycling.
+Creative reuse, inventing new things from discard.
+Some of the scholar uses recycling \cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
+Some of the scholars and artist uses upcycling for their process.
 
-It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard.
+\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
+Analysis of them may be subject of another thesis.}
 
-% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
-  \caption{Chris Jordan, Break Down}
-  \label{fig:ChrisJordan_BreakDown}
-\end{figure}
-
-\paraphrase{Not all artist transform trash although some deconstruct them.
-Michael Landy is one of them.
-Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
-Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
-Reveal all his possessions.
-and loosing them while you are alive.
-Turning them to rubbish making them unusable.
-breaking down the all the meaning.
-breaking down the connections.} It can be an example of downcycling process.
-It is preferred to decompose all the complex link and relationships between the objects.
-They are not just ordinary things they are possessions of artist.
-Break Down 2001, in which he systematically destroyed all his personal possessions.
-His work examines what we value and what we discard, consumerism and waste, and human labour and its worth.
-It happens in public space.
-People can see the process.
-This process last 2 weeks.
-Places where people buy things actually.
-
-\comment{Yıktığı şeyler aslında bir noktada hepimizin yaşayacağı şeyler. Bunu yaşarken yapıyor. Tüm sahip olduklarını yaşarken kendi isteği ile bunların hepsini yok ediyor.}
-
-In this thesis scope mainly single use, disposable objects are considered generally.
-Nearly half of the material used in the project is disposable packets.
-Therefore as well as other words used but mainly trash is used to refer the material.
-
-Some of the scholar uses recycling\cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it. Some of the scholars and artist uses upcycling for their process.
-
-%****************************************
-% UPCYCLING:
-% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended
-% Raw+Matrial=Art burda da upcycling deniliyor.
-%
-% RECYCLING:
-% recycled, re-seen book.
-%........................................
+\comment{What were people throwing out when these words were coined?}

### 2015-12-06 chapter2_reduced.tex
Reduction
Former-commit-id: 5f9534d56a5913adc6ea4ef6840a4bdae4860f35

--- 2015-11-22 chapter2.tex
@@
 
+%
+%
 In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect.
-Theoretical foundations of trash are discussed.
-Further benefited from historical and social aspect of trash.
-It is questioned that how do scholars conceptualized the trash, what do they say about it?
+Theoretical foundations of trash (Rubbish Theory) are discussed.
+Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with help of ideas of philosophers (Zizek).
+Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash.
+Further it is mentioned how artist are approached these notions?
+and how their work viewed as their offered window or framework.
 
-Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots
+%
+%
+\section{Throw away culture}
+[What is questioned in this section?] Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?
 
-%%%
-%%%
-%%%
-\section{Throw away culture}
-%%% Reference from Identity, mobility and the throwaway society
-The term is actually a criticism of over consumption of short-live disposable objects.
-\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
-O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere.
-Even if conducted a qualitative research people are really do not throw away their things.
-\paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
-They analyzed the things like television, furniture and toys like that.
+%
+%
+[Disposable items.] \comment{Disposable: made to be used once or only a few times.
+Made to be thrown away after one use or several uses.
+Not permanent or durable.
+Not designed to reuse again and again.
+For examples packages of bevarages, paper cups etc.
+They are used very short-time.
+Their lifetime can be measured in minutes in terms of usage.
+I have never seen such person that uses own paper cup again and again.
+However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.
+Importantly the term throw away society has a slightly negative connotation, or meaning.
+When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval.
+\todo{ref.}}
 
-\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}
+\paraphrase{being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid (Hawkins 2006: x)}
 
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
+Disposable items are first introduced X and their usage accelerated after Y. There are Z factors that give rise to usage of single-use ites excessively \todo{Bu cümleyi doğru düzgün kurmak gerekli.}.
 
-\paraphrase{In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
-Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
-The thesis, however, lacks depth and provenance.
-It is, actually, glib.
-Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
-
-\comment{zaten zengin olanın atma lüksü var.}
+% Reference from Identity, mobility and the throwaway society
+[The term throwaway culture] Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}.
+\comment{Scholars argue that contemporary societies are throwaway societies (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
+O’Brien, 1999; Hawkins and Muecke, 2003) \todo{ref required.}.} The term is actually a criticism of over consumption of short-live disposable objects.
+\comment{The term overconsumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.}
 
@@
 was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century.
-the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)
+the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} \todo{ref.
+Hangi kaynaktan?}
 
-% Resource is here: mmmacleo2005.pdf (throw away culture ile ilgili.) (Çünkü ben bunun ürününü kullanıyorum.)
+% Reference from Identity, mobility and the throwaway society
+[Counter-argument] Even if conducted a qualitative research people are really do not throw away their things.
+\paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
+They analyzed the things like television, furniture and toys like that.
 
-\comment{All around of us filled with the things that are disposable. They are part of our daily activities.}
+[Factors.] \comment{Not only one factor, technological advacements can be one of them.
+These items with the help of industrialization can be produced easily.
+Mass production.
+Disposable items are reduces the labour and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup).
+Another point is that they are more affordable in terms of supply chain and cost.
+In other words you can put new one easily.
+Therefore there is no need to save the old one.
+Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.} \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref.
+ontology of trash}
 
-% not easily understandable with the entering non-art objects in art.
-artist are responding the current societies habits in a different ways.
-what they are doing here is to see other possibliteis and show actually what is going on.
-what does it mean all of these things.
+\paraphrase{Taken to its obsessive extreme, the germ theory proscribes companionship.
+The Latin root for this word, cum pani, literally means to share bread.
+But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self.
+Safety in a world of bacteria implies isolation.
+Packaging successfully isolates both food and consumer within a structure of sterile control.
+In essence, it encloses the commons.
+Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
+\todo{ref.
+ontology of trash}}
 
-\todo[inline]{Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.
-Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.
-Bir anlamda çöplerin sanatçıların günlüklerine dönüştüklerini görüyoruz.
-Yani bir dönüşüm var.
-Benzer bir şey her gün yapılan işin fotoğrafını çeken insanda da var.
-Günlük rutinleri çöp üzerinden yakalayanlar var.}
+\begin{quote}
+While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs.
+The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations.
+Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic.
+Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
+Disposable paper cups met significant resistance.
+Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free.
+Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs.
+Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup.
+Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913.
+And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
+\end{quote}
 
-\todo{need to elaborate}
+[Dark side.] Usage of disposable items in the society is very widespread.
+For same cases it is inevitable.
+Beyond the advantages of disposable items there are side of effects of consuming them excessively.
+They result in mountains of garbage.
+
+\comment{Handling of this mountains of garbage is another topic.
+It is not the topic of this thesis.
+It is not debated that usage of disposals are supported or not supported.
+It might be subject of another thesis.
+What is important here the results of it and the reflection of the artist.} \comment{Buna karşı geliştirilen bir refleks olduğu için bu kısma giriyorum.
+Aynı zamanda ben de bu ürünü kullanıyorum.
+Konuyu o yüzden farkl açılarından anlamak gerekli.
+\todo{Ama benim konuya nasıl yaklaştığım biraz belirsiz.}}
+
+[Art] There are some artists whose works are related with the pheomena expressed above. (Some of the works of artist can be examined in this pheomena.)
+
+% ARTWORK
+% Portraits of Global Mass culture
+\begin{figure}[h!]
+\centering
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
+  \caption{Original view}
+  \label{fig:ChrisJordan_Numbers_CloseView}
+\end{subfigure}
+\hfill
+\begin{subfigure}{.47\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
+  \caption{Close view}
+  \label{fig:ChrisJordan_Numbers_OriginalView}
+\end{subfigure}
+\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
+\label{fig:ChrisJordan_Numbers_CapsSeurat}
+\end{figure}
+
+Chris Jordan creates digital photographic series that turns numbers to visuals.
+Provide different way to understand the statistics and the missed reality of consumerism.
+Creates gigantic prints to express numbers in a visual manner.
+Draws attention the the global consumerism.
+reveals the reality that is hard to understand.
+Because it is spread to the community and time.
+
+\paraphrase{Portraits of Global Mass culture from Chris Jordan.
+Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
+“There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says.
+“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
+His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits.
+He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
+Here he draw attention to the our consumerism and express them numbers that are very big to understand.
+All the material that we have is trash to create this pictures.}
+
+[CRITICS] Visuals of Chris jordan are like modern versions of mosaics.
+In the age of consumption the most easily accessible matariel is trash.
+Trash has different colors and sizes and shapes.
+Therefore it is a perfect material to build sculptures from them.
+There is a great diversity of trashes and offers new alternatives.
+
+Not every people throw away disposible objects, some of them save them and use for their own purposes.
+
+% ARTWORK
+% TEA BAGS
+% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
+  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
+  \label{fig:RubySilvious_TeaBag}
+\end{figure}
+
+\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
+She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
+The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags.
+This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers.
+Every day she creates a new piece that reflects her impressions in that moment.
+endeavour of re-purposing recycled and found materials.} \todo{cite website}
+
+[CRITICS] This work is for fathers day.
+Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day).
+Trashes trasnformed to diaries.
+Trash is every where, already at hand.
 
@@
 
-I began to save all of my coffee cups to use as "canvases" for making art.
+\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art.
 Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture.
@@
 These coffee shops all around the world.
-As she drinks her coffee in the public, she also publicly transform its cup.
+As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}
 
-% TEA BAGS
-% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
-  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
-  \label{fig:RubySilvious_TeaBag}
-\end{figure}
+[CRITICS] inside of glass window. public space. publicly drawing, as she drinks her coffee publicly, also paints them publicly.
 
-Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
-She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
-The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags.
-This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers.
-Every day she creates a new piece that reflects her impressions in that moment.
-Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.
+%
+%
+\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of peoples life.
+What people consume is actually tells many things about them \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}.
+As scholars mentioned that throughout the discards of someone else many thing can be understand.
+They are end product of our activities and it can be traced through the discard and garbage.
 
-\begin{figure}[h!]
-\centering
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
-  \caption{Original view}
-  \label{fig:ChrisJordan_Numbers_CloseView}
-\end{subfigure}
-\hfill
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
-  \caption{Close view}
-  \label{fig:ChrisJordan_Numbers_OriginalView}
-\end{subfigure}
-\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
-\label{fig:ChrisJordan_Numbers_CapsSeurat}
-\end{figure}
+%
+%
+[GARBOLOGY] Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
 
-Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
-Portraits of Global Mass culture from Chris Jordan.
-In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
-“There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says.
-“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
-His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits.
-He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
-Here he draw attention to the our consumerism and express them numbers that are very big to understand.
-All the material that we have is trash to create this pictures.
-\todo[inline]{Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.
-Chris jordan hem bir gerçeği açığa çıkarıyor.
-Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor.
-Bize konuya farklı bir açıdan bakmaya davet ediyor.}
-
-%****************************************
-% HAKAN GÜRSU
-% Buraya aslında bir de Hakan Gürsu koymak gerekli olabilir.
-Yani aslında kendisi pek de sanatla ilgili bir laf etmiyor.
-Ama aslında tükettiğimiz onlarca şeye karşı bir tavır yaklaşım sergiliyor.
-Bu yüzden theory kısmında yer alabilir.
-Bu çöpün içinde boğulacağımızdan bahsediyor.
-Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.
-
-% TEZ STATEMENT.
-% Ya gerçekten çöpü dönüştürüyorlar ya da çöpe dair düşünceleri dönüştürüyorlar, ve bunu ele alırken aslında heykel, kolaj, fotoğraf gibi şeylerden yararlanıyorlar ama aslında ortaya koydukları şey bir sanatsal eylem.
-veya bunu sanatsal eylem bağlamında ele alabiliriz.
-
-% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı.
-Çöpün de bu tekrar eden yapısı buna uyum sağlıyor.
-Çünkü zaten hatayın sürekli bir parçası.
-Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.
-
-% Sanatçıların işlerine bir de bu açıdan baktığımızda ne görüyoruz.
-%........................................
-
-\comment{Things that are thrown away are one side of it.
-Actually all of our waste tells about us.
-ref required.
-Meaning of waste and what it tells about us.
-Understanding people through their wastes.
-REF.
-Tracey Emin's work.
-She opens up her wastes and also her life.}
-
-% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
-\comment{GARBOLOGY} Garbology is a study of waste as a social science.
-Applying methodologies of archeology to the human debris.
-\todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
+\paraphrase{Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away.}" \cite{lukas2012garbage}}
 
 % Garbology, from Encyclopedia, Abhijit Roy
-\paraphrase{"The field of garbology involves the study of refuse and waste.
+\paraphrase{The field of garbology involves the study of refuse and waste.
 It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
 According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
-A.
-J.
 Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."}\todo{ref.}
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.}\todo{ref.}
 
-% Rubbish: The Archeology of Garbage, p.24
-\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
-The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
-(example of Medical researches)} \todo{ref.}
+\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice.
+At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of   the human being as a wasted or discarded element in discourses of socio-political hygiene.
+(from Trash Culture)}
+
+\todo{transition needed.} With the help above understanding of trash, what can we see the work of arts. For examples tracey emin.
 
@@
 We can understand from her junk what type of life her has.
-We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış.
-İşte o sürede birikenler.}
+We enter the world of artist through the her trashes.} \todo{Hastalık dönemi...
+Sanattaki yerine bakmak gerekli.}
 
-%%%
-%%%
-%%%
-% FROM Examined Life
-\section{Zizek's Approach to Garbage}
-(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
-In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home".
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-Draw attention to notion of even if trash disappears from our world but not world.
+%
+%
+\section{Zizek's Approach to Rubbish}
+[Transition, introduction] 
+\todo{Adam bir transition bulmalı buraya.} Last decades increasing attention the the ecology and rubbish.
+This section is related with the increasing interest on ecology.
+Global warming is one of them, plastic pollution on the oceans also is part of it.
+These types of news and talks increasingly find a place on media more and more.
+Zizek comments on ecology and trash.
+
+In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London.
+His part starts with these sentence: \quote{This [garbage dump] is where we should start feeling at home}.
+
+Draws attention to notion of even if trash disappears from our world but not world.
 It seems as though the thrown out garbage disappears from our world.
 However, it disappears only from the world of illusions, but still exists in reality.
+\comment{Getting rid of it is not action of production.
+It is action of ignorance.
+It still waits us at somewhere else or the next generations will have to cope with it.
+Maybe (as Zizek suggest) the first thing to do is accept the trash.}
+
+He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
 He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
@@
 Nature contains unimaginable catastrophes.
-think oil and distinct animals and plants.
-we profit balance part of the nature but it is created from catastrophe.
-Are we aware of this catastrophe.
-He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that.
-It would be too much." its voice is like "Don't mess with D.N.A.
+Consider distinction of animals and creation of oil.
+People profit from the balance of the nature but it is created from a series of catastrophes.
+He asserts that ecology will slowly turn to religion that \quotes{is a kind of an unquestionable highest authority.} Ideology of ecology warns us like, \quotes{Don't do that.
+It would be too much.} its voice is like \quotes{Don't mess with D.N.A.
 Don't mess with nature.
-Don't do it" etc.
-We should not forget that we are part of the ecology.
-We must more alienated from the nature.
-We must find poetry and spirituality in the dimension of trash.
+Don't do it} etc.
+He suggests that people must more alienated from the nature.
+They must find poetry and spirituality in the dimension of trash.
 That's the true love of world.
 Love is not about idealization.
-This part will be extended later.)
-
-% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
-  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
-  \label{fig:ChrisJordan_Albatross}
-\end{figure}
-
-The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.
-
-Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash.
-Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.
-
-Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures
-
-% Effect of plastic on wildlife in Antartica.
-% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor.
-Sadece başka bir yerlere gidiyor.
-Mesela kuşların midelerine.
-Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor.
-Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar.
-Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor.
-Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız.
-Karşı durduğum nokta ise tam olarak burası.
+Therefore he thinks that garbage dump is a place that people should accept it as a home.
 
@@
 
-His basic argument is that the modern eco movement is a conservative ideology.
+\paraphrase{His basic argument is that the modern eco movement is a conservative ideology.
 It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
 Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.
+If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.}
 
+Some of his ideas can be summarized as follows:
 \begin{itemize}
@@
 
-How much harmonious all these produced materials with nature?
-How many animals and the plant can use these discarded items?
-(Because of complex production methods their recycling requires complex processes again.
-Some of them already produced to protect goods from natural factors (like decaying etc.).
-However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature.
-However, some artists turned to trash into site-specific sculptures that are more than trash heap.
-not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.
+Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervantion.
+Not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
+(Converting what we create harmonious with the existing system.
+Because it is not possible to think that nature will live harmoniously what we created.
+The more likely idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together \todo{Buraya sanat işi gelebilir, özellikle kamusal alana yapılan çöten heykel işleri gibi.}.
 
-Getting rid of it is not the significant action.
-It still waits us at somewhere else or the next generations have to cope with it.
-(Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing.
-To break out of this eternal cycle of functioning.
+\todo{needs a discussion.}
 
-The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why?
-and what are the other dimensions?)
+[Summary.] \comment{Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor.
+Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor.
+Onun dediği aslında yanlış sebep sonuç ilişkileri kurduğumuz üzerinden gidiyor.
+Çöpü tekrar ele aldığımızda ise yep yeni şeyler keşfedeğiz.
+Yeni alternatifler oluşacak.
+Aslında yeni bir dünya kurgulanacak.
+Çöp nasıl dönüştürülecekse, çöp de insanları dönüştürecek.}
 
-Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.
+Transforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.
 
-Trash of developed societies has higher decomposing period in the nature.
-Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.
-
-\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic.
-Show the problematic understanding thought to the garbage.
+Zizek mentions that ecology is something wrong point to approach trash.
+Shows the problematic understanding of garbage.
 Suggest another thing, and point out the need for the new approach.
@@
 
-% Her şey çöpe dönüyor. 
-% En fazla ürettiğimiz şey çöp. Böyle giderse her şey her yer çöp olur mu? Aslında tezin konusu bu değil ve buna cevap verilmeyecektir? Ama WALL_E denilen dizi böyle bir alternatifte geçen bir dizi.
-% İki tane yöntem var birisi bu çöp dağları...
-ve dağlardan ne görüleceği.
-Gerçi vik munizde o dağlara gidenlerden birisi ve oradaki insanlardan portreler yapıyor.
-Çöp dağlarını nasıl görmek gerek, nasıl farklı bir şekilde görebiliriz.
-\comment{Zizekin çizdiği potreden aslında çöp dağlarınan oluşan bir dünya tasavvur edebiliriz.
-Ve bun noktada wall-e'ye bakabiliriz.
-Bir an için çöpümüzün içinde buğulacağımızı düşünürüz.
-Ya da bu çöp dağlarının bizleri sınırladığını düşünebiliriz.}
-
-%\comment{WALL-E belki olabilir.
-Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir.
-Çöp dağları, çöp denizleri.
-Atılmış binbir türlü nesne.
-ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor.
-Bundan basetmişken aslında pressleme işi yapan şu cesar.
-Bu şekilde olmak zorunda mı?
-Bunun alternatifi yok mu?
-Aslında bu tezde bunlara cevap bulunabilir.
-Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var.
-Ya da başka neler var?
-Bunları araştıran inceleyen bir yazı.
-Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz.
-İnsanlık buna mı dönüşücek?
-Başka bir ihtimal yok mu?
-Gerçekten de dünyayı bekleyen şey bu mu?
-Bir çöp yığını olması mı?
-Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?}
-
-%\comment{WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios.
-A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future.
-WALL-E resembles giant dozers that moves and piles trash in the landfills.
-This robot creates squeezed trash blocks that have no meaning and interpretation.
-All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.
-There are mountains of trash and place is very limited.
-By squeezing them, WALL-E saves space.
-\todo{What is the context of it?
-Which part is related with my topic?} What are we going to do with all these mountains of trash?
-\todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.}
-
-% HERŞEY ÇÖPE DÖNÜYOR.
-Relationship between entropy (second law of thermodynamics) and waste.
-Resources of nature turns to waste that it can revert it.
-Creating that are reversible again is problematic through the nature of sustainability.
-What is produced after it is consumed become worthless.
-
-% Yani bir çözüm bulmaktan bahsediliyor ama sanat çözüm bulur mu bilmiyorum.
-Zaten derdim de benim aslında tüm bu çöp sorununu ele almak çözmek değil.
-Çöpe olan bakış açısındaki problemi göstermek olabilir.
-Burda beni destekleyen şey zizekin sözleri olacak.
-
-idealization of nature, to love nature is to love trash.
+Idealization of nature is problematic.
+Loving nature is loving trash.
 Live with trash.
 Do not see it as trash actually.
-Then the question is how to love trash?
-how to live with trash?
-can living with our trash enrich (our perceptions, abilities)?
-how not to see them as trash and useless?
+Then the question is How to love trash?
+How to live with trash?
+Think beyond the common perception.
+Do not think it as abject, disgust.
+Can living with our trash enrich (our perceptions, abilities)?
+How not to see them as trash and useless?
 Can it be possible with art?
 
-%%%
-%%%
-%%%
+\todo{Çöp evler buraya gelebilir belki, çöpleriyle birlikte yaşayanlar?}
+
+%
+%
 \section{Rubbish Theory}
-Objects have a lifetime and they don't remain same through that lifetime.
+
+\comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük.
+Bu hareketlilik ve farklılık ise bir teorik çerçeveye oturulmuş, hadi ona baklım şimdi.
+Zaten bu hayatta çöp her zaman karşımıza çöp olarak çıkmıyor.}
+
+In this thesis transformation of trash is claimed and this theory provides a framework for this transformation.
+
+\paraphrase{Michael Thompson’s 1979 study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity and social status \todo{ref.
+from Trash Culture}.}
+
+\paraphrase{The potential of the discarded thing also relies on its status as a thing approaching a \quotes{zero point} of value.
+In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty.
+As Michael Thompson’s Rubbish Theory  suggests, at its nadir in a cycle of consumption and production, rubbish is both ready for disappearance and yet ripe for reinvestment, reinterpretation or revaluing \todo{ref.
+from Trash Culture}.}
+
+\paraphrase{Objects have a lifetime and they don't remain same through that lifetime.
 Their value, usage, location change over time.
@@
 Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.
+Rubbish theory presents a conceptual approach to this argument.}
 
@@
 Thompson label some transitions as possible and the others as impossible.
-"He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system" \cite{meadow2011relocation}.
+\quotes{He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
+Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system} \cite{meadow2011relocation}.
 Further, he does not allow move from transient to durable.
@@
 In another word, it is not rubbish.
-This urine with the approach of Duchamp turned to be an artwork.
+This urine with the intervention of Duchamp turned to be an artwork.
 It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum.
+After Duchamp's intervention to the urine, it becomes a durable object placed in a museum \todo{Fontain's importance in the history of art} \todo{what happens when we look at from the eyes of rubbish theory}.
 
-In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.
-(explain details) (It can also be thought that they are the way of value creation.) (turning trash to treasure or something else is a value problem.
-transforming them creates new a value system?
-or just finding place existing value system.
-by the way there is a value theory related with (or inside of) game theory.)
+\paraphrase{In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.}
 
-Further another conducted research examines the psychological, social, and aesthetic factors involved in found object and found that ... \cite{camic2010trashed}.
+\paraphrase{Rubbish theory, a philosophy that attempts to address how value is placed on material objects.
+It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed.
+An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people.
+The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile.
+What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always} \todo{burada bir şeyler eksik.}
+% - Çöp ile birlikte yaşa diyorsun ama bu nasıl olacak.
+en azından mümkün mü?
+Burada aslında çöp dediğin şeyin aslında bir şeyin bir sınıflandırma sorunu olduğu ve farklı stateler arasında geçişler yaptığını görebiliriz.
+Çöp evlere değinmek gerekebilir.
+increase, while the remainder of society owns objects whose value will eventually decrease to nothing.
+\todo{ref from Liz Parsons}}
 
-"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
+\paraphrase{Rubbsih theory suggests that value emerges through our ways of seeing and placing objects. \todo{ref from Liz Parsons}}
 
-The paper suggests the Theory is useful in foregrounding the material dimensions of markets.
-It also highlights the importance of thinking in terms of movement, flow and circulation in markets.
-Finally the theory suggests that value emerges through our ways of seeing and placing objects.
-(From Liz Parsons)
-
-%%
-%%
-\subsection{Rubbish Theory in Practice}
-% TODO PRAP. REF.
-(Summary From Liz Parsons.)
-
-A key critique of the rubbish theory is its neglect of the practices of value creation.
-Thus the paper draws from existing studies in consumer research in exploring three such sets of practices: finding objects, displaying objects, and transforming and re-using objects.
-
-Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
+\paraphrase{Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
 Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
@@
 There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
+(Summary From Liz Parsons)}
 
-In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
+\paraphrase{In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
 Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
@@
 This is where Thompson’s Rubbish Theory comes in.
+(Summary From Liz Parsons.)}
 
-\subsubsection{Transients, Rubbish and Durables}
-The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
+\paraphrase{The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
 The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
@@
 He further observes that their category membership determines the way we act towards them.
+(Summary From Liz Parsons.)}
 
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
+\paraphrase{Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
 Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
 Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
+(Summary From Liz Parsons.)}
 
-Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
+\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
 (Further there is similar analogy at Waste and Want.
@@
 Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
+(Summary From Liz Parsons.)}
 
-\quotes{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
+\paraphrase{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
 disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)}
+But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)(Summary From Liz Parsons.)}
 
-\subsubsection{The Practices: From Rubbish to Durable}
+%
+%
+\subsection{Rubbish Theory in Practice: From Rubbish to Durable}
+% TODO PRAP. REF.
+(Summary From Liz Parsons.) 
 Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
@@
 
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.
-
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
-Transformations may also involve the modification or updating of objects through painting, alteration or repair.
-Transformations may not only be based around creating new uses but also creating new looks.
-The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
-
-%%
-%%
-\subsection{Theoretical Analysis of Found Object}
-(Summary From Paul M Camic.)
-
-% TODO PRAP. REF.
-\subsubsection{Seeking Objects}
+%****************************************
+% Theoretical Analysis of Found Object
+% (Summary From Paul M Camic.)
 As a species Homo sapiens has been gathering and collecting objects for thousands of years.
@@
 of salvaging and using found and second-hand objects has potential implications for \ldots 
+%........................................
 
-% [TODO adapt for my case] The main aim of the current study was to produce an initial conceptual model that explains contemporary found and second-hand object use in blablabla.
+\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.
 
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
+\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
+Transformations may also involve the modification or updating of objects through painting, alteration or repair.
+Transformations may not only be based around creating new uses but also creating new looks.
+The re-use of objects also creates value for things that otherwise would be allowed to slip away (or slide terminally into the rubbish category).
 
-\subsubsection{Found Objects in Art}
-The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
-
-How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-Camic's \quotes{project surveyed participants who currently use found objects in their daily lives in order to investigate and understand possible purposes, determining factors, and potential benefits of their use.}
-
-\todo[inline]{table moved to drafts.}
-
-The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
-The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
-When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
-Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
-This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
-
-An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
-Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
-
-Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.
-
-%%%
-%%%
-%%%
+%
+%
 \section{Summary}
 \begin{itemize}
+\item Trash has archaeological value. It reflects out habits.
+\item Ecological perceptions have problems. 
 \item Moving nature of trash/objects.
-\item Classification is the main key, trash is not related with the object property. 
-\item Value creation, shifts in the society. 
-\item Trash has archaeological value.
-\item Trash has potential to be used again.
+Objects value/state is not static open to intervantion, has potential to be reconsidered.
+Their place shift in the society.
+Classification is the main key, being trash is not related with the object property.
+It is about perception the trash.
 \end{itemize}
 
-Thompson thinks that the switch only occurs from losing all the value given the object.
-He refers that to gain new value previous systems ruins must be cleaned.
-Changing the context by first rubbishing them.
+It is part of discussion of trash and ecology.
 
-Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.
+First part analysis trash of disposable items and the works of art that looks differently to these trash.
+Whose trash?
+Which trash?
+Answers these questions.
+It displays common approach to the trash.
+Artist reflection to them.
+When we look at personal level (previous one is general one) discards tells us about our activities, possessions, preferences etc.
+They can be viewed as potrait of artist and us.
 
@@
 
-% Burada zizekten rubbish theorye geçerken aslında bir bağlantı bulmalı.
-İkisi arasında bir ilişki kurmalı.
-Ya da aslında static değildir çöp arkadaş bak bunu ileriki kısımda rubbish theory ile sana anlatacağım diyeceğim  mesela.
+Thoughts on ecology and garbage (Zizek's part). Zizek points out wrong opinion about ecology among the society. Stacking trash outside of living space is not the solution.
+
+% Adam demiş ki çöpünüzle birlikte yaşayın. Ben de zaten bunu yapmaya çalışıyorum işimde.
 
@@
 
-% Aslında burda bazı pratikler veriliyor. Ama daha detaylısı bir sonraki bölümde verilecek. Sanat bağlamına yoğunlaşılarak.
+Thompson thinks that the switch only occurs from losing all the value given the object.
+He refers that to gain new value previous systems ruins must be cleaned.
+Changing the context by first rubbishing them.
+
+Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.
 
 Then next chapter discusses the practices in art world in more detail. Trash in the context of art. Which purpose and which method? Approaches of artist.
-
-% Bu bölümün faydası ne oldu bana. Neleri çıkartmış oldum. Tüm bunlara göz atmak gerekli.
-% - ilk olarak throw away culture denilen bir şey var.
-belli çeşit üretim ve tüketim yöntemleri var.
-ve sanatçılar bunu karşı eleştirel yaklaşmışlar.
-hatta bir şeyin alternatifi olduğunu söylerken bunun neyin alternetifi olduğunu göstermem gerektiği için kullanıyorum.
-Konu çok geniş olabilir.
-kapitalizm, endüstrileşme faktörler olabilir.
-Aslında ben bu kültürün nasıl oluştuğundan değil nasıl şeyler ürettiğiyle ilgileniyorum.
-Büyük çöp yığınları oluşturuyorlar.
-(Benim kimin çöpüyle uğraşıyorum.
-Yani aslında bir sürü çöp var.
-Biraz da bunu netleştirmek için buna ihtiyaç var.)
-
-% - Sonrasında ise bu çöp yığınlarını ne yapacağız.
-Dert bu.
-Nasıl yaklaşmak gerekli bu çöp yığınlarına.
-Burada belki bir kaç yaklaşım verilebilir.
-Ama ben zizekin yaklaşımını ele alıyorum.
-Çünkü adam demiş ki çöpünüzle birlikte yaşayın.
-Ben de zaten bunu yapmaya çalışıyorum işimde.
-
-% - Çöp ile birlikte yaşa diyorsun ama bu nasıl olacak.
-en azından mümkün mü?
-Burada aslında çöp dediğin şeyin aslında bir şeyin bir sınıflandırma sorunu olduğu ve farklı stateler arasında geçişler yaptığını görebiliriz.
-Çöp evlere değinmek gerekebilir.
-
-% Sonra bu iş pratikte nasıl oluyor ona bakılabilir.
-
-% Yeri gelmişken pisuvarı da bu rubbish theorynin sınıflandırmasına sokabilirim.
-
-Zizek points out wrong opinion about ecology among the society.

### 2015-12-06 chapter3_reduced.tex
Reduction
Former-commit-id: 776addea2a8d261fe4b62f86718a2555ef817347

--- 2015-11-22 chapter3.tex
@@
 The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense.
-If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}}
+If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}, 1998}
 
-Its roots go all the way back to the 1800s in Europe.
-
-How and why does trash draw attention of artists(, and also mine)?
+How and why does trash draw attention of artists?
 In this chapter how artist approached to the trash and their techniques are discussed in the context of art.
@@
 
-% TODO List motivations of artists and their ideas about junk. Because it reveals the different dimensions of this topic.
+%
+%
+\section{Root in the Art History}
+Using trashed objects in making of art can be examined with the enterance of non-art objects to art \todo{sadece bu yeterli olmayabilir.}.
+In other words using objects in artworks beyond their intended purpose or intended meaning and function.
+Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together.
+(How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
+However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso.
+\todo{Still Life with Chair Caning} \todo{Violin with sheet of music}.
+One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting.
+This work of Picasso also can be considered as first example of assamblage because of a rope was used to frame the picture.
+Using non-art objects in the production of art challanges existing conventions of painting.
+% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
+\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
+The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).} \textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
+The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
 
-% Diğer tezlerde ne diyordu. Bu nasıl bir anlatış biçimi be mustafa. doğru düzgün bir şey yok. Anlatcak olsan birisine böyle mi anlatırsın ha?
-
-%%%
-%%%
-%%%
-\section{Root in the Art History}
-In this chapter root of using ---(non-art)--- objects in the artworks is examined.
-In other words using objects in artworks beyond their intended purpose or intended meaning and function.
-Developing artworks not only painting but also using paper and other stuff by pasting them together.
-(Foundations of trash in art.) Using object apart from their proposed meaning is not a new thing[ref required, using jewelry by African tribes], through the ages people used objects and tools for different purposes.
-However it is not discussed in the context of (western)art and not accepted method for art making.
-Therefore who and which work introduces this concept and how it is developed and evolved in time.
-(of course it is a brief overview by some remarkable pieces.)
+% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
+\todo{works of Kurt Schwitters} \paraphrase{The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
+\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
+The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.}
 
@@
 
-\todo[inline]{örnek bulduğum tezlerin izlediği yolu burda izleyebilirim.}
-
-%****************************************
-% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
-% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
-\ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
-As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
-%........................................
-
-%%
-%%
-\subsection{Collage}
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
+%
+%
+[Collage] Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
 In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
 Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
+\todo{read greenberg1984collage}
 
-% Works of picasso baraque.
-
-% TODO reading...
-\cite{greenberg1984collage}
-
-%%
-%%
-\subsection{Assemblage}
-Assemblage work produced by the incorporation of everyday objects into a composition.
+%
+%
+[Assemblage] Assemblage work produced by the incorporation of everyday objects into a composition.
 It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
@@
 William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
-
 \todo{Joseph Cornell, assemblage artist.}
 
-%%
-%%
-\subsection{Bricolage}
-Dictionary meaning; something constructed using whatever was available at the time.
+%
+%
+[Bricolage] Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
+\paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
+\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
 
-% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;
-
-% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime.
-bunu yapan kişiye de bricoleur deniyormuş.
-lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş.
-kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.
-
-Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}
-
-the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
+\paraphrase{\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.}
 
@@
 \end{quote}
-
-\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.
 
@@
 
-% TODO reading...
 [TODO use this ref]\cite{strasser1999waste}
 
-Bricolage is different than collage.
-Bricolage > collage.
-Because it is more general understanding of human practice.
-Collage is just only gluing paper together and it can be only a subset of bricolage.
-Same applicable for assemblage.
-Transforming trash can be examined within bricolage.
+%
+%
+[Found Object] Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
 
-%%
-%%
-\subsection{Found Object (Ready-mades)}
-Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
-Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).
-Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
-The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+%
+%
+[Ready-Mades]
 
-% Duchamp falan.
+%
+%
+\section{Examples from contemporary artists}
+Beyond historical development of art with non-art objects and trash, for contemporary artist what it means has slight differences.
+Firstly their purpose do not want to express the language of art by using trash and non-art objects because they are already done and the way of making art dramatically changed.
+Therefore what are their purpose and how they can be viewed?
 
-\todo[inline]{place in the folk art.}
+% FROM ReVista
+\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} \paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
 
-%%
-%% junkyard art
-\subsection{Garbage Art, Recycling Art}
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
+% FROM Paola Ibarra ReVista
+\paraphrase{Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
+Is there a limit to recycling and representation?
+Or is there a point at which waste cannot become art (or anything else)?}
 
-% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].
+% TODO Naive debate??
+\comment{All that can be seen as naive act because of little impact and outside of the system(which system?).
+As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill.
+However this very argumentative that having no impact or little impact.
+It might be true that this practices solve all problems of landfill or etc.
+But changes individuals and communities life.
+It recreate and rebuilds the community.
+Even if it is one simple object worth look and see the opportunities of it.}
 
-%%%
-%%%
-%%%
+%
+% Tags: "dikkate alınmayanı tekrar ele alıyor". Mekan: sokaklar, şehir, kamusal alan. Traces of our life.
+\textbf{Road Kill.} \paraphrase{Filomena Cruz creates photographic series named as \quotes{Road Kill} painstakingly captures tiny \quotes{trash corpses} on the pavement.
+It is that particular type of trash meet in the public places.
+Trash left behind, trash on the sidewalk, squished, squashed, and weathered.
+Filomena Cruz sees trash that people don’t want to see.
+A piece of chewing gum with an \quotes{engraved} leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of \quotes{worthlessness} suddenly becoming meaningful (and moving).
+For one thing, trash corpses faithfully record city life.} Uses public spaces and takes photos of streets and roads in unfamiliar fashion, focussing onto trash.
+Captures the trace of city life from trash.
+She does not collect the trash physically, collects the images of them.
+They are still there and continously changing.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
+  \caption{Road Kill by Filomena Cruz}
+  \label{fig:FilomenaCruz_RoadKill_ReVista}
+\end{figure}
+
+%
+%
+\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.
+
+%
+%
+\textbf{Pictures of Garbage.} Vic Muniz creates monumental portraits from trash in Jardim Gramacho, an open-air dump just outside Rio, with the help of \textit{catadores} in the documentary film (Waste Land, 2010) Waste Land, directed by Lucy Walker.
+Called “Pictures of Garbage,” they were created by Mr.
+Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America.
+(Important point is here collaboration with the pickers.
+Listening their stories and capturing their portraits.
+It methods similar to the mosaics, every type of discard collected from dump used his photos.) Trash and people who live there is the subject of his portraits.
+None of the trash is belong to that people.
+However again these trash express them perfectly because they make a life from trash.
+Their home is dump.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
+  \caption{Pictures of Garbage by Vic Muniz}
+  \label{fig:VicMuniz_PicturesOfGarbage}
+\end{figure}
+
+%
+%
+\textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their \quotes{Recycled Orchestra}.
+
+Cateura, Paraguay is a small city that has grown atop a massive dump.
+It is regarded as one of the poorest slums in Latin America, a village where people live among a sea of garbage.
+Incredibly, the landfill itself is the primary form of subsistence for many residents, who pick through waste for items that can be used or sold.
+Prospects for most of the children born in Cateura is bleak as gangs and drugs await many of them.
+But then one day, something amazing happened.
+A garbage picker named Nicolás Gómez (known as “Cola”) found a piece of trash that resembled a violin and brought it to musician Favio Chávez.
+Using other objects collected from the dump, the pair constructed a functional violin in a place where a real violin is worth more a house.
+Using items gleaned completely from the dump, the pair then built a cello, a flute, a drum, and suddenly had a wild idea: could a children’s orchestra be born in one of the most depressed areas in the world?
+As you can guess, the answer was yes.
+
+To view scenes from the landfill slum of Cateura in Paraguay is to look into the depths of extreme poverty.
+But within the contents of the landfill are glimmers of hope in the form of cardboard, utensils and other discarded materials that can be crafted into imperfect but usable musical instruments.
+These makeshift violins, flutes and cellos, combined with instruction from a local music teacher, have given birth to the Recycled Orchestra of Cateura.
+Through the music of Mozart, Beethoven and Vivaldi, this orchestra allows the young musicians to transcend their identity as children of poverty.
+
+"A violin is worth more than a house here," says Favio Chavez, the orchestra's director and founder.
+In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
+"My life would be worthless without music." says one girl in pigtails.
+A young man named Juan Manuel Chavez, nicknamed Bebi, has a cello fashioned out of an oil can and old cooking tools.
+For the camera, he plays the Prelude to Bach's Cello Suite No.
+1 — beautifully.
+
+"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer.
+"Well, we shouldn't throw away people either." \quotes{The world send us garbage.
+We send back music}.
+
+[Critics] This project can be seen as a bricolage practice.
+They build their musical instruments from what is available around.
+What they create is actually not expected thing from trash.
+This work also can be seen as an example of resistence because playing western classical music with their instruments is very costly.
+To enjoy and play such a music requires economical wealth and it is not possible for everyone.
+They create their opportunites or turn trash to oppornutiy for them.
+Here economical restirictions result in great production boost with creativity.
+After seeing this instruments and listen their music changes peoples mind to the perception of the classical music and the intruments.
+The original items are well designed and perfect.
+They have identical outlook(or view).
+Not only trash is here transformed, but also perception to the trash and instruments are transformed here.
+After that point trash that you know is no longer same trash.
+At the same time with music lives of children are changed.
+They work on unimaginable thing for them.
+Quality of their music is different than the original one.
+
+% Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
+% Beni bu projede etkileyen en önemli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
+yokluk içinden bir şeyler üretmeleri.
+Her ne kadar üretilen müzik aletleri mükemmel olmasalarda onlar için bulunmayacak bir nimet.
+Üretilen ürünün kalitesi gerçekten de endüstriyel standartların altında.
+Müziğin kalitesi diğer kadar olmasa bile farklı bir yaklaşım sunuyor olması önemli.
+Nasıl oluyor da bu aletten bu ses çıkıyor.
+Amatör ruhun getirdiği bambaşka bir algı var.
+Müziğin ötesi, düşündürdüğü bambaşka şeyler var, olaya yeni bir boyut getiriyor.
+Başka bir alanla diğerinin buluştuğunun bir göstergesi.
+
+\todo{indiginazation of western goods here.}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
+        \caption{Sax}
+        \label{fig:landfill_harmonic-sax}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
+        \caption{Violin}
+        \label{fig:landfill_harmonic-violin}
+    \end{subfigure}
+    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
+\end{figure}
+
+% TODO: http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
+% http://www.eloisacartonera.com.ar/ENGversion.html
+\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers.
+\quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets.
+Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
+
+It reminds me that litreary is also a combination of reused thing. Because to create meanings we reuse words and idioms again and again with different combination.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
+  \caption{Books covered by Eloisa Cartonera}
+  \label{fig:EloisaCartonera_Books}
+\end{figure}
+
+%
+%
+\textbf{American Beauty.} The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air.
+It is hard to think of plastic bags as things of beauty.
+\todo{Bunun hakkında daha fazla bilgiye ihtiyaç var.}
+
+%
+% From http://www.thisiscolossal.com/2014/06/historical-fine-oil-portraits-on-crumpled-trash-by-kim-alsbrooks/, http://www.thisiscolossal.com/2015/05/new-historical-portraits-on-flattened-cans-by-kim-alsbrooks/, http://kimalsbrookswhitetrash.blogspot.com.tr/
+\textbf{Paintings on beer can.} Kim Alsbrooks, historical oil portraits on flattened beers cans and fast food containers.
+\quotes{The White Trash Series was developed while living in the South out of frustration with some of the prevailing ideologies, in particular, class distinction.
+This ideology seems to be based on a combination of myth, biased history and a bizarre sentimentality about old wars and social structures.
+With the juxtaposition of the portraits from museums, once painted on ivory, now on flattened trash like beer cans and fast food containers, the artist sets out to even the playing field, challenging the perception of the social elite in today’s society.} \quotes{On technique: The trash is found flat, on the street.
+One cannot flatten the trash.
+It just doesn't work.
+It must be found so that there are no wrinkles in the middle and the graphic should be well centered.
+Then the portraits are found that are complimentary to the particular trash.
+Generally I depict miniature portraits from the watercolor on ivory era (17th-18th century more or less).
+The trash is gessoed in the oval shape, image drawn in graphite, painted in oils and varnished.} I need to mention that this images are very subversing to the perception of us about these images.
+It is unexpected way of presenting images.
+There is a relationship with the image and painting.
+At least this work questioned this relation.
+With tihs work one can ask that with the painting trashed can become valueable thing or with this can this paintiing became valueless.
+Artsist combines two thing that can be never thought together.
+New combination, new meaning.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[height=6cm]{graphics/Alsbrooks.jpg}
+  \caption{The White Trash Series by Kim Alsbrooks}
+  \label{fig:Alsbrooks}
+\end{figure}
+
+%
+% ARTWORK http://timgaudreau.com/2012/trash/trash.html
+[Self-Portrait as Revealed by Trash] Even if most of people pay little attention to the trash, everybody do not.
+An artist takes photos of his every trash, like a popular habit that is taking photos of face everyday.
+He focuses on the thing that paid little attention.
+At the end he exhibits all the photos by covering all the walls of room.
+It can seen as record of his activities, record of commodities.
+Most of them we are not aware of them.
+Draw the attention of is being thrown away and every time and everywhere.
+They are too much and can only fit covering all the walls.
+\todo[inline]{Tim Gaudreau Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
+These collections of grids represent my first experiments with using those images.
+This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
+
+% act of taking a picture of every single item that I threw out became something else that I can't quite put my finger on.
+It became more than a chore; it became part of my life (albeit, a bit awkward on first dates).
+
+%  Did this project change your behavior?
+Yes!
+At the beginning of this project, on an average day, I would consume: (1) cup of iced coffee, (2) bottles of water, (1) bottle of iced tea and (1) bottle of a sports drink.
+After photographing so many plastic bottles, there came a point when I couldn't bear to admit throwing out another one.
+As I came to understand the flow of my plastic trash, I started by cutting back everywhere I could.
+I stopped using plastic and foil wrap in my kitchen; I started mixing my own iced tea from concentrate; Drinking water came from gallon jugs rather than pint bottles, then ultimately just tap water.
+Then I switched my morning coffee to a rather beautiful reusable ceramic mug and to mixing my own sports drink from powder.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
+  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
+  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+\end{figure}
+
+\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure.
+Garbage dump or gold mine?
+The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource.
+Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear.
+In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization.
+For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden.
+In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.
+
+Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
+Pavilions, villages of huts and even whole houses are appearing over night.
+Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources.
+In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation.
+Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning.
+Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible.
+Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.
+
+% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
+Public space is under siege.
+The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities.
+In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation.
+Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.
+
+Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
+Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures.
+The work will be an act of resistance to occupy and reclaim a space and change its meaning.
+At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.
+
+For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
+
+Public space and transformed materials.
+
+% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
+Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
+The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.
+
+They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
+In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces.
+And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.
+
+%
+% http://www.tate.org.uk/art/artworks/nelson-the-coral-reef-t12859/text-summary
+% \textbf{The Coral Reef} Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London.
+The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says.
+(It is very corralate between Ages Varda's work.
+She shows at the side of human practice, Nelson looks the topic from object side.)
+
+% FROM Paola Ibarra, ReVista
+% Forever; Blue Yonder by artist Kyle Huffman
+% Too Too---Much Much by Thomas Hirschhorn
+% Autoconstrucción by Abraham Cruzvillegas
+
+% FROM Burning Messages BY MICHAEL WELLEN, ReVista
+% Antonio Berni
+
+% Bu adamın ilkeleri var. Benim de var aslında.
+% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
+% https://www.youtube.com/watch?v=v6IoEF_Tsrw
+% Nick Quijano has some rules to create assemblages.
+\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
+As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
+Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
+
+% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
+% Haiti.
+When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
+It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
+When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
+When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
+It shows that working with trash and being clean healthy is not a contradiction.
+Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
+
+% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
+% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
+In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
+These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
+The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
+Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
+It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
+
+% \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
+"Free is certainly great, and that was a driving force for me early on in my career," he said.
+
+% \textbf{SOUP} Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
+The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
+
+% http://www.keaggy.com/chairs/sad/12/
+% \textbf{Sad chair.} Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
+
+% \textbf{ArtBin} Chris Jordan [Trashing Things]
+%****************************************
+% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
+% Michael Landy's Art Bin uses a art gallery to create his dust bin.
+Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
+Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
+"There's no hierarchy once they are in the bin" All of them are accepted as same.
+Ultimate equality.
+Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
+Nothing's too good for the art bin.
+Everything can fit into the art bin.
+Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
+As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
+It is a very big glass bin and isolates people.
+There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
+There is no limitation of throwing away even if art.
+
+% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
+%........................................
+
+% \textbf{Squeezing}
+
+%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
+% \textbf{Found in Nature} Barry Rosenthal
+
+% \textbf{Compression} César Baldaccini [Trashing Things]
+
+% \textbf{Found Photos}
+
+%
+%
 \section{The case of \quotes{The Gleaners and I}}
@@
 %%%
-\section{Examples from contemporary artists}
-Artist and artworks related with trash and their analysis.
-Stages of their works and methods.
-(Keep in mind that what can be extracted from these works?) There are a lot of work that needs to mentioned here but to stay focused and not to move away from the scope of the thesis only the works are selected with relation to the theory chapter.
-(is it really like that?)
+\section{Summary}
+% Turning art making process to a life practice\ldots
 
-% FROM ReVista
-Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.
-
-% FROM Paola Ibarra ReVista
-Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
-Is there a limit to recycling and representation?
-Or is there a point at which waste cannot become art (or anything else)?
-
-% TODO Naive debate??
-All that can be seen as naive act because of little impact and outside of the system(which system?).
-As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill.
-However this very argumentative that having no impact or little impact.
-It might be true that this practices solve all problems of landfill or etc.
-But changes individuals and communities life.
-It recreate and rebuilds the community.
-Even if it is one simple object worth look and see the opportunities of it.
-
-\begin{itemize}
-% FROM Maite Zubiaurre, Re Vista Garbage
-\item \textbf{Road Kill.} Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement.
-It is that particular type of trash meet in the public places.
-trash left behind, trash on the sidewalk, squished, squashed, and weathered.
-Filomena Cruz sees trash that we don’t want to see.
-A piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.
-
-% They are continuously changing. Unrecognized things. Created unintentionally. Part of the streets roads. It can be seen as a archive.
-
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-      \caption{Road Kill by Filomena Cruz}
-      \label{fig:FilomenaCruz_RoadKill_ReVista}
-  \end{figure}
-
-%\item Pictures of Garbage by Vic Muniz
-\item \textbf{Pictures of Garbage.} Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010) Waste Land, directed by Lucy Walker  tracks the development of a series of monumental photographic portraits made from trash.
-Called “Pictures of Garbage,” they were created by Mr.
-Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America.
-(Important point is here collaboration with the pickers.
-Listening their stories and capturing their portraits.
-What is specific about trash here?)
-
-% Talking with people picks up trash. Goes to landfill?
-
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.5\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
-      \caption{Pictures of Garbage by Vic Muniz}
-      \label{fig:VicMuniz_PicturesOfGarbage}
-  \end{figure}
-
-\item \textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra”.
-``The world send us garbage.
-We send back music''.
-
-Cateura, Paraguay is a small city that has grown atop a massive dump.
-It is regarded as one of the poorest slums in Latin America, a village where people live among a sea of garbage.
-Incredibly, the landfill itself is the primary form of subsistence for many residents, who pick through waste for items that can be used or sold.
-Prospects for most of the children born in Cateura is bleak as gangs and drugs await many of them.
-But then one day, something amazing happened.
-A garbage picker named Nicolás Gómez (known as “Cola”) found a piece of trash that resembled a violin and brought it to musician Favio Chávez.
-Using other objects collected from the dump, the pair constructed a functional violin in a place where a real violin is worth more a house.
-Using items gleaned completely from the dump, the pair then built a cello, a flute, a drum, and suddenly had a wild idea: could a children’s orchestra be born in one of the most depressed areas in the world?
-As you can guess, the answer was yes.
-
-To view scenes from the landfill slum of Cateura in Paraguay is to look into the depths of extreme poverty.
-But within the contents of the landfill are glimmers of hope in the form of cardboard, utensils and other discarded materials that can be crafted into imperfect but usable musical instruments.
-These makeshift violins, flutes and cellos, combined with instruction from a local music teacher, have given birth to the Recycled Orchestra of Cateura.
-Through the music of Mozart, Beethoven and Vivaldi, this orchestra allows the young musicians to transcend their identity as children of poverty.
-
-"A violin is worth more than a house here," says Favio Chavez, the orchestra's director and founder.
-In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
-"My life would be worthless without music." says one girl in pigtails.
-A young man named Juan Manuel Chavez, nicknamed Bebi, has a cello fashioned out of an oil can and old cooking tools.
-For the camera, he plays the Prelude to Bach's Cello Suite No.
-1 — beautifully.
-
-"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either."
-
-This project can be seen as a bricolage practice. They build their musical instruments from what is available around.
-
-Resistance'a bir örnek. Çünkü müzik yapmak para isteyen bir şey mi? ya da bir senfoni orkestrası kurmak?
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
-        \caption{Sax}
-        \label{fig:landfill_harmonic-sax}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
-        \caption{Violin}
-        \label{fig:landfill_harmonic-violin}
-    \end{subfigure}
-    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
-\end{figure}
-
-% Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
-% Beni bu projede etkileyen en önemli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
-yokluk içinden bir şeyler üretmeleri.
-Her ne kadar üretilen müzik aletleri mükemmel olmasalarda onlar için bulunmayacak bir nimet.
-Üretilen ürünün kalitesi gerçekten de endüstriyel standartların altında.
-Müziğin kalitesi diğer kadar olmasa bile farklı bir yaklaşım sunuyor olması önemli.
-Nasıl oluyor da bu aletten bu ses çıkıyor.
-Amatör ruhun getirdiği bambaşka bir algı var.
-Müziğin ötesi, düşündürdüğü bambaşka şeyler var, olaya yeni bir boyut getiriyor.
-Başka bir alanla diğerinin buluştuğunun bir göstergesi.
-
-% Peki bu iş neden sanat işi olsun ki?
-
-% Bambaşka şeylere dönüşen ürünler.
-Üretim amaçlarının dışında.
-Yeni linkler bağlantılar kuran müzik aletleri.
-Kendilerinden beklenmeyeni başarmak vs.
-Daha önce görülmeyen şeyler, görülmeyen ilişkiler.
-
-% Bunu bir okuyabilirsin.
-% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
-% http://www.eloisacartonera.com.ar/ENGversion.html
-\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
-urban pickers (\textit{cartoneros}) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
-
-It reminds me that litreary is also a reuse concept.
-Because to create meanings we reuse words and idioms again again with different combination.
-\comment{tüm kelimeler vs hepsi sıralanıyor.
-Arka arkaya getiriliyor.
-Kelimeler harflerin hepsi tekrar tekrar kullanılıyor.
-Reused cartbord reminds all of these and as an object all of it...}
-
-\todo[inline]{Bu ne anlama geliyor onu bulmak gerekli. nereye bağlamalı bilemiyorum. Bu ileri dağıtmak gerekiyor ama gene de burada kalanlar var. Ne yapsam ki?}
-
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
-      \caption{Books covered by Eloisa Cartonera}
-      \label{fig:EloisaCartonera_Books}
-  \end{figure}
-
-% FROM Paola Ibarra, ReVista
-%\item Forever; Blue Yonder by artist Kyle Huffman
-%\item Too Too---Much Much by Thomas Hirschhorn
-%\item Autoconstrucción by Abraham Cruzvillegas
-
-% Bu adamın ilkeleri var. Benim de var aslında.
-% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
-% https://www.youtube.com/watch?v=v6IoEF_Tsrw
-%\item Nick Quijano has some rules to create assemblages.
-\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
-As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
-Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
-
-% FROM Burning Messages BY MICHAEL WELLEN, ReVista
-%\item Antonio Berni
-
-% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
-\item Haiti case.
-When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
-It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
-When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
-When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
-It shows that working with trash and being clean healthy is not a contradiction.
-Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
-
-% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
-% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
-In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
-These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
-The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
-Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
-It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
-
-\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.
-
-% Recycled art.
-%\item \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
-"Free is certainly great, and that was a driving force for me early on in my career," he said.
-
-% http://www.tate.org.uk/art/artworks/nelson-the-coral-reef-t12859/text-summary
-\item Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London.
-The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says.
-(It is very corralate between Ages Varda's work.
-She shows at the side of human practice, Nelson looks the topic from object side.)
-
-\todo[inline]{very important maybe the second case will this one.}
-
-% From http://www.thisiscolossal.com/2014/06/historical-fine-oil-portraits-on-crumpled-trash-by-kim-alsbrooks/, http://www.thisiscolossal.com/2015/05/new-historical-portraits-on-flattened-cans-by-kim-alsbrooks/, http://kimalsbrookswhitetrash.blogspot.com.tr/
-\item
-\parbox[t]{
-	\dimexpr\textwidth-\leftmargin}{%
-      \vspace{-2.5mm}
-      \begin{wrapfigure}[22]{r}{0.4\textwidth}
-        \centering
-        \vspace{-\baselineskip}
-        \includegraphics[width=\linewidth]{graphics/Alsbrooks.jpg}
-        \caption{The White Trash Series by Kim Alsbrooks}
-      \end{wrapfigure}
-Kim Alsbrooks, historical oil portraits on flattened beers cans and fast food containers.
-\quotes{The White Trash Series was developed while living in the South out of frustration with some of the prevailing ideologies, in particular, class distinction.
-This ideology seems to be based on a combination of myth, biased history and a bizarre sentimentality about old wars and social structures.
-With the juxtaposition of the portraits from museums, once painted on ivory, now on flattened trash like beer cans and fast food containers, the artist sets out to even the playing field, challenging the perception of the social elite in today’s society.} \quotes{On technique: The trash is found flat, on the street.
-One cannot flatten the trash.
-It just doesn't work.
-It must be found so that there are no wrinkles in the middle and the graphic should be well centered.
-Then the portraits are found that are complimentary to the particular trash.
-Generally I depict miniature portraits from the watercolor on ivory era (17th-18th century more or less).
-The trash is gessoed in the oval shape, image drawn in graphite, painted in oils and varnished.} I need to mention that this images are very subversing to the perception of us about these images.
-It is unexpected way of presenting images.
-There is a relationship with the image and painting.
-At least this work questioned this relation.
-With tihs work one can ask that with the painting trashed can become valueable thing or with this can this paintiing became valueless.
-Artsist combines two thing that can be never thought together.
-New combination, new meaning.}
-
-% Yav biraz da tarihsel fotoğraflara ihtiyaç var mı? aslında bu artworkleri anlatiştaki sıra nasıl olmalı.
-
-% Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
-The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
-
-% http://www.keaggy.com/chairs/sad/12/
-\item{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
-
-\item Martin Kaltwasser \& Folke Föbberling: City As a Resource.
-One Man's Trash Is Another Man's Treasure.
-Garbage dump or gold mine?
-The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource.
-Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear.
-In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization.
-For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden.
-In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.
-
-\todo[inline]{One Man's Trash Is Another Man's Treasure. bu kısım rubbish theorydede geçiyordu. bunu bir şekikde sonra kullabilirsin.}
-
-Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
-Pavilions, villages of huts and even whole houses are appearing over night.
-Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources.
-In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation.
-Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning.
-Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible.
-Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.
-
-% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
-Public space is under siege.
-The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities.
-In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation.
-Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.
-
-Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
-Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures.
-The work will be an act of resistance to occupy and reclaim a space and change its meaning.
-At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.
-
-For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
-
-Public space and transformed materials.
-
-% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
-Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
-The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.
-
-They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
-In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces.
-And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.
-
-% Sample phrases
-% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
-Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
-With recycled objects, one can build anti-seismic and energy efficient houses.
-Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
-There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
-Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
-Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
-David Hertz reused the wings of a 747 as roof for a villa in Malibu.
-TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
-Yatin Pandya and Footprints E.A.R.T.H.
-built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
-James & Mau and Infiniski designed fashion homes with recycled containers.
-The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
-The GAD.
-In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
-The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
-All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.
-
-\end{itemize}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
-  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
-  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
-\end{figure}
-
-% ARTWORK http://timgaudreau.com/2012/trash/trash.html
-[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if most of people pay little attention to the trash, everybody do not.
-An artist takes photos of his every trash, like a popular habit that is taking photos of face everyday.
-He focuses on the thing that paid little attention.
-At the end he exhibits all the photos by covering all the walls of room.
-It can seen as record of his activities, record of commodities.
-Most of them we are not aware of them.
-Draw the attention of is being thrown away and every time and everywhere.
-They are too much and can only fit covering all the walls.
-\todo[inline]{Tim Gaudreau Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
-These collections of grids represent my first experiments with using those images.
-This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
-
-% act of taking a picture of every single item that I threw out became something else that I can't quite put my finger on.
-It became more than a chore; it became part of my life (albeit, a bit awkward on first dates).
-
-%  Did this project change your behavior?
-Yes!
-At the beginning of this project, on an average day, I would consume: (1) cup of iced coffee, (2) bottles of water, (1) bottle of iced tea and (1) bottle of a sports drink.
-After photographing so many plastic bottles, there came a point when I couldn't bear to admit throwing out another one.
-As I came to understand the flow of my plastic trash, I started by cutting back everywhere I could.
-I stopped using plastic and foil wrap in my kitchen; I started mixing my own iced tea from concentrate; Drinking water came from gallon jugs rather than pint bottles, then ultimately just tap water.
-Then I switched my morning coffee to a rather beautiful reusable ceramic mug and to mixing my own sports drink from powder.
-
-%****************************************
-% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
-
-% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
-%........................................
-
-\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}
-
-%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
-\todo[inline]{Showing trash as they are, or a database\ldots [Artwork] by Barry Rosenthal}
-
-[Çöpleştirme, heykelleştirme.] not all artist transform, some of them use them as they are.
-further some of them trashes things.
-[squeezing, artbin.] As we can think that trash is valuess.
-But the works of cesar claims that opposite of it.
-In his work he sequuzes objects and commodities.
-Makes them useless and functionless.
-But they earn great value in different value systems.
-
-In the literature generally focused topic is to analysis of transformation of trash to treasure (trash->treasure) but at the same time the opposite way is also exist.
-
-%*****************************************
-% Maybe...
-% Artistic tactics
-% Topology of artworks
-%*****************************************
-
-%%%
-%%%
-%%%
-\section{Summary}
-Are artworks made from trash just examples of collage and assemblage or more than from them?
-What about the experience and interaction with other people?
-Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created).
-But all of them work in fragments, combine many objects together.
-
-Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
-
-In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.
-
-(Trash has a history. They have different stories. But same destiny?)
+% TODO MOVE another chapter.
+% Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
 
@@
 
-%%
-%%
-\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
+"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
+
+%
+%
+\textbf{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
 \begin{itemize}
@@
 toplumun davranışlarına karşı bir cevap, görülmeyen, veya farkedilemeyen unutulup giden bir hale getiriyor.
+
+[Çöpleştirme, heykelleştirme.] not all artist transform, some of them use them as they are.
+further some of them trashes things.
+[squeezing, artbin.] As we can think that trash is valuess.
+But the works of cesar claims that opposite of it.
+In his work he sequuzes objects and commodities.
+Makes them useless and functionless.
+But they earn great value in different value systems.
+In the literature generally focused topic is to analysis of transformation of trash to treasure (trash->treasure) but at the same time the opposite way is also exist.
+
+% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+Recycling has always been a common practice in the arts at least at a non-material level.
+From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
+Take and put.
+De-contextualize and re-contextualize.
+In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].
+
+%
+% Sample phrases
+% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
+Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
+With recycled objects, one can build anti-seismic and energy efficient houses.
+Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
+There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
+Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
+Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
+David Hertz reused the wings of a 747 as roof for a villa in Malibu.
+TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
+Yatin Pandya and Footprints E.A.R.T.H.
+built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
+James & Mau and Infiniski designed fashion homes with recycled containers.
+The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
+The GAD.
+In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
+The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
+All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.

### 2015-12-06 chapter1_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@
 %
-[Every.] \paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others \cite{zimring2012encyclopedia}.}
+\comment{[Every.]}
+\paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes \cite{zimring2012encyclopedia}.}
 
-Trash in every age and every society.
-Refuse is part of people's consumption practices and it is very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}.
+Trash exists in every age and every society.
+Refuse is part of people's consumption practices and it is a very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}.
 For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.
@@
 During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated.
-The pattern is spread to the all day and different places.
-It is hard to say that any location(place) is waste free.
+Different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes and that become invisible.
+We are surrounded by all kinds of consumer goods.
+We are consuming everywhere while walking, working and traveling.
+The pattern is spread to all day and different places.
+It is hard to say that any (place) is waste free.
 Nearly every place people require waste bin.
-If we do not find a waste bin, people often leave it (to the ground?).
+If people do not find a waste bin, people often leave it (to the ground?).
 Production of trash never stops.
+It is inseparable from people's activities.
 
@@
 Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}.
-Even if trash is tried to be moved away from people life, it is close as closest waste bin.
+Even if trash is tried to be moved away from people life, it is close as nearest waste bin.
+
+\comment{[Global.]}
+\paraphrase{It is not limited with geography, ethnicity, gender, nationality.
+The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.}
+
+%
+% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
+\comment{[Facts.]}
+\paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
+Turkey is a member of this organization.} countries produce almost half of the world’s waste.
+Africa and South Asia produce the least waste.
+High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
+Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}
+
+% Üstteki kısmı neden diyorsun? Teze nasıl bir katkı sağlıyor? Throw away culture a taşınabilir.
+% From recycled book.
+\paraphrase{A person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
+America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}}
 
@@
 %
-% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-[Facts.] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
-Turkey is member of this organization.} countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}
-
-\comment{Bunu neden diyorsun? Teze nasıl bir katkı sağlıyor?}
-
-%
-%
-[Common.] (In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded.
+\comment{[Common.]}
+(In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded.
 In parallel to this definition, common perception is to get rid of them as soon as possible.
@@
 From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
+From streets to landfills.
+From waste bins to sculptures.
 Lots of different people touches to trash.
 With the trash what moves?
-Trash moves around.
 Travels like humans.
@@
 When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.
+\todo{summarize here.
+ve bir yere bağla.}
 
 People do not think what happens after they throw trash away.
-\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not the world.
+\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not from the world.
 It is stacked to another place.
@@
 What happens when it is traveled to the other countries, how they approaches these items.
-\comment{They find new uses and meanings on them.} \todo[inline]{consider African native}
+\comment{They find new uses and meanings on them.} \todo{consider African native}
 
@@
 %
-[Aspects.
-Approaches.] In this thesis study to understand the different aspects of trash is a key element.
+\comment{[Aspects. Approaches.]}
+In this thesis study to understand the different aspects of trash is a key element.
 Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed.
@@
 For some people it is disgusting thing and moved away from living space and for the others source of their life.
-\paraphrase{While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
+\paraphrase{While dictionary definitions of garbage describe it as \quotes{filth} and \quotes{worthless}, scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
 
-[Relative.] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
+\comment{[Relative.]}
+As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
 She realized that any of them called the practice as recycling.
@@
 
-[Production of trash and removal of trash.] For example a project conducted by MIT Sensible City Lab.
-reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.
+\comment{[Production of trash and removal of trash.]}
+For example a project conducted by MIT Sensible City Lab. reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.
 
@@
 %
-[Parts of us.] \paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
+\comment{[Parts of us.]}
+\paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
 Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}.
@@
 %
-[Change in the production and consumption practices.] \paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+\comment{[Change in the production and consumption practices.]}
+\paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
 Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced.
@@
 %
-[Art] \paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}
+\comment{[Art]}
+\paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}
 
@@
 
-\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.}
+\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.} \todo{ref missing.}
+
+% TODO new comer
+\paraphrase{This thesis seeks to answer the following questions: How did art and literature respond to this age of consumption?
+What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification (depersonalization), mechanical reproduction, and meaning?
+(FROM Collage Culture)}
+
+Do people want to take back (or revisit) the trash once thrown away? The purpose is to turn them to a things that worth to reconsider.
+
+Questioned that how do artists reflect garbage and what are their tactics?
 
@@
 %
-[Different types of trash] There are different types of trashes.
-Result of different production and consumption practices different trashes are generated.
+[Different types of trash] There are different types of trashes result of different production and consumption practices.
 For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}.
@@
 As it can be seen that there are lots of different types and as various as activities of human.
-In this scope of thesis \ldots \todo{Ben hangisini kullanacağım.
-Buna burada değinmek gerekli mi?}
+In this scope of thesis focused on disposable items and paper trash.
 
@@
 \paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.} \todo{ref.}
-
-Increasing ecological concerns is one of the aspects of trash. As most of trash last decades are not easily decomposable. Relases toxics and other things.
 
@@
 They collect and sell them to survive.
-There are companies that are collect waste materials to regain them again the industry.
+There are companies that are collect waste materials to regain them to the industry.
 In thesis they are not in the scope.
@@
 
-%
-%
-[Scope] Human discard. In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.
+% TODO new comer
+% PERCEPTION TO THE TRASH, DICIPLINES
+\comment{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
+In other word the problem is our technology which is not perfect.
+(and I'm not sure that at some point that technology will reach to the perfection or not.)
+
+% TODO new comer
+\comment{TECHNICAL PROBLEM, NEED TO MANAGED, RECYCLING (CAPITALISM), UPCYCLING} \paraphrase{On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
+The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
+Waste now became evil.
+If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
+Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
+Upcycling...
+On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
+Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
+In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
+In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+% TODO new comer
+\comment{DESIGN, ALTERNATIVE DICIPLINE.} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+% TODO new comer
+\comment{UPCYCLING, sample thesis statement sentence} \paraphrase{This article is about those objects that are recreated from trash through the process of upcycling.
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of.} \todo[inline]{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}
+
+% TODO new comer
+% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{OTHER DICIPLINE, INDUSTRY} \paraphrase{the process of re fabrication explored here is not to be confused with the kind of industrial strength recycling to which we in the West are most accustomed.
+When we think of recycling in America and other industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers.
+returned to the industrial process.
+solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.}
 
@@
 By the way it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
-
-% TODO Move to chapter 4.
-\comment{Research and the found samples of works helped a lot to shape my work.
-They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}
 
@@
 \section{A Note on Terminology}
-Many scholars and authors have used different words (or terminology) to define trash\todo{bunun yerine başka bir şey demek gerekir mi?}.
+Many scholars and authors have used different words (or terminology) to define trash.
 Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them.
@@
 
-\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
-Analysis of them may be subject of another thesis.}
-
 \comment{What were people throwing out when these words were coined?}

### 2015-12-06 chapter2_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@
 Theoretical foundations of trash (Rubbish Theory) are discussed.
-Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with help of ideas of philosophers (Zizek).
+Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with the help of ideas of philosophers (Zizek).
 Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash.
@@
 \section{Throw away culture}
-[What is questioned in this section?] Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?
+Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?
 
@@
 %
-[Disposable items.] \comment{Disposable: made to be used once or only a few times.
+\comment{[Disposable items.]}
+\comment{Disposable: made to be used once or only a few times.
 Made to be thrown away after one use or several uses.
@@
 \todo{ref.}}
+
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\comment{LIFE AN OBJECT} \paraphrase{In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
+This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
+In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+\comment{[Capitalism, market.]} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
+This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
+themselves.
+\todo{Waste and wantta bununla ilgili bir bölüm olmalı.}
+
+\comment{[Initial function.]} 
+When an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
 
@@
 
-[Factors.] \comment{Not only one factor, technological advacements can be one of them.
+\comment{CONSUMER CULTURE}
+\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these thesis are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}
+
+%
+%
+\comment{[Factors.]}
+Factors that cause over consumption habits.
+Technological advacements can be one of them.
 These items with the help of industrialization can be produced easily.
@@
 Therefore there is no need to save the old one.
-Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.} \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref.
+Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.
+\paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref.
 ontology of trash}
@@
 
-[Art] There are some artists whose works are related with the pheomena expressed above. (Some of the works of artist can be examined in this pheomena.)
+%
+%
+[Art] There are some artists whose works are related with the pheomena expressed above.
+(Some of the works of artist can be examined in this pheomena.) Not every people throw away disposible objects, some of them save them and use for their own purposes.
 
@@
 There is a great diversity of trashes and offers new alternatives.
-
-Not every people throw away disposible objects, some of them save them and use for their own purposes.
 
@@
 %
-\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of peoples life.
-What people consume is actually tells many things about them \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}.
+\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of people's life.
+What people consume is actually tells many things about them (their choices, possessions etc.) \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}.
 As scholars mentioned that throughout the discards of someone else many thing can be understand.
@@
 
+% TODO need relocation
+% FROM Culture, Values, and Garbage, Encyclopedia 
+%\comment{INTERACTION WITH GARBAGE. VALUE SYSTEM, DECIDING TO GARBAGE.}
+%\paraphrase{"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
+In terms of their relationship to garbage, all people interact with it on two levels.
+One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
+In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
+Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
+The second connection that people maintain with garbage is an ideational one.
+Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
+The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
+Instead, humans determine whether the object is of value or whether it is considered trash.
+The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
+The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}
+
+% TODO need relocation.
+% FROM Garbage in Modern Thought, Encyclopedia
+%\comment{THROW AWAY CULTURE.} 
+%\paraphrase{Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.” "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
+It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
+Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
+
+% TODO need relocation.
+% FROM Garbage in Modern Thought, Encyclopedia
+%\comment{CATEGORIZATION.} \paraphrase{"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
+Consumers have become accustomed to the categories that are often applied to garbage.
+Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper).
+Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}}
+
+% TODO need relocation.
+% Garbage is universal.
+%\comment{NO VALUE, UNIVERSAL} \paraphrase{"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
+Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
+While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
+Many non-Western societies attach a much greater value to items after they are discarded.
+In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
+Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
+People define what is trash and what is valuable." \cite{lukas2012garbage}}
+
+\todo[inline] transition required.
+
 %
 %
-[GARBOLOGY] Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
+\comment{[GARBOLOGY]}
+Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
 
@@
 
-\todo{transition needed.} With the help above understanding of trash, what can we see the work of arts. For examples tracey emin.
+\todo{transition required.} With the help above understanding of trash, what can we see the work of arts?
 
@@
 The work, which Emin now describes as a portrait of a young woman.
-It is a time capsule.
-The cigarettes that litter the floor will one day no longer exist; neither will the newspapers.
 Around her there are pieces of junks speared all over the room.
@@
 \section{Zizek's Approach to Rubbish}
-[Transition, introduction] 
-\todo{Adam bir transition bulmalı buraya.} Last decades increasing attention the the ecology and rubbish.
+\todo[inline]{transition required.} 
+Last decades increasing attention the the ecology and rubbish.
 This section is related with the increasing interest on ecology.
@@
 These types of news and talks increasingly find a place on media more and more.
-Zizek comments on ecology and trash.
+At this stage Zizek comments on ecology and trash conversly .
+
+% TODO new comer
+% \paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}
 
 In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London.
-His part starts with these sentence: \quote{This [garbage dump] is where we should start feeling at home}.
+His part starts with these sentence: \quotes{This [garbage dump] is where we should start feeling at home}.
 
@@
 
-Transforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.
+Transforming trash is not related with ecological perspective. We are not trying to save the planet earth. Beyond ecological concerns we are trying to find ways to live our trash.
 
@@
 In this thesis transformation of trash is claimed and this theory provides a framework for this transformation.
+
+% Rubbish theory'de durable dediğimiz bir kategori var.
+mesela picassonun sözü de buna bir şekilde karşı duruş sergiliyor.
+Çünkü dönüştürmenin devamlılığını arzuluyor.
+Ama durable olan şeyin bir konumu sabitlenmiş oluyor herhalde.
+
+% TODO new comer.
+%\comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
+The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.
+
+% TODO new comer
+\comment{MOVES.} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}
+
+% TODO new comer
+\comment{MOVES.} \paraphrase{Objects moves around and their values change constantly.
+(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
+The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}
+
+% TODO new comer
+% BAZI KISIMLARINI AÇMAK GEREKLİ AMA.
+\comment{MOVES.} Here the important thing is moving nature of trash.
+Objects moves and gains different meanings through this movement.
+Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
+It also signifies that it is relative and result of a classification issue.
+
+% TODO new comer
+% From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
+\comment{MOVES.} \paraphrase{Below part explains journey of trash in different steps/stages.
+Object moves and trash also moves.
+How is it life of trash?
+This part explains life of trash.
+How does it intersect with other people in which places?
+This part also can be understand by pointing out different part of it with detailed explanation.
+For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
+In other words there are different places to touch on trash.
+Every place generates different story?
+Or to understand it more deeply it covers different part of it.
+Or provides ideas about it.
+Lots of people touches it from philosophers to artist.
+Also in the later parts it draws attention to them.}
+
+% TODO new comer
+% Ama çöp olarak zaten kalmıyor.
+Bir şekilde hayatımıza tekrar giriyor.
+Ne kadar itise de...
+Trashion: the return of disposed.
+Peki geri dönüşü nasıl bir değişiklik yaratıyor.
+Ya da gerçekten geri geliyor mu?
+Kullandığımız ürünlerin ne kadarı tek kullanımlık.
+Tek kullanımlıklarla nerede karşılaşıyoruz.
+Evet belki hayatımızda çok kullanılan şeyler var fakat.
+Daha tek kullanımlıklar da var denilebilir.
+\comment{TRASH MOVES.} \paraphrase{Trash moves, all the time.
+It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
+Even in the landfill, it does not remain still.
+Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
+More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
+When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
+This is how trash moves.
+But\ldots who moves on trash?
+In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
+In Latin America, it is mostly people.
+People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
+In many of the garbage dumps around the world, scavenging becomes a steady job.
+\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
+(through the works of Filomena Cruz's photographic series “Road Kill”)}
+
+% TODO new comer
+\comment{CATEGORIZATION OF WASTE} \paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+(Think that the transformation process.
+Previous argument support that the transformation of trash is possible by changing the place of them.
+In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
+For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.} \todo{Reference, (Waste by William Viney).}
+
+% TODO new comer
+\comment{CATEGORIZATION OF WASTE} \paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
+
+% TODO new comer
+\comment{CATEGORIZATION OF WASTE} \comment{susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
+Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
+Remember the example given: shoes  on the dinner table.}
+
+\comment{CATEGORIZATION OF WASTE} \paraphrase{waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
+
+\quotes{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
 

### 2015-12-06 chapter3_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@
 
+% Bicycle wheel duchamp 1913.
+
 % TODO paraphrase
@@
 \todo{read greenberg1984collage}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{hybrid} each recycled object contains within it a reference to two or more distinct times.
+\comment{not every time actually, if you transfor ok.
+it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{ref.}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{HYBRIDITY} \paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another.
+Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
+It is story of people --- the women, men, children etc.
+one person's trash into another's treasure.}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{HYBRIDITY} They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{SEMIOTIC CONTEXT} \quotes{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)} \todo{ref.}
+
+% TODO new comer
+\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
 
@@
 
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
+From western trash to tribal treasure.
+\paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods.
+A disposable item becomes imminent desire and profound social consequence.
+(Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
+It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\todo{yerlinin fotoğrafı}
+\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}
+
+%(Summary From Paul M Camic.) 
+The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
+It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
+The junk object becomes transformed into the valued found object.
+Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
+His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
+97) and labeled it a work of art.
+A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
+These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
+
+Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
+169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
+170).
+The finder discovers an unrealised significance in the object.
+A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
+He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
+
+How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
+(Important points a gap in the literature.
+Although Parsons article analyze practices, it is not very broad and detailed.
+Further what is the importance of it is missing.)
+
+The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
+The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
+
+Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
+The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
+When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
+Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
+This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
+
+An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
+Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
+
+Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.
+
+% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
+To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
+This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
+
+% Amelie olabilir.
+Orada fotoğraf toplayan çocuk olabilir.
+Onları itinayla toplayan bir adam.
+Tren garındaki fotoğraf kulubesi.
+Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
+Bir birinden farklı bir sürü insan.
+Filmde neden böyle bir eyleme yer veriliyor?
+Film fotoğraflar üzerinden defter üzerinden ilerliyor.
+Onun çevresinden bir hikaye kurgulanıyor.
+İnsanların artıklarını topluyor.
+Onların değer vermedikleri şeyleri topluyor.
+Bunlar baya baya aslında o insanlar.
+Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
+Çok iyi bir örnek mi bilmiyorum.
+Burada niyet nedir ki?
+Ben buna şöyle bir okuma getireceğim diyebilirim.
+Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
+Bu arada bu fotoğraf toplama işi ilk değil.
+Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
+Ama benim işime yarayan kısmı ne?
+Neden o fotoğrafları ya da bunun filmini yapıyor.
+Aslında puzzlelar üretiyor.
+Belirli tekrar olacaktır.
+insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
+Tekrar bir kitap haline geliyor.
+Tanınmayan insanların fotoğrafları.
+Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
+Aslında tam da amelie bunu yapmıyor mu?
+Hikayeler üretiyor bu fotoğraflardan.
+Yeni karşılaşmalar üretmesi.
+Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
+Bin bir türlü şey vardır aralarında.
+Nereye yerleşmeli.
+Başkasının çöpünü toplama.
+O dönemin o eşyasını arşivini tutma.
+ve herkes sunuluyor sonrasında bu.
+
 %
@@
 Therefore what are their purpose and how they can be viewed?
+
+% not easily understandable with the entering non-art objects in art.
+artist are responding the current societies habits in a different ways.
+what they are doing here is to see other possibliteis and show actually what is going on.
+what does it mean all of these things.
 
@@
 
+% TODO new comer.
+[indigenization] the indigenization of western objects.
+(sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"?
+Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves.
+They do not necessarily despise our commodities.
+But they are selective in their demands and transformative of their uses of such things.
+(sahlins, 13)"
+
+\comment{This is a proff of the transformation of the original concept.}
+
+% TODO new comer.
+[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse.
+but even if they have no economical struggle, they continue recycle.
+what is the reason of it?} Recycling as an economic strategy of survival in developing countries throughout the world.
+creative production that is motivated, primarily, by adverse conditions of economic necessity.
+(lanfill orchestra here.
+bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised.
+(p25)
+
 % Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
@@
   \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+\end{figure}
+
+[Chrish Jordan Break Down inventory] \paraphrase{Not all artist transform trash although some deconstruct them.
+Michael Landy is one of them.
+Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
+Reveal all his possessions.
+and loosing them while you are alive.
+Turning them to rubbish making them unusable.
+breaking down the all the meaning.
+breaking down the connections.} It can be an example of downcycling process.
+It is preferred to decompose all the complex link and relationships between the objects.
+They are not just ordinary things they are possessions of artist.
+Break Down 2001, in which he systematically destroyed all his personal possessions.
+His work examines what we value and what we discard, consumerism and waste, and human labour and its worth.
+It happens in public space.
+People can see the process.
+This process last 2 weeks.
+Places where people buy things actually.
+
+%\comment{Tüm sahip olduklarını yaşarken kendi isteği ile yok ediyor. Bu hepimizin paylaştığı bir şey.}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
+  \caption{Chris Jordan, Break Down}
+  \label{fig:ChrisJordan_BreakDown}
 \end{figure}
@@
 
-%
-% Sample phrases
-% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
-Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
-With recycled objects, one can build anti-seismic and energy efficient houses.
-Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
-There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
-Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
-Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
-David Hertz reused the wings of a 747 as roof for a villa in Malibu.
-TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
-Yatin Pandya and Footprints E.A.R.T.H.
-built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
-James & Mau and Infiniski designed fashion homes with recycled containers.
-The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
-The GAD.
-In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
-The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
-All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+[Resistance] \comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+(sahlins 1992, 16)"
+
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+[Ironic] \comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
+the irony is often embodied visually and conceptually.
+opposite of natural use, expected perception.
+for example making something from nothing or turning trash into treasure.
+By juxtaposing different materials changing context and place.
+
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
+It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
+
+% Günlük rutinleri çöp üzerinden yakalayanlar var. Her gün ürettiği çöpün fotoğrafını çeken insan... Ürettikleri çöpleri ifade etme araçları olarak kullananlar.

### 2015-12-06 chapter4_reduced.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

--- 2015-11-22 chapter4.tex
@@
-\chapter{Thesis Project: Notebooks from Trashed Papers}
+\chapter{The Project: Notebooks from Trashed Papers}
 
 %****************************************
-% Structure of Chapter:
-% 
-% Artist Statement
-% Development of Work
-%  Collecting, Transforming, Tests...
-%
-% Final Work
-%  - Notebooks
-%  - Website
-%  - Exhibition
-%........................................
-
-%****************************************
-% Relationship between my project and theoretical aspects:
-% - First one is actually is to analyze what is trash?
-Because I am using trash material and what is point of view of scholars to the trash.
-Realizing the potentials of it.
-Also the difference comes from the working on virgin object and trash object.
-Understanding the difference between the bricolouer and engineer.
-If trash has multiple life than these research will somehow reveal it.
-It is actually research on trash but what purposes.
-I guess it is missing?
-I need to set a purpose for the theory chapter.
-Or it is a just a background chapter?
-% - Roots in the art history. (Also roots on the social life can be researched?)
-% - Inspiration from the other artist and also 
-%........................................
-
-%****************************************
-% Sample Phrases
-% \ldots is the concern of this study which aims to \ldots
-% The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
-% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
-The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
+% TODO proje ismi çok iyi değil onu bir adam etmek gerekli. 
+% Notebook Project; from trash
+% Notebooks from Trashed Papers
+% Notebooks from trash
+% Notebook Project: from trash to treasure
+% Notebook Project: from trash
 %........................................
@@
 
+% Proje nedir, kısaca bahsetmek lazım. Projenin bileşenleri daha sonra detaylı bir şekilde anlatılacaktır. Ama önce nasıl geliştiğine bakalım.
+
 % What I have write is here to cover the project can not be sufficient.
@@
 
-% TODO
-% Felix Gonzales Torres'in untitled işi benim yapmaya çalıştığım ile ilgili.
+\comment{Research and the found samples of works helped a lot to shape my work.
+They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}
 
-%%%
-%%%
-%%% 
-% TODO
 \section{Artist Statement}
-(Collect, Save, Transform, Spread.)(Rescue, Revive)
+(Collect, Save, Transform, Spread.)(Rescue, Revive.)
 
-The work aims to liberate the imagination and change the way people see the trash.
+[Transform] With the help of art (and artistic practices) discarded things can find a place in the society.
+(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) With the help of art discarded things ---in the scope of thesis particularly paper trash--- can be transformed beyond the other industrial (or technological) methods.
 
-% Closest waste bin is actually my own pocket.
+[Work] Converting disposal things to multiple usage (or anything that is durable as noted in the rubbish theory).
+Realizing the alternative lifes of trash beyond their defined one shot life.
+Giving attention to the things.
+\comment{Inquerying concepts and perceptions that are not cared.} The work aims to liberate the imagination and change the way people see the trash.
 
-% Converting disposal things to multiple time usage. Realizing the alternative lives of trash beyond their defined one shot life. Giving attention to the things.
+[LIFE PRACTICE, CHANGES ON PEOPLE] Actually (It is questioned that) the effects of working with trash to the life practice.
+Working with trash is a convergence of behavioral patterns (attitudes toward to trash) and art making.
+The process effects one's life and lifestyle.
+(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) Looking for things and meanings in the normal course of life.
 
-% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir.
-Zaten toplama sürecinde bunu insanlarla ilişki kurarak yapıyorum.
-O insanlarda diğerleriyle konuşarak yapıyorlar.
-
-% At this stage it is claimed that the process of transformation of trash can be treated as artistic act.
-In the production of notebooks people collected papers from different places and location.
-During the collection phase they also collect them from other people.
-In other words there is human communication during this process.
-
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects one's life and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
+[DISTANCE] The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
 The important thing is to interact with it.
-Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it.
+Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it.
+This work must change it.
 It must call the viewer to interact with it.
+Trash must be accepted.
 
@@
 Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki?
-İnsanların bu işin aşamalarının bir parçası olmalılar.
+İnsanlar bu işin aşamalarının bir parçası olmalılar.
 
-With the help of art (and artistic practices) discarded things can find a place in the society.
-(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.)
+[ACT, COMMUNICATION, COLLABORATION] In this work it is claimed that the process of transformation of trash can be treated as artistic act.
+In the production of notebooks people collected papers from different places and location.
+During the collection phase, they have also collected them from other people.
+Communication and collaboration played significant role in the progress.
+(With this communication and collaboration the approach to the trash is explored in different cases.)
 
-% Using trash can not only understand in ecological perceptions, it also have powerful political claims.
-Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
-
-% SEEING IT AS A RESOURCE.
-Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
-Ignored and discarded nature of garbage when rethought becomes fertile resource.
+[NEW RESOURCE] Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
+Ignored and discarded nature of garbage, when rethought, becomes a fertile resource.
 Trash as a resource (as an artistic material).
@@
 Many artist approach to trash as resource.
-It is a shared approach.
 Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)
 
-% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.
+% TODO new comer. [POTENTIAL, new resource]
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+[building new things from ruin] \comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.
 
-Do she/he want to take back (or revisit) the trash once thrown away?
-People do not want to think of what they throw away.
-Turning them to a things that worth to look again.
-How do artists reflect garbage and what are their tactics?
-What is the thing that add value to trash and what is the role of art in that?
+% Belki Chapter 3'e taşınabilir.
+% [Resource, Potentials] I resurrect things that have been killed off...
+My work is all about the potential of materials — even when it looks like they've lost all possibilities.
+(Cornelia Parker) https://en.wikipedia.org/wiki/Cornelia_Parker
 
-With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods.
-In other words autistics practices generates applies different methods.
+% TODO new comer. Statement or approach.
+\comment{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
+Even if they are excluded, there is also life for them.
 
-%%%
-%%%
-%%%
-%\section{Inspired Works}
-%There are some works that inspire me a lot when developing the work.
-They are not actually trash related works therefore I put them in different section and here before the details of my work.
-However the previous chapter has also very inspirational contributions to the my work.
-They helped the understand the topic and develop an approach to the topic.
-In this section some projects are mentioned and their methodologies are explained.
-How are these works effected my work.
-What is the relationship between them?
-(Maybe all of them can be explained only the related part of it.)
-%SketchBook Project.
-Inspires me a lot.
-Lots of works from all over the world.
-Full of creativity and showcase of richness of people's expressions on the small notebooks.
-My work can be considered as a sketch book project through trash.
-Sketches or only creative progress is not the only consideration.
-You can send your lecture notes.
+% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.
 
-% Daha öncesinden ne yaptığımı biliyor olmalı insanlar.
-% Benim kriterlerim nedir?
-% Benim kurallarım nelerdir?
+% Çöpe nasıl yaklaşak gerekli? Bu tezde sorulan sorulardan birisi bu.
 
-%%%
-%%%
-%%%
+%
+%
 \section{Development Progress of Work}
+How does it start?
 How does it evolve in time?
-Important points.
-This progress also reveals the how this work can be positioned among the other works.
-\comment{Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?}
+Important points that shaped the work\ldots This progress also reveals the how this work can be positioned among the other works.
+Choices, interpretations, approaches...
+Encountered problems.
+Experiments with the material.
+% \comment{Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?}
 
-\begin{description}
+It is not a fixed(static) project. It is evolved in time and affected from other artists' work, and gain meaning from research.
 
-%%
-%%
-\item[How is it started?]
+Before explaning the details of the work, it would be better how it was started, what is my approach to the trash and so on?
 
-%%
-%%
-\item[Memories.] As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
+%
+%
+\textbf{How is it started?} As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
 One of these (First of them) is from my primary school teacher.
@@
 Do not throw out packages, look for the useful parts and keep them to use later.
+\comment{Actually people collect things.
+There is nothing strange here.
+They collect what their needs.
+or they will need in the future.
+It is more different than just need.
+It is also self exploration.
+Feeling uncomfortable to buy simple things.
+I can make some of them.
+Looking for alternative, different feeling and texture.}
 
-\item[What do I think about trash?] I need to clarify my approach to the trash, wasting and discarding.
+\comment{I have remembered that we are covering our notebooks at school. Sometimes we also cover the books.}
+
+\comment{Being under pressure of spirit of our age.
+Looking for the everytime most efficient way and best performance.
+Everything can be purchaseble...
+ready, easy to use, easy to throw away.
+no intimate relationships with items objects.
+By trasnforming the disposable items I establish a different connection between them.
+They are replaceable with the other one (Especially it can be seen in the works of TeaBagWork and PaperCoffeeCupWork).}
+
+%
+%
+\textbf{What do I think about trash?} I need to clarify my approach to the trash, wasting and discarding.
 First point is that I am very uncomfortable to the action of discarding thing.
@@
 
-Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}
+Significance of thinking outside of the box (about trash) is actually breaking the loops.
+You have to look at differently from your common perception.
+\textbf{Break the rules, break the loops} to realize the alternative.
+\comment{Even if the market gives many alternatives of commodities, why do people still seek the alternative?
+Is not is enough?
+What type of gap that industrial products can not fill the gaps.
+Neden tüm insanlara hitap etmiyor?}
 
 [Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
-Because it is discarded and undiscovered.
-Wait us to be discarded.
-and possible (as picasso mentioned) discovered again and again.
+Because it is ignored by discarding and therefore undiscovered.
+Wait us to be discovered.
+and possiblely (as picasso mentioned) discovered again and again.
+\comment{Different people from different culture bring new interperation, but it is exist all of things.}
 
-%%
-%%
-\item[Motivation.] I can not throw them away.
+[Motivation.] I can not throw them away.
 When I throw them I became sad for them.
 I have to find something useful for it.
-Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
-We are humans that can produce, transform items.
+(Failure of imagination, failure of making meaning) Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
+We are humans that can able to make meanings, produce something, transform items.
 One of most developed species in the earth that produce and use tools.
-There is a lot of effort to produce thrown away and it seems that all this efforts are wasted.
+There is a lot of effort to produce objects and it seems that all this efforts are wasted.
 What I mention is not related about ultimate productivity.
@@
 
-%%
-%%
-\item[Paper]
-"Paper is an indispensable product throughout the world.
+Beyond everything I make notebook for myself. I am showing(proving) that I can still make things. not everything is stolen from me. It does not steal anywhere.
+
+%
+%
+\textbf{Paper}\todo{Konuyu biraz daha özetle.} [History] \todo{history of trash} The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
+
+[Wide range of use] \paraphrase{Paper is an indispensable product throughout the world.
 Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
@@
 Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
+Paper in several forms is consumed on a daily basis by each person in the Western world \cite{trafford2012paper}.} Having wide range of usage offers great diversity in order to make compositions.
+As they bring their old identity.
 
-\comment{My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.}
+[Uses of Paper] Paper has become the most ubiquitous product in the age of information.
+Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+\comment{Traditionally, newspapers and magazines have been reused as paper for packing; covering different surfaces, such as  windows and furniture; and even as toilet paper.}
 
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
-
+[Production, Recycling] \paraphrase{All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
 Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
@@
 It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
+In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.}
 
-% History of Paper
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
+\paraphrase{Post-consumer paper waste has to be manually sorted  into  different  types,  such  as  paperboard, office  paper,  and  newsprint.
+Staples  are  removed with  a  magnet.
+The  paper  is  chopped  into  small pieces  and  added  to  water  and  chemicals.
+Denser objects that are not paper sink.
+Any inked or colored  papers  must  be  deinked  with  sodium  silicate or  sodium  hydroxide.
+Some  paper  pulp  is  also bleached.
+The effluent of the pulping process, called “sludge,”  includes  chemicals,  inks,  clay  (from glossy paper), plastics, and short paper fibers.
+This sludge can be toxic and is landfilled or incinerated.
+When paper is recycled, the fibers break down and become shorter, requiring the input of virgin material.
+If virgin pulp is not added, the pulp can be used in lower-quality paper products, such as cardboard or newsprint.}
 
-% Production of Paper
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
+[Recycling, effects to the nature] \paraphrase{Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
+However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
+In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
+Further, forest resources are not always as renewable as one may like to think.
+These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.}
 
-% Uses of Paper
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+One of the key elements of the project is paper.
+Notebooks are made from trashed papers.
+Eve if they are discaeded they are still functional.
+There is a increasing intereset on papers because of  biodegrable nature of it(compared to plastic and nylon materials) [it is one of the reasons, not only.].
+Therefore they are becoming more common.
+Mostly they are used as a package to keep safe and isolated commodities.
+Most of them  contain brand's logo and carry the identity of company.
+
+Papers that are mostly blank are used inside of the notebooks for writing.
+Others that have colorful logo and images on them are used as a cover for notebooks.
+\comment{I have also other type of packs such as Starbucks coffee packets.}
+
+All packs are cleaned up. Because it is important that it needs to be safe to use. With mix of water and little bleach they are swabbed.
 
@@
 
-%%
-%%
-\item[Collecting.] One of the most found trash in my habitat is paper.
+%
+%
+\textbf{Collecting.} \comment{When I collect the papers under the dishes or food packages, people often think that it is disgusting and called them as dirty.
+However, it is very strange that the fat on the paper was previously what they are eating.}
+
+One of the most found trash in my habitat is paper.
 I work at METU Technopolis, live at 100.
@@
 
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
+I have stored papers in my rooms. \todo{an image of storage of papers.}
+
+% Why do I collect trash? Why paper? Who wants to keep trash? Who wants to re-see(re-visit) trash again? To use it again.
+
+% [Why do I collect trash?] Herkes neye ihtiyacı var ise onu toplar.
+Ben neden niçin topluyorum?
+Toplama sebepleri?
+Dönüştürme sebepleri.
+Neden sadece toplamakla yetinmiyorum.
+yani toplamak ile ayrıldığı noktalar nelerdir.
+Ben bir mana mı arıyorum?
+Yoksa kaybetmekten mi korkuyorum?
+Yeni kompozisyonlar oluşturmak istiyorum.
+Farklı karşımlar elde etmek istiyorum.
+Bir tür şaşırtmak durumu...
+Beklenmeyeni yapmak...
+En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
+
+% Bilinçsiz bir şekilde mi topluyorum yoksa, bilinçli bir şekilde.
 
@@
 Everyone actually approached positively and somehow they contributed the project.
-How does it differ from asking for their help?
-What type of meaning I add here?
+\todo{How does it differ from asking for their help?
+What type of meaning I add here?}
 
-%%
-%%
-\item[Collected Materials.] There are different papers and objects are used to produce papers.
+% [İnsanları işe dahil etmekle ilgili.] Bu işin olması için ben insanlardan bir şeyler yapmalarını istiyorum.
+Yani aslında kendimde yapabilirim ama neden insanları da dahil ediyorum?
+Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de deönüştürmek gerekmek.
+ve bu bir süreç işi (şart mı tek bir yöntem bu mu?) İnsanlar nasıl değişir diye sormak gerekir o zaman.
+İnsanların değiştiğini dönüştüğünü gerçekten nasıl ölçeceğim ki?
+
+% CROWDSOURSING, CITIZEN SCIENCE
+% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art.
+Table 1 organizes this classification according to a set of multiple criteria.
+(But this one can be used at introduction, but it is too long to fit on introduction.
+Maybe select works by giving prominence to some of the features.
+So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art.
+Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.)
+
+% In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}.
+The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers.
+Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing.
+Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.
+
+% The value of crowdsourcing lies in the collective intelligence of the contributors.
+Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p.
+13).
+The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism.
+Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004).
+Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?
+
+% All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks.
+They are not bought, not gift.
+They are found.
+They are accepted.
+One of the most creative medium is paper and pencil.
+Chance given to the people through this work.
+
+% However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment.
+It is well studied area.
+Pick a method here.
+Transforming trash with collaboration.
+
+% As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).
+
+% Here this question can be raised about why this type collaboration.
+Another option can be working together with people on a table.
+Creating things at that time and transforming the objects here.
+Possibly the connection to the people will more realistic and intense.
+However same things can be succeed on the internet at some level.
+
+% While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers.
+(This totally a new area to discuss, I'm going to summarize and introduce concepts and debates.
+How are they support my work and how they are give way to me?)
+
+% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories.
+Principally, my interest is in answering two key questions.
+What is crowdsourced art and how can it be classified?
+And how does the structure of the artwork determine the degree or significance of participation?
+
+% TODO: Umberto Eco's Open Work
+
+[Criters, rules] There are some rules defines the frame of collecting act. Paper must be trash or going to be trashed.
+
+\textbf{Collected Materials.} There are different papers and packages are used to produce notebooks.
+
+\todo{Tüm buradaki resimleri appendixe eklemek gerekli, hatta bunlar sitede de olacaklar.}
 
 \begin{description}
-  \item[Burger King packages] from office at launch time
-  \item[Starbucks packages] from supervisor, office and my friend.
-Especially my supervisor and friend collect them from their friends and their own uses.
-They save them for me and later I take them later.
+  \item[Burger King packages] are collected from the office where I work.
+At launch time, some of the colleagues order the meal from Burger King.
+The package of the meal is collected and used as a cover of notebooks.
+  \item[Starbucks packages] are colled from my supervisor, office and my friend. Especially my supervisor and friend saved and collected them from their friends. They are used as a cover of notebooks.
   \item[Modshifters papers] that are covered on table and at the end of the day they are cut out and throw away.
@@
 
-%%
-%%
-\item[Experiments.] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
-Again the purpose is to find a way that to shock people, surprise them.
-After ward somehow they should understand that these notebooks can be taken.
-\comment{I set up makets and try some installations of it.
-Take photo it.
-listed them here.}
+%  \begin{figure}[ht]
+%      \centering
+%      \includegraphics[height=6cm]{project_graphics/banner1.jpg}
+%      \caption{Banner}
+%      \label{fig:Banner_1}
+%  \end{figure}
 
-\todo{images are here.}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
+  \caption{Banner}
+  \label{fig:Banner_1}
+\end{figure}
 
-I imagine a exhibition environment and place notebooks at that place.
-Different placement are tried.
-All of them are look like sculptural.
-I have insert no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
-which I do not want.
+% Collecting
+% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili. Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life).
+
+% There is also strong relationship with the collecting discarded stuff and archeologies of waste.
+
+% TODO new comer
+% WHO OWNS TRASH?
+kısmı benim işimde sorgulanabilir, ya da ünlülerin trashlerini inceleyen adam kısmında ele alınabilir.
+Orada aslında başkalarının trashlerinin insanlar hakkında neler anlattığını çok güzel anlıyoruz.
+\comment{ANALOGY Between landfill and graveyards.
+WHOSE TRASH?} \quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
+\quotes{What is happening to trash is what is going to happen to us.
+We’re all going to end up in a dump, and we’re going to decompose.
+That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
+Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
+But when the same student went to Beverly Hills to go through trash, the police were nearly called.
+\quotes{Who decides what is public and what is private?
+How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
+
+%
+%
+\textbf{Transforming.} I turned them to notebooks.
+Actually I use them for my self.
+While I was using of them, I am very proud.
+I am studying nearly more than twenty years and I have always need for notebooks and use them.
+It is some sort of passion for me notebooks.
+Because I always admire notebook beautifully design or uniquely designed.
+I collect them whenever I find and most of the time I only save them for later use.
 
@@
 
-%%
-%%
-\item[Transforming.] I turned them to notebooks.
-Actually I use it for my self.
-And while I was using of it I am very proud of it.
-I am studying nearly more 20 twenty years and I have always need for notebooks and use them.
-It is some sort of passion for me notebooks.
-Because I always admire notebook beautifully design or uniquely designed.
-I collect them whenever I find and most of the time I only save them for later use.
-
-%%
-%%
-\item[Notebooks.] Actually I have been collecting same materials that are used in my project before the thesis work.
-In my mind there is always belief that I can I find something useful for them.
+Actually I have been collecting same materials that are used in my project before the thesis work.
+In my mind there is always a belief\todo{objective olmalı...} that I can I find something useful for them.
 (In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork.
@@
 
-%%
-%%
-\item[Exhibition] Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
+[Artistic tactics] Here I followed some tactics to accomplish my purposes. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+
+% Notebooklar insanın yanında kolayca taşınabildiği için aslında bir yandan fikri yaymak için idea. Zaten showing off'un ne kadar önemli olduğu rubbish theoryde söylenmişti.
+
+% [Standartlar, Dönüştürme seviyesi] endüstriyel standartlar, kaplar ve kağıtlar hep bir şekilde bir birleriyle boyut olarak uyuşuyorlar.
+İlk başlarda kesip biçmeye daha çok ihitiyaç duyarken zamanla basit katlamalar işimi görmeye başladı.
+Ne kadar az müdahele bulunursam aslında o kadar çok geldiği yerin özelliklerini o kadar çok temsil ediyordu.
+Bu da benim hoşuma gidiyordu.
+Kolaj mantığı işte abi.
+Ne kadar çok değiştirmek dönüştürmek istiyorsun.
+Burda şöyle bir durum var.
+çöpleri hiç tanınmayacak bir hale de getirebilirsin.
+Bu şekilde kimse onların farkına bile varmaz.
+Ya da neredeyse olduğu gibi kullanırsın.
+Yani uygulanan dönüştürmenin derecesi çok önemli burada.
+
+% TODO new comer
+the question of who owns these discards is not trivial. \cite{zimring2012encyclopedia}
+
+%
+%
+\textbf{Exhibiting.} Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
+Again the purpose is to find a way that to shock people, surprise them.
+After ward somehow they should understand that these notebooks can be taken.
+\comment{I set up makets and try some installations of it.
+Take photo it.
+listed them here.}
+
+\todo{images are here.}
+
+I imagine a exhibition environment and place notebooks at that place.
+Different placement are tried.
+All of them are look like sculptural.
+I have insert no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
+which I do not want.
+
+Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
 
@@
 
-%%
-%%
-\item[Artistic tactics]
-Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+% TODO
+% [Why giving away?] Felix Gonzales Torres, Unlimited Editions.
+% TODO insanlar bu defterleri alsınlar.
 
-\end{description}
-
+%
+%
 \section{Parts of project (or final work)}
@@
 
+%
+%
 \subsection{Notebooks}
-Mixing materials is main method in the production process.
+Mixing(juxtaposing) materials is main method in the production process.
 I combine different papers and packages.
@@
 
-All package papers are cleaned up. Because it is important that it needs to be safe to use. With mix of water and little bleach they are swabbed.
+Every notebook has numbers and with this numbers it can be tracked down when it was produced and which materials are used production of it.
 
-Here are the name of notebooks and their story:
-
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{project_graphics/banner1.jpg}
-      \caption{Banner}
-      \label{fig:Banner_1}
-  \end{figure}
+There are notebook series that have a name. Here are the name of notebooks and their story:
 
@@
 It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
+
 \item[12:00 pm.] Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+
 \item[08:00 am.] Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+
 \item[Friday Night.] (Maybe there can be another option related with traveling, or union).
@@
 I took some of the papers, and that papers are part the sheets of these papers.
+
 % Name of the paper can be related with this place and related with the meaning.
-% Again I need some memory from here. 
-% They are all my memories actually and I also turn my memories something different. Changing and constructing memories. And also others' memories... These project also contains others memories.
-
-% Ersan hoca's packages.
-Elgins' papers etc.
-I do not know actually their stories.
-Maybe I can dream up stories for them.
-Creating histories from some of the trashes.
-They do not have proper memory with me, but I tried to construct memories, (fake memories can be said that.)
 
 % Refer to 9 canlı. Never dies, revives again and again. Because trash moves in the community, even if thrown away can be find another use.
-
 \end{description}
 
+% Counter Argument:
+% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
+Here there are available different answers to the question.
+Firstly they are different once they are designed.
+Turned to different thing.
+I suggest that them to consider in different context like Duchamp.
+
+%
+%
 \subsection{Exhibition}
@@
 Public space.
-\todo[inline]{problematic because of resusing. actually is sharing.}
+\todo{problematic because of resusing. actually is sharing.}
 Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor. 
@@
 
+%
+%
 \subsection{Website}
-As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place peoples life again, it also finds another place in the digital space. ()
+As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.
 
-Mainly websites displays the story(History) of notebooks.
-Also it is a place to track the journey the notebooks.
+Mainly websites displays the (hi)story of notebooks.
+Further it is a place to track the journey the notebooks.
 As I claimed that it is not a finished work.
@@
 
-% I add the screenshoots of website. Also the development of it. Sketches of website. Navigation of it. User interaction. Use cases and actions. Functionalities.
+SketchBook Project is also inspired me a lot especially in terms of website.
+This project provides a platform to people in order to share their works with other people.
+It contains lots of works from all over the world.
+Full of creativity and showcase of richness of people's expressions on the small notebooks.
+My work can be considered as a sketch book project through trash.
+Sketches or only creative progress is not the only consideration.
+You can send your lecture notes.
 
-% Documenting the progress.
+% [Why website] (database, establishing communication, tracking in time) It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing coding and website.
 
-% It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing photography
+\todo{screen shots of website}
 
-% Counter Argument:
-% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
-Here there are available different answers to the question.
-Firstly they are different once they are designed.
-Turned to different thing.
-I suggest that them to consider in different context like Duchamp.
+\todo{use cases, use scenarios, actions}
 
-% I resurrect things that have been killed off...
-My work is all about the potential of materials — even when it looks like they've lost all possibilities.
-(Cornelia Parker) https://en.wikipedia.org/wiki/Cornelia_Parker
-
-% These all memories and collected materials related with the my history.
-So why is it important for the other people.
-What can they found my memories.
-This is not theirs.
-How other people connect to the topic.
-They important for me but also I need to find something important for the other people.
-For example modshifter and varuna gezgin is one of them.
-This not only my experience.
-Some kind of shared memories and histories.
-What will find people in these notebooks.
-
-%****************************************
-% TODO Find a solution for this problem:
-% Bu işin olması için ben insanlardan bir şeyler yapmalarını istiyorum.
-Yani aslında kendimde yapabilirim ama neden insanları da dahil ediyorum?
-Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de deönüştürmek gerekmek.
-ve bu bir süreç işi (şart mı tek bir yöntem bu mu?) İnsanlar nasıl değişir diye sormak gerekir o zaman.
-İnsanların değiştiğini dönüştüğünü gerçekten nasıl ölçeceğim ki?
-
-% important question: herkes neye ihtiyacı var ise onu toplar.
-ben neden niçin topluyorum.
-toplama sebepleri.
-dönüştürme sebepleri.
-neden sadece toplamakla yetinmiyorum.
-yani toplamak ile ayrıldığı noktalar nelerdir.
-Ben bir mana mı arıyorum?
-Yoksa kaybetmekten mi korkuyorum?
-Yeni kompozisyonlar oluşturmak istiyorum.
-Farklı karşımlar elde etmek istiyorum.
-Bir tür şaşırtmak durumu...
-Beklenmeyeni yapmak...
-En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
-
-%
-% PROBLEM:
-% In theoratical part I am focusing on actually the trash.
-But should I focus on paper trash?
-Is there any difference?
-Ya da ben oradaki bir farklılıktan besleniyor muyum?
-It is not totally paper, actually they are package.
-Examples can be given related with package material.
-It has a very short life.
-Not short actually.
-
-% How to establish the relationship between the collaboration and the trash?
-transforming them with the help of people.
-However, main discussion is not about collaboration.
-Here collaboration is a method to reach the aim of the project.
-In other words it is a methodology.
-There are different methodologies applied by artist to transform them.
-My methodology is to collaborate with the other people.
-My aim is to transform trash with people.
-Also make them to engage with trash.
-Trash is only one of the things discarded by the society.
-What is the importance of co-authored work?
-%........................................
+% TODO I add the screenshoots of website. Also the development of it. Sketches of website. Navigation of it. User interaction. Use cases and actions. Functionalities.

### 2015-12-06 chapter5.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@
 
-%****************************************
-% Savunma.
-% Yani aslında bu tezdeki fikirler, işler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar. 
-%........................................
-
+%
+%
 \epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces.
@@
 
-Many artworks are introduced. They have differences in terms of purpose and approached to the trash. Some of them only valued from its plastics effects. Some of them turned to the performative act.
+%
+%
+Many artworks are introduced.
+They have differences in terms of purpose and approached to the trash.
+Some of them only valued from its plastics effects (physicall properties).
+Some of them turned to the performative act.
 
+%
+%
+\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers.
+Cutting and pasting things also leave unused items.
+I do not know what to do with them.
+It is hard to use all of them.
+Saved for later use.
+On the other hand being aware of this trasnformation act is very tiny part of the big picture.
+I can say that my trash is reduced but is it same for the other people.
+Hard to collect all of them.
+
+\comment{There is also discard is being generated during the production process of papers.
+How to use them?
+Need to find a way because varda uses her discarded item inside of the film.
+Always(or in every proceses) new discard items are generated.}
+
+%
+%
 \textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
 
-There is also discard is being generated during the production process of papers.
-as an production process how to use them?
-need to find a way because varda uses this discard items.
-etc.
-even if work is generated from discard items.
-again always new discard items are generated.
+\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
+Analysis of them may be subject of another thesis.}

### 2015-12-06 drafts.tex
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06

@@
 Karşı durduğum nokta ise tam olarak burası.
+
+%****************************************
+
+% First one is actually is to analyze what is trash?
+Because I am using trash material and what is point of view of scholars to the trash.
+Realizing the potentials of it.
+Also the difference comes from the working on virgin object and trash object.
+Çöp kendi geçmişini falan taşıyor.
+Yeni blank bir şey değil aslında.
+Boş bir kağıda resim yapmak ile başka bir kağıdın üzerine resim yapmak arasındaki fark gibi bu.
+If trash has multiple life than these research will somehow reveal it.
+It is actually research on trash.
+I guess it is missing?
+Yani sanatın dilini genişleten yeni bir soru gündeme atan bir iş değil.
+I need to set a purpose for the theory chapter.
+Or it is a just a background chapter?
+
+% Genel anlayışın tersine --- çöpün değersiz, iğrenç, uzak durulması algısına --- karşıt değerli olabileceğini, bir kaynak olduğunu iddia ediyorum, tıpkı bu sanatçıların işleri gibi.
+Genel göürüşe meydan okuyorum.
+Sizleri gerçekten bunların değerli bir şeyler olduğuna vs.
+ikna etmeye çalışacağım
+
+% Ben bu bu bu methodlarla bu işi geliştirdim. Bir dert var o dert üzerine (şu yöntemlerle) sorgulamalar yapıyorum.
+
+%........................................
+
+%****************************************
+% Rubbish: the archaeology of garbage. rathje1992rubbish
+% [Refreshed ideas] Garbage project's findings have supplied a fresh perspective on what we know --- and what we think we know --- about certain aspects of our lives. p.24
+
+% The basic methods of garbage disposal are four: dumping it, burning it, turning it into something that can be useful (recycling), and minimizing the volume of material goods. p.33
+
+% ancient peoples p.33
+
+% fast food packaging. p.97
+
+% human behavior p.55 can you tell a lot about the customers from their garbage?
+
+%p.191-192 people tend to think of "recycling" as a relatively modern conceit that has only recently gained broad public acceptance, and whose practical benefits have only just began to be realized.
+Recycling itself is probably as old as --- indeed, seems to be a fundamental characteristic of --- human species.
+
+%p.209 The reuse of paper, for example, involves processes that generated a considerable amount of hazardous waste.
+In order to recycle newspapers, magazines, and, indeed, any printed paper, the paper must first be de-inked.
+At the end of the de-inking process one is left with essentially two products: on the one hand, de-inked fiber that will be turned into new paper; and on th other, a large quantity of toxic sludge.
+%........................................
+
+%****************************************
+% trasformations
+
+% during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8
+
+% p11. for decades we've taken for granted used cars and old houses. Is there anyone alive who has always lived in new houses or driven only new cars?
+
+% p.11 Economics has always been a factor in recycling.
+
+% p.12 recycling is not limited to folk art.
+
+% Use of recycled materials is not new, not is it exclusive to the united states. p.18
+
+% p.22 Material, meaning, and memory --- these are artists' reasons for using found objects.
+
+% p.48 recycling may be the most wasteful activity in modern America --- a waste of time and money, a waste of human and anutral resources. john tierney, "What a Waste," seattle postintelligencer...
+%........................................
+
+\paraphrase{The names we give this material ---waste, garbage, refuse, trash, rubbish--- have pejorative definitions.
+Worthless.
+Rejected and useless matter of any kind.
+Unimportant.
+\cite{zimring2012encyclopedia}}
+
+[Trashing Habits] Various objects become trash after their primary functions consumed.
+People do not care the package of the objects that they buy.
+They buy the coffee not the cup of it.
+After coffee finished the life of cup also finishes.
+They are actually packages that are used to carry or protect other materials.
+After real material used these packages became valueless (or useless).
+
+[LIFE OF OBJECTS] Objects life time in the nature is more than human being.
+People use them for just 5 minutes.
+However, they continue to exist on the nature through the years becauseof they are the result of highly complex industrial production methods and They are not easily decomposable items in the nature.
+
+% Şu anda lazım değil.
+[Biodegradable] \comment{Biodegradable matter is material capable of being decomposed by bacteria or other biological means.
+Biodegradable  matter usually consists of organic materials such as plant, animal, and other substance matter originating from living  organisms.
+It has the ability to be broken down into smaller, harmless products by way of the action of living organisms.
+The term is often used in relation to ecology, garbology, and waste management.
+Biodegradable products are often associated with perishables (products, food, and waste materials subject to death or decay).
+The term biodegradability of a product  refers to its disposition to disintegrate as the result of natural processes.}
+
+% Bu kısma hiç gerek yok.
+[Different types of trash] The complexity of produced trashes of societies is increasing.
+For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
+Think batteries and so on.
+It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase.
+Therefore for the ones that have no complex tools it is becoming harder to reuse objects.
+In other words objects become more complex their re-usage becomes less likely.
+Different production process generates different types of trash.
+According to production process, decomposition process\ldots The approach to the different type of trash will be different.
+In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it.
+There are some trashes that are more close to the people.
+More easy to convert them.
+more easy to regain to the society.
+
+%****************************************
+% UPCYCLING:
+% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended
+% Raw+Matrial=Art burda da upcycling deniliyor.
+%
+% RECYCLING:
+% recycled, re-seen book.
+%........................................
+
+\todo{throwaway spirit (vance packard)}
+
+[Unprofitable, Value, Definition] Waste is considered as something useless, something no longer has value; something sufficiently degraded so that the cost of reclaimation seems higher than the cost of disposal, in other words, something unprofitable.
+
+[Determination] \paraphrase{The value of things rises and diminishes according to the work they do or the feature imagined for them, in other words, to their potential realized in time.
+Waste by Willian Viley.}
+
+We are very good at producing waste as well as hiding our garbage.
+
+[Question] Is it trash or trashed? Is it waste or wasted?
+
+% CHANGE
+\paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}
+
+% Reference from Identity, mobility and the throwaway society
+% Resource is here: mmmacleo2005.pdf (throw away culture ile ilgili.) (Çünkü ben bunun ürününü kullanıyorum.)
+\paraphrase{In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new.
+Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act.
+The thesis, however, lacks depth and provenance.
+It is, actually, glib.
+Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
+
+%****************************************
+% MOVE TO CHAPTER 4
+% HAKAN GÜRSU, ZIZEK
+% Buraya aslında bir de Hakan Gürsu koymak gerekli olabilir.
+Yani aslında kendisi pek de sanatla ilgili bir laf etmiyor.
+Ama aslında tükettiğimiz onlarca şeye karşı bir tavır yaklaşım sergiliyor.
+Bu yüzden theory kısmında yer alabilir.
+Bu çöpün içinde boğulacağımızdan bahsediyor.
+Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.
+%........................................
+
+%****************************************
+% TEZ STATEMENT. Dönüştürme
+% Ya gerçekten çöpü dönüştürüyorlar ya da çöpe dair düşünceleri dönüştürüyorlar, ve bunu ele alırken aslında heykel, kolaj, fotoğraf gibi şeylerden yararlanıyorlar ama aslında ortaya koydukları şey bir sanatsal eylem.
+veya bunu sanatsal eylem bağlamında ele alabiliriz.
+
+% Dönüştürme çok temel bir şey ve çöpe çok bağlı. Çünkü değeri sıfıra inmiş bir şeyden bahsediyoruz.
+%........................................
+
+as trash live longer than human being, next generations have to cope with previous generations trash.
+
+[Inspired Works] There are some works that inspire me a lot when developing the work.
+They are not actually trash related works therefore I put them in different section and here before the details of my work.
+However the previous chapter has also very inspirational contributions to the my work.
+They helped the understand the topic and develop an approach to the topic.
+In this section some projects are mentioned and their methodologies are explained.
+How are these works effected my work.
+What is the relationship between them?
+(Maybe all of them can be explained only the related part of it.)
+
+Recycle the Classics, BY DORIS SOMMER
+
+Trash as History/Memory, Encylopedia, bullock2012trash
+
+John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
+
+Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+
+%****************************************
+% RESOURCES:
+%
+% Plagiarism check: http://mashable.com/2012/08/29/plagiarism-online-services/
+% What is Plagiarism: http://www.plagiarism.org/plagiarism-101/what-is-plagiarism
+%
+% How to cite epigraph: http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
+%
+% Artist ve artist statementlar için kaynak:
+% - http://www.amandadonahue.com/artist-statement/
+% - http://www.smfa.edu/cyclo-show
+% - http://www.gwynethleech.com/statement
+%........................................
+
+%**************************************
+% HERE Same sample phrases are listed you can use them:
+
+% The work that follows is divided into three sections
+
+% The artist thinks, acts, performs music, and writes outside the framework that society has created.
+
+% This thesis takes a rather different approach to the resonant possibilities of discarded things.
+It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
+
+% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
+
+% I’d like to criticize a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
+
+% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
+
+% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.
+
+% What specific social issues are you trying to address through Labyrinth?
+
+% The discussions (mentioned discussion are also formed the thesis project entitled ... )
+
+% Aim of this thesis is ...
+
+% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
+
+% as a reaction to the consumerist society.
+
+% \ldots is the concern of this study which aims to \ldots
+
+% The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
+
+% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
+The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
+
+% The main aim of the current study was to produce an initial conceptual model that explains
+
+% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
+Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
+With recycled objects, one can build anti-seismic and energy efficient houses.
+Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
+There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
+Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
+Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
+David Hertz reused the wings of a 747 as roof for a villa in Malibu.
+TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
+Yatin Pandya and Footprints E.A.R.T.H.
+built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
+James & Mau and Infiniski designed fashion homes with recycled containers.
+The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
+The GAD.
+In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
+The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
+All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.
+
+% In light of this argument
+
+% To frame a discussion, narrow down the topic
+
+%........................................

### 2015-12-06 chapter1_reduced.tex
reduction
Former-commit-id: 6bbc0d2d54fc40b36523e0d0976e845eec1e8bf2

--- 2015-12-06 chapter1_reduced.tex
@@
 %
-[Every.] \paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others \cite{zimring2012encyclopedia}.}
+\summary{Trash exists in every age and every society} 
+Refuse is part of people's consumption practices and it is a very common concept from developed cities to rural areas, from modern societies to ancient societies \cite[p.33]{rathje1992rubbish}.
+\todo{more ref.} For archaeologist dumps are one the significant places to figure what people consume in the ancient times \cite{rathje1992rubbish}.
+\summary{Global}
+\paraphrase{It is not limited with geography, ethnicity, gender, nationality.
+The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.}
+\summary{Trash is everywhere and, produced every time.}
+\paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes \cite{zimring2012encyclopedia}.} During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated.
+Different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes, and that become invisible.
+People are surrounded by all kinds of consumer goods.
+People are consuming everywhere while walking, working and traveling.
+The pattern is spread to all day and different places.
+It is hard to say that any place is waste free.
+Nearly every place people require waste bin.
+If people do not find a waste bin, people often leave it (to the ground).
+Production of trash never stops.
+It is inseparable from people's activities.
+\summary{Trash is everywhere} 
+Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
+Even if trash is tried to be moved away from people life, it is close as nearest waste bin.
 
-Trash in every age and every society.
-Refuse is part of people's consumption practices and it is very common concept from developed cities to rural areas, from modern societies to ancient societies\cite[p.33]{rathje1992rubbish} \todo{more ref.}.
-For archaeologist dumps are one the significant places to figure how people consume in the ancient times \todo{ref}.
+%
+% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
+\summary{Facts}
+\paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
+Turkey is a member of this organization.} countries produce almost half of the world’s waste.
+Africa and South Asia produce the least waste.
+High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
+Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}
 
-Trash is everywhere and, produced every time.
-During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated.
-The pattern is spread to the all day and different places.
-It is hard to say that any location(place) is waste free.
-Nearly every place people require waste bin.
-If we do not find a waste bin, people often leave it (to the ground?).
-Production of trash never stops.
-
-Trash is everywhere.
-Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards leaved the atmosphere and they rotate around the globe like satellites.}.
-Even if trash is tried to be moved away from people life, it is close as closest waste bin.
+% Üstteki kısmı neden diyorsun? Teze nasıl bir katkı sağlıyor? Throw away culture a taşınabilir.
+% From recycled book.
+\paraphrase{A person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
+America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}} \todo{iki paragrafı bir araya getir.}
 
@@
 %
-% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-[Facts.] \paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
-Turkey is member of this organization.} countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.} \todo{Zengin adamın harcama lüksü}
+\summary{Moves} 
+The vast amount of industrial discarded items spread through the landfills to oceans.
+Trash moves like objects from place to place.
+From homes to garbage trucks.
+From streets to landfills.
+From waste bins to sculptures.
+Lots of different people touches to trash.
+Travels like humans.
+Travels like commodities.
+As commodities spread to the every corner of the world, trash also.
+It is not static, not fixed.
+\todo{bir yere bağla.} \todo{summarized edilebilir, repetition var.}%With the trash what moves?
 
-\comment{Bunu neden diyorsun? Teze nasıl bir katkı sağlıyor?}
+People do not think what happens after they throw trash away.
+It exits from people's life but not from the world.
+It is stacked to another place.
+A project conducted by MIT in America explores the journey of trash by placing trackers onto the trash \cite{chen2009mit}.
+According to their results trash spreads away across the country and this journey takes month.
+Further it is not limited with the border of America because they are exported to the other countries\todo{ref.}.
+In other words American's trash is not only their trash.
+\comment{What happens when it is traveled to the other countries, how do people approach these items?
+They find new uses and meanings on them because their understanding of that items is different.} \todo{Bu soru daha sonraki bölümde sorulabilir.}
 
@@
 %
-[Common.] (In the dictionary \todo{Which dictionary?} trash means anything useless, worthless or discarded.
-In parallel to this definition, common perception is to get rid of them as soon as possible.
-People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore.
-People want to refuse them from their lives most of the time not thinking beyond (or alternative).
-However to establish solid understanding of trash (or trashing things), we have to give attention to the trash (and ask why it is trash).
-\comment{(To understand the beyond common perception we have to ask...)} How does it become trash?
-\comment{Is it possible to do something other than refusing them?}
-
-Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash. People do not see beyond the primary function.
+\summary{Common}
+(In the dictionary, \todo{Which dictionary?} trash means anything useless, worthless or discarded.
+In parallel to this definition, the common perception is to get rid of them as soon as possible.
+People tend to think that trash is valueless because it is no longer needed or not wanted anymore.
+People want to get rid of them from their lives most of the time not thinking beyond (or alternative).
+\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} However to establish a solid understanding of trash (or the action of trashing), we have to give attention to the trash (and ask why it is trash).
+To understand the beyond common perception we have to ask is it possible to do something other than refusing them?
+%\comment{Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash.
+People do not see beyond the primary function.}
 
@@
 %
-[Moves.] The vast amount of industrial discarded items spread through the landfills to oceans.
-
-Trash moves, objects moves from place to place.
-From homes to garbage trucks.
-From streets to land fills.
-From garbage baskets to sculptures.
-Lots of different people touches to trash.
-With the trash what moves?
-Trash moves around.
-Travels like humans.
-Travels like commodities.
-When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.
-
-People do not think what happens after they throw trash away.
-\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} It exits from people's life but not the world.
-It is stacked to another place.
-
-A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}.
-The results are surprising.
-Trashes spread away across the country and this journey takes month.
-Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
-In other words American's trash is not only their trash.
-As commodities spread to the every corner of the world, trash also.
-What happens when it is traveled to the other countries, how they approaches these items.
-\comment{They find new uses and meanings on them.} \todo[inline]{consider African native}
-
-%
-%
-[Aspects.
-Approaches.] In this thesis study to understand the different aspects of trash is a key element.
-Sometimes it is accepted as a problem (for examples keeping streets clean, handling the smell) that is need to carefully and seriously managed.
-On the other hand it is accepted as a source of diversity.
-Further for the recyclers it is a source of income.
+\summary{Aspects and Approaches}
+In this thesis study to understand the different aspects of trash is a key element.
+Sometimes it is accepted as a problem (because of accepted as useless, dirty, smelly) that needs to be carefully and seriously managed.
+On the other hand it is accepted as a source of diversity \todo{by whom, artist?}.
+For the recyclers it is a source of income.
 The economical aspect of trash can not ignored.
@@
 Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes.
+
 As it can be seen clearly there are different aspects and approaches to the trash.
-For some people it is disgusting thing and moved away from living space and for the others source of their life.
-\paraphrase{While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
+For some people, it is disgusting thing and moved away from living space and for the others source (or treasure) of their life.
+\paraphrase{While dictionary definitions of garbage describe it as \quotes{filth} and \quotes{worthless}, scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
 
-[Relative.] As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
+\summary{Relative}
+As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
 She realized that any of them called the practice as recycling.
@@
 There is no place for trash in their life.
-It can be understood that approach to the trash is not same for the all regions of world \todo{ref}.
+It can be understood that approaches to the garbage are not same for all regions of the world \todo{ref}.
 
@@
 
-[Production of trash and removal of trash.] For example a project conducted by MIT Sensible City Lab.
-reveals the \quotes{removal-chain} of objects by tracking trash with the mobile trackers places onto the trash \cite{chen2009mit}.
+%
+%
+\summary{Parts of us}
+\paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
+Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}.
+The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}
+
+% TODO Summarize
+% FROM Book: Trash Culture
+\summary{Change in the production and consumption practices}
+\paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line \cite{pye2010trashculture}.} As the result of it amount of goods boost and the cost of them significantly reduced.
+Things once reused again and again, now thrown away because it is more affordable to replace with new one.
+\paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production.
+\cite{pye2010trashculture}} As the production increased its by-product material waste is also increased.
+\paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption.
+\cite{pye2010trashculture}} \todo{summarize}
 
@@
 %
-[Parts of us.] \paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
-Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}.
-The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}
-
-%
-%
-[Change in the production and consumption practices.] \paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
-Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As the result of it amount of goods boost and the cost of them significantly reduced.
-Things once reused again and again, now thrown away because it is more affordable to replace \todo{daha uygun bir kelime bul} with new one.
-\paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production.
-(FROM Collage Culture)} As the production increased its by-product material waste is also increased.
-\paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption.
-(Trash Culture)} \todo{Ref: Trash Culture}
-
-%
-%
-[Current] During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste.
+\summary{Current} 
+During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste. \todo{bir yere bağlamak gerek.}
 
@@
 %
-[Art] \paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}
+\summary{Art} \todo{belki kısaca bahsedip chapter 3'e taşınabilir.}
+\paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art \cite{pye2010trashculture}.}
 
 % Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti. 
-\comment{In the beginning of the 20th century non-art objects enter the scope of art making.
-This is a revolutionary change in the making of art.
+\comment{Using non art objects in the art opened new dimensions for the language of art and practice (act) of art.} In the beginning of the 20th century non-art objects \todo{non-art objecti aç} enter the scope of art making.
+This is a revolutionary change in the practice of art making.
 Production of art and the approach to the art changed dramatically.
 This changes actually started at the end of the 19th century with impressionist.
-(But not related with non-art objects.) Picasso is the first artist that used non-art object in his works.
-Later many of them followed him.
-First works are collage which gluing different papers together.
-Yes using non art objects in the art is introduced and opened new dimensions for the language of art.
-But some of them treated as sculptures from trash.
-Reflects our world.
-But it is not limited with this.
-Some of the works are provokes the consumption habits of society and offers an alternative perception.}
+Picasso is the first artist that used non-art object in his works.
+Later many of artists followed him with their collages and assemblages (for example surrealist).
+Later Duchamp challenged the nature (or language) of art by using, non-unique, fabricated object to express his ideas.
+His work changed the way of perceiving art dramatically.
+With these developments trash has find a place in the art and contemporary artist are notably interested in trash.
+They use trash for different purposes (and these are explored in detail in the following chapters.).
+\comment{Trash find places in sculptures, paintings, assemblages, photographs\ldots Artist express themselves through trash.
+Portraits build from trash.
+Consumption habits of society are criticized through trash.}
 
@@
 \section{Purpose of the Study}
+
+% Some of the artist also interested in others trash. Why people are interested in rubbish?
+
+% In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
+
+The aim of this study is to explore the theories and methods of transformation of trash\todo{open} in the context of art and artistic act.
 % FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-\paraphrase{Particularly in the connection between garbage and the arts, I am interested in two questions.
+\paraphrase{Particularly in the connection between garbage and the arts, [this thesis] interested in two questions.
 First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material \cite{ibarra2015beautiful}.}
+Why and how is trash used by the artist?
+Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items?
+Has using discarded material or trash specific (or special) meaning and message?
+Questioned that how do artists reflect garbage and what are their tactics?
 
-Some of the artist also interested in others trash. Why people are interested in rubbish?
+\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature \cite{pye2010trashculture}.}
 
-\todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}
+% \paraphrase{This thesis seeks to answer the following questions: How did art and literature respond to this age of consumption?
+What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification (depersonalization), mechanical reproduction, and meaning?
+(FROM Collage Culture)}
 
-The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.
-
-In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
-Why and how are they used by the artist?
-Are there any differences with the original items compared to discarded items?
-Has using discarded material or trash specific (or special) meaning and message?
-
-\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.}
+Do people want to take back (or revisit) the trash once thrown away? In the project, the purpose is to turn them to things that worth to reconsider.
 
@@
 %
-[Different types of trash] There are different types of trashes.
-Result of different production and consumption practices different trashes are generated.
+\summary{Different types of trash, narrowing down scope} 
+There are different types of trashes result of different production and consumption practices.
 For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}.
-Electronic waste (e-waste), Construction and demolition waste, Medical waste are one of them.
+Electronic waste (e-waste), construction and demolition waste, medical waste are some of them.
 As it can be seen that there are lots of different types and as various as activities of human.
-In this scope of thesis \ldots \todo{Ben hangisini kullanacağım.
-Buna burada değinmek gerekli mi?}
+In this scope of thesis focused on disposable items and paper trash.
 
@@
 %
-[Different disciplines of trash] Trash draws attention different peoples and disciplines.
+\summary{Different disciplines of trash, narrowing down scope}
+Trash attract the attention of different peoples and disciplines.
+% From Trashion: The Return of Disposed, Bahar Emgin. 
+\paraphrase{Such a conceptualization of waste as \quotes{the degree zero of value} has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture \cite{emgin2012trashion}.}
 
-% From Trashion: The Return of Disposed, Bahar Emgin.
-\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.} \todo{ref.}
+Technological perspectives are one them. Trash is seen as a design and technological problem \cite{mcdonough2010cradle}.  
+% Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
+Developed in what sense?
+What are the criterion (foundation, measure) of technology?
+Technology is interested in which problems?)
 
-Increasing ecological concerns is one of the aspects of trash. As most of trash last decades are not easily decomposable. Relases toxics and other things.
+% Management of it (handled by the municipals generally). Removal from the life spaces of human.
 
-Technological perspectives.
-(seeing trash as a design problem.
-developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-development in what sense?)
+% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\paraphrase{In addition, the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed.
+When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \cite{cerny1996recycled}.}
 
-Management of it (handled by the municipals generally). Removal from the life spaces of human.
+% TODO Relocate and contextualize
+% Solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.
 
-As many people are inside the business of transforming trash through craft and so on.
+Many people are inside the business of transforming trash through recycling and reusing.
 People on the streets looking for aluminum cans, glass bottles, plastic.
 They collect and sell them to survive.
-There are companies that are collect waste materials to regain them again the industry.
+There are companies that are collect waste materials to regain them to the industry.
 In thesis they are not in the scope.
-People that give attention to the trash and behave artistic act is in the scope of this thesis.
+Artist that give attention to the trash and transform them is in the scope of this thesis.
 
-%
-%
-[Scope] Human discard. In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.
+% TODO Relocate, summarize and contextualize
+%\summary{Waste and technology relationship} 
+%\paraphrase{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design \cite{mcdonough2010cradle}.} \todo{can be moved to zizek part.} In other words, the problem is our technology (or design, or both) which is not perfect and causes mountains of rubbish.
+It is questionable that at some point, technology will reach to a level when there is no trash generated.
+
+% TODO Relocate, summarize and contextualize
+%\comment{Technical problem, need to managed, recycling (capitalism), upcycling} 
+%\paraphrase{With respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
+The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
+Waste now became evil.
+If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
+Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
+Upcycling...
+On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
+Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
+In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
+In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+% TODO relocation.
+% MOVE TO Conclusion of art chapter, discussion of transformation.
+%\comment{Design, alternative discipline} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
@@
 \section{Structure of the Study}
-Theory and artworks are not strictly separated from each other.
+Theory and artworks are not strictly separated from each other in this thesis.
 Artworks are explained with the help of theories.
 This study is structured by many examples of artworks in different part of the thesis.
-When a topic or argument is presented, immediately example artwork is given at this moment and how artist replies this issue is illustrated.
+When an argument is presented, (immediately) an artwork is given at this moment and how artists respond this issue is illustrated.
 Thereby artworks are examined in the theoretical and cultural context.
@@
 Only basic information is given and how it is related with this topic explained.
-By the way it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
+By the way, it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.
 
-% TODO Move to chapter 4.
-\comment{Research and the found samples of works helped a lot to shape my work.
-They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}
-
-Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on(of?) trash.
+Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on (of?) trash.
 The aim is to understand the trash in cultural and theoretical aspects.
-(Better realization the notion of trash) Chapter 2 provides theoretical and cultural background.
-It is explored the trash is being worked is whose trash.
-Or what type of society generate this trash.
+(Aim is to establish better realization the notion of trash.) Chapter 2 provides theoretical and cultural background of the project.
+It is explored the trash is being worked is whose trash and what type of society generate this type of trash.
 What type of approach generate it and what are the dynamics of it?
@@
 Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system.
-How explained the transient nature of trash?
+How can the transient nature of trash be explained?
 
-Third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and looks through the sample artworks and artists.
+Third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and analyses the sample artworks and artists.
 As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply.
@@
 Fourth chapter consists of the overview of the project.
-Stated the approach to topic clearly.
+Stated the approach to subject clearly.
 Development process of the work is presented in detail.
-It will start with the development process of the work.
-I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied.
-Development process of my work shaped the way I think on the subject of my thesis.
-Therefore, I will explain my process as detailed as possible.
-Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level.
-At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.
-\todo{rewrite, copy paste from another thesis.}
+Decisions, factors and considerations that shaped the work is expressed.
 
@@
 From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:
+
+%\comment{What were people throwing out when these words were coined?}
 
@@
 
-From another book (Trash Culture):
-\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand.
+%From another book (Trash Culture):
+%\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand.
 Many of these terms --- such as ‘trash’, ‘garbage’ and ‘rubbish’ --- are frequently used interchangeably.
 This is not least because the variety of terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of this volume.
-Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.
-Again, these usages have been retained to reflect the focus of individual studies.}
+Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.}
 
-In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods transforming trash to the another thing. Both of them are used widely by scholars.
+In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods of transforming trash to the another thing. Both of them are used widely by scholars.
 
@@
 Reusing lengthens the life of the item or material.
-Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others.
 The main purpose is to make the item last as long as it can.
-To reuse is to use something again instead of throwing it away or sending it off to a recycling company.
+To reuse is to use something again instead of throwing it away.
 \textbf{Why throw something away when you can give it another life?} Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.} Reusing is possible with re seeing (rethinking).
-Reusing is possible meet the needs of the human itself.
-Using creativity and personal approach can change objects functions.
-It is possible to use objects for different purposes.
+In thesis, it is explored through the work of artist.}
 
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-It is an energy consuming process.
+% Reusing is possible with re-seeing (and re-thinking). Using creativity and personal approach can change objects functions. It is possible to use objects for different purposes.
+
+% TODO Summarize
+\paraphrase{According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
 For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-In this process, energy is required which depends upon the stages of transformation.
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers (cullet) used to make new glass containers, and scrap metal used in foundries.
+Examples are crushed glass containers used to make new glass containers, and scrap metal used in foundries.}
 
-Recycling is very similar the rotting (decaying), reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
+Recycling is very similar the rotting (decaying), and reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
 
@@
 
+Some of the scholar uses recycling \cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
 Many scholar used the word recycling when mentioning works use trash and the concept of it.
@@
 Creative reuse, inventing new things from discard.
-Some of the scholar uses recycling \cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
-Some of the scholars and artist uses upcycling for their process.
-
-\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
-Analysis of them may be subject of another thesis.}
-
-\comment{What were people throwing out when these words were coined?}
+\paraphrase{Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of.} \todo{Reference, emgin2012trashion.} Some of the scholars and artist uses upcycling for their process.
+\paraphrase{This thesis project is about those objects that are recreated from trash through the process of upcycling.}

### 2015-12-06 chapter2_reduced.tex
reduction
Former-commit-id: 6bbc0d2d54fc40b36523e0d0976e845eec1e8bf2

@@
 Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash.
-Further it is mentioned how artist are approached these notions?
-and how their work viewed as their offered window or framework.
+Further it is mentioned how artist are approached to these notions and how their work viewed from offered window (or theoretical and conceptual framework).
 
@@
 %
-\comment{[Disposable items.]}
+\summary{Disposable items}
 \comment{Disposable: made to be used once or only a few times.
@@
 Their lifetime can be measured in minutes in terms of usage.
-I have never seen such person that uses own paper cup again and again.
-However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.
-Importantly the term throw away society has a slightly negative connotation, or meaning.
-When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval.
-\todo{ref.}}
+However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.} \todo{ref.}
+
+% In light of this argument,
 
 % FROM Trashion: The Return of the Disposed by Bahar Emgin
-\comment{LIFE AN OBJECT} \paraphrase{In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
+\summary{Life an object} 
+\paraphrase{One could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
 This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
@@
 % FROM Trashion: The Return of the Disposed by Bahar Emgin
-\comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+\summary{Consumerism} 
+\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
 The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
 
-\comment{[Capitalism, market.]} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+\summary{Capitalism, market} 
+The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
 They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
 This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
-themselves.
 \todo{Waste and wantta bununla ilgili bir bölüm olmalı.}
 
-\comment{[Initial function.]} 
+\summary{Initial function} 
 When an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
-Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
+Once a newspaper is read, or a bottle of coca cola consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
 
@@
 
-Disposable items are first introduced X and their usage accelerated after Y. There are Z factors that give rise to usage of single-use ites excessively \todo{Bu cümleyi doğru düzgün kurmak gerekli.}.
+% TODO 
+% Disposable items are first introduced X and their usage accelerated after Y.
+There are Z factors that give rise to usage of single-use items excessively \todo{Bu cümleyi doğru düzgün kurmak gerekli.}.
 
 % Reference from Identity, mobility and the throwaway society
-[The term throwaway culture] Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}.
+\summary{The term throwaway culture} 
+Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}.
 \comment{Scholars argue that contemporary societies are throwaway societies (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
 O’Brien, 1999; Hawkins and Muecke, 2003) \todo{ref required.}.} The term is actually a criticism of over consumption of short-live disposable objects.
-\comment{The term overconsumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.}
+\comment{The term over consumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.} \paraphrase{Importantly the term throw away society has a slightly negative connotation, or meaning.
+When you describe a society as a throw away society, you are probably criticizing that behaviors or showing your disapproval.}
 
@@
 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ...
-was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century.
+was supplying the customer with hundreds of disposable containers and materials by the end of the nineteenth century.
 the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} \todo{ref.
@@
 % Reference from Identity, mobility and the throwaway society
-[Counter-argument] Even if conducted a qualitative research people are really do not throw away their things.
-\paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
+\summary{Counter-argument} 
+According to conducted a qualitative research people are really do not throw away their things.
+People are not wasteful as claimed.
+However, \paraphrase{the research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
 They analyzed the things like television, furniture and toys like that.
+Therefore their result showed that people are not so wasteful as claimed when considering durable items.
+However in this thesis scope, the focus is disposable items and it can be mentioned the wastefulness of society.
+\todo{bu kısmı adam et.}
 
-\comment{CONSUMER CULTURE}
+\summary{Consumer culture}
 \paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these thesis are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
-In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}
+In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2).} \todo{find exact ref.}
 
@@
 %
-\comment{[Factors.]}
-Factors that cause over consumption habits.
-Technological advacements can be one of them.
+\summary{Factors that cause over consumption habits}
+Technological advancements can be one of them.
 These items with the help of industrialization can be produced easily.
 Mass production.
-Disposable items are reduces the labour and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup).
+Disposable items are reduces the labor and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup).
 Another point is that they are more affordable in terms of supply chain and cost.
@@
 Therefore there is no need to save the old one.
-Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.
+Last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
 \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref.
@@
 In essence, it encloses the commons.
-Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
-\todo{ref.
-ontology of trash}}
+Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.} \todo{ref.
+ontology of trash}
 
@@
 
-[Dark side.] Usage of disposable items in the society is very widespread.
+\summary{Dark side} 
+Usage of disposable items in the society is very widespread.
 For same cases it is inevitable.
@@
 
-\comment{Handling of this mountains of garbage is another topic.
+\comment{Handling of mountains of garbage is another topic.
 It is not the topic of this thesis.
@@
 Aynı zamanda ben de bu ürünü kullanıyorum.
-Konuyu o yüzden farkl açılarından anlamak gerekli.
-\todo{Ama benim konuya nasıl yaklaştığım biraz belirsiz.}}
+Konuyu o yüzden farklı açılarından anlamak gerekli.}
 
@@
 %
-[Art] There are some artists whose works are related with the pheomena expressed above.
-(Some of the works of artist can be examined in this pheomena.) Not every people throw away disposible objects, some of them save them and use for their own purposes.
+[Art] There are some artists whose works are related with the phenomena expressed above.
+(Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.
 
@@
 
-[CRITICS] Visuals of Chris jordan are like modern versions of mosaics.
-In the age of consumption the most easily accessible matariel is trash.
+\summary{Analysis}
+Visuals of Chris Jordan are like modern versions of mosaics.
+In the age of consumption the most easily accessible material is trash.
 Trash has different colors and sizes and shapes.
@@
 Every day she creates a new piece that reflects her impressions in that moment.
-endeavour of re-purposing recycled and found materials.} \todo{cite website}
+Endeavour of re-purposing recycled and found materials.} \todo{cite website}
 
-[CRITICS] This work is for fathers day.
+\summary{Analysis}
+This work is for fathers day.
 Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day).
-Trashes trasnformed to diaries.
+Trashes transformed to diaries.
 Trash is every where, already at hand.
@@
 
-[CRITICS] inside of glass window. public space. publicly drawing, as she drinks her coffee publicly, also paints them publicly.
+\summary{Analysis}
+Inside of glass window. Public space. As she drinks her coffee publicly, also paints them publicly. \todo{related with Liz Parson's argument: practice of trash to durable.}
 
@@
 \todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of people's life.
-What people consume is actually tells many things about them (their choices, possessions etc.) \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}.
+What people consume is actually tells many things about them (their choices, possessions etc.) \todo{ref.}.
 As scholars mentioned that throughout the discards of someone else many thing can be understand.
@@
 
-\todo[inline] transition required.
-
 %
 %
-\comment{[GARBOLOGY]}
+\summary{Garbology}
 Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
@@
 \todo[inline]{transition required.} 
-Last decades increasing attention the the ecology and rubbish.
-This section is related with the increasing interest on ecology.
+Last decades there is increasing attention the ecology and rubbish.
+This section is related to the increasing interest in ecology.
 Global warming is one of them, plastic pollution on the oceans also is part of it.
 These types of news and talks increasingly find a place on media more and more.
-At this stage Zizek comments on ecology and trash conversly .
+At this stage, Zizek comments on ecology and trash conversely.
 
@@
 
-Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervantion.
+Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervention.
 Not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
@@
 
-[Summary.] \comment{Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor.
+\comment{Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor.
 Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor.
@@
 
-\todo{Çöp evler buraya gelebilir belki, çöpleriyle birlikte yaşayanlar?}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
+  \caption{Song Dong, Waste Not, 1990}
+  \label{fig:SongDong_WasteNot}
+\end{figure}
+
+Zizek's argument can bring minds to the question that is our home going to be turned to trash home? Actually an artist work is related with not wasting. \todo{details}
 
@@
 \comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük.
-Bu hareketlilik ve farklılık ise bir teorik çerçeveye oturulmuş, hadi ona baklım şimdi.
-Zaten bu hayatta çöp her zaman karşımıza çöp olarak çıkmıyor.}
+Zaten bu hayatta çöp her zaman karşımıza çöp olarak çıkmıyor.
+Bu hareketlilik ve farklılık ise Rubbish theory ile teorik çerçeveye oturulmuş.
+Bir yandan da çöple birlikte yaşayalım dedik ama bakalım nasıl olacak o iş.}
 
@@
 % TODO new comer
-\comment{MOVES.} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+\summary{Moves} 
+\paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
 (Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}
-
 % TODO new comer
-\comment{MOVES.} \paraphrase{Objects moves around and their values change constantly.
+\paraphrase{Objects moves around and their values change constantly.
 (The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
 The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}
-
-% TODO new comer
-% BAZI KISIMLARINI AÇMAK GEREKLİ AMA.
-\comment{MOVES.} Here the important thing is moving nature of trash.
+% TODO new comer,  BAZI KISIMLARINI AÇMAK GEREKLİ AMA.
+The important thing is moving nature of trash.
 Objects moves and gains different meanings through this movement.
@@
 % From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-\comment{MOVES.} \paraphrase{Below part explains journey of trash in different steps/stages.
+\summary{Moves} 
+\paraphrase{Below part explains journey of trash in different steps/stages.
 Object moves and trash also moves.
@@
 Daha tek kullanımlıklar da var denilebilir.
-\comment{TRASH MOVES.} \paraphrase{Trash moves, all the time.
+\summary{Moves}
+\paraphrase{Trash moves, all the time.
 It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
@@
 
+\summary{Categorization of waste} 
 % TODO new comer
-\comment{CATEGORIZATION OF WASTE} \paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+\paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
 (Think that the transformation process.
@@
 % TODO new comer
-\comment{CATEGORIZATION OF WASTE} \paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+\paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
 Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
@@
 % TODO new comer
-\comment{CATEGORIZATION OF WASTE} \comment{susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
+\comment{Susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
 Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
-Remember the example given: shoes  on the dinner table.}
+Remember the given example: shoes on the dinner table.}
 
-\comment{CATEGORIZATION OF WASTE} \paraphrase{waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
+\paraphrase{Waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
 
-\quotes{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
+\todo[inline]{Buradan nasıl rubbish theorye geçilecek???}
 
-\paraphrase{Michael Thompson’s 1979 study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity and social status \todo{ref.
-from Trash Culture}.}
+\paraphrase{Michael Thompson’s study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity and social status.} \todo{ref.
+from Trash Culture} \paraphrase{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder \cite[97]{thompson1979rubbish}.}
 
@@
 % (Summary From Paul M Camic.)
-As a species Homo sapiens has been gathering and collecting objects for thousands of years.
+\summary{Theoretical Analysis of Found Object}
+\paraphrase{As a species Homo sapiens has been gathering and collecting objects for thousands of years.
 Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
@@
 When early prehistoric eople recognized a cave’s natural feature as a “found object” and incorporated it in a picture, it is possible that the natural feature took on a higher value than if left alone, thus adding to the value of the object on the cave wall.
-Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.
+Once found and incorporated in paintings and drawings on a cave wall, it is possible that these protrusions and indentations became objects that functioned symbolically.}
 
-In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
+\paraphrase{In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
 Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
@@
 A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots 
+of salvaging and using found and second-hand objects has potential implications for \ldots }
 %........................................
@@
 \begin{itemize}
-\item Trash has archaeological value. It reflects out habits.
+\item Trash has archaeological value. It reflects our habits.
 \item Ecological perceptions have problems. 
@@
 When we look at personal level (previous one is general one) discards tells us about our activities, possessions, preferences etc.
-They can be viewed as potrait of artist and us.
+They can be viewed as portrait of artist and us.
 

### 2015-12-06 main.tex
re organization
Former-commit-id: f7f7ca407330448c19799f535ba2ea18fbe043ee
Reorganization
Former-commit-id: d2f4ba3d6ef984f2a64e4a3f955bf472f7cb7cc7
Reduction
Former-commit-id: c287ed58ed0af64082641437043495694a05ba72
Reduction
Former-commit-id: 5f9534d56a5913adc6ea4ef6840a4bdae4860f35
Reduction
Former-commit-id: 776addea2a8d261fe4b62f86718a2555ef817347
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06
reduction
Former-commit-id: 6bbc0d2d54fc40b36523e0d0976e845eec1e8bf2

@@
 \usepackage{wrapfig}
-\usepackage[usenames, dvipsnames]{color}
+\usepackage[usenames,dvipsnames]{color}
 \usepackage[titletoc]{appendix}
@@
 \providecommand{\singlequotes}[1]{`#1'}
-%\providecommand{\todo}[1]{\textcolor{red}{#1}}
 \providecommand{\comment}[1]{\textcolor{cyan}{#1}}
-\providecommand{\paraphrase}[1]{\textcolor{magenta}{#1}}
-
-\newenvironment{blockquote}{%
-  \par%
-  \medskip
-  \leftskip=4em\rightskip=2em%
-  \noindent\ignorespaces}{%
-  \par\medskip}
-
+\providecommand{\summary}[1]{\textcolor{green}{[#1]}}
+\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}
 \renewcommand*\bibname{Bibliography}
@@
 %****************************************
-% Ideas for Abstract
-% You can add short definition of trash. Any object can be art in 20th century. Society generated trash and a culture that do not reuse and throws away.
-% Structure of this thesis: written part of it and the project support each other.
-%........................................
-
-%****************************************
-% Structure of Abstract
-% What is this study?
-% What is questioned/examined/investigated?
-% How is it investigated?
-% What is the outcome?
-%........................................
-
-%****************************************
 % ENGLISH
 \begin{abstract}
-The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act.
-Approach and methodologies of artists who uses discarded materials in their works are explored.
-It is questioned that why and how they use discarded materials.
-How can artworks be understood in terms of theoretical and cultural aspects?
+Usage of non-art objects in the artworks can be traced back to the beginning of 20th century.
+This approach has broken the existing rules and extended the language of art in an unprecedented way.
+After that point, trash has found a place in the work of artists \comment{(and their expression)}.
 
-\comment{The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art).
-It is questioned that the role of art in transformation of discarded items.
-This thesis follows the discussions of what is waste and the states of waste or meaning of waste.
-Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.}
-
-Artists has used trash to reproduce artwork since the first ready-made introduced.
-\comment{first examples are not actually made of trash.
-not considered as trash, but entering non-art object traced back to beginning of 20th century.}
-
-\comment{First ready-made (or using non-art) object in the art making has extended the language of art and opened new playground for artist.}
+The purpose of this study is to discuss transformation (or usage) of trash in the context of (art and) artistic act.
+It is questioned that the role of art in the transformation of discarded items.
+Approaches and methodologies of artists who use discarded materials in their works are explored.
+This thesis follows the discussions of the place of trash in culture and theories of trash.
+Then approaches and methodologies of artists who use discarded materials in their works are explored.
+\comment{Usage of discarded materials in the artwork by the contemporary artist are studied through their works.} It is questioned that why and how they use discarded materials and how artworks can be understood regarding theoretical and cultural aspects.
 
 Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act.
-Notebooks are made from trash/discarded papers by the help of people.
-Process and notebooks are recorded on a website.
-Notebooks are distributed in different locations.
+In the scope of the project, discarded papers are collected with the help people and transformed to notebooks.
+Progress and collected items are recorded on a website.
+Notebooks are installed in different locations in order to invite people to use trash again.
 
-%\todo[inline]{Does trash can be seen as a (new) resource for artist.}
-
-\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory?, Throw Away Culture?, Handmade Notebooks.
+\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
 \end{abstract}
@@
 
-%****************************************
-% SAMPLE ABSTRACTS
-
-% Bu çalışmada, ne kadar itici bir kavram olsa da, çöplük olgusunun çirkinlikten güzelliğe ulaşarak estetik bir haz uyandırması amaç edinilmiştir.
-Iticici gözüken bir konunun resim diliyle anlatımı ile tersine çekici ilginç bir sanat konusu olabileceğinin somutlaştırılması amaçlanmıştır.
-Sanatçı bir anlamda doğada yaşamda bulunan küçük ayrıntıları, sanatsal bir gözle yaklaşarak gösterebilendir.
-Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.
-Oysa önemsiz gibi gözüken itici karmaşık konular bile sanatsal kaygılarla ele ahnabilmelidir.
-Önemli olan, bu konalara estetik yaklaşım ve izlenen anlatım yol ve teknikleridir.
-Özgün baskı dallarından kazı resim (gravür) tekniğinin ele alınan konunun görselleştirilmesinde, anlatımında en uygun teknik olmasıdır.
-Çünkü her sanatçı kendi doğasına en uygun olan teknik ve malzemelerin olanaklarıyla kendini en rahat biçimde ifade etme olanağı bulur.
-Kendine özgü bir biçim ve anlatım diliyle dile getirmek gerçekleştirmek çabalan özgünlüğü yakalamak içindir.
-Bu çalışmada özgünlüğü yakalamak, çöplük olgusunun oluşturduğu dinamik yapı, objelerin biçimlerine bağlı kalmadan plastik dille görselleştirilmiştir.
-Seçilen teknik doğası gereği raslantısal tadlarada olanak vermektedir.
-Oluşturulan resimlerde durağan bir dengeden çok dinamik biçim ilişkilerine dayanan gerilimli bir etkinin yakalanması amaçlanmıştır.
-
-% ON THE RELATIONSHIP BETWEEN IMAGES AND WORDS AND THEIR RELATION TO BODY AND PERCEPTION
-% Prehistoric man created a mark and throughout the history this mark evolved and bifurcated into two: a word and an image. While images were cherished, words were set apart from images. 
-% This thesis attempts to look at the relationship between images and words through seeking their connection to perception and body.
-It investigates how image-word dichotomy occurred and how this dichotomy obscured the connection between writing and body.
-The thesis also examines different approaches to overcome this phenomenon in the context of Modern Art.
-% By examining my artwork within this framework, it argues that it is possible to embody the inseparable relationship between images and words through reconnecting with the body’s primordial existence.
-
-% ALTERNATIVE PHOTOGRAPHY IN THE DIGITAL AGE: PERFECT PHOTOGRAPHS IN AN IMPERFECT WAY
-% This thesis explores the possibility of an alternative future of photography from the union of digital and chemical domains of the photographic medium.
-The historical photographic processes known as Cyanotype, Salt print and Vandyke Brown are employed for this project in conjunction with the modern inkjet printer produced digital negatives.
-% As being highly sensitive to the variables during the process, each alternative photographic print exhibits a visual uniqueness.
-In this aspect, there is conceptual correlation with the visual uniqueness of alternative photographic processes and the visual uniqueness of albinism.
-Emphasizing the human element in subject, vision and craft of making photographs, this project aims to produce unique photographs of a visually unique subject.
-
-% LAND ART ON THE BORDER BETWEEN TOPOLOGY AND ATOPOLOGY
-% The purpose of this study is to discuss the Land Art movement from a topological and atopological perspective.
-In order to establish an extensive understanding of the matters of topology and atopology, Arkady Plotnitsky’s formalization of quasi- mathematical thinking, which is derived from Jacques Derrida’s philosophy, is treated in detail.
-The artistic stance, Robert Smithson, as a major figure of Land Art movement is analyzed both from the artistic and the theoretical perspectives.
-Thereafter, an algebraic reading of the Smithsonian conceptualization is executed in order to illuminate the liaison between the Land Art movement and the matters of topology and atopology.
-Finally, the thesis project, Nonlocalizable Displaced Mirrors depicts the whole attitude, which is taken throughout the study, towards the issue of Land Art on the Border between Topology and Atopology.
-
-%........................................
-
 \setcounter{secnumdepth}{3}
@@
 \pagenumbering{arabic}
-\include{chapter1}
-\include{chapter2}
-\include{chapter3}
-\include{chapter4}
+\include{chapter1_reduced}
+\include{chapter2_reduced}
+\include{chapter3_reduced}
+\include{chapter4_reduced}
 \include{chapter5}
-\include{uncategorized}
 \bibliographystyle{apacite}

### 2015-12-06 chapter2_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

@@
 %
-\summary{Factors that cause over consumption habits}
+\summary{Factors that cause over-consumption habits}
 Technological advancements can be one of them.
@@
 %
-[Art] There are some artists whose works are related with the phenomena expressed above.
+\summary{Art}
+There are some artists whose works are related with the phenomena expressed above.
 (Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.
@@
 
-Zizek's argument can bring minds to the question that is our home going to be turned to trash home? Actually an artist work is related with not wasting. \todo{details}
+Zizek's argument can bring minds to the question that is our home going to be turned to trash home?
+Actually an artist work is based on habit of not wasting.
+In the installation thousands of items are displayed.
+They are saved instead of throwing.
+\todo{details}
 

### 2015-12-06 chapter3_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

--- 2015-12-06 chapter3_reduced.tex
@@
 \section{Root in the Art History}
-Using trashed objects in making of art can be examined with the enterance of non-art objects to art \todo{sadece bu yeterli olmayabilir.}.
-In other words using objects in artworks beyond their intended purpose or intended meaning and function.
+Using trashed objects in making of art can be examined with the enterance of non-art objects to art\todo{sadece bu yeterli olmayabilir}.
+In other words, using objects in artworks beyond their intended purpose or intended meaning and function.
 Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together.
@@
 However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso.
-\todo{Still Life with Chair Caning} \todo{Violin with sheet of music}.
 One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting.
-This work of Picasso also can be considered as first example of assamblage because of a rope was used to frame the picture.
-Using non-art objects in the production of art challanges existing conventions of painting.
+This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture.
+Using non-art objects in the production of art challenges existing conventions of painting.
 % FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
 \paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
-The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).} \textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
+The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/picasso_chair.png}
+  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
+  \label{fig:Picasso_Chair}
+\end{figure}
+
+\textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
 The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
+  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
+  \label{fig:Duchamp_BicycleWheel}
+\end{figure}
 
@@
 \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+As he wrote: ‘It grows more or less according to the principle of a metropolis.’ The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
 Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
@@
 % TODO paraphrase
-\quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
 Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
@@
 A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996}  \cite{tauxe2012encyclopedia}.
+Schuldt’s famous “Trash People,” which has traveled around the world since 1996 \cite{tauxe2012encyclopedia}.}
 
@@
 %
-[Collage] Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
+\summary{Collage}
+Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
 In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
@@
 
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\summary{Hybridity} 
+\paraphrase{Recycled object contains within it a reference to two or more distinct times.
+Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)} \todo{ref.}
+
+% TODO MOVE
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%\comment{Different meanings for everybody.} 
+%\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another.
+Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
+It is story of people --- the women, men, children etc.
+one person's trash into another's treasure.}
+
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
+It is claimed that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
+
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\paraphrase{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)} \todo{ref.}
+
+% TODO MOVE TO COMMON APPROACH
+%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
+
 %
 %
-[Assemblage] Assemblage work produced by the incorporation of everyday objects into a composition.
+\summary{Assemblage} 
+Assemblage work produced by the incorporation of everyday objects into a composition.
 It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
@@
 %
-[Bricolage] Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
+\summary{Bricolage} 
+Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
 \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
@@
 
-\paraphrase{\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.}
+\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
 
-\begin{quote}
-[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
+%\begin{quote}
+%[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
 His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
-\end{quote}
+%\end{quote}
 
-\begin{quote}
-The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
+%\begin{quote}
+%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
 There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-\end{quote}
+%\end{quote}
 
-\begin{quote}
-The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
+%\begin{quote}
+%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
 In this sense the engineer is a myth.
@@
 The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-\end{quote}
+%\end{quote}
 
-[TODO use this ref]\cite{strasser1999waste}
+%[TODO use this ref]\cite{strasser1999waste}
 
@@
 %
-[Found Object] Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
+\summary{Found Object} 
+Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
+From western trash to tribal treasure.
+\paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods.
+A disposable item becomes imminent desire and profound social consequence.
+(Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
+It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.
+
+% TODO new comer
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%\todo{yerlinin fotoğrafı}
+%\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}
+
+%(Summary From Paul M Camic.) 
+%The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
+It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
+The junk object becomes transformed into the valued found object.
+Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
+His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
+97) and labeled it a work of art.
+A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
+These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
+
+%Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
+169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
+170).
+The finder discovers an unrealised significance in the object.
+A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
+He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
+
+%How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
+(Important points a gap in the literature.
+Although Parsons article analyze practices, it is not very broad and detailed.
+Further what is the importance of it is missing.)
+
+%The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
+The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
+
+%Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
+The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
+When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
+Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
+This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
+
+%An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
+Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
+
+%Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.
+
+% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
+To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
+This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
+
+% Amelie olabilir.
+Orada fotoğraf toplayan çocuk olabilir.
+Onları itinayla toplayan bir adam.
+Tren garındaki fotoğraf kulubesi.
+Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
+Bir birinden farklı bir sürü insan.
+Filmde neden böyle bir eyleme yer veriliyor?
+Film fotoğraflar üzerinden defter üzerinden ilerliyor.
+Onun çevresinden bir hikaye kurgulanıyor.
+İnsanların artıklarını topluyor.
+Onların değer vermedikleri şeyleri topluyor.
+Bunlar baya baya aslında o insanlar.
+Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
+Çok iyi bir örnek mi bilmiyorum.
+Burada niyet nedir ki?
+Ben buna şöyle bir okuma getireceğim diyebilirim.
+Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
+Bu arada bu fotoğraf toplama işi ilk değil.
+Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
+Ama benim işime yarayan kısmı ne?
+Neden o fotoğrafları ya da bunun filmini yapıyor.
+Aslında puzzlelar üretiyor.
+Belirli tekrar olacaktır.
+insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
+Tekrar bir kitap haline geliyor.
+Tanınmayan insanların fotoğrafları.
+Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
+Aslında tam da amelie bunu yapmıyor mu?
+Hikayeler üretiyor bu fotoğraflardan.
+Yeni karşılaşmalar üretmesi.
+Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
+Bin bir türlü şey vardır aralarında.
+Nereye yerleşmeli.
+Başkasının çöpünü toplama.
+O dönemin o eşyasını arşivini tutma.
+ve herkes sunuluyor sonrasında bu.
 
@@
 %
-[Ready-Mades]
+%[Ready-Mades]
 
@@
 
+% not easily understandable with the entering non-art objects in art.
+artist are responding the current societies habits in a different ways.
+what they are doing here is to see other possibilities and show actually what is going on.
+what does it mean all of these things.
+
 % FROM ReVista
-\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} \paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
+%\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} 
+\paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
 
@@
 %
-\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.
+%\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
-  \caption{Pictures of Garbage by Vic Muniz}
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=0.37\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
+  \end{center}
+  \caption{Vic Muniz, Pictures of Garbage}
   \label{fig:VicMuniz_PicturesOfGarbage}
-\end{figure}
+\end{wrapfigure}
 
@@
 
+\comment{This is a proff of the transformation of the original concept.}
+
+% TODO new comer.
+[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse.
+but even if they have no economical struggle, they continue recycle.
+what is the reason of it?} Recycling as an economic strategy of survival in developing countries throughout the world.
+creative production that is motivated, primarily, by adverse conditions of economic necessity.
+(lanfill orchestra here.
+bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised.
+(p25)
+
 % Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
@@
 
-\todo{indiginazation of western goods here.}
+\summary{Indigenization} 
+The indigenization of western objects.
+(sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"?
+Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves.
+They do not necessarily despise our commodities.
+But they are selective in their demands and transformative of their uses of such things.
+(sahlins, 13)"
 
@@
 
-\begin{figure}[ht]
-  \centering
-  \includegraphics[height=6cm]{graphics/Alsbrooks.jpg}
-  \caption{The White Trash Series by Kim Alsbrooks}
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=0.37\textwidth]{graphics/Alsbrooks.jpg}
+  \end{center}
+  \caption{Kim Alsbrooks, The White Trash Series}
   \label{fig:Alsbrooks}
-\end{figure}
+\end{wrapfigure}
 
@@
 
-\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure.
+[Chrish Jordan Break Down inventory] \paraphrase{Not all artist transform trash although some deconstruct them.
+Michael Landy is one of them.
+Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
+Reveal all his possessions.
+and loosing them while you are alive.
+Turning them to rubbish making them unusable.
+breaking down the all the meaning.
+breaking down the connections.} It can be an example of downcycling process.
+It is preferred to decompose all the complex link and relationships between the objects.
+They are not just ordinary things they are possessions of artist.
+Break Down 2001, in which he systematically destroyed all his personal possessions.
+His work examines what we value and what we discard, consumerism and waste, and human labour and its worth.
+It happens in public space.
+People can see the process.
+This process last 2 weeks.
+Places where people buy things actually.
+
+%\comment{Tüm sahip olduklarını yaşarken kendi isteği ile yok ediyor. Bu hepimizin paylaştığı bir şey.}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
+  \caption{Chris Jordan, Break Down}
+  \label{fig:ChrisJordan_BreakDown}
+\end{figure}
+
+%\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure.
 Garbage dump or gold mine?
@@
 
-Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
+%Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
 Pavilions, villages of huts and even whole houses are appearing over night.
@@
 % From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
-Public space is under siege.
+%Public space is under siege.
 The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities.
@@
 
-Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
+%Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
 Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures.
@@
 
-For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
+%For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
 
-Public space and transformed materials.
+%Public space and transformed materials.
 
 % From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
-Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
+%Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
 The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.
 
-They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
+%They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
 In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces.
@@
 
-\textbf{Resim tahtası.} Bazı işler çöpleri kendi işleri için bir kanvasa dönüştürmüşler.
+\summary{As a canvas}
+Bazı işler çöpleri kendi işleri için bir kanvasa dönüştürmüşler.
 Çay poşetlerini boyayan kadın, Kitapları boyayanlar, teneke kutuları boyayanlar.
@@
 
-toplumun davranışlarına karşı bir cevap, görülmeyen, veya farkedilemeyen unutulup giden bir hale getiriyor.
+Toplumun davranışlarına karşı bir cevap, görülmeyen, veya farkedilemeyen unutulup giden bir hale getiriyor.
 
-[Çöpleştirme, heykelleştirme.] not all artist transform, some of them use them as they are.
+\summary{Trashing}
+Not all artist transform, some of them use them as they are.
 further some of them trashes things.
@@
 
-%
-% Sample phrases
-% The topic of recycling, presented in this issue, is the "re-use" of materials, objects and structures, for different purposes, and in different ways from their original uses, in order to build or re-build, to provide possible solutions to problems related to the environment, and to manage waste more intelligently.
-Tyres, containers, bottles, cans, CD-ROMs and even keyboards, can find new and unexpected uses in experimental architecture, exhibition pavilions, or low-cost housing.
-With recycled objects, one can build anti-seismic and energy efficient houses.
-Recycled materials can contribute towards building shelters to meet the needs of people affected by disasters.
-There are many topics connected to recycling, and they vary depending on the objects that one wishes to recycle and how they will be put to use.
-Used tyres find many applications in REfunc architecture and the Bohlin-Cywinski-Jackson studio.
-Dorte Mandrup transformed a piezometer into the supporting structure for apartments built with standardized modules.
-David Hertz reused the wings of a 747 as roof for a villa in Malibu.
-TYIN Tegnestue architects restored a building with recycled materials, mainly found on location.
-Yatin Pandya and Footprints E.A.R.T.H.
-built an activity centre in Ahmedabad using items that were considered as rubbish to their original owners.
-James & Mau and Infiniski designed fashion homes with recycled containers.
-The same kind of containers were used by MacArthur Studio and Means & Wells, to build a travelling exhibition pavilion.
-The GAD.
-In London, Folke Koebberling and Martin Kaltwasser constructed an experimental theatre using only recycled materials.
-The panorama that emerges shows the extreme heterogeneity of the work, materials and techniques, the intuitive approach and the infinite possibilities offered by recycling.
-All of these projects highlight the importance of the construction process as an opportunity for learning and discussion.
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\summary{Resistance} 
+\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+(sahlins 1992, 16)"
+
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\summary{Ironic}
+\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
+the irony is often embodied visually and conceptually.
+opposite of natural use, expected perception.
+for example making something from nothing or turning trash into treasure.
+By juxtaposing different materials changing context and place.
+
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
+It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
+
+% Günlük rutinleri çöp üzerinden yakalayanlar var. Her gün ürettiği çöpün fotoğrafını çeken insan... Ürettikleri çöpleri ifade etme araçları olarak kullananlar.

### 2015-12-06 chapter4_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

@@
 
-[Transform] With the help of art (and artistic practices) discarded things can find a place in the society.
+\summary{Transform} 
+With the help of art (and artistic practices) discarded things can find a place in the society.
 (By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).) With the help of art discarded things ---in the scope of thesis particularly paper trash--- can be transformed beyond the other industrial (or technological) methods.
 
-[Work] Converting disposal things to multiple usage (or anything that is durable as noted in the rubbish theory).
+\summary{Work} 
+Converting disposal things to multiple usage (or anything that is durable as noted in the rubbish theory).
 Realizing the alternative lifes of trash beyond their defined one shot life.
@@
 
-[LIFE PRACTICE, CHANGES ON PEOPLE] Actually (It is questioned that) the effects of working with trash to the life practice.
+\summary{Life practice, changes on people} 
+It is questioned that the effects of working with trash to the life practice.
 Working with trash is a convergence of behavioral patterns (attitudes toward to trash) and art making.
@@
 
-[DISTANCE] The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
+\summary{Participation} 
+The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
 The important thing is to interact with it.
@@
 
-[ACT, COMMUNICATION, COLLABORATION] In this work it is claimed that the process of transformation of trash can be treated as artistic act.
+\summary{Act, communication, collaboration}
+In this work it is claimed that the process of transformation of trash can be treated as artistic act.
 In the production of notebooks people collected papers from different places and location.
@@
 
-[NEW RESOURCE] Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
+\summary{New resource} 
+Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
 Ignored and discarded nature of garbage, when rethought, becomes a fertile resource.
@@
 % FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-[building new things from ruin] \comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+\summary{Building new things from ruin} 
+\comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
 Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.
@@
 % TODO new comer. Statement or approach.
-\comment{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+\summary{Trash and other discarded notions} 
+From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
 There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
@@
 
-\todo{images are here.}
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
+        %\caption{Sax}
+        \label{fig:exhibition1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
+        %\caption{Violin}
+        \label{fig:exhibition2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
+        %\caption{Violin}
+        \label{fig:exhibition3}
+    \end{subfigure}
+    \caption{Installation try outs}
+    \label{fig:exhibition}
+\end{figure}
 

### 2015-12-06 chapter5.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

@@
 They have differences in terms of purpose and approached to the trash.
-Some of them only valued from its plastics effects (physicall properties).
-Some of them turned to the performative act.
+Some of them only valued from its plastics effects (physical properties).
+Some of them turned to the performance.
 
@@
 %
-\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers.
+\summary{Evolution, Critics} During the process I have also generated lots of trashed papers.
 Cutting and pasting things also leave unused items.
@@
 Saved for later use.
-On the other hand being aware of this trasnformation act is very tiny part of the big picture.
+On the other hand being aware of this transformation act is very tiny part of the big picture.
 I can say that my trash is reduced but is it same for the other people.
@@
 Need to find a way because varda uses her discarded item inside of the film.
-Always(or in every proceses) new discard items are generated.}
+Always(or in every process) new discard items are generated.}
 
@@
 %
-\textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
+\summary{Future Works} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
 

### 2015-12-16 chapter2_reduced.tex
Chapter review
Former-commit-id: f64723a83902ea5f39ee5e85800eba6ae02dbc92

@@
 %
-In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect.
-Theoretical foundations of trash (Rubbish Theory) are discussed.
-Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with the help of ideas of philosophers (Zizek).
-Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash.
-Further it is mentioned how artist are approached to these notions and how their work viewed from offered window (or theoretical and conceptual framework).
+In this chapter trash and the practice of transforming it is examined in theoretical and conceptual aspect.
+Referred to the ideas and work of philosophers and anthropologists to establish a better understanding of trash beyond common perception and dictionary meaning of it.
+
+Firstly, focused on the disposable items that are designed to be ended up in waste bin after a single use.
+Their usage and place are examined in the society and how other artists used and transformed them is analyzed.
+Further, disposable items are one of the key material used in the thesis project.
+Therefore, they need to be discussed in detail.
+
+Secondly, looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.
+
+Lastly, through "Rubbish Theory" transformation of trash and its various status as an object category that is not static is examined.
 
@@
 \section{Throw away culture}
-Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?
 
-%
-%
-\summary{Disposable items}
-\comment{Disposable: made to be used once or only a few times.
-Made to be thrown away after one use or several uses.
-Not permanent or durable.
-Not designed to reuse again and again.
-For examples packages of bevarages, paper cups etc.
-They are used very short-time.
-Their lifetime can be measured in minutes in terms of usage.
-However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.} \todo{ref.}
+% Life Magazine, 1955, "Throwaway Living", p43
+\summary{Throwaway Society} 
+Life magazine published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955 \todo{ref}.
+It is described as behavioral consumption pattern of society based on throwing away objects after use.
+The article addresses the question of
+% https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
+\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?
+\todo{cite}} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
 
-% In light of this argument,
+According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth. \todo{ref. rathje1992rubbish p41}
 
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-\summary{Life an object} 
-\paraphrase{One could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
-This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
-In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \cite{gregson2007identity}.
+According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
+However, their research did not include disposable packaging and bottles.
+Therefore, the act of throwing away can be narrowed down the specific goods.
 
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-\summary{Consumerism} 
-\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
-
-\summary{Capitalism, market} 
-The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
-They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
-This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
-\todo{Waste and wantta bununla ilgili bir bölüm olmalı.}
-
-\summary{Initial function} 
-When an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
-Once a newspaper is read, or a bottle of coca cola consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
-
-\paraphrase{being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid (Hawkins 2006: x)}
+In this thesis dealt specifically with industrially produced consumer discards and their subsequent transformation.
+This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production \todo{ref.
+Mamiya 1992, 2}.
 
@@
 
-% Reference from Identity, mobility and the throwaway society
-\summary{The term throwaway culture} 
-Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}.
-\comment{Scholars argue that contemporary societies are throwaway societies (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
-O’Brien, 1999; Hawkins and Muecke, 2003) \todo{ref required.}.} The term is actually a criticism of over consumption of short-live disposable objects.
-\comment{The term over consumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.} \paraphrase{Importantly the term throw away society has a slightly negative connotation, or meaning.
-When you describe a society as a throw away society, you are probably criticizing that behaviors or showing your disapproval.}
+%
+%
+\summary{Disposable Items}
+Disposable items are made to be thrown away after used once or only a few times.
+They are not permanent or durable and not designed to reuse again.
+Packages of beverages, paper cups and tissues are some of them.
+They are used very short-time.
+Their lifetime can be measured in minutes in terms of usage.
+However, their usage duration is very short, they continue to exist in nature.
 
-\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
-1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ...
-was supplying the customer with hundreds of disposable containers and materials by the end of the nineteenth century.
-the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} \todo{ref.
-Hangi kaynaktan?}
+Many products that are delivered in these days are not designed to last for a long time. As a result, this encourages people to continue throwing goods away instead of repairing and reusing.
 
-% Reference from Identity, mobility and the throwaway society
-\summary{Counter-argument} 
-According to conducted a qualitative research people are really do not throw away their things.
-People are not wasteful as claimed.
-However, \paraphrase{the research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}.
-They analyzed the things like television, furniture and toys like that.
-Therefore their result showed that people are not so wasteful as claimed when considering durable items.
-However in this thesis scope, the focus is disposable items and it can be mentioned the wastefulness of society.
-\todo{bu kısmı adam et.}
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\summary{Life of an Object} 
+One could claim that the end of the life of an object corresponds to the moment when it is refused.
+This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
+At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
+\todo{ref.
+emgin2012trashion p.63}
 
-\summary{Consumer culture}
-\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these thesis are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
-In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2).} \todo{find exact ref.}
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
+\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{ref.
+hawkins2001plastic p.9, emgin2012trashion p.64}
+
+% TODO Waste and Want disposibility p9
+
+\summary{Capitalism, market, encouragement} 
+\paraphrase{The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+They were designed to decrease in value over time - to be used one, or twice and then to be thrown away.
+This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.} \todo{ref.
+cerny1996recycled}
+
+\summary{Initial function} 
+\paraphrase{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash.} \todo{ref.
+cerny1996recycled}
+
+\summary{Being wasteful}
+As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \todo{ref, hawkins2005ethics p.viii} because the cost of repairing objects sometimes is higher than the original one or very close to it.
+On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.
 
@@
 Technological advancements can be one of them.
-These items with the help of industrialization can be produced easily.
+Disposable items with the help of industrialization can be produced easily.
 Mass production.
-Disposable items are reduces the labor and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup).
-Another point is that they are more affordable in terms of supply chain and cost.
-In other words you can put new one easily.
-Therefore there is no need to save the old one.
-Last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
-\paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref.
-ontology of trash}
+Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs.
+wipes, glass vs.
+paper cup).
+Another point is that they are more affordable regarding supply chain and cost.
+In other words, people can put new one easily.
+Therefore, there is no need to save the old one.
+The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
+\paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontologyh}.}
 
-\paraphrase{Taken to its obsessive extreme, the germ theory proscribes companionship.
+% hygiene and cleanliness (Shove, 2003, Comfort, Cleanliness and Convenience)
+
+\paraphrase{The germ theory proscribes companionship.
 The Latin root for this word, cum pani, literally means to share bread.
-But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self.
+However, insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self.
 Safety in a world of bacteria implies isolation.
@@
 ontology of trash}
+
+% toilet paper comes here. Factors related with disposable items.
 
@@
 Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free.
-Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs.
+Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs.
 Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup.
@@
 For same cases it is inevitable.
-Beyond the advantages of disposable items there are side of effects of consuming them excessively.
+Beyond the advantages of disposable items, there are side effects of consuming them excessively.
 They result in mountains of garbage.
 
-\comment{Handling of mountains of garbage is another topic.
-It is not the topic of this thesis.
-It is not debated that usage of disposals are supported or not supported.
-It might be subject of another thesis.
-What is important here the results of it and the reflection of the artist.} \comment{Buna karşı geliştirilen bir refleks olduğu için bu kısma giriyorum.
-Aynı zamanda ben de bu ürünü kullanıyorum.
-Konuyu o yüzden farklı açılarından anlamak gerekli.}
+Handling of mountains of garbage is another subject and will not be discussed in this thesis.
+It is not claimed that whether usage of disposals is supported or not.
+It might be subject to another thesis.
+What is important here understanding the place of garbage for the people and the reflection (approach) of the artist.
+
+% TODO need relocation.
+% FROM Garbage in Modern Thought, Encyclopedia
+%\comment{THROW AWAY CULTURE.} 
+%\paraphrase{Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.” "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
+It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
+Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
 
@@
 \summary{Art}
-There are some artists whose works are related with the phenomena expressed above.
-(Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.
+There are some artists whose works are related to the phenomena expressed above.
+(Some of the works of the artist can be examined in this phenomena.) Not every person throw away disposable objects, some of them save them and use for their purposes.
+They establish some methods to reflect the throwaway culture and its consumption and trash generated patterns.
 
@@
 \end{subfigure}
-\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
+\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
 \label{fig:ChrisJordan_Numbers_CapsSeurat}
@@
 Chris Jordan creates digital photographic series that turns numbers to visuals.
-Provide different way to understand the statistics and the missed reality of consumerism.
-Creates gigantic prints to express numbers in a visual manner.
-Draws attention the the global consumerism.
-reveals the reality that is hard to understand.
-Because it is spread to the community and time.
+He provides a different way to understand the statistics and the missed reality of consumerism.
+He creates gigantic prints to express the numbers in a visual manner.
+He draws attention the global consumerism.
+The work reveals the reality that is hard to capture because of widespread of subject to the community and time.
 
-\paraphrase{Portraits of Global Mass culture from Chris Jordan.
-Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+\paraphrase{Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work.
+In this series, he revisits the statistics of modern societies.
 In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
@@
 \summary{Analysis}
+In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism.
+The work accepted as a well-known example of pointilizm that is a technique of painting in which little, individual dots of color are applied in patterns to form an image.
+This method shows similarities with mosaics of ancient times and pixels of modern times.
+To make an work from bottle cups with different colors can be related to painting millions of small dots on a canvas.
+The shape of plastics cups similar to the dots painted onto the canvas so that there could not be a better example of reproduction.
+
+Seurat spent over two years painting A Sunday Afternoon, focusing meticulously on the landscape of the park.
+However, in our age, it takes only one minute to create the bottle caps that form this painting.
+In this respect, it reveals the point where society reached.
+
 Visuals of Chris Jordan are like modern versions of mosaics.
-In the age of consumption the most easily accessible material is trash.
-Trash has different colors and sizes and shapes.
-Therefore it is a perfect material to build sculptures from them.
-There is a great diversity of trashes and offers new alternatives.
+In the age of mass production and consumption, the most readily available material is trash.
+It is free and available everywhere, produced every time.
+Trash has different colors, sizes, and shapes.
+Therefore, it is a perfect material to build sculptures from them.
+There is a great diversity of rubbish and offers new alternatives.
+Nothing is missing with the physical attributes of trash to create visual work.
+
+% Here, sculptures from trash can be added.
 
@@
 She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
-The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags.
+The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations.
+The artist draws, paints, and forms collages on the salvaged tea bags.
 This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers.
@@
 Trashes transformed to diaries.
-Trash is every where, already at hand.
+Trash is everywhere, already at hand.
+Small pieces of paper or packages are used as a canvas.
 
@@
 \paraphrase{I began to save all of my coffee cups to use as "canvases" for making art.
-Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture.
+Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture.
 I like my coffee or tea in a paper take-out cup.
 Even better than the contents, I like the used cup as a surface on which to draw and paint.
-And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
-Each cup representing a daily caffeine break.
+Moreover, on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
+Each cup is representing a daily caffeine break.
 The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
 It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill.
-But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.
+However, as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.
 There are different versions of it.
-paintings on paper coffee cups displayed as installation in public window spaces.
-She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date.
-During public drawing projects she draw with other people.
-and so.
+Paintings on paper coffee cups displayed in open window spaces.
+She publicly draws their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date.
+During public drawing projects, she draws with other people.
+Moreover, so.
 Buying a beverage is a daily event for Leech (and also many people.
 These coffee shops all around the world.
-As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}
+As she drinks her coffee in the public, she also publicly transforms its cup.} \todo{cite her website}
 
 \summary{Analysis}
-Inside of glass window. Public space. As she drinks her coffee publicly, also paints them publicly. \todo{related with Liz Parson's argument: practice of trash to durable.}
+She is inside of glass window not white, isolated cube.
+Glass window provide her to be close to public space.
+As she drinks her coffee publicly, also paints them publicly.
+\todo{related with Liz Parson's argument: practice of trash to durable.} There is no difference between them, and also they should not be separated (Why?
+Trash, production of it, coffee cups are all experienced widespread.).
+By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something.
+Further she is not only transforming her trash, it is everybody's trash because of everyone uses it.
+
+These three artists mentioned here use disposable items to make their art.
+Their approach bring another dimension to criticize (or see) the disposable items.
+New things can be built from them.
+They can be used for new purposes.
+
+Throwaway culture is a way of producing trash.
+It is a behavioral pattern, an approach to objects and commodities.
+Some artists develop different approaches to them.
+In this type of culture or behavior throwing them is a natural act and promoted.
+Consumption and wasting things are encouraged.
+On the other hand, there are examples of saving everything instead of wasting.
+In the work of Song Dong, "Waste Not" thousands of domestic objects are exhibited.
+They are owned by his mother and saved for later use.
+His mother lived a great depression in China, suffered from poorness.
+She developed the habit of saving things.
+After died of her husband this habit reached to extreme levels.
+She saves every tiny little thing.
+For her trash becomes an essential part of her life.
+In fact, it not is hard to say that preserved these things are not useless or worthless.
+She establishes a different relationship with these used objects.
 
@@
 %
-\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of people's life.
-What people consume is actually tells many things about them (their choices, possessions etc.) \todo{ref.}.
-As scholars mentioned that throughout the discards of someone else many thing can be understand.
-They are end product of our activities and it can be traced through the discard and garbage.
+Trash is much more than what people want to discard. Characteristic of people and societies can be understood from their produced trash.
+
+\summary{TRASH and POTRAIT OF PEOPLE} 
+Trash is a reminder of consumption and production activities.
+In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action.
+Trash tells about societies choices.
+What is being left is one of the key things to realize what kind of people, society, action produce it.
+At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.) \todo{ref.}.
+As scholars mentioned that throughout the discards of someone else many things can be understood.
+They are end product of people activities, and it can be traced through the discard and garbage.
+It is a great example of the approach to the trash is relative and changes from people to people.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
+  \caption{Song Dong, Waste Not, 1990}
+  \label{fig:SongDong_WasteNot}
+\end{figure}
+
+"Waste Not" is an exhibit by Chinese artist Song Dong that displays over 10,000 domestic objects formerly owned by his late mother, who refused to throw anything away if she could possibly reuse it.
+
+Song’s mother, Zhao Xiangyuan (1938–2009), was typical of the generation of Chinese who lived through the hardships of the Cultural Revolution in the 1960s and 1970s abiding by the dictum "wu jin qi yong" (waste not).
+As a result, all commodities owned or collected stockpiled and preserved as protection against future hardship, even in the face of improving economic conditions.
+
+Waste Not is an installation exhibited different locations of the world. This work is a collaboration with the artist’s mother.
+
+\paraphrase{Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had.
+Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.}
+
+\paraphrase{When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends.
+Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful.
+Song eventually came to understand that, as he puts it:}
+
+\begin{quote}
+My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death.
+I recognised that in this era of transition, a person could live through several different lives in just one lifetime.
+In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
+\end{quote}
+
+Everything that are exhibited here is different than presented on supermarkets.
+They are not new and not for sale.
+They represents a way of life.
+It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects
+
+For most of people living in western modern societies it is unimaginable to live with all of these items together.
+However, for Chinese who are faced with same struggles share the emotion and  comment as "It's not [only] your home, it's my home."
+
+Jane Alison, senior curator at the Barbican, said that Waste Not helps us to understand the reality of Chinese history and culture in the 20th century in a way that newspapers can't.
 
@@
 The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}
-
-% TODO need relocation.
-% FROM Garbage in Modern Thought, Encyclopedia
-%\comment{THROW AWAY CULTURE.} 
-%\paraphrase{Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.” "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
 
@@
 
-\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice.
+\paraphrase{The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice.
 At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene.
@@
 
-\todo{transition required.} With the help above understanding of trash, what can we see the work of arts?
+\todo{transition required.} With the help of mentioned understanding of trash, what can we see the work of arts?
 
@@
 
-\paraphrase{Tracey Emin puts her private life to the public.
+Tracey Emin puts her private life to the public.
 The work, which Emin now describes as a portrait of a young woman.
-Around her there are pieces of junks speared all over the room.
-We can understand from her junk what type of life her has.
-We enter the world of artist through the her trashes.} \todo{Hastalık dönemi...
-Sanattaki yerine bakmak gerekli.}
+Around her, there are pieces of junks speared all over the room.
+We can understand from her junk what type of life she has.
+We enter the world of the artist through her trashes.
+
+% From wiki
+Every detail of her private life is presented through her bed.
+The idea for The Bed was inspired by a depressive phase in the artist’s life when she had remained in bed for several days without eating or drinking anything but alcohol.
+The sensation of depression leading to disarray and detritus is not wholly unfamiliar to many people, and The Bed therefore enforces the communicative power that Tracey Emin seeks with her work.
+The artwork generated considerable media furor, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist's room, such as condoms, underwear with menstrual blood stains, other detritus, and functional, everyday objects, including a pair of slippers.
+The bed was presented in the state that Emin claimed it had been after languishing in it for several days; at the time she was suffering suicidal depression brought on by relationship difficulties.
+
+It is a realization what she did during her depression time.
+It perfectly represents her condition during days.
+It can be understood that trash is part of our life.
+Things that are exhibited in this work are part of her action.
+She created them and later through them in the mind of people the condition and life of Tracey Emin are recreated.
+
+% Independent http://www.independent.co.uk/arts-entertainment/art/reviews/tracey-emins-my-bed-at-tate-britain-review-in-the-flesh-its-frankness-is-still-arresting-10144882.html
+You can interpret it as an uncompromising self-portrait of a woman at a time of emotional trauma – or as a turbulent still life – but it is still a bed and all that a bed symbolizes and encompasses: sleep, sleeplessness, sex in all its manifestations, birth, death and dreams.
+
+Beds meaning also are not same for everyone.
+It is not just for sleep.
+Especially for the ones that have small rooms and spaces bed becomes a life space.
+I have also experienced such a thing at boarding school and university dormitory for total my eight years.
+Having tight space sometimes bed becomes a place for studying and reading.
+Sometimes it was used to dry the clothes.
+It is more than sleeping and provide place for other activities.
+
+% Aslan yattigi yerden belli olur.
 
@@
 \section{Zizek's Approach to Rubbish}
-\todo[inline]{transition required.} 
-Last decades there is increasing attention the ecology and rubbish.
-This section is related to the increasing interest in ecology.
+Last decades there is an increasing attention the ecology and rubbish.
 Global warming is one of them, plastic pollution on the oceans also is part of it.
@@
 
-% TODO new comer
-% \paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}
+\paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}
 
-In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London.
-His part starts with these sentence: \quotes{This [garbage dump] is where we should start feeling at home}.
+In the documentary film Examined-life Zizek dressed as a sanitation man discusses ecology in the middle of a dump in London.
+His part starts with these sentence: \quotes{This [dump] is where we should start feeling at home}.
+The place where he talks is a site for depositing people's excess and unwanted material.
+It is a place of out of sight.
 
-Draws attention to notion of even if trash disappears from our world but not world.
-It seems as though the thrown out garbage disappears from our world.
-However, it disappears only from the world of illusions, but still exists in reality.
-\comment{Getting rid of it is not action of production.
-It is action of ignorance.
-It still waits us at somewhere else or the next generations will have to cope with it.
-Maybe (as Zizek suggest) the first thing to do is accept the trash.}
+He draws attention that the thrown out garbage only disappears from people's living environment.
+Particularly discarding it is an action of escape from the unwanted.
+However, it still exists in reality and waits at somewhere else.
+In other words, it does not disappear, moves away.
 
-He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology.
-He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing.
-He claims that it is ideological in the sense that wrong thinking important problems.
-Nature contains unimaginable catastrophes.
-Consider distinction of animals and creation of oil.
-People profit from the balance of the nature but it is created from a series of catastrophes.
-He asserts that ecology will slowly turn to religion that \quotes{is a kind of an unquestionable highest authority.} Ideology of ecology warns us like, \quotes{Don't do that.
-It would be too much.} its voice is like \quotes{Don't mess with D.N.A.
-Don't mess with nature.
-Don't do it} etc.
-He suggests that people must more alienated from the nature.
-They must find poetry and spirituality in the dimension of trash.
-That's the true love of world.
-Love is not about idealization.
-Therefore he thinks that garbage dump is a place that people should accept it as a home.
+According to Zizek, the way of approaching ecology is problematic in current societies because of accepting nature as a balanced, and harmonious.
+He claims that it is ideological in the sense that "wrong way of thinking and perceiving reality".
+The meaning of ideology is here mystification of real problems.
+He claims that one of the key mechanism of ideology is temptation of meaning.
+In other words, people search for meaning when a terrible event happens in order to make it easier to accept.
+He opposed the notion of the existing world is in the best possible state and that humans disturb nature.
+According to him, nature is not an organism in balance that humans exploit, but rather a series of "unimaginable catastrophes" by asking the question what type of disasters would happened on the earth to compose oil that is a significant source of energy.
+Zizek asserts that ecology will slowly turn to a conservative ideology that is a kind of an unquestionable highest authority.
+Its voice is like "Do not mess with D.N.A.
+Do not mess with nature".
+In the light of these arguments instead of talking from an authoritarian high ground, he suggests that to find poetry and spirituality in the dimension of rubbish people create.
+He thinks that that is the true love of the world by asserting that "love is not idealization." Therefore, that is the reason why he thinks that a dump is a place that people should accept it as a home.
 
-\quotes{According to Zizek, modern understanding of ecology is the real false consciousness, connected with mystification of real problems.
-Postmodern mysticism arises when disasters begin to be rationalized, interpreted in strict logic terms of cause-effect relations.
-Such interpretation makes life easier.
-However, nature is not an absolute balance and total harmony (this aspect of Zizek’s thought makes him akin to classical conservatives).
-Nature is a series of unthinkable disasters.
-Zizek believes that ecology is transforming into a new western conservative ideology: “One should not play games with nature!
-Do not touch DNA!
-Do not develop new medicines!
-Do not invent new technologies!” How one should react to these reproaches?
-Zizek’s recipe is to reinforce alienation from nature, to become more artificial.} \cite{vafin2012zizek}
+In the light of Zizek's arguments ecology is not an appropriate point (or enough) to approach trash.
+He points out the need for the new approach to trash.
+This new approach should not idealize it.
+At this point where the practices of art gains importance to establish new understanding of trash.
 
-\paraphrase{His basic argument is that the modern eco movement is a conservative ideology.
-It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology.
-Basically he says the eco movement has it's head in the clouds.
-If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.}
-
-Some of his ideas can be summarized as follows:
-\begin{itemize}
-\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
-\item Ideology addresses real problems but mystifies them.
-\item We search for meaning when a horrible event happens to make it easier to accept.
-\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
-\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
-\item Ecology is becoming more like religion with dogmas.
-\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
-\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
-\item Learn to love our trash as a part of ecology.
-\end{itemize}
+Not every act of transforming trash is not related to ecological concerns.
+Artists are not trying to save the planet earth.
+Beyond ecological concerns, they are attempting to find new ways to look and live with trash.
 
@@
 (Converting what we create harmonious with the existing system.
-Because it is not possible to think that nature will live harmoniously what we created.
-The more likely idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together \todo{Buraya sanat işi gelebilir, özellikle kamusal alana yapılan çöten heykel işleri gibi.}.
+Because it is not possible to think that nature will live harmoniously with what we created.
+The more reasonable idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together.
 
-\todo{needs a discussion.}
+Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.
 
-\comment{Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor.
-Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor.
-Onun dediği aslında yanlış sebep sonuç ilişkileri kurduğumuz üzerinden gidiyor.
-Çöpü tekrar ele aldığımızda ise yep yeni şeyler keşfedeğiz.
-Yeni alternatifler oluşacak.
-Aslında yeni bir dünya kurgulanacak.
-Çöp nasıl dönüştürülecekse, çöp de insanları dönüştürecek.}
-
-Transforming trash is not related with ecological perspective. We are not trying to save the planet earth. Beyond ecological concerns we are trying to find ways to live our trash.
-
-Zizek mentions that ecology is something wrong point to approach trash.
-Shows the problematic understanding of garbage.
-Suggest another thing, and point out the need for the new approach.
-Beyond the ecological problem there are different sides of it.
-Different readings can be added to the topic.
-Adding spirituality and new aesthetics dimension to the topic.
-
-Idealization of nature is problematic.
+The idealization of nature is problematic.
 Loving nature is loving trash.
 Live with trash.
-Do not see it as trash actually.
+Do not see it as trash.
 Then the question is How to love trash?
@@
 Think beyond the common perception.
-Do not think it as abject, disgust.
-Can living with our trash enrich (our perceptions, abilities)?
+Do not consider it as abject, disgust.
+Can live with our trash enrich (our perceptions, abilities)?
 How not to see them as trash and useless?
 Can it be possible with art?
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
-  \caption{Song Dong, Waste Not, 1990}
-  \label{fig:SongDong_WasteNot}
-\end{figure}
-
-Zizek's argument can bring minds to the question that is our home going to be turned to trash home?
-Actually an artist work is based on habit of not wasting.
-In the installation thousands of items are displayed.
-They are saved instead of throwing.
-\todo{details}
 
@@
 \section{Rubbish Theory}
+Objects have a lifetime similar to humans, and they do not remain same through that time.
+They move around, and their value, usage, location change constantly.
+During their lifetime objects may circulate different markets and values systems such as economic, social and aesthetic.
+Especially these cycles have picked up speed with the advent of consumer culture.
+For instance, most recent technological gadgets become obsolete within two or three years.
+Firsthand, secondhand and even trash is exchanged among not only people but also countries.
+People from other cultures and understanding interpret objects differently.
+They often are not aware of their initial and intended usage.
+They find new original purposes and meanings.
+Therefore, objects turn different items in their hand.
+Anthropologist Sidney Mintz (as cited in Susan Strasser) writes that "I have seen automobile bearings fashioned into portable vulcanizing kits; bits of toothbrush handles used as 'jewels' for rings, and ordinary tin cans turned into simple kerosene lamps." As it can be understood that objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
 
-\comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük.
-Zaten bu hayatta çöp her zaman karşımıza çöp olarak çıkmıyor.
-Bu hareketlilik ve farklılık ise Rubbish theory ile teorik çerçeveye oturulmuş.
-Bir yandan da çöple birlikte yaşayalım dedik ama bakalım nasıl olacak o iş.}
+In ‘The Social Life of Things’ Appadurai (1986: 3) highlights that "commodities, like persons, have social lives." As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+Appadurai focuses on the "commodity potential" of things and asserts that "things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant" (1986: 13).
+However, one can ask that what are these commodity states and does anything exist between them?
+Thompson’s Rubbish Theory fills this gap.
 
-In this thesis transformation of trash is claimed and this theory provides a framework for this transformation.
+Thompson observes the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
+He notes how an object’s economic and cultural value diminishes over time rendering the objects worthless or redundant and how others value increases overtime.
+In his notable Rubbish Theory, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value).
+The transient represents the common state of objects that are lessening in value and have limited life period.
+A used car can be an example of transient state.
+On the contrary, the durable objects increase in value over time and have (ideally) infinite life spans.
+Antiques and objects in museums can be an example of durable.
+This theory gives rubbish a key role between transient and durable.
 
-% Rubbish theory'de durable dediğimiz bir kategori var.
-mesela picassonun sözü de buna bir şekilde karşı duruş sergiliyor.
-Çünkü dönüştürmenin devamlılığını arzuluyor.
-Ama durable olan şeyin bir konumu sabitlenmiş oluyor herhalde.
-
-% TODO new comer.
-%\comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+% TODO Bu nereden
+Rubbish is, by definition, an object that is not or is no longer, owned by anyone, which falls outside all categories of economics, culture, and social control.
 As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
@@
 
-% TODO new comer
-\summary{Moves} 
-\paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}
-% TODO new comer
-\paraphrase{Objects moves around and their values change constantly.
-(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
-The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}
-% TODO new comer,  BAZI KISIMLARINI AÇMAK GEREKLİ AMA.
-The important thing is moving nature of trash.
-Objects moves and gains different meanings through this movement.
-Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
-It also signifies that it is relative and result of a classification issue.
+The potential of the discarded thing also relies on its status as a thing approaching a zero point of value.
+In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty.
+As Michael Thompson’s Rubbish Theory suggests that rubbish is both ready for the disappearance and yet ripe for reinvestment, reinterpretation or revaluing.
+Trash as a state of being flexible is ready to transformation.
 
-% TODO new comer
+Similar to Žižek's claim that is "trash does not disappear", Thompson notes that "in reality ...
+[trash] just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered."
+
+Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
+Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
+Figure X demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
+  \caption{Thompson’s Rubbish Theory}
+  \label{fig:rubish_theory}
+\end{figure}
+
+The transitions between these states defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).
+
+To illustrate rubbish theory the series of compression by French sculpture César can be analyzed in the context of it.
+His early work is composed of soldered and welded metal as well as junk materials.
+In 1960, Caesar discovered the hydraulic press that is capable of compacting scrap metal (especially car bodies) during on a visit to a scrap merchant in search of metal.
+He admired from the hydraulic crushing machine in operation and started to experiment with it in his sculptures.
+The machine is used to compress the metal items in order to gain from space.
+His first three automobile compression exhibited at Salon de Mai in 1960 and bring him a supportive fame.
+Later Viscountess Marie-Laure de Noailles who is important figure of these ages, gave him her Zim model car to compress.
+It is
+% http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
+"a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac." Additionally car was one of the most desired possessions of people in 20th century.
+Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum.
+In other words, it switched to durable category by interestingly trashing it.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/Cesar_Zim.jpg}
+  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
+  \label{fig:Cesar_Zim}
+\end{figure}
+
+Although Thompson is quite successful describing states of objects, claimed transitions between states in the theory have some problems.
+Thompson label some transitions as possible and the others as impossible.
+He only allows movement of goods from transient to rubbish, and from rubbish to durable.
+Movement in the other directions, from durable to either transient or rubbish, does not exist in this system.
+However, Duchamp's notable ready-made "Fountain" is one of the examples outside of the defined transitions.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
+  \caption{Marcel Duchamp, Fountain, 1917}
+  \label{fig:Duchamp_Fountaine}
+\end{figure}
+
+Fountain is a 1917 work produced by Marcel Duchamp, who is notable member of provocative Dada movement.
+The piece was an industrial porcelain urinal, which was signed "R.Mutt".
+Submitted for the exhibition of the Society of Independent Artists, in 1917, Fountain was rejected by the committee, even though the rules stated that all works would be accepted from artists who paid the fee.
+It is considered one of the major artworks of the 20th century because of challenging the existing understanding of art.
+Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist.
+It forces to the limits of the language of art and perception the art.
+To understand his works requires shift inside of the peoples mind.
+For him, the idea is important rather than the object.
+He also criticized the position of artist by signing urinal as "R.Mutt" who is actually not exist.
+In the editorial The Blind Man summarized this work as follows: "Whether Mr.
+Mutt with his own hands made the fountain or not has no importance.
+He CHOSE it.
+He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object.\todo{ref}" To debate all the aspects of this work is not possible with the scope of this thesis.
+However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist.
+Urine titled as "fountain" is still functional and have a place in the market.
+In another word, it is not rubbish.
+
+\todo{bir conslusion lazım buraya.}
+
+% TODO move to conclusion.
+%Rubbish theory suggests that value emerges through people ways of seeing, and their category membership determines the way people act towards them.
+Similar to X (as indicating that scholars agree on this argument.)
+
+% TODO move to conclusion.
+% \paraphrase{Michael Thompson’s study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity, and social status.} \todo{ref.
+from Trash Culture} \paraphrase{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder \cite[97]{thompson1979rubbish}.}
+
+% TODO relocate
 % From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-\summary{Moves} 
-\paraphrase{Below part explains journey of trash in different steps/stages.
+%\summary{Moves} 
+%\paraphrase{Below part explains journey of trash in different steps/stages.
 Object moves and trash also moves.
@@
 
-% TODO new comer
-% Ama çöp olarak zaten kalmıyor.
-Bir şekilde hayatımıza tekrar giriyor.
-Ne kadar itise de...
-Trashion: the return of disposed.
-Peki geri dönüşü nasıl bir değişiklik yaratıyor.
-Ya da gerçekten geri geliyor mu?
-Kullandığımız ürünlerin ne kadarı tek kullanımlık.
-Tek kullanımlıklarla nerede karşılaşıyoruz.
-Evet belki hayatımızda çok kullanılan şeyler var fakat.
-Daha tek kullanımlıklar da var denilebilir.
-\summary{Moves}
-\paraphrase{Trash moves, all the time.
+% TODO relocate
+%\summary{Moves}
+%\paraphrase{Trash moves, all the time.
 It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
@@
 
-\summary{Categorization of waste} 
-% TODO new comer
-\paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+% TODO relocate
+%\summary{Categorization of waste} 
+%\paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
 (Think that the transformation process.
@@
 
-% TODO new comer
-\paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+% TODO relocate
+%\paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
 Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
 
-% TODO new comer
-\comment{Susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
-Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
-Remember the given example: shoes on the dinner table.}
+% TODO relocate
+%\paraphrase{Waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
 
-\paraphrase{Waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
+% TODO relocate
+%Trash is something that is out of sight, out of mind.
+Paid little attention to them and only catches attention when it is in wrong place.
+It is an unexpected object for people.
+Therefore transformation of it can create powerful and suprising effect onto the people.
 
-\todo[inline]{Buradan nasıl rubbish theorye geçilecek???}
-
-\paraphrase{Michael Thompson’s study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity and social status.} \todo{ref.
-from Trash Culture} \paraphrase{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder \cite[97]{thompson1979rubbish}.}
-
-\paraphrase{The potential of the discarded thing also relies on its status as a thing approaching a \quotes{zero point} of value.
-In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty.
-As Michael Thompson’s Rubbish Theory  suggests, at its nadir in a cycle of consumption and production, rubbish is both ready for disappearance and yet ripe for reinvestment, reinterpretation or revaluing \todo{ref.
-from Trash Culture}.}
-
-\paraphrase{Objects have a lifetime and they don't remain same through that lifetime.
-Their value, usage, location change over time.
-During its lifetime objects may circulate different markets and values systems like economical value, social value, aesthetic value etc.
-Especially this cycle has picked up speed with the advent of consumer culture, our most recent technological gadgets becoming obsolete within 3 years.
-Objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
-This flow(transition) and transformation theorized with Rubbish Theory by Thompson \cite{thompson1979rubbish}.
-Thompson looks at the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and/or cultural value diminishes over time rendering the objects worthless or redundant.
-The theory looks at how some of these objects then regain value, such as antiques or historic homes.
-It claims that there are three types of objects; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish(zero value, will be destroyed or reinvested for economic and social value).
-The transition from transient to durable is only possible firstly transient to rubbish and later rubbish to durable.
-Further, there is a common idea/argument/motto that is "trash to treasure" among artists who use trash as a medium.
-Rubbish theory presents a conceptual approach to this argument.}
-
-Although Thompson is quite successful categorizing states of objects throughout their lifetime, claimed transitions between states in the theory have some problems.
-Thompson label some transitions as possible and the others as impossible.
-\quotes{He allows goods only to move from a transient to become rubbish, and from rubbish they can either be destroyed or become durable.
-Movement in the other direction, from durable to either transient or rubbish, is not allowed in this system} \cite{meadow2011relocation}.
-Further, he does not allow move from transient to durable.
-However, Duchamp's fountain breaks this rule.
-Because urine used as a fountain is still functional and have a place in the market.
-In another word, it is not rubbish.
-This urine with the intervention of Duchamp turned to be an artwork.
-It is one of the most influential piece of modern art and one of the best examples of ready-made.
-After Duchamp's intervention to the urine, it becomes a durable object placed in a museum \todo{Fontain's importance in the history of art} \todo{what happens when we look at from the eyes of rubbish theory}.
-
-\paraphrase{In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.}
-
-\paraphrase{Rubbish theory, a philosophy that attempts to address how value is placed on material objects.
-It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed.
-An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people.
-The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile.
-What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always} \todo{burada bir şeyler eksik.}
-% - Çöp ile birlikte yaşa diyorsun ama bu nasıl olacak.
-en azından mümkün mü?
-Burada aslında çöp dediğin şeyin aslında bir şeyin bir sınıflandırma sorunu olduğu ve farklı stateler arasında geçişler yaptığını görebiliriz.
-Çöp evlere değinmek gerekebilir.
-increase, while the remainder of society owns objects whose value will eventually decrease to nothing.
-\todo{ref from Liz Parsons}}
-
-\paraphrase{Rubbsih theory suggests that value emerges through our ways of seeing and placing objects. \todo{ref from Liz Parsons}}
-
-\paraphrase{Plenty of work in consumer research explores the ways in which goods might act as symbolic resources for lifestyle and identity construction (i.e.
-Belk 1988), but there is less reflection on the actual practices and activities through which goods become meaningful and valued.
-McCracken’s (1988) work on ‘Meaning Manufacture and Movement in the World of Goods’ begins to address this gap.
-He views advertising and the fashion system as instruments of meaning transfer between the culturally constituted world and consumer goods.
-He then suggests that a series of consumer rituals operate to transfer meanings from consumer goods to the individual consumer.
-These rituals include those of possession, exchange, grooming and divestment.
-The strengths of his argument include a focus on the mobile quality of meaning and some exploration of the instruments though which meaning is transferred.
-However he is not clear as to the practices which constitute these rituals.
-In addition his contention that ‘meaning resides in three locations: the culturally constituted world, the consumer good, and the individual consumer’ (1988: 89) fails to completely capture the complexity and fluidity of meaning movement.
-There is a linearity to his conceptualisation which misses the constant flux and flow of meanings in markets.
-(Summary From Liz Parsons)}
-
-\paraphrase{In ‘The Social Life of Things’ Appadurai (1986) highlights the restlessness of objects arguing that ‘from a methodological point of view it is things-in-motion that illuminate their human and social context.’ (1986: 5).
-Appadurai usefully observes that ‘commodities, like persons, have social lives’ (1986: 3).
-He focuses on the ‘commodity potential’ of things.
-‘things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant’ (1986: 13).
-However these movements do appear to be reduced to the opposites of commoditization and singularization, one might ask the question, does anything exist in-between?
-This is where Thompson’s Rubbish Theory comes in.
-(Summary From Liz Parsons.)}
-
-\paraphrase{The category of objects and experiences of no value (rubbish objects and experiences) is largely invisible.
-The transient represents the usual state of commodities as objects which are declining in value and which have finite life spans.
-Whereas the durable increase in value over time and have (ideally) infinite life spans (1979: 7).
-Thompson uses the example of a used car as a transient and Queen Anne tallboy as a durable.
-He further observes that their category membership determines the way we act towards them.
-(Summary From Liz Parsons.)}
-
-\paraphrase{Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life-span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure one demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-(Summary From Liz Parsons.)}
-
-\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
+% TODO relocate
+%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
 (Further there is similar analogy at Waste and Want.
@@
 
-\paraphrase{In an ideal world\ldots an object would reach zero value and zero expected life-span at the same instant, and then...
-disappear into dust.
-But, in reality, it usually does not do this; it just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered’ (1979: 8-9)(Summary From Liz Parsons.)}
+%
+% TODO move it to the art chapter and discuss it with the found photos.
+%\subsection{Rubbish Theory in Practice: From Rubbish to Durable}
+%\paraphrase{In rubbish theory beyond the objects states how it happens transition of objects in practice is missing and Parsons fills this gap by claiming that transition from rubbish to durable are possible with finding objects, displaying objects, re-using objects \cite{parsons2008thompsons}.} (finding paper, transforming to notebooks and giving away them to create an opportunity to be displayed different location and times.)
 
-%
-%
-\subsection{Rubbish Theory in Practice: From Rubbish to Durable}
-% TODO PRAP. REF.
-(Summary From Liz Parsons.) 
-Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
+%Three such sets of practices are explored below, they include: finding objects, displaying objects and transforming and re-using objects.
 It is argued that each of these sets of practices changes the way we view an object moving it from being seen as a ‘rubbish object’ of no value to a ‘durable object’ of increasing value.
 
-\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
-Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.What, then might one mean by ‘the find’?
+%\textbf{Finding Objects:} One key way in which objects may slide from the category of rubbish to durable is through the act of finding.
+Indeed, Gabriel and Lang (1995) include the ‘Consumer as Explorer’ as one of many possible consumer identities.
+What, then might one mean by ‘the find’?
 Ultimately the find relates to discovery, and suggests that something has been otherwise overlooked, ignored or hidden away.
@@
 % (Summary From Paul M Camic.)
-\summary{Theoretical Analysis of Found Object}
-\paraphrase{As a species Homo sapiens has been gathering and collecting objects for thousands of years.
+%\summary{Theoretical Analysis of Found Object}
+%\paraphrase{As a species Homo sapiens has been gathering and collecting objects for thousands of years.
 Food, clothing, weapons, fuel, animals, and plants are the more obvious items, but visually pleasing objects, things that arouse curiosity, and shapes that stimulate the imagination have also been sought.
@@
 
-\paraphrase{In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
+%\paraphrase{In contemporary societies, people seek objects to adorn bodies, decorate homes and gardens, and personalize places of work (Menzel, 1994).
 Seeking and finding objects, whether in vast Asian cities, remote African villages, or the high streets of Europe and North America, have become part of daily life for millions of people.
@@
 These “other reasons” pose an opportunity for researchers to better understand why people voluntarily seek society’s discarded material objects and how they make use of them.
-A form of cultural reuse, the process
-of salvaging and using found and second-hand objects has potential implications for \ldots }
+A form of cultural reuse, the process of salvaging and using found and second-hand objects has potential implications for \ldots}
 %........................................
 
-\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.
+%\textbf{Displaying Objects:} by displaying objects in home, fashion etc. (This is not a strong category.) Maybe publicly exhibiting them.
 
-\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
+%\textbf{Transforming and Re-using Objects:} These transformations may involve creating new uses for old things to fit in with contemporary lifestyles.
 Transformations may also involve the modification or updating of objects through painting, alteration or repair.
@@
 %
-%
-\section{Summary}
-\begin{itemize}
-\item Trash has archaeological value. It reflects our habits.
-\item Ecological perceptions have problems. 
-\item Moving nature of trash/objects.
+% TODO Move to Conclusion.
+%Trash has archaeological value. It reflects our habits. It is like a mirror. Can not be sepereted from their producers.
+
+%Ecological perceptions have problems. In modern socities trash seen as an ecological problem.
+
+%Moving nature of trash/objects.
 Objects value/state is not static open to intervantion, has potential to be reconsidered.
@@
 It is about perception the trash.
-\end{itemize}
 
-It is part of discussion of trash and ecology.
-
-First part analysis trash of disposable items and the works of art that looks differently to these trash.
+%First part analysis trash of disposable items and the works of art that looks differently to these trash.
 Whose trash?
@@
 
-Firstly trash is created (by the throw away culture).
+%Firstly trash is created (by the throw away culture).
 Even if there is counter argument about it, the focus is disposable items and their amount is very high.
@@
 
-Thoughts on ecology and garbage (Zizek's part). Zizek points out wrong opinion about ecology among the society. Stacking trash outside of living space is not the solution.
+%Zizek points out wrong opinion about ecology among the society. Stacking trash outside of living space is not the solution.
 
-% Adam demiş ki çöpünüzle birlikte yaşayın. Ben de zaten bunu yapmaya çalışıyorum işimde.
+%Later rubbish theory and relative approach to the trash. Trash is not static. Objects are not static. It related with the perception.
 
-Later rubbish theory and relative approach to the trash.
-Trash is not static.
-Objects are not static.
-It related with the perception.
-Classification of them.
-It is possible to change shift.
-Practices of it.
+%Thompson thinks that the switch only occurs when all the value to the given object is removed.
+To gain a new value, meaning and purpose it must be exit from previous system.
+Changing the context can only be possible first rubbishing them or loosing all value.
 
-Thompson thinks that the switch only occurs from losing all the value given the object.
-He refers that to gain new value previous systems ruins must be cleaned.
-Changing the context by first rubbishing them.
+%Thompson and Zubiaurre say trash moves amoung various range of value systems.
 
-Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.
-
-Then next chapter discusses the practices in art world in more detail. Trash in the context of art. Which purpose and which method? Approaches of artist.
+%Zizek says you must find a way of loving your trash, or a way of living with trash instead of idealization of nature and waste. Purification is not suggested by him.

### 2015-12-16 main.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999
Chapter review
Former-commit-id: f64723a83902ea5f39ee5e85800eba6ae02dbc92
Chapter 2 review
Former-commit-id: de9640209bade5dc3b51e32502a643f004e1026b

@@
 \usepackage{apacite}
-\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
+\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
 \usepackage{epigraph}
@@
 
+\usepackage[doublespacing]{setspace}
+
+\usepackage{natbib}
+\setlength{\bibsep}{0.0pt}
+
+% Adding extra space between paragraphs
+\setlength{\parskip}{\baselineskip}
+
+% To align left todos
+\reversemarginpar
+
+% Chapter titles
+\usepackage{titlesec}
+\titleformat{\chapter}[display]
+        {\normalfont\fontsize{14pt}{12pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
+\titleformat*{\section}{\bfseries\fontsize{12pt}{12pt}}
+\titleformat*{\subsection}{\bfseries\fontsize{12pt}{12pt}}
+
+% Chapter title spacing
+\titlespacing{\chapter}{0pt}{25mm}{3\baselineskip}
+
+% EPIGRAPH
 \setlength{\epigraphwidth}{.6\textwidth}
@@
 \providecommand{\comment}[1]{\textcolor{cyan}{#1}}
-\providecommand{\summary}[1]{\textcolor{green}{[#1]}}
+\providecommand{\summary}[1]{\textcolor{blue}{[#1]}}
 \providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}
-\renewcommand*\bibname{Bibliography}
+
+\addto\captionsenglish{%
+  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
+  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
+  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
+  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
+}
 
@@
 \selectlanguage{english}
+
 \begin{titlepage}
@@
 
-        \Huge
-        Transforming Trash as an Artistic Act
+        \singlespacing
 
-        \vfill
-        \Large
+        \vspace*{25mm}
+        \uppercase{Transforming Trash as an Artistic Act}
+
+        \vspace{15mm}
         A Master’s Thesis\\
+        \vspace{15mm}
         by\\
-        Mustafa İlhan
+        MUSTAFA İLHAN
 
@@
         \today
+        \vspace{25mm}
+
+    \end{center}
+\end{titlepage}
+
+\begin{titlepage}
+    \begin{center}
+
+        \singlespacing
+
+        \vspace*{25mm}
+        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
+        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
+        \vspace*{4\baselineskip}
+        Graduate School of Economics and Social Sciences\\
+        of\\
+		İhsan Doğramacı Bilkent University\\
+		\vspace*{3\baselineskip}
+        by\\
+       	\vspace*{3\baselineskip}
+        MUSTAFA İLHAN\\
+        \vspace*{4\baselineskip}
+        In Partial Fulfilment of the Requirements for the Degree of\\
+		MASTER FINE OF ARTS\\
+        \vspace{2\baselineskip}
+        in\\
+        \vspace{2\baselineskip}
+        THE DEPARTMENT OF\\
+        COMMUNICATION AND DESIGN\\
+       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
+        ANKARA\\
+        \vspace{\baselineskip}
+        January 2016
 
@@
 
+\addcontentsline{toc}{chapter}{List of Figures}
 \listoffigures
@@
 \include{chapter5}
+
+\addcontentsline{toc}{chapter}{Bibliography}
 \bibliographystyle{apacite}

### 2015-12-16 main.tex
Thesis format edits
Former-commit-id: d1dea8cb723a1b15083a10b05c3c9849cab174b9

@@
 \usepackage{graphicx}
-%\graphicspath{ {graphics/} }
 \usepackage{float}
@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage{afterpage}
+\usepackage[doublespacing]{setspace}
+\usepackage{tocloft}
 
-%\usepackage{chngcntr}
-%\counterwithout{figure}{chapter}
-
-%\usepackage{setspace}
-%\doublespacing
-
-\usepackage[doublespacing]{setspace}
+\usepackage{chngcntr}
+\counterwithout{figure}{chapter}
+\counterwithout{table}{chapter}
 
@@
 \hypersetup{
-    pdftitle			= {Thesis Draft},
+    pdftitle			= {MFA Thesis},
     pdfauthor			= {Mustafa ilhan},
@@
 
+% RENAMING CHAPTER TITLES
 \addto\captionsenglish{%
@@
 
+%****************************************
+% BEGIN
 \begin{document}
+\pagenumbering{gobble}
 \selectlanguage{english}
 
+%****************************************
+% COVER
 \begin{titlepage}
@@
         Ankara\\
-        \today
+        January 2016
         \vspace{25mm}
@@
 \end{titlepage}
+%........................................
 
-\begin{titlepage}
+%****************************************
+% BLANK PAGE
+\clearpage
+\afterpage{\null\newpage}
+\clearpage
+%........................................
+
+%****************************************
+% DEDICATION
+\newenvironment{dedication}
+  {\clearpage           % we want a new page
+   \thispagestyle{empty}% no header and footer
+   \vspace*{2in}		% some space at the top 
+   \centering
+  }
+  {\par					% end the paragraph
+   \vfill
+   \clearpage           % finish off the page
+  }
+
+\begin{dedication}
+To my family and for those who embrace trash
+\end{dedication}
+%........................................
+
+\pagenumbering{roman}
+
+%****************************************
+% TITLE PAGE
+\clearpage
+\thispagestyle{empty}
+\singlespacing
 	\begin{center}
 
-        \singlespacing
-
         \vspace*{25mm}
-        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
         TRANSFORMING TRASH AS AN ARTISTIC ACT\\
@@
         January 2016
-
 	\end{center}
-\end{titlepage}
-
-\pagenumbering{roman}
+\clearpage
+%........................................
 
 %****************************************
-% ENGLISH
-\begin{abstract}
-Usage of non-art objects in the artworks can be traced back to the beginning of 20th century.
+% APPROVAL PAGE
+\clearpage
+\thispagestyle{empty}
+\singlespacing
+\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\
+
+\noindent---------------------------------\\
+Assist. Prof. Dr. Ersan Ocak\\
+Supervisor\\
+
+\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\
+
+\noindent---------------------------------\\
+Prof. Dr. Mehmet Yılmaz\\
+Examining Commitee Member\\
+
+\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\
+
+\noindent---------------------------------\\
+Instructor Ekin Kılıç\\
+Examining Commitee Member\\
+
+\noindent Approval of the Graduate School of Economics and Social Sciences\\
+
+\noindent---------------------------------\\
+Prof. Dr. Halime Demirkan\\
+Director\\
+
+\clearpage
+%........................................
+
+%****************************************
+% ENGLISH ABSTRACT
+\thispagestyle{plain}
+\addcontentsline{toc}{chapter}{ABSTRACT}
+\doublespacing
+\begin{center}
+	\vspace*{25mm}
+	\MakeUppercase{Abstract}\\
+    \vspace{\baselineskip}
+    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
+    İlhan, Mustafa\\
+    M.F.A., Department of Communication and Design\\
+    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
+    \vspace{\baselineskip}
+    January 2016
+\end{center}
+\singlespacing
+\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century.
 This approach has broken the existing rules and extended the language of art in an unprecedented way.
@@
 
-\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
-\end{abstract}
+\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
+\clearpage
 %........................................
 
+%****************************************
+% TURKISH ABSTRACT
+\thispagestyle{plain}
 \selectlanguage{turkish}
-%****************************************
-% TURKISH
-\begin{abstract}
-\comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
+\addcontentsline{toc}{chapter}{ÖZET}
+\doublespacing
+\begin{center}
+	\vspace*{25mm}
+	\MakeUppercase{Özet}\\
+    \vspace{\baselineskip}
+    \MakeUppercase{Sanatsal Bir Eylem Olarak Çöpü Dönüştürme}\\
+    İlhan, Mustafa\\
+    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
+    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
+    \vspace{\baselineskip}
+    Ocak 2016
+\end{center}
+\singlespacing
+\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
 Ya da en azından proje kapsamında üretilen işin.
@@
 
-\vfill\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
-\end{abstract}
+\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
+\clearpage
 %........................................
+
 \selectlanguage{english}
+
+%****************************************
+% ACKNOWLEDGMENTS
+\thispagestyle{plain}
+\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
+\doublespacing
+\begin{center}
+	\vspace*{25mm}
+	\MakeUppercase{ACKNOWLEDGMENTS}\\
+    \vspace{3\baselineskip}
+\end{center}
+\par First and foremost, I would like to thank to my thesis supervisor Ersan Ocak for his continuous patience, support, encouragement and immense knowledge that he shared with me through the entire process.
+I cannot imagine having a better advisor for both this written thesis and the project I conducted.
+I also would like to thank the rest of my thesis committee; Mehmet Yılmaz and Ekin Kılıç for their motivation and insightful comments.
+\clearpage
+%........................................
+
+%****************************************
+% TABLE OF CONTENTS
+\addcontentsline{toc}{chapter}{Table of Contents}
 
@@
 \setcounter{tocdepth}{3}
+
+\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % dots for chapters
+\renewcommand{\cfttoctitlefont}{\normalfont\MakeUppercase\hfil}
+\renewcommand\cftchapfont{\mdseries}
+\renewcommand\cftchappagefont{\mdseries}
+\renewcommand{\cftchappresnum}{Chapter\space}
+\renewcommand{\cftchapaftersnum}{:}
+
+\setlength{\cftbeforetoctitleskip}{25mm}
+\setlength{\cftaftertoctitleskip}{3\baselineskip}
+\setlength{\cftchapnumwidth}{5em}
+%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}
+
+\begin{singlespace}
 \tableofcontents
+\end{singlespace}
+\clearpage
+%........................................
 
+%****************************************
+% LIST OF FIGURES
 \addcontentsline{toc}{chapter}{List of Figures}
+
+\renewcommand{\cftloftitlefont}{\normalfont\MakeUppercase\hfil}
+\renewcommand{\cftfigaftersnum}{.}
+
+\setlength{\cftbeforeloftitleskip}{25mm}
+\setlength{\cftafterloftitleskip}{3\baselineskip}
+
+\begin{singlespace}
 \listoffigures
+\end{singlespace}
+\clearpage
 %{%
@@
 %}
+%........................................
 
+%****************************************
+% LIST OF FIGURES
+%\addcontentsline{toc}{chapter}{List of Tables}
 %\listoftables
-\listoftodos
+%........................................
+
+%\listoftodos
 
 \pagenumbering{arabic}
+
+%****************************************
+% CHAPTERS
 \include{chapter1_reduced}
@@
 \include{chapter5}
+%........................................
 
+%****************************************
+% BIBLIOGRAPHY
 \addcontentsline{toc}{chapter}{Bibliography}
 \bibliographystyle{apacite}
+\begin{singlespace}
+\setlength{\bibsep}{2\itemsep}
 \bibliography{literature}
+\end{singlespace}
+\clearpage
+%........................................
+
+%****************************************
+% APENDICES
 \begin{appendices}
@@
 \end{appendices}
+%........................................
 

### 2015-12-29 chapter3_reduced.tex
Artworks
Former-commit-id: 1d407fb6662feff21c99012d4101d152fa73dcd2

@@
 
-How and why does trash draw attention of artists?
-In this chapter how artist approached to the trash and their techniques are discussed in the context of art.
-(Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?).
-How does it turn to medium?
+In this chapter, questioned the purpose and meaning of using trash as a medium in the artworks.
+The reasons and motivations of artists who use trash are analyzed.
+The artist uses discarded items in their work is analyzed in the light of arguments discussed in the previous chapter.
+Questioned that why artists select to use society's debris rather than fresh items.
+Researched the place of trash in the world of art by looking at different methods and approaches.
+Started from masterpieces and founding works.
+Continued with recent examples of artworks.
+
+% Çöpün sanatta kullanılmasının temelleri arastirilmakta.
+
+% Ben bölümde aslında çöpün sanatta nasıl yer aldığına bakıyor olacağım. İlk kim kullanmış nasıl kullanmış. Sonrasında hangi anlamlarda kullanılmış.
+
+Firstly looked at how artist started using objects that are not produced by artist and with the purpose of making art.
+Their works are notable and founding works that open new dimensions to reconsider objects and their meaning.
+Further, they extended the ways of art making and the language of art.
+Therefore, it is important to analyze Their intent and methods are analyzed (how?).
+In other words, looked at the foundation of using non-art objects in the art making.
+First examples are analyzed and how it evolved over time is explored.
+Questioned that how they affected successor artist.
+
+Secondly looked at the some examples of contemporary works (or works from recent history). In particular, capture the current approaches on trash. Several methods and genres are explored.
+
+Lastly focused on the inspiring documentary of Agnes Varda, The Gleaners and I which provides a general picture of the subject.
 
@@
 \section{Root in the Art History}
-Using trashed objects in making of art can be examined with the enterance of non-art objects to art\todo{sadece bu yeterli olmayabilir}.
-In other words, using objects in artworks beyond their intended purpose or intended meaning and function.
-Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together.
-(How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
-However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso.
-One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting.
+Using trashed objects in making art can be examined with the entrance of non-art objects into the art.
+In other words, using objects in different scope beyond their intended purpose or intended meaning and function.
+Developing artworks not only painting but also using paper and other stuff by pasting (or juxtaposing) them together.
+(How using non-art objects affected art?
+Fragments) Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
+However, it is not discussed in the context of fine art and not accepted method for art making.
+
+From the beginning of 20th-century non-art, objects draw the attention of the artist.
+Development of art in this century evolved through this non-art objects (or these objects play significant role development of art trough time).
+They bring new dimension (or perception) to consider objects.
+Usage of these objects dramatically changed the way people look at art.
+In short, they introduced a new way of making art.
+
+One of the remarkable change in the 20th-century art is the using unconventional materials in the making of paintings and sculptures, rather than the original (pure, fresh) materials produced with the purpose of art.
+These objects are not normally considered as art, often because they already have a non-art function.
+Possibly they are part of different disciplines and markets.
+Their place in the society and people's mind commonly have a different meaning.
+Beyond them, artists started to use them for their own purposes.
+Objects gain different meanings and usages with the hands of artists.
+(It is explained in the previous chapter that objects are not static and absolute.
+Objects can be used for new purposes even if they lost their meaning and value in the conventional system.)
+
+They questioned the way of traditional (conventional) way of art making in every dimension.
+Their approach out of the previous methods.
+They are looking for the beyond of painting.
+With using different objects they break the pureness of artwork.
+It is not pure anymore, fragmented.
+Boundaries are pushed.
+Using non-art objects in the production of art challenges existing conventions of painting.
+
+Using non-art object can be considered as moving away from the purification of art \todo{ref req}.
+It is a composition of different fragments and pieces.
+Rather than the traditional way of painting on canvas they composed their work with the combination of various objects from different context.
+With this approach works can be examined in multi-dimensional context.
+
+% (Peki neden sanatçılar bunu tercih ettiler, buhran neydi?
+Azıcık öncesindeki kıpırdanmaları anlatmak gerekli.
+Bu apayrı ve uzun bir konu.
+Ama değişmeler yavaş yavaş gelmeye başlamıştı.
+Neye karşıydı, ne getirdi.
+Sanatın var olan kalıplarını yıkıp yerine ne koydu?
+ronesanstan beri gercekligin temsili uzerine kurulan sanat ve estetik anlayis coktan sorgulanmaya baslamistir izlenimcilerle birlikte.)
+
+Before the 20th-century, artists started to inquiry the existing methods and themes of previous periods.
+Modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
+Previously paintings are based on linear perspective and realistic style.
+Themes are often composed of religious and mythical narratives \todo{MOMA ref}.
+After the second half of the 19th-century, they started to abandon these themes and painting methods.
+For instance, in the works of impressionist paint brushstrokes can be easily identified, and themes are composed of everyday scenes.
+With Cezanne, the linear perspective started to question and later reached to its peak point with cubism.
+Cubism is developed with the collaboration of the Picasso and Braque.
+Besides, these two artists experimented non-traditional materials in their works for the first time in the scope of fine art.
+They continuously produced works with using different objects.
+They support each others art.
+They showed that an endless potential lay there.
+They collaborated with each other on the development of cubism and collage.
+
+One of the keys to understanding the importance of Cubism, of Picasso and Braque, is to consider their actions and how unusual they were for the time.
+When Braque, and then Picasso placed industrially-produced objects ("low" commercial culture) into the realm of fine art ("high" culture) they acted as artistic iconoclasts (icon=image/clast=destroyer).
+\todo{ref}
+
+% Sanat disi objenin kullanilmasi aslinda sanatin saflasmasininda disinda yer almaktadir.
+Saf oz bir sekilde kurulmasindan ziyade farkli seylerin parcalarin bir araya gelmesiyle birlikte kullanilmasi.
+Tabuların yıkılması.
+Sınırlarının aşılması.
+geleneksel anlamda tuvalin uzerine boya surmekten ziyade farkli teknikler denenmeye baslanmistir.
+20yuzyilda geleneksel sanat tum boyutlariyla yeniden ele alinmistir.
+Resmin konusu, sergileme bicimleri, yenikikler gostermistir.
+
+Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
+In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
+Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
+
+Collage was a major turning point in the evolution of Cubism, and therefore a major turning point in the whole evolution of modernist art in this century \cite{greenberg1984collage}.
+
+Similar to the collage, assamblage is produced by the incorporation of three-dimensional elements.
+In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
+William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.
+\todo{ref.}
+
+%Who invented collage--Braque or Picasso--and when is still not settled. because of most of their early works are undated and unsigned. the question of priority is less important rather than
+
+One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting.
 This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture.
-Using non-art objects in the production of art challenges existing conventions of painting.
-% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
-\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
-The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}
+Picasso combined painting with already existing materials.
+He used real objects to represent instead of painting.
+As mentioned in the name of the work Picasso give clues of the parts of it.
+For instance the oval canvas\todo{canvas or oilcloth?} and the rope around it represent the table.
+Pasted chair caning signifies the chair within the table.
+On the table folded paper shadow represent newspaper.
+Further there is a cut out lemon painted onto the table.
+\paraphrase{The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.
+This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.}
+
+% Greenberg
+% The abiding effect is of a constant shuttling between surface and depth, in which the depicted flatness is "infected" by the undepicted.
+Rather than being deceived, the eye is puzzled; instead of seeing objects in space, it sees nothing more than--a picture.
+
+% \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}
 
@@
 
-\textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art.
-The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+Moreover, they questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the rarefied, contemplative realm of artistic creation.
+Of equal importance, their work highlighted and separated the role of technical skill from art-making.
+Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of high and low, of unique and mass-produced objects.
+They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
-  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
-  \label{fig:Duchamp_BicycleWheel}
-\end{figure}
+% http://www.nybooks.com/articles/2010/12/09/artist-everything/
+% http://www.artchive.com/artchive/S/schwitters.html
+After Picasso and Baraque, many artists applied collage and assamblage techniques to their works.
+Dada artist Kurt Schwitters is one of the productive artists of them.
+In 1918 created his own form of Dada in Hanover called 'Merz', using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions.
+The nonsense word 'Merz' is generated from the name of the name of a bank: the Kommerz und Privatbank.
+Merz was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt Merz Schwitters or simply Merz.
+
+"The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
+In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism." (Gwendolyn Webster)\todo{ref}
+
+% http://www.artchive.com/artchive/S/schwitters.html
+Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.\todo{ref}
+
+Merzbau is most important ones.
+In 1937 after his work had been included in the Degenerate Art Exhibition he fled Germany for Norway.
+There he created a second Merzbau.
+In 1940 he found refuge in England where he started a third Merzbau at Ambleside in the Lake District.
+The first Merzbau was destroyed in the Second World War, the second by fire in 1951 and the third was left unfinished at his death in 1947.
+It is now preserved in the Hatton Gallery of the University of Newcastle upon Tyne.
+
+% Yaptığı işte ısrarcı ve üretken. Sürekli inşa ettiği yapılar merzbaular aslında bitmiş bir izlenimi vermiyor. sürekli büyüyor değişiyor. sabit ve bitmiş bir yapısı bulunmamakta.
 
@@
 
-% TODO paraphrase
-\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+\paraphrase{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)} \todo{ref.}
+
+Recycled object contains within it a reference to two or more distinct times.
+Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them".
+\todo{ref}
+
+% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
+It is claimed that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
+
+Collages and assemblages can be composed of all types of objects such as trash and found object.
+The notion of found object is researched by the many scholars \todo{ref.}, but usage in the art has gained new dimensions with the Duchamp's concept of readymade.
+Industrially manufactured or anything found  anymore can found a place in the art.
+The most famous example is Fountain (1917) (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+Before that first one is Bicycle Wheel.
+He mounted the bicycle wheel upside down onto a stool.
+% http://www.moma.org/learn/moma_learning/marcel-duchamp-bicycle-wheel-new-york-1951-third-version-after-lost-original-of-1913
+When Bicycle Wheel was first displayed, Duchamp encouraged viewers to spin the wheel.
+(Participation of the audience) Although he claimed to select objects for his readymades without regard to beauty, he said, “To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.”
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
+  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
+  \label{fig:Duchamp_BicycleWheel}
+\end{figure}
+
+% TODO Bunu sadece referans olarak kullanabilirsin, çünkü zaten çok fazla tekrar var.
+%\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
 Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
@@
 
-%
-%
-\summary{Collage}
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
-\todo{read greenberg1984collage}
-
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\summary{Hybridity} 
-\paraphrase{Recycled object contains within it a reference to two or more distinct times.
-Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)} \todo{ref.}
-
-% TODO MOVE
+% TODO rubbish theoryinin başına konulabilir, referans olarak kullanılabilir.
 % Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
@@
 
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
-It is claimed that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
-
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\paraphrase{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
-Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
-(Jacknis 1992)} \todo{ref.}
-
 % TODO MOVE TO COMMON APPROACH
 %\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
-
-%
-%
-\summary{Assemblage} 
-Assemblage work produced by the incorporation of everyday objects into a composition.
-It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional.
-Diverse range of things can be used production of work.
-In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
-William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.
-\todo{Joseph Cornell, assemblage artist.}
-
-%
-%
-\summary{Bricolage} 
-Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
-\paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
-
-\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
-
-%\begin{quote}
-%[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
-His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
-%\end{quote}
-
-%\begin{quote}
-%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
-There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-%\end{quote}
-
-%\begin{quote}
-%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
-In this sense the engineer is a myth.
-A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
-The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-%\end{quote}
-
-%[TODO use this ref]\cite{strasser1999waste}
 
@@
 
-% TODO new comer
+% TODO will not be used. just for rerefence
 % Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
@@
 
-% TODO new comer
+% TODO will not be used. just for reference
 % Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
@@
 
-%Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
+\paraphrase{Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
@@
 He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).} \todo{parap.
+ref.}
+
+\paraphrase{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
+Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}
 
@@
 
-% Amelie olabilir.
-Orada fotoğraf toplayan çocuk olabilir.
-Onları itinayla toplayan bir adam.
-Tren garındaki fotoğraf kulubesi.
-Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
-Bir birinden farklı bir sürü insan.
-Filmde neden böyle bir eyleme yer veriliyor?
-Film fotoğraflar üzerinden defter üzerinden ilerliyor.
-Onun çevresinden bir hikaye kurgulanıyor.
-İnsanların artıklarını topluyor.
-Onların değer vermedikleri şeyleri topluyor.
-Bunlar baya baya aslında o insanlar.
-Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
-Çok iyi bir örnek mi bilmiyorum.
-Burada niyet nedir ki?
-Ben buna şöyle bir okuma getireceğim diyebilirim.
-Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
-Bu arada bu fotoğraf toplama işi ilk değil.
-Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
-Ama benim işime yarayan kısmı ne?
-Neden o fotoğrafları ya da bunun filmini yapıyor.
-Aslında puzzlelar üretiyor.
-Belirli tekrar olacaktır.
-insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
-Tekrar bir kitap haline geliyor.
-Tanınmayan insanların fotoğrafları.
-Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
-Aslında tam da amelie bunu yapmıyor mu?
-Hikayeler üretiyor bu fotoğraflardan.
-Yeni karşılaşmalar üretmesi.
-Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
-Bin bir türlü şey vardır aralarında.
-Nereye yerleşmeli.
-Başkasının çöpünü toplama.
-O dönemin o eşyasını arşivini tutma.
-ve herkes sunuluyor sonrasında bu.
-
-%
-%
-%[Ready-Mades]
-
 %
@@
 \section{Examples from contemporary artists}
-Beyond historical development of art with non-art objects and trash, for contemporary artist what it means has slight differences.
-Firstly their purpose do not want to express the language of art by using trash and non-art objects because they are already done and the way of making art dramatically changed.
-Therefore what are their purpose and how they can be viewed?
+In the light of discussions at previous section, some of the works (or current strategies and approaches ) of artist are analyzed. First one is related with found objects.
 
-% not easily understandable with the entering non-art objects in art.
-artist are responding the current societies habits in a different ways.
-what they are doing here is to see other possibilities and show actually what is going on.
-what does it mean all of these things.
+% Neden bu işler, neden bu sıra?
 
-% FROM ReVista
-%\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} 
-\paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
+% Neden çöpü kullanıyorlar.
+Bunu belirmek gerekli.
+İlki sanata farklı bir obje sokarak saflığını bozma, hazır yapım ile geleneksel yöntemlere karşı çıkış, fikrin ön plana çıkması.
+Visual uniqueness, aesthetics dimension, Economic reasons
 
-% FROM Paola Ibarra ReVista
-\paraphrase{Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere.
-Is there a limit to recycling and representation?
-Or is there a point at which waste cannot become art (or anything else)?}
+Photobooths are machines that place crowded places and with affordable cost people can get their photos.
+It is a pheonema that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as a two volume.
 
-% TODO Naive debate??
-\comment{All that can be seen as naive act because of little impact and outside of the system(which system?).
-As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill.
-However this very argumentative that having no impact or little impact.
-It might be true that this practices solve all problems of landfill or etc.
-But changes individuals and communities life.
-It recreate and rebuilds the community.
-Even if it is one simple object worth look and see the opportunities of it.}
+In the French film Amélie\footnote{Original title: Le fabuleux destin d'Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris.
+He collects them and glue them together in a photo album.
+In the film photo booths and found photos are central catalytic.
+Amélie falls in love with him when she realize him searching for found photos.
+After his photo album passed to Amélie, she looks every page of photo album again and again.
+Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away.
+The important part of the film it generates images of a man who scanvage the photos of another people.
+There are a lot of artist who collects discarded items but their process is not well documented.
+Therefore we are not aware of the artist process.
 
-%
-% Tags: "dikkate alınmayanı tekrar ele alıyor". Mekan: sokaklar, şehir, kamusal alan. Traces of our life.
-\textbf{Road Kill.} \paraphrase{Filomena Cruz creates photographic series named as \quotes{Road Kill} painstakingly captures tiny \quotes{trash corpses} on the pavement.
-It is that particular type of trash meet in the public places.
-Trash left behind, trash on the sidewalk, squished, squashed, and weathered.
-Filomena Cruz sees trash that people don’t want to see.
-A piece of chewing gum with an \quotes{engraved} leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of \quotes{worthlessness} suddenly becoming meaningful (and moving).
-For one thing, trash corpses faithfully record city life.} Uses public spaces and takes photos of streets and roads in unfamiliar fashion, focussing onto trash.
-Captures the trace of city life from trash.
-She does not collect the trash physically, collects the images of them.
-They are still there and continously changing.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
+  \caption{Still image from Amélie}
+  \label{fig:Amelie}
+\end{figure}
+
+Prior to film Amélie, British artist Dick Jewell published a book in title of "Found Photos" in 1977.
+It is a collection of photobooth images that had been thrown away or torn up by the people in the photos.
+Ian Walker comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine.
+They are scavenged by the artist from the photo booths of London.
+The reasons of why photos are rejected vary including technical problems like flash or posing time.
+On the other hand, some of them are very good condition, and it is a mystery that why they are rejected.
+Walker explains that the \todo{block qoute} "gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving." Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them.
+"Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ‘readymades’." His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin.
+Badger describes Found Photos as ‘both a conceptual artwork and a sociological footnote’.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
+  \caption{Dick Jewell}
+  \label{fig:DickJewell_FoundPhotos}
+\end{figure}
+
+On the other side for another artist photographs serve a function to record his daily trash.
+Tim Gaudreau photographed every object that he threw away for one year.
+At the end around five thousand images are covered all the gallery and opened to visitors.
+He notes that it just started as a documentation of his discards, but later it became (part of his life and) an obsession that he can not able to easily quit off.
+He says that "this collection of images intimately displays what I do, what I consume.
+It reveals me." Like in the case of Tracey Emin trash turns to a medium that is used to express oneself.
+People are not only composed of the listed items in the CVs like in the film Fight Club Tyler Durden draws attention to the narrator by saying: "You are not your bank account".
+It is an effective way of looking things left behind rather that things put forward.
+Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
+  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
+  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+\end{figure}
+
+Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement.
+In her photographic series "Road Kill", she captures tiny "trash corpses" that are generally ignored and out of sight.
+In other words, the skin of city revealed through her photos in micro scale.
+On the skin of city there are lots of trash including "a piece of chewing gum with an "engraved" leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful" as looked through the window of they capture the city life and skin of the city that we touched.
+She shows us tiny details of huge cities.
+(Somehow these trashes for all effort succeeded to stay in the towns.) These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.
 
@@
 
-%
-%
-%\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.
-
-%
-%
-\textbf{Pictures of Garbage.} Vic Muniz creates monumental portraits from trash in Jardim Gramacho, an open-air dump just outside Rio, with the help of \textit{catadores} in the documentary film (Waste Land, 2010) Waste Land, directed by Lucy Walker.
-Called “Pictures of Garbage,” they were created by Mr.
-Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America.
-(Important point is here collaboration with the pickers.
-Listening their stories and capturing their portraits.
-It methods similar to the mosaics, every type of discard collected from dump used his photos.) Trash and people who live there is the subject of his portraits.
-None of the trash is belong to that people.
-However again these trash express them perfectly because they make a life from trash.
-Their home is dump.
+In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump.
+He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millons of people.
+Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump.
+He selects unusual materials and people for potraits rather than the powerful and notable people as commonly encountered at Renaissance.
+To create portraits of \textit{catadores} there is any other material than trash because of they are already build up their life in trash of city.
+[Also these image are sold an auction and earned money donated to the \textit{catadores}.
+The images of trash moved to beloved places such as homes and museums.
+As stated in the rubbish theory they transformed to a durable object.]
 
@@
 
-%
-%
-\textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their \quotes{Recycled Orchestra}.
+Not only monumental portraits extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez.
+Favio Chávez is a music teacher, and Nicolás Gómez is a garbage picker.
+They live in Cateura at Paraguay.
+It is a one of the poorest villages where people live among the sea of garbage.
+"A violin is worth more than a house here," says Favio Chavez in documentary film.
+The orchestra's director and founder.
+Favio Chavez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez.
+Players of the orchestra are compiled from the children who are hopeless for their future.
+In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
+They are given birth to an orchestra that plays the masterpieces of classical music composed by Mozart, Beethoven, and Vivaldi.
+Trash turned to treasure and totally ironic that a signifiers of high culture like classical music can be even played with imperfect instruments.
+For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music.
+(To enjoy and play such music requires economic wealth and it is not possible for everyone.) What they create is actually not expected from them, and their success is not limited with their location.
+They have given concerts around the world.
 
-Cateura, Paraguay is a small city that has grown atop a massive dump.
-It is regarded as one of the poorest slums in Latin America, a village where people live among a sea of garbage.
-Incredibly, the landfill itself is the primary form of subsistence for many residents, who pick through waste for items that can be used or sold.
-Prospects for most of the children born in Cateura is bleak as gangs and drugs await many of them.
-But then one day, something amazing happened.
-A garbage picker named Nicolás Gómez (known as “Cola”) found a piece of trash that resembled a violin and brought it to musician Favio Chávez.
-Using other objects collected from the dump, the pair constructed a functional violin in a place where a real violin is worth more a house.
-Using items gleaned completely from the dump, the pair then built a cello, a flute, a drum, and suddenly had a wild idea: could a children’s orchestra be born in one of the most depressed areas in the world?
-As you can guess, the answer was yes.
-
-To view scenes from the landfill slum of Cateura in Paraguay is to look into the depths of extreme poverty.
-But within the contents of the landfill are glimmers of hope in the form of cardboard, utensils and other discarded materials that can be crafted into imperfect but usable musical instruments.
-These makeshift violins, flutes and cellos, combined with instruction from a local music teacher, have given birth to the Recycled Orchestra of Cateura.
-Through the music of Mozart, Beethoven and Vivaldi, this orchestra allows the young musicians to transcend their identity as children of poverty.
-
-"A violin is worth more than a house here," says Favio Chavez, the orchestra's director and founder.
-In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
-"My life would be worthless without music." says one girl in pigtails.
-A young man named Juan Manuel Chavez, nicknamed Bebi, has a cello fashioned out of an oil can and old cooking tools.
-For the camera, he plays the Prelude to Bach's Cello Suite No.
-1 — beautifully.
-
-"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer.
+%"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer.
 "Well, we shouldn't throw away people either." \quotes{The world send us garbage.
@@
 
-[Critics] This project can be seen as a bricolage practice.
-They build their musical instruments from what is available around.
-What they create is actually not expected thing from trash.
-This work also can be seen as an example of resistence because playing western classical music with their instruments is very costly.
-To enjoy and play such a music requires economical wealth and it is not possible for everyone.
-They create their opportunites or turn trash to oppornutiy for them.
-Here economical restirictions result in great production boost with creativity.
-After seeing this instruments and listen their music changes peoples mind to the perception of the classical music and the intruments.
-The original items are well designed and perfect.
-They have identical outlook(or view).
-Not only trash is here transformed, but also perception to the trash and instruments are transformed here.
-After that point trash that you know is no longer same trash.
-At the same time with music lives of children are changed.
-They work on unimaginable thing for them.
-Quality of their music is different than the original one.
-
-\comment{This is a proff of the transformation of the original concept.}
-
-% TODO new comer.
-[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse.
-but even if they have no economical struggle, they continue recycle.
-what is the reason of it?} Recycling as an economic strategy of survival in developing countries throughout the world.
-creative production that is motivated, primarily, by adverse conditions of economic necessity.
-(lanfill orchestra here.
-bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised.
-(p25)
-
-% Dönüşümün aslında burada görebiliyorsun. Yav bu sanat mı peki? Sadece maddelerin dönüşmesi değil onlarla birlikte insanlarında dönüştüğünü görebiliyorsun burada. 
-% Beni bu projede etkileyen en önemli şeyler: ilk olarak oradaki insanların hayatlarını değiştirmesi, hiç hayal edemiyecekleri bir noktaya ulaşmaları, tümünüde kendi emek ve yetenekleriyle başarmaları.
-yokluk içinden bir şeyler üretmeleri.
-Her ne kadar üretilen müzik aletleri mükemmel olmasalarda onlar için bulunmayacak bir nimet.
-Üretilen ürünün kalitesi gerçekten de endüstriyel standartların altında.
-Müziğin kalitesi diğer kadar olmasa bile farklı bir yaklaşım sunuyor olması önemli.
-Nasıl oluyor da bu aletten bu ses çıkıyor.
-Amatör ruhun getirdiği bambaşka bir algı var.
-Müziğin ötesi, düşündürdüğü bambaşka şeyler var, olaya yeni bir boyut getiriyor.
-Başka bir alanla diğerinin buluştuğunun bir göstergesi.
-
-\summary{Indigenization} 
-The indigenization of western objects.
-(sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"?
-Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves.
-They do not necessarily despise our commodities.
-But they are selective in their demands and transformative of their uses of such things.
-(sahlins, 13)"
+% Resistance to all hard conditions
 
@@
 
-% TODO: http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
-% http://www.eloisacartonera.com.ar/ENGversion.html
-\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers.
-\quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
+As noted that recycling as an economic strategy of survival in developing countries throughout the world.
+Creative production that is motivated, primarily, by adverse conditions of economic necessity.
+Economic survival and adaptation are influential factors for both the makers, who build an informal business on the making and selling of recycled goods and the local consumers, for whom the market for affordable, utilitarian goods is devised.
+(p25)
 
-It reminds me that litreary is also a combination of reused thing. Because to create meanings we reuse words and idioms again and again with different combination.
+They build their musical instruments from what is available around.
+This project can be seen as a bricolage practice.
+Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
+\paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
+\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
 
-\begin{figure}[ht]
-  \centering
-  \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
-  \caption{Books covered by Eloisa Cartonera}
-  \label{fig:EloisaCartonera_Books}
-\end{figure}
+\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
 
-%
-%
-\textbf{American Beauty.} The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air.
-It is hard to think of plastic bags as things of beauty.
-\todo{Bunun hakkında daha fazla bilgiye ihtiyaç var.}
+\begin{quote}
+[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
+His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
+\end{quote}
 
-%
-% From http://www.thisiscolossal.com/2014/06/historical-fine-oil-portraits-on-crumpled-trash-by-kim-alsbrooks/, http://www.thisiscolossal.com/2015/05/new-historical-portraits-on-flattened-cans-by-kim-alsbrooks/, http://kimalsbrookswhitetrash.blogspot.com.tr/
-\textbf{Paintings on beer can.} Kim Alsbrooks, historical oil portraits on flattened beers cans and fast food containers.
-\quotes{The White Trash Series was developed while living in the South out of frustration with some of the prevailing ideologies, in particular, class distinction.
-This ideology seems to be based on a combination of myth, biased history and a bizarre sentimentality about old wars and social structures.
-With the juxtaposition of the portraits from museums, once painted on ivory, now on flattened trash like beer cans and fast food containers, the artist sets out to even the playing field, challenging the perception of the social elite in today’s society.} \quotes{On technique: The trash is found flat, on the street.
-One cannot flatten the trash.
-It just doesn't work.
-It must be found so that there are no wrinkles in the middle and the graphic should be well centered.
-Then the portraits are found that are complimentary to the particular trash.
-Generally I depict miniature portraits from the watercolor on ivory era (17th-18th century more or less).
-The trash is gessoed in the oval shape, image drawn in graphite, painted in oils and varnished.} I need to mention that this images are very subversing to the perception of us about these images.
-It is unexpected way of presenting images.
-There is a relationship with the image and painting.
-At least this work questioned this relation.
-With tihs work one can ask that with the painting trashed can become valueable thing or with this can this paintiing became valueless.
-Artsist combines two thing that can be never thought together.
-New combination, new meaning.
+%\begin{quote}
+%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
+There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
+%\end{quote}
+
+%\begin{quote}
+%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
+In this sense the engineer is a myth.
+A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
+The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
+%\end{quote}
+
+% TODO Bunu bitirirken de bir şeyler demek gerekli.
+
+In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical potraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects.
+The people in the figure X is General Jefferson C.
+Davis who was an officer at United States Army in 19th-century.
+Selected persons can be viewed as a member of the higher or ruling class of society.
+Therefore Kim Alsbrooks, painter of these works, might thought that to make trash is more valuable, their face will be good.
+Or the vice versa.
+She may use trash to provocate social elite of that time.
 
@@
 
-%
-% ARTWORK http://timgaudreau.com/2012/trash/trash.html
-[Self-Portrait as Revealed by Trash] Even if most of people pay little attention to the trash, everybody do not.
-An artist takes photos of his every trash, like a popular habit that is taking photos of face everyday.
-He focuses on the thing that paid little attention.
-At the end he exhibits all the photos by covering all the walls of room.
-It can seen as record of his activities, record of commodities.
-Most of them we are not aware of them.
-Draw the attention of is being thrown away and every time and everywhere.
-They are too much and can only fit covering all the walls.
-\todo[inline]{Tim Gaudreau Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
-These collections of grids represent my first experiments with using those images.
-This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
-
-% act of taking a picture of every single item that I threw out became something else that I can't quite put my finger on.
-It became more than a chore; it became part of my life (albeit, a bit awkward on first dates).
-
-%  Did this project change your behavior?
-Yes!
-At the beginning of this project, on an average day, I would consume: (1) cup of iced coffee, (2) bottles of water, (1) bottle of iced tea and (1) bottle of a sports drink.
-After photographing so many plastic bottles, there came a point when I couldn't bear to admit throwing out another one.
-As I came to understand the flow of my plastic trash, I started by cutting back everywhere I could.
-I stopped using plastic and foil wrap in my kitchen; I started mixing my own iced tea from concentrate; Drinking water came from gallon jugs rather than pint bottles, then ultimately just tap water.
-Then I switched my morning coffee to a rather beautiful reusable ceramic mug and to mixing my own sports drink from powder.
+Not all the time and every artist turn trash into different objects sometimes they trash them.
+Michael Landy's Art Bin is one of them.
+It is a room size transparent bin placed inside of the art gallery.
+He invites people to bring their own artworks of failed attempts.
+Some of the notable contemporary artists such as Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner participated in by throwing their sculptures, paintings, and prints into the Art Bin.
+People publicly toss their work from a high platform, and all of them can be seen outside of the transparent walls.
+He listens to the story and the failure of the artworks from their creator, and it is not allowed to throw others work.
+At one side he criticizes the idea of not aware of that artist also have lots of failures.
+People only can see the final work in the galleries and museums.
+In this work he break-ups this notion that encouraging the artist reveals their failures to the public.
+Like his words, it is “a monument to creative failure”.
+(According to this approach one can extract that failures belong to the trash bin.
+However, there must be other alternatives that to demystify the practice of the artist.) On the other side, there is a provocative approach to the art and art objects by saying that "Nothing is too good for the art bin." There is no limitation of throwing away even if art.
 
@@
   \centering
-  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
-  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
-  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+  \includegraphics[width=0.37\textwidth]{graphics/MichaelLandy_ArtBin.jpg}
+  \caption{Michael Landy, Art Bin}
+  \label{fig:MichaelLandy_ArtBin}
 \end{figure}
 
-[Chrish Jordan Break Down inventory] \paraphrase{Not all artist transform trash although some deconstruct them.
+Not all artist transform trash although some deconstruct them.
 Michael Landy is one of them.
-Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Michael Landy's Break Down Inventory is a two-week show (display) of destruction process of his all possessions on a dissemble line with the help of 10 workers.
 Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
-Reveal all his possessions.
-and loosing them while you are alive.
-Turning them to rubbish making them unusable.
-breaking down the all the meaning.
-breaking down the connections.} It can be an example of downcycling process.
+Reveal all his possessions and deconstruct of them while he is alive.
+He turns them to rubbish and makes them unusable.
+Breaking down the all the meaning.
+Breaking down the connections.
+It can be an example of a downcycling process.
 It is preferred to decompose all the complex link and relationships between the objects.
-They are not just ordinary things they are possessions of artist.
+They are not just ordinary things they are possessions of the artist.
 Break Down 2001, in which he systematically destroyed all his personal possessions.
-His work examines what we value and what we discard, consumerism and waste, and human labour and its worth.
+His work examines what we value and what we discard, consumerism and waste, and human labor and its worth.
 It happens in public space.
 People can see the process.
-This process last 2 weeks.
-Places where people buy things actually.
-
-%\comment{Tüm sahip olduklarını yaşarken kendi isteği ile yok ediyor. Bu hepimizin paylaştığı bir şey.}
+This process lasts two weeks at a place where people buy goods.
 
@@
 
-%\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure.
-Garbage dump or gold mine?
-The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource.
-Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear.
-In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization.
-For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden.
-In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.
+% TODO kendi işime taşıyacağım.
+% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa, http://www.eloisacartonera.com.ar/ENGversion.html
+%\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers.
+\quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets.
+Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
 
-%Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses.
-Pavilions, villages of huts and even whole houses are appearing over night.
-Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources.
-In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation.
-Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning.
-Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible.
-Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.
+%It reminds me that litreary is also a combination of reused thing. Because to create meanings we reuse words and idioms again and again with different combination.
 
-% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
-%Public space is under siege.
-The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities.
-In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation.
-Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.
+%\begin{figure}[ht]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
+%  \caption{Books covered by Eloisa Cartonera}
+%  \label{fig:EloisaCartonera_Books}
+%\end{figure}
 
-%Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces.
-Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures.
-The work will be an act of resistance to occupy and reclaim a space and change its meaning.
-At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.
+The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air yet people find it hard to think of plastic bags as things of beauty.
+But as a product -- as something created and then unleashed to become seamlessly integrated into the lives of millions of people around the world -- there is a strange allure to them, just as a pathologist can admire the structure of a particularly virulent and contagious virus.
 
-%For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.
-
-%Public space and transformed materials.
-
-% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
-%Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically.
-The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.
-
-%They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories.
-In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces.
-And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.
-
-%
-% http://www.tate.org.uk/art/artworks/nelson-the-coral-reef-t12859/text-summary
-% \textbf{The Coral Reef} Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London.
-The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says.
-(It is very corralate between Ages Varda's work.
-She shows at the side of human practice, Nelson looks the topic from object side.)
-
-% FROM Paola Ibarra, ReVista
-% Forever; Blue Yonder by artist Kyle Huffman
-% Too Too---Much Much by Thomas Hirschhorn
-% Autoconstrucción by Abraham Cruzvillegas
-
-% FROM Burning Messages BY MICHAEL WELLEN, ReVista
-% Antonio Berni
-
-% Bu adamın ilkeleri var. Benim de var aslında.
-% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
-% https://www.youtube.com/watch?v=v6IoEF_Tsrw
-% Nick Quijano has some rules to create assemblages.
-\quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor.
-As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object.
-Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.
-
-% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
-% Haiti.
-When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage.
-It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city.
-When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No.
-When you have clean streets you have good health, and that is the most important thing.} (This is very strange.
-It shows that working with trash and being clean healthy is not a contradiction.
-Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.
-
-% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
-% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy.
-In these films, trash is not the end of a process of consumption but the beginning of a cycle of production.
-These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development.
-The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city.
-Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art.
-It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.
-
-% \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price.
-"Free is certainly great, and that was a driving force for me early on in my career," he said.
-
-% \textbf{SOUP} Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition.
-The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.
-
-% http://www.keaggy.com/chairs/sad/12/
-% \textbf{Sad chair.} Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
-
-% \textbf{ArtBin} Chris Jordan [Trashing Things]
-%****************************************
-% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
-
-% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
-%........................................
-
-% \textbf{Squeezing}
-
-%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
-% \textbf{Found in Nature} Barry Rosenthal
-
-% \textbf{Compression} César Baldaccini [Trashing Things]
-
-% \textbf{Found Photos}
+Examples are not limited with these. Even if \paraphrase{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
 
@@
 \section{The case of \quotes{The Gleaners and I}}
-The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning.
-The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras.
-This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.
+"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000.
+The film features various kinds of gleaning.
+According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers".
+Varda searches for the historical and current practices of gleaning in rural and urban areas of France.
+Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest.
+By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles.
+In particularly she curiously focuses on the (un)familiar people who glean leftover of society.
+Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her filmmaking practice.
+Some people glean crops; the others discarded food, and Varda gleans images.
 
-It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice.
-Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.
+The film is more than a research and document of the lives of many gleaners.
+It highlights the degree of global consumerism of the modern world and how technological advancements (or industrial (technical, modern) standards) result in waste.
+Varda seeks the several stages of potatoes from producers to consumers.
+As she discovers that supermarkets, buy only potatoes that fit in industrial standards of shape and size.
+So what happens to the others?
+Varda discovers and shares with us the disturbing fact that they are taken back to the field where they came from, by following with the camera the trucks that unload mountains of potatoes.
+As Rosello notes that "The ‘good’ potato is not the edible potato but one that will fit into a plastic container to be displayed on the shelf of a supermarket." Varda records few people who glean the rejected potatoes from the field, and also she joins them by collecting heart shaped potatoes that fascinate her.
+Rosello explains that she is collecting not only refused potatoes but also images that are left behind.
 
-\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France.
-Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest.
-However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way.
-Moreover, Varda includes her actions of collecting images with a video camera as gleaning.
-She is gleaning images.
-The Gleaners and I far more than document the lives of gleaners.
-It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
+  \caption{Still image from The Gleaners and I}
+  \label{fig:AgnesVarda_Potatoes}
+\end{figure}
 
-The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest.
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
-And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).
+The industrial processes have some standards and beyond that standards, there is not a place for anything.
+It clears out (or move away) the rest.
+It can be viewed as the idealization of goods and products (even people).
+At this point, it can be referred back to Žižek's claim that people's false consciousness about balanced and idealized notion of nature.
+It can be understood that this type of clarification of objects may result in this false perception.
+What Varda's finding is an excellent exemplification of what Žižek wants to point out.
 
-Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops.
-There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-Seeing the value in what someone else has defined as trash is an art in itself.
-
-Once as a common practice of gleaning throughout the years has evolved, but not disappeared.
-She keeps light to the modern life gleaners that are not visible every time.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
-In other word we can be subject of the refusal.
-At some point she become the subject of the thing that she track.
-
-There are many aspects of this documentary film.
-First draw attention the practice of gleaning.
-The discarded items that are not fit in the industrial standards because of their shape, color etc.
-Even if these items are discarded and we are not aware of them, there is also another life for them.
-Modern life gleaners feed from them.
-In another words someones trash becomes another trash.
-There are people live the boundaries of consumption societies.
-They create their life from the unwanted items.
-what the society refuses, they find a life or create a life from them.
-Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism.
-(as also Zizek mentions that love is not idealization.
-But the industrial processes has some standards and beyond that standards there is not a place for everyone.
-Life is being lived in the cites is somehow idealized life or tried to be idealized life.
-beyond the border of the urban there is new life generated.
-What is not succeed in the cities succeed outside of it.)
-
-She uses unconsciously recorded pieces in the film.
-\quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film.
+Contrary to the common act of discarding, Varda finds out a creative way to use her unconscious recorded piece that might be deleted by the others.
 It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks.
-She sets this scene to a jazz soundtrack.
-While watching the scene I was certainly confused.
-Why is this in here?
-What does this have to do with gleaning?
-And certainly why did the scene last so long?
-But there was also something lovely about it.
-Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing.
-I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.
-Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+She uses this scene with a jazz soundtrack at background.
+Watching this scene is confusing at first hand regarding context.
+It might be viewed as worthless and recorded by accident.
+One can ask that why is this placed here, what does this have to do with gleaning?
+However, Varda forces us to watch it (wants us to pay attention).
+This scene called "the dance of the lens cap".
+Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
 Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
-Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
+\quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value.
 Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}.
 Things that are often forgotten or discarded can easily be revamped to create something useful to someone.
-The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}
+The scene was revamped using music, and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.
 
-Refused is not only foods and trash.
-there are a lot of things that are pushed outside border of the society.
+\todo{image}
+
+As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
+Making use out of something that has been left behind and labeled as obsolete is not unique to potatoes.
+There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
+More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
+By showing them she shows that once was a common practice of gleaning throughout the years has evolved, but not disappeared.
+She keeps light to the modern life gleaners that are not visible every time.
+One of the is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
+Probably he has all the capabilities that live amoung the other people(???).
+It can seen that from this example, gleaning becomes also a form of resistence to ruling system.
+a way of refusing to be boxed in by conventional expectations
+
+\todo{waste and want rules of eating from garbage.}
+
+She shows that the act of gleaning does not bound to the collecting food and survival reasons.
+Some of them build their own meaning and existig and identity through the collected items.
+One of the examples that she gaves is ghat the man who collects baby dolls and use them in the decoration of his home.
+Every where is filled up with the babydolls even if wall of the garden.
+
+Through the film she experiences the act of gleaning with different people.
+At one side she gleans potatoes in the field and on the other side follows a man with biycle look for the garbages front of the homes.
+By documenting their life in action she also participate them.
+But she bring them her own perception to them.
+For example in the case of potato gleaning she collect the heart shaped ones which are attract attion of her.
+Moreover in the case of night searching, she finds a clock without hand.
+It has fullfiled lits function and leaved away.
+Most important part of clock is missing therefore it is not functioning.
+However for it is a different meaning.
+Not every time people seek that want to aware of time sometimes they wantto forget that.
+They want to challange them.
+
+A clock without hands found the garbage pile and taken by Agnès Varda.
+It does not work properly but it has important meaning for her.
+The time does not go on and it does not remind her that she is aging.
+One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
+
 She talks and investigates artist that are using discarded items in the artworks.
@@
 Giving life or finding life from discarded life.
-
-The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.
 
@@
 
-The Gleaners And I is not an environmental film.
-Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.
-
-The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection.
-Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners.
-The film spends time capturing the many aspects of gleaning and the many people who glean to survive.
-One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-
-Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property.
+Varda's other subjects include artists who incorporate discarded materials into their work, symbols she discovers during her filming, and the French laws regarding gleaning versus abandoned property.
 Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
@@
 %%%
-\section{Summary}
-% Turning art making process to a life practice\ldots
-
-% TODO MOVE another chapter.
-% Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
-
-Lets make clear the motto: "trash to treasure".
-What is treasure here.
-What does it signify?
-Treasure---something very valuable.
-from trash.
-Then it is trash.
-Not once it is trash.
-What type of treasure.
-Who can get value from it.
-Who creates this treasure?
-How does it created?
-Trash is actually is opposite of treasure and then it is switched.
-In other words trash become treasure and treasure become trash?
-
-Lets consider the practice of working with trash.
-Why someone believes that discarded objects of people \ldots Looking things that people are refused.
-Transforming is the one of the most common practice of whole history of man and nature.
-This practice is forgotten or it is still alive.
-Agnes Varda actually shows that it is still exist but in different forms.
-They use it what ruling lifestyle throw out.
-They are everywhere actually but you should look them carefully.
-They live in the borders.
-But live.
-Event if they are refused they live.
-Actually it is hard to say that they want to integrate to the system.
-They want to change it?
-
-ability of transform, well actually it is very easy to throw away. hard thing is to keep it. force the material. the dimension of trash.
+%\section{Summary}
 
@@
 
-% Trash is as a material or a subject. Both of them. Can be traced examples of artworks.
-
-\begin{itemize}
-\item Where do you think this object came from?
-\item Why do you think that someone labeled this object as waste?
-\item How can you transform this object to tell the story that you thought of before?
-\item What story does it tell you?
-\item Does it remind you of an event, a specific time in history or in your life, a place, or a state of mind?
-\item How can you bring that story to life? (Taylor, 2006, p. 9).
-\end{itemize}
-
 % TODO PRAP. from rethink, reimagine, reinvent
-\paraphrase{Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
+%\paraphrase{Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
 Assemblage art involves the creation of new and innovative objects from what were once considered objects of waste; that is.
@@
 
-\todo[inline]{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
-Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}
-
-"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+%"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
 This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
@@
 %
-\textbf{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-\begin{itemize}
-\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-\item Try to find a new value and meaning from the discarded material that are useless anymore.
+%\textbf{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
+%\begin{itemize}
+%\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
+%\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
+%\item Try to find a new value and meaning from the discarded material that are useless anymore.
 To explore a new approach, new way.
@@
 Trash to treasure.
-\item Using discarded item to represent other discarded things by the ruling ideology or approach.
+%\item Using discarded item to represent other discarded things by the ruling ideology or approach.
 For example, trash can be used to represent refugees.
@@
 Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-\item Instead of a world that produce trash, how could it be a world created from trash?
-\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
+%\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
+%\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
+%\item Instead of a world that produce trash, how could it be a world created from trash?
+%\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
 It also signifies that trash still has a good quality to used with new materials.
@@
 Depends on the perception.
-\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-\end{itemize}
-
-Artists works and the place of the trash in the art can be summarized as follow:
-\begin{itemize}
-\item Artist see them as potential.
-But what type potential it haves.
-In which areas.
-They are already thrown away, if it was value or has a place in the current system they are not thrown away.
-There is an alternative life and outside of the ruling system.
-\item Visual uniqueness, aesthetics dimension.
-\end{itemize}
-
-% Ben bölümde aslında çöpün sanatta nasıl yer aldığına bakıyor olacağım. İlk kim kullanmış nasıl kullanmış. Sonrasında hangi anlamlarda kullanılmış.
-
-% Aslında ben uygun her yerde çöpe olan yaklaşımlarla ilgili örnekler verdim. Peki ya bu bölümde ne yapacağım. Belki gene değineceğim. Ya da ne anlamlara geldiklerini özetleyeceğim.
-
-% Hangi sonuçlar çıkacak aslında bu bölümden benim için kıymetli olan o. Özellikle caselerden. Bu nasıl bir artistict act oluyor.
-
-% Her sanatçı bu arada çöpü dönüştürmüyor. Bazıları ise onu oldukları gibi kullanıyorlar. Yani farklı kullanım seneryoları var. Ama ben dönüştürmeye dair ne çıkaracağım bu bölümde.
-
-% aslında dönüştüğünü nereden iddia edebilirim.
-Rubbish theory?
-Durable state.
-Ya da onun tekrar hayata geçtiği.
-Benimkiler de belli noktalarda fösterilecekler.
-İnsanlar o defterleri saklıyorlar ne de olsa.
-Zaten dönüşme işlemi direk müzeye çıkmasıyla oluyor.
-İllaha onun materyal olarak dönüşmesi gerekmiyor.
-Bu yüzden her iş aslında bir şekilde dönüştürüyor.
-Sanatsal pratikler çöpü dönüştürüyorlar.
+%\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
+%\end{itemize}
 
@@
 
-% Ne topladım buradan.
-Bu işin sanatsal bağlamdaki yerini öğrendik, yaklaşımları öğrendik.
-Yeni ihtimaller görme, hayatta var olma, alternatif oluşturma gibi.
-Ben de bu tür şeyleri kendi işimde kullanacağım.
-
-Childs can enjoy with trash.
+% TODO 4th chapter
+% Childs can enjoy with trash.
 I remember from my childhood, we collect crown cap and play with them.
@@
 
-Think a city that has trash monument in the every corner.
-created from their trash.
-merged with the city life and gaining unique cityscapes and aesthetics.
-or think that a museum a trash museum.
-Exhibits works of art embracing the trash in all aspects.
-Maybe done by the artist or the visitors from all around world.
-A place for garbage other than a landfill.
-Waiting their creator to meet again.
-What a great idea isn't it?
-Meeting their creators again.
-But this time their creator can recognize their trash.
-They transformed to totally new thing.
-Reborn.
-Transformed (Kafka, Gregor Samsa).
-
-\todo[inline]{Overview of all artworks. How do they differ from each other in terms of transformation(conceptually, physically), methodology, collecting, composition and so on.}
-
-\todo{a chart here.}
-
-\summary{As a canvas}
-Bazı işler çöpleri kendi işleri için bir kanvasa dönüştürmüşler.
-Çay poşetlerini boyayan kadın, Kitapları boyayanlar, teneke kutuları boyayanlar.
-Hepsi aslında kullandığı ürünle farklı bir ilişki kuruyor.
-Onları farklı bir hale getiriyor.
-
-Toplumun davranışlarına karşı bir cevap, görülmeyen, veya farkedilemeyen unutulup giden bir hale getiriyor.
-
-\summary{Trashing}
-Not all artist transform, some of them use them as they are.
-further some of them trashes things.
-[squeezing, artbin.] As we can think that trash is valuess.
-But the works of cesar claims that opposite of it.
-In his work he sequuzes objects and commodities.
-Makes them useless and functionless.
-But they earn great value in different value systems.
-In the literature generally focused topic is to analysis of transformation of trash to treasure (trash->treasure) but at the same time the opposite way is also exist.
-
 % TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-Recycling has always been a common practice in the arts at least at a non-material level.
+%Recycling has always been a common practice in the arts at least at a non-material level.
 From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
@@
 % FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\summary{Resistance} 
-\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+%\summary{Resistance} 
+%\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
 (sahlins 1992, 16)"
@@
 % FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\summary{Ironic}
-\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
+%\summary{Ironic}
+%\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
 the irony is often embodied visually and conceptually.
@@
 % FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
+%\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
 It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
-
-% Günlük rutinleri çöp üzerinden yakalayanlar var. Her gün ürettiği çöpün fotoğrafını çeken insan... Ürettikleri çöpleri ifade etme araçları olarak kullananlar.

### 2015-12-29 chapter2_reduced.tex
Chapter 2 review
Former-commit-id: de9640209bade5dc3b51e32502a643f004e1026b
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88

@@
-\chapter{Trash in Culture and Theory}
+\chapter{TRASH IN CULTURE AND THEORY}
 
+% Epigraph
+\begin{singlespace}
 % FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych, http://priscilauppal.ca/books/alphabet-city/
-\epigraph{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
+\epigraph{Anger is nothing compared to garbage:\\Garbage eats anger for breakfast.\\It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
+\end{singlespace}
 
@@
 The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
-\paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontologyh}.}
+\paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontology}.}
 

### 2015-12-29 drafts.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88

@@
 %........................................
+
+My work relation with the other works.
+
+(My work needs to be considered in the context of art. I need to focus on the notebooks establish with art.)
+
+sanki çöplerden bir şeyler yapmak bir şeyleri ispatlamak gibi gözüküyor.
+Ya da gene bir yetenek gibi gözüküyor.
+Bulunmaz kumaş misali.
+Yok abi kimsenin başaramadığı şeyi başarıyorum gibi bir şey yok.
+Ben ilgilinilmeyenle ilgileniyorum.

### 2015-12-29 chapter1_reduced.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

@@
-\chapter{Introduction}
+\chapter{INTRODUCTION}
 
+% Epigraph
+\begin{singlespace}
 \epigraph{One can even shout out through refuse \ldots}{\hfill---Kurt Schwitters, \textit{Kurt Schwitters}, 1985}
+\end{singlespace}
 
@@
 %
-\summary{Trash exists in every age and every society} 
-Refuse is part of people's consumption practices and it is a very common concept from developed cities to rural areas, from modern societies to ancient societies \cite[p.33]{rathje1992rubbish}.
-\todo{more ref.} For archaeologist dumps are one the significant places to figure what people consume in the ancient times \cite{rathje1992rubbish}.
-\summary{Global}
-\paraphrase{It is not limited with geography, ethnicity, gender, nationality.
-The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.}
-\summary{Trash is everywhere and, produced every time.}
-\paraphrase{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes \cite{zimring2012encyclopedia}.} During daily activities such as drinking coffee, eating beverages, waiting in the bank trash is generated.
-Different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes, and that become invisible.
-People are surrounded by all kinds of consumer goods.
-People are consuming everywhere while walking, working and traveling.
+%\summary{Trash exists in every age and every society} 
+Refuse is part of people's daily consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}. 
+%\todo{more ref.} 
+For archaeologist dumps are one of the significant places to figure out what people consume in the ancient times \citep{rathje1992rubbish}.
+%\summary{Global}
+%It is not limited with geography, ethnicity, gender, nationality.
+The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.
+Trash is everywhere and, produced every time.
+\quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes} \citep{zimring2012encyclopedia}.
+Various activities of our life such as eating, drinking, working, traveling leave behind wastes.
+People are surrounded by all kinds of goods and they are consuming everywhere while walking, working and traveling.
 The pattern is spread to all day and different places.
@@
 Nearly every place people require waste bin.
-If people do not find a waste bin, people often leave it (to the ground).
+If people do not find a waste bin, they often leave their trash to the ground.
 Production of trash never stops.
 It is inseparable from people's activities.
-\summary{Trash is everywhere} 
-Trash is in the streets, in your home, in the sea that you swam, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
-Even if trash is tried to be moved away from people life, it is close as nearest waste bin.
+%\summary{Trash is everywhere} 
+Trash is in the streets, in your home, in the sea that you swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
+Even if trash is tried to be moved away from people life, it is as close as nearest waste bin.
 
@@
 % FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-\summary{Facts}
-\paraphrase{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+%\summary{Facts}
+\begin{singlespace}
+\begin{quote}
+The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
 The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{OECD(Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
+OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
 Turkey is a member of this organization.} countries produce almost half of the world’s waste.
@@
 Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \cite{fash2015trash}.}
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \citep{fash2015trash}.
+\end{quote}
+\end{singlespace}
 
@@
 % From recycled book.
-\paraphrase{A person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
-America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}} \todo{iki paragrafı bir araya getir.}
+Similar to these as stated by \cite{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.}
 
@@
 %
-\summary{Moves} 
-The vast amount of industrial discarded items spread through the landfills to oceans.
-Trash moves like objects from place to place.
-From homes to garbage trucks.
-From streets to landfills.
-From waste bins to sculptures.
-Lots of different people touches to trash.
-Travels like humans.
-Travels like commodities.
-As commodities spread to the every corner of the world, trash also.
-It is not static, not fixed.
-\todo{bir yere bağla.} \todo{summarized edilebilir, repetition var.}%With the trash what moves?
+%\summary{Moves} 
+The vast amount of discarded items spread through the landfills to oceans.
+As commodities spread to the every corner of the world, trash do also.
+It moves from homes to garbage trucks, from streets to landfills and also from waste bins to sculptures.
+Various people including garbage collectors and artist touches to trash.
+It is not static, not fixed, not totally isolated from us.
 
@@
 It is stacked to another place.
-A project conducted by MIT in America explores the journey of trash by placing trackers onto the trash \cite{chen2009mit}.
+A project conducted by MIT in America explores the journey of trash by placing trackers onto the trash \citep{chen2009mit}.
 According to their results trash spreads away across the country and this journey takes month.
-Further it is not limited with the border of America because they are exported to the other countries\todo{ref.}.
+Further it is not limited with the border of America because they are exported to the other countries.
 In other words American's trash is not only their trash.
-\comment{What happens when it is traveled to the other countries, how do people approach these items?
+
+%\comment{What happens when it is traveled to the other countries, how do people approach these items?
 They find new uses and meanings on them because their understanding of that items is different.} \todo{Bu soru daha sonraki bölümde sorulabilir.}
@@
 %
-\summary{Common}
-(In the dictionary, \todo{Which dictionary?} trash means anything useless, worthless or discarded.
+%\summary{Common}
+In the dictionary, 
+%\todo{Which dictionary?}
+trash means anything useless, worthless or discarded.
 In parallel to this definition, the common perception is to get rid of them as soon as possible.
 People tend to think that trash is valueless because it is no longer needed or not wanted anymore.
-People want to get rid of them from their lives most of the time not thinking beyond (or alternative).
-\paraphrase{They forget about it and don’t think about all the time and energy and money put into disposing of it.} However to establish a solid understanding of trash (or the action of trashing), we have to give attention to the trash (and ask why it is trash).
-To understand the beyond common perception we have to ask is it possible to do something other than refusing them?
+People want to get rid of them not thinking any alternative.
+\quotes{They forget about it and don’t think about all the time and energy and money put into disposing of it} \citep{navarro2015followingtrash}.
+However to establish a solid understanding of trash and the action of trashing, we have to give attention to the trash.
+To move the beyond common perception we have to ask is it possible to do something other than refusing them?
 %\comment{Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash.
@@
 %
-\summary{Aspects and Approaches}
+%\summary{Aspects and Approaches}
 In this thesis study to understand the different aspects of trash is a key element.
-Sometimes it is accepted as a problem (because of accepted as useless, dirty, smelly) that needs to be carefully and seriously managed.
-On the other hand it is accepted as a source of diversity \todo{by whom, artist?}.
+Sometimes it is accepted as a problem (because of accepted as dirty, smelly) that needs to be carefully and seriously managed.
+On the other hand it is accepted as a source of diversity by the artists.
 For the recyclers it is a source of income.
@@
 By collecting and selling them they endure their life.
-Further some of the countries \todo{ref.} imports garbage to recycle or use their own purposes.
 
@@
 For some people, it is disgusting thing and moved away from living space and for the others source (or treasure) of their life.
-\paraphrase{While dictionary definitions of garbage describe it as \quotes{filth} and \quotes{worthless}, scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared \cite{zimring2012encyclopedia}.}
+It is noted that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep{zimring2012encyclopedia}.
 
-\summary{Relative}
-As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \cite{erlick2015editorsletter}.
+%\summary{Relative}
+As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \citep{erlick2015editorsletter}.
 She realized that any of them called the practice as recycling.
@@
 There is no place for trash in their life.
-It can be understood that approaches to the garbage are not same for all regions of the world \todo{ref}.
-
-% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-\paraphrase{We use it, produce it and dispose of it \cite{ibarra2015beautiful}.
-The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes \cite{ibarra2015beautiful}.}
+It can be understood from this anectode that approaches to the garbage are not same for all regions of the world.
 
@@
 %
-\summary{Parts of us}
-\paraphrase{Our trash is a testament; what we throw away says much about our values, our habits, and our lives \cite{zimring2012encyclopedia}.
-Our trash is part of us, whether or not we choose to acknowledge it \cite{zimring2012encyclopedia}.
-The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream \cite{zimring2012encyclopedia}.}
+%\summary{Parts of us}
+\begin{singlespace}
+\begin{quote}
+Our trash is a testament; what we throw away says much about our values, our habits, and our lives.
+...
+Our trash is part of us, whether or not we choose to acknowledge it.
+...
+The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
+\citep{zimring2012encyclopedia}
+\end{quote}
+\end{singlespace}
 
@@
 % FROM Book: Trash Culture
-\summary{Change in the production and consumption practices}
-\paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
-Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line \cite{pye2010trashculture}.} As the result of it amount of goods boost and the cost of them significantly reduced.
+%\summary{Change in the production and consumption practices}
+\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}.
+As the result of it amount of goods boost and the cost of them significantly reduced.
 Things once reused again and again, now thrown away because it is more affordable to replace with new one.
-\paraphrase{Mass production and commodification liquidated what remained of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production.
-\cite{pye2010trashculture}} As the production increased its by-product material waste is also increased.
-\paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption.
-\cite{pye2010trashculture}} \todo{summarize}
+As the production increased its by-product material waste is also increased.
+\quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.
+%\todo{summarize}
 
@@
 %
-\summary{Current} 
-During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste. \todo{bir yere bağlamak gerek.}
-
-% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-\paraphrase{Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding \cite{ibarra2015beautiful}.}
+%\summary{Current} 
+During the last decades much attention has been devoted to the waste.
+In particularly environmental considerations dominates the perceptions of waste.
+\cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.
 
@@
 %
-\summary{Art} \todo{belki kısaca bahsedip chapter 3'e taşınabilir.}
-\paraphrase{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art \cite{pye2010trashculture}.}
-
-% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti. 
-\comment{Using non art objects in the art opened new dimensions for the language of art and practice (act) of art.} In the beginning of the 20th century non-art objects \todo{non-art objecti aç} enter the scope of art making.
-This is a revolutionary change in the practice of art making.
-Production of art and the approach to the art changed dramatically.
-This changes actually started at the end of the 19th century with impressionist.
+%\summary{Art}
+As noted by \cite{pye2010trashculture} \quotes{at least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art}.
+Using non art objects in the art opened new dimensions for the language of art and practice (act) of art.
+In the beginning of the 20th century non-art objects
+%\todo{non-art objecti aç} 
+enter the scope of art making. This is a revolutionary change in the practice of art making. Production of art and the approach to the art changed dramatically. 
+%This changes actually started at the end of the 19th century with impressionist. 
 Picasso is the first artist that used non-art object in his works.
-Later many of artists followed him with their collages and assemblages (for example surrealist).
+Later many of artists such as Kurt Schwitters and Joseph Cornell  followed him with their collages and assemblages.
 Later Duchamp challenged the nature (or language) of art by using, non-unique, fabricated object to express his ideas.
 His work changed the way of perceiving art dramatically.
-With these developments trash has find a place in the art and contemporary artist are notably interested in trash.
+With these developments trash has found a place in the art and contemporary artists become interested in trash.
 They use trash for different purposes (and these are explored in detail in the following chapters.).
-\comment{Trash find places in sculptures, paintings, assemblages, photographs\ldots Artist express themselves through trash.
+Trash find places in many mediums such as sculptures, paintings, assemblages and photographs.
+Artist express themselves through trash.
 Portraits build from trash.
-Consumption habits of society are criticized through trash.}
+Consumption habits of society are criticized through trash.
 
@@
 
+% Bu tezde sorulan sorulardan birisi Çöpe daha farklı nasıl yaklaşılabilir... sanatçılardan örnekler verilerek bu açıklanmıştır.
+
 % Some of the artist also interested in others trash. Why people are interested in rubbish?
@@
 
-The aim of this study is to explore the theories and methods of transformation of trash\todo{open} in the context of art and artistic act.
+The aim of this study is to explore the theories and methods of transformation of trash in the context of art and artistic act. 
 % FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-\paraphrase{Particularly in the connection between garbage and the arts, [this thesis] interested in two questions.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material \cite{ibarra2015beautiful}.}
+\quotes{Particularly in the connection between trash and the arts, this thesis is interested in two issues.
+First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as artistic material} \citep{ibarra2015beautiful}.
 Why and how is trash used by the artist?
 Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items?
-Has using discarded material or trash specific (or special) meaning and message?
-Questioned that how do artists reflect garbage and what are their tactics?
+Has using discarded material or trash have specific (or special) meaning and message?
+Questioned that how do artists reflect trash and what are their tactics?
 
-\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature \cite{pye2010trashculture}.}
+%\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature \citep{pye2010trashculture}.}
 
@@
 
-Do people want to take back (or revisit) the trash once thrown away? In the project, the purpose is to turn them to things that worth to reconsider.
+%Do people want to take back (or revisit) the trash once thrown away
+In my project, the purpose is to transform trash and make it worth to reconsider.
 
@@
 %
-\summary{Different types of trash, narrowing down scope} 
+%\summary{Different types of trash, narrowing down scope} 
 There are different types of trashes result of different production and consumption practices.
-For example \paraphrase{radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology}.
+For example radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology.
 Electronic waste (e-waste), construction and demolition waste, medical waste are some of them.
 As it can be seen that there are lots of different types and as various as activities of human.
-In this scope of thesis focused on disposable items and paper trash.
+In this scope of thesis focused on disposable items and specifically paper trash.
 
@@
 %
-\summary{Different disciplines of trash, narrowing down scope}
-Trash attract the attention of different peoples and disciplines.
-% From Trashion: The Return of Disposed, Bahar Emgin. 
-\paraphrase{Such a conceptualization of waste as \quotes{the degree zero of value} has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture \cite{emgin2012trashion}.}
+%\summary{Different disciplines of trash, narrowing down scope}
+Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}.
 
-Technological perspectives are one them. Trash is seen as a design and technological problem \cite{mcdonough2010cradle}.  
+Technological perspectives are one them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
 % Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
@@
 % FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\paraphrase{In addition, the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed.
-When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \cite{cerny1996recycled}.}
+In addition to these
+\begin{singlespace}
+\begin{quote} 
+the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed.
+When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}.
+\end{quote}
+\end{singlespace}
 
@@
 %\summary{Waste and technology relationship} 
-%\paraphrase{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design \cite{mcdonough2010cradle}.} \todo{can be moved to zizek part.} In other words, the problem is our technology (or design, or both) which is not perfect and causes mountains of rubbish.
+%\paraphrase{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design \citep{mcdonough2010cradle}.} \todo{can be moved to zizek part.} In other words, the problem is our technology (or design, or both) which is not perfect and causes mountains of rubbish.
 It is questionable that at some point, technology will reach to a level when there is no trash generated.
@@
 This study is structured by many examples of artworks in different part of the thesis.
-When an argument is presented, (immediately) an artwork is given at this moment and how artists respond this issue is illustrated.
+When an argument is presented, immediately an examplory artwork is given and how artists respond this issue is illustrated.
 Thereby artworks are examined in the theoretical and cultural context.
-Artworks are used as a supportive elements for the stated arguments.
-However, not every time artworks are discussed in detail.
+Artworks are used as supportive elements for the stated arguments.
+However, artworks are discussed with all of their aspects.
 Only basic information is given and how it is related with this topic explained.
@@
 
-Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on (of?) trash.
+Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on trash.
 The aim is to understand the trash in cultural and theoretical aspects.
-(Aim is to establish better realization the notion of trash.) Chapter 2 provides theoretical and cultural background of the project.
+Purpose is to establish better realization the notion of trash.
+This chapter provides theoretical and cultural background of the project.
 It is explored the trash is being worked is whose trash and what type of society generate this type of trash.
@@
 
-Third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and analyses the sample artworks and artists.
+In the third chapter, Trash (in) Art, seeks the root of usin discarded materials in the artworks and analyses the sample artworks and artists.
 As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply.
-Artists methods and approaches to the subject are stated.
+Artists' methods and approaches to the subject are stated.
 
 Fourth chapter consists of the overview of the project.
-Stated the approach to subject clearly.
-Development process of the work is presented in detail.
-Decisions, factors and considerations that shaped the work is expressed.
+In this chapter, my aim is to state the approach to subject clearly.
+The development process of the work is also presented in detail.
+Finally I put the factors, decisions and considerations that shaped the work.
 
-Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.
+The last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.
 
@@
 Words are used interchangeably.
-From the book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:
+The book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:
 
@@
 % FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
+\begin{singlespace}
 \begin{quote}
@@
 The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.
+\citep[9]{rathje1992rubbish}
 \end{quote}
+\end{singlespace}
 
@@
 
-In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods of transforming trash to the another thing. Both of them are used widely by scholars.
+In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods of transforming trash to the another object. Both of them are used widely by scholars.
 
-\paraphrase{According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
 Reusing lengthens the life of the item or material.
@@
 To reuse is to use something again instead of throwing it away.
-\textbf{Why throw something away when you can give it another life?} Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-In thesis, it is explored through the work of artist.}
+
+%Why throw something away when you can give it another life?
+Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
+In this thesis, it is explored through the work of the artist.
 
@@
 % TODO Summarize
-\paraphrase{According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
+According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
 For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers used to make new glass containers, and scrap metal used in foundries.}
+Examples are crushed glass containers used to make new glass containers, and scrap metal used in foundries.
 
@@
 
-Some of the scholar uses recycling \cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
+Some of the scholar uses recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
 Many scholar used the word recycling when mentioning works use trash and the concept of it.
@@
 Creative reuse, inventing new things from discard.
-\paraphrase{Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of.} \todo{Reference, emgin2012trashion.} Some of the scholars and artist uses upcycling for their process.
-\paraphrase{This thesis project is about those objects that are recreated from trash through the process of upcycling.}
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
+Some of the scholars and artist uses upcycling for their process.
+This thesis project is about those objects that are recreated from trash through the process of upcycling.

### 2015-12-29 chapter2_reduced.tex
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

@@
 
-Firstly, focused on the disposable items that are designed to be ended up in waste bin after a single use.
+Firstly, I focused on the disposable items that are designed to be ended up in waste bin after a single use.
 Their usage and place are examined in the society and how other artists used and transformed them is analyzed.
@@
 
-Secondly, looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.
+Secondly, I looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.
 
@@
 
-% Life Magazine, 1955, "Throwaway Living", p43
-\summary{Throwaway Society} 
-Life magazine published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955 \todo{ref}.
+% TODO ref Life Magazine, 1955, "Throwaway Living", p43
+%\summary{Throwaway Society} 
+%\cite[43]{life1955throwaway} 
+Life magazize published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955.
 It is described as behavioral consumption pattern of society based on throwing away objects after use.
@@
 % https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
-\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?
-\todo{cite}} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
+\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?} \citep{tully2014throw} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
 
-According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth. \todo{ref. rathje1992rubbish p41}
-
-On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \cite{gregson2007identity}.
+According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
 According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
 However, their research did not include disposable packaging and bottles.
-Therefore, the act of throwing away can be narrowed down the specific goods.
+Therefore, the act of throwing away can be narrowed down to the specific goods.
 
@@
 This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century.
-In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production \todo{ref.
-Mamiya 1992, 2}.
+In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production
+%\todo{ref. Mamiya 1992, 2}.
 
@@
 %
-\summary{Disposable Items}
+%\summary{Disposable Items}
 Disposable items are made to be thrown away after used once or only a few times.
@@
 % FROM Trashion: The Return of the Disposed by Bahar Emgin
-\summary{Life of an Object} 
+%\summary{Life of an Object} 
 One could claim that the end of the life of an object corresponds to the moment when it is refused.
 This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
-At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.
-\todo{ref.
-emgin2012trashion p.63}
+At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}.
 
 % FROM Trashion: The Return of the Disposed by Bahar Emgin
-\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
-\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{ref.
-hawkins2001plastic p.9, emgin2012trashion p.64}
+%\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
+\cite[9]{hawkins2001plastic} argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”
+%\todo{ref. hawkins2001plastic p.9, emgin2012trashion p.64}
 
@@
 
-\summary{Capitalism, market, encouragement} 
-\paraphrase{The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+%\summary{Capitalism, market, encouragement} 
+The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}.
 They were designed to decrease in value over time - to be used one, or twice and then to be thrown away.
-This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.} \todo{ref.
-cerny1996recycled}
+This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
 
-\summary{Initial function} 
-\paraphrase{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it.
-Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash.} \todo{ref.
-cerny1996recycled}
+%\summary{Initial function} 
+\quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash} \citep{cerny1996recycled}.
 
-\summary{Being wasteful}
-As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \todo{ref, hawkins2005ethics p.viii} because the cost of repairing objects sometimes is higher than the original one or very close to it.
+%\summary{Being wasteful}
+As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \citep[viii]{hawkins2005ethics} because the cost of repairing objects sometimes is higher than the original one or very close to it.
 On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.
@@
 %
-\summary{Factors that cause over-consumption habits}
+%\summary{Factors that cause over-consumption habits}
 Technological advancements can be one of them.
@@
 The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
-\paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontology}.}
+\quotes{The commodities of food and drink must be safe, sterile and private} \citep{kennedy2007ontology}.
 
@@
 
-\paraphrase{The germ theory proscribes companionship.
+The germ theory proscribes companionship.
 The Latin root for this word, cum pani, literally means to share bread.
@@
 In essence, it encloses the commons.
-Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.} \todo{ref.
-ontology of trash}
+Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
+%\todo{ref. ontology of trash}
 
@@
 
+\begin{singlespace}
 \begin{quote}
@@
 And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
+\citep{strasser1999waste}
 \end{quote}
+\end{singlespace}
 
-\summary{Dark side} 
+%\summary{Dark side} 
 Usage of disposable items in the society is very widespread.
@@
 %
-\summary{Art}
+%\summary{Art}
 There are some artists whose works are related to the phenomena expressed above.
@@
 
-\paraphrase{Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
+Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
 It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work.
@@
 Here he draw attention to the our consumerism and express them numbers that are very big to understand.
-All the material that we have is trash to create this pictures.}
+All the material that we have is trash to create this pictures.
 
-\summary{Analysis}
+%\summary{Analysis}
 In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism.
@@
 
-\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
+Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
 She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
@@
 Every day she creates a new piece that reflects her impressions in that moment.
-Endeavour of re-purposing recycled and found materials.} \todo{cite website}
+Endeavour of re-purposing recycled and found materials.
+%\todo{cite website}
 
-\summary{Analysis}
+%\summary{Analysis}
 This work is for fathers day.
@@
 
-\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art.
+She saves all of her coffee cups to use as "canvases" for making art.
 Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture.
-I like my coffee or tea in a paper take-out cup.
-Even better than the contents, I like the used cup as a surface on which to draw and paint.
-Moreover, on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
+She uses cups as a surface on which to draw and paint.
+Moreover, on the bottom of each one, She record the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
 Each cup is representing a daily caffeine break.
@@
 These coffee shops all around the world.
-As she drinks her coffee in the public, she also publicly transforms its cup.} \todo{cite her website}
+As she drinks her coffee in the public, she also publicly transforms its cup.
+%\todo{cite her website}
 
-\summary{Analysis}
-She is inside of glass window not white, isolated cube.
-Glass window provide her to be close to public space.
-As she drinks her coffee publicly, also paints them publicly.
-\todo{related with Liz Parson's argument: practice of trash to durable.} There is no difference between them, and also they should not be separated (Why?
-Trash, production of it, coffee cups are all experienced widespread.).
+%\summary{Analysis}
+She is inside of glass window not white, isolated cube. Glass window provide her to be close to public space. As she drinks her coffee publicly, also paints them publicly. 
+%\todo{related with Liz Parson's argument: practice of trash to durable.} 
+There is no difference between them, and also they should not be separated.
 By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something.
@@
 
-\summary{TRASH and POTRAIT OF PEOPLE} 
+%\summary{TRASH and POTRAIT OF PEOPLE} 
 Trash is a reminder of consumption and production activities.
 In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action.
-Trash tells about societies choices.
+Trash tells about societies' choices.
 What is being left is one of the key things to realize what kind of people, society, action produce it.
-At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.) \todo{ref.}.
+At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.)
+%\todo{ref.}
+.
 As scholars mentioned that throughout the discards of someone else many things can be understood.
@@
 
-\paraphrase{Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had.
-Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.}
+Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had.
+Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.
 
-\paraphrase{When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends.
+When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends.
 Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful.
-Song eventually came to understand that, as he puts it:}
+Song eventually came to understand that, as he puts it:
 
+\begin{singlespace}
 \begin{quote}
@@
 \end{quote}
+\end{singlespace}
 
@@
 They are not new and not for sale.
-They represents a way of life.
+They represent a way of life.
 It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects
@@
 %
-\summary{Garbology}
+%\summary{Garbology}
 Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
 
-\paraphrase{Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away.}" \cite{lukas2012garbage}}
+Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away} \citep{lukas2012garbage}.
 
 % Garbology, from Encyclopedia, Abhijit Roy
-\paraphrase{The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
+The field of garbology involves the study of refuse and waste.
+It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}.
 According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
 Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
-It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.}\todo{ref.}
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.
+%roy2012garbology
 
-\paraphrase{The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice.
-At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene.
-(from Trash Culture)}
+The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice.
+At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene \citep{pye2010trashculture}.
 
-\todo{transition required.} With the help of mentioned understanding of trash, what can we see the work of arts?
+%\todo{transition required.} 
+With the help of mentioned understanding of trash, what can we see the work of arts?
 
@@
 It is a realization what she did during her depression time.
-It perfectly represents her condition during days.
+It perfectly represents her condition during those days.
 It can be understood that trash is part of our life.
@@
 
-Beds meaning also are not same for everyone.
-It is not just for sleep.
+Beds are not just for sleep.
 Especially for the ones that have small rooms and spaces bed becomes a life space.
@@
 It is more than sleeping and provide place for other activities.
+
+% tracey emin joseph beuys arasında bir ilişki var. sanatsal eylem ve kalıntı olarak bakıldığında.
 
@@
 
-\paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}
+\begin{singlespace}
+\begin{quote}
+In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects \citep[5]{hawkins2005ethics}.
+\end{quote}
+\end{singlespace}
 
@@
 
-Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.
+%Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.
 
@@
 He also criticized the position of artist by signing urinal as "R.Mutt" who is actually not exist.
-In the editorial The Blind Man summarized this work as follows: "Whether Mr.
+In the editorial The Blind Man summarized this work as follows: \quotes{Whether Mr.
 Mutt with his own hands made the fountain or not has no importance.
 He CHOSE it.
-He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object.\todo{ref}" To debate all the aspects of this work is not possible with the scope of this thesis.
+He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object} \citep{duchamp1917mutt}.
+To debate all the aspects of this work is not possible with the scope of this thesis.
 However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist.
@@
 
-\todo{bir conslusion lazım buraya.}
+%\todo{bir conslusion lazım buraya.}
 

### 2015-12-29 chapter3_reduced.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

@@
-\chapter{Trash (in) Art}
+\chapter{TRASH (IN) ART}
 
+% Epigraph
+\begin{singlespace}
 \epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together.
@@
 If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}, 1998}
+\end{singlespace}
 
-In this chapter, questioned the purpose and meaning of using trash as a medium in the artworks.
-The reasons and motivations of artists who use trash are analyzed.
-The artist uses discarded items in their work is analyzed in the light of arguments discussed in the previous chapter.
-Questioned that why artists select to use society's debris rather than fresh items.
-Researched the place of trash in the world of art by looking at different methods and approaches.
-Started from masterpieces and founding works.
-Continued with recent examples of artworks.
+In this chapter, I question the purpose and meaning of using trash as a medium in the artworks.
+The reasons and motivations of artists who use trash will be elaborated.
+The artists who use discarded items in their work will be analyzed in the light of arguments discussed in the previous chapter.
+Here, the main question is why artists select to use society's debris rather than fresh items.
+Hence, my research will focus on the place of trash in the world of art by looking at different methods and approaches.
+The scope of this research is Started from masterpieces and founding works, and continued with recent examples of artworks.
 
@@
 
-Firstly looked at how artist started using objects that are not produced by artist and with the purpose of making art.
-Their works are notable and founding works that open new dimensions to reconsider objects and their meaning.
+Firstly I look at how artist started using objects that are not produced by herself/himself and with the purpose of making art.
+Early works are notable and founding ones that open new dimensions to reconsider objects and their meaning.
 Further, they extended the ways of art making and the language of art.
-Therefore, it is important to analyze Their intent and methods are analyzed (how?).
-In other words, looked at the foundation of using non-art objects in the art making.
-First examples are analyzed and how it evolved over time is explored.
-Questioned that how they affected successor artist.
+Therefore, it is important and necessarry to analyze them.
+In other words, I first look at the foundation of using non-art objects in the art making.
+Early examples are analyzed and how they evolved over time is explored.
+I try to find out how they affected successor artist.
 
-Secondly looked at the some examples of contemporary works (or works from recent history). In particular, capture the current approaches on trash. Several methods and genres are explored.
-
+Secondly looked at some examples of contemporary works (or works from recent history).
+In particular, I try to capture the current approaches on trash.
+Several methods and genres are explored.
 Lastly focused on the inspiring documentary of Agnes Varda, The Gleaners and I which provides a general picture of the subject.
@@
 \section{Root in the Art History}
-Using trashed objects in making art can be examined with the entrance of non-art objects into the art.
-In other words, using objects in different scope beyond their intended purpose or intended meaning and function.
-Developing artworks not only painting but also using paper and other stuff by pasting (or juxtaposing) them together.
-(How using non-art objects affected art?
-Fragments) Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
+Using trashed objects in making art can be examined with the use of non-art objects in modern art.
+In other words, some artist started using objects in different scope beyond their intended purpose or intended meaning and function in their modern artworks.
+They develop their artworks by using paper and other stuff by pasting (or juxtaposing) them together.
+
+%Indeed, using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
 However, it is not discussed in the context of fine art and not accepted method for art making.
 
-From the beginning of 20th-century non-art, objects draw the attention of the artist.
+From the beginning of 20th-century non-art objects draw the attention of the artist.
 Development of art in this century evolved through this non-art objects (or these objects play significant role development of art trough time).
-They bring new dimension (or perception) to consider objects.
-Usage of these objects dramatically changed the way people look at art.
+Usage of these objects dramatically changed the way how people look at art.
 In short, they introduced a new way of making art.
 
-One of the remarkable change in the 20th-century art is the using unconventional materials in the making of paintings and sculptures, rather than the original (pure, fresh) materials produced with the purpose of art.
-These objects are not normally considered as art, often because they already have a non-art function.
-Possibly they are part of different disciplines and markets.
+One of the remarkable change in the 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
+These objects are not normally considered as art often because they already have a non-art function.
 Their place in the society and people's mind commonly have a different meaning.
-Beyond them, artists started to use them for their own purposes.
-Objects gain different meanings and usages with the hands of artists.
+Beyond that, artists started to use them for their own purposes.
+Thus, objects gained different meanings and usages with the hands of artists.
 (It is explained in the previous chapter that objects are not static and absolute.
@@
 
-They questioned the way of traditional (conventional) way of art making in every dimension.
+Modern artist questioned the way of traditional (conventional) way of art making in every dimension.
 Their approach out of the previous methods.
@@
 It is a composition of different fragments and pieces.
-Rather than the traditional way of painting on canvas they composed their work with the combination of various objects from different context.
+Rather than the traditional way of painting on canvas modern artists composed their work with the combination of various objects from different context.
 With this approach works can be examined in multi-dimensional context.
@@
 
-Before the 20th-century, artists started to inquiry the existing methods and themes of previous periods.
-Modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
+In the 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
 Previously paintings are based on linear perspective and realistic style.
-Themes are often composed of religious and mythical narratives \todo{MOMA ref}.
+Themes are often composed of religious and mythical narratives.
 After the second half of the 19th-century, they started to abandon these themes and painting methods.
-For instance, in the works of impressionist paint brushstrokes can be easily identified, and themes are composed of everyday scenes.
-With Cezanne, the linear perspective started to question and later reached to its peak point with cubism.
-Cubism is developed with the collaboration of the Picasso and Braque.
+For instance, in the works of impressionist paint brushstrokes can be easily identified.
+In impressionist paintings, themes are composed of everyday scenes.
+With Cezanne, the linear perspective is questioned and later this questioning reached to its peak point with cubism.
+Cubism is developed with the collaboration of Picasso and Braque.
 Besides, these two artists experimented non-traditional materials in their works for the first time in the scope of fine art.
@@
 
-One of the keys to understanding the importance of Cubism, of Picasso and Braque, is to consider their actions and how unusual they were for the time.
-When Braque, and then Picasso placed industrially-produced objects ("low" commercial culture) into the realm of fine art ("high" culture) they acted as artistic iconoclasts (icon=image/clast=destroyer).
-\todo{ref}
+One of the keys to understanding the importance of Cubism of Picasso and Braque, is to consider their actions and how unusual they were for the time.
+When Braque, and then Picasso placed industrially-produced objects into the realm of fine art they acted as artistic iconoclasts of their age.
+%\todo{ref}
 
@@
 In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.
-
-Collage was a major turning point in the evolution of Cubism, and therefore a major turning point in the whole evolution of modernist art in this century \cite{greenberg1984collage}.
+Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \citep{waldman1992collage}.
+Collage was a major turning point in the evolution of Cubism, and therefore a major turning point in the whole evolution of modernist art in this century \citep{greenberg1984collage}.
 
@@
 William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.
-\todo{ref.}
+%\todo{ref.}
 
@@
 One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting.
-This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture.
+This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture.
 Picasso combined painting with already existing materials.
-He used real objects to represent instead of painting.
-As mentioned in the name of the work Picasso give clues of the parts of it.
-For instance the oval canvas\todo{canvas or oilcloth?} and the rope around it represent the table.
+As mentioned in the name of the work, Picasso give clues of the parts of it.
+For instance the oval canvas and the rope around it represent the table.
 Pasted chair caning signifies the chair within the table.
@@
 
-Moreover, they questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the rarefied, contemplative realm of artistic creation.
+Moreover, Braque and Picasso questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the  contemplative realm of artistic creation.
 Of equal importance, their work highlighted and separated the role of technical skill from art-making.
-Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of high and low, of unique and mass-produced objects.
+Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
 They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"
@@
 After Picasso and Baraque, many artists applied collage and assamblage techniques to their works.
-Dada artist Kurt Schwitters is one of the productive artists of them.
+Dada artist Kurt Schwitters is one of the productive artists amoung them.
 In 1918 created his own form of Dada in Hanover called 'Merz', using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions.
@@
 
-"The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
-In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism." (Gwendolyn Webster)\todo{ref}
+\begin{singlespace}
+\begin{quote}
+The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
+In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism...
 
-% http://www.artchive.com/artchive/S/schwitters.html
-Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.\todo{ref}
+Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.
+\citep{webster2011kurt}
+\end{quote}
+\end{singlespace}
 
-Merzbau is most important ones.
-In 1937 after his work had been included in the Degenerate Art Exhibition he fled Germany for Norway.
+In 1937 after Merzbau had been included in the Degenerate Art Exhibition he fled from Germany to Norway.
 There he created a second Merzbau.
@@
 % FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-\todo{works of Kurt Schwitters} \paraphrase{The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
+\begin{singlespace}
+\begin{quote}
+The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
 Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay.
@@
 Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.}
+The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
+\citep{carroll2011ruin}
+\end{quote}
+\end{singlespace}
 
 % Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-\paraphrase{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
-Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
-(Jacknis 1992)} \todo{ref.}
+Jacknis claims that \quotes{like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others} \citep[as cited in][]{cerny1996recycled}
 
@@
 Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them".
-\todo{ref}
+%\todo{ref}
 
 % Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
-It is claimed that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
+It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.
 
-Collages and assemblages can be composed of all types of objects such as trash and found object.
-The notion of found object is researched by the many scholars \todo{ref.}, but usage in the art has gained new dimensions with the Duchamp's concept of readymade.
+Collages and assemblages can be composed of all types of objects such as trash and found object. The notion of found object is researched by many scholars 
+%\todo{ref.}
+, but usage in the art has gained new dimensions with the Duchamp's concept of readymade.
 Industrially manufactured or anything found  anymore can found a place in the art.
@@
 When Bicycle Wheel was first displayed, Duchamp encouraged viewers to spin the wheel.
-(Participation of the audience) Although he claimed to select objects for his readymades without regard to beauty, he said, “To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.”
+Although he claimed to select objects for his readymades without regard to beauty, he said, “To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.”
 
@@
 %
-\summary{Found Object} 
+%\summary{Found Object} 
 Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
@@
 
-\paraphrase{Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
+Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
@@
 He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).} \todo{parap.
-ref.}
+\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
+%\todo{parap. ref.}
 
@@
 \section{Examples from contemporary artists}
-In the light of discussions at previous section, some of the works (or current strategies and approaches ) of artist are analyzed. First one is related with found objects.
+In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed.
+First one is related with found objects.
+In this section focus will be shifted to the examples from contemporary artists.
 
@@
 Photobooths are machines that place crowded places and with affordable cost people can get their photos.
-It is a pheonema that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as a two volume.
+It is a pheonema that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.
 
@@
 He collects them and glue them together in a photo album.
-In the film photo booths and found photos are central catalytic.
+In the film photo booths and found photos are centrally catalytic.
 Amélie falls in love with him when she realize him searching for found photos.
@@
 Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away.
-The important part of the film it generates images of a man who scanvage the photos of another people.
+The important part of the film, images of a man are generated who scanvage the photos of another people.
 There are a lot of artist who collects discarded items but their process is not well documented.
-Therefore we are not aware of the artist process.
+Therefore we are not aware of the artistic process.
 
@@
 It is a collection of photobooth images that had been thrown away or torn up by the people in the photos.
-Ian Walker comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine.
+\cite{walker2010dick} comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine.
 They are scavenged by the artist from the photo booths of London.
@@
 On the other hand, some of them are very good condition, and it is a mystery that why they are rejected.
-Walker explains that the \todo{block qoute} "gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving." Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them.
+Walker explains that the
+
+\begin{singlespace}
+\begin{quote}
+gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving.
+\end{quote}
+\end{singlespace}
+
+Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them.
 "Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ‘readymades’." His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin.
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-  \begin{center}
-    \includegraphics[width=0.37\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
-  \end{center}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=8cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
   \caption{Vic Muniz, Pictures of Garbage}
   \label{fig:VicMuniz_PicturesOfGarbage}
-\end{wrapfigure}
+\end{figure}
 
@@
 For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music.
-(To enjoy and play such music requires economic wealth and it is not possible for everyone.) What they create is actually not expected from them, and their success is not limited with their location.
+What they create is actually not expected from them, and their success is not limited with their location.
 They have given concerts around the world.
@@
 This project can be seen as a bricolage practice.
-Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time.
+Dictionary meaning; something constructed using whatever was available at the time.
 \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
 It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}
+\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.
 
@@
 Selected persons can be viewed as a member of the higher or ruling class of society.
-Therefore Kim Alsbrooks, painter of these works, might thought that to make trash is more valuable, their face will be good.
-Or the vice versa.
-She may use trash to provocate social elite of that time.
+Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good.
+Or vice versa.
+She probably use trash to provocate social elite of that time.
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-  \begin{center}
-    \includegraphics[width=0.37\textwidth]{graphics/Alsbrooks.jpg}
-  \end{center}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
   \caption{Kim Alsbrooks, The White Trash Series}
   \label{fig:Alsbrooks}
-\end{wrapfigure}
+\end{figure}
 
-Not all the time and every artist turn trash into different objects sometimes they trash them.
+Not all the time and every artist turn trash into different objects, sometimes they only trash them.
 Michael Landy's Art Bin is one of them.
@@
 Like his words, it is “a monument to creative failure”.
-(According to this approach one can extract that failures belong to the trash bin.
-However, there must be other alternatives that to demystify the practice of the artist.) On the other side, there is a provocative approach to the art and art objects by saying that "Nothing is too good for the art bin." There is no limitation of throwing away even if art.
+On the other side, there is a provocative approach to the art and art objects by saying that "Nothing is too good for the art bin." There is no limitation of throwing away even if art.
 
@@
   \centering
-  \includegraphics[width=0.37\textwidth]{graphics/MichaelLandy_ArtBin.jpg}
+  \includegraphics[height=7cm]{graphics/MichaelLandy_ArtBin.jpg}
   \caption{Michael Landy, Art Bin}
@@
   \centering
-  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
-  \caption{Chris Jordan, Break Down}
-  \label{fig:ChrisJordan_BreakDown}
+  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
+  \caption{Michael Landy, Break Down}
+  \label{fig:MichaelLandy_BreakDown}
 \end{figure}
@@
 %
-\section{The case of \quotes{The Gleaners and I}}
+\section{The documentary \quotes{The Gleaners and I} by Agnès Varda}
 "The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000.
@@
 Varda seeks the several stages of potatoes from producers to consumers.
-As she discovers that supermarkets, buy only potatoes that fit in industrial standards of shape and size.
+As she discovers that supermarkets buy only potatoes that fit in industrial standards of shape and size.
 So what happens to the others?
@@
 
-\todo{image}
+%\todo{image}
 
@@
 There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed.
+More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have been closed.
 By showing them she shows that once was a common practice of gleaning throughout the years has evolved, but not disappeared.
 She keeps light to the modern life gleaners that are not visible every time.
-One of the is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-Probably he has all the capabilities that live amoung the other people(???).
+One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
 It can seen that from this example, gleaning becomes also a form of resistence to ruling system.
@@
 
-\todo{waste and want rules of eating from garbage.}
+%\todo{waste and want rules of eating from garbage.}
 
 She shows that the act of gleaning does not bound to the collecting food and survival reasons.
-Some of them build their own meaning and existig and identity through the collected items.
-One of the examples that she gaves is ghat the man who collects baby dolls and use them in the decoration of his home.
+Some of them build their own meaning, existence and identity through the collected items.
+One of the examples that she gaves is that the man who collects baby dolls and use them in the decoration of his home.
 Every where is filled up with the babydolls even if wall of the garden.
@@
 Through the film she experiences the act of gleaning with different people.
-At one side she gleans potatoes in the field and on the other side follows a man with biycle look for the garbages front of the homes.
-By documenting their life in action she also participate them.
-But she bring them her own perception to them.
-For example in the case of potato gleaning she collect the heart shaped ones which are attract attion of her.
+At one side she gleans potatoes in the field and on the other side follows a man with biycle look for the garbages in front of the homes.
+By documenting their life in action she also participates their life.
+But she brings her own perception to them.
+For example in the case of potato gleaning she collects the heart shaped ones which attract attention of her.
 Moreover in the case of night searching, she finds a clock without hand.
-It has fullfiled lits function and leaved away.
+It has fullfiled its function and left away.
 Most important part of clock is missing therefore it is not functioning.
-However for it is a different meaning.
-Not every time people seek that want to aware of time sometimes they wantto forget that.
-They want to challange them.
+However for her it has a different meaning.
+Not every time people seek to be aware of time sometimes they want to forget that.
 
@@
 The time does not go on and it does not remind her that she is aging.
-One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person.
+One of the interesting thing is here Agnès Varda feels that as an aging person who will later become a discarded person.
 
-She talks and investigates artist that are using discarded items in the artworks.
-What people not found anything the artist see countless possibilities from them.
-There is always alternative ways to see something different.
-Giving life or finding life from discarded life.
+She talks and investigates artists who are using discarded items in the artworks.
+Which people could not find anything, the artists see countless possibilities.
+There is always alternative ways to see something different: Giving life or finding life from discarded life.
 
 Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collecting things in their life but particularly she selects these people and their images in action.
-There should reason for this?
+Everyone somehow collect things in their life but particularlly she selects these people and their images in action.
+There should be a reason for this!
 For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life.
@@
 
-% TODO 4th chapter
-% Childs can enjoy with trash.
-I remember from my childhood, we collect crown cap and play with them.
-Some caps are found less and they worth more.
-We are looking everywhere for them.
-To make them flat we put them on the railways.
-After train passed we get perfect plat cap.
-At that time it is not trash for us.
-It has a value and part of our games and enjoy.
-To have fun a bunch of trash can be enough for us.
-
 % TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista

### 2015-12-29 chapter4_reduced.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

--- 2015-11-22 chapter4.tex
@@
-\chapter{Thesis Project: Notebooks from Trashed Papers}
+\chapter{NOTEBOOKS FROM TRASHED PAPERS}
 
-%****************************************
-% Structure of Chapter:
-% 
-% Artist Statement
-% Development of Work
-%  Collecting, Transforming, Tests...
-%
-% Final Work
-%  - Notebooks
-%  - Website
-%  - Exhibition
-%........................................
+% başka bir yerde kullanırsın: , as illustrated by the examples cited so far,
 
-%****************************************
-% Relationship between my project and theoretical aspects:
-% - First one is actually is to analyze what is trash?
-Because I am using trash material and what is point of view of scholars to the trash.
-Realizing the potentials of it.
-Also the difference comes from the working on virgin object and trash object.
-Understanding the difference between the bricolouer and engineer.
-If trash has multiple life than these research will somehow reveal it.
-It is actually research on trash but what purposes.
-I guess it is missing?
-I need to set a purpose for the theory chapter.
-Or it is a just a background chapter?
-% - Roots in the art history. (Also roots on the social life can be researched?)
-% - Inspiration from the other artist and also 
-%........................................
-
-%****************************************
-% Sample Phrases
-% \ldots is the concern of this study which aims to \ldots
-% The aim is not to practice Antiquarian Avant-Garde techniques as a puritan form of photography, but rather to envision new means of photography.
-% The aim of the thesis paper is to historically, socially and theoretically contextualize a student's work.
-The written thesis documents and informs the development and resolution of each student's artistic practice during the MFA program.
-%........................................
-
+% Epigraph
+\begin{singlespace}
 % FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
@@
 That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
+\end{singlespace}
 
-In this chapter thesis project with the development progress of it will be explained in detail in the light of what has been discussed in previous chapters.
+In this chapter thesis project and its development progress will be explained in detail in the light of what has been discussed in previous chapters.
+The project will be examined in various dimensions.
+The relationship will be established between the previously mentioned artworks.
+How this project is related to the discussed concepts and how it can be positioned among the previous works will be explained.
 
-% What I have write is here to cover the project can not be sufficient.
-Because it is not possible to say everything about this project.
-I wish that this work would allow different interpretation and readings.
+Firstly, brief statement and description of the work is given. Secondly, the development of the project and experiments are explained. Lastly, the final body of the work with its parts is presented.
 
-% TODO
-% Felix Gonzales Torres'in untitled işi benim yapmaya çalıştığım ile ilgili.
+%
+%
+% TODO: Burada geçmiş, şimdiki zamanlara dikkat etmek gerek.
+\section{The Statement}
+% TODO Ekolojik, harmful, iğreç falan diye de değinmek gerekli bence.
+% --disgusting, abject, unattractive, harmful to the people and nature--
+Refuse is part of people’s consumption practices.
+It is a very common concept from developed cities to rural areas, from modern societies to ancient societies.
+It is not wanted, thrown away, kept away.
+It is considered as useless and disgusting.
+Contrary to the common approach as Michael Thompson, author of the book Rubbish Theory, stated "one man's trash is another man's treasure".
 
-%%%
-%%%
-%%% 
-% TODO
-\section{Artist Statement}
-(Collect, Save, Transform, Spread.)(Rescue, Revive)
+% Her zaman her yerde olan çöp.
+% people are invited in the phase of collecting and finding trash
+With the collaboration of many people discarded papers and packages were collected from different places.
+This time, it was not thrown away, it was collected and saved.
+Later they were transformed to notebooks by hand with traditional methods.
+Juxtaposition of trashes create notebooks that are different from the blank industrial ones, and through them challenged the widespread understanding of trash.
 
-The work aims to liberate the imagination and change the way people see the trash.
+Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek. As it is discarded, missed potentials were discovered.
 
-% Closest waste bin is actually my own pocket.
+The purpose is not to build an object that is produced from discarded material to watch it from distance.
+The important thing is to interact with it.
+It is already discarded and general behavior avoid from it.
+This work must change it.
+It must call the viewer to interact with it.
+Trash must be accepted by them.
+For this reason notebooks are given away free at various places where people visit frequently.
+By doing that once thrown materials would find a place with new purposes in the community.
 
-% Converting disposal things to multiple time usage. Realizing the alternative lives of trash beyond their defined one shot life. Giving attention to the things.
+% Bu proje çöpte yeni imkanlar bulmayı amaçlıyor. İnsanların tekrar onları hayatlarına sokmalarını istiyor.
 
-% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir.
-Zaten toplama sürecinde bunu insanlarla ilişki kurarak yapıyorum.
-O insanlarda diğerleriyle konuşarak yapıyorlar.
+%
+%
+\section{Development Progress of the Project}
+In order to have an insight of this project and realize artistic intentions, it is important to look at the process that reveals the path to the final work and critical decisions that were necessary to the completion of the project.
 
-% At this stage it is claimed that the process of transformation of trash can be treated as artistic act.
-In the production of notebooks people collected papers from different places and location.
-During the collection phase they also collect them from other people.
-In other words there is human communication during this process.
+% Starting from the very beginning, I would like to explain which paths and turns I took and how they let my work to come out as it is now.
+In other words, this will be the story of how I developed my work from scratch.
 
-Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making.
-The process effects one's life and lifestyle.
-(But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance.
-The important thing is to interact with it.
-Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it.
-It must call the viewer to interact with it.
+% Artist's work and their approach supported my project.
+Through the process, there are several problems that needed to be solved.
+Some of the questions in my mind are solved through the research on trash.
+Further, the found samples of artworks helped me a lot to shape unclear points of the project.
+They provide me a deeper understanding of the subject and what I am doing.
+They lead me during the development of the work.
+% played significant role.
+% It is evolved in time and affected from other artists' work, and gain meaning from research.
 
-% Ersan hoca uzak seyretmek yerine etkileşime geçilmesini auranın kırılması olarak bakıyor.
-Performatif olması veya bir act olması zaten bunu kıran bir şey olabilir.
-Sanatsal eylem, performans kavramlarını araştırmak gerekli.
-Uzaktan seyredip hayranlık duymak yerine ilişkiye geçilen bir hale getirmek çöpü.
-Amaç bu aslında.
-Çöpü tekrar tanımak, onunla barışmak, onunla yaşamak.
-İşte bu yüzden bir eylem olabilir.
-Ya da yaşam pratiği.
+% This progress also reveals the how this work can be positioned among the other works.
 
-% Olay sadece böyle çöpten bir şeyler yapıp insanların seyretmesi değil, mühim olan onunla iletişime, ilişkeye geçmek.
-Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki?
-İnsanların bu işin aşamalarının bir parçası olmalılar.
+% NEW PART [approach, history] 
+Before explaining the details of the work, it would be better to explain how it was started and what is my approach to the trash. % It is not developed from scratch.
 
-With the help of art (and artistic practices) discarded things can find a place in the society.
-(By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society).
-The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.)
+My interaction with discarded material is not limited with this thesis project.
+There are some previous attempts and several memories that I remember.
+Briefly, I want to examine them.
+These will also reveal my approach shaped through time (and how thesis work affected from it?).
+My motivation also revealed through it.
 
-% Using trash can not only understand in ecological perceptions, it also have powerful political claims.
-Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.
+% [SODA CAPS]
+I remember from my childhood that we were collecting soda caps and played with them.
+We were looking everywhere to collect them.
+Some caps were found less and they worth more in the game.
+We put them on the railways to make them flat.
+After the train had passed we had perfect flat caps for our games.
+At that time, it was not waste for us.
+It has a value and part of our games and indispensable source of fun.
+The notion of playing with it can be related with the Picasso's collage -"Still Life with Chair Caning"-- mentioned previously.
+He pasted letters of the French word "JOU" means "game" signifying that playing with the materials.
+We were already playing with trash while we were child.
+Therefore, it can be better understand that while Picasso said that "every child is an artist".
 
-% SEEING IT AS A RESOURCE.
-Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics.
-Ignored and discarded nature of garbage when rethought becomes fertile resource.
-Trash as a resource (as an artistic material).
-(City as a resource.
-Seeing the discarded items as a resource.
-Many artist approach to trash as resource.
-It is a shared approach.
-Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)
+% [VASVIYE HOCA]
+Another important memory is from my primary school teacher.
+When I was at third class, our teacher wanted us to bring colorful papers to make something (whatever it is I do not remember now).
+The day after we brought some colorful paper that was bought from stationery store.
+Our papers' shape and color looked same.
+However her papers were different in every dimension.
+They were cut out from packages and advertisements.
+I remember clearly that she suggested that same for us.
+"Do not throw out packages, look for the useful parts and keep them to use later." Whenever I am going to throw something away, this comes to my mind.
+Can it be reused?
+Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice.
+Further, this practice is also support to the bricolage methodology.
+Keeping many things makes easier to build (or produce) whatever at hand.
 
-% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.
+% Song dong, economical struggles.
 
-Do she/he want to take back (or revisit) the trash once thrown away?
-People do not want to think of what they throw away.
-Turning them to a things that worth to look again.
-How do artists reflect garbage and what are their tactics?
-What is the thing that add value to trash and what is the role of art in that?
+% [EXPERIMENTS AT HOME]
+Most remarkable interaction with trash is from recent years.
+Long years I stayed at dormitory during when I was high school and university while undergraduate.
+Dormitory is place that living spaces is shared with many people.
+Therefore there is a limited place for you and your possessions.
+There is no space for unused items.
+After I graduated from university I started to living a rented house.
+This give me to opportunity to save the materials to use them later.
+My very first intention is to use them on my painting.
+Instead of white blank canvas I want to experiment with different surfaces.
+I collected boxes and cart boards from my friends.
+My aim is to turn discard materials to the different things.
+Here is some of the my previous works.
 
-With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods.
-In other words autistics practices generates applies different methods.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
+        \caption{Sax}
+        \label{fig:landfill_harmonic-sax}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
+        \caption{Violin}
+        \label{fig:landfill_harmonic-violin}
+    \end{subfigure}
+    \caption{Examples of previous works}
+    \label{fig:animals}
+\end{figure}
 
-%%%
-%%%
-%%%
-%\section{Inspired Works}
-%There are some works that inspire me a lot when developing the work.
-They are not actually trash related works therefore I put them in different section and here before the details of my work.
-However the previous chapter has also very inspirational contributions to the my work.
-They helped the understand the topic and develop an approach to the topic.
-In this section some projects are mentioned and their methodologies are explained.
-How are these works effected my work.
-What is the relationship between them?
-(Maybe all of them can be explained only the related part of it.)
-%SketchBook Project.
-Inspires me a lot.
-Lots of works from all over the world.
-Full of creativity and showcase of richness of people's expressions on the small notebooks.
-My work can be considered as a sketch book project through trash.
-Sketches or only creative progress is not the only consideration.
-You can send your lecture notes.
+[image of previous works.]
 
-% Daha öncesinden ne yaptığımı biliyor olmalı insanlar.
-% Benim kriterlerim nedir?
-% Benim kurallarım nelerdir?
+After turning discarded materials to different uses I began to collect them more eagerly.
+At the same time I also gave what I did to my friends as a birthday gift.
+I was experimenting with the material and at some point with the help of my mother I made my first notebook covered by Starbucks package.
+Papers inside of it are blank mimeograph paper which different than white paper.
+Particularly purpose is to move away from white paper because I feel uncomfortable when using it.
+It looks to me very bright.
+Therefore mimeograph paper is better for me.
+At that time it was a great victory for me.
+I started to carry it and use it every possible place.
+I show them to people and some of them supported to me giving their discard.
+One of them is my supervisor.
+He started to collect packages for me.
+After turning his packages to notebooks, he suggested me to go deeper in this subject and make my thesis project from them.
+Thereafter what I need is more discarded material.
 
-%%%
-%%%
-%%%
-\section{Development Progress of Work}
-How does it evolve in time?
-Important points.
-This progress also reveals the how this work can be positioned among the other works.
-\comment{Tarihsel bir süreç mi yoksa bu işi bir araya getiren şeylerin nasıl bir araya geldikleri mi?}
+% But covering things are not new actually, when we are primary school again, we cover our books and notebooks.
+My mother, she is also a teacher, still covers her books things whatever at hand.
+(I have remembered that we are covering our notebooks at school.
+Sometimes we also cover the books.)
 
-\begin{description}
+% bir yandan free olması experiment yapmak için ideal olması.
 
-%%
-%%
-\item[How is it started?]
-
-%%
-%%
-\item[Memories.] As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember.
-One of these (First of them) is from my primary school teacher.
-When I was third class my teacher give us a homework to bring colorful paper to make something(whatever it is I don't remember).
-The day after we bring some colorful paper but she did not.
-Instead of this she bring paper cut out from packages that are colorful, shinny and qualify.
-And I remember clearly that she suggest that same for us.
-Do not throw out packages, look for the useful parts and keep them to use later.
-
-\item[What do I think about trash?] I need to clarify my approach to the trash, wasting and discarding.
+%\textbf{What do I think about trash?} I need to clarify my approach to the trash, wasting and discarding.
 First point is that I am very uncomfortable to the action of discarding thing.
@@
 
-Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}
+%Significance of thinking outside of the box (about trash) is actually breaking the loops.
+You have to look at differently from common perception.
+\textbf{Break the rules, break the loops} to realize the alternative.
+\comment{Even if the market gives many alternatives of commodities, why do people still seek the alternative?
+Is not is enough?
+What type of gap that industrial products can not fill the gaps.
+Neden tüm insanlara hitap etmiyor?}
 
-[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
-Because it is discarded and undiscovered.
-Wait us to be discarded.
-and possible (as picasso mentioned) discovered again and again.
+%[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
+Because it is ignored by discarding and therefore undiscovered.
+Wait us to be discovered.
+and possiblely (as picasso mentioned) discovered again and again.
+\comment{Different people from different culture bring new interperation, but it is exist all of things.}
 
-%%
-%%
-\item[Motivation.] I can not throw them away.
+%It contains evraka moments.
+
+%[Motivation.] I can not throw them away.
 When I throw them I became sad for them.
 I have to find something useful for it.
-Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
-We are humans that can produce, transform items.
-One of most developed species in the earth that produce and use tools.
-There is a lot of effort to produce thrown away and it seems that all this efforts are wasted.
+(Failure of imagination, failure of making meaning) Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
+There is a lot of effort to produce objects and it seems that all this efforts are wasted.
 What I mention is not related about ultimate productivity.
@@
 
-%%
-%%
-\item[Paper]
-"Paper is an indispensable product throughout the world.
-Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information.
-In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment.
-Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes.
-Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}
+% Önceki chapterlarda insanların kişisel olarak objelerde neler buldukları önemliydi. Ben de burada kendiminkini anlatacağım. Benim için yeni bir şeyler üretmek için birer kaynak.
 
-\comment{My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty.
-But it is very strange that the fat on the paper is previously what they are eat.}
+% NEW PART [collecting] 
+Collecting discarded objects has carried out through the efforts of mine and people around me.
+Lars Eighner's instructions helped me a lot when collecting objects.
+He writes that "Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question 'Why was this discarded?'".
+[SUSAN STRASSER p6] I applied these instructions to my case and I checked some points regularly and seeked the reason of why was it discarded.
+Details will be given later for each objects.
 
-Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage.
-However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic.
-In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions.
-Further, forest resources are not always as renewable as one may like to think.
-These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.
+% Bozulduğu için mi yoksa şekli standartlara uygun düşmediği için mi atılmış agnes varda da gösterildiği gibi.
 
+% [Mode of search] looking for waste bins. asking for people. realizing during the daily life. for example bank splits.
+% ofis, varuna, bilkent labı gibi mekanlar aslında önemli. benim malzemelerin büyük kısmını bulduğum yerler. iş bankası mesela. found photos.
+
+Moreover there are other rules that define the frame of collecting act.
+Paper or package must be trash or will be trashed.
+For this project anything must not intentionally bought to use as trash.
+In other words first rule is to consume less and generate less trash.
+Lots of trash is accessible.
+Aim is to reach them.
+
+%[owner of disard]
+"The question of who owns these discards is not trivial" \cite{zimring2012encyclopedia}.
+The answer of it is not trivial and sometimes it makes me uncomfortable because of feeling that stealing that someone elses objects.
+Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
+
+% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
+Trash is also regarded differently, depending on where you live.
+Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
+But when the same student went to Beverly Hills to go through trash, the police were nearly called.
+“Who decides what is public and what is private?
+How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?” Zubiaurre said.
+
+% bırakıldığını nasıl anlıyordum vs.
+
+%[people]
+% Bu kısmın daha güzel anlatılması gerekli.
+% TODO ref.
+As mentioned previously many people contributed to the project by collecting.
+Whenever i meet my friends I ask them to save their discard.
+The importance of collaboration with them can be understood the term "citizen science" which is “defined as scientific research performed in part or in whole by volunteers who are not professional scientists” [REF].
+I need to note that this is not a scientific project but the notion belongs there.
+The value of it lies in the collective intelligence of the contributors.
+In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select.
+When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.
+
+% They provide me the materials to transform it.
+They select the items and find them.
+They bring their approach and selection.
+They are part of the selection of the materials.
+They started to engage with the work.
+People bring the material also wonder the result of it.
+
+% taxi drivers is wonder what will happen? they can not understand the idea here. not only collectors wonder but also people see me in action wonder the reason of it.
+
+The purpose is here not only to transform objects but also change the perceptions of trash. Asking people to collect things and inform them started to shift in peoples mind. For instance
+
+Collected items reflect my and contributors' consumption practices.
+People as mentioned previously consumption patterns can be tracked from their leftover.
+From logos of companies onto the packages reveal people's choices and give clues about their social status.
+
+% TODO What type of activities generates waste.
+% Beyond social status it reveals activities that generate such a waste.
+It can be also extracted that most of the trashed papers are thrown away from feeding activity.
+On the other hand vastness of some types of disposables reveal the dark side of the some enterprises such as Starbucks and Burger King.
+Few people thought that after seeing the project I only collected Starbucks packets.
+There is no such a limitation but as a result of habitat the number of them suppress the others.
+
+[disposable paper, packaging]
+Collected items are mainly disposables ones.
+Most of them are paper or contains paper pulp.
+The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China.
+It is fundamental medium for writing, reading, education, communication, information storage and many others.
+Its role in the development of human civilization can not be neglected.
+(Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people.
+On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage.
+Further it is easy to find and collect them.
+Even if it is thrown out, still appropriate for painting and writing.
+
+% TODO: Free ve accessible olması experiment yapmak için önemli bir yere getiriyor onu.
+
+% [Production, Recycling] \paraphrase{All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
 Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
@@
 It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.
+In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.}
 
-% History of Paper
-The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.
+Since paper is both biodegradable and a renewable resource, it is selected by some of corporation for their products to show their respect to the nature.
+The motivation why they use can be seen their notes printed on the papers.
 
-% Production of Paper
-All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
+[images here.]
 
-% Uses of Paper
-Paper has become the most ubiquitous product in the age of information.
-Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+% meaning of paper for me.
+% TODO buraya bir şey eklenecek.
+Seeing papers on the waste bin is a disappointment for me. As stated by the artist "failure of imagination".
 
-[Why (package) paper?] Easy to collect.
-Easy to find.
-Thrown out even if it is good quality.
-Packaging materials are very widespread.
-Appropriate for painting and writing.
-Has a very short life time.
-Disposable, there are a lot of package outside.
-No need to carry it.
-Every place gives you package paper.
+% [Why do I collect trash?] Herkes neye ihtiyacı var ise onu toplar.
+Ben neden niçin topluyorum?
+Toplama sebepleri?
+Dönüştürme sebepleri.
+Neden sadece toplamakla yetinmiyorum.
+yani toplamak ile ayrıldığı noktalar nelerdir.
+Ben bir mana mı arıyorum?
+Yoksa kaybetmekten mi korkuyorum?
+Yeni kompozisyonlar oluşturmak istiyorum.
+Farklı karşımlar elde etmek istiyorum.
+Bir tür şaşırtmak durumu...
+Beklenmeyeni yapmak...
+En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
 
-%%
-%%
-\item[Collecting.] One of the most found trash in my habitat is paper.
-I work at METU Technopolis, live at 100.
-yil which is the nearest settlement to METU and study at Bilkent.
-People live there commonly use paper and needs paper.
-Paper is nearly everywhere.
-Reusing the paper is not limited with recycling of it.
-There is a another ways of it.
-When we recycle them actually we again send away them and use it as we all know.
-(industrial papers and notebooks.) There is no richness here.
-Same type of paper.
-Produced after a industrial process.
-I collected them from my friends (people that have communicate often).
-Sometimes I collect them from trash bins and roads.
+Collected items are stored in my room. All of they are varies. Most of them are not belong to me. Here the detailed information of the collected materials are listed.
 
-One of the most important parts of the using trash in the artwork (or expressing something, or representation) is to collect them.
-What are the dynamics(considerations) of collecting them?
-(easily accessible materials or unique items.) Where to store them?
-Does it mean that live with trash?
-In other words collecting trash and using them is live with them?
-(making them part of life.) After the being part of the are they still trash?
-Can be thought that it is something that affects the lifestyle.
-(possessions and trash.) Another question is that how differs collecting trash from collecting other things such as objects that have archival value.
-What is the driving force?
-You may collect it to prevent object being lost.
-For archival things what you collect is something that has some sort of social use and meaning which is going to disappear.
-However, trash is never disappearing, even its amount increasing rapidly.
-For archival things people have memories with them, but does some applies for the trash?
-Who wants to keep trash?
-or who wants to re-see(re-visit) trash again (in a museum for example)?
+[kağıt yığını fotoğrafı]
 
-[Organizing People] Well I  actually follow very simple methods.
-I just talk them all.
-I explain what I did, ask for their help.
-Everyone actually approached positively and somehow they contributed the project.
-How does it differ from asking for their help?
-What type of meaning I add here?
+\textbf{Burger King packages} are collected from the office where I work.
+At launch time, some of the colleagues order the meal from Burger King which is a global chain of hamburger fast food restaurants.
+Meals are delivered to the office with paper packages.
+The package of the meal is collected and used as a cover of notebooks.
+Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
+Some people think that it is disgusting because of greasy onto it.
+But immediately I replied them just not you eat that greasy fires so what is wrong with it.
+At that time what Susan Strassed said comes my mind.
+(it fits here)
 
-%%
-%%
-\item[Collected Materials.] There are different papers and objects are used to produce papers.
+Why people throw them away varies.
+Through my experience I can give one anecdote that I encounter frequently.
+When I collect the papers under the dishes or food packages, people often think that it is disgusting and called them as dirty.
+However, it is very strange that the fat on the paper was previously what they are eating.
 
-  \begin{description}
-  \item[Burger King packages] from office at launch time
-  \item[Starbucks packages] from supervisor, office and my friend.
-Especially my supervisor and friend collect them from their friends and their own uses.
-They save them for me and later I take them later.
-  \item[Modshifters papers] that are covered on table and at the end of the day they are cut out and throw away.
+\textbf{Starbucks packages} are collected from my supervisor, office and my friend.
+Especially my supervisor and friend saved and collected them from their friends.
+They are used as a cover of notebooks.
+There are different types of packets from this category.
+for some of them are build from recycled (precisely downcycled) paper, and the others packages for coffee beans.
+they are airtight and waterproof packages very solid and strong.
+and well graphic design with different color and illustration.
+
+\textbf{Modshifters papers} that are covered on table and at the end of the day they are cut out and throw away.
 I go this place many times and every time questioned what they are doing to the papers.
-One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day.
+One of my visit we stay there at a late time and catch the garson collecting the old papers and preparing tables to the next customer or day.
 I ask him to give me and he kindly accepted.
@@
 I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
-  \item[Varuna Gezgin]
-  \item[Graduation banner]
-  \item[Tea bags]
-  \item[Banka sıra fişleri]
-  \item[Elginden gelen kağıtlar]
-  \item[Bilkent kağıtları]
-  \end{description}
 
-%%
-%%
-\item[Experiments.] Starting point is to stack the notebooks onto the each other, and there are some ideas like putting them inside a waste bin to re-do the action of throwing away.
-Again the purpose is to find a way that to shock people, surprise them.
-After ward somehow they should understand that these notebooks can be taken.
-\comment{I set up makets and try some installations of it.
-Take photo it.
-listed them here.}
+\textbf{Varuna Gezgin}, is a cafe. papers of old menus. They are waited to be discarded.
 
-\todo{images are here.}
-
-I imagine a exhibition environment and place notebooks at that place.
-Different placement are tried.
-All of them are look like sculptural.
-I have insert no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
-which I do not want.
-
-% What I tried during this progress: Wrap out the trees, because I think that most of the materials that I collected are package papers.
-Well I somehow package the trees again.
-not to carry them but to raise awareness.
-Yani benim amacımı en iyi anlatacak olan şey nedir?
-Aslında ben burada defterden gidip bunu anlamlandırmaya çalıştım.
-Dolayısıyla deneyerek deftere nasıl ulaştım da ziyade defterden başlayıp nasıl tekrar defterde karar kıldığımı anlatan bir hikaye olabilir?
-Yani bu çok da şart olmayabilir bir diğer yandan da?
-Developlement of work?
-Nasıldı nereye geldi?
-How my project evolved?
-And this also explains how it is relates with the research.
-Because the reasearch is shaped the project also.
-Which part of the project shaped by the project?
-Not thinking in the ecological perspective.
-Raised questions also mature the project?
-For example zizek suggest that to find spirutuality and aesthetics to the trash, and for me?
-
-%%
-%%
-\item[Transforming.] I turned them to notebooks.
-Actually I use it for my self.
-And while I was using of it I am very proud of it.
-I am studying nearly more 20 twenty years and I have always need for notebooks and use them.
-It is some sort of passion for me notebooks.
-Because I always admire notebook beautifully design or uniquely designed.
-I collect them whenever I find and most of the time I only save them for later use.
-
-%%
-%%
-\item[Notebooks.] Actually I have been collecting same materials that are used in my project before the thesis work.
-In my mind there is always belief that I can I find something useful for them.
-(In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork.
-Before the thesis I also produce the notebooks for myself.
-However what is changed in thesis.
-First my approach to the trash is a little bit deeper.
-What is added to the notebooks.
-I started to use also used papers.
-for the cover of the notebook, I use more different materials.
-more close to collage.
-production method changed.
-and I started to collect different things, from different places.
-My realization increased.
-I organized my close friends and others to collect or save their trash for me.
-I discovered some points.
-their differences.
-
-Because I already do it.
-So What I didn't change it.
-It is the best one or no to change it.
-I love idea of carrying notebook with near of you.
-I have also save my notebooks.
-I don't throw away them.
-A notebook is actually is a work of you.
-It carries your signature.
-It is one of best gift to give someone.
-Because it is a combination of your work and the other peoples works.
-It is co-authored work.
-Actually there is also a part of people who throw away this peace.
-Actually the best part of it the transformation is not finishes after my creation of notebook.
-It continues with the usage of it.
-How it turned to is not actually uncertain.
-Therefore it is very appropriate of my idea that transforming trash is increases the diversity.
-
-[What is different from industrial notebooks?] Handmade, from trash.
-an alternative to other versions.
-every one have different stories, they are different in visuals (but the others are also different.) What makes them different is not clear actually.
-Does it have to be different?
-Yes.
-The production method is different.
-You pay no money.
-There is different with gift notebooks from companies.
-This notebooks call to you change the destiny of trash together.
-
-[Why covering notebooks?] They are all package paper, already used as carry things and this work it has used again for the same purpose (but in different connection, this time trash is bound to the notebook).
-Trash is used to cover the papers.
-Cover is the most visible part of the notebook and book.
-Therefore trash becomes most visible part of the produced item.
-What is the function of cover?
-It gives ideas about what is inside, distinguishes from other things, protect it.
-
-%%
-%%
-\item[Exhibition] Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
-
-[Why in the public space?] To reach more audience.
-Actually the audience is out of the art galleries.
-They are walking in the streets.
-Putting them to next to people is much more effective.
-It is not visible and nearly it is hided from society.
-It is dirty.
-Removed from the society.
-There is a effort to hide them away.
-However in this project it is again showed to the society.
-Because it is revisited and reclaimed.
-
-%%
-%%
-\item[Artistic tactics]
-Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.
-
-\end{description}
-
-\section{Parts of project (or final work)}
-The project introduced in this thesis have different parts.
-Each of them are connected to have relation with and support the other.
-Different parts also enable us that different level of integration to the project.
-
-\subsection{Notebooks}
-Mixing materials is main method in the production process.
-I combine different papers and packages.
-I try to generate every possible combination.
-For some of them I establish the connection but for the others the connection is not obvious but it is not obligatory.
-Because trash is state where you can find meaning through the trash or material later.
-
-All package papers are cleaned up. Because it is important that it needs to be safe to use. With mix of water and little bleach they are swabbed.
-
-Here are the name of notebooks and their story:
-
-  \begin{figure}[ht]
-      \centering
-      \includegraphics[width=0.8\textwidth]{project_graphics/banner1.jpg}
-      \caption{Banner}
-      \label{fig:Banner_1}
-  \end{figure}
-
-\begin{description}
-\item[Puzzle.] Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
+\textbf{Graduation banner} Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
 Every piece was a part of bigger banner.
@@
 It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
-\item[12:00 pm.] Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
-\item[08:00 am.] Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
-\item[Friday Night.] (Maybe there can be another option related with traveling, or union).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
+  \caption{Banner}
+  \label{fig:Banner_1}
+\end{figure}
+
+\textbf{Tea bags] are collected from my friend. Their a couple of consumption of tea and their covers.
+
+\textbf{Banka sıra fişleri} my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
+% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili.
+Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life).
+iş bankası örneğinde anlatılabilir.
+bir de art gallery found object örneği verilebilir.
+\textbf{Elginden gelen kağıtlar}
+\textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.
+\textbf{Others} collected items are not limited with these by the remanings are little to open a new category.
+
+as it can be seen here there are various types of paper and most of them some memories for me.???
+
+% NEW PART [transforming]
+%[experiments with paper.]
+
+% TODO sadece defter yapmakla uğraşmadım bşka şeyler de denedim.
+
+% [Artistic tactics] Here I followed some tactics to accomplish my purposes. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+
+% bi de ben bunu insanlara vermek istiyordum o yüzden defter iyi bir şey.
+ve bu benim aslında bir taktiğim arkadaş.
+defter insanın yanında taşıdığı kullandığı bir şey.
+sadece galeri de olmayan başka alanlara da sızan bir şey olması önemli.
+
+% sadece belli bir yerde geösterile bir şey olmayıp yayılan, insanlarla birlikte hareket eden bir şey olmasını istiyorum.
+
+At one side while paper is being collected, on the other side I started to make experiments with the material.
+I questioned what else can be made with these collected materials and tried to cover (wrap out) objects and plants in the public.
+However these do not give the result what I want.
+People cannot interact with these and possibly they will turn to trash again.
+For that reason the first approach which is making notebooks are more appropriate to accomplish the purpose.
+
+[IMAGE experiments with trees.]
+
+Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memoranda by many artists, scientists, and thinkers through the ages.
+Further same exist for me and people around me.
+Although the digital alternatives of it paper maintains its place in the community.
+
+% TODO notebook hakkında daha fazla şey söylebilmelisin tamam?
+
+Through this project handmade notebooks are produced from discarded paper.
+They are impure, imperfect and different than usual industrial notebooks.
+They still carry the traces of previous usage.
+Every one of them have different stories.
+Combination of various pieces offer new interpretations of writing.
+
+There are different types of notebooks regarding their color, shape, size and combination.
+They are simple, imperfect and different than usual industrial notebooks, but more importantly they are from trash.
+Every one of them has a unique serial and with that serial the (hi)story of it can be viewed.
+
+% [notebooks]
+Papers that are mostly blank(empty) are used inside of the notebooks for writing.
+Others that are solid and colorful are used as a cover for notebooks.
+Mixing (juxtaposing) materials is main method in the production process.
+I combine different papers and packages.
+I try to generate every possible combination.
+The purpose is to create as many alternatives as I can because trash is ignored and people do not give it new alternatives.
+Therefore these notebooks provide many alternatives to show that otherwise is possible.
+
+Technically papers combined together by sewing and gluing.
+I learned sewing techniques from my mother and the gluing part is trivial.
+For this project I need to produce dozens of notebooks.
+However through time I started to produce them more rapid by improving my technique.
+One of the struggles that I faced is to punch holes with needle.
+At this process I cracked a needle.
+Later I discovered that with the help of pushpin punching the holes becomes more easy.
+After punching holes I just followed the holes with needle.
+I used nylon yarn which is solid and thin.
+Being thin is important it must fit into the opened holes.
+After sewing them I fixed the yarn with hole by gluing to make it more solid.
+
+% TODO starbucks defterlerinin hep yapıştırılmış olmasını da eklemek gerekli.
+
+% TODO muhakkak tekrar kontrol etmek gerekli.
+Size of the paper used inside of the notebooks are mostly equals to the size of an A4 sheet.
+Usage of papers differs among the notebooks.
+Especially for the papers taken from Varuna Gezgin written part is folded inward by hiding it.
+However for the ones collected from Bilkent Computer Laboratory written side of it leaved open.
+Their content comes from various students whose departments are also various.
+In other words offers great diversity and they are mixed to allow different interpretations.
+Further it provides what students from other departments works on.
+% What other students work on.
+
+% TODO Dimensions of notebooks. most of them half of A4 or quarte of it. böyle bir fotoğraf eklenmeli. farklı boyutlarda farklı şekillerde ve renklerde.
+
+% TODO sabahleyin bir fotoğrafını çek bunların.
+
+% TODO defterin yakından fotoğrafları
+
+% TODO kullandığım malzemelerin listesi olabilir. fotoğraf çok fazla olur.
+
+Moreover I have reviewed other notebook projects.
+Notable ones are The Sketchbook Project and myDetour from Moleskine.
+In these projects anyone who bought the notebooks from them can participate and send their notebooks filled with illustrations and paintings.
+These projects can be seen as crowd-sourced library.
+Further the pages of the notebooks are available at online.
+After checking sketches in these notebooks, the diversity of them surprised me a lot.
+It forced me think that the transformation process is not limited with the production of notebooks from trash.
+After notebooks are given to the people, their transformation will continue.
+Therefore I think the process of transformation is a continuous act.
+% amaç çeşitliliği arttırmak olduğu için
+
+% TODO siteye nasıl karar verdin la?
+
+% [showing]
+% [Exhibiting experiments] main question id how to give them to people?
+After producing notebooks the most important point is to present and reach to people.
+Starting point is to stack the notebooks onto the each other, and there are other ideas like putting them inside a waste bin to re-do the action of throwing away.
+After ward somehow they should understand that these notebooks can be taken.
+I set up makets and tried some installations of them.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
+        %\caption{Sax}
+        \label{fig:exhibition1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
+        %\caption{Violin}
+        \label{fig:exhibition2}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
+        %\caption{Violin}
+        \label{fig:exhibition3}
+    \end{subfigure}
+    \caption{Installation try outs}
+    \label{fig:exhibition}
+\end{figure}
+
+They were early interpretations and ideas.
+I imagined an exhibition environment to place notebooks.
+Different placements were tried.
+All of them looked like sculpture.
+I have inserted no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
+which I do not want.
+
+Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
+
+% Bu örnekle insanlara daha fazla yakın olmam gerektiğini gösterdi bana. onların ayaklarına bu proje gitmeliydi. ziyaret ettikleri bir yerde olmalıydım.
+
+% [Why in the public space?] To reach more audience.
+Actually the audience is out of the art galleries.
+They are walking in the streets.
+Putting them to next to people is much more effective.
+It is not visible and nearly it is hided from society.
+It is dirty.
+Removed from the society.
+There is a effort to hide them away.
+However in this project it is again showed to the society.
+Because it is revisited and reclaimed.
+
+% TODO [Why giving away?] Felix Gonzales Torres, Unlimited Editions.
+% TODO insanlar bu defterleri alsınlar.
+
+%
+%
+\section{Parts of project (or final work)}
+% TODO la olum bir önceki kısımla bir ilişki kur istersen ha?
+The project introduced in this thesis have different parts. Each part support the other. They are connected with each other. Different parts lead different inqueries.
+
+%
+%
+\subsection{Notebooks}
+
+% TODO defterle ilgili şeyleri buraya taşı. hepsi belli seriler ve isimler altında toplandı. bu seriler onların nasıl oluştuklarına dair ip uçları veriyor.
+
+Every notebook has numbers and with this numbers it can be tracked down when it was produced and which materials are used production of it.
+
+There are notebook series that have a name. Here are the name of notebooks and their story:
+
+\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner.
+As mentioned previously the objects are bring their history.
+They are not blank.
+Heterogen, hiybrid.
+It can be one of the examples of this argument.
+
+\textbf{09:00 am.} Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+
+\textbf{12:00 pm.} Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+
+\textbf{Friday Night.} (Maybe there can be another option related with traveling, or union).
 These notebook's pages are collected from restaurant "Varuna Gezgin".
@@
 I took some of the papers, and that papers are part the sheets of these papers.
+
 % Name of the paper can be related with this place and related with the meaning.
-% Again I need some memory from here. 
-% They are all my memories actually and I also turn my memories something different. Changing and constructing memories. And also others' memories... These project also contains others memories.
 
-% Ersan hoca's packages.
-Elgins' papers etc.
-I do not know actually their stories.
-Maybe I can dream up stories for them.
-Creating histories from some of the trashes.
-They do not have proper memory with me, but I tried to construct memories, (fake memories can be said that.)
+% Refer to 9 canlı.
+Never dies, revives again and again.
+Because trash moves in the community, even if thrown away can be find another use.
+Ikinci kez degilde ucuncu kez kullanilan bir sey olursa aslinda onkara dokuz canli demek istiyorum.
+Gorunus acisindan farkli olmasalar da aslinda isin farkli yanlarini gormek icin faydali olabilirler.
 
-% Refer to 9 canlı. Never dies, revives again and again. Because trash moves in the community, even if thrown away can be find another use.
+% 9 canlı (cat) / puzzle / bir de dada kelimesi. 9 canlı olmanın kaynağı neresi abi..
 
-\end{description}
+% Maybe Later
+% Counter Argument:
+% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
+Here there are available different answers to the question.
+Firstly they are different once they are designed.
+Turned to different thing.
+I suggest that them to consider in different context like Duchamp.
 
+%
+%
 \subsection{Exhibition}
@@
 
-\begin{description}
-\item[Library.] The reason why select library is there are small papers to write down the location of books.
+\textbf{Public space.} The reason why select library is there are small papers to write down the location of books.
 Libraries are places that things are reused.
@@
 Public space.
-\todo[inline]{problematic because of resusing. actually is sharing.}
-Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor. 
-\item[Torun.] as an alternative place?
-\end{description}
+It is place that students from different department use the same place.
 
+% Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor.
+
+% TODO bir çok insanın ortaklaşa kullandığı bir alan. kesişim alanı. bir tanesi de özellikle zaten toplanan yer. insanların karşılaşmalarını istiyorum. karşılaşma noktası.
+
+% Selected places are frequently visited by people. Shared places.
+
+% TODO  [Yerleştirme fotoğrafları]
+
+\textbf{Alternative art space.}
+
+bu işin alternatif bir yer olduğunu düşünürken de aslında nasıl bir alternatif olduğuna torun örnek olabilir.
+
+From another point exhibiting it from a art fallery which is different.
+
+Torun describe itself as a place for free place for sharing art. Open to everybody. Makes open call to the others. Middle of the house.
+
+People can take with them.
+
+Özgür ortam, kamera yok, evlerin arasında.
+
+[IMAGES of torun]
+
+%
+%
 \subsection{Website}
-As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place peoples life again, it also finds another place in the digital space. ()
+As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.
 
-Mainly websites displays the story(History) of notebooks.
-Also it is a place to track the journey the notebooks.
+Mainly websites displays the (hi)story of notebooks.
+Further it is a place to track the journey the notebooks.
 As I claimed that it is not a finished work.
@@
 
-% I add the screenshoots of website. Also the development of it. Sketches of website. Navigation of it. User interaction. Use cases and actions. Functionalities.
+SketchBook Project is also inspired me a lot especially in terms of website.
+This project provides a platform to people in order to share their works with other people.
+It contains lots of works from all over the world.
+Full of creativity and showcase of richness of people's expressions on the small notebooks.
+My work can be considered as a sketch book project through trash.
+Sketches or only creative progress is not the only consideration.
+You can send your lecture notes.
 
-% Documenting the progress.
+% [Why website] (database, establishing communication, tracking in time) It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in coding and web development.
 
-% It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing photography
+to record and make it available available to the public.
 
-% Counter Argument:
-% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
-Here there are available different answers to the question.
-Firstly they are different once they are designed.
-Turned to different thing.
-I suggest that them to consider in different context like Duchamp.
+It is placed different locations and the pass the proggress of project is limited in time and place.
+In particularly through the small boxes placed to the libarary.
+Therefore website can provide a solution for this.
 
-% I resurrect things that have been killed off...
-My work is all about the potential of materials — even when it looks like they've lost all possibilities.
-(Cornelia Parker) https://en.wikipedia.org/wiki/Cornelia_Parker
+Ben insanlarin ayagina gitmeyi dusundum. This project is placed where people frequently visit.
 
-% These all memories and collected materials related with the my history.
-So why is it important for the other people.
-What can they found my memories.
-This is not theirs.
-How other people connect to the topic.
-They important for me but also I need to find something important for the other people.
-For example modshifter and varuna gezgin is one of them.
-This not only my experience.
-Some kind of shared memories and histories.
-What will find people in these notebooks.
+The aim of this project is to work on website.
+Website is a supportive element of it.
+Therefore I only briefly mention the technical details of website.
+Common and trusted open source technologies are selected.
 
-%****************************************
-% TODO Find a solution for this problem:
-% Bu işin olması için ben insanlardan bir şeyler yapmalarını istiyorum.
-Yani aslında kendimde yapabilirim ama neden insanları da dahil ediyorum?
-Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de deönüştürmek gerekmek.
-ve bu bir süreç işi (şart mı tek bir yöntem bu mu?) İnsanlar nasıl değişir diye sormak gerekir o zaman.
-İnsanların değiştiğini dönüştüğünü gerçekten nasıl ölçeceğim ki?
+Served from github pages. Images are are sefved from dropbox.
 
-% important question: herkes neye ihtiyacı var ise onu toplar.
-ben neden niçin topluyorum.
-toplama sebepleri.
-dönüştürme sebepleri.
-neden sadece toplamakla yetinmiyorum.
-yani toplamak ile ayrıldığı noktalar nelerdir.
-Ben bir mana mı arıyorum?
-Yoksa kaybetmekten mi korkuyorum?
-Yeni kompozisyonlar oluşturmak istiyorum.
-Farklı karşımlar elde etmek istiyorum.
-Bir tür şaşırtmak durumu...
-Beklenmeyeni yapmak...
-En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
+Website can be accessible through the this address http:\\kulü.be\notebook-project. Domain name kulü.be belongs to me and roject placed under a directory of it.
 
-%
-% PROBLEM:
-% In theoratical part I am focusing on actually the trash.
-But should I focus on paper trash?
-Is there any difference?
-Ya da ben oradaki bir farklılıktan besleniyor muyum?
-It is not totally paper, actually they are package.
-Examples can be given related with package material.
-It has a very short life.
-Not short actually.
+Technical information.
+Website is coded by me with the open source libraries and frameworks.
+Its code also available at this address.
+Site is hosted by github which is code repository.
+Pages are generated by jekyll which is a static website generatir through it som repetive works are can be easily automobized and modilarized.
 
-% How to establish the relationship between the collaboration and the trash?
-transforming them with the help of people.
-However, main discussion is not about collaboration.
-Here collaboration is a method to reach the aim of the project.
-In other words it is a methodology.
-There are different methodologies applied by artist to transform them.
-My methodology is to collaborate with the other people.
-My aim is to transform trash with people.
-Also make them to engage with trash.
-Trash is only one of the things discarded by the society.
-What is the importance of co-authored work?
-%........................................
+Content of website.
+
+Functionalities of website.
+
+Future works.
+
+Users or visitors can see the notebook series is made. Each notebook serie has a detailed explanation. It can be viewed at there.
+
+It can accessible through the internet. Richer media. Covergence of analog and digital media.
+
+People can access to images and descriptions of notebooks. All the development process of the project will be revealed in this website. Will contain list of collected materials.
+
+From one point of view it can bee seen that website function visitors book.
+
+Components of website:
+- Images of notebooks. 
+- Descriptions of notebooks.
+- Collected materials.
+- Comment and sharing.
+- subscribing to email.
+- hastag ile filtreleme.
+
+- event photos.
+- event announcement.
+- videos.
+- essays, writings, related word. content related with this topic.
+
+framework to analyze the work.
+
+This thesis and presentation will also be added to the website.
+
+adding different dimension to the project.
+
+% seri numbers and the name of notebook are written inside of the notebooks. How this numbers are given.
+
+Into the notebooks a sticker which contaons qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.
+
+[qr image]
+
+If someone share their work through social networks it betracked and can be viewed in the website. Social networks. Entegration with them.
+
+People can be abke to add their comment to the website. How they are using their notebooks will be showed through it.
+
+People can be able to subscribe to the newsletter to get updates about the project.
+
+Tum bu yapilanlarin uzerine gene de yapilabilecekler var. Kisaca bunlardan bahsetmek istiyorum.
+
+Websitesi ozellikle proje ileride devam edebilsin diye tasarlandi.
+
+In the future all the discussions and research can be moved to the website that people get reach more information about the subject.
+
+Website will function as a platform to get into touch with people. People leave their comments.
+
+The project will be continued after thesis project.
+New features can be added to the website.
+New events can be held.
+All the progress up to now forms the core of the project.
+In the future it is planned that through the website people can be able to request to get notebooks.
+Thus project becomes more accessible to the othse people.
+Moreover notebooks done by others from trash can be added to the website.
+Beyond notebooks various objects transformed from trash can find a place.
+
+% MAYBE LATER
+% trasnformation practices...
+% Notebooklar insanın yanında kolayca taşınabildiği için aslında bir yandan fikri yaymak için ideal. Zaten showing off'un ne kadar önemli olduğu rubbish theoryde söylenmişti.
+
+% MAYBE LATER
+% [Standartlar, Dönüştürme seviyesi] endüstriyel standartlar, kaplar ve kağıtlar hep bir şekilde bir birleriyle boyut olarak uyuşuyorlar.
+İlk başlarda kesip biçmeye daha çok ihitiyaç duyarken zamanla basit katlamalar işimi görmeye başladı.
+Ne kadar az müdahele bulunursam aslında o kadar çok geldiği yerin özelliklerini o kadar çok temsil ediyordu.
+Bu da benim hoşuma gidiyordu.
+Kolaj mantığı işte abi.
+Ne kadar çok değiştirmek dönüştürmek istiyorsun.
+Burda şöyle bir durum var.
+çöpleri hiç tanınmayacak bir hale de getirebilirsin.
+Bu şekilde kimse onların farkına bile varmaz.
+Ya da neredeyse olduğu gibi kullanırsın.
+Yani uygulanan dönüştürmenin derecesi çok önemli burada..

### 2015-12-29 main.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

@@
 
+% Figure and Table counters
 \usepackage{chngcntr}
@@
 Prof. Dr. Mehmet Yılmaz\\
-Examining Commitee Member\\
+Examining Committee Member\\
 
@@
 Instructor Ekin Kılıç\\
-Examining Commitee Member\\
+Examining Committee Member\\
 
@@
 \thispagestyle{plain}
+\phantomsection
 \addcontentsline{toc}{chapter}{ABSTRACT}
@@
 This approach has broken the existing rules and extended the language of art in an unprecedented way.
-After that point, trash has found a place in the work of artists \comment{(and their expression)}.
+After that point, trash has found a place in the work of artists.
 
-The purpose of this study is to discuss transformation (or usage) of trash in the context of (art and) artistic act.
-It is questioned that the role of art in the transformation of discarded items.
-Approaches and methodologies of artists who use discarded materials in their works are explored.
-This thesis follows the discussions of the place of trash in culture and theories of trash.
+The purpose of this study is to discuss usage of trash in the context of art.
+The role of art is questioned in the transformation of discarded items.
+This thesis follows the discussions on the place of trash in culture and theories of trash.
 Then approaches and methodologies of artists who use discarded materials in their works are explored.
-\comment{Usage of discarded materials in the artwork by the contemporary artist are studied through their works.} It is questioned that why and how they use discarded materials and how artworks can be understood regarding theoretical and cultural aspects.
+It is questioned that why and how they use discarded materials and how their artworks can be understood regarding theoretical and cultural aspects.
 
-Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act.
+Within this framework, thesis project argues that it is possible to see the process of transforming trash as an artistic act.
 In the scope of the project, discarded papers are collected with the help people and transformed to notebooks.
 Progress and collected items are recorded on a website.
-Notebooks are installed in different locations in order to invite people to use trash again.
+Notebooks are installed in non-conventional locations such as library desks and computer labs in order to invite people to use trash again.
 
-\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
+\noindent Keywords: Transformation of Trash, Trash in Art, Trash as an Art Material.
 \clearpage
@@
 \selectlanguage{turkish}
+\phantomsection
 \addcontentsline{toc}{chapter}{ÖZET}
@@
     \vspace{\baselineskip}
-    \MakeUppercase{Sanatsal Bir Eylem Olarak Çöpü Dönüştürme}\\
+    \MakeUppercase{Sanatsal Bir Eylem Olarak Atığı Dönüştürme}\\
     İlhan, Mustafa\\
@@
 \singlespacing
-\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
+\par Sanat işlerinde sanat dışı nesnenin kullanımı 20.
+yüzyılın başına kadar takip edilebilmektedir.
+Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir.
+Bu noktadan sonra atık sanatçıların işlerinde yer bulmuştur.
+
+Bu çalışmanın amacı sanatsal bağlamda atığın kullanımını tartışmaktır.
+Atık ürünlerin dönüştürülmesinde sanatın rolü işlerinde atık maddeleri kullanan sanatçıların yaklaşımları ve yöntemleri üzerinden sorgulanmıştır.
+Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır.
+Sanatçıların neden ve nasıl atık malzemeleri kullandıkları ve işlerinin kültürel ve kuramsal açılardan nasıl anlaşılabileceği sorgulanmıştır.
+
+Bu çerçevede, tez projesi atığı dönüştürme sürecinin bir sanatsal eylem olarak görülebileceğini savunmaktadır.
+Proje kapsamında atık kağıtlar insanların yardımıyla toplanıp not defterlerine dönüştürülmüştür.
+Süreç ve toplanan ürünler bir web sitesinde kayıt altına alınmıştır.
+İnsanların atığı tekrar kullanmaya davet etmek amacıyla defterler sık ziyaret edilen kütüphane, bilgisayar laboratuvarı gibi ortak kullanım alanlarına yerleştirilmiştir.
+
+%\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
 Ya da en azından proje kapsamında üretilen işin.
@@
 
-Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır.
+% Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır.
 Çöpün kültürel ve kuramsal olarak nasıl ele alındığı(alınabileceği) araştırılmıştır.
@@
 
-\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
+%\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
 Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
@@
 
-\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
+%\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
 Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
@@
 
-Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
+%Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
 Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
@@
 
-Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
+%Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
 Bu atık maddeler dönüştürülerek defter yapılmıştır.
@@
 
-\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
+\noindent Anahtar Kelimeler: Atığın Dönüştürülmesi, Sanatta Atık, Sanatsal Malzeme olarak Atık.
 \clearpage
@@
 \thispagestyle{plain}
+\phantomsection
 \addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
@@
 \end{center}
-\par First and foremost, I would like to thank to my thesis supervisor Ersan Ocak for his continuous patience, support, encouragement and immense knowledge that he shared with me through the entire process.
-I cannot imagine having a better advisor for both this written thesis and the project I conducted.
-I also would like to thank the rest of my thesis committee; Mehmet Yılmaz and Ekin Kılıç for their motivation and insightful comments.
+\par First and foremost, I would like to thank to my thesis supervisor Assist.
+Prof.
+Dr.
+Ersan Ocak for his endless patience, support and encouragement through the whole progress.
+He contributed in every way he can and guided me through the development of this thesis with his immense knowledge.
+I also would like to thank the rest of my thesis committee; Prof.
+Dr.
+Mehmet Yılmaz and Instructor Ekin Kılıç for their valuable contributions and insightful comments on the issues of this thesis.
+
+I am grateful for Assist. Prof. Dr. Marek Brzozowski, Assist. Prof. Dr. Andreas Treske and Assist. Prof. Dr. Ahmet Gürata for their valuable ideas and criticisms.
+
+I would like to thank my colleagues; Mert Aslan and Eda Erdem for their friendship and comments.
+
+I must thank to Melis Golar and Cemil Batur Gökçeer from Torun for opening their space to my project.
+
+I would like to thank my bosses and colleagues from Mobilus; Özgür Deniz Önür, Yağız Yaşaroğlu, Ekin Dino, Ayşegül Yaşaroğlu, Süleyman Yıldız and Aytaç Kocaman for their support, trust and sharing their discard with me.
+
+I am grateful to M.
+Elgin Akpınar, Nihan Özdemirler, M.
+Cem B.
+Üstündağ, B.
+Ceren D.
+Üstündağ, Ayşenur Durgut, Emrah Şamdan, Duygu Ç.
+Şamdan, Ali from METU Technopolis İş Bank Office, Aykut from Modshifters and Varuna Gezgin for collecting and sharing their discard with me.
+
+Lastly and mostly, I would like to thank my family for their love, trust and support from the very beginning of this work. 
 \clearpage
@@
 % TABLE OF CONTENTS
-\addcontentsline{toc}{chapter}{Table of Contents}
+\phantomsection
+\addcontentsline{toc}{chapter}{TABLE OF CONTENTS}
 
@@
 \renewcommand\cftchappagefont{\mdseries}
-\renewcommand{\cftchappresnum}{Chapter\space}
+\renewcommand{\cftchappresnum}{CHAPTER\space}
 \renewcommand{\cftchapaftersnum}{:}
@@
 \setlength{\cftaftertoctitleskip}{3\baselineskip}
-\setlength{\cftchapnumwidth}{5em}
+\setlength{\cftchapnumwidth}{7em}
 %\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}
@@
 % LIST OF FIGURES
-\addcontentsline{toc}{chapter}{List of Figures}
+\phantomsection
+\addcontentsline{toc}{chapter}{LIST OF FIGURES}
 
@@
 %****************************************
-% LIST OF FIGURES
-%\addcontentsline{toc}{chapter}{List of Tables}
+% LIST OF TABLES
+%\phantomsection
+%\addcontentsline{toc}{chapter}{LIST OF TABLES}
 %\listoftables
@@
 % BIBLIOGRAPHY
-\addcontentsline{toc}{chapter}{Bibliography}
+\nocite{*} % Add all references
+\phantomsection
+\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
 \bibliographystyle{apacite}
@@
 \begin{appendices}
+\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
 \include{appendix_glossary}
+\include{appendix_materials}
+\include{appendix_project}
 \end{appendices}

### 2015-12-29 chapter3_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7

@@
 
-Using non-art object can be considered as moving away from the purification of art \todo{ref req}.
+Using non-art object can be considered as moving away from the purification of art.
 It is a composition of different fragments and pieces.
@@
 Further there is a cut out lemon painted onto the table.
-\paraphrase{The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.
-This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.}
+The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.
+This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
 
@@
 
-\paraphrase{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998).
-Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}
-
 %How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
@@
   \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
-  \caption{Dick Jewell}
+  \caption{Dick Jewell, Found Photos, 1978}
   \label{fig:DickJewell_FoundPhotos}
@@
   \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-  \caption{Road Kill by Filomena Cruz}
+  \caption{Filomena Cruz, Road Kill, 2014, Photography}
   \label{fig:FilomenaCruz_RoadKill_ReVista}
@@
   \centering
-  \includegraphics[height=8cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
-  \caption{Vic Muniz, Pictures of Garbage}
+  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
+  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
   \label{fig:VicMuniz_PicturesOfGarbage}
@@
 Dictionary meaning; something constructed using whatever was available at the time.
-\paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
+\quotes{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
 It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.
+\citep{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.
 
-\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
+\quotes{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
 
@@
 Or vice versa.
-She probably use trash to provocate social elite of that time.
+She probably use trash to criticize social elite of that time.
 
@@
   \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
-  \caption{Kim Alsbrooks, The White Trash Series}
+  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
   \label{fig:Alsbrooks}
@@
   \centering
-  \includegraphics[height=7cm]{graphics/MichaelLandy_ArtBin.jpg}
+  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
   \caption{Michael Landy, Art Bin}
@@
 
-Examples are not limited with these. Even if \paraphrase{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
+Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
 

### 2015-12-29 chapter4_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7

@@
 It is considered as useless and disgusting.
-Contrary to the common approach as Michael Thompson, author of the book Rubbish Theory, stated "one man's trash is another man's treasure".
+Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.
 
@@
 It has a value and part of our games and indispensable source of fun.
-The notion of playing with it can be related with the Picasso's collage -"Still Life with Chair Caning"-- mentioned previously.
-He pasted letters of the French word "JOU" means "game" signifying that playing with the materials.
+The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously.
+He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials.
 We were already playing with trash while we were child.
-Therefore, it can be better understand that while Picasso said that "every child is an artist".
+Therefore, it can be better understand that while Picasso said that \quotes{every child is an artist}.
 
@@
 I remember clearly that she suggested that same for us.
-"Do not throw out packages, look for the useful parts and keep them to use later." Whenever I am going to throw something away, this comes to my mind.
+\quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind.
 Can it be reused?
@@
     \centering
-    \begin{subfigure}[b]{0.47\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
-        \caption{Sax}
-        \label{fig:landfill_harmonic-sax}
+    \begin{subfigure}[b]{0.30\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.47\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
-        \caption{Violin}
-        \label{fig:landfill_harmonic-violin}
+    \begin{subfigure}[b]{0.30\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
     \end{subfigure}
-    \caption{Examples of previous works}
-    \label{fig:animals}
+    \begin{subfigure}[b]{0.30\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
+    \end{subfigure}
+    \caption{Examples of early works}
+    \label{fig:EarlyWorks}
 \end{figure}
-
-[image of previous works.]
 
@@
 % NEW PART [collecting] 
-Collecting discarded objects has carried out through the efforts of mine and people around me.
-Lars Eighner's instructions helped me a lot when collecting objects.
-He writes that "Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question 'Why was this discarded?'".
-[SUSAN STRASSER p6] I applied these instructions to my case and I checked some points regularly and seeked the reason of why was it discarded.
-Details will be given later for each objects.
+Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
+\begin{singlespace}
+\begin{quote}
+Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
+\end{quote}
+\end{singlespace}
+I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.
 
@@
 %[owner of disard]
-"The question of who owns these discards is not trivial" \cite{zimring2012encyclopedia}.
-The answer of it is not trivial and sometimes it makes me uncomfortable because of feeling that stealing that someone elses objects.
+\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}.
+This question makes me uncomfortable because of feeling that stealing that someone elses' objects.
 Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
@@
 % http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
-Trash is also regarded differently, depending on where you live.
+%Trash is also regarded differently, depending on where you live.
 Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
@@
 Whenever i meet my friends I ask them to save their discard.
-The importance of collaboration with them can be understood the term "citizen science" which is “defined as scientific research performed in part or in whole by volunteers who are not professional scientists” [REF].
+The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}.
 I need to note that this is not a scientific project but the notion belongs there.
@@
 When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.
+
+It can be viewed as a co-authored work.
+Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them.
+After production of papers I also want them to continue as co-authored process.
+In other words many people will be part of this project.
+As people see different things on objects and bring them to me.
+the variety of things is increased in time.
+Because people sad me that \quotes{I thought that you can use it.
+Do you collect also these?}.
+After that time I want to continue as so.
 
@@
 
-[disposable paper, packaging]
+%[disposable paper, packaging]
 Collected items are mainly disposables ones.
@@
 
-Since paper is both biodegradable and a renewable resource, it is selected by some of corporation for their products to show their respect to the nature.
-The motivation why they use can be seen their notes printed on the papers.
+Since paper is both biodegradable and a renewable resource, it is preferred by some of corporations for their products to show their respect to the nature.
+The motivation why they use can be seen their notes printed on the papers (Figure \ref{fig:NoteOnPackage}).
 
-[images here.]
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
+  \caption{Recycling notice on the package}
+  \label{fig:NoteOnPackage}
+\end{figure}
 
@@
 % TODO buraya bir şey eklenecek.
-Seeing papers on the waste bin is a disappointment for me. As stated by the artist "failure of imagination".
+%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.
 
@@
 
-[kağıt yığını fotoğrafı]
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
+  \caption{Collected materials}
+  \label{fig:CollectedAllTogether}
+\end{figure}
 
@@
 The package of the meal is collected and used as a cover of notebooks.
-Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
+
+%Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
 Some people think that it is disgusting because of greasy onto it.
@@
 
-\textbf{Tea bags] are collected from my friend. Their a couple of consumption of tea and their covers.
+\textbf{Tea bags} are collected from my friend. Their a couple of consumption of tea and their covers.
 
-\textbf{Banka sıra fişleri} my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
+\textbf{Order slips} are collected from bank office my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
 % [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili.
@@
 bir de art gallery found object örneği verilebilir.
+
 \textbf{Elginden gelen kağıtlar}
+
 \textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.
+
 \textbf{Others} collected items are not limited with these by the remanings are little to open a new category.
 
-as it can be seen here there are various types of paper and most of them some memories for me.???
+%as it can be seen here there are various types of paper and most of them some memories for me.???
 
@@
 
-[IMAGE experiments with trees.]
-
-Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memoranda by many artists, scientists, and thinkers through the ages.
-Further same exist for me and people around me.
-Although the digital alternatives of it paper maintains its place in the community.
-
-% TODO notebook hakkında daha fazla şey söylebilmelisin tamam?
-
-Through this project handmade notebooks are produced from discarded paper.
-They are impure, imperfect and different than usual industrial notebooks.
-They still carry the traces of previous usage.
-Every one of them have different stories.
-Combination of various pieces offer new interpretations of writing.
-
-There are different types of notebooks regarding their color, shape, size and combination.
-They are simple, imperfect and different than usual industrial notebooks, but more importantly they are from trash.
-Every one of them has a unique serial and with that serial the (hi)story of it can be viewed.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
+    \end{subfigure}
+    \caption{Experiments with collected paper}
+    \label{fig:ExperimentWithPaper}
+\end{figure}
 
@@
     \end{subfigure}
-    \caption{Installation try outs}
+    \caption{Installation experiments with models}
     \label{fig:exhibition}
@@
 
-% TODO defterle ilgili şeyleri buraya taşı. hepsi belli seriler ve isimler altında toplandı. bu seriler onların nasıl oluştuklarına dair ip uçları veriyor.
+% TODO notebook hakkında daha fazla şey söylebilmelisin tamam?
+
+Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memoranda by many artists, scientists, and thinkers through the ages.
+Further same exist for me and people around me.
+Although the digital alternatives of it paper maintains its place in the community.
+
+Through this project handmade notebooks are produced from discarded paper.
+They are impure, imperfect and different than usual industrial notebooks.
+They still carry the traces of previous usage.
+Every one of them have different stories.
+Combination of various pieces offer new interpretations of writing.
+
+There are different types of notebooks regarding their color, shape, size and combination.
+They are simple, imperfect and different than usual industrial notebooks, but more importantly they are from trash.
+Every one of them has a unique serial and with that serial the (hi)story of it can be viewed.
+
+% Meaning of stories behind the process
+There are different stories behind the objects.
+I try to record their stories (by photography and taking notes) but some of them were not possible.
+However I still use them in the work because even if I missed their story, with their materiality reveals their history.
+It still has a history but needs to rewritten.
+Maybe forgetting all the history maybe creates different notebook.
 
@@
 
-\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner.
+\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (Figure \ref{fig:Banner_1}).
 As mentioned previously the objects are bring their history.
@@
 \subsection{Exhibition}
-Especially it is the most hard topic in the development of the thesis. To find a place for the notebooks is great issue for me?
+Especially it is the most hard topic in the development of the thesis. To find an appropriate place for the notebooks is great challenge for me.
 
@@
 
+Notebooks are places where people frequently visit such as computer desks.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
+    \end{subfigure}
+    \caption{Example placement at Bilkent}
+    \label{fig:ExperimentWithPaper}
+\end{figure}
+
 % Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor.
@@
 
-\textbf{Alternative art space.}
+Through this project another exhibition alternative is thought.
+In the notable museums and art galleries there are gift shops that people can buy souvenirs.
+Often they are mass produced imitations and replicas of well-known artists work embedded various objects such as cover on the notebooks.
+At this point I image an art space you can buy these types of items freely.
+In other words alternative to the existing approach this types of gadgets.
+Another alternative interpretation can be giving away different that the industrial items such as notebooks from trash as in my project.
+For this type of approach Torun is a great place to show my notebooks and give them away.
+Torun describe itself as a place for free place for sharing art.
+Open to everybody.
+Makes open call to the any artist.
+There are no security cameras on this gallery therefore no one is watching you at there.
+This idea shared with Torun and they accepted it.
+However Torun will opened after 14th of the January currently I just took some photos at there.
 
-bu işin alternatif bir yer olduğunu düşünürken de aslında nasıl bir alternatif olduğuna torun örnek olabilir.
-
-From another point exhibiting it from a art fallery which is different.
-
-Torun describe itself as a place for free place for sharing art. Open to everybody. Makes open call to the others. Middle of the house.
-
-People can take with them.
-
-Özgür ortam, kamera yok, evlerin arasında.
-
-[IMAGES of torun]
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
+    \end{subfigure}
+    \caption{Example placement at Torun}
+    \label{fig:ExperimentWithPaper}
+\end{figure}
 
@@
 \subsection{Website}
-As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.
+As I think that finding a place to the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.
 
@@
 As I claimed that it is not a finished work.
-It does not completed transformation.
+Transformation of it does not completed.
 It always continues.
-Therefore a website that anyone can reach share their progress via website.
-Anyone can later discover how they turned to new things etc.
+Therefore a website that anyone can reach and share their progress via website  Anyone can later discover how they turned to new things.
 
-Collect peoples comment with this notebooks.
-As I leave notebooks different places I do not have connection with people who take them.
-This website also will help to collect/share peoples ideas about the notebooks.
+As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.
 
-It will contains a section for how notebooks are produced and the story behind it.
+It will contain a section for how notebooks are produced and the story behind it.
 The purpose is to record the creative process and share with the others.
@@
 
-\textbf{Why website?} Maybe you can think that there are different methods to accomplish recording and sharing the process.
+Maybe it can be thought that there are different methods to accomplish recording and sharing the process.
 In a gallery on a single table or a room it can be succeed.
@@
 
-% Meaning of stories behind the process
-There are different stories behind the objects.
-I try to record their stories (by photography and taking notes) but some of them were not possible.
-However I still use them in the work because even if I missed their story, with their materiality reveals their history.
-It still has a history but needs to rewritten.
-Maybe forgetting all the history maybe creates different notebook.
-
-It is also co-authored work.
-Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them.
-After production of papers I also want them to continue as co-authored process.
-In other words many people will be part of this project.
-As people see different things on objects and bring them to me.
-the variety of things is increased in time.
-Because people sad me that \quotes{I thought that you can use it.
-Do you collect also these?}.
-After that time I want to continue as so.
-
-SketchBook Project is also inspired me a lot especially in terms of website.
+%SketchBook Project is also inspired me a lot especially in terms of website.
 This project provides a platform to people in order to share their works with other people.
@@
 
-to record and make it available available to the public.
-
-It is placed different locations and the pass the proggress of project is limited in time and place.
-In particularly through the small boxes placed to the libarary.
-Therefore website can provide a solution for this.
-
-Ben insanlarin ayagina gitmeyi dusundum. This project is placed where people frequently visit.
-
-The aim of this project is to work on website.
-Website is a supportive element of it.
-Therefore I only briefly mention the technical details of website.
-Common and trusted open source technologies are selected.
-
-Served from github pages. Images are are sefved from dropbox.
-
-Website can be accessible through the this address http:\\kulü.be\notebook-project. Domain name kulü.be belongs to me and roject placed under a directory of it.
-
-Technical information.
-Website is coded by me with the open source libraries and frameworks.
+Website can be accessible through the this address http:\\kulu.be\\notebook-project.
+Domain name kulu.be belongs to me and project placed under a directory of it.
+Website is coded by me with the common and trusted open source libraries and frameworks.
 Its code also available at this address.
-Site is hosted by github which is code repository.
-Pages are generated by jekyll which is a static website generatir through it som repetive works are can be easily automobized and modilarized.
-
-Content of website.
-
-Functionalities of website.
-
-Future works.
-
-Users or visitors can see the notebook series is made. Each notebook serie has a detailed explanation. It can be viewed at there.
-
-It can accessible through the internet. Richer media. Covergence of analog and digital media.
+Site is served from GitHub pages which provides free website hosting.
+Pages are generated by Jekyll which is a static website generator through it some repetitive works are can be easily automatized.
 
@@
 
-From one point of view it can bee seen that website function visitors book.
+Into the notebooks a sticker which contains qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.
 
-Components of website:
-- Images of notebooks. 
-- Descriptions of notebooks.
-- Collected materials.
-- Comment and sharing.
-- subscribing to email.
-- hastag ile filtreleme.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
+  \caption{QR Code sample}
+  \label{fig:Banner_1}
+\end{figure}
 
-- event photos.
-- event announcement.
-- videos.
-- essays, writings, related word. content related with this topic.
+Through the website people can be able to subscribe to the newsletter to get updates about the project.
+People can be able to add their comment to the website.
+How they are using their notebooks will be showed through it.
+Website will function as a platform to get into touch with people.
+From one point of view website can bee seen as a visitors book.
 
-framework to analyze the work.
+In the future all the discussions and research can be moved to the website that people can reach more information about the subject. This thesis and presentation will also be added to the website.
 
-This thesis and presentation will also be added to the website.
-
-adding different dimension to the project.
-
-% seri numbers and the name of notebook are written inside of the notebooks. How this numbers are given.
-
-Into the notebooks a sticker which contaons qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.
-
-[qr image]
-
-If someone share their work through social networks it betracked and can be viewed in the website. Social networks. Entegration with them.
-
-People can be abke to add their comment to the website. How they are using their notebooks will be showed through it.
-
-People can be able to subscribe to the newsletter to get updates about the project.
-
-Tum bu yapilanlarin uzerine gene de yapilabilecekler var. Kisaca bunlardan bahsetmek istiyorum.
-
-Websitesi ozellikle proje ileride devam edebilsin diye tasarlandi.
-
-In the future all the discussions and research can be moved to the website that people get reach more information about the subject.
-
-Website will function as a platform to get into touch with people. People leave their comments.
-
-The project will be continued after thesis project.
-New features can be added to the website.
-New events can be held.
 All the progress up to now forms the core of the project.
+However it is not limited with it.
+The project will be continued after this thesis completed.
+New features will be added to the website.
 In the future it is planned that through the website people can be able to request to get notebooks.
-Thus project becomes more accessible to the othse people.
+Thus project becomes more accessible to the other people.
 Moreover notebooks done by others from trash can be added to the website.
-Beyond notebooks various objects transformed from trash can find a place.
+Beyond notebooks various objects transformed from trash can find a place in the website.
 
@@
 Ya da neredeyse olduğu gibi kullanırsın.
-Yani uygulanan dönüştürmenin derecesi çok önemli burada..
+Yani uygulanan dönüştürmenin derecesi çok önemli burada...

### 2015-12-29 chapter5.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7

--- 2015-12-06 chapter5.tex
@@
 %
+\begin{singlespace}
 \epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces.
@@
 But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}
+\end{singlespace}
+
+Trash is everywhere.
+Part of our activities.
+Rubbish as an object state is not static.
+Its value, usage may vary according to the people.
+Artistic intentions are aimed to transform the material.
+Whatever the reason that people are discarding things there must be other type of action that can be able to reverse it.
+Aimed to create new possibilities from trash.
 
@@
 %
-Many artworks are introduced.
+Through this thesis many artworks are analyzed.
 They have differences in terms of purpose and approached to the trash.
-Some of them only valued from its plastics effects (physicall properties).
-Some of them turned to the performative act.
+Some of them only valued from its plastics effects (physical properties).
+Some of them turned to the performance.
+
+Their methodologies are different. Their works can be viewed in various dimensions. Their works are also show that the great diversity and the potential usages of trash. 
+There are different motivations.
+
+Reconsidered the notion of trash through the examining the phenonemnons of current age disposable items and ecological concerns.
+
+There are lots of points to approach to the trash. This shows that our richness of this topic.
 
@@
 
-\comment{There is also discard is being generated during the production process of papers.
+There is also discard is being generated during the production process of papers.
 How to use them?
 Need to find a way because varda uses her discarded item inside of the film.
-Always(or in every proceses) new discard items are generated.}
+Always(or in every proceses) new discard items are generated.
 
@@
 
-\comment{Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
-Analysis of them may be subject of another thesis.}
+Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
+Analysis of them may be subject of another thesis.
+
+% TODO conclusion?
+% \comment{ANALOGY Between landfill and graveyards.
+WHOSE TRASH?} \quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
+\quotes{What is happening to trash is what is going to happen to us.
+We’re all going to end up in a dump, and we’re going to decompose.
+That’s the ultimate destiny of humankind, and we don’t want to face that.}
+
+% Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de dönüştürmek gerekli ve bu bir süreç işi.

### 2016-01-01 chapter4_reduced.tex
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346

@@
 
-% Song dong, economical struggles.
+% Temel fikir sonra kullanmak için saklamak gerektigi.
+Bu acidan bakildiginda song dongun annesinin pratigi ile benzerlik gostermektedir.
+Song durumunda etkili olan farktorler ekonomik zorluklar ve boslugun doldurulmasiyla ilgili iken buradaki tam olarak belli degil.
+Ama benim yaklasimi aciklayan bir sey.
+Daha sonra kullanmak icin saklamak.
 
@@
 \end{figure}
+
+% Bu calismalardaki amacim farkli yuzeylerde resim yapabilmekti.
+Copu uzerine bir swyler yapmak benim icin yeni bir sey yapmakti.
+Deneysel bir yaklasimdi.
+Bir digeri ise bedavaydi.
+Kolayca elde edilen bir malzeme ve rahat ucuzlugundan dolayi bana daha fazla deneme imkani sunmaktaydi.
+
+% cok ve kolay ulasilabildigi icin deneme imkani da cok. Benim icin cok iyi bir durum.
+
+% Artik biriktirip, onlari daha sonrasi icin kullanabilirdim. Bunlari sadece yapmakla kalmiyordum, cevremdeki insanlara gosteriyordum, onlara hediye olarak veriyordum.
+
+% ben bir suru bir suru yapiyordum. Kendi urunumu kendimin yapmak istiyordum.
+
+% cope bakis acim buradan hissedilebilir.
+
+% tum imkansizliklara ragmen copten bir sey yapmak yerine aslinda imkanlarla birlikte copten bir sey yapmak.
+Hazir bir sey kullandigim zaman kolay kacmak olarak goruluyor.
+Ama benim amacim zoru basarmak degil ki?
+Boyle bir zorlamaya gerek var mi emin degilim.
+Bu zorlamanin artisi nedir bilmiyorum.
+
+% ben boyle kimsenin yapamayacagi bir seyle ugrasmak istemiyorum. Sadece ben yapmis olmak istemiyorum. Herkes yapabilir. Hatta yaapsin. Ben sadece yapan insani gostermek istiyorum.
 
@@
 Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
-\begin{singlespace}
 \begin{quote}
@@
 \end{quote}
-\end{singlespace}
 I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.
+
+% ilk toplama hareketim aslinda belli noktalari konrtol etmek. Ama bunlari kesfetmem gerekti. Bunlari ise normal hayatin akisi icinde kesfettim.
+
+% found photosdaki adam da boyle bir mod var acikcasi.
+
+% nicin atildigina gelince. Fazlalim olmasi, isini bitirmis olmasi. Labda unutulanlar ozellikle fazlalik hatali olmasi. Ve kimsenin umursamadigi bir sey olmasi.
+
+% copten beslenmek ile aslinda oldukca benzer noktalar var. Secerken konrol ediyorsun. Birakilma swbebini dusununce aslinda benim kulamnimjm icin uygun olmadigini anlayacaktim.
 
@@
 
+% ben kendim ve cevremdekilere bu is icin gereksiz yere cop urettirmemeliydim. Bu ise hile karistirmam olurdu.
+
 %[owner of disard]
@@
 Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
+
+% birakilmis bir seyi alirken yasanan huzursuzluk olarak tanimlasak bunu daha uygun olabilir. Onun baskasina bir sekilde ait oldugunu biliyorsun.
+
+% tolanilan mrkanlar ise onemli.
+Fakir mahallesinde toplamak ile, zengin mallallesinde toplamak ayni sey degil.
+Ve devldtin coplugunu karistirmak ayni sey degil.
+Cope bir seyin izi ki ondan kurtulmak icin oguticuler var.
+Mesela herkesinkagidini alamadim.
+Her seyinde kagidinialamdim.
+Bohle bir sey mumkun degil.
 
@@
 
-% bırakıldığını nasıl anlıyordum vs.
+% bırakıldığını nasıl anlıyordum vs. Uzun sure bekleyince. Zaten bunlarda cope gidiyorlar. Temizlikcinin onlari topladigini gordum ne de olsa ben.
 
@@
 Do you collect also these?}.
-After that time I want to continue as so.
+
+% ayni zamanda baska insanlarin da yaraticiligi bu is. Bilkente gidip o kagitlari almaliyim ben.
 
@@
 
-The purpose is here not only to transform objects but also change the perceptions of trash. Asking people to collect things and inform them started to shift in peoples mind. For instance
+The purpose is here not only to transform objects but also change the perceptions of trash. Asking people to collect things and inform them started to shift in peoples mind.
 
@@
 
-% meaning of paper for me.
-% TODO buraya bir şey eklenecek.
+% meaning of paper for me
+
+% kagit benim cevremde cok fazla kullanilan bir sey.
+
 %Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.
@@
 
+% Packets and Bags.
+
+% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta. Diğerleri arkadaşın ofisinden, bir kısmı hocamdan. Bir kısmı da benim yoldan topladıklarım.
+
+% Toplama mekanları: Yollar, Bilkent labı. Sabahleyin geçtiğim yollarda genelde öğrencilerin bıraktıları simit pohaça gibi şeylerin paketleri bulunmakta.
+
+% Toplanan malzemeler ve toplanan mekanlar. Bilkent labaratuvarı, Restraurants, Pazar yeri, Kendi çalıştığım ofis,
+
+% Toplanan eşyalar mass produce üretilmiş ürünlerden oluşmakta.
+
+% Toplanan eşyalar çok fazla özel eşyalardan oluşan şeyler değil.
+Evsel atık değil.
+Evin dışından toplanan şeyler değil.
+Daha çok halka açık alanlarda üretilen çöpler benimki.
+Yani Tracey eminin kiler gibi benimkiler kişisel eşyalardan oluşmamakta.
+
+% Bu yüzden aslında toplanan eşyalarda kullanıcılarına ait çok fazla bir şey yok.
+Labdan alınanlardan olmakla birlikte, paket ve poşetlerde böyle bir durum yok.
+Found photosdaki gibi bir ilişki de yok mesela.
+
+% Elimde bazılarının fotoğrafları var bazılarının ise yok.
+
+% Detaylı olarak bakmak gerekirse;
+
 \textbf{Burger King packages} are collected from the office where I work.
@@
 
-%Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
+% Yemek posetleri. Ogle vaktinde kurye tarafindan teslim ediliyor. Kağıt, yağı iyi emdiği için kullanılıyor burada.
+
+% Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
 Some people think that it is disgusting because of greasy onto it.
@@
 
+% Masaların üzerine örtülen ve sonra atılan kağıtlar.
+
+% Bir yandan da kağıtların nasıl kullanıldıklarına dair bir gösterge. Yemek için kullanılıyor. Gıda sektörü için.
+
 \textbf{Varuna Gezgin}, is a cafe. papers of old menus. They are waited to be discarded.
+
+% amacim aslinda sadece yemeklerin altindaki kagitlari toladiktan sonra bunlari bunrada gosterebilir miyiz diye sormakti.
+Ama sonrasinda konusmamizda bana bir suru kagit getirdi.
+Ellerindeki kullanilmayan kagitlarin sadec bir kismiydi.
+Zatenben tek basima cok ufak kucuk bir kismina dokumus oluyordum bunkaron.
+Hatta kasadaki cocuk kalanlari da ogrencilere dagitmayi dusundu.
+En azindan kenarda bekleyen kagitlar gun yuzue cikmis oldu.
+
+% burdaki dikkate alinan sey satilan bir sey olmadigdi.
+Ktuphanede ise aslinda bunun bir reklam anlami tasiyip tasimayagi idi.
+Bilkent labindakiler ise bunukomsenin almayacagi dokunmayacagi yonundeydi.
+E napalim artik.
+Insanlarla konustukca farkli seyler dusunuyorum.
+
+% websitesinde amac bun!ari anlatabilmekti.
 
@@
 
+% Gıda sektörüne bir diğer örnek.
+
 \textbf{Order slips} are collected from bank office my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
@@
 
+%arkadastan gelen kagitlar.
+
+% Ders için kullanılanlar. Arkadaştan gelen kağıtlar, ders notları, tez yaprakları.
+
 \textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.
+
+% bilkent bilgisayar labindan toplanan kagitlar.
+Ben kendim ilk kez orada cikti aldigim zaman fark ettim.
+Bol miktarda kagit atilmisti.
+Bunlar aslinda tam da benim aradigim kagitlar olabilirdi.
+Okul ogrencileri buradan ihtiyaclari olan baskilari aliyorlardi.
+Her labaratuvarda birer tane yazici vardi.
+Labaratuvar sisteminde isleyisten kaynaklandigi dusundugum bir sebepten kagitlar orada birakiliyordu.
+Unutuluyorlardi.
+Ya da cikmadi zannedilip, fazladan bastiriliyorlardi.
+
+% Ders notları, çalışma notları, kişisel çıktılar.
 
@@
 
+% tam olarak kategorolendirmeye degmeyecek cokgunlukta olan kagitlar. Bunlarin arasinda yemeklerin altinda toplanan kagitlar gosterilebilir. Sagdan soldan toplanan kagit paketler olabilir.
+
+% iki parcasi var defterin biri kapagi bir digeri de icindeki sayfalari.
+
 %as it can be seen here there are various types of paper and most of them some memories for me.???
+
+% websitesi aslinda
 
@@
 After sewing them I fixed the yarn with hole by gluing to make it more solid.
+
+% Benim dönüştürme ve yeniden kullanma pratiğim ise daha önceden bahsedilen upcycling kategorisine girmekte.
+
+% Kullandığım ve malzemeler açısından bricolaj yöntemine yaklaşmaya çalışmak istesem de tam olarak ulaştığımı söyleyemem.
+Belli başlı bazı araçları satın aldım veya hazır kullandım.
+Bir diğer yandan ise benim işi yapmam uzunca bir süreyi kapsadığı için aslında o anda elde ne varsa ondan yapma tanımına da uymamakta.
+Kullandığım malzemelerde ise en profesyonel için olanı kullanmaya çalışmadım, eksik nelerse onları aldım onun dışındakiler için ihtiyaçlarımı kendim gidermeye, kendim yöntem bulmaya çalıştım.
 

### 2016-01-01 chapter5.tex
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346

@@
-\chapter{Conclusion}
+\chapter{CONCLUSION}
 
@@
 
-Reconsidered the notion of trash through the examining the phenonemnons of current age disposable items and ecological concerns.
+Reconsidered the notion of trash through the examining the phenomenons of current age disposable items and ecological concerns.
 
 There are lots of points to approach to the trash. This shows that our richness of this topic.
+
+% Agnes Varda mesela aslında farklı toplama biçimlerini araştırıyor. Ben de aslında bu tezde atığa dair farklı pratikleri keşfetmeye çalışıyorum.
+
+% Agnes Varda belgeseline başlarken sözlük tanımından başlıyor. Sözlük tanımı aslında giriş için iyi bir başlangıç. Bir şeye başladığımızı görüyoruz.
+
+% Dadaların kelimeleri rastgele oluşturdukları gibi ben de özellikle üzeri yazılı olan kağıtları karıştırıp kullandım. Bu konu hakkında ne diyorlar araştırmak gerekli.
+
+% İsim verme yöntemi olarak aslında bir diğer yanda ise kurt'un yönetemi. Gene bir dada yaklaşımı. Nonsense kelime üretme pratiği
 
@@
 Need to find a way because varda uses her discarded item inside of the film.
-Always(or in every proceses) new discard items are generated.
+Always(or in every processes) new discard items are generated.
 

### 2016-01-01 chapter4_reduced.tex
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632

@@
 
+% The chapter that follows is divided into three sections
+
 In this chapter thesis project and its development progress will be explained in detail in the light of what has been discussed in previous chapters.
@@
 %
-% TODO: Burada geçmiş, şimdiki zamanlara dikkat etmek gerek.
+% TODO: Be careful on tenses.
 \section{The Statement}
-% TODO Ekolojik, harmful, iğreç falan diye de değinmek gerekli bence.
 % --disgusting, abject, unattractive, harmful to the people and nature--
@@
 
-% Her zaman her yerde olan çöp.
-% people are invited in the phase of collecting and finding trash
+% people are invited in the phase of collecting and finding trash that is every where and produced every time.
 With the collaboration of many people discarded papers and packages were collected from different places.
@@
 
-% Bu proje çöpte yeni imkanlar bulmayı amaçlıyor. İnsanların tekrar onları hayatlarına sokmalarını istiyor.
+% This project aims to find new potentials on trash. This project asks people to readmit the trash to the their life.
 
@@
 They lead me during the development of the work.
-% played significant role.
+% played significant role, solved problems.
 % It is evolved in time and affected from other artists' work, and gain meaning from research.
 
-% This progress also reveals the how this work can be positioned among the other works.
+% This progress also reveals that how this work can be positioned among the other works.
 
@@
 
-% Temel fikir sonra kullanmak için saklamak gerektigi.
-Bu acidan bakildiginda song dongun annesinin pratigi ile benzerlik gostermektedir.
-Song durumunda etkili olan farktorler ekonomik zorluklar ve boslugun doldurulmasiyla ilgili iken buradaki tam olarak belli degil.
-Ama benim yaklasimi aciklayan bir sey.
-Daha sonra kullanmak icin saklamak.
+% [Song Dong]
+The main idea is to save them to use later.
+For some people it is a life saving practice.
+It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2).
+This practice result in establishing stronger (intimate) relationship with objects.
+
+% TODO artist name
+
+%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.
+
+I am very uncomfortable with the act of discarding.
+I often think that by discarding objects, I am missing their potentials.
+I must find another use which is more effective than throwing away.
+At least I can give them to someone else who can use it for own purposes.
+As artist X argues that it is a "failure of imagination".
+There is a lot of effort to produce objects and it seems that all this efforts are wasted.
+What I mention is not related about ultimate productivity.
+It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using.
+Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.
+On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind.
+It is the result of inevitable rhythm of modern life style.
+Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard.
+In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines.
+The use of that object can be decided in the future.
+
+% [encouraging point]
+One of the encouraging factor of working on trash is to explore something different that others cannot see.
+In other words, it contains eureka moments.
+Because it is ignored by discarding and therefore undiscovered.
+Wait us to be discovered and possibly (as Picasso explanation on his work 'Bull's Head') discovered again and again.
 
 % [EXPERIMENTS AT HOME]
-Most remarkable interaction with trash is from recent years.
+My remarkable interaction with trash is from recent years.
 Long years I stayed at dormitory during when I was high school and university while undergraduate.
@@
 
-% Bu calismalardaki amacim farkli yuzeylerde resim yapabilmekti.
-Copu uzerine bir swyler yapmak benim icin yeni bir sey yapmakti.
-Deneysel bir yaklasimdi.
-Bir digeri ise bedavaydi.
-Kolayca elde edilen bir malzeme ve rahat ucuzlugundan dolayi bana daha fazla deneme imkani sunmaktaydi.
-
-% cok ve kolay ulasilabildigi icin deneme imkani da cok. Benim icin cok iyi bir durum.
-
-% Artik biriktirip, onlari daha sonrasi icin kullanabilirdim. Bunlari sadece yapmakla kalmiyordum, cevremdeki insanlara gosteriyordum, onlara hediye olarak veriyordum.
-
-% ben bir suru bir suru yapiyordum. Kendi urunumu kendimin yapmak istiyordum.
-
-% cope bakis acim buradan hissedilebilir.
-
-% tum imkansizliklara ragmen copten bir sey yapmak yerine aslinda imkanlarla birlikte copten bir sey yapmak.
-Hazir bir sey kullandigim zaman kolay kacmak olarak goruluyor.
-Ama benim amacim zoru basarmak degil ki?
-Boyle bir zorlamaya gerek var mi emin degilim.
-Bu zorlamanin artisi nedir bilmiyorum.
-
-% ben boyle kimsenin yapamayacagi bir seyle ugrasmak istemiyorum. Sadece ben yapmis olmak istemiyorum. Herkes yapabilir. Hatta yaapsin. Ben sadece yapan insani gostermek istiyorum.
+% TODO Free material add reference here.
+My purpose in these work is to paint on different surfaces, experiment new materials.
+They are not flat, not blank.
+These surfaces bring their previous histories to the painting.
+Another factor is they are free and easily available.
+Therefore I can make many experiments on these materials.
+After I completed them, I showed them people around me and give them as a gift.
 
@@
 
-% But covering things are not new actually, when we are primary school again, we cover our books and notebooks.
+% But covering things are not new actually, when we were studying at primary school, we covered our books and notebooks.
 My mother, she is also a teacher, still covers her books things whatever at hand.
@@
 
-% bir yandan free olması experiment yapmak için ideal olması.
-
-%\textbf{What do I think about trash?} I need to clarify my approach to the trash, wasting and discarding.
-First point is that I am very uncomfortable to the action of discarding thing.
-I always think that by discarding this think I am missing something rather than getting rid of something.
-Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on.
-However almost it is never ending loop.
-(I believe that sometimes we need to break the loops to realize different meanings.
-To think outside the box, we need to behave outside of common habits.
-As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on.
-But for what?
-and also ought to be like that?
-(throw away them to same bin.
-(Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it.
-At that times I become very sad and feel very comfortable.
-I must have find to another place for it more suitable than a waste bin.
-At least I can give them someone else who can use it for own purposes.
-Do I really luxury of discard?
-
-%Significance of thinking outside of the box (about trash) is actually breaking the loops.
-You have to look at differently from common perception.
-\textbf{Break the rules, break the loops} to realize the alternative.
-\comment{Even if the market gives many alternatives of commodities, why do people still seek the alternative?
-Is not is enough?
-What type of gap that industrial products can not fill the gaps.
-Neden tüm insanlara hitap etmiyor?}
-
-%[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard.
-Because it is ignored by discarding and therefore undiscovered.
-Wait us to be discovered.
-and possiblely (as picasso mentioned) discovered again and again.
-\comment{Different people from different culture bring new interperation, but it is exist all of things.}
-
-%It contains evraka moments.
-
-%[Motivation.] I can not throw them away.
-When I throw them I became sad for them.
-I have to find something useful for it.
-(Failure of imagination, failure of making meaning) Even if I can not find it, I can pass it to another person who can make use of it for own purposes.
-There is a lot of effort to produce objects and it seems that all this efforts are wasted.
-What I mention is not related about ultimate productivity.
-It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using.
-Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.
-
-% Önceki chapterlarda insanların kişisel olarak objelerde neler buldukları önemliydi. Ben de burada kendiminkini anlatacağım. Benim için yeni bir şeyler üretmek için birer kaynak.
-
+% TODO referans hatası olabilir.
 % NEW PART [collecting] 
@@
 
-% ilk toplama hareketim aslinda belli noktalari konrtol etmek. Ama bunlari kesfetmem gerekti. Bunlari ise normal hayatin akisi icinde kesfettim.
+% There are similar points with my practice. I also check the condition of material.
 
-% found photosdaki adam da boyle bir mod var acikcasi.
+% TODO Sanatçı adını bulmak gerekli.
+% It can be viewed as mode of search for objects and it can be seen clearly on Dick Jewlss found photos.
 
-% nicin atildigina gelince. Fazlalim olmasi, isini bitirmis olmasi. Labda unutulanlar ozellikle fazlalik hatali olmasi. Ve kimsenin umursamadigi bir sey olmasi.
+% Firstly I need to explore different locations to collect items. Most of them are not obvious for me. I discovered them on the flow of normal life and tasks.
 
-% copten beslenmek ile aslinda oldukca benzer noktalar var. Secerken konrol ediyorsun. Birakilma swbebini dusununce aslinda benim kulamnimjm icin uygun olmadigini anlayacaktim.
+% The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation.
+Nobody cares others print out.
 
-% Bozulduğu için mi yoksa şekli standartlara uygun düşmediği için mi atılmış agnes varda da gösterildiği gibi.
+% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.
 
-% [Mode of search] looking for waste bins. asking for people. realizing during the daily life. for example bank splits.
-% ofis, varuna, bilkent labı gibi mekanlar aslında önemli. benim malzemelerin büyük kısmını bulduğum yerler. iş bankası mesela. found photos.
+% Does it discarded because of rotten, not fitting industrial standard or being surplus (production excess)?
+For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards.
+Therefore these potatoes fall into the category of edible (eatable).
+They are in good quality but not liked shape???
+
+% [Mode of search] looking for waste bins.
+asking for people.
+realizing during the daily life.
+for example bank splits.
+I discover them during my life.
+For instance,  after I leaved bank split I realized that I can use them in my notebooks.
+Back of the splits are empty and appropriate for writing.
+Lots of them are used in the bank.
+The other places are discovered while daily life continues.
 
@@
 In other words first rule is to consume less and generate less trash.
-Lots of trash is accessible.
+Lots of trash is already produced every time everywhere.
 Aim is to reach them.
 
-% ben kendim ve cevremdekilere bu is icin gereksiz yere cop urettirmemeliydim. Bu ise hile karistirmam olurdu.
+% OWNER
+\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}.
+This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects.
+Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
+You already know that it owned by somebody else and after a while owner can take them.
+I solved this issue checking the leaved papers in every couples hours.
+If it stays there I take them.
+Further I encountered that If nobody takes them for a long time servants collect them.
 
-%[owner of disard]
-\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}.
-This question makes me uncomfortable because of feeling that stealing that someone elses' objects.
-Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
+% TODO reference gerekli.
+% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
+The issue of owner becomes more complicated when owners' social status considered.
+Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood.
+On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.
 
-% birakilmis bir seyi alirken yasanan huzursuzluk olarak tanimlasak bunu daha uygun olabilir. Onun baskasina bir sekilde ait oldugunu biliyorsun.
-
-% tolanilan mrkanlar ise onemli.
-Fakir mahallesinde toplamak ile, zengin mallallesinde toplamak ayni sey degil.
-Ve devldtin coplugunu karistirmak ayni sey degil.
-Cope bir seyin izi ki ondan kurtulmak icin oguticuler var.
-Mesela herkesinkagidini alamadim.
-Her seyinde kagidinialamdim.
-Bohle bir sey mumkun degil.
-
-% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
-%Trash is also regarded differently, depending on where you live.
-Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
-But when the same student went to Beverly Hills to go through trash, the police were nearly called.
-“Who decides what is public and what is private?
-How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?” Zubiaurre said.
-
-% bırakıldığını nasıl anlıyordum vs. Uzun sure bekleyince. Zaten bunlarda cope gidiyorlar. Temizlikcinin onlari topladigini gordum ne de olsa ben.
-
-%[people]
+% CONTRIBUTIONS OF PEOPLE
 % Bu kısmın daha güzel anlatılması gerekli.
@@
 Do you collect also these?}.
-
-% ayni zamanda baska insanlarin da yaraticiligi bu is. Bilkente gidip o kagitlari almaliyim ben.
+They bring their unique approach.
 
@@
 People bring the material also wonder the result of it.
+Further people see me when collecting objects and transporting them wonders their purpose.
 
@@
 Collected items are mainly disposables ones.
-Most of them are paper or contains paper pulp.
+Most of them are paper or made from paper.
 The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China.
+In modern times all types and qualities of paper such as newspaper paper, print paper, and carton used for boxes pass through the same basic method of manufacture \citep{trafford2012paper}.
 It is fundamental medium for writing, reading, education, communication, information storage and many others.
@@
 Even if it is thrown out, still appropriate for painting and writing.
-
-% TODO: Free ve accessible olması experiment yapmak için önemli bir yere getiriyor onu.
 
@@
 
-% meaning of paper for me
+% [importance of paper for me]
+% ilki resimden geliyor.
+Onu toplamaya başladım.
+ve daha onu tükettiğimi düşünmüyorum.
+bana hala bir sürü imkan tanıdığını düşünüyorum.
+Bir de yaygın kullanılması.
+Hala daha kimsenin görmediği küçük noktaları görmeye başlamamış olabilir.
 
-% kagit benim cevremde cok fazla kullanilan bir sey.
+% The importance of paper cames from previoulsy I mentioned.
 
-%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.
+% Not only important for the community but also for me.
 
-% [Why do I collect trash?] Herkes neye ihtiyacı var ise onu toplar.
-Ben neden niçin topluyorum?
-Toplama sebepleri?
-Dönüştürme sebepleri.
+% Kagit benim cevremde cok fazla kullanilan bir sey. yaygın kullanımı olması.
+
+% Çok basit bir şekilde çöp olarak görülen bir şeyi başka bir şey olarak görmek keyifli bir şey benim için. zaten dönüştürmek kullanmak için topluyorum.
+
+% Dönüştürme sebepleri.
 Neden sadece toplamakla yetinmiyorum.
-yani toplamak ile ayrıldığı noktalar nelerdir.
-Ben bir mana mı arıyorum?
-Yoksa kaybetmekten mi korkuyorum?
 Yeni kompozisyonlar oluşturmak istiyorum.
@@
 
-Collected items are stored in my room. All of they are varies. Most of them are not belong to me. Here the detailed information of the collected materials are listed.
+Collected items are stored in my room for a long time.
+Most of them are not belong to me.
+Here the detailed information of the collected materials including the place where it is collected and their usage are listed.
 
+% Bu resme gerek olmayabilir. Appendixe konulabilir.
 \begin{figure}[h!]
@@
 
-% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta. Diğerleri arkadaşın ofisinden, bir kısmı hocamdan. Bir kısmı da benim yoldan topladıklarım.
+% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta.
+Diğerleri arkadaşın ofisinden, bir kısmı ise hocamdan.
+Bir kısmı da benim yoldan topladıklarım.
 
@@
 
-% Elimde bazılarının fotoğrafları var bazılarının ise yok.
+% Elimde bazılarının fotoğrafları var bazılarının ise yok. Yani bazılarının kayıtları var, bazılarının ise yok.
 
@@
 (it fits here)
+
+% Nothing is inherently trash(5).
+matter out of place.
+Dirt is relative emphasize.
+"Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on" (Douglas 2003, 36-7)
 
@@
 
+% Buradaki kağıtlar tüm yemek masasının üzerine örtüyor.
+büyük bir rulo halinde masanın başında bulunuyor.
+yemek yendikten sonra masanın üzerindeki kısım yırtılıp atılıyor.
+yenisi rulodan seriliyor.
+ne kadar kağıt harcandığı bir bakışta anlaşılmakta.
+Tüm o rulodaki kağıtlar çöpe gidecek.
+Arkadaşlarla bir gün dışarı gittikten sonra buradaki kağıtları farkettim ve çıkışta onlar eskileri toplarken kağıtları topladım.
+
 \textbf{Varuna Gezgin}, is a cafe. papers of old menus. They are waited to be discarded.
+
+% arkadaşlarla yemeğe gittikten sonra kasiyerdeki arkaştan defterleri burada verip veremeyeceğimi sorduktan sonra bana ellerindeki kağıtlardan bahsetti ve onları verebileceğinden bahsetti.
 
@@
 
-% websitesinde amac bun!ari anlatabilmekti.
+% websitesinde amac bunlari anlatabilmekti.
 
@@
 
+% özellikle içinde kullandığım kağıtları karıştırarak oluşturdum. Burda dada şiiri ile benzerlikler içermekte.
+
 % Benim dönüştürme ve yeniden kullanma pratiğim ise daha önceden bahsedilen upcycling kategorisine girmekte.
@@
 
-% TODO sabahleyin bir fotoğrafını çek bunların.
+% TODO defterin yakından fotoğrafları
 
-% TODO defterin yakından fotoğrafları
+% Defter dikme yöntemi ???
+
+% Kullandığım malzemeler. İğne, iplik, makas, maket bıçağı, raptiye, yapıştırıcı, ve yapıştırıcı.
 
@@
 Therefore I think the process of transformation is a continuous act.
-% amaç çeşitliliği arttırmak olduğu için
 
-% TODO siteye nasıl karar verdin la?
+% amaç çeşitliliği arttırmak
 

### 2016-01-01 chapter5.tex
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632

--- 2015-12-29 chapter5.tex
@@
 
+Inseparable part of our activities.
 Trash is everywhere.
@@
 
+% This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.
+
+% This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material.
+
+% Through the analysis of selected works metadologies, approaches, placement trash, positing of trash ...
+show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.
+
+% Our evaluations of what is 'rubbish' and 'art' or 'useful/non-useful' and 'good/bad' is both content and context dependent and are not fixed values.
+Apparent polar opposites of 'rubbish' and 'art' are blurred notions that are explored in many art works using rubbish materials.
+Indeed, temporal value judgements of 'rubbish' and 'art' are often at the core of such art works.
+
+% This research began through a desire to understand more about the subject of rubbish in art practice.
+(or especially turning discarded papers to notebooks from a hobby to framed project or research.)
+
+% While the notebooks have potentials to be rubbish, records of them in the website are preserved.
+
+% In the project notebooks are given away.
+They are transformed to trash and served to the flow again.
+They will continue to flow.
+There is a possibility that they can be trashed again.
+However vice verse is possible.
+In other words has potential be turn to durable.
+Decision belongs to people again.
+
+% Through this research another dimension of trash is explored. This present more solid understanding of trash.
+
+% Sanatçıların sorguladıkları şeylerin sonuçlarını görmek gerekli. Neden çöpü kullanıyorlar. İlkinde  geleneksel yöntemleri terk etmeleri,
+
+% This research present different uses of trash and approaches. This suggests that it provides to artists wide range of representation styles. (limitless possibilities)
+
+% In the introduction part, questioned the why artist choose to use discarded material. examples, different approaches. what are they.
+
+% But it cannot be completely explained by trend of moving away from traditional methods, modern times throwaway spirit play significant role in this movement.
+
 %
@@
 
-Their methodologies are different. Their works can be viewed in various dimensions. Their works are also show that the great diversity and the potential usages of trash. 
+Their methodologies are different.
+Their works can be viewed in various dimensions.
+Their works are also show that the great diversity and the potential usages of trash.
 There are different motivations.
+(Artist have different motivations and interpretations on trash.)
 
@@
 Saved for later use.
-On the other hand being aware of this trasnformation act is very tiny part of the big picture.
+On the other hand being aware of this transformation act is very tiny part of the big picture.
 I can say that my trash is reduced but is it same for the other people.
 Hard to collect all of them.
-
 There is also discard is being generated during the production process of papers.
@@
 
-% Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de dönüştürmek gerekli ve bu bir süreç işi.
+% The purpose is here to find new possibilities and dimensions to see the objects. The physically transforming objects is not sufficient, at the same time it will change people's viewpoint.
+
+% try to the capture the reality behind the consumption practices.
+
+% transform to their daily trash, use them for their on artist purposes, surface for their art.
+
+% how it is essential for some people.
+
+% as a portrait of them.
+
+% zim car,
+
+% Duchamp, beyond the objects, the ideas embeded them gain importance when considering artworks.
+
+% many possibilities in terms of their shape, size and color. offer great diversity.
+
+% narratives through the people's discard. the image of people, their
+
+% record of their trash, preserving the images of them, or the others.
+
+% destructive manner, break down
+
+% form - structure - shape
+
+% different forms of trash. modes, practices, type, kind.
+
+% photos, everyday objects, disposables, luxury possessions like car.
+
+% place of trash
+
+% different people touches on trash. different cultures, different manner
+
+% for us and artist it is a source of diversity. for their work, representation and expression.
+
+% it is not only found in landfill but also can be found in museums.
+
+- çöpün değişik formları. çöpü kullanmanın değişik formları. çöpün hayattaki değişik formları.
+- çöpe dokunan farklı insanlar.
+- o yüzden bizim için bir çeşitliliğin kaynağı
+- o yüzden kaynak.
+- o yüzden hazine
+- nasıl bir hazine, ifade aracı olarak birer hazine.
+- sadece çöplüklerde değil aynı zamanda müzelerde,
+
+% The initial reduction of the research scope leaves potentially much more relevant work to be done.
+Certain major avenues have not been discussed in depth, not because they are irrelevant, but because there simply has not been time or space to explore them in sufficient detail and some reduction in scope has been necessary to be specific in such a wide field
+
+% For example, virtual/digital rubbish-as-art was specifically omitted in this project due to the object/material-basis of the enquiry.
+However, through the project development, the informal language basis of exchange in understanding the value of rubbish-as-art has proven fundamental and a further area to develop, which will most likely include in the virtual/digital realm.
+The question of whether there still needs to be a material/object basis of this further investigation is yet to be answered.
+
+% The focus on material waste in art in this study has also largely omitted waste of other non-material things such as time.
+Wasting time as art and the relationship to labour and value is another significant area of exploration.
+The relationship between wasting time and material waste as documentation that is evident in some studied art works has not been developed in this thesis.
+Again, there is much potential for further work in this area and also links in with notions of value of online exchange also as 'wasting time'.
+
+% Future works, as mentioned the value and meaning objects changes people to people society to society.
+Therefore more focused research can be conducted to analyze the local practices of transformation.
+the history and the place of the peoples life.
+
+% Different selection of works and their analysis and relation between them will form another thesis which identifies another dimension of trash.
+
+% Paraphrase 
+%This thesis takes a rather different approach to the discarded objects.
+It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.

### 2016-01-08 chapter3_reduced.tex
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d

@@
 However, it is not discussed in the context of fine art and not accepted method for art making.
+
+% Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.
 
@@
 
-\begin{singlespace}
 \begin{quote}
@@
 \end{quote}
-\end{singlespace}
 
@@
 % FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
-\begin{singlespace}
 \begin{quote}
@@
 %
-\section{Examples from contemporary artists}
+\section{Examples from Contemporary Artists}
 In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed.
@@
 
-Prior to film Amélie, British artist Dick Jewell published a book in title of "Found Photos" in 1977.
+Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977.
 It is a collection of photobooth images that had been thrown away or torn up by the people in the photos.
-\cite{walker2010dick} comments on that it is "always a joy to look through." Images capture diverse range of activities and expressions of people using photo booth machine.
+\cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine.
 They are scavenged by the artist from the photo booths of London.
@@
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.47\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
@@
   \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
-  \caption{Michael Landy, Art Bin}
+  \caption{Michael Landy, Art Bin, 2014}
   \label{fig:MichaelLandy_ArtBin}
 \end{figure}
+
+% Landy'nin yaptığı bir çok iş aslında çöple ilgili olduğu savunulabilir.
+Hepsinin anlatmak mümkün olmasada bir diğer için sahip olduğu tüm eşyaları bozmasıyla ilgili.
+Daha önceden bahsettiğim geri dönüştürme tanımları ile ilgili olarak bu işi downcycling yöntemi arasında görülebilir.
 
@@
   \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
-  \caption{Michael Landy, Break Down}
+  \caption{Michael Landy, Break Down, 2001}
   \label{fig:MichaelLandy_BreakDown}
@@
 
-% TODO kendi işime taşıyacağım.
 % http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa, http://www.eloisacartonera.com.ar/ENGversion.html
@@
 
+% , as illustrated by the examples cited so far,
+
+% Örnek sadece bunlarla sınırlı değil, daha bir çoğu sayılabilir, plastik poşetinde şiirselliğin yakalandığı american beauty filmi, kamusal alanı dönüştüren sanatçılar gibi.
+
 %
 %
-\section{The documentary \quotes{The Gleaners and I} by Agnès Varda}
+\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
 "The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000.

### 2016-01-08 chapter4_reduced.tex
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d

@@
 \chapter{NOTEBOOKS FROM TRASHED PAPERS}
-
-% başka bir yerde kullanırsın: , as illustrated by the examples cited so far,
 
@@
 \end{singlespace}
-
-% The chapter that follows is divided into three sections
 
@@
 \section{The Statement}
-% --disgusting, abject, unattractive, harmful to the people and nature--
 Refuse is part of people’s consumption practices.
@@
 It is not wanted, thrown away, kept away.
-It is considered as useless and disgusting.
+It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature.
 Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.
 
-% people are invited in the phase of collecting and finding trash that is every where and produced every time.
 With the collaboration of many people discarded papers and packages were collected from different places.
@@
 
-Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek. As it is discarded, missed potentials were discovered.
+Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek.
+As it is discarded, missed potentials were discovered.
+This project aims to find new potentials on trash.
 
@@
 Trash must be accepted by them.
+This project asks people to readmit the trash to the their life.
 For this reason notebooks are given away free at various places where people visit frequently.
 By doing that once thrown materials would find a place with new purposes in the community.
-
-% This project aims to find new potentials on trash. This project asks people to readmit the trash to the their life.
 
@@
 
-% Starting from the very beginning, I would like to explain which paths and turns I took and how they let my work to come out as it is now.
-In other words, this will be the story of how I developed my work from scratch.
-
-% Artist's work and their approach supported my project.
 Through the process, there are several problems that needed to be solved.
-Some of the questions in my mind are solved through the research on trash.
-Further, the found samples of artworks helped me a lot to shape unclear points of the project.
+Some of the questions in my mind are solved through the research on the subject.
+Further, the found samples of artworks played significant role in progress.
+They helped me a lot to shape unclear points of the project.
 They provide me a deeper understanding of the subject and what I am doing.
-They lead me during the development of the work.
-% played significant role, solved problems.
-% It is evolved in time and affected from other artists' work, and gain meaning from research.
+In other words, they lead me during the development of the work.
 
@@
 % NEW PART [approach, history] 
-Before explaining the details of the work, it would be better to explain how it was started and what is my approach to the trash. % It is not developed from scratch.
+Before explaining the details of the work, it would be better to explain how it was started and what is my approach to the trash.
 
 My interaction with discarded material is not limited with this thesis project.
-There are some previous attempts and several memories that I remember.
+There are a few previous attempts and several memories that I remember.
 Briefly, I want to examine them.
-These will also reveal my approach shaped through time (and how thesis work affected from it?).
-My motivation also revealed through it.
+These will also reveal my motivation and approach shaped through time and how thesis work affected from it.
 
 % [SODA CAPS]
-I remember from my childhood that we were collecting soda caps and played with them.
+I remember from my childhood that we were collecting soda caps and were playing with them.
 We were looking everywhere to collect them.
@@
 We were already playing with trash while we were child.
-Therefore, it can be better understand that while Picasso said that \quotes{every child is an artist}.
+Therefore, it can be better understand that why Picasso said that \quotes{every child is an artist}.
 
@@
 It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2).
-This practice result in establishing stronger (intimate) relationship with objects.
-
-% TODO artist name
-
-%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.
+This practice result in establishing stronger and intimate relationship with objects.
 
@@
 At least I can give them to someone else who can use it for own purposes.
-As artist X argues that it is a "failure of imagination".
+Seeing papers on the waste bin is a disappointment for me.
+As artist Aaron Kramer argues that \quotes{[t]rash is the failure of imagination} \citep[as cited in][]{meyer2007turning}.
 There is a lot of effort to produce objects and it seems that all this efforts are wasted.
@@
 Because it is ignored by discarding and therefore undiscovered.
-Wait us to be discovered and possibly (as Picasso explanation on his work 'Bull's Head') discovered again and again.
+It waits us to be discovered and possibly (as Picasso's explanation on his work 'Bull's Head'\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.
 
@@
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.30\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.30\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.30\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
@@
 
-% But covering things are not new actually, when we were studying at primary school, we covered our books and notebooks.
-My mother, she is also a teacher, still covers her books things whatever at hand.
-(I have remembered that we are covering our notebooks at school.
-Sometimes we also cover the books.)
+% TODO Lars Eighner BIB'e eklenecek.
 
-% TODO referans hatası olabilir.
 % NEW PART [collecting] 
+\subsection{Collecting}
 Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that
+
 \begin{quote}
@@
 \end{quote}
-I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.
 
-% There are similar points with my practice. I also check the condition of material.
+Does it discarded because of rotten, not fitting industrial standard or being production excess?
+For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards.
+Therefore these potatoes fall into the category of eatable.
 
-% TODO Sanatçı adını bulmak gerekli.
-% It can be viewed as mode of search for objects and it can be seen clearly on Dick Jewlss found photos.
-
-% Firstly I need to explore different locations to collect items. Most of them are not obvious for me. I discovered them on the flow of normal life and tasks.
-
-% The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation.
-Nobody cares others print out.
-
-% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.
-
-% Does it discarded because of rotten, not fitting industrial standard or being surplus (production excess)?
-For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards.
-Therefore these potatoes fall into the category of edible (eatable).
-They are in good quality but not liked shape???
-
-% [Mode of search] looking for waste bins.
-asking for people.
-realizing during the daily life.
-for example bank splits.
-I discover them during my life.
-For instance,  after I leaved bank split I realized that I can use them in my notebooks.
-Back of the splits are empty and appropriate for writing.
-Lots of them are used in the bank.
-The other places are discovered while daily life continues.
+I applied above instructions to my case and I checked discovered places regularly and seek the reason of why was it discarded.
+I also checked the condition of material.
+However I need to explore different locations to collect items.
+Most of them are not obvious for me.
+I discovered them on the flow of normal life and tasks.
+Similar to the methodology of Dick Jewell when searching for photos, my mode of search includes waste bins.
+However every object have a different story and they will be explained later.
 
@@
 % OWNER
-\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}.
+\quotes{The question of who owns these discards is not trivial} \citep{zimring2012encyclopedia}.
 This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects.
@@
 
-% TODO reference gerekli.
-% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
 The issue of owner becomes more complicated when owners' social status considered.
-Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood.
+Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood \citep[as cited in][]{pricano2011trashtalk}.
 On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.
@@
 % CONTRIBUTIONS OF PEOPLE
-% Bu kısmın daha güzel anlatılması gerekli.
-% TODO ref.
 As mentioned previously many people contributed to the project by collecting.
-Whenever i meet my friends I ask them to save their discard.
+Whenever I meet my friends I ask them to save their discard for the project.
 The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}.
@@
 
-% They provide me the materials to transform it.
+They provide me the materials to transform it.
 They select the items and find them.
@@
 
-% taxi drivers is wonder what will happen? they can not understand the idea here. not only collectors wonder but also people see me in action wonder the reason of it.
-
 The purpose is here not only to transform objects but also change the perceptions of trash. Asking people to collect things and inform them started to shift in peoples mind.
@@
 
-% TODO What type of activities generates waste.
-% Beyond social status it reveals activities that generate such a waste.
-It can be also extracted that most of the trashed papers are thrown away from feeding activity.
-On the other hand vastness of some types of disposables reveal the dark side of the some enterprises such as Starbucks and Burger King.
+% What type of activities generates waste.
+Beyond social status it reveals activities that generate such a waste.It can be also extracted that most of the trashed papers are thrown away from feeding activity.
+On the other hand vastness of some types of disposables reveal the dark side of the enterprises such as Starbucks and Burger King.
 Few people thought that after seeing the project I only collected Starbucks packets.
-There is no such a limitation but as a result of habitat the number of them suppress the others.
+There is no such a limitation but as a result of my habitat the number of them suppress the others.
 
@@
 
-% [Production, Recycling] \paraphrase{All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.
-Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper.
-Recycling paper can greatly diminish demand for virgin fiber from wood.
-However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely.
-It can only be recycled four to six times, as the fibers get shorter and weaker each time.
-In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.}
-
 Since paper is both biodegradable and a renewable resource, it is preferred by some of corporations for their products to show their respect to the nature.
@@
 
-% [importance of paper for me]
-% ilki resimden geliyor.
-Onu toplamaya başladım.
-ve daha onu tükettiğimi düşünmüyorum.
-bana hala bir sürü imkan tanıdığını düşünüyorum.
-Bir de yaygın kullanılması.
-Hala daha kimsenin görmediği küçük noktaları görmeye başlamamış olabilir.
+The reason of collecting papers based on my interest on painting and writing. This medium offers me great possibilities that I cannot consume yet. This project is one of them.
 
-% The importance of paper cames from previoulsy I mentioned.
-
-% Not only important for the community but also for me.
-
-% Kagit benim cevremde cok fazla kullanilan bir sey. yaygın kullanımı olması.
-
-% Çok basit bir şekilde çöp olarak görülen bir şeyi başka bir şey olarak görmek keyifli bir şey benim için. zaten dönüştürmek kullanmak için topluyorum.
-
-% Dönüştürme sebepleri.
-Neden sadece toplamakla yetinmiyorum.
-Yeni kompozisyonlar oluşturmak istiyorum.
-Farklı karşımlar elde etmek istiyorum.
-Bir tür şaşırtmak durumu...
-Beklenmeyeni yapmak...
-En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
-
+% TODO see figure appendix.
 Collected items are stored in my room for a long time.
 Most of them are not belong to me.
-Here the detailed information of the collected materials including the place where it is collected and their usage are listed.
-
-% Bu resme gerek olmayabilir. Appendixe konulabilir.
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
-  \caption{Collected materials}
-  \label{fig:CollectedAllTogether}
-\end{figure}
-
-% Packets and Bags.
-
-% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta.
-Diğerleri arkadaşın ofisinden, bir kısmı ise hocamdan.
-Bir kısmı da benim yoldan topladıklarım.
-
-% Toplama mekanları: Yollar, Bilkent labı. Sabahleyin geçtiğim yollarda genelde öğrencilerin bıraktıları simit pohaça gibi şeylerin paketleri bulunmakta.
-
-% Toplanan malzemeler ve toplanan mekanlar. Bilkent labaratuvarı, Restraurants, Pazar yeri, Kendi çalıştığım ofis,
-
-% Toplanan eşyalar mass produce üretilmiş ürünlerden oluşmakta.
-
-% Toplanan eşyalar çok fazla özel eşyalardan oluşan şeyler değil.
-Evsel atık değil.
-Evin dışından toplanan şeyler değil.
-Daha çok halka açık alanlarda üretilen çöpler benimki.
-Yani Tracey eminin kiler gibi benimkiler kişisel eşyalardan oluşmamakta.
-
-% Bu yüzden aslında toplanan eşyalarda kullanıcılarına ait çok fazla bir şey yok.
-Labdan alınanlardan olmakla birlikte, paket ve poşetlerde böyle bir durum yok.
-Found photosdaki gibi bir ilişki de yok mesela.
-
-% Elimde bazılarının fotoğrafları var bazılarının ise yok. Yani bazılarının kayıtları var, bazılarının ise yok.
-
-% Detaylı olarak bakmak gerekirse;
+Here the detailed information of the collected materials including the place where it is collected and their previous usage are listed.
 
 \textbf{Burger King packages} are collected from the office where I work.
-At launch time, some of the colleagues order the meal from Burger King which is a global chain of hamburger fast food restaurants.
+At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant.
 Meals are delivered to the office with paper packages.
@@
 
-% Yemek posetleri. Ogle vaktinde kurye tarafindan teslim ediliyor. Kağıt, yağı iyi emdiği için kullanılıyor burada.
+Inside the bag one paper package is used for French fries which is oily and paper is very good to absorb oil.
+Some people think that it is disgusting to use it for other purposes because of oil onto it.
+But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \cite[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}.
+She refers to resolution on dirt of \cite[36]{douglas2003purity}:
+\begin{quote}
+Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on.
+\end{quote}
 
-% Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy.
-Some people think that it is disgusting because of greasy onto it.
-But immediately I replied them just not you eat that greasy fires so what is wrong with it.
-At that time what Susan Strassed said comes my mind.
-(it fits here)
+This simply explains that our perceptions to the objects are relative and change in their usage context.
 
-% Nothing is inherently trash(5).
-matter out of place.
-Dirt is relative emphasize.
-"Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on" (Douglas 2003, 36-7)
-
-Why people throw them away varies.
-Through my experience I can give one anecdote that I encounter frequently.
-When I collect the papers under the dishes or food packages, people often think that it is disgusting and called them as dirty.
-However, it is very strange that the fat on the paper was previously what they are eating.
-
-\textbf{Starbucks packages} are collected from my supervisor, office and my friend.
-Especially my supervisor and friend saved and collected them from their friends.
+\textbf{Starbucks packages} are collected from my supervisor, office where I work and my friend.
+Particularly my friend saved and collected them from her friends.
+Few of them collected from waste bins.
 They are used as a cover of notebooks.
 There are different types of packets from this category.
-for some of them are build from recycled (precisely downcycled) paper, and the others packages for coffee beans.
-they are airtight and waterproof packages very solid and strong.
-and well graphic design with different color and illustration.
+As claimed by the company all of them are build from recycled ---precisely downcycled--- paper.
+There is also one category of object that is not paper.
+It is package of coffee beans.
+It is airtight and waterproof.
+It is very solid and strong.
+It has well graphic designs with different color and illustration.
 
-\textbf{Modshifters papers} that are covered on table and at the end of the day they are cut out and throw away.
-I go this place many times and every time questioned what they are doing to the papers.
-One of my visit we stay there at a late time and catch the garson collecting the old papers and preparing tables to the next customer or day.
-I ask him to give me and he kindly accepted.
-From this paper I covered [x] notebooks.
+\textbf{Modshifters papers} are used to cover the dinner table.
+Beginning of the table there is a big roll of paper to cover the table.
+At the end of the day used parts are cut out and thrown away.
+One of my visit I stayed there at a late time and catch the waiter when collecting the used papers and preparing tables to the next customer.
+I asked kindly him to give me these papers and he accepted.
+They are used as a cover of notebooks.
 All of them contains track of people who sit down there.
-I do not know them and I am not sure that the paper that they are sit down turned to such a thing.
+I do not know any of them and I am not sure that the paper that they are laid down on their dinner turned to such a thing.
 
-% Masaların üzerine örtülen ve sonra atılan kağıtlar.
+\textbf{Varuna Gezgin papers} are the pages of obsolete dinner menu.
+When leaving there I showed my notebooks and asked to the cashier that I could able to present them at Varuna Gezgin.
+He immediately mentioned their vast amount of unused papers and gave me some of them that I can able to carry with me.
+This was a very strange experience for me because I did not expect such a thing.
+These paper are used inside of the notebooks as a page.
 
-% Bir yandan da kağıtların nasıl kullanıldıklarına dair bir gösterge. Yemek için kullanılıyor. Gıda sektörü için.
+\textbf{The banner} is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates.
+In Middle East Technical University there is a tradition that in graduation ceremony new grads walk through in the stadium and greet to the tribunes.
+With this event they carry some banners to express their feelings and point out the issues of the country in an ironic and humorous way.
+This one of them.
+At that time there are serious debates about freedom on the web.
+Most of the website are banned from the decision to the courts and they were not accessible.
+The slogan (Access to this banner is blocked by a court decision) decided by the new grads and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.After the ceremony I could not throw away this banner.
+I do not know what to do it.
+It is a very big roll of paper to save but I could not throw away.
+I think that I will figure out later.
+Maybe I can use it as a draft paper.
+However is it worth to cut out this all long banner?
+Moreover to strengthen the banner we tape it from its boundaries.
+In other words some of the areas can not appropriate for writing.
+When I decided to my thesis subject I remembered to this banner.
+It stands in a corner in a dusty way.
+Now it is time to use it.
+It waited very log time and it is time to revive.
+I cut out them to the smaller pieces to use them as pages of notebooks.
+All pages have unique patterns.
+They contain parts of letters.
+Most of the time it is not recognizable belongs to which letter.
+These papers offers unique writing experience to the writer because of the patterns of letters and residue of tapes.
 
-% Buradaki kağıtlar tüm yemek masasının üzerine örtüyor.
-büyük bir rulo halinde masanın başında bulunuyor.
-yemek yendikten sonra masanın üzerindeki kısım yırtılıp atılıyor.
-yenisi rulodan seriliyor.
-ne kadar kağıt harcandığı bir bakışta anlaşılmakta.
-Tüm o rulodaki kağıtlar çöpe gidecek.
-Arkadaşlarla bir gün dışarı gittikten sonra buradaki kağıtları farkettim ve çıkışta onlar eskileri toplarken kağıtları topladım.
+By the way currently in Turkey the problem of banning web-sites continues.
+Event it can said that people do not surprises when a website is blocked by the courts.
+In other words still the slogan preserves its significance and through this project people will remember these days.
 
-\textbf{Varuna Gezgin}, is a cafe. papers of old menus. They are waited to be discarded.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
+  \caption{The banner carried by new grads, 2011}
+  \label{fig:Banner_1}
+\end{figure}
 
-% arkadaşlarla yemeğe gittikten sonra kasiyerdeki arkaştan defterleri burada verip veremeyeceğimi sorduktan sonra bana ellerindeki kağıtlardan bahsetti ve onları verebileceğinden bahsetti.
+\textbf{Order slips} are collected from bank office located at Technopolis of Middle East Technical University.
+They are used to record the order of customers.
+I realized that back of them are empty and appropriate for writing.
+Further there many others are waiting on the bin.
+After this experiment I really convinced that I am really looking for trash everywhere every time.
+The act of collecting spread through the every moment of life.
 
-% amacim aslinda sadece yemeklerin altindaki kagitlari toladiktan sonra bunlari bunrada gosterebilir miyiz diye sormakti.
-Ama sonrasinda konusmamizda bana bir suru kagit getirdi.
-Ellerindeki kullanilmayan kagitlarin sadec bir kismiydi.
-Zatenben tek basima cok ufak kucuk bir kismina dokumus oluyordum bunkaron.
-Hatta kasadaki cocuk kalanlari da ogrencilere dagitmayi dusundu.
-En azindan kenarda bekleyen kagitlar gun yuzue cikmis oldu.
+\textbf{A4 photocopy papers} are collected from Bilkent Computer Laboratory.
+In every lab there is a one printer.
+However when someone wants to print computers suggest firstly printer on the room 307.
+This result in many confusions and extra prints.
+I explored this place during my thesis research.
+I went there to print out draft of my thesis.
+I encountered that many papers are leaved on the tables.
+The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation.
+Nobody cares others print out.
+Papers are mostly composed of lecture notes.
+I collected many papers from there and they are used as a page of notebooks.
+I do not know owner of them and possibly users of notebooks so.
+However it will increase our realization of what other students in this university are dealing with.
+
+Similar type of papers are also taken from my friend. They are composed of his lecture notes. He donated them to the project.
+
+Collected items are not limited with these but for the others there are no special memory. Tea bags, collected packages from the streets are some of them.
+
+Most of the materials that I collect are mass produced items.
+Generally their usage fall into the two category; education and food industry.
+They are found on public places.
+They are not personal objects like in the work of Tracey Emin's \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets.
+Identity of owner are not certain.
+
+% Elimde bazılarının fotoğrafları (kayıtları) var bazılarının ise yok.
 
 % burdaki dikkate alinan sey satilan bir sey olmadigdi.
-Ktuphanede ise aslinda bunun bir reklam anlami tasiyip tasimayagi idi.
+Kütuphanede ise aslinda bunun bir reklam anlami tasiyip tasimayagi idi.
 Bilkent labindakiler ise bunukomsenin almayacagi dokunmayacagi yonundeydi.
@@
 
-% websitesinde amac bunlari anlatabilmekti.
-
-\textbf{Graduation banner} Because it is cut out from very big and long banner (which is carried at graduation ceremony at METU, 2011).
-Every piece was a part of bigger banner.
-At that time there are serious debates about freedom on the internet.
-Most of the website are banned from the decision to the courts and they were not accessible.
-(Access to this banner is blocked by a court decision.) In Middle East Technical University there is a tradition that in graduation ceremony people walk through in the stadium and greet to the tribunes.
-With this event they carry some banners to express their feelings and criticize some realities in the country.
-This one of them.
-It is carried by students (new grads of Computer Engineering) The slogan decided by among the students and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.
-After the ceremony I could not throw away this banner.
-I do not know what to do it, it is very big actually to store but I could not.
-I think that I will figure out later.
-Maybe I can use it as a draft paper.
-But is it worth to cut out this all long banner etc.
-Also to strengthen the banner and to prevent to tear while carried by the many people we are tape it from its boundaries.
-In other words some of the areas can not appropriate for writing.
-When I decided to this topic I remembered to this banner.
-It is stands in a corner in a dusty way.
-Now it is time use it.
-It waited very log time and it is time to revive again.
-Currently In turkey the problem of banning web-sites continues.
-Event it can said that people do not surprises when a website is blocked by the courts.
-It can be turn be a paper that people can freely express their ideas and feeling onto the it.
-Cut out them to the smaller pieces and make them as notebooks.
-They are part of puzzle.
-for the smaller parts what is written on them can not easily understandable.
-To realize what is the message is you have to bring together all of them again.
-But It is not possible, therefore website is a very good solution for them.
-All pages have unique patterns.
-Remaining parts of letter and tape.
-It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
-  \caption{Banner}
-  \label{fig:Banner_1}
-\end{figure}
-
-\textbf{Tea bags} are collected from my friend. Their a couple of consumption of tea and their covers.
-
-% Gıda sektörüne bir diğer örnek.
-
-\textbf{Order slips} are collected from bank office my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
-% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili.
-Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life).
-iş bankası örneğinde anlatılabilir.
-bir de art gallery found object örneği verilebilir.
-
-\textbf{Elginden gelen kağıtlar}
-
-%arkadastan gelen kagitlar.
-
-% Ders için kullanılanlar. Arkadaştan gelen kağıtlar, ders notları, tez yaprakları.
-
-\textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.
-
-% bilkent bilgisayar labindan toplanan kagitlar.
-Ben kendim ilk kez orada cikti aldigim zaman fark ettim.
-Bol miktarda kagit atilmisti.
-Bunlar aslinda tam da benim aradigim kagitlar olabilirdi.
-Okul ogrencileri buradan ihtiyaclari olan baskilari aliyorlardi.
-Her labaratuvarda birer tane yazici vardi.
-Labaratuvar sisteminde isleyisten kaynaklandigi dusundugum bir sebepten kagitlar orada birakiliyordu.
-Unutuluyorlardi.
-Ya da cikmadi zannedilip, fazladan bastiriliyorlardi.
-
-% Ders notları, çalışma notları, kişisel çıktılar.
-
-\textbf{Others} collected items are not limited with these by the remanings are little to open a new category.
-
-% tam olarak kategorolendirmeye degmeyecek cokgunlukta olan kagitlar. Bunlarin arasinda yemeklerin altinda toplanan kagitlar gosterilebilir. Sagdan soldan toplanan kagit paketler olabilir.
-
-% iki parcasi var defterin biri kapagi bir digeri de icindeki sayfalari.
-
-%as it can be seen here there are various types of paper and most of them some memories for me.???
-
-% websitesi aslinda
+% ozellikle resterantlardan bunkari tplarken, genekde garsonlar hemen almaya calisiyorlardi.
+Ben topladigimi soylerken bu zman yenisini getirmeyi teklif ediyorardi.
+Bu benim onceden bahsettigimaz tuketme kurali ile celismekteydi ve ben bunu reddediyordum.
 
 % NEW PART [transforming]
-%[experiments with paper.]
-
-% TODO sadece defter yapmakla uğraşmadım bşka şeyler de denedim.
-
-% [Artistic tactics] Here I followed some tactics to accomplish my purposes. Easy to carry while traveling. Small notebooks. Placing them to their routes.
-
-% bi de ben bunu insanlara vermek istiyordum o yüzden defter iyi bir şey.
-ve bu benim aslında bir taktiğim arkadaş.
-defter insanın yanında taşıdığı kullandığı bir şey.
-sadece galeri de olmayan başka alanlara da sızan bir şey olması önemli.
-
-% sadece belli bir yerde geösterile bir şey olmayıp yayılan, insanlarla birlikte hareket eden bir şey olmasını istiyorum.
-
+\subsection{Transformation}
 At one side while paper is being collected, on the other side I started to make experiments with the material.
@@
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.47\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
     \end{subfigure}
-    \caption{Experiments with collected paper}
+    \caption{Experiments with collected papers}
     \label{fig:ExperimentWithPaper}
@@
 % [notebooks]
+There are two main parts of notebooks; cover and pages.
 Papers that are mostly blank(empty) are used inside of the notebooks for writing.
@@
 
-% özellikle içinde kullandığım kağıtları karıştırarak oluşturdum. Burda dada şiiri ile benzerlikler içermekte.
+I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
+\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem};
 
-% Benim dönüştürme ve yeniden kullanma pratiğim ise daha önceden bahsedilen upcycling kategorisine girmekte.
-
-% Kullandığım ve malzemeler açısından bricolaj yöntemine yaklaşmaya çalışmak istesem de tam olarak ulaştığımı söyleyemem.
-Belli başlı bazı araçları satın aldım veya hazır kullandım.
-Bir diğer yandan ise benim işi yapmam uzunca bir süreyi kapsadığı için aslında o anda elde ne varsa ondan yapma tanımına da uymamakta.
-Kullandığım malzemelerde ise en profesyonel için olanı kullanmaya çalışmadım, eksik nelerse onları aldım onun dışındakiler için ihtiyaçlarımı kendim gidermeye, kendim yöntem bulmaya çalıştım.
+% TODO refre
+\begin{quote}
+Take a newspaper.\\
+Take some scissors.\\
+Choose from this paper an article the length you want to make your poem.\\
+Cut out the article.\\
+Next carefully cut out each of the words that make up this article and put them all in a bag.\\
+Shake gently.\\
+Next take out each cutting one after the other.\\
+Copy conscientiously in the order in which they left the bag.\\
+The poem will resemble you.\\
+And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
+\end{quote}
 
@@
 Further it provides what students from other departments works on.
-% What other students work on.
+What other students work on can be understand from these.
+
+There are different dimensions of notebooks. Most of them are half of A4 or quarter of it.
 
@@
 
-% Defter dikme yöntemi ???
+% TODO defter dikme yönteminin fotoğrafı
 
-% Kullandığım malzemeler. İğne, iplik, makas, maket bıçağı, raptiye, yapıştırıcı, ve yapıştırıcı.
+The tools used in the making of notebooks are as follows; needle, sewing thread, scissors, utility knife, pushpin, silicone, caulking guns.
 
-% TODO kullandığım malzemelerin listesi olabilir. fotoğraf çok fazla olur.
+While transforming collected materials my method can be explained with the term upcycling mentioned at the end of the Chapter 1.
+Further I tried to use objects already at hand.
+In other words I followed the bricolage technique.
+However I have to do buy some tools for my work.
+Therefore it is hard to consider it as bricolage but my intention is to follow it.
 
@@
 
-% amaç çeşitliliği arttırmak
+% The purpose is here to increase the diversity.
 
-% [showing]
-% [Exhibiting experiments] main question id how to give them to people?
+% Çok basit bir şekilde çöp olarak görülen bir şeyi başka bir şey olarak görmek keyifli bir şey benim için. zaten dönüştürmek kullanmak için topluyorum.
+
+% Dönüştürme sebepleri.
+Neden sadece toplamakla yetinmiyorum.
+Yeni kompozisyonlar oluşturmak istiyorum.
+Farklı karşımlar elde etmek istiyorum.
+Bir tür şaşırtmak durumu...
+Beklenmeyeni yapmak...
+En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.
+
+% [Artistic tactics] Here I followed some tactics to accomplish my purposes. Easy to carry while traveling. Small notebooks. Placing them to their routes.
+
+% bi de ben bunu insanlara vermek istiyordum o yüzden defter iyi bir şey.
+ve bu benim aslında bir taktiğim arkadaş.
+defter insanın yanında taşıdığı kullandığı bir şey.
+sadece galeri de olmayan başka alanlara da sızan bir şey olması önemli.
+
+% NEW PART
+\subsection{Demonstration}
 After producing notebooks the most important point is to present and reach to people.
+Main question is how to give them to people.
 Starting point is to stack the notebooks onto the each other, and there are other ideas like putting them inside a waste bin to re-do the action of throwing away.
 After ward somehow they should understand that these notebooks can be taken.
-I set up makets and tried some installations of them.
+I set up models and tried some installations of them.
 
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
-        %\caption{Sax}
+        %\caption{}
         \label{fig:exhibition1}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
-        %\caption{Violin}
+        %\caption{}
         \label{fig:exhibition2}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
-        %\caption{Violin}
+        %\caption{}
         \label{fig:exhibition3}
@@
 Different placements were tried.
-All of them looked like sculpture.
-I have inserted no special meaning as sculpture to this object an I also I am afraid that people does not close them to the notebooks and look them away.
-which I do not want.
+All of them looked like a sculpture.
+I have inserted no special meaning as sculpture to this objects.
+I also afraid that people will not interact with them and look them away.
+My purpose is give people.
+Aim is to spread the idea by making something useful from trash.
+Increase diversity, encourage people to embrace the trash.
 
-Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.
-
-% Bu örnekle insanlara daha fazla yakın olmam gerektiğini gösterdi bana. onların ayaklarına bu proje gitmeliydi. ziyaret ettikleri bir yerde olmalıydım.
-
-% [Why in the public space?] To reach more audience.
-Actually the audience is out of the art galleries.
-They are walking in the streets.
-Putting them to next to people is much more effective.
-It is not visible and nearly it is hided from society.
-It is dirty.
-Removed from the society.
-There is a effort to hide them away.
-However in this project it is again showed to the society.
-Because it is revisited and reclaimed.
+These experiments showed me that I need to place them to the locations where people frequently visit.
+It must be inside of the life.
+As it is collected publicly it must be showed publicly.
+Thus the project can reach more audience.
+It will spread and can be showed in different contexts.
+Notebooks can move with people.
 
 % TODO [Why giving away?] Felix Gonzales Torres, Unlimited Editions.
-% TODO insanlar bu defterleri alsınlar.
+
+% The \quotes{Untitled} series of Felix Gonzales Torres inspired me a lot when deciding giving notebooks away.
+He has created variations on the theme of the “stack,” which consists of “unlimited” editions of offset prints.
+Visitors can take a copy of them.
+
+% TODO insanlar bu defterleri neden alsınlar.
+
+% [Website]
+
+% websitesinde amac bunlari anlatabilmekti. 
+% Anlattığım bir çok şeyi sadece deftere bakarak anlamak mümkün değil ve ben bunların insanlara ulaşmasını istiyorum.
+buradaki seçeneklerden bir tanesi site ile onlara ulaşmaktı.
+temel sebeplerden bir tanesi bu mediumda ben tecrübeliydim.
+for the smaller parts what is written on them can not easily understandable.
+To realize what is the message is you have to bring together all of them again.
+But It is not possible, therefore website is a very good solution for them.
+
+Beyond all of these for the audience the story of the collected materials is a mystery.
+Audience are not aware from all of these written in this thesis.
+I want to reveal the act behind these notebooks.
+For that reason a website that store the records of collected materials can be helpful.
+They can visit there anytime.
+The other other reason that I select to website is I am fluent in web development.
 
@@
 %
-\section{Parts of project (or final work)}
-% TODO la olum bir önceki kısımla bir ilişki kur istersen ha?
-The project introduced in this thesis have different parts. Each part support the other. They are connected with each other. Different parts lead different inqueries.
+\section{Parts of the Final Work}
+% The development progress result in different part of the objects.
+As also can be understood by the previous section the project introduced in this thesis have different parts.
+Each part support the other.
+They are connected with each other.
+Different parts lead different inquiries.
 
@@
 \subsection{Notebooks}
-
-% TODO notebook hakkında daha fazla şey söylebilmelisin tamam?
 
@@
 
-Every notebook has numbers and with this numbers it can be tracked down when it was produced and which materials are used production of it.
+Every notebook has unique serial and with this it can be tracked down when it was produced and which materials are used production of it.
+Serial is generated through the first letter of composed metarial.
 
-There are notebook series that have a name. Here are the name of notebooks and their story:
+Giving name is another hard topic for me.
+However point out the story behind the notebooks and properties of it.
+These nanes gives clues about how they are combined what they represent, defines the aspects of them.
+Name of the paper can be related with this place and related with the meaning.
+These names captures the memory of notebooks.
+However for one serie i barrowed the idea of nonsenseword generation from the kurt.
+similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word.
+There are notebook series that have a name.
+Here are the name of notebooks and their story:
 
-\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (Figure \ref{fig:Banner_1}).
-As mentioned previously the objects are bring their history.
-They are not blank.
-Heterogen, hiybrid.
-It can be one of the examples of this argument.
+\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (see figure \ref{fig:Banner_1}).
+Every piece is a part of bigger banner.
+Pages of paper is similar to the pieces of puzzle.
+All of them are composes the banner.
+However they are cut out and give away combining them is not possible but the image of the original one can be viewed on the website.
 
-\textbf{09:00 am.} Breakfast time. I think that these packages are used at the morning, very the beginning of the day.
+It provides unique layout for writing and I strongly think that all the notebooks after used have strong visual impact.
 
-\textbf{12:00 pm.} Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
+As mentioned previously the objects are bring their history. They are not blank, they are heterogeneous and hybrid. It can be one of the examples of this argument.
 
-\textbf{Friday Night.} (Maybe there can be another option related with traveling, or union).
-These notebook's pages are collected from restaurant "Varuna Gezgin".
+\textbf{Reunion.} These notebook's pages are collected from restaurant "Varuna Gezgin".
 We go there to meet some friends after long time.
 One of them is coming from Australia, the other one is coming from Norway.
-they are my friends from the university.
+They are my friends from the university.
 We united again at varuna gezgin.
@@
 
-% Name of the paper can be related with this place and related with the meaning.
+Same exist for the paper actually, they seperated and by the action making notebooks they are also reunited again.
 
-% Refer to 9 canlı.
-Never dies, revives again and again.
-Because trash moves in the community, even if thrown away can be find another use.
-Ikinci kez degilde ucuncu kez kullanilan bir sey olursa aslinda onkara dokuz canli demek istiyorum.
-Gorunus acisindan farkli olmasalar da aslinda isin farkli yanlarini gormek icin faydali olabilirler.
+\textbf{Second hand} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.
 
-% 9 canlı (cat) / puzzle / bir de dada kelimesi. 9 canlı olmanın kaynağı neresi abi..
-
-% Maybe Later
-% Counter Argument:
-% People may think and raise the question that none of notebooks is actually my work they belongs to others, others(Starbucks, Burger King) designed it and I am stealing their work.
-Here there are available different answers to the question.
-Firstly they are different once they are designed.
-Turned to different thing.
-I suggest that them to consider in different context like Duchamp.
+\textbf{Dada}
 
@@
 
-Notebooks are places where people frequently visit such as computer desks.
+Notebooks are placed where people frequently visit such as computer desks.
 
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.47\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
@@
 
-% Bilkent, METU, Milli Kütüphane. Buraya nasıl gidilecek. Ama öncelik zaten bilkent kütüphanesinde. ODTÜ sonra geliyor.
+% su anda sadece bilkente yerlestirildi. Odtuye daha koyamadim. Neden koymadim. Nicin koymadim. Koymali miyim?
 
-% TODO bir çok insanın ortaklaşa kullandığı bir alan. kesişim alanı. bir tanesi de özellikle zaten toplanan yer. insanların karşılaşmalarını istiyorum. karşılaşma noktası.
+% bir çok insanın ortaklaşa kullandığı bir alan. kesişim alanı. bir tanesi de özellikle zaten toplanan yer. insanların defterlerle karşılaşmalarını istiyorum.
 
@@
 
-% TODO  [Yerleştirme fotoğrafları]
-
+% Torun
 Through this project another exhibition alternative is thought.
@@
 
+I used wooden market boxes to lift up them from ground to more reachable height.
+It is hole body of stand to put notebooks.
+Notebooks are placed on the top box and below them I just put the collected items to provide for those who want to make their own notebook.
+People can get them both.
+Further it reveals the process of the production of the notebooks.
+Shows the previous state of the materials.
+
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.47\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
     \end{subfigure}
-    \begin{subfigure}[b]{0.47\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
         \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
@@
 \end{figure}
+
+These are example placement.
+The exhibition event is not held.
+It is only decided.
+These notebooks are not only exhibited there, but also I will turn it to an workshop that continue to produce notebooks and show people to how to do it.
+Maybe they will join me in the production of notebooks.
+They can bring their items and transform all together.
+We can share our ideas and thoughts with each other.
 
@@
 % MAYBE LATER
-% trasnformation practices...
+% transformation practices...
 % Notebooklar insanın yanında kolayca taşınabildiği için aslında bir yandan fikri yaymak için ideal. Zaten showing off'un ne kadar önemli olduğu rubbish theoryde söylenmişti.
 
-% MAYBE LATER
-% [Standartlar, Dönüştürme seviyesi] endüstriyel standartlar, kaplar ve kağıtlar hep bir şekilde bir birleriyle boyut olarak uyuşuyorlar.
-İlk başlarda kesip biçmeye daha çok ihitiyaç duyarken zamanla basit katlamalar işimi görmeye başladı.
-Ne kadar az müdahele bulunursam aslında o kadar çok geldiği yerin özelliklerini o kadar çok temsil ediyordu.
-Bu da benim hoşuma gidiyordu.
-Kolaj mantığı işte abi.
-Ne kadar çok değiştirmek dönüştürmek istiyorsun.
-Burda şöyle bir durum var.
-çöpleri hiç tanınmayacak bir hale de getirebilirsin.
-Bu şekilde kimse onların farkına bile varmaz.
-Ya da neredeyse olduğu gibi kullanırsın.
-Yani uygulanan dönüştürmenin derecesi çok önemli burada...
+% their dimensions matches.
+In the production phase of the boxes, I discovered that my folded notebooks are fit into the many cardboxes.
+In other words dimensions of them are not very different.
+This property of items make the production easy.
+System supports the reuse of the object with less effort in this way.
+
+At first I often cut the paper to match the dimensions of notebooks but later only folding gives the same result.
+Thus I can preserve their state.
+While turning objects to the notebooks I tried to be preserve their look and feel.
+Olabildigince az mudahelede bulundum.
+Bu sekilde onceki halleri hakkinda daha cok fikir sahibi olunabilir.
+Ben copleri taninir halde birakmak istiyordum.
+Neredeyse olduklari gibi biraktim.
+Gerisini onu kullananlara biraktim.

### 2016-01-08 drafts.tex
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d

@@
 Ben ilgilinilmeyenle ilgileniyorum.
+
+\chapter{Uncategorized}
+
+%****************************************
+% RESOURCES:
+%
+% Plagiarism check: http://mashable.com/2012/08/29/plagiarism-online-services/
+% What is Plagiarism: http://www.plagiarism.org/plagiarism-101/what-is-plagiarism
+%
+% How to cite epigraph: http://blog.apastyle.org/apastyle/2013/10/how-to-format-an-epigraph.html
+%
+% Artist ve artist statementlar için kaynak:
+% - http://www.amandadonahue.com/artist-statement/
+% - http://www.smfa.edu/cyclo-show
+% - http://www.gwynethleech.com/statement
+%........................................
+
+%**************************************
+% HERE Same sample phrases are listed you can use them:
+
+% The work that follows is divided into three sections
+
+% The artist thinks, acts, performs music, and writes outside the framework that society has created.
+
+% This thesis takes a rather different approach to the resonant possibilities of discarded things.
+It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
+
+% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.
+
+% I’d like to criticize a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.
+
+% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.
+
+% This thesis is written as a study of the socio-economic change that is currently happening in Serbia, but it’s a study that critically engages with everyday materials that provide the basis for change, rather than the economic development philosophies that are practiced through policy.
+%........................................
+
+%%%
+%%%
+%%%
+\section{In Theory}
+
+% TODO PRAP. REF.
+% FROM Recycle the Classics, BY DORIS SOMMER
+% Her alanda recycling var olabilir, literatürde de vardır?
+\comment{WHAT, WHERE?} Literature is recycled material, a pretext for making more art.
+I learned this distillation of lots of literary criticism in workshops with children.
+I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation.
+For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress.
+
+\comment{MOVES} \paraphrase{Igor Kopytoff, a professor of anthropology, introduced the notion of commoditization “as a process of becoming rather than as an all-or-none state of being.” As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
+(Igor Kopytoff, “The Cultural Biography of Things: Commoditization as Process)} \todo{ref.}
+
+\comment{MOVES} \paraphrase{Objects moves around and their values change constantly.
+(The idea that objects lead social lives was elaborated and discussed in detail in Arjun Appadurai (ed.).
+The Social Life of Things: Commodities in Cultural Perspective)}\todo{ref.}
+
+% Like a summary sentence
+\comment{TRASH MOVES.} Here the important thing is moving nature of trash.
+Objects moves and gains different meanings through this movement.
+Sometimes it becomes artwork, sometimes it becomes archaeological part, waits in the dump-site or wait to be recycle.
+It also signifies that it is relative and result of a classification issue.
+All of them are creates a harmony.
+supports each other with different words and conceptualization.
+
+% <From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
+\comment{TRASH MOVES.} \paraphrase{Below part Explains journey of trash, its different steps.
+Object moves and also trash also moves.
+How is it life of trash?
+This part explains life of trash.
+How does it intersect with other people in which places?
+This part also can be understand by pointing out different part of it with detailed explanation.
+For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
+In other words there are different places to touch on trash.
+Every place generates different story?
+Or to understand it more deeply it covers different part of it.
+Or provides ideas about it.
+Lots of people touches it from philosophers to artist.
+Also in the later parts it draws attention to them.}
+
+% Ama çöp olarak zaten kalmıyor bu trash bir şekilde hayatımıza tekrar giriyor.
+Ne kadar itise de...
+Trashion: the return of disposed.
+trash moves.
+Peki geri dönüşü nasıl bir değişiklik yaratıyor.
+Ya da gerçekten geri geliyor mu?
+Kullandığımız ürünlerin ne kadarı tek kullanımlık.
+Tek kullanımlıklarla nerede karşılaşıyoruz.
+Evet belki hayatımızda çok kullanılan şeyler var fakat.
+daha tek kullanımlıklar da var denilebilir.
+\comment{TRASH MOVES.} \paraphrase{Trash moves, all the time.
+It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
+Even in the landfill, it does not remain still.
+Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
+More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
+When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
+This is how trash moves.
+But\ldots who moves on trash?
+In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
+In Latin America, it is mostly people.
+People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
+In many of the garbage dumps around the world, scavenging becomes a steady job.
+\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
+(through the works of Filomena Cruz's photographic series “Road Kill”)}
+% >
+
+\comment{WASTE AND TECHNOLOGY RELATIONSHIP} \quotes{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design} \cite{mcdonough2010cradle}.
+In other word the problem is our technology which is not perfect.
+(and I'm not sure that at some point that technology will reach to the perfection or not.)
+
+% WHO OWNS TRASH?
+kısmı benim işimde sorgulanabilir, ya da ünlülerin trashlerini inceleyen adam kısmında ele alınabilir.
+Orada aslında başkalarının trashlerinin insanlar hakkında neler anlattığını çok güzel anlıyoruz.
+\comment{ANALOGY Between landfill and graveyards.
+WHOSE TRASH?} \quotes{There’s a relationship between graveyards and landfills, one that makes us uncomfortable, Zubiaurre explained.
+\quotes{What is happening to trash is what is going to happen to us.
+We’re all going to end up in a dump, and we’re going to decompose.
+That’s the ultimate destiny of humankind, and we don’t want to face that.} Trash is also regarded differently, depending on where you live.
+Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said.
+But when the same student went to Beverly Hills to go through trash, the police were nearly called.
+\quotes{Who decides what is public and what is private?
+How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?} Zubiaurre said.} \cite{zubiaurre2015trash}
+
+\comment{TRASH AND OTHER DISCARDED NOTIONS} From my point of view and approach in this thesis, trash is only one of the thing that is being discarded by humans and communities.
+There are lots of things that are being excluded such as homosexuals, trans, disabled peoples etc.
+Even if they are excluded, there is also life for them.
+
+% TODO Reference
+\comment{WHAT?} John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
+
+% FROM Culture, Values, and Garbage, Encyclopedia 
+\comment{INTERACTION WITH GARBAGE.
+VALUE SYSTEM, DECIDING TO GARBAGE.} \paraphrase{"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
+In terms of their relationship to garbage, all people interact with it on two levels.
+One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
+In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
+Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
+The second connection that people maintain with garbage is an ideational one.
+Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
+The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
+Instead, humans determine whether the object is of value or whether it is considered trash.
+The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
+The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}
+
+% FROM Garbage in Modern Thought, Encyclopedia
+\comment{THROW AWAY CULTURE.} \paraphrase{"Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.”" "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
+It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
+Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
+
+% FROM Garbage in Modern Thought, Encyclopedia
+\comment{CATEGORIZATION.} \paraphrase{"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
+Consumers have become accustomed to the categories that are often applied to garbage.
+Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper) and smaller subsets (such as PET or 01, PE-HD or 02, and PVC or 03).
+Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}}
+
+% Garbage is universal, reference
+\comment{NO VALUE, UNIVERSAL} \paraphrase{"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
+Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
+While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
+Many non-Western societies attach a much greater value to items after they are discarded.
+In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
+Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
+People define what is trash and what is valuable." \cite{lukas2012garbage}}
+
+% Hepsinin ayrı bir manası olması falan.
+\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
+
+\comment{read resource (Trash as History/Memory) \cite{bullock2012trash}}
+
+% Walter Benjamin's trash aesthetics and Adornos reflection? Bu konudan ben hiç bir şey anlamadım açıkcası. Çünkü ne dedikleri ne yaptıkları hiç belli değil.
+\todo[inline]{BU NE OLACAK?
+NEREYE BAGLANACAK, GARBOLOGY??}\paraphrase{\quotes{Benjamin’s approach to history is through \singlequotes{trash}---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}.
+Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity.
+In the face of the endless proliferation of trash, Benjamin potentially suggests a \singlequotes{trash aesthetics} that could be used radically and critically to attend to the everyday.
+The method might be thought of in terms of \singlequotes{recycling} --- an ecology of everyday experience.}
+
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\comment{LIFE AN OBJECT} \paraphrase{In light of this argument, one could claim that the end of the life of an object corresponds to the moment in which it is disposed of.
+This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
+In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+\comment{REFLOW IN THE MARKET} \paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+\comment{TECHNICAL PROBLEM, NEED TO MANAGED, RECYCLING (CAPITALISM), UPCYCLING} \paraphrase{On the contrary, with respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
+The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
+Waste now became evil.
+If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
+Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
+Upcycling...
+On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
+Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
+In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
+In short, there is a whole sector of upcycling now.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+\comment{DESIGN, ALTERNATIVE DICIPLINE.} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
+People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+
+\comment{UPCYCLING, sample thesis statement sentence} \paraphrase{This article is about those objects that are recreated from trash through the process of upcycling.
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” I argue that design, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+This theory counters the argument that an object is dead once it is disposed of.} \todo[inline]{Reference, (Trashion: The Return of the Disposed by Bahar Emgin).}
+
+\comment{CATEGORIZATION OF WASTE} \paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
+(Think that the transformation process.
+Previous argument support that the transformation of trash is possible by changing the place of them.
+In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
+For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.} \todo{Reference, (Waste by William Viney).}
+
+\comment{CATEGORIZATION OF WASTE} \paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
+Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
+
+\comment{CATEGORIZATION OF WASTE} \comment{susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte.
+Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda.
+Remember the example given: shoes  on the dinner table.}
+
+\comment{CATEGORIZATION OF WASTE} \paraphrase{waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
+
+% https://narratingwaste.wordpress.com/tag/king-lear/
+% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.
+
+% Cornelia Parker's work, narrate an absent event of waste
+% There is also strong relationship with the collecting discarded stuff and archeologies of waste.
+
+%%%
+%%%
+%%%
+\section{In Art}
+
+\comment{Crowdsourcing artworkümde neden insanlardan topladığımı, neden onları kullanıdığımı anlatacağım yer ile ilgili olabilir.}
+
+%*************************************
+% Phrases...
+% What specific social issues are you trying to address through Labyrinth?
+% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art.
+Table 1 organizes this classification according to a set of multiple criteria.
+(But this one can be used at introduction, but it is too long to fit on introduction.
+Maybe select works by giving prominence to some of the features.
+So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art.
+Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.)
+\subsection{Crowdsourcing, Participation, Open Work}
+\todo[inline]{TODO needs reference, FROM Crowdsourced Art and Collective Creativity}
+In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}.
+The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers.
+Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing.
+Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.
+
+The value of crowdsourcing lies in the collective intelligence of the contributors.
+Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p.
+13).
+The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism.
+Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004).
+Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?
+
+All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks.
+They are not bought, not gift.
+They are found.
+They are accepted.
+One of the most creative medium is paper and pencil.
+Chance given to the people through this work.
+
+However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment.
+It is well studied area.
+Pick a method here.
+Transforming trash with collaboration.
+
+As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).
+
+Here this question can be raised about why this type collaboration.
+Another option can be working together with people on a table.
+Creating things at that time and transforming the objects here.
+Possibly the connection to the people will more realistic and intense.
+However same things can be succeed on the internet at some level.
+
+While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers.
+(This totally a new area to discuss, I'm going to summarize and introduce concepts and debates.
+How are they support my work and how they are give way to me?)
+
+% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories.
+Principally, my interest is in answering two key questions.
+What is crowdsourced art and how can it be classified?
+And how does the structure of the artwork determine the degree or significance of participation?
+
+% why collaboration, is it really a collaboration? It is methodology used in my practice.
+
+% TODO: Umberto Eco's Open Work
+
+%*************************************
+% ARTWORKS:
+
+% Dark Matter: Explosive View.
+
+%.....................................
+
+%*************************************
+% Solid claims about its cultural aspect.
+\subsection{Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap}
+\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
+From western trash to tribal treasure.
+\paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods.
+A disposable item becomes imminent desire and profound social consequence.
+(Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}
+
+\comment{HYBRIDITY} They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}
+
+\comment{SEMIOTIC CONTEXT} \quotes{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
+Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others.
+(Jacknis 1992)} \todo{ref.}
+
+\comment{HYBRIDITY} \paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another.
+Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
+It is story of people --- the women, men, children etc.
+one person's trash into another's treasure.}
+
+\comment{OTHER DICIPLINE, INDUSTRY} \paraphrase{the process of re fabrication explored here is not to be confused with the kind of industrial strength recycling to which we in the West are most accustomed.
+When we think of recycling in America and other industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers.
+returned to the industrial process.
+solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.}
+
+\comment{DIFFERENT SCALES OF RECYCLING} There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ...
+
+[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
+It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders
+
+\todo[inline]{yerlinin fotoğrafı}
+\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
+In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}
+
+\comment{CONSUMER CULTURE} \paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these essays are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}
+
+\comment{CONSUMER CULTURE, SORUCE OF TRASH} While consumption has provided a foundation for the transnational capitalist system adntheus has much longer history than the last fifty years this thesis focused on the more recent history.
+because it is during the history of consumption.
+consumption can be though that as global not to a western or first world countries.
+
+\comment{GLOBAL} It is not limited with geography, ethnicity, gender, nationality.
+The process of of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of amazonian rain forest.
+
+\comment{GLOBAL, SELECTING COMMODOTIES, } To frame a discussion that incorporates an understanding of such diverse locations, objects, and peoples is to claim links between material process that originate under vastly different social, economic, environmental, and political circumstances.
+\ldots The most obvious link are the raw materials the raw materials themselves: the packaging, broken pieces.
+becomes raw materials for other things.
+these consumer items.
+and it is spreated globally.
+It can be seen remotest corner of the world.
+the indigenization of western objects.
+(sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"?
+Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves.
+They do not necessarily despise our commodities.
+But they are selective in their demands and transformative of their uses of such things.
+(sahlins, 13)"
+
+\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
+It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."
+
+\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
+the irony is often embodied visually and conceptually.
+opposite of natural use, expected perception.
+for example making something from nothing or turning trash into treasure.
+By juxtaposing different materials changing context and place.
+
+\quotes{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}
+
+[initial function throw away society] \comment{Karşı çıktığım şeylerden birisi objelerin ilk manaları, ilk kullanım alanları.
+many scholar stated the general attitude in the society.
+It is key ingredients of throw away society.
+initial function is fulfilled by }
+
+\comment{How does it become trash?, initial function.} when an object is discarded it is perceived as being no longer of value to the person or society that once possessed it.
+Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown out as trash.
+
+[Chapter 2] rubbish Theory \comment{DEFINITION} Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control.
+As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
+The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.
+
+[Chapter 2] \comment{Capitalism, market.} The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap.
+They were designed to decrease in value over time - to be used one, or twice and than to be thrown away.
+This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
+themselves.
+\todo[inline]{Waste and wantta bununla ilgili bir bölüm olmalı.}
+
+[building new things from ruin] \comment{small amount of it} while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population.
+Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and transformed back into an object of greater or lesser durability.
+
+[Resistance] \comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+(sahlins 1992, 16)"
+
+\comment{hybrid} each recycled object contains within it a reference to two or more distinct times.
+\comment{not every time actually, if you transfor ok.
+it applicable for my case.} Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992) \todo{ref.}
+
+[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse.
+but even if they have no economical struggle, they continue recycle.
+what is the reason of it.} Recycling as an economic strategy of survival in developing countries throughout the world.
+creative production that is motivated, primarily, by adverse conditions of economic necessity.
+(lanfill orchestra here.
+bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised.
+(p25)

### 2016-01-08 appendix_materials.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
Appendix
Former-commit-id: f50b1827cfcdd3397352f16ee911421b2a0086a8

@@
-\appendix
-\chapter{Examples of collected materials}
+\chapter{COLLECTED MATERIALS AND MAKING OF}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
+  \caption{Collected materials all together}
+  \label{fig:CollectedAllTogether}
+\end{figure}
+
+% BugerKing - Starbucks
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_burgerking.jpg}
+    \caption{Burger King Bag}
+    \label{fig:BurgerKingBag}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_starbucks.jpg}
+    \caption{Starbucks Bag}
+    \label{fig:StarbucksBag}
+  \end{minipage}
+\end{figure}
+
+% Coffee Packages - Liva Bag
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_coffee_packages.jpg}
+    \caption{Coffee Packages}
+    \label{fig:CoffeePackages}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_liva.jpg}
+    \caption{Paper Bag}
+    \label{fig:LivaBag}
+  \end{minipage}
+\end{figure}
+
+% Envolpe - Bank Slips
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_envelope.jpg}
+    \caption{Envelope}
+    \label{fig:Envelope}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_bankslips.jpg}
+    \caption{Bank Slips}
+    \label{fig:BankSlips}
+  \end{minipage}
+\end{figure}
+
+% Varuna Gezgin - Cardboard
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_cardboard.jpg}
+    \caption{Cardboard}
+    \label{fig:CardBoard}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_varuna_gezgin.jpg}
+    \caption{Menu Pages}
+    \label{fig:VarunaGezgin}
+  \end{minipage}
+\end{figure}
+
+% Waste bin - Modshifters
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_from.jpg}
+    \caption{Waste Bin}
+    \label{fig:CardBoard}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{project_graphics/collected_modshifters.jpg}
+    \caption{Modshifters}
+    \label{fig:Modshifters}
+  \end{minipage}
+\end{figure}

### 2016-01-08 chapter4_reduced.tex
fixing errors
Former-commit-id: cb1fa634f5502bfce534528cc9f2324c88009894

@@
 Its role in the development of human civilization can not be neglected.
-(Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people.
+(Paper in several forms is consumed on a daily basis \citep{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people.
 On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage.
@@
 \begin{quote}
-Take a newspaper.\\
-Take some scissors.\\
-Choose from this paper an article the length you want to make your poem.\\
-Cut out the article.\\
-Next carefully cut out each of the words that make up this article and put them all in a bag.\\
-Shake gently.\\
-Next take out each cutting one after the other.\\
-Copy conscientiously in the order in which they left the bag.\\
-The poem will resemble you.\\
+Take a newspaper.
+Take some scissors.
+Choose from this paper an article the length you want to make your poem.
+Cut out the article.
+Next carefully cut out each of the words that make up this article and put them all in a bag.
+Shake gently.
+Next take out each cutting one after the other.
+Copy conscientiously in the order in which they left the bag.
+The poem will resemble you.
 And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
@@
 
+% TODO boxes and wooden cases
+To hold notebooks together I made several small boxes from discarded card boxes. Notebooks are put inside of them.
+
+In the production phase of the boxes, I discovered that my folded notebooks are fit into the many card boxes.
+In other words dimensions of them are not very different.
+This property of items make my production more easier.
+It shows that industrial system supports the reuse of the object with less effort in this way.
+
+% Rubbish Theory showing off.
+
 % TODO [Why giving away?] Felix Gonzales Torres, Unlimited Editions.
@@
 I want to reveal the act behind these notebooks.
-For that reason a website that store the records of collected materials can be helpful.
+However there is a lot information that can not be fit into the pages of notebooks.
+For that reason such problems was clearly solved through a website that store the records of notebooks and collected materials.
 They can visit there anytime.
-The other other reason that I select to website is I am fluent in web development.
+The other other reason that I select to website is I am comfortably and confidently fluent in coding and web development.
 
@@
 \section{Parts of the Final Work}
-% The development progress result in different part of the objects.
 As also can be understood by the previous section the project introduced in this thesis have different parts.
@@
 
-Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memoranda by many artists, scientists, and thinkers through the ages.
+Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memorandum by many artists, scientists, and thinkers through the ages.
 Further same exist for me and people around me.
@@
 Every notebook has unique serial and with this it can be tracked down when it was produced and which materials are used production of it.
-Serial is generated through the first letter of composed metarial.
+Serial is generated through the first letter of composed material.
 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.48\textwidth}
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.48\textwidth}
     \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
-    \end{subfigure}
+    \caption{Library}
+    \label{fig:BilkentLibrary}
+  \end{minipage}
   \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
+  \begin{minipage}[b]{0.48\textwidth}
     \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
-    \end{subfigure}
-    \caption{Example placement at Bilkent}
-    \label{fig:ExperimentWithPaper}
+    \caption{Computer Laboratory}
+    \label{fig:BilkentLaboratory}
+  \end{minipage}
 \end{figure}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
+        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
+        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
     \end{subfigure}
-    \caption{Example placement at Torun}
+    \caption{Sample placement at Torun}
     \label{fig:ExperimentWithPaper}
@@
 \subsection{Website}
-As I think that finding a place to the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.
+Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people's life again, but also it finds another place in the digital space.
 
-Mainly websites displays the (hi)story of notebooks.
-Further it is a place to track the journey the notebooks.
-As I claimed that it is not a finished work.
+Mainly website displays the (hi)story of notebooks.
+It contains a section for how notebooks are produced and the story behind it.
+The purpose is to record the creative process and share with others.
+Revealing the process is significant to demystifiying the truth about the project.
+It makes it more clear that the object used here is actually transformed from something else.
+People can access to images and descriptions of notebooks.
+All the development process of the project will be revealed in this website.
+Will contain list of collected materials.
+
+Into the notebooks a sticker which contains qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
+  \caption{Sample of QR code and notebook serial}
+  \label{fig:Banner_1}
+\end{figure}
+
+Website is a place to track the journey the notebooks.
 Transformation of it does not completed.
 It always continues.
-Therefore a website that anyone can reach and share their progress via website  Anyone can later discover how they turned to new things.
+Therefore a website that anyone can reach and share their progress via website will show their evolution in time.
+Anyone can later discover how they turned to new things.
 
-As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.
-
-It will contain a section for how notebooks are produced and the story behind it.
-The purpose is to record the creative process and share with the others.
-Revealing the process is significant to demystifiying the truth about the project.
-It makes it more clear that the object used here is actually transformed from something else.
+As I leave notebooks different places I do not have connection with people who take them. This website also will help to share peoples ideas about the notebooks.
 
@@
 
-% [Why website] (database, establishing communication, tracking in time) It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in coding and web development.
-
-Website can be accessible through the this address http:\\kulu.be\\notebook-project.
+Website can be accessible through this address http:\textbackslash\textbackslash kulu.be\textbackslash notebook-project.
 Domain name kulu.be belongs to me and project placed under a directory of it.
@@
 Pages are generated by Jekyll which is a static website generator through it some repetitive works are can be easily automatized.
-
-People can access to images and descriptions of notebooks. All the development process of the project will be revealed in this website. Will contain list of collected materials.
-
-Into the notebooks a sticker which contains qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
-  \caption{QR Code sample}
-  \label{fig:Banner_1}
-\end{figure}
 
@@
 In the future it is planned that through the website people can be able to request to get notebooks.
-Thus project becomes more accessible to the other people.
+Thus notebooks become more accessible to the other people.
 Moreover notebooks done by others from trash can be added to the website.
 Beyond notebooks various objects transformed from trash can find a place in the website.
-
-% MAYBE LATER
-% transformation practices...
-% Notebooklar insanın yanında kolayca taşınabildiği için aslında bir yandan fikri yaymak için ideal. Zaten showing off'un ne kadar önemli olduğu rubbish theoryde söylenmişti.
-
-% their dimensions matches.
-In the production phase of the boxes, I discovered that my folded notebooks are fit into the many cardboxes.
-In other words dimensions of them are not very different.
-This property of items make the production easy.
-System supports the reuse of the object with less effort in this way.
-
-At first I often cut the paper to match the dimensions of notebooks but later only folding gives the same result.
-Thus I can preserve their state.
-While turning objects to the notebooks I tried to be preserve their look and feel.
-Olabildigince az mudahelede bulundum.
-Bu sekilde onceki halleri hakkinda daha cok fikir sahibi olunabilir.
-Ben copleri taninir halde birakmak istiyordum.
-Neredeyse olduklari gibi biraktim.
-Gerisini onu kullananlara biraktim.

### 2016-01-08 chapter4_reduced.tex
adding missing points
Former-commit-id: e0bc8a55ecfaec1fb59d7c767d7a834a1bc15614

@@
 
+% I'm collecting the paper that are under the plates.
+When we are leaving this place, I ask the cashier at the desk that \quotes{I am making small notebooks and is it possible to exhibit there?} I asked that is it possible to give them to people.
+Firstly he asked me that did I sell them or not but I said \quotes{no they are free and part of my thesis project.} After that he offered me to give e are a lot of unused papers.
+I can give you.
+they are not used and waiting to be recycling.
+I took some of the papers, and that papers are part the sheets of these papers.
+
 \textbf{The banner} is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates.
@@
 
-% TODO refre
 \begin{quote}
@@
 % TODO boxes and wooden cases
-To hold notebooks together I made several small boxes from discarded card boxes. Notebooks are put inside of them.
+To hold notebooks together I made several small boxes from discarded card boxes. Notebooks were put inside of them.
 
@@
 However point out the story behind the notebooks and properties of it.
-These nanes gives clues about how they are combined what they represent, defines the aspects of them.
+These names gives clues about how they are combined what they represent, defines the aspects of them.
 Name of the paper can be related with this place and related with the meaning.
 These names captures the memory of notebooks.
-However for one serie i barrowed the idea of nonsenseword generation from the kurt.
-similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word.
+However for one series I borrowed the idea of nonsense word generation from the Kurt Schwitters.
+Similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word.
 There are notebook series that have a name.
@@
 
-\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (see figure \ref{fig:Banner_1}).
+\textbf{Puzzle.} Papers inside of these notebooks are cut out from very big and long banner (see figure \ref{fig:Banner_1}).
 Every piece is a part of bigger banner.
@@
 
-\textbf{Reunion.} These notebook's pages are collected from restaurant "Varuna Gezgin".
-We go there to meet some friends after long time.
-One of them is coming from Australia, the other one is coming from Norway.
-They are my friends from the university.
-We united again at varuna gezgin.
-The place also interesting story.
-It is a place of travelers.
-It supports them.
-and the decoration of that place contains a lot of items collected from different sides of the world.
+\textbf{Reunion.} These notebook's pages are collected from restaurant Varuna Gezgin, in Ankara.
+We went there to meet some friends after long time.
+One of them was coming from Australia, the other one was coming from Norway.
+They were my friends from the university.
+We united again at this restaurant.
+The place has also similar story.
+Their founders and workers travel around the world.
+It is a popular restaurant of travelers.
+The decoration of that place contains a lot of items collected from different sides of the world.
 The concept of the place and our meeting perfectly matched.
-I'm collecting the paper that are under the plates.
-When we are leaving this place, I ask the guy at the desk, I am making small notebooks and is it possible to exhibit there.
-I said that is it possible to give them to people.
-Firstly he asked me that selling them but I said no they are free and part of my thesis project.
-and later he offered me there are a lot of unused papers.
-I can give you.
-they are not used and waiting to be recycling.
-I took some of the papers, and that papers are part the sheets of these papers.
+Same exist for the papers actually, they are separated from big paper rolls in the factory and by the action making notebooks they are also reunited again.
+These notebooks represent my memory about the place.
 
-Same exist for the paper actually, they seperated and by the action making notebooks they are also reunited again.
+\textbf{Secondhand.} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.
 
-\textbf{Second hand} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.
-
-\textbf{Dada}
+% TODO burada bir isim uydurmak gerekli.
+\textbf{Dada.} For some of the notebooks it is not obvious to name them.
+At this point approach of Kurt Schwitters provide me a way.
+He created his frequently used word \quotes{Merz} from an advertisement.
+It is a nonsense word and used it most of his works.
+I followed what he did and generated a word from a paper.
+I use this word for the ones the story of them are not obvious and significant.
 

### 2016-01-08 chapter5.tex
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
adding missing points
Former-commit-id: e0bc8a55ecfaec1fb59d7c767d7a834a1bc15614

@@
 
-Inseparable part of our activities.
-Trash is everywhere.
-Part of our activities.
+% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.
+
+% Toplama mekanları: Yollar, Bilkent labı.
+Sabahleyin geçtiğim yollarda genelde öğrencilerin bıraktıları simit pohaça gibi şeylerin paketleri bulunmakta.
+Bilkent labaratuvarı, Restraurants, Pazar yeri, Kendi çalıştığım ofis,
+
+Trash is everywhere and produced every time.
+It is inseparable part of our activities.
 Rubbish as an object state is not static.
-Its value, usage may vary according to the people.
+Its value, usage might vary according to the people.
 Artistic intentions are aimed to transform the material.
@@
 
-% This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.
+This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.
 
-% This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material.
-
-% Through the analysis of selected works metadologies, approaches, placement trash, positing of trash ...
+This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material. 
+Through the analysis of selected works methodologies, approaches, placement trash, positing of trash ...
 show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.
@@
 %
-\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers.
+During the process I have also generated lots of trashed papers.
 Cutting and pasting things also leave unused items.
@@
 %
-\textbf{Future Works.} Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
+Web site will expand in time. New notebooks from different papers (in terms of location, meaning, usage purpose)
 

### 2016-01-08 chapter4_reduced.tex
adding missing parts
Former-commit-id: 39df71832a3bfe85638abe835222f964c95f8651

@@
 
-% Rubbish Theory showing off.
+% TODO Rubbish Theory showing off.
 
@@
 However there is a lot information that can not be fit into the pages of notebooks.
-For that reason such problems was clearly solved through a website that store the records of notebooks and collected materials.
-They can visit there anytime.
-The other other reason that I select to website is I am comfortably and confidently fluent in coding and web development.
+For that reason such problems can be clearly solved through a website that store the records of notebooks and collected materials.
+People can visit the website anytime.
+Further I am comfortably and confidently fluent in coding and web development.
+Therefore it is more appropriate for the scope of this thesis.
+
+Notebooks will be given away.
+They will continue to flow between people.
+There is a possibility that notebooks can be trashed again.
+However vice verse is possible.
+In other words they might turn to durable objects as mentioned in Rubbish Theory.
+At this time, decision belongs to people.
+However website serve great functionality here.
+While the notebooks have potentials to be rubbish, records of them in the website are preserved.
 
@@
 % TODO burada bir isim uydurmak gerekli.
-\textbf{Dada.} For some of the notebooks it is not obvious to name them.
-At this point approach of Kurt Schwitters provide me a way.
-He created his frequently used word \quotes{Merz} from an advertisement.
-It is a nonsense word and used it most of his works.
-I followed what he did and generated a word from a paper.
-I use this word for the ones the story of them are not obvious and significant.
+\textbf{Daro.} For some of the notebooks it is not obvious to name them.
+At this point approach of Kurt Schwitters provides me a way.
+He generated his frequently used word \quotes{Merz} from an advertisement.
+It is a nonsense word and used in most of his works.
+I followed what he did and generated a word from the papers that used inside of the notebooks.
+I use the word \quotes{Daro} extracted from \quotes{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.
 

### 2016-01-08 chapter2_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

@@
 %
-\section{Throw away culture}
+\section{Throw Away Culture}
 
@@
 % Portraits of Global Mass culture
-\begin{figure}[h!]
-\centering
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
-  \caption{Original view}
-  \label{fig:ChrisJordan_Numbers_CloseView}
-\end{subfigure}
-\hfill
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
-  \caption{Close view}
-  \label{fig:ChrisJordan_Numbers_OriginalView}
-\end{subfigure}
-\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
-\label{fig:ChrisJordan_Numbers_CapsSeurat}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{subfigure}{.48\textwidth}
+%  \centering
+%  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
+%  \caption{Original view}
+%  \label{fig:ChrisJordan_Numbers_CloseView}
+%\end{subfigure}
+%\hfill
+%\begin{subfigure}{.48\textwidth}
+%  \centering
+%  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
+%  \caption{Close view}
+%  \label{fig:ChrisJordan_Numbers_OriginalView}
+%\end{subfigure}
+%\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
+%\label{fig:ChrisJordan_Numbers_CapsSeurat}
+%\end{figure}
 
@@
 
+% John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
+He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
+
 % Here, sculptures from trash can be added.
@@
 % FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
-  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
-  \label{fig:RubySilvious_TeaBag}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
+%  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
+%  \label{fig:RubySilvious_TeaBag}
+%\end{figure}
 
@@
 % FROM http://www.gwynethleech.com/
-\begin{figure}[h!]
-\centering
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
-  \caption{Installation view}
-  \label{fig:GwynethLeech_Installation}
-\end{subfigure}
-\hfill
-\begin{subfigure}{.47\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
-  \caption{Painting in the public}
-  \label{fig:GwynethLeech_Public}
-\end{subfigure}
-\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
-\label{fig:GwynethLeech_CoffeeCups}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{subfigure}{.48\textwidth}
+%  \centering
+%  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
+%  \caption{Installation view}
+%  \label{fig:GwynethLeech_Installation}
+%\end{subfigure}
+%\hfill
+%\begin{subfigure}{.48\textwidth}
+%  \centering
+%  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
+%  \caption{Painting in the public}
+%  \label{fig:GwynethLeech_Public}
+%\end{subfigure}
+%\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
+%\label{fig:GwynethLeech_CoffeeCups}
+%\end{figure}
 
@@
 
+% the installation consists of the complete contents of her home, amassed over fifty years during which the Chinese concept of wu jin qi yong, or "waste not," was a prerequisite for survival.
+The assembled materials, ranging from pots and basins to blankets, oil flasks, and legless dolls, form a miniature cityscape that viewers can navigate around and through.
+
 %
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
-  \caption{Song Dong, Waste Not, 1990}
-  \label{fig:SongDong_WasteNot}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=8cm]{graphics/SongDong_WasteNot.jpg}
+%  \caption{Song Dong, Waste Not, 1990}
+%  \label{fig:SongDong_WasteNot}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
-  \caption{Tracey Emin, My Bed, 1998}
-  \label{fig:TraceyEmin_MyBed}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
+%  \caption{Tracey Emin, My Bed, 1998}
+%  \label{fig:TraceyEmin_MyBed}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
-  \caption{Thompson’s Rubbish Theory}
-  \label{fig:rubish_theory}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
+%  \caption{Thompson’s Rubbish Theory}
+%  \label{fig:rubish_theory}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/Cesar_Zim.jpg}
-  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
-  \label{fig:Cesar_Zim}
-\end{figure}
+% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor.
+Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.
+
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
+%  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
+%  \label{fig:Cesar_Zim}
+%\end{figure}
 
@@
 However, Duchamp's notable ready-made "Fountain" is one of the examples outside of the defined transitions.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
-  \caption{Marcel Duchamp, Fountain, 1917}
-  \label{fig:Duchamp_Fountaine}
-\end{figure}
 
@@
 In another word, it is not rubbish.
+
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
+%  \caption{Marcel Duchamp, Fountain, 1917, Porcelain urinal}
+%  \label{fig:Duchamp_Fountaine}
+%\end{figure}
 

### 2016-01-08 chapter3_reduced.tex
fixing errors
Former-commit-id: cb1fa634f5502bfce534528cc9f2324c88009894
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/picasso_chair.png}
-  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
-  \label{fig:Picasso_Chair}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/picasso_chair.png}
+%  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
+%  \label{fig:Picasso_Chair}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
-  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
-  \label{fig:Duchamp_BicycleWheel}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
+%  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
+  %\label{fig:Duchamp_BicycleWheel}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
-  \caption{Still image from Amélie}
-  \label{fig:Amelie}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
+%  \caption{Still image from Amélie}
+%  \label{fig:Amelie}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
-  \caption{Dick Jewell, Found Photos, 1978}
-  \label{fig:DickJewell_FoundPhotos}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
+%  \caption{Dick Jewell, Found Photos, 1978}
+%  \label{fig:DickJewell_FoundPhotos}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
-  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
-  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
+%  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
+%  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-  \caption{Filomena Cruz, Road Kill, 2014, Photography}
-  \label{fig:FilomenaCruz_RoadKill_ReVista}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
+%  \caption{Filomena Cruz, Road Kill, 2014, Photography}
+%  \label{fig:FilomenaCruz_RoadKill_ReVista}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
-  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
-  \label{fig:VicMuniz_PicturesOfGarbage}
-\end{figure}
+% TODO resim yanlış
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
+%  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
+%  \label{fig:VicMuniz_PicturesOfGarbage}
+%\end{figure}
 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
-        \caption{Sax}
-        \label{fig:landfill_harmonic-sax}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
-        \caption{Violin}
-        \label{fig:landfill_harmonic-violin}
-    \end{subfigure}
-    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
-\end{figure}
+%\begin{figure}
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
+%        \caption{Sax}
+%        \label{fig:landfill_harmonic-sax}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
+%        \caption{Violin}
+%        \label{fig:landfill_harmonic-violin}
+%    \end{subfigure}
+%    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
-  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
-  \label{fig:Alsbrooks}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
+%  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
+%  \label{fig:Alsbrooks}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
-  \caption{Michael Landy, Art Bin, 2014}
-  \label{fig:MichaelLandy_ArtBin}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
+%  \caption{Michael Landy, Art Bin, 2014}
+%  \label{fig:MichaelLandy_ArtBin}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
-  \caption{Michael Landy, Break Down, 2001}
-  \label{fig:MichaelLandy_BreakDown}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
+%  \caption{Michael Landy, Break Down, 2001}
+%  \label{fig:MichaelLandy_BreakDown}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
-  \caption{Still image from The Gleaners and I}
-  \label{fig:AgnesVarda_Potatoes}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
+%  \caption{Still image from The Gleaners and I}
+%  \label{fig:AgnesVarda_Potatoes}
+%\end{figure}
 

### 2016-01-08 chapter4_reduced.tex
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
-    \end{subfigure}
-    \caption{Examples of early works}
-    \label{fig:EarlyWorks}
-\end{figure}
+%\begin{figure}
+%    \begin{subfigure}[b]{0.31\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.31\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.31\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
+%    \end{subfigure}
+%    \caption{Examples of early works}
+%    \label{fig:EarlyWorks}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
-  \caption{Recycling notice on the package}
-  \label{fig:NoteOnPackage}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
+%  \caption{Recycling notice on the package}
+%  \label{fig:NoteOnPackage}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
-  \caption{The banner carried by new grads, 2011}
-  \label{fig:Banner_1}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
+%  \caption{The banner carried by new grads, 2011}
+%  \label{fig:Banner_1}
+%\end{figure}
 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
-    \end{subfigure}
-    \caption{Experiments with collected papers}
-    \label{fig:ExperimentWithPaper}
-\end{figure}
+%\begin{figure}
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
+%    \end{subfigure}
+%    \caption{Experiments with collected papers}
+%    \label{fig:ExperimentWithPaper}
+%\end{figure}
 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
+%\begin{figure}
+%    \begin{subfigure}[b]{0.31\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
         %\caption{}
-        \label{fig:exhibition1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
+%        \label{fig:exhibition1}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.31\textwidth}
+ %       \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
         %\caption{}
-        \label{fig:exhibition2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
+  %      \label{fig:exhibition2}
+   % \end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.31\textwidth}
+     %   \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
         %\caption{}
-        \label{fig:exhibition3}
-    \end{subfigure}
-    \caption{Installation experiments with models}
-    \label{fig:exhibition}
-\end{figure}
+      %  \label{fig:exhibition3}
+    %\end{subfigure}
+    %\caption{Installation experiments with models}
+    %\label{fig:exhibition}
+%\end{figure}
 
@@
 
-\begin{figure}[!tbp]
-  \centering
-  \begin{minipage}[b]{0.48\textwidth}
-    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
-    \caption{Library}
-    \label{fig:BilkentLibrary}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.48\textwidth}
-    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
-    \caption{Computer Laboratory}
-    \label{fig:BilkentLaboratory}
-  \end{minipage}
-\end{figure}
+%\begin{figure}[!tbp]
+%  \centering
+%  \begin{minipage}[b]{0.48\textwidth}
+%    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
+%    \caption{Library}
+%    \label{fig:BilkentLibrary}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}[b]{0.48\textwidth}
+%    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
+%    \caption{Computer Laboratory}
+%    \label{fig:BilkentLaboratory}
+%  \end{minipage}
+%\end{figure}
 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
-    \end{subfigure}
-    \caption{Sample placement at Torun}
-    \label{fig:ExperimentWithPaper}
-\end{figure}
+%\begin{figure}
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.48\textwidth}
+%        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
+%    \end{subfigure}
+%    \caption{Sample placement at Torun}
+%    \label{fig:ExperimentWithPaper}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
-  \caption{Sample of QR code and notebook serial}
-  \label{fig:Banner_1}
-\end{figure}
+%\begin{figure}[h!]
+%  \centering
+%  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
+%  \caption{Sample of QR code and notebook serial}
+%  \label{fig:Banner_1}
+%\end{figure}
 

### 2016-01-08 main.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

@@
 \usepackage{apacite}
-\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
+\usepackage[a4paper,left=40.1mm,top=24.1mm,right=25.1mm,bottom=36mm]{geometry}
 \usepackage{epigraph}
@@
 \usepackage[usenames,dvipsnames]{color}
-\usepackage[titletoc]{appendix}
+\usepackage[titletoc,title]{appendix}
 \usepackage[colorinlistoftodos]{todonotes}
@@
 
+% Bibliography line spacing
 \usepackage{natbib}
@@
 
+\usepackage{xpatch}
+
+\xpatchbibmacro{date+extrayear}{%
+  \printtext[parens]%
+}{%
+  \setunit*{\addperiod\space}%
+  \printtext%
+}{}{}
+
+% Footnote line spacing
+\setlength{\footnotesep}{\baselineskip}
+
 % Adding extra space between paragraphs
 \setlength{\parskip}{\baselineskip}
+
+% Quote spacing
+\expandafter\def\expandafter\quote\expandafter{\quote\singlespacing}
 
@@
 % Chapter title spacing
-\titlespacing{\chapter}{0pt}{25mm}{3\baselineskip}
+\titlespacing{\chapter}{0pt}{9mm}{3\baselineskip}
 
-% EPIGRAPH
-\setlength{\epigraphwidth}{.6\textwidth}
+% Epigraph setup
+\setlength{\epigraphwidth}{.65\textwidth}
 \setlength{\epigraphrule}{0pt}
 
+% PDF setup
 \hypersetup{
@@
 
+% Utilities
 \providecommand{\quotes}[1]{``#1''}
@@
 %****************************************
-% Title Ideas for Thesis 
-% - Trash as an Artistic Medium
-% - Notebooks from Trash: Trash in the Context of Art
-% - Notebooks from Trash: Exploring the potential of trash through art practice
-% - Transforming Trash as an Artistic Act
-% - Act of Transforming Trash in the Context of Art
-%........................................
-
-%****************************************
 % BEGIN
@@
 
-        \vspace*{25mm}
-        \uppercase{Transforming Trash as an Artistic Act}
-
-        \vspace{15mm}
+        \vspace*{20mm}
+        \uppercase{Transforming Trash as an Artistic Act}\\
+        \vspace*{3\baselineskip}
         A Master’s Thesis\\
-        \vspace{15mm}
+        \vspace*{3\baselineskip}
         by\\
@@
         January 2016
-        \vspace{25mm}
+        \vspace*{28mm}
 
@@
 		İhsan Doğramacı Bilkent University\\
+		\vspace*{2\baselineskip}
+        by\\
+       	\vspace*{2\baselineskip}
+        MUSTAFA İLHAN\\
         \vspace*{3\baselineskip}
-        by\\
-       	\vspace*{3\baselineskip}
-        MUSTAFA İLHAN\\
-        \vspace*{4\baselineskip}
         In Partial Fulfilment of the Requirements for the Degree of\\
-		MASTER FINE OF ARTS\\
-        \vspace{2\baselineskip}
+		MASTER OF FINE ARTS\\
+        \vspace{\baselineskip}
         in\\
-        \vspace{2\baselineskip}
+        \vspace{\baselineskip}
         THE DEPARTMENT OF\\
@@
 \begin{center}
-	\vspace*{25mm}
+	\vspace*{7mm}
 	\MakeUppercase{Abstract}\\
@@
 \begin{center}
-	\vspace*{25mm}
+	\vspace*{9mm}
 	\MakeUppercase{Özet}\\
@@
 \begin{center}
-	\vspace*{25mm}
+	\vspace*{7mm}
 	\MakeUppercase{ACKNOWLEDGMENTS}\\
@@
 
-\setlength{\cftbeforetoctitleskip}{25mm}
+\setlength{\cftbeforetoctitleskip}{19mm}
 \setlength{\cftaftertoctitleskip}{3\baselineskip}
@@
 %\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}
+
+% Spacing between items
+\setlength{\cftbeforesecskip}{\cftbeforechapskip}
+\setlength{\cftbeforesubsecskip}{\cftbeforechapskip}
 
@@
 
+% Spacing between items
+\makeatletter
+\def\@chapter[#1]#2{\ifnum \c@secnumdepth >\m@ne
+	\refstepcounter{chapter}%
+	\typeout{\@chapapp\space\thechapter.}%
+	\addcontentsline{toc}{chapter}%
+	{\protect\numberline{\thechapter}#1}%
+	\else
+	\addcontentsline{toc}{chapter}{#1}%
+	\fi
+	\chaptermark{#1}%
+	\if@twocolumn
+	\@topnewpage[\@makechapterhead{#2}]%
+	\else
+	\@makechapterhead{#2}%
+	\@afterheading
+	\fi}
+\makeatother
+
 \renewcommand{\cftloftitlefont}{\normalfont\MakeUppercase\hfil}
@@
 
-\setlength{\cftbeforeloftitleskip}{25mm}
+\setlength{\cftbeforeloftitleskip}{19mm}
 \setlength{\cftafterloftitleskip}{3\baselineskip}
+\setlength{\cftbeforefigskip}{\cftbeforechapskip}
 
@@
 \clearpage
-%{%
-%\let\oldnumberline\numberline%
-%\renewcommand{\numberline}{\figurename~\oldnumberline}%
-%\listoffigures%
-%}
 %........................................
@@
 %........................................
-
-%\listoftodos
 
@@
 %........................................
+
+% TODO yıl olayını düzeltmeli
+% Bibliographyden sonra 4 boşluk olmalı?
 
@@
 % APENDICES
-\begin{appendices}
-\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
-\include{appendix_glossary}
-\include{appendix_materials}
-\include{appendix_project}
-\end{appendices}
+%\appendix
+
+%\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
+%\chapter*{APPENDICES}
+%\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}
+
+%\addtocontents{toc}{\cftpagenumberson{chapter}}
+
+%\makeatletter
+%\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
+%\makeatother
+
+%\include{appendix_glossary}
+%\include{appendix_materials}
+%\include{appendix_project}
 %........................................

### 2016-01-08 chapter1_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
reorganization
Former-commit-id: e5cf9d1ed889ae9676d7eb070201bb31780d7a02

@@
 %\summary{Facts}
-\begin{singlespace}
 \begin{quote}
@@
 %\summary{Parts of us}
-\begin{singlespace}
 \begin{quote}
@@
 Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}.
-
-Technological perspectives are one them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
+Technological perspectives are one of them.
+Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.
 % Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
@@
 In addition to these
-\begin{singlespace}
 \begin{quote}
+%\vspace{-\baselineskip}
 the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed.
 When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}.
+%\vspace{-\baselineskip}
 \end{quote}
-\end{singlespace}
 
@@
 % FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
-\begin{singlespace}
 \begin{quote}
@@
 This thesis project is about those objects that are recreated from trash through the process of upcycling.
+
+% FROM Susan Strasser
+% According to the Oxford English Dictionary, recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste.
+Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.
+
+% RUBBISH NEWSPAPER
+
+% All these variety of words forms her research and rubbish newspaper.
+
+% these all words commonly used to refer is a subject of Alice Bradshaw's thesis and work. She analyzes each word in her rubbish newspaper. Figure X shows newspaper cover photo.
+
+% The Museum of Contemporary Rubbish continues a tradition of celebrating and reversing the status of low culture objects within the ‘high status’ gallery space.
+Bradshaw reflects on this connection between rubbish and contemporary artistic practice in the Rubbish newspaper which is given away to visitors at the show.
+A large body of research is disseminated and contextualised in this throwaway (often unwanted) medium of the free newspaper.
+The subject of rubbish is broken down into its taxonomic elements (eg detritus, rejects, litter), these sub-categories become collections in themselves, of theories and works that have now been transformed through the disposable nature of the newspaper as medium.
+The paper communicates this research in a way which reflects on the content: through quotations, references and Bradshaw’s charmingly simplistic renderings of the artworks she cites, each section is made up of remains.
+Here, Bradshaw has linked a review of discarded waste with contemporary practice, and, even further, she adapts Walter Benjamin’s method in the paper made up of quotations, and an exhibition consisting of elements found whilst wandering the urban space.
+Connecting the writer’s earlier comparison of the poet and rag picker, here the artist becomes the collector and hoarder of waste.
+
+% Her works shows us that the increasing interests on the subject starting from the beginning of the 20th century.
+
+% use it "brings to mind"

### 2016-01-17 chapter2_reduced.tex
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352

--- 2015-12-29 chapter2_reduced.tex
@@
 \begin{figure}[h!]
-\centering
-\begin{subfigure}{.47\textwidth}
+\begin{subfigure}{.48\textwidth}
   \centering
@@
 \hfill
-\begin{subfigure}{.47\textwidth}
+\begin{subfigure}{.48\textwidth}
   \centering
@@
 \end{subfigure}
-\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
+\caption{Chris Jordan, \textit{Caps Seurat}, 2011, 60x90" in one panel, and 88x132" in 3 panels}
 \label{fig:ChrisJordan_Numbers_CapsSeurat}
@@
   \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
-  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
+  \caption{Ruby Silvious, \textit{Day 169, 363 Days of Tea}, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
   \label{fig:RubySilvious_TeaBag}
@@
 \end{subfigure}
-\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
+\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
 \label{fig:GwynethLeech_CoffeeCups}
@@
   \centering
-  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
-  \caption{Song Dong, Waste Not, 1990}
+  \includegraphics[height=8cm]{graphics/SongDong_WasteNot.jpg}
+  \caption{Song Dong, \textit{Waste Not}, 1990}
   \label{fig:SongDong_WasteNot}
@@
   \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
-  \caption{Tracey Emin, My Bed, 1998}
+  \caption{Tracey Emin, \textit{My Bed}, 1998}
   \label{fig:TraceyEmin_MyBed}
@@
 
+% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor.
+Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.
+
 \begin{figure}[h!]
   \centering
-  \includegraphics[height=6cm]{graphics/Cesar_Zim.jpg}
-  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
+  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
+  \caption{César, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
   \label{fig:Cesar_Zim}
@@
 In another word, it is not rubbish.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
+  \caption{Marcel Duchamp, \textit{Fountain}, 1917, Porcelain urinal}
+  \label{fig:Duchamp_Fountaine}
+\end{figure}
 

### 2016-01-17 chapter3_reduced.tex
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352

--- 2016-01-08 chapter3_reduced.tex
@@
   \includegraphics[height=6cm]{graphics/picasso_chair.png}
-  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
+  \caption{Pablo Picasso, \textit{Still Life with Chair Caning}, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
   \label{fig:Picasso_Chair}
@@
   \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
-  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
+  \caption{Marcel Duchamp, \textit{Bicycle Wheel}, 1913 (authorised reproduction 1951, original lost)}
   \label{fig:Duchamp_BicycleWheel}
@@
   \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
-  \caption{Dick Jewell, Found Photos, 1978}
+  \caption{Dick Jewell, \textit{Found Photos}, 1978}
   \label{fig:DickJewell_FoundPhotos}
@@
   \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
-  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
+  \caption{Tim Gaudreau, \textit{Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I}, 2006, Photograph}
   \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
@@
   \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
-  \caption{Filomena Cruz, Road Kill, 2014, Photography}
+  \caption{Filomena Cruz, \textit{Road Kill}, 2014, Photograph}
   \label{fig:FilomenaCruz_RoadKill_ReVista}
@@
 
+% TODO resim yanlış
 \begin{figure}[h!]
@@
   \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
-  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
+  \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
   \label{fig:VicMuniz_PicturesOfGarbage}
@@
   \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
-  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
+  \caption{Kim Alsbrooks, \textit{Gen. Jefferson Davis}, 2015, oil on aluminum can}
   \label{fig:Alsbrooks}
@@
   \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
-  \caption{Michael Landy, Art Bin, 2014}
+  \caption{Michael Landy, \textit{Art Bin}, 2014}
   \label{fig:MichaelLandy_ArtBin}
@@
   \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
-  \caption{Michael Landy, Break Down, 2001}
+  \caption{Michael Landy, \textit{Break Down}, 2001}
   \label{fig:MichaelLandy_BreakDown}

### 2016-01-17 chapter1_final.tex
Proof reading
Former-commit-id: d835c4ff57c702c8f90dae1816f3609db8679019

--- 2015-12-29 chapter1_reduced.tex
@@
 
-%
-%
-%\summary{Trash exists in every age and every society} 
-Refuse is part of people's daily consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}. 
-%\todo{more ref.} 
-For archaeologist dumps are one of the significant places to figure out what people consume in the ancient times \citep{rathje1992rubbish}.
-%\summary{Global}
-%It is not limited with geography, ethnicity, gender, nationality.
-The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.
+According to dictionary Merriam-Webster, trash means anything useless, worthless or discarded.
+In parallel to this definition, the common perception is to get rid of them as soon as possible.
+People tend to think that trash is valueless because it is no longer needed or not wanted anymore.
+People want to get rid of them not thinking any alternative.
+Stav says that \quotes{[t]hey forget about it and don’t think about all the time and energy and money put into disposing of it} \citep[as cited in][]{navarro2015followingtrash}.
+On the other hand the issue of trash and transformation is not that simple.
+There are a lot of points to examine the trash.
+
+% TODO Summarize
+% Change in the production and consumption practices
+\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}.
+As the result of it amount of goods boost and the cost of them significantly reduced.
+Things once reused again and again, now thrown away because it is more affordable to replace with new one.
+As the production increased its by-product material waste is also increased.
+\quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.
+
+% Dominant approaches
+During the last decades much attention has been devoted to the waste.
+In particularly environmental considerations dominates the perceptions of waste.
+\cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.
+
+The act of trashing objects and the process of transforming them is not limited with geography, nationality and modern ages.
+It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}.
+Anyone can encounter with trash in the crowded urban areas \quotes{as well as the remotest corners of the world} \citep[16]{cerny1996recycled}.
+
 Trash is everywhere and, produced every time.
-\quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes} \citep{zimring2012encyclopedia}.
-Various activities of our life such as eating, drinking, working, traveling leave behind wastes.
-People are surrounded by all kinds of goods and they are consuming everywhere while walking, working and traveling.
-The pattern is spread to all day and different places.
+It is inseparable from people's activities.
+\quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from} \citep[xxv]{zimring2012encyclopedia} their habitat.
+In other words, refuse is part of people's daily activities.
+Production of it never stops.
+Various activities of life such as eating, drinking, working and traveling leave behind wastes.
+These activities are not only taking place every time, but also spread to different places such as homes, offices and picnic areas.
 It is hard to say that any place is waste free.
-Nearly every place people require waste bin.
-If people do not find a waste bin, they often leave their trash to the ground.
-Production of trash never stops.
-It is inseparable from people's activities.
-%\summary{Trash is everywhere} 
-Trash is in the streets, in your home, in the sea that you swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
-Even if trash is tried to be moved away from people life, it is as close as nearest waste bin.
+Nearly every place require waste bin because people can easily access vary kinds of goods that are going to be thrown away after used.
+If people do not find a waste bin, they often leave their trash wherever possible.
 
-%
-% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
-%\summary{Facts}
-\begin{singlespace}
-\begin{quote}
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
-Turkey is a member of this organization.} countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \citep{fash2015trash}.
-\end{quote}
-\end{singlespace}
-
-% Üstteki kısmı neden diyorsun? Teze nasıl bir katkı sağlıyor? Throw away culture a taşınabilir.
-% From recycled book.
-Similar to these as stated by \cite{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.}
-
-%
-%
-%\summary{Moves} 
-The vast amount of discarded items spread through the landfills to oceans.
-As commodities spread to the every corner of the world, trash do also.
-It moves from homes to garbage trucks, from streets to landfills and also from waste bins to sculptures.
-Various people including garbage collectors and artist touches to trash.
-It is not static, not fixed, not totally isolated from us.
+Trash is in the streets, in people's home, in the sea that people swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
+Even if trash is tried to move away from people's habitat, it is as close as the nearest waste bin.
 
@@
 
-%\comment{What happens when it is traveled to the other countries, how do people approach these items?
-They find new uses and meanings on them because their understanding of that items is different.} \todo{Bu soru daha sonraki bölümde sorulabilir.}
+The vast amount of discarded items spread through the landfills to oceans.
+As commodities spread to the every corner of the world, trash do also.
+It moves from homes to garbage trucks, from streets to landfills and also from landfills to sculptures inside museums.
+In other words, trash is not only found on the most disgusting and avoided places, but also can be found on the most steril and frequently visited places.
 
-%
-%
-%\summary{Common}
-In the dictionary, 
-%\todo{Which dictionary?}
-trash means anything useless, worthless or discarded.
-In parallel to this definition, the common perception is to get rid of them as soon as possible.
-People tend to think that trash is valueless because it is no longer needed or not wanted anymore.
-People want to get rid of them not thinking any alternative.
-\quotes{They forget about it and don’t think about all the time and energy and money put into disposing of it} \citep{navarro2015followingtrash}.
-However to establish a solid understanding of trash and the action of trashing, we have to give attention to the trash.
-To move the beyond common perception we have to ask is it possible to do something other than refusing them?
-%\comment{Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash.
-People do not see beyond the primary function.}
+% Different scales
+The scale of trash production is not same for everybody or every country. \cite[2]{chen2015waste} writes that: 
+\begin{quote}
+The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
+The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
+OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
+Turkey is a member of this organization.} countries produce almost half of the world’s waste.
+Africa and South Asia produce the least waste.
+High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
+Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
+However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
+\end{quote}
 
-%
-%
-%\summary{Aspects and Approaches}
-In this thesis study to understand the different aspects of trash is a key element.
-Sometimes it is accepted as a problem (because of accepted as dirty, smelly) that needs to be carefully and seriously managed.
-On the other hand it is accepted as a source of diversity by the artists.
-For the recyclers it is a source of income.
-The economical aspect of trash can not ignored.
-There are people who collects plastics, scraps and papers from waste bins and landfills.
-By collecting and selling them they endure their life.
-
-As it can be seen clearly there are different aspects and approaches to the trash.
-For some people, it is disgusting thing and moved away from living space and for the others source (or treasure) of their life.
-It is noted that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep{zimring2012encyclopedia}.
-
-%\summary{Relative}
-As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \citep{erlick2015editorsletter}.
-She realized that any of them called the practice as recycling.
-For them using trash again and again is very natural and it is part of their life.
-On the contrary for the developed countries trash considered as a thing that must be avoided.
-There is no place for trash in their life.
-It can be understood from this anectode that approaches to the garbage are not same for all regions of the world.
-
-%
-%
-%\summary{Parts of us}
-\begin{singlespace}
+Similar to these as stated by \cite[16]{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.} Moreover from trash many unexpected results can be extracted.
+\cite[xxv]{zimring2012encyclopedia} argues that:
 \begin{quote}
@@
 The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
-\citep{zimring2012encyclopedia}
 \end{quote}
-\end{singlespace}
 
-% TODO Summarize
-% FROM Book: Trash Culture
-%\summary{Change in the production and consumption practices}
-\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
-Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}.
-As the result of it amount of goods boost and the cost of them significantly reduced.
-Things once reused again and again, now thrown away because it is more affordable to replace with new one.
-As the production increased its by-product material waste is also increased.
-\quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.
-%\todo{summarize}
+% Different types
+Electronic waste, construction and demolition waste, medical waste are some of the various types of waste.
+They are result of different production and consumption practices.
+For example nuclear power generation and applications of nuclear fission or nuclear technology produces not only engery but also radioactive waste which is very dangerous for living creatures.
 
-%
-%
-%\summary{Current} 
-During the last decades much attention has been devoted to the waste.
-In particularly environmental considerations dominates the perceptions of waste.
-\cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.
+% Different diciplines
+Trash attracts the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep[63]{emgin2012trashion}.
+For instance for archaeologist dumps near the residential area are one of the significant places to figure out what people consume in the ancient times \citep{rathje1992rubbish}.
+Moreover scholars argues that there is a relationship between technological and waste.
+Trash can be seen as a design and technological problem \citep{mcdonough2010cradle}.
+Further economical aspect of trash can not ignored.
+\cite[65]{emgin2012trashion} states that there is a huge business based on eco-friendly products and recyclable goods that is increasingly promoted.
 
-%
-%
-%\summary{Art}
+% Different people
+Various people including garbage collectors and artists interact with trash for different purposes.
+There are people who collects plastics, scraps and papers from waste bins and landfills.
+For the ragpickers, collecting others excess and discard is significant source of economical income.
+They collect and clasify recycle materials to sell them.
+By collecting and selling them they endure their life.
+On the other side for some of the people it is not considered as trash.
+As stated by the editor of the Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \citep{erlick2015editorsletter}.
+She realized that any of them called the practice as recycling.
+For them using trash again and again is very natural and it is part of their life.
+On the contrary for the developed countries trash considered as a thing that must be avoided.
+There is no place for trash in their life.
+It can be understood from this anectode that approaches to the garbage are not same for all regions of the world.
+It can be said that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep[xxvi]{zimring2012encyclopedia}.
+
 As noted by \cite{pye2010trashculture} \quotes{at least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art}.
-Using non art objects in the art opened new dimensions for the language of art and practice (act) of art.
-In the beginning of the 20th century non-art objects
-%\todo{non-art objecti aç} 
-enter the scope of art making. This is a revolutionary change in the practice of art making. Production of art and the approach to the art changed dramatically. 
-%This changes actually started at the end of the 19th century with impressionist. 
-Picasso is the first artist that used non-art object in his works.
-Later many of artists such as Kurt Schwitters and Joseph Cornell  followed him with their collages and assemblages.
-Later Duchamp challenged the nature (or language) of art by using, non-unique, fabricated object to express his ideas.
+In the beginning of the 20th century objects that are considered as art enter the scope of art making.
+Using non-art objects in the art opened new dimensions for the language of art and practice art making.
+This is a revolutionary change in the practice of art making.
+Production of art and the approach to the art changed dramatically.
+Picasso and Baraque are the first artists that used non-art object in their works.
+Later many of artists such as Kurt Schwitters and Joseph Cornell followed them with their collages and assemblages.
+Later Duchamp challenged the nature of art by using, non-unique, fabricated object to express his ideas.
 His work changed the way of perceiving art dramatically.
 With these developments trash has found a place in the art and contemporary artists become interested in trash.
-They use trash for different purposes (and these are explored in detail in the following chapters.).
+They use trash for different purposes and these are explored in detail in the following chapters.
 Trash find places in many mediums such as sculptures, paintings, assemblages and photographs.
 Artist express themselves through trash.
-Portraits build from trash.
+Portraits are build from trash.
 Consumption habits of society are criticized through trash.
+\cite[2]{pye2010trashculture} states that \quotes{trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature}.
 
-%
 %****************************************
 \section{Purpose of the Study}
+As it can be seen clearly that there are different aspects and approaches to the trash.
+In this thesis study to understand them is a key element because main driving force is to explore the alternative perceptions of trash.
+It is not static, not fixed, not totally isolated from people and social life.
+Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash.
+People often do not look beyond the primary function of objects.
+To establish a solid understanding of trash and transformation of it, we have to give more attention to the trash.
+In order to move away the common perception this study asks that is it possible to reuse discarded items rather than refusing them?
 
-% Bu tezde sorulan sorulardan birisi Çöpe daha farklı nasıl yaklaşılabilir... sanatçılardan örnekler verilerek bu açıklanmıştır.
+The aim of this study is to explore the theories and methods focused on transformation of trash in the context of art and artistic act.
+Particularly this thesis is interested in the relationship between art and waste.
+It investigates that how waste represented as a subject and how waste is used as an art material to represent or draw attention to the other subjects.
+It asks and seeks answers of these questions: Why and how is trash used by the artist?
+Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items?
+Has using discarded material or trash have specific (or special) meaning (or message)?
 
-% Some of the artist also interested in others trash. Why people are interested in rubbish?
-
-% In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.
-
-The aim of this study is to explore the theories and methods of transformation of trash in the context of art and artistic act. 
-% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-\quotes{Particularly in the connection between trash and the arts, this thesis is interested in two issues.
-First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as artistic material} \citep{ibarra2015beautiful}.
-Why and how is trash used by the artist?
-Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items?
-Has using discarded material or trash have specific (or special) meaning and message?
-Questioned that how do artists reflect trash and what are their tactics?
-
-%\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature \citep{pye2010trashculture}.}
-
-% \paraphrase{This thesis seeks to answer the following questions: How did art and literature respond to this age of consumption?
-What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification (depersonalization), mechanical reproduction, and meaning?
-(FROM Collage Culture)}
-
-%Do people want to take back (or revisit) the trash once thrown away
-In my project, the purpose is to transform trash and make it worth to reconsider.
-
-%
-%
-%\summary{Different types of trash, narrowing down scope} 
-There are different types of trashes result of different production and consumption practices.
-For example radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology.
-Electronic waste (e-waste), construction and demolition waste, medical waste are some of them.
-As it can be seen that there are lots of different types and as various as activities of human.
-In this scope of thesis focused on disposable items and specifically paper trash.
-
-%
-%
-%\summary{Different disciplines of trash, narrowing down scope}
-Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}.
-
-Technological perspectives are one them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
-% Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed?
-Developed in what sense?
-What are the criterion (foundation, measure) of technology?
-Technology is interested in which problems?)
-
-% Management of it (handled by the municipals generally). Removal from the life spaces of human.
-
-% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-In addition to these
-\begin{singlespace}
-\begin{quote} 
-the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed.
-When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}.
-\end{quote}
-\end{singlespace}
-
-% TODO Relocate and contextualize
-% Solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.
-
-Many people are inside the business of transforming trash through recycling and reusing.
-People on the streets looking for aluminum cans, glass bottles, plastic.
+Thesis project focuses on disposable items and specifically paper trash.
+Its purpose is to transform trash and make it worth to reconsider.
+At this point I need to state that the process of transformation is not to be confused with the kind of industrial recycling that is applying automated procedures to the products such as paper cups, glass bottles, plastics caps and aluminum cans with the purpose of returning them to the industrial production as raw materials.
+Further many people are inside the business of transforming trash through recycling and reusing.
+People has been looking for aluminum cans, glass bottles and plastics on the streets.
 They collect and sell them to survive.
@@
 
-% TODO Relocate, summarize and contextualize
-%\summary{Waste and technology relationship} 
-%\paraphrase{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design \citep{mcdonough2010cradle}.} \todo{can be moved to zizek part.} In other words, the problem is our technology (or design, or both) which is not perfect and causes mountains of rubbish.
-It is questionable that at some point, technology will reach to a level when there is no trash generated.
-
-% TODO Relocate, summarize and contextualize
-%\comment{Technical problem, need to managed, recycling (capitalism), upcycling} 
-%\paraphrase{With respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework.
-The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society.
-Waste now became evil.
-If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts.
-Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world.
-Upcycling...
-On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit.
-Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste.
-In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home.
-In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
-
 % TODO relocation.
 % MOVE TO Conclusion of art chapter, discussion of transformation.
-%\comment{Design, alternative discipline} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless.
-People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}
+% FROM Trashion: The Return of the Disposed by Bahar Emgin
+%\ People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
 
@@
 
-%
 %****************************************
 \section{A Note on Terminology}
-Many scholars and authors have used different words (or terminology) to define trash.
+Many scholars and authors have used broad range of terms to refer the notion.
 Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them.
-Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes).
-It signifies that the topic is so broad and there is no consensus on terminology.
+Sometimes these words are used to signify same concept.
+Although there are slight differences between these words.
+This situation signifies that literature of trash is so wide and there is no consensus on terminology.
 Words are used interchangeably.
-The book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:
+The book Rubbish: the Archeology of Garbage gives clearer definition of some these words:
 
-%\comment{What were people throwing out when these words were coined?}
-
-% FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
-\begin{singlespace}
 \begin{quote}
-Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings.
-\textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on.
+Several words for the things we throw away ---\quotes{garbage}, \quotes{trash}, \quotes{refuse}, \quotes{rubbish}--- are used synonymously in causal speech but in fact have different meanings.
+\textit{Trash} refers specifically to discards that are at least theoretically \quotes{dry} ---newspapers, boxes, cans, and so on.
 \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal.
@@
 \end{quote}
-\end{singlespace}
 
-%From another book (Trash Culture):
-%\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand.
-Many of these terms --- such as ‘trash’, ‘garbage’ and ‘rubbish’ --- are frequently used interchangeably.
-This is not least because the variety of terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of this volume.
-Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.}
+Artist Alice Bradshaw has published a \quotes{Rubbish Newspaper} which contains these words and shows their place in litreature and artworks. It is based on her extensive researh on this subject.
 
-In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods of transforming trash to the another object. Both of them are used widely by scholars.
+In addition to these there is also a confusion of the terms: reuse and recycling which are the general methods of transforming trash to the another object or concept.
+Both of them are used widely by scholars.
 
-According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form.
+According to dictionary Merriam-Webster, the word reuse means \quotes{to use again especially in a different way or after reclaiming or reprocessing.} Reusing involves usage of the same product unchanged in form.
 Reusing lengthens the life of the item or material.
@@
 To reuse is to use something again instead of throwing it away.
+In this thesis, reuse is explored through the work of the artist.
 
-%Why throw something away when you can give it another life?
-Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose.
-In this thesis, it is explored through the work of the artist.
+On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} In recycling an item, it is processed into a totally new product.
+Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
+Crushed glass containers used to make new glass containers, and scrap metal used in foundries can ge given as examples.
 
-% Reusing is possible with re-seeing (and re-thinking). Using creativity and personal approach can change objects functions. It is possible to use objects for different purposes.
-
-% TODO Summarize
-According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product.
-For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt.
-Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Examples are crushed glass containers used to make new glass containers, and scrap metal used in foundries.
-
-Recycling is very similar the rotting (decaying), and reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
+Recycling is very similar the rotting, and reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.
 
@@
 
-Some of the scholar uses recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
+\cite[72]{strasser1999waste} explains recycling by referring to the Oxford English Dictionary as:
+\begin{quote}
+...
+recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste.
+Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.
+\end{quote}
+
+Some of the scholars use recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of waste.
 Many scholar used the word recycling when mentioning works use trash and the concept of it.
@@
 Creative reuse, inventing new things from discard.
-Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
+Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
+It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
 This theory counters the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.

### 2016-01-17 main.tex
errors
Former-commit-id: 15772ce8859d48cb14d18f35bbe189c5237d715a
reorganization
Former-commit-id: e5cf9d1ed889ae9676d7eb070201bb31780d7a02
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352
Proof reading
Former-commit-id: d835c4ff57c702c8f90dae1816f3609db8679019

@@
 \usepackage{apacite}
-\usepackage[a4paper,left=40.1mm,top=24.1mm,right=25.1mm,bottom=36mm]{geometry}
+\usepackage[a4paper,left=41.2mm,top=25.2mm,right=24.2mm,bottom=35mm]{geometry} % left: 40mm, top: 25mm, right: 25mm, bottom: 25mm
 \usepackage{epigraph}
@@
 \usepackage{float}
-\usepackage{caption}
-\usepackage{subcaption}
+\usepackage[font={footnotesize,bf}]{caption}
+\usepackage[font={footnotesize,bf}]{subcaption}
 \usepackage{wrapfig}
@@
 \usepackage[titletoc,title]{appendix}
-\usepackage[colorinlistoftodos]{todonotes}
 \usepackage{afterpage}
@@
 \usepackage{tocloft}
+\usepackage{url}
+\usepackage{indentfirst}
+
+% Turning off all figures, required for turnitin upload
+% Remove the next two lines if you want the figures at their place
+\usepackage[figuresonly,nolists,nomarkers]{endfloat}
+\renewcommand{\processdelayedfloats}{}
+
+% Same fonts for URL
+\AtBeginDocument{\urlstyle{APACsame}}
 
@@
 
-% Bibliography line spacing
-\usepackage{natbib}
-\setlength{\bibsep}{0.0pt}
-
-\usepackage{xpatch}
-
-\xpatchbibmacro{date+extrayear}{%
-  \printtext[parens]%
-}{%
-  \setunit*{\addperiod\space}%
-  \printtext%
-}{}{}
+%****************************************
+% SPACING
 
@@
 % Adding extra space between paragraphs
-\setlength{\parskip}{\baselineskip}
+\setlength{\parskip}{0.5\baselineskip}
+%........................................
 
-% Quote spacing
+%****************************************
+% BIBLIOGRAPHY
+
+% Bibliography line spacing
+\usepackage{natbib}
+\setlength{\bibsep}{0.0pt}
+
+% Removing parentheses around year in bibliography
+\AtBeginDocument{
+\renewcommand{\BBOP}{}
+\renewcommand{\BBCP}{}
+}
+
+% Adding ":" character before page number
+\bibpunct[: ]{(}{)}{:}{a}{,}{~}
+%........................................
+
+%****************************************
+% BLOCK QUOTES
+
+% Spaces before and after block quotes
+\usepackage{etoolbox}
+\AtBeginEnvironment{quote}{\vspace{-\baselineskip}}
+\AtEndEnvironment{quote}{\vspace{-\baselineskip}}
+
+% Spaces before and after block quotes, indentation
+\renewcommand{\quote}{\list{}{\rightmargin=4em\leftmargin=4em}\item\relax}
+
+% Spacing
 \expandafter\def\expandafter\quote\expandafter{\quote\singlespacing}
+%........................................
 
-% To align left todos
-\reversemarginpar
+%****************************************
+% CHAPTERS
 
@@
 \titleformat{\chapter}[display]
-        {\normalfont\fontsize{14pt}{12pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
+        {\normalfont\fontsize{14pt}{14pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
 \titleformat*{\section}{\bfseries\fontsize{12pt}{12pt}}
@@
 % Chapter title spacing
-\titlespacing{\chapter}{0pt}{9mm}{3\baselineskip}
+\titlespacing{\chapter}{0pt}{13mm}{3\baselineskip} % Centered, Top: 50mm, Next: 3 line after
+% Bibliography title spacing
+\titlespacing*{name=\chapter,numberless}{0pt}{16mm}{4\baselineskip} % Centered, Top: 50mm, Next: 4 line after
+
+% RENAMING CHAPTER TITLES
+\addto\captionsenglish{%
+  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
+  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
+  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
+  \renewcommand{\bibname}{\MakeUppercase{Select Bibliography}}%
+}
+%........................................
+
+%****************************************
+% EPIGRAPH
 
@@
 \setlength{\epigraphrule}{0pt}
+%........................................
 
@@
 
-% RENAMING CHAPTER TITLES
-\addto\captionsenglish{%
-  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
-  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
-  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
-  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
-}
-
 %****************************************
@@
 \begin{titlepage}
+\singlespacing
     \begin{center}
-
-        \singlespacing
 
@@
         January 2016
+
 	\end{center}
@@
 \thispagestyle{empty}
-\singlespacing
+%\singlespacing
+%\doublespacing
 \noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\
@@
 \begin{center}
-	\vspace*{7mm}
-	\MakeUppercase{Abstract}\\
+	\vspace*{13mm} % Top: 50mm
+	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{Abstract}}}\\
     \vspace{\baselineskip}
@@
 \end{center}
-\singlespacing
+%\singlespacing
 \par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century.
@@
 The purpose of this study is to discuss usage of trash in the context of art.
-The role of art is questioned in the transformation of discarded items.
-This thesis follows the discussions on the place of trash in culture and theories of trash.
-Then approaches and methodologies of artists who use discarded materials in their works are explored.
-It is questioned that why and how they use discarded materials and how their artworks can be understood regarding theoretical and cultural aspects.
+This thesis questions the role of art in the transformation of discarded items through the approaches and methods of artists who use discarded materials in their works.
+It examines why and how artists use discarded materials and how their artworks can be understood regarding theoretical and cultural aspects.
+This study is supported by theoretical and philosophical ideas about garbage.
 
@@
 In the scope of the project, discarded papers are collected with the help people and transformed to notebooks.
-Progress and collected items are recorded on a website.
-Notebooks are installed in non-conventional locations such as library desks and computer labs in order to invite people to use trash again.
+Progress and collected materials are recorded on a website.
+Notebooks are installed in non-conventional art spaces such as library desks and computer labs that are frequently visited common places in order to invite people to use trash again.
 
@@
 \begin{center}
-	\vspace*{9mm}
-	\MakeUppercase{Özet}\\
+	\vspace*{13.5mm} % Top: 50mm
+	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{Özet}}}\\
     \vspace{\baselineskip}
@@
 \end{center}
-\singlespacing
+%\singlespacing
 \par Sanat işlerinde sanat dışı nesnenin kullanımı 20.
@@
 Bu çalışmanın amacı sanatsal bağlamda atığın kullanımını tartışmaktır.
-Atık ürünlerin dönüştürülmesinde sanatın rolü işlerinde atık maddeleri kullanan sanatçıların yaklaşımları ve yöntemleri üzerinden sorgulanmıştır.
-Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır.
-Sanatçıların neden ve nasıl atık malzemeleri kullandıkları ve işlerinin kültürel ve kuramsal açılardan nasıl anlaşılabileceği sorgulanmıştır.
+Atık ürünlerin dönüştürülmesinde sanatın rolü, işlerinde atık maddeleri kullanan sanatçıların yaklaşımları ve yöntemleri üzerinden sorgulanmaktadır.
+Sanatçıların neden ve nasıl atık malzemeleri kullandıkları ve işlerinin kültürel ve kuramsal açılardan nasıl anlaşılabileceği araştırılmaktadır.
+Bu çalışma çöpe dair kuramsal ve felsefi fikirler ile desteklenmektedir.
 
@@
 Proje kapsamında atık kağıtlar insanların yardımıyla toplanıp not defterlerine dönüştürülmüştür.
-Süreç ve toplanan ürünler bir web sitesinde kayıt altına alınmıştır.
-İnsanların atığı tekrar kullanmaya davet etmek amacıyla defterler sık ziyaret edilen kütüphane, bilgisayar laboratuvarı gibi ortak kullanım alanlarına yerleştirilmiştir.
+Süreç ve toplanan malzemeler bir web sitesinde kayıt altına alınmıştır.
+İnsanları atığı tekrar kullanmaya davet etmek amacıyla, defterler geleneksel sanat mekanı olarak kabul edilmeyen kütüphane, bilgisayar laboratuvarı gibi sık ziyaret edilen ortak kullanım alanlarına yerleştirilmiştir.
 
-%\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
+% Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
 Ya da en azından proje kapsamında üretilen işin.
-Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}
+Ya da bu bağlamda ele alınabileceği iddia edilmektedir.
 
@@
 
-%\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
+% Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
 Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
 Bu defter hakim sistemin dışındaki mekanlarda konulmuştur.
-(kamusal ortak alan)}
+(kamusal ortak alan)
 
-%\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
+% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
 Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
@@
 Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır.
-Çöpün nasıl sanatta yer bulduğu incelenmiştir.}
+Çöpün nasıl sanatta yer bulduğu incelenmiştir.
 
-%Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
+% Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
 Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
@@
 
-%Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
+% Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
 Bu atık maddeler dönüştürülerek defter yapılmıştır.
@@
 \begin{center}
-	\vspace*{7mm}
-	\MakeUppercase{ACKNOWLEDGMENTS}\\
+	\vspace*{13mm}
+	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{ACKNOWLEDGMENTS}}}\\
     \vspace{3\baselineskip}
@@
 
-I would like to thank my bosses and colleagues from Mobilus; Özgür Deniz Önür, Yağız Yaşaroğlu, Ekin Dino, Ayşegül Yaşaroğlu, Süleyman Yıldız and Aytaç Kocaman for their support, trust and sharing their discard with me.
+I would like to thank my bosses and colleagues from Mobilus; Özgür Deniz Önür, Yağız Yaşaroğlu, Ekin Dino, Ayşegül Yaşaroğlu, Süleyman Yıldız and Aytaç Kocaman for their support, trust and collecting their discard for the thesis project.
 
@@
 Üstündağ, Ayşenur Durgut, Emrah Şamdan, Duygu Ç.
-Şamdan, Ali from METU Technopolis İş Bank Office, Aykut from Modshifters and Varuna Gezgin for collecting and sharing their discard with me.
+Şamdan, and Koray Benli for their valuable friendship, and also Ali from METU Technopolis İş Bank Office, Aykut from Modshifters, and Varuna Gezgin for collecting discarded materials for the thesis project.
 
-Lastly and mostly, I would like to thank my family for their love, trust and support from the very beginning of this work. 
+Lastly and mostly, I would like to thank my family for their love, trust and support from the very beginning of this study. 
 \clearpage
@@
 \renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % dots for chapters
-\renewcommand{\cfttoctitlefont}{\normalfont\MakeUppercase\hfil}
+\renewcommand{\cfttoctitlefont}{\MakeUppercase\hfil\bfseries\fontsize{14pt}{14pt}\selectfont}
 \renewcommand\cftchapfont{\mdseries}
@@
 
-\setlength{\cftbeforetoctitleskip}{19mm}
+\setlength{\cftbeforetoctitleskip}{20mm}
 \setlength{\cftaftertoctitleskip}{3\baselineskip}
@@
 
-\renewcommand{\cftloftitlefont}{\normalfont\MakeUppercase\hfil}
+\renewcommand{\cftloftitlefont}{\MakeUppercase\hfil\bfseries\fontsize{14pt}{14pt}\selectfont}
 \renewcommand{\cftfigaftersnum}{.}
 
-\setlength{\cftbeforeloftitleskip}{19mm}
+\setlength{\cftbeforeloftitleskip}{20mm}
 \setlength{\cftafterloftitleskip}{3\baselineskip}
@@
 % CHAPTERS
-\include{chapter1_reduced}
+\include{chapter1_final}
 \include{chapter2_reduced}
@@
 
-% TODO yıl olayını düzeltmeli
-% Bibliographyden sonra 4 boşluk olmalı?
-
 %****************************************
@@
 \phantomsection
-\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
+\addcontentsline{toc}{chapter}{SELECT BIBLIOGRAPHY}
 \bibliographystyle{apacite}
@@
 % APENDICES
-%\appendix
+\appendix
+\phantomsection
+\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
+\chapter*{APPENDICES}
+\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}
 
-%\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
-%\chapter*{APPENDICES}
-%\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}
+\addtocontents{toc}{\cftpagenumberson{chapter}}
 
-%\addtocontents{toc}{\cftpagenumberson{chapter}}
-
-%\makeatletter
-%\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
-%\makeatother
+\makeatletter
+\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
+\makeatother
 
 %\include{appendix_glossary}
-%\include{appendix_materials}
-%\include{appendix_project}
+\include{appendix_materials}
+\include{appendix_project}
 %........................................

### 2016-01-17 chapter1_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

@@
 
-% Epigraph
 \begin{singlespace}
@@
 
-% TODO Summarize
 % Change in the production and consumption practices
-\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
-Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}.
-As the result of it amount of goods boost and the cost of them significantly reduced.
+\cite[11]{banash2013collage} states that:
+\begin{quote}
+Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.
+\end{quote}
+As a result of it amount of goods boost and the cost of them significantly reduced.
 Things once reused again and again, now thrown away because it is more affordable to replace with new one.
@@
 It is stacked to another place.
-A project conducted by MIT in America explores the journey of trash by placing trackers onto the trash \citep{chen2009mit}.
+A project conducted by MIT\footnote{Massachusetts Institute of Technology} in America explores the journey of trash by placing trackers onto the trash \citep{chen2009mit}.
 According to their results trash spreads away across the country and this journey takes month.
 Further it is not limited with the border of America because they are exported to the other countries.
-In other words American's trash is not only their trash.
+In other words Americans trash is not only their trash.
 
@@
 It moves from homes to garbage trucks, from streets to landfills and also from landfills to sculptures inside museums.
-In other words, trash is not only found on the most disgusting and avoided places, but also can be found on the most steril and frequently visited places.
+In other words, trash is not only found on the most disgusting and avoided places, but also can be found on the most sterile and frequently visited places.
 
@@
 They are result of different production and consumption practices.
-For example nuclear power generation and applications of nuclear fission or nuclear technology produces not only engery but also radioactive waste which is very dangerous for living creatures.
+For example nuclear power generation and applications of nuclear fission or nuclear technology produces not only energy but also radioactive waste which is very dangerous for living creatures.
 
-% Different diciplines
+% Different disciplines
 Trash attracts the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep[63]{emgin2012trashion}.
@@
 There are people who collects plastics, scraps and papers from waste bins and landfills.
-For the ragpickers, collecting others excess and discard is significant source of economical income.
-They collect and clasify recycle materials to sell them.
+For the rag-pickers, collecting others excess and discard is significant source of economical income.
+They collect and classify recycle materials to sell them.
 By collecting and selling them they endure their life.
@@
 There is no place for trash in their life.
-It can be understood from this anectode that approaches to the garbage are not same for all regions of the world.
+It can be understood from this anecdote that approaches to the garbage are not same for all regions of the world.
 It can be said that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep[xxvi]{zimring2012encyclopedia}.
@@
 Production of art and the approach to the art changed dramatically.
-Picasso and Baraque are the first artists that used non-art object in their works.
+Picasso and Braque are the first artists that used non-art object in their works.
 Later many of artists such as Kurt Schwitters and Joseph Cornell followed them with their collages and assemblages.
@@
 
-%
 %****************************************
@@
 
-In the third chapter, Trash (in) Art, seeks the root of usin discarded materials in the artworks and analyses the sample artworks and artists.
+In the third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and analyses the sample artworks and artists.
 As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply.
@@
 
-The last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.
+The last chapter is reserved for an overall conclusion and evaluation of this thesis and further suggestions on the subject and the project.
 
@@
 
-Artist Alice Bradshaw has published a \quotes{Rubbish Newspaper} which contains these words and shows their place in litreature and artworks. It is based on her extensive researh on this subject.
+Artist Alice Bradshaw has published a 36 page \quotes{Rubbish Newspaper} which contains these words and illustrates their place in literature and artworks.
+It is based on her extensive research on this subject.
+
+In this thesis like many scholars I also use these words interchangeably. However mainly in this thesis scope I prefer trash which better signifies dry paper discard.
 
@@
 
-According to dictionary Merriam-Webster, the word reuse means \quotes{to use again especially in a different way or after reclaiming or reprocessing.} Reusing involves usage of the same product unchanged in form.
+According to dictionary Merriam-Webster, the word reuse means \quotes{to use again especially in a different way or after reclaiming or reprocessing.} Reusing includes usage of the same product unaltered in structure.
 Reusing lengthens the life of the item or material.
@@
 
-On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} In recycling an item, it is processed into a totally new product.
+On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} In recycling, an object is processed into a totally new product.
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
-Crushed glass containers used to make new glass containers, and scrap metal used in foundries can ge given as examples.
+Crushed glass containers used to make new glass containers, and scrap metal used in foundries can be given as examples.
 
@@
 Some of the scholars use recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of waste.
-Many scholar used the word recycling when mentioning works use trash and the concept of it.
+Many scholar used the word recycling when mentioning works use trash.
 However they are not mentioning the meaning that is decomposing things to the their particles.
-What they is actually is reusing and combining things, concepts, creating new mixtures.
+What they actually referring is reusing and combining things, concepts to create new mixtures.
 It is hard to say that they use it wrongly, but what they refer is actually upcycling.
 Creative reuse, inventing new things from discard.
-Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
-It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste.
-This theory counters the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
-Some of the scholars and artist uses upcycling for their process.
-This thesis project is about those objects that are recreated from trash through the process of upcycling.
+Upcycling is a term coined by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
+It is argued that art, in this scope, acts as a tool of transformation and reintroduces into certain orders what was once regarded waste.
+This approach resists the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
+Some of the scholars and artist uses upcycling for their works.
+Undertaking thesis project is about those objects that are reproduced from trash through the procedure of upcycling.

### 2016-01-17 chapter2_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2016-01-17 chapter2_reduced.tex
@@
 
-% Epigraph
 \begin{singlespace}
-% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych, http://priscilauppal.ca/books/alphabet-city/
 \epigraph{Anger is nothing compared to garbage:\\Garbage eats anger for breakfast.\\It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
@@
 
-%
-%
 In this chapter trash and the practice of transforming it is examined in theoretical and conceptual aspect.
-Referred to the ideas and work of philosophers and anthropologists to establish a better understanding of trash beyond common perception and dictionary meaning of it.
+Referred to the ideas of philosophers and anthropologists to establish a better understanding of trash beyond common perception and dictionary meaning of it.
 
@@
 Therefore, they need to be discussed in detail.
+Secondly, I looked through the Žižek’s comments on ecological perspectives that dominate the approaches on rubbish.
+Lastly, through \quotes{Rubbish Theory} transformation of trash and its various states as an object category is examined.
 
-Secondly, I looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.
-
-Lastly, through "Rubbish Theory" transformation of trash and its various status as an object category that is not static is examined.
-
-%
-%
+%****************************************
 \section{Throw Away Culture}
 
-% TODO ref Life Magazine, 1955, "Throwaway Living", p43
-%\summary{Throwaway Society} 
-%\cite[43]{life1955throwaway} 
-Life magazize published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955.
+Life Magazine (1955: 43) published an article titled \quotes{throw away Living} and proclaimed the arrival of the \quotes{throw away society}.
 It is described as behavioral consumption pattern of society based on throwing away objects after use.
-The article addresses the question of
-% https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
-\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?} \citep{tully2014throw} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
+The article addresses the question of \quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?} \citep{tully2014throw}.
+One can claim that disposable items provide easiness by bringing affordable alternatives of daily used gadgets.
+With these items people can spend their time and effort for other activities.
+In fact, the term \quotes{throw away society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
 
-According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
+According to findings of archaeologist Daniel Ingersoll the age of the throw away world began not in the twentieth century but during the nineteenth \citep[41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throw away society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
 According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
@@
 This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century.
-In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production
-%\todo{ref. Mamiya 1992, 2}.
+In its most basic form, consumer culture can be explained, as \quotes{the activities and ethics of a society are determined by patterns of consumption} \citep[2]{mamiya1992pop} rather than production.
 
-% TODO 
-% Disposable items are first introduced X and their usage accelerated after Y.
-There are Z factors that give rise to usage of single-use items excessively \todo{Bu cümleyi doğru düzgün kurmak gerekli.}.
-
-%
-%
-%\summary{Disposable Items}
+% Disposable Items
 Disposable items are made to be thrown away after used once or only a few times.
@@
 
-Many products that are delivered in these days are not designed to last for a long time. As a result, this encourages people to continue throwing goods away instead of repairing and reusing.
+Many products that are delivered in these days are not designed to last for a long time. As a result, this encourages people to continue throwing goods away instead of repairing and reusing them.
 
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-%\summary{Life of an Object} 
-One could claim that the end of the life of an object corresponds to the moment when it is refused.
-This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste.
-At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}.
+\cite[9]{hawkins2001plastic} argues that \quotes{Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throw away without concern.} It can be understood that both mass production and consumption support each other.
+Not only consumerism, but also mass production plays significant role in this phenomena.
+They need to be considered as a whole.
 
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-%\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
-\cite[9]{hawkins2001plastic} argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.”
-%\todo{ref. hawkins2001plastic p.9, emgin2012trashion p.64}
-
-% TODO Waste and Want disposibility p9
-
-%\summary{Capitalism, market, encouragement} 
-The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}.
-They were designed to decrease in value over time - to be used one, or twice and then to be thrown away.
-This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.
-
-%\summary{Initial function} 
+The remarkable thing about many of these objects ---especially those produced in the last of the twentieth century--- is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}.
+They were designed to decrease in value over time to be used one, or twice and then to be thrown away.
+This applies not only applies packing ---designed containers that protect and promote products--- but to an ever expanding list of products.
 \quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it.
@@
 
-%\summary{Being wasteful}
-As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \citep[viii]{hawkins2005ethics} because the cost of repairing objects sometimes is higher than the original one or very close to it.
+% Being wasteful
+As stated, \quotes{being wasteful in the ways [people] live is encouraged, expected and in many instances impossible to avoid} \citep[viii]{hawkins2005ethics} because the cost of repairing objects sometimes is higher than the original one or very close to it.
 On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.
+Moreover over time particularly electrical gadgets become incompatible with new formats and contents.
 
-%
-%
-%\summary{Factors that cause over-consumption habits}
-Technological advancements can be one of them.
+Technological advancements can be one of the factors that cause over-consumption habits.
 Disposable items with the help of industrialization can be produced easily.
-Mass production.
-Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs.
-wipes, glass vs.
-paper cup).
+Disposable items reduce the labor and human resources as compared to the traditional ways.
+For instance, consider napkin(tissue, towel) versus wipes, glass versus paper cup.
 Another point is that they are more affordable regarding supply chain and cost.
@@
 The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly.
-\quotes{The commodities of food and drink must be safe, sterile and private} \citep{kennedy2007ontology}.
+\quotes{The commodities of food and drink must be safe, sterile and private} \citep[70]{kennedy2007ontology}.
 
-% hygiene and cleanliness (Shove, 2003, Comfort, Cleanliness and Convenience)
-
-The germ theory proscribes companionship.
-The Latin root for this word, cum pani, literally means to share bread.
+\cite{kennedy2007ontology} notes that the germ theory prohibits companionship.
+The Latin root of this word, \textit{cum pani}, exactly means to share bread.
 However, insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self.
 Safety in a world of bacteria implies isolation.
-Packaging successfully isolates both food and consumer within a structure of sterile control.
+Packaging goods successfully isolates both food and consumer within a structure of sterile control.
 In essence, it encloses the commons.
-Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
-%\todo{ref. ontology of trash}
 
-% toilet paper comes here. Factors related with disposable items.
+\citep[176--177]{strasser1999waste} narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century:
 
@@
 Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
+
 Disposable paper cups met significant resistance.
 Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free.
-Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs.
+Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsible and folding designs.
 Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup.
@@
 And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
-\citep{strasser1999waste}
 \end{quote}
@@
 %\summary{Dark side} 
-Usage of disposable items in the society is very widespread.
-For same cases it is inevitable.
-Beyond the advantages of disposable items, there are side effects of consuming them excessively.
-They result in mountains of garbage.
+Nowadays usage of disposable items in the society is very widespread.
+As stated previously for same cases it is inevitable.
+Beyond the advantages of disposable items, there are dark sides of consuming them excessively.
+They result in mountains of garbage, spread through remotest corner of the world.
 
@@
 
-% TODO need relocation.
-% FROM Garbage in Modern Thought, Encyclopedia
-%\comment{THROW AWAY CULTURE.} 
-%\paraphrase{Philosophers and intellectuals have expressed the need to focus on the centrality of garbage, but for everyday individuals, the understanding of garbage is often as something “out of sight, out of mind.” "Modern humans, as part of their penchant for consumption and unsustainable living, often think very little about the waste that they produce." "Like many aspects of capitalist living, the person throwing away a piece of trash does not connect the various levels of production, consumption, and post-consumption involved in the trash.
-It becomes a secondary matter---an afterthought." "Martin O’Brien, among many thinkers, argues that the understanding of garbage should be a central concept, especially since garbage typically correlates with social change, social roles, and institutions.
-Thus, beyond the level of individuals and their relationship to garbage, there is an interest in understanding the central role that garbage plays in all of society’s roles, institutions, and forms of change." "Garbage is excess--- it is a part of society that society no longer desires." \cite{lukas2012garbage}}
-
-%
-%
-%\summary{Art}
-There are some artists whose works are related to the phenomena expressed above.
-(Some of the works of the artist can be examined in this phenomena.) Not every person throw away disposable objects, some of them save them and use for their purposes.
-They establish some methods to reflect the throwaway culture and its consumption and trash generated patterns.
+% Art
+Some of the works of the artist can be examined in the light of discussed phenomena.
+They establish some methods to reflect the throw away culture and its waste generated patterns.
+They offer new dimensions to see the subject.
 
@@
   \caption{Original view}
-  \label{fig:ChrisJordan_Numbers_CloseView}
+  \label{fig:ChrisJordan_Numbers_OriginalView}
 \end{subfigure}
@@
   \caption{Close view}
-  \label{fig:ChrisJordan_Numbers_OriginalView}
+  \label{fig:ChrisJordan_Numbers_CloseView}
 \end{subfigure}
-\caption{Chris Jordan, \textit{Caps Seurat}, 2011, 60x90" in one panel, and 88x132" in 3 panels}
+\caption{Chris Jordan, \textit{Caps Seurat}, 2011, Offset print, 60x90" in one panel, and 88x132" in 3 panels}
 \label{fig:ChrisJordan_Numbers_CapsSeurat}
@@
 Chris Jordan creates digital photographic series that turns numbers to visuals.
-He provides a different way to understand the statistics and the missed reality of consumerism.
+He provides a different way to understand the statistics and the reality behind the consumerism.
 He creates gigantic prints to express the numbers in a visual manner.
 He draws attention the global consumerism.
-The work reveals the reality that is hard to capture because of widespread of subject to the community and time.
+His work reveals the reality that is hard to capture because of widespread acceptance among the community.
 
-Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute.
-It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work.
+\textit{Caps Seurat} shown in figure \ref{fig:ChrisJordan_Numbers_CapsSeurat} displays 400,000 plastic bottle caps together, equal to the average number of plastic bottles consumed in the United States in every minute.
+It is one of the pieces of Portraits of Global Mass Culture by photographer Chris Jordan.
 In this series, he revisits the statistics of modern societies.
-In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.
-“There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says.
-“I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism.
+\cite{boustead2015impossible} explains that \quotes{Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.} Jordan says that \quotes{[t]here’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles} \citep[as cite in][]{boustead2015impossible}.
+He argues that \quotes{translating these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension} \citep[as cite in][]{boustead2015impossible}.
+Most of his works are created from photographs of everyday trash and mass consumption leftover.
+He points out the blind unawareness involved in consumerism.
 His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits.
 He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
-Here he draw attention to the our consumerism and express them numbers that are very big to understand.
-All the material that we have is trash to create this pictures.
+Here he draws attention to the our consumerism and express them in visuals and all the material that we have in these days is trash to create this pictures.
 
 %\summary{Analysis}
-In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism.
-The work accepted as a well-known example of pointilizm that is a technique of painting in which little, individual dots of color are applied in patterns to form an image.
+In fact, the work of Chris Jordan is a reproduction of \textit{A Sunday Afternoon on the Island of La Grande Jatte} which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism.
+The work accepted as a well-known example of pointilizm that is a technique of painting in which little and individual dots of color are applied in patterns to construct an image.
 This method shows similarities with mosaics of ancient times and pixels of modern times.
@@
 
-Seurat spent over two years painting A Sunday Afternoon, focusing meticulously on the landscape of the park.
+Seurat spent over two years painting \textit{A Sunday Afternoon}, focusing meticulously on the landscape of the park.
 However, in our age, it takes only one minute to create the bottle caps that form this painting.
@@
 
-Visuals of Chris Jordan are like modern versions of mosaics.
+Visuals of Chris Jordan are like post-modern versions of mosaics.
 In the age of mass production and consumption, the most readily available material is trash.
@@
 Trash has different colors, sizes, and shapes.
-Therefore, it is a perfect material to build sculptures from them.
+Therefore, it is a perfect material to build images from them.
 There is a great diversity of rubbish and offers new alternatives.
@@
 
-% John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge.
-He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.
-
-% Here, sculptures from trash can be added.
-
 % ARTWORK
 % TEA BAGS
-% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
 \begin{figure}[h!]
@@
 Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
-She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
-The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations.
+She decided to re-purpose mushy and muddy tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
+The project, entitled \textit{363 Days of Tea}, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations.
 The artist draws, paints, and forms collages on the salvaged tea bags.
@@
 Endeavour of re-purposing recycled and found materials.
-%\todo{cite website}
 
-%\summary{Analysis}
-This work is for fathers day.
+Work shown in figure \ref{fig:RubySilvious_TeaBag} is for fathers day.
 Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day).
@@
 % COFFEE CUP
-% FROM http://www.gwynethleech.com/
 \begin{figure}[h!]
@@
 
-She saves all of her coffee cups to use as "canvases" for making art.
-Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture.
+Gwyneth Leech saves all of her coffee cups to use them as canvases for her abstract illustrations.
+She transforms her coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of throw away caffeine culture.
+Buying a beverage from a coffee shop is a daily event for Leech and also for many other people.
+These coffee shops are located all around the world and busy corners of cities.
 She uses cups as a surface on which to draw and paint.
-Moreover, on the bottom of each one, She record the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment.
-Each cup is representing a daily caffeine break.
-The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
-It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill.
-However, as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.
-There are different versions of it.
-Paintings on paper coffee cups displayed in open window spaces.
-She publicly draws their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date.
+Moreover, on the bottom of each one, she records the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a moment.
+The installation shown in figure \ref{fig:GwynethLeech_CoffeeCups} makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
+It can be seen as a measure of time gone by, of money spent, of space to be taken up in a dump site.
+However, as \cite{leech2015cups} \quotes{upcycles each used cup into an artwork, it becomes the measure of other things as well: an artist’s regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.} There are different versions of installations.
+Here paintings on paper coffee cups are displayed in an open window space.
+She publicly draws their cups.
+Public drawing project were showed at many places and date.
 During public drawing projects, she draws with other people.
-Moreover, so.
-Buying a beverage is a daily event for Leech (and also many people.
-These coffee shops all around the world.
-As she drinks her coffee in the public, she also publicly transforms its cup.
-%\todo{cite her website}
-
-%\summary{Analysis}
-She is inside of glass window not white, isolated cube. Glass window provide her to be close to public space. As she drinks her coffee publicly, also paints them publicly. 
-%\todo{related with Liz Parson's argument: practice of trash to durable.} 
+She is inside of glass window not white, isolated cube.
+Glass window provide her to be close to public space.
+As she drinks her coffee publicly, and also paints them publicly.
 There is no difference between them, and also they should not be separated.
 By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something.
-Further she is not only transforming her trash, it is everybody's trash because of everyone uses it.
+Further she is not only transforming her trash, it is every body’s trash because of everyone uses it.
 
@@
 Their approach bring another dimension to criticize (or see) the disposable items.
-New things can be built from them.
-They can be used for new purposes.
+As it can be seen that new things can be built from them and they can be used for new purposes.
 
-Throwaway culture is a way of producing trash.
-It is a behavioral pattern, an approach to objects and commodities.
-Some artists develop different approaches to them.
+Throw away culture has a significant place in producing trash.
+It is a behavioral pattern, and an approach to objects and commodities.
+Some artists and people develop different approaches to them.
 In this type of culture or behavior throwing them is a natural act and promoted.
@@
 On the other hand, there are examples of saving everything instead of wasting.
-In the work of Song Dong, "Waste Not" thousands of domestic objects are exhibited.
+In the work of Song Dong, \textit{Waste Not} thousands of domestic objects are exhibited.
 They are owned by his mother and saved for later use.
-His mother lived a great depression in China, suffered from poorness.
-She developed the habit of saving things.
+They are extracted from her home.
+The compiled objects ranging from toothpaste to shoe, from bottles to toys.
+His mother lived a great depression in China, and suffered from poorness.
+As a result of it she developed the habit of saving things.
 After died of her husband this habit reached to extreme levels.
-She saves every tiny little thing.
-For her trash becomes an essential part of her life.
+She started to save every tiny object.
+For her, trash becomes an essential part of her life.
 In fact, it not is hard to say that preserved these things are not useless or worthless.
@@
 
-% the installation consists of the complete contents of her home, amassed over fifty years during which the Chinese concept of wu jin qi yong, or "waste not," was a prerequisite for survival.
-The assembled materials, ranging from pots and basins to blankets, oil flasks, and legless dolls, form a miniature cityscape that viewers can navigate around and through.
-
-%
-%
-Trash is much more than what people want to discard. Characteristic of people and societies can be understood from their produced trash.
-
-%\summary{TRASH and POTRAIT OF PEOPLE} 
-Trash is a reminder of consumption and production activities.
+Trash is much more than what people want to discard.
+Characteristic of people and societies can be understood from their produced trash.
+Trash can be seen as a reminder of consumption and production activities.
 In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action.
-Trash tells about societies' choices.
+Trash tells about societies’ choices.
 What is being left is one of the key things to realize what kind of people, society, action produce it.
-At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.)
-%\todo{ref.}
-.
+At one side trash is a produced thing and what people consume is tells many things about them such as their choices, possessions.
 As scholars mentioned that throughout the discards of someone else many things can be understood.
@@
 
-"Waste Not" is an exhibit by Chinese artist Song Dong that displays over 10,000 domestic objects formerly owned by his late mother, who refused to throw anything away if she could possibly reuse it.
+Figure \ref{fig:SongDong_WasteNot} displays over 10,000 objects owned by Chinese artist Song Dong’s mother.
+She refused to throw anything away if she could possibly reuse it.
+\textit{Waste Not} is an installation exhibited various museums of the world.
+This work can be seen as a work of collaboration of artist and his mother.
 
-Song’s mother, Zhao Xiangyuan (1938–2009), was typical of the generation of Chinese who lived through the hardships of the Cultural Revolution in the 1960s and 1970s abiding by the dictum "wu jin qi yong" (waste not).
-As a result, all commodities owned or collected stockpiled and preserved as protection against future hardship, even in the face of improving economic conditions.
+Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of 20th century by the saying \textit{wu jin qi yong} (waste not).
+As a result, all commodities owned or collected items are stockpiled and preserved as protection against for future poverty, even in the times of improving economic conditions.
 
-Waste Not is an installation exhibited different locations of the world. This work is a collaboration with the artist’s mother.
+Like many other Chinese at the time, Zhao developed the habits of frugality and thrift in order to make the best of what limited she had.
+Song recalls that when he was a child, \quotes{my mother always brought scraps of fabric to make clothes, because they did not need to be purchased with the government ---distributed clothing coupons.} She continued to collect them even in prosperity times because she feared that the shortages might some day return.
+The habit of waste not is seen as a \textit{fabao} ---literally a powerful weapon to protect against a return to hardships.
 
-Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had.
-Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.
-
-When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends.
-Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful.
-Song eventually came to understand that, as he puts it:
+When Song’s father died suddenly in 2002 his mother suffered an emotional collapse and her habit of holding on to matters was taken to extremes.
+Every possible space of her tiny house completely filled with thousands of domestic items.
+Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao resisted their efforts to dispose of things that she saw as potentially useful.
+In other words, she maintained her habit.
+Song eventually realized that, as he states it:
 
 \begin{quote}
-My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death.
+My mother’s need to fill space with daily-life objects resulted from a need to fill the emptiness after my father’s death.
 I recognised that in this era of transition, a person could live through several different lives in just one lifetime.
-In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
+In the wink of an eye, ones life could undergo great changes causing deep divisions between old and young.
 \end{quote}
 
-Everything that are exhibited here is different than presented on supermarkets.
+Everything that are exhibited in this work is different than presented on supermarkets.
 They are not new and not for sale.
 They represent a way of life.
-It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects
+It is common a notion that the exhibitions of famous people’s possessions but this work is separated from them as showing ordinary people’s objects.
 
 For most of people living in western modern societies it is unimaginable to live with all of these items together.
-However, for Chinese who are faced with same struggles share the emotion and  comment as "It's not [only] your home, it's my home."
+However, for Chinese who are faced with same struggles share the same emotion and comment as \quotes{It’s not [only] your home, it’s [our] home.}
 
-Jane Alison, senior curator at the Barbican, said that Waste Not helps us to understand the reality of Chinese history and culture in the 20th century in a way that newspapers can't.
+Jane Alison, senior curator at the Barbican, states that \textit{Waste Not} \quotes{helps us to understand the reality of Chinese history and culture in the 20th century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
 
-% TODO need relocation
-% FROM Culture, Values, and Garbage, Encyclopedia 
-%\comment{INTERACTION WITH GARBAGE. VALUE SYSTEM, DECIDING TO GARBAGE.}
-%\paraphrase{"The Trash Talk project emphasizes the complex, yet overlooked, relationships that garbage and people share.
-In terms of their relationship to garbage, all people interact with it on two levels.
-One is a material connection, indicative of the physical and sensory contacts that people have with garbage.
-In some households, this connection begins with an individual removing an item from packaging, disposing of that item in the kitchen receptacle, placing that item and others into a larger bin, taking that bin to the curbside, and then the material connection ends.
-Others, including workers in sanitation plants and recycling centers, then continue a material connection with the garbage, but the material connection of the consumer and the garbage ends with the bin on the curbside.
-The second connection that people maintain with garbage is an ideational one.
-Unlike the material one, which is manifested in things that can be touched, moved, and sensed, the ideational connection operates on the level of cognition.
-The differentiation of an item of value from an item of trash, for example, has nothing to do with the material principles of the object.
-Instead, humans determine whether the object is of value or whether it is considered trash.
-The decision of whether an individual decides to dispose of a broken radio or to consider it an heirloom to be kept is highly subjective and rooted in the value systems of a culture." "After the item is eaten, the individual has to decide what to do with the remainder, such as the leftover package.
-The package might be reused, re-purposed, or recycled but, most likely, will be disposed of in the trash." \cite{lukas2012culture}}
-
-% TODO need relocation.
-% FROM Garbage in Modern Thought, Encyclopedia
-%\comment{CATEGORIZATION.} \paraphrase{"Garbage is categorization, according to Susan Strasser." "In recycling programs and in places of refuse disposal, items of trash are categorized depending on their potential value, possible environmental harm, or time of decay.
-Consumers have become accustomed to the categories that are often applied to garbage.
-Many cities require people to dispose of their garbage in an orderly fashion---perhaps separating wet household waste from dry---and recycling programs ask individuals to divide their recyclable items into sets (such as plastic, glass, aluminum, and paper).
-Garbage is an illustration of how humans use mental categories to order the material world." \cite{lukas2012garbage}}
-
-% TODO need relocation.
-% Garbage is universal.
-%\comment{NO VALUE, UNIVERSAL} \paraphrase{"According to John Scanlon, garbage is indicative of a separation of the world---the desirable from the unwanted.
-Michael Thompson uses the riddle of the rich and poor person’s approach to snot (one keeps his in a handkerchief, the other disposes of it with a tissue) to underscore the curious ways in which garbage is connected to the issue of value.
-While garbage is universal---all societies, extinct and extant, have produced or produce garbage--- the conditions under which garbage is understood are culturally determined.
-Many non-Western societies attach a much greater value to items after they are discarded.
-In the United States and many other nations, garbage often results not because something no longer has utilitarian value but because the item in question is defined as something of no value.
-Thus, garbage is not only an objective condition of material culture, but also a subjective one of mentalist culture.
-People define what is trash and what is valuable." \cite{lukas2012garbage}}
-
-%
-%
-%\summary{Garbology}
-Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.
-
+As it can be understood trash reflects people's habits.
+It is like a mirror.
+It can not be separated from their producers and it is well studied area by scholars.
+Garbology is a study of waste as a social science.
+It applies methodologies of archeology to the human debris.
 Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away} \citep{lukas2012garbage}.
-
-% Garbology, from Encyclopedia, Abhijit Roy
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away} \citep[as cited in][301]{lukas2012garbage}.
 The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}.
+It enables researchers to document information on the nature and changing patterns of modern rubbish, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}.
 According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
@@
 It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.
-%roy2012garbology
-
 The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice.
 At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene \citep{pye2010trashculture}.
-
-%\todo{transition required.} 
-With the help of mentioned understanding of trash, what can we see the work of arts?
+With the help of mentioned understanding of trash, what can be understand from the works of art?
 
@@
 % From wiki
-Every detail of her private life is presented through her bed.
-The idea for The Bed was inspired by a depressive phase in the artist’s life when she had remained in bed for several days without eating or drinking anything but alcohol.
-The sensation of depression leading to disarray and detritus is not wholly unfamiliar to many people, and The Bed therefore enforces the communicative power that Tracey Emin seeks with her work.
-The artwork generated considerable media furor, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist's room, such as condoms, underwear with menstrual blood stains, other detritus, and functional, everyday objects, including a pair of slippers.
+Every detail of her private life is presented through her bed in an uncensored fashion.
+The idea of \textit{My Bed} was result of a depressive period in the artist’s life when she had remained in bed for several days without eating or drinking anything but alcohol.
+The sensation of depression leading to disarray and detritus is not completely unusual to many people, and \textit{My Bed} therefore enforces the communicative power that Tracey Emin seeks with her work.
+The artwork generated great media enthusiasm, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist’s room, such as condoms, underwear with menstrual blood stains, other junks, and functional, everyday objects, including a pair of slippers.
 The bed was presented in the state that Emin claimed it had been after languishing in it for several days; at the time she was suffering suicidal depression brought on by relationship difficulties.
@@
 
-% Independent http://www.independent.co.uk/arts-entertainment/art/reviews/tracey-emins-my-bed-at-tate-britain-review-in-the-flesh-its-frankness-is-still-arresting-10144882.html
-You can interpret it as an uncompromising self-portrait of a woman at a time of emotional trauma – or as a turbulent still life – but it is still a bed and all that a bed symbolizes and encompasses: sleep, sleeplessness, sex in all its manifestations, birth, death and dreams.
-
-Beds are not just for sleep.
-Especially for the ones that have small rooms and spaces bed becomes a life space.
+The work can be interpreted as a self-portrait of a woman at a time of emotional depression.
+However, it is still a bed and all that a bed symbolizes and covers: sleep, sleeplessness, sex, birth, death and dreams.
+Particularly for the ones that have small rooms and spaces bed becomes a life space.
 I have also experienced such a thing at boarding school and university dormitory for total my eight years.
@@
 
-%
-%
-\section{Zizek's Approach to Rubbish}
+%****************************************
+\section{Žižek’s Approach to Rubbish}
 Last decades there is an increasing attention the ecology and rubbish.
@@
 These types of news and talks increasingly find a place on media more and more.
-At this stage, Zizek comments on ecology and trash conversely.
+At this stage, Žižek comments on ecology and trash conversely.
 
@@
 
-In the documentary film Examined-life Zizek dressed as a sanitation man discusses ecology in the middle of a dump in London.
+In the documentary film Examined-life Žižek dressed as a sanitation man discusses ecology in the middle of a dump in London.
 His part starts with these sentence: \quotes{This [dump] is where we should start feeling at home}.
-The place where he talks is a site for depositing people's excess and unwanted material.
+The place where he talks is a site for depositing people’s excess and unwanted material.
 It is a place of out of sight.
 
-He draws attention that the thrown out garbage only disappears from people's living environment.
+He draws attention that the thrown out garbage only disappears from people’s living environment.
 Particularly discarding it is an action of escape from the unwanted.
@@
 
-According to Zizek, the way of approaching ecology is problematic in current societies because of accepting nature as a balanced, and harmonious.
-He claims that it is ideological in the sense that "wrong way of thinking and perceiving reality".
-The meaning of ideology is here mystification of real problems.
+According to Žižek, the way of approaching ecology is problematic in current societies because of accepting nature as a balanced, and harmonious.
+He claims that it is ideological in the sense that \quotes{wrong way of thinking and perceiving reality.} The meaning of ideology is here mystification of real problems.
 He claims that one of the key mechanism of ideology is temptation of meaning.
@@
 He opposed the notion of the existing world is in the best possible state and that humans disturb nature.
-According to him, nature is not an organism in balance that humans exploit, but rather a series of "unimaginable catastrophes" by asking the question what type of disasters would happened on the earth to compose oil that is a significant source of energy.
-Zizek asserts that ecology will slowly turn to a conservative ideology that is a kind of an unquestionable highest authority.
-Its voice is like "Do not mess with D.N.A.
-Do not mess with nature".
-In the light of these arguments instead of talking from an authoritarian high ground, he suggests that to find poetry and spirituality in the dimension of rubbish people create.
-He thinks that that is the true love of the world by asserting that "love is not idealization." Therefore, that is the reason why he thinks that a dump is a place that people should accept it as a home.
+According to him, nature is not an balanced organism that humans exploit, but rather a series of \quotes{unimaginable catastrophes} by asking the question what type of disasters would happened on the earth to compose oil that is a significant source of energy.
+Žižek asserts that ecology will slowly turn to a conservative ideology that is a kind of an unquestionable highest authority.
+Its voice is like \quotes{Do not mess with D.N.A.
+Do not mess with nature.} In the light of these arguments instead of talking from an authoritarian high ground, he suggests that to find poetry and spirituality in the dimension of rubbish people create.
+He thinks that that is the true love of the world by asserting that \quotes{love is not idealization.} Therefore, that is the reason why he thinks that a dump is a place that people should accept it as a home.
 
-In the light of Zizek's arguments ecology is not an appropriate point (or enough) to approach trash.
+% TODO buarada aşağısını toparlamak gerekli.
+In the light of Žižek’s arguments ecology is not an appropriate (or enough) point to approach trash.
 He points out the need for the new approach to trash.
@@
 
-%Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.
-
-The idealization of nature is problematic.
-Loving nature is loving trash.
+In the light of this arguments the idealization of nature is problematic.
+Loving nature is loving it with all dimensions.
 Live with trash.
@@
 Do not consider it as abject, disgust.
-Can live with our trash enrich (our perceptions, abilities)?
+Can live with our trash enrich our perceptions and abilities?
 How not to see them as trash and useless?
@@
 
-%
-%
+%****************************************
 \section{Rubbish Theory}
@@
 During their lifetime objects may circulate different markets and values systems such as economic, social and aesthetic.
-Especially these cycles have picked up speed with the advent of consumer culture.
+Especially these cycles have accelerated with the arrival of consumer culture.
 For instance, most recent technological gadgets become obsolete within two or three years.
@@
 Therefore, objects turn different items in their hand.
-Anthropologist Sidney Mintz (as cited in Susan Strasser) writes that "I have seen automobile bearings fashioned into portable vulcanizing kits; bits of toothbrush handles used as 'jewels' for rings, and ordinary tin cans turned into simple kerosene lamps." As it can be understood that objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
+Anthropologist Sidney Mintz \citep[as cited in][]{strasser1999waste} writes that \quotes{I have seen automobile bearings fashioned into portable vulcanizing kits; bits of toothbrush handles used as \singlequotes{jewels} for rings, and ordinary tin cans turned into simple kerosene lamps.} As it can be understood that objects function and value are transformed by relocation and revaluation of objects from one place to the other or one discipline to another.
 
-In ‘The Social Life of Things’ Appadurai (1986: 3) highlights that "commodities, like persons, have social lives." As such, Kopytoff wrote, the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different regimes of value that are both economically and culturally inscribed.
-Appadurai focuses on the "commodity potential" of things and asserts that "things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant" (1986: 13).
+It can be claimed that the end of an object’s life equates to the moment when it is refused.
+This action might take place in different forms and for various reasons.
+Nonetheless, in the most accurate and common sense, the life of an object ends in a dump in the state of waste.
+At this moment, the object is left valueless in all the possible meanings of the term value.
+It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}.
+However, Thompson’s Rubbish Theory shows us the opposite of it.
+Trash can is not an end it is starting point of another life.
+
+In \singlequotes{The Social Life of Things} \cite[3]{appadurai1988social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \cite{kopytoff1986cultural} notes that the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different systems of value that are both economically and culturally inscribed.
+Appadurai focuses on the \quotes{commodity potential} of things and asserts that \quotes{things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant} (1986: 13).
 However, one can ask that what are these commodity states and does anything exist between them?
@@
 
-Thompson observes the creation and destruction of value in man-made objects, cultural artifacts, and ideas.
-He notes how an object’s economic and cultural value diminishes over time rendering the objects worthless or redundant and how others value increases overtime.
+Thompson observes the creation and destruction of value in produced gadgets, cultural artifacts, and ideas.
+He notes that how an object’s economic and cultural value diminishes over time rendering the objects worthless or redundant and how others value increases overtime.
 In his notable Rubbish Theory, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value).
-The transient represents the common state of objects that are lessening in value and have limited life period.
+The transient category falls into the common state of objects that are lessening in value and have limited life period.
 A used car can be an example of transient state.
-On the contrary, the durable objects increase in value over time and have (ideally) infinite life spans.
+On the contrary, the durable objects’ value increase over time and have preferably unlimited life spans.
 Antiques and objects in museums can be an example of durable.
@@
 
-% TODO Bu nereden
 Rubbish is, by definition, an object that is not or is no longer, owned by anyone, which falls outside all categories of economics, culture, and social control.
 As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
-The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.
+The socially constructed value of the object has shifted over time from its limited life span of usefulness and meaning to a infinite and valuable socially accepted rubbish.
 
-The potential of the discarded thing also relies on its status as a thing approaching a zero point of value.
+The potential of the discarded material also relies on its status as an object approaching a zero point of value.
 In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty.
@@
 
-Similar to Žižek's claim that is "trash does not disappear", Thompson notes that "in reality ...
-[trash] just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered."
+Similar to Žižek’s claim, that is \quotes{trash does not disappear}, Thompson notes that \quotes{in reality ...
+[trash] just continues to exist in a timeless and valueless limbo, where, at some later date (if it has not by that time turned, or been made, into dust) it has the chance of being discovered.}
 
-Thompson argues that rubbish represents an important possible ‘in-between’ category in a ‘region of flexibility’ which is not subject to the same control mechanisms of the valuable and socially significant categories of transient and durable.
-Therefore it ‘is able to provide the path for the seemingly impossible transfer of an object from transience to durability’ (1979: 9) he further suggests that ‘a transient object gradually declining in value and in expected life span may slide across into rubbish’ (1979: 9) where it has the chance of being re-discovered, brought to light or cherished once gain.
-Figure X demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
+As argued by Thompson, rubbish represents a remarkable in-between ---middle--- category in a area of flexibility which is not exposed to the same control systems of the valuable and socially considerable categories of transient and durable.
+Hence, it \quotes{is able to provide the path for the seemingly impossible transfer of an object from transience to durability} (1979: 9) he also puts forward that \quotes{a transient object gradually declining in value and in expected life span may slide across into rubbish} (1979: 9) where it has the chance of being re-discovered, brought to light or admired once again.
+Figure \ref{fig:rubbish_theory} demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
+The transitions between these states are defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).
 
+% TODO
 \begin{figure}[h!]
@@
   \caption{Thompson’s Rubbish Theory}
-  \label{fig:rubish_theory}
+  \label{fig:rubbish_theory}
 \end{figure}
-
-The transitions between these states defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).
 
@@
 % http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
-"a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac." Additionally car was one of the most desired possessions of people in 20th century.
+\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in 20th century.
 Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum.
@@
 Movement in the other directions, from durable to either transient or rubbish, does not exist in this system.
-However, Duchamp's notable ready-made "Fountain" is one of the examples outside of the defined transitions.
+However, Duchamp’s notable ready-made \textit{Fountain} is one of the examples outside of the defined transitions.
 
-Fountain is a 1917 work produced by Marcel Duchamp, who is notable member of provocative Dada movement.
-The piece was an industrial porcelain urinal, which was signed "R.Mutt".
-Submitted for the exhibition of the Society of Independent Artists, in 1917, Fountain was rejected by the committee, even though the rules stated that all works would be accepted from artists who paid the fee.
+\textit{Fountain} (1917) is a artwork produced by Marcel Duchamp, who is notable member of provocative Dada movement.
+The piece was an industrial porcelain urinal, which was signed \quotes{R.Mutt}.
+It is submitted for the exhibition of the Society of Independent Artists in 1917.
+Committee rejected \textit{Fountain}, even though the rules declared that all works would be accepted from artists who paid the fee.
 It is considered one of the major artworks of the 20th century because of challenging the existing understanding of art.
@@
 For him, the idea is important rather than the object.
-He also criticized the position of artist by signing urinal as "R.Mutt" who is actually not exist.
+He also criticized the position of artist by signing urinal as \quotes{R.Mutt} who is actually not exist.
 In the editorial The Blind Man summarized this work as follows: \quotes{Whether Mr.
@@
 He CHOSE it.
-He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object} \citep{duchamp1917mutt}.
+He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view --- created a new thought for that object} \citep{duchamp1917mutt}.
 To debate all the aspects of this work is not possible with the scope of this thesis.
 However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist.
-Urine titled as "fountain" is still functional and have a place in the market.
+Urine titled as \textit{Fountain} is still functional and have a place in the market.
 In another word, it is not rubbish.
@@
 
-%\todo{bir conslusion lazım buraya.}
-
-% TODO move to conclusion.
-%Rubbish theory suggests that value emerges through people ways of seeing, and their category membership determines the way people act towards them.
-Similar to X (as indicating that scholars agree on this argument.)
-
-% TODO move to conclusion.
-% \paraphrase{Michael Thompson’s study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity, and social status.} \todo{ref.
-from Trash Culture} \paraphrase{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder \cite[97]{thompson1979rubbish}.}
-
-% TODO relocate
-% From "Trash Moves On Landfills, Urban Litter and Art" by Maite Zubiaurre
-%\summary{Moves} 
-%\paraphrase{Below part explains journey of trash in different steps/stages.
-Object moves and trash also moves.
-How is it life of trash?
-This part explains life of trash.
-How does it intersect with other people in which places?
-This part also can be understand by pointing out different part of it with detailed explanation.
-For example an artist collect from trash from streets and the other one goes to the (For example Vik Muniz) landfill.
-In other words there are different places to touch on trash.
-Every place generates different story?
-Or to understand it more deeply it covers different part of it.
-Or provides ideas about it.
-Lots of people touches it from philosophers to artist.
-Also in the later parts it draws attention to them.}
-
-% TODO relocate
-%\summary{Moves}
-%\paraphrase{Trash moves, all the time.
-It becomes a steadily growing heap of clutter behind closed walls, accumulates and festers under tight lids, travels from a small trash can in the kitchen to a large one on the curbside, joins other people’s rubbish when the garbage truck arrives, drives to the transfer station, where it circles around on conveyer belts, bids farewell to recyclable or composable goods, is loaded (if declared useless: the ultimate trash) into yet another garbage truck, or barge, or even train, until it arrives at its final destination: a sanitary landfill.
-Even in the landfill, it does not remain still.
-Monster "waste handling dozers" move rubbish around, compact it and press it against the soil.
-More importantly, they incessantly “sculpt” refuse with their huge shovels and caterpillar wheels, making sure the garbage mound does not tip over to create a fetid avalanche.
-When night falls, and the trash load of the day finally disappears under a thick layer of mud, detritus still moves: once underground, it settles differently, and decomposes at a different speed, thus continuously altering landfill topography: where there was an even plateau, now there is an abruptly descending slope, and a valley; and where there was a perfectly smooth road, now there are deep crevices in the pavement.
-This is how trash moves.
-But\ldots who moves on trash?
-In the United States, it is mostly big-wheeled machines, an industrious army of giant yellow insects busying themselves on a heap of rubbish.
-In Latin America, it is mostly people.
-People who hand-pick garbage, who build their shacks on densely compacted trash layers, and who, day in and day out, eagerly throw themselves into the boisterous cascades of fresh debris falling from garbage trucks.
-In many of the garbage dumps around the world, scavenging becomes a steady job.
-\quotes{Garbage properly \quotes{stored} and put away brings peace of mind, as do corpses boxed and buried, or criminals confined to a cell.} And thanks to Art: for Art shows how trash--even the one that stops moving, and particularly the one that lies squished, squashed, and weathered, almost fossilized, on the ground---has the potential to move: to move us, that is.
-(through the works of Filomena Cruz's photographic series “Road Kill”)}
-
-% TODO relocate
-%\summary{Categorization of waste} 
-%\paraphrase{Douglas argues that our classification of dirt lies not with what objects are but where those objects are.
-(Think that the transformation process.
-Previous argument support that the transformation of trash is possible by changing the place of them.
-In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’.
-For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.} \todo{Reference, (Waste by William Viney).}
-
-% TODO relocate
-%\paraphrase{“Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position.
-Just as faces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.}  \todo{Reference, (Waste by William Viney).}
-
-% TODO relocate
-%\paraphrase{Waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.}
-
-% TODO relocate
-%Trash is something that is out of sight, out of mind.
-Paid little attention to them and only catches attention when it is in wrong place.
-It is an unexpected object for people.
-Therefore transformation of it can create powerful and suprising effect onto the people.
-
-% TODO relocate
-%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
-(Further there is similar analogy at Waste and Want.
-The author give the example of shoe and claim that thrash is relative.
-The shoe on the dinner table is something disgusting but in the foots is not at like that.) Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
-Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
-(Summary From Liz Parsons.)}
-
-%
-% TODO move it to the art chapter and discuss it with the found photos.
+%****************************************
 %\subsection{Rubbish Theory in Practice: From Rubbish to Durable}
@@
 The transition from thing of little or no value (rubbish), to thing of value (durable) can result form a relatively minor shift in the way we see something.
+%........................................
 
@@
 
-%
-% TODO Move to Conclusion.
-%Trash has archaeological value. It reflects our habits. It is like a mirror. Can not be sepereted from their producers.
-
-%Ecological perceptions have problems. In modern socities trash seen as an ecological problem.
-
 %Moving nature of trash/objects.
-Objects value/state is not static open to intervantion, has potential to be reconsidered.
+Objects value/state is not static open to intervention, has potential to be reconsidered.
 Their place shift in the society.
@@
 Even if there is counter argument about it, the focus is disposable items and their amount is very high.
-After generating mountains of garbage the approach of zizek introduced.
+After generating mountains of garbage the approach of Žižek introduced.
 What to do this garbage see.
@@
 Learn to live with the trash.
-
-%Zizek points out wrong opinion about ecology among the society. Stacking trash outside of living space is not the solution.
 
@@
 
-%Thompson and Zubiaurre say trash moves amoung various range of value systems.
+%Thompson and Zubiaurre say trash moves among various range of value systems.
 
-%Zizek says you must find a way of loving your trash, or a way of living with trash instead of idealization of nature and waste. Purification is not suggested by him.
+%Žižek says you must find a way of loving your trash, or a way of living with trash instead of idealization of nature and waste. Purification is not suggested by him.

### 2016-01-17 chapter3_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2016-01-17 chapter3_reduced.tex
@@
 
-% Çöpün sanatta kullanılmasının temelleri arastirilmakta.
-
-% Ben bölümde aslında çöpün sanatta nasıl yer aldığına bakıyor olacağım. İlk kim kullanmış nasıl kullanmış. Sonrasında hangi anlamlarda kullanılmış.
-
 Firstly I look at how artist started using objects that are not produced by herself/himself and with the purpose of making art.
@@
 Further, they extended the ways of art making and the language of art.
-Therefore, it is important and necessarry to analyze them.
+Therefore, it is important and necessary to analyze them.
 In other words, I first look at the foundation of using non-art objects in the art making.
@@
 Several methods and genres are explored.
-Lastly focused on the inspiring documentary of Agnes Varda, The Gleaners and I which provides a general picture of the subject.
+Lastly focused on the inspiring documentary of Agnés Varda, The Gleaners and I which provides a general picture of the subject.
 
-%
-%
 \section{Root in the Art History}
@@
 
-% Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.
-
 From the beginning of 20th-century non-art objects draw the attention of the artist.
@@
 One of the remarkable change in the 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
-These objects are not normally considered as art often because they already have a non-art function.
+These objects are not commonly recognized as art often because they already have a non-art function.
 Their place in the society and people's mind commonly have a different meaning.
@@
 Thus, objects gained different meanings and usages with the hands of artists.
-(It is explained in the previous chapter that objects are not static and absolute.
-Objects can be used for new purposes even if they lost their meaning and value in the conventional system.)
+It is explained in the previous chapter that objects are not static and absolute.
+Objects can be used for new purposes even if they lost their meaning and value in the conventional system.
 
@@
 Of equal importance, their work highlighted and separated the role of technical skill from art-making.
-Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
+Braque and Picasso introduced a fake element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
 They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"
@@
 % http://www.artchive.com/artchive/S/schwitters.html
-After Picasso and Baraque, many artists applied collage and assamblage techniques to their works.
-Dada artist Kurt Schwitters is one of the productive artists amoung them.
-In 1918 created his own form of Dada in Hanover called 'Merz', using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions.
-The nonsense word 'Merz' is generated from the name of the name of a bank: the Kommerz und Privatbank.
-Merz was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt Merz Schwitters or simply Merz.
+After Picasso and Baraque, many artists applied collage and assemblage techniques to their works.
+Dada artist Kurt Schwitters is one of the productive artists among them.
+In 1918 created his own form of Dada in Hanover called \textit{Merz}, using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions.
+The nonsense word \textit{Merz} is generated from the name of the name of a bank: the Kommerz und Privatbank.
+\textit{Merz} was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt \textit{Merz} Schwitters or simply \textit{Merz}.
 
@@
 In particularly she curiously focuses on the (un)familiar people who glean leftover of society.
-Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her filmmaking practice.
+Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her film making practice.
 Some people glean crops; the others discarded food, and Varda gleans images.
@@
 This scene called "the dance of the lens cap".
-Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s \textit{Les Glaneurs et la Glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
 Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
@@
 One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-It can seen that from this example, gleaning becomes also a form of resistence to ruling system.
-a way of refusing to be boxed in by conventional expectations
-
-%\todo{waste and want rules of eating from garbage.}
+It can seen that from this example, gleaning becomes also a form of resistance to ruling system ---a way of rejecting to be limited in by conventional expectations.
 
@@
 Some of them build their own meaning, existence and identity through the collected items.
-One of the examples that she gaves is that the man who collects baby dolls and use them in the decoration of his home.
-Every where is filled up with the babydolls even if wall of the garden.
+One of the examples that she gave is that the man who collects baby dolls and use them in the decoration of his home.
+Every where is filled up with the baby dolls even if the wall of the garden.
 
 Through the film she experiences the act of gleaning with different people.
-At one side she gleans potatoes in the field and on the other side follows a man with biycle look for the garbages in front of the homes.
+At one side she gleans potatoes in the field and on the other side follows a man with bicycle look for the garbage in front of the homes.
 By documenting their life in action she also participates their life.
@@
 Moreover in the case of night searching, she finds a clock without hand.
-It has fullfiled its function and left away.
+It has fulfilled its function and left away.
 Most important part of clock is missing therefore it is not functioning.
@@
 Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
-Everyone somehow collect things in their life but particularlly she selects these people and their images in action.
+Everyone somehow collect things in their life but particularly she selects these people and their images in action.
 There should be a reason for this!
@@
 
-Varda's other subjects include artists who incorporate discarded materials into their work, symbols she discovers during her filming, and the French laws regarding gleaning versus abandoned property.
-Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist.
-He specializes in reliefs and assemblages made entirely from discarded objects and junk.
-In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.
+Varda's other subjects include artists who include discarded objects into their work.
+Louis Pons is one of them.
+He (born 1927) is a French collage artist.
+He specializes in reliefs and assemblages made wholly from refused materials and trash.
+Pons describes his artistic process and understanding of art as what others see \quotes{a cluster of junk,} he sees \quotes{a cluster of possibilities.} By showing these people and their ideas about junk Varda presents alternative ways to see objects and invites people to rethink.
 

### 2016-01-17 chapter4_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2016-01-08 chapter4_reduced.tex
@@
 \subsection{Collecting}
-Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that
+Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that:
 
@@
 This simply explains that our perceptions to the objects are relative and change in their usage context.
+
+% TODO relocate
+%Trash is something that is out of sight, out of mind.
+Paid little attention to them and only catches attention when it is in wrong place.
+It is an unexpected object for people.
+Therefore transformation of it can create powerful and surprising effect onto the people.
+
+%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92).
+Rubbish objects are things that are no longer used or loved or cared for and often no longer seen.
+Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.
+(Summary From Liz Parsons.)}
 
@@
 I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
-\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem};
+\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem}:
 
@@
 The poem will resemble you.
-And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
+And there you are ---an infinitely original author of charming sensibility, even though unappreciated by the vulgar herd.
 \end{quote}
@@
     \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
-        %\caption{}
     \label{fig:exhibition1}
@@
     \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
-        %\caption{}
     \label{fig:exhibition2}
@@
     \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
-        %\caption{}
     \label{fig:exhibition3}
@@
 \begin{figure}[!tbp]
-  \centering
   \begin{minipage}[b]{0.48\textwidth}
@@
   \caption{Sample placement at Torun}
-    \label{fig:ExperimentWithPaper}
+  \label{fig:SamplePlacementAtTorun}
 \end{figure}
@@
   \caption{Sample of QR code and notebook serial}
-  \label{fig:Banner_1}
+  \label{fig:QR}
 \end{figure}
@@
 
-Website can be accessible through this address http:\textbackslash\textbackslash kulu.be\textbackslash notebook-project.
+Website can be accessible through this address \url{http://kulu.be/notebook-project}.
 Domain name kulu.be belongs to me and project placed under a directory of it.

### 2016-01-17 chapter5_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

\chapter{CONCLUSION}

%
%
\begin{singlespace}
\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces. I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects. My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower. But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}
\end{singlespace}

This research began through a desire to understand more about the subject of rubbish in art practice. It attempts to figure out the transformation of trash through the artistic practices. It presents different uses of trash and approaches in the context of art. Example artworks suggest that it provides to artists wide range of possibilities. In other words it can be viewed as a source of diversity.

This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas, theories and people's experiences of things in throw away culture.

People's evaluations of what is trash and treasure are both content and context dependent and are not fixed values. The line between them are blurred in the explored practices and works of art. Indeed, temporal value judgements of 'rubbish' and 'art' are often at the core of such art works. The analysis of selected works methodologies and approaches show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

This thesis analyzes the basic principles and approaches in the act of transformation of trash. It provides examples of artworks that inquiry the issue of trash in various dimensions. César shows that trash is not only found in dumps but also can be found in museums. Dong shows that how trash is essential for some people to hold on the life.

Whatever the reason of discarding objects the alternative if it showed through the works of artist and the thesis project. In the project aimed to create new possibilities from trash. The usage of discarded paper bags, packages in the project provide audience new interpretations of the materials and meanings. On the other hand transforming discarded papers to notebooks evolved from a hobby to research grounded framed project.

The project developed in the scope of the thesis open to further developments. Content of the web site will expand in time. New notebooks from various discarded papers (in terms of location, meaning and purpose) will be compiled. Upcycling of trash will be extended to the other waste materials in addition to the paper. However research, practices, methods followed in this thesis form the basis of all these.

There are lots of points to approach to the trash. This shows that the richness of this topic. The scope of the research leaves many more areas untouched. There is much potential for further work in this subject. Certain major avenues have not been discussed in depth, not because they are irrelevant, but because there simply has not been time or space to explore them in sufficient detail and some reduction in scope has been necessary to be specific in such a wide field.

For instance, research can be extended to the notion of waste in the digital realm. Both digital notions like spam emails and  effects of digital devices on e-waste need further investigation.

The focus on waste material in art in this study has also largely disregarded waste of other non-material concepts such as time. Wasting time is another significant area of exploration.

As mentioned the value and meaning of objects changes from people to people, from society to society. Therefore more focused research can be conducted to analyze the local practices of transformation. This thesis work is formed in the English language but local languages have potentials to reveal the various concepts and practices of trash.

Different selection of works and their analysis and relation between them will form another thesis which identifies another dimension of trash.

### 2016-01-17 drafts/chapter1.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2015-11-22 chapter1.tex
@@
 
-Common perception to the trash is to get rid of it as soon as possible.
+\paraphrase{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption.
+(Trash Culture)}
+
+\comment{Common approach on trash is dominated by the environmentalist.}
+
+\comment{Last decades much attention has been devoted to the waste.}
+
+\comment{At least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art.} \todo{Bu nereden?}
+
+\paraphrase{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Global North completed a total transformation of everyday life, reorienting almost every activity toward consumption.
+Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.
+This world of mass production radically altered the meaning of objects in an unprecedented and profound reification that reached into every sphere of life.
+This was not just the fate of objects, but also of the practices with which they are always enmeshed.
+Mass production and commodification liquidated what rema ined of folkways tied to local production, demanding people construct the meaning of their lives through purchases rather than production.
+This transition to a lifeworld of consumption affected not only concrete objects, but even more forcefully altered symbolic and aesthetic practices.
+Technologies of mechanical reproduction redefine d story, image, and music, altering the traditions of both fine and fol k art with mass produced and distributed forms in newspapers, advertising, radio, film, and television that shattered the aura of fine art and liquidated folk art almost completely.
+Rather than making their stories, images, and music, ever more urbanized workers and manage rs consumed new massproduced art forms that, epitomized b y the Hollywood studio system, developed into the walltowall media scape of twentyfour hour broadband that now blankets the city, the suburb, and the country alike.
+(FROM Collage Culture)}
+
+\paraphrase{Given these developments, this book seeks to answer the following questions: How did art and literature respond to this age of consumption?
+What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification, mechanical reproduction, and meaning?
+(FROM Collage Culture)}
+
+[COMMON PERCEPTION] (In the dictionary trash means anything useless, worthless or discarded.
+In parallel to this definition) Common perception to the trash is to get rid of it as soon as possible.
 People want to depose trash from their lives most of time not thinking beyond.
@@
 How does it become trash?
+People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore.
+However is it really values?
+What does make it valueless?
 
@@
 
-In this thesis work to understand the different aspects of trash is a key element.
-\todo[inline]{These aspects are \ldots} As scholars agreed on \todo{ref.} it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
-Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
+It is part of our consumption activities (/practices) and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies.
+
+[DILEMMA] In this thesis work to understand the different aspects of trash is a key element.
+\todo{These aspects are \ldots} Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed.
 On the other hand it is accepted as a source of diversity.
@@
 
-%\comment{Dört bir yanımız metalarla çevrilmş durumda, istediğimiz şeylere çok kolay bir şekilde ulaşabiliyoruz.
-Yemek siparişi veriyoruz ayağımıza geliyor.
-İki blok ötedeki kahveciden istediğimiz zaman kahvemizi alıyoruz.
-Ama tüm bunların bir bedeli var.
-Bir yandan da sürekli olarak çöp üretiyoruz.
-Her ne kadar son derece sistemli bir şekilde çöpler toplanıyor ve belki de ne kadar tüketildiğini hiçbir zaman farkına var mıyoruz?}
-
 % Trash is everywhere and, produced every time
-Modern (developed) societies are continuously generating trash and, pile them on landfills.
+[LIFE OF OBJECTS] Modern (developed) societies are continuously generating trash and, pile them on landfills.
 During daily activities (drinking, eating, waiting in the bank?) trash is generated and people get rid of them as quickly as possible.
@@
 
-People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless?
-
-People do not think what happens after they throw it away.
-It exits from your life but not the world.
+[MIT, COMMON APPROACH] People do not think what happens after they throw it away.
+It exits from people's life but not the world.
 What happens when you throw it away?
 It is stacked from another place.
-Value of objects are not static.
-Trash is not static \todo{ref.
+\comment{Value of objects are not static.} Trash is not static \todo{ref.
 first paragraph.} also it has a long journey.
@@
 Trashes spread away across the country and this journey takes month.
-\todo[inline]{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
-In other worlds Americans trash is not only their trash.
+Further it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}.
+In other words American's trash is not only their trash.
 As commodities spread to the every corner of the world, trash also.
 What happens when it is traveled to the other countries, how they approaches these items.
-\comment{They find new uses and meanings on them.} \todo[inline]{consider Papua genen people}
+\comment{They find new uses and meanings on them.} \todo[inline]{consider African native}
 
 \begin{quote}
-\paraphrase{“Nobody wonders where, each day, they carry their load of refuse.
+\paraphrase{Nobody wonders where, each day, they carry their load of refuse.
 Outside the city, surely; but each year the city expands, and the street cleaners have to fall farther back.
-The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter” – Italo Calvino, Invisible Cities} The project is an initial investigation into understanding the 'removal-chain' in urban areas and it represents a type of change that is taking place in cities: a bottom-up approach to managing resources and promoting behavioral change through pervasive technologies.
-TrashTrack builds on previous work of the SENSEable City Lab in its exploration of how the increasing deployment of sensors and mobile technologies radically transforms how we understand and describe cities.
-“People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.”
+The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter (by Italo Calvino, Invisible Citie).
+People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.}
 \end{quote}
 
+\comment{MIT project can be seen as a different approach to understand the trash and its \quotes{removal-chain} from people's life.}
+
+\comment{Biodegradable matter is material capable of being decomposed by bacteria or other biological means.
+Biodegradable  matter usually consists of organic materials such as plant, animal, and other substance matter originating from living  organisms.
+It has the ability to be broken down into smaller, harmless products by way of the action of living organisms.
+The term is often used in relation to ecology, garbology, and waste management.
+Biodegradable products are often associated with perishables (products, food, and waste materials subject to death or decay).
+The term biodegradability of a product  refers to its disposition to disintegrate as the result of natural processes.}
+
 % Cycle of trash
-Trash moves, objects moves from place to place.
+[MOVES] Trash moves, objects moves from place to place.
 From homes to garbage trucks.
@@
 From garbage baskets to sculptures.
-\todo[inline]{REF.
-MIT Garbage project} Lots of different people touches to trash.
+Lots of different people touches to trash.
 With the trash what moves?
+Trash moves around.
+Travels like humans.
+Travels like commodities.
+When we are telling about the travel of commodities, then it is easy to say that trashes also moves around.
 
-% ARTWORK http://timgaudreau.com/2012/trash/trash.html
-[ARTWORK] \comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not.
-An artist takes photos of his every trash, like people take photos of their faces.
-He focuses on the thing that paid little attention, that is trash.
-At the end he exhibits all the photos by covering all the walls of room.
-It can seen as record of his activities, record of commodities.
-Most of them we are not aware of them.
-Draw the attention of is being thrown away and every time and everywhere.
-They are too much and can only fit covering all the walls.
-\todo[inline]{Tim Gaudreau “Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006”} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream.
-These collections of grids represent my first experiments with using those images.
-This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}
-
-% ARTWORK http://www.keaggy.com/chairs/sad/12/
-\todo[inline]{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}
-
-Why people are interested in rubbish.
+[IMPORTANT, QUESTINING] Why people are interested in rubbish.
 Some of the artist also interested in others trash.
@@
 çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.}
-
-% TODO Life time of objects.
-% Nesnelerin yaşam süreleri... Can you imagine how much plastic cup is being consumed every hour?
 
@@
 %****************************************
-% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
-% Michael Landy's Art Bin uses a art gallery to create his dust bin.
-Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed.
-Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints.
-"There's no hierarchy once they are in the bin" All of them are accepted as same.
-Ultimate equality.
-Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts.
-Nothing's too good for the art bin.
-Everything can fit into the art bin.
-Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art.
-As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”.
-It is a very big glass bin and isolates people.
-There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin".
-There is no limitation of throwing away even if art.
-
-% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
-%........................................
-
-\todo[inline]{ArtBin, squeezing. [Trashing Things, Artwork]}
-
-%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
-\todo[inline]{showing trash as they are... [Artwork] by Barry Rosenthal}
-
-%****************************************
 % Different types of trash
-\todo[inline]{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}
-
-The complexity of produced trashes of societies is increasing.
+[Different types of trash] The complexity of produced trashes of societies is increasing.
 For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies.
@@
 more easy to regain to the society.
+
+\comment{Biodegradable waste, Human waste, Organic waste, Food waste, Biomedical waste, Clinical waste, Medical waste, Household waste, Radioactive waste, Marine debris, Electronic waste (e-waste), Construction and demolition waste\ldots}
+
+\comment{Liquid type, Solid type, Hazardous type, Organic type, Recyclable type}
+
+\comment{Radioactive waste is waste that contains radioactive material.
+Radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology, such as research and medicine.
+Radioactive waste is hazardous to most forms of life and the environment, and is regulated by government agencies in order to protect human health and the environment.}
 %........................................
@@
 % Different disciplines, Perspectives related with trash from different disciplines
-\todo[inline]{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines.
-In other words there are different studies related with trash.
-Different approaches to the trash and son on.}
+\comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on.}
+
+trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature.
 
@@
 
-As many people are inside the business of transforming trash through craft and so on.
+[Different approaches] As many people are inside the business of transforming trash through craft and so on.
 People on the streets looking for aluminum cans, glass bottles, plastic.
@@
 
-\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash.
-By understanding them is provide a road map (or ideas) how to turn trash to something valuable?
-(The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods?
-Therefore first question is why they are less-valued, and ignored.
-How to make them valuable?
-How to make them part of our life again?)
+In the scope of trash not biodegradable trash is considered. Produced, industrial commodities are considered.
 
@@
 \section{Structure of the Study}
+\comment{Theory and artworks are not strictly separated from each other. Artworks are explained with the help of theories.}
+
+\comment{Research and the found samples of works helped a lot to shape my work.
+They provide me deeper understanding of the subject and what I am doing and they lead me during the development of the work.}
+
+\comment{the thesis is separated into three part.}
+
 This study is structured by many examples of artworks in different part of the thesis.
@@
 \section{A Note on Terminology}
+\comment{using words interchangeably.}
+
 Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash.
@@
 
+\paraphrase{A note on terminology: The chapters in this book feature a broad range of   terms, reflecting the multifaceted and conceptually complex nature of   the issue at hand.
+Many of   these terms – such as ‘trash’, ‘garbage’ and ‘rubbish’ – are frequently used interchangeably.
+This is not least because the variety of   terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of   this volume.
+Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.
+Again, these usages have been retained to reflect the focus of individual studies.
+(Trash Culture)}
+
 Some notes on methods:
@@
 % Reuse and Recycle
-One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars \todo{ref}
+One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used widely by scholars. \todo{ref}
 
@@
 For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.
+
+\comment{There is a difference between garbage and waste, although garbage is a part and an aspect of waste.}
 
@@
 It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard.
+
+Some of the scholar uses recycling \cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.
+Some of the scholars and artist uses upcycling for their process.
+\todo{move to the more appropriate place}
 
@@
 
-In this thesis scope mainly single use, disposable objects are considered generally.
-Nearly half of the material used in the project is disposable packets.
-Therefore as well as other words used but mainly trash is used to refer the material.
-
-Some of the scholar uses recycling\cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it. Some of the scholars and artist uses upcycling for their process.
-
 %****************************************

### 2016-01-17 drafts/chapter2.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2015-11-22 chapter2.tex
@@
 Further benefited from historical and social aspect of trash.
-It is questioned that how do scholars conceptualized the trash, what do they say about it?
+It is questioned that how do scholars conceptualized the trash.
+\comment{(what do they say about it?)} and how artist are approached these notions?
+and how their work viewed as their offered window or framework.
 
-Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots
+Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?
 
@@
 \section{Throw away culture}
+
+\todo{throwaway spirit (vance packard)}
+
+excessive use of short-lived/single-use or disposable objects.
+Disposable items are first introduced X and their usage accelerated after Y.
+There are Z factors.
+/ reduced cost and qualitative products.
+Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society.
+
+disposable: made to be used once or only a few times. made to be thrown away after one use or several uses.
+
+One of the possession that are spreaded to the community is disposable items. They are designed for single-use and personal items. Not reusing of these items are intended.
+
+Even if disposable items are reduces the labour and human resources in a short term they are create mountains of garbage.
+
+They are used very short-time.
+Their lifetime can be measured in minutes in terms of usage.
+I have never seen such person that uses own paper cup again and again.
+However their usage durations are very short, they continue to exist in the nature.
+
+Waste is considered as something useless, something no longer has value; something sufficiently degraded so that the cost of reclaimation seems higher than the cost of disposal, in other words, something unprofitable.
+
+We are very good at producing waste as well as hiding our garbage.
+
+Is it trash or trashed? Is it waste or wasted?
+
+different aspects of our life, eating, drinking, working, traveling, all of them are leave behind wastes and that are become invisible.
+
+we are sorrunded by all kinds of consumer goods [bevarages, ...] We are consing everywhere while walking, working and travelling.
+
+\paraphrase{The value of things rises and diminishes according to the work they do or the feature imagined for them, in other words, to their potential realized in time. Waste by Willian Viley.}
+
+\paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.
+Importantly the term throw away society has a slightly negative connotation, or meaning.
+When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval.
+}
+
+\begin{itemize}
+\item Which trash? Disposable
+\item When is it introduced first disposable and how?
+\item Terminology?
+\item Counter argument.
+\end{itemize}
+
+\paraphrase{‘being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid’ (Hawkins 2006: x) In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in dif  ferent ways and with dif  ferent ef  fects’ (Hawkins 2006: 5).}
+
 %%% Reference from Identity, mobility and the throwaway society
 The term is actually a criticism of over consumption of short-live disposable objects.
-\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
+\paraphrase{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf.
 O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere.
+\todo{ref.} \comment{Scholars argue that contemporary societies are throwaway societies.}
+
+\comment{The term overconsumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.}
+
+(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
+Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
+
 Even if conducted a qualitative research people are really do not throw away their things.
@@
 They analyzed the things like television, furniture and toys like that.
-
-\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}
-
-(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?
-Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)
 
@@
 
-\comment{zaten zengin olanın atma lüksü var.}
+[Social classification, throw away culture, place in society.] \paraphrase{The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.
+America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourth world countries.\cite{cerny1996recycled}} \todo{footnote, fourth world countries}
 
-\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
+[first occurrence of term.]\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955.
 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ...
@@
 
+Some of the works of artist can be examined in this pheomena.
+
 \todo[inline]{Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor.
@@
 
-\todo{need to elaborate}
+%*************************************
+% From ontology of trash
+% Taken to its obsessive extreme, the germ theory proscribes companionship.
+The Latin root for this word, cum pani , literally means to share bread.
+But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self.
+Safety in a world of bacteria implies isolation.
+Packaging successfully isolates both food and consumer within a structure of sterile control.
+In essence, it encloses the commons.
+Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
+
+% Susan Strasser
+% While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs.
+The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations.
+Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic.
+Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
+% Disposable paper cups met significant resistance.
+Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free.
+Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs.
+Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup.
+Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913.
+And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
+
+% The commodities of food and drink must be safe, sterile and private.
+
+% But there are lots of disposable items and single use items.
+Some of them can seen my project.
+Each of them have different use and created from different requirement of modern societies.
+This is not my intention to understand the reasons of disposable items just want to illustrate the notion and give and idea about it.
+
+% Hijyenik mi değil mi bilmiyorum, o benim derdim değil, Başka bir tez konusu, ona çözüm üretmek de derdim değil. Ama sonuçları ile ilgileniyorum.
+
+%....................................
 
@@
 These coffee shops all around the world.
-As she drinks her coffee in the public, she also publicly transform its cup.
+As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}
+
+inside of glass window. public space. publicly drawing, as she drinks her coffee publicly, also paints them publicly.
 
@@
 
-Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
+\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days.
 She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression.
@@
 Every day she creates a new piece that reflects her impressions in that moment.
-Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.
+endeavour of re-purposing recycled and found materials.} \todo{cite website}
+
+This work is for fathers day. catches the important moments of days and works as a diary.
 
@@
 
+turns numbers to visuals. provide different way to understand the statistics and the missed reality of consumerism. creates gigantic prints to express numbers in a visual manner.
+
+draws attention the the global consumerism. reveals the reality that is hard to understand. Because it is spread to the community and time.
+
 %****************************************
@@
 
+Trash tells about societies and also reveals personal aspects of peoples life.
+
+What people consume is actually tells many things about them.
+As scholars mentioned that throughout the discards of someone else many thing can be understand.
+They are end product of our activities and it can be traced through the discard and garbage.
+
 \comment{Things that are thrown away are one side of it.
@@
 Applying methodologies of archeology to the human debris.
-\todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+\paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
 He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
@@
 
+% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
+\comment{GARBOLOGY} Garbology is a study of waste as a social science.
+Applying methodologies of archeology to the human debris.
+\todo{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}
+
+% Garbology, from Encyclopedia, Abhijit Roy
+\paraphrase{"The field of garbology involves the study of refuse and waste.
+It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture.
+According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
+A.
+J.
+Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970.
+It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."} \todo{reference}
+
+% Rubbish: The Archeology of Garbage, p.24
+\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades.
+The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life.
+(example of Medical researches)} \todo{reference}
+
+\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has of  fered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice.
+At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of   the human being as a wasted or discarded element in discourses of socio-political hygiene.
+(Trash Culture)}
+
 \begin{figure}[h!]
@@
 We can understand from her junk what type of life her has.
-We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış.
-İşte o sürede birikenler.}
+We enter the world of artist through the her trashes.} \todo[inline]{Hastalık dönemi falan.}
 
@@
 \section{Zizek's Approach to Garbage}
+Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor.
+Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor.
+Onun dediği aslında yanlış sebep sonuç ilişkileri kurduğumuz üzerinden gidiyor.
+
+This section is related with the increasing interest on ecology. globa warming is one of them. These types of news and talks increasingly find a place more and more on media.
+
+trasnforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.
+
+as trash live longer than human being, next generations have to cope with previous generations trash.
+
 (There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence.
@@
 This part will be extended later.)
-
-% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
-  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
-  \label{fig:ChrisJordan_Albatross}
-\end{figure}
-
-The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.
-
-Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash.
-Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.
-
-Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures
-
-% Effect of plastic on wildlife in Antartica.
-% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor.
-Sadece başka bir yerlere gidiyor.
-Mesela kuşların midelerine.
-Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor.
-Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar.
-Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor.
-Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız.
-Karşı durduğum nokta ise tam olarak burası.
 
@@
 \section{Rubbish Theory}
+
+\comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük. Bu hareketlilik ve farklılık ise bir teorik çerçeveye oturulmuş, hadi ona baklım şimdi. }
+
+\paraphrase{Michael Thompson’s 1979 study Rubbish Theory  elaborated an understanding of rubbish as part of a f lexible and shifting system of value construction, underlying notions of innovation, creativity and social status.
+(Trash Culture)}
+
+\paraphrase{The potential of the discarded thing also relies on its status as a thing approaching a ‘zero point’ of value.
+In other words, it has reached a point in transition between the world of   the functioning, the useful and visible, and the realm of   the invisible, the non-functioning and empty.
+As Michael Thompson’s Rubbish Theory  suggests, at its nadir in a cycle of consumption and production, rubbish is both ready for disappearance and yet ripe for reinvestment, reinterpretation or revaluing.
+(Trash Culture)}
+
 Objects have a lifetime and they don't remain same through that lifetime.
@@
 
+% Amelie olabilir.
+Orada fotoğraf toplayan çocuk olabilir.
+Onları itinayla toplayan bir adam.
+Tren garındaki fotoğraf kulubesi.
+Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası.
+Bir birinden farklı bir sürü insan.
+Filmde neden böyle bir eyleme yer veriliyor?
+Film fotoğraflar üzerinden defter üzerinden ilerliyor.
+Onun çevresinden bir hikaye kurgulanıyor.
+İnsanların artıklarını topluyor.
+Onların değer vermedikleri şeyleri topluyor.
+Bunlar baya baya aslında o insanlar.
+Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor.
+Çok iyi bir örnek mi bilmiyorum.
+Burada niyet nedir ki?
+Ben buna şöyle bir okuma getireceğim diyebilirim.
+Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde.
+Bu arada bu fotoğraf toplama işi ilk değil.
+Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte.
+Ama benim işime yarayan kısmı ne?
+Neden o fotoğrafları ya da bunun filmini yapıyor.
+Aslında puzzlelar üretiyor.
+Belirli tekrar olacaktır.
+insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir.
+Tekrar bir kitap haline geliyor.
+Tanınmayan insanların fotoğrafları.
+Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon.
+Aslında tam da amelie bunu yapmıyor mu?
+Hikayeler üretiyor bu fotoğraflardan.
+Yeni karşılaşmalar üretmesi.
+Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır.
+Bin bir türlü şey vardır aralarında.
+Nereye yerleşmeli.
+Başkasının çöpünü toplama.
+O dönemin o eşyasını arşivini tutma.
+ve herkes sunuluyor sonrasında bu.
+
 \subsubsection{Found Objects in Art}

### 2016-01-17 drafts/chapter4.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

--- 2015-11-22 chapter4.tex
@@
 Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.
+
+\comment{Post-consumer  paper  waste  has  to  be  manually sorted  into  different  types,  such  as  paperboard, office  paper,  and  newsprint.
+Staples  are  removed with  a  magnet.
+The  paper  is  chopped  into  small pieces  and  added  to  water  and  chemicals.
+Denser objects that are not paper sink.
+Any inked or colored  papers  must  be  deinked  with  sodium  silicate or  sodium  hydroxide.
+Some  paper  pulp  is  also bleached.
+The effluent of the pulping process, called “sludge,”  includes  chemicals,  inks,  clay  (from glossy paper), plastics, and short paper fibers.
+This sludge can be toxic and is landfilled or incinerated.
+When paper is recycled, the fibers break down and become shorter, requiring the input of virgin material.
+If virgin pulp is not added, the pulp can be used in lower-quality paper products, such as cardboard or newsprint.}
+
+\comment{Traditionally,  newspapers and magazines have been reused as paper for packing;  covering  different  surfaces,  such  as  windows and furniture; and even as toilet paper. }
 

### 2016-01-17 chapter3_final.tex
turnitin fixes
Former-commit-id: 979c7f85b096336823eba6510e83756cbc45169e

@@
 
-In this chapter, I question the purpose and meaning of using trash as a medium in the artworks.
-The reasons and motivations of artists who use trash will be elaborated.
-The artists who use discarded items in their work will be analyzed in the light of arguments discussed in the previous chapter.
+This chapter questions the purpose and meaning of using trash as a medium in the artworks.
+Reasons and motivations of artists who use trash will be elaborated.
+Artists who use discarded items in their work will be analyzed in the light of arguments discussed in the previous chapter.
 Here, the main question is why artists select to use society's debris rather than fresh items.
 Hence, my research will focus on the place of trash in the world of art by looking at different methods and approaches.
-The scope of this research is Started from masterpieces and founding works, and continued with recent examples of artworks.
+The scope of this research is started from masterpieces and founding works, and continued with recent examples of artworks.
 
 Firstly I look at how artist started using objects that are not produced by herself/himself and with the purpose of making art.
-Early works are notable and founding ones that open new dimensions to reconsider objects and their meaning.
+Considered early works are notable and founding ones that open new dimensions to reconsider objects and their meaning.
 Further, they extended the ways of art making and the language of art.
@@
 I try to find out how they affected successor artist.
+Secondly this chapter looks some examples of contemporary works.
+Particularly, I try to capture the current approaches on trash.
+Several methods and genres are explored.
+Lastly focused on the inspiring documentary of Agnès Varda, The Gleaners and I, which provides a general picture of the subject.
 
-Secondly looked at some examples of contemporary works (or works from recent history).
-In particular, I try to capture the current approaches on trash.
-Several methods and genres are explored.
-Lastly focused on the inspiring documentary of Agnés Varda, The Gleaners and I which provides a general picture of the subject.
-
+%****************************************
 \section{Root in the Art History}
@@
 In other words, some artist started using objects in different scope beyond their intended purpose or intended meaning and function in their modern artworks.
-They develop their artworks by using paper and other stuff by pasting (or juxtaposing) them together.
+They develop their artworks by using paper and other stuff by pasting or juxtaposing them together.
 
-%Indeed, using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes.
-However, it is not discussed in the context of fine art and not accepted method for art making.
-
-From the beginning of 20th-century non-art objects draw the attention of the artist.
-Development of art in this century evolved through this non-art objects (or these objects play significant role development of art trough time).
+From the beginning of 20th-century non-art objects draw attention of artists.
+Usage of these objects play significant role in the development of art trough time.
 Usage of these objects dramatically changed the way how people look at art.
@@
 
-One of the remarkable change in the 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
+One of the remarkable change in 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
 These objects are not commonly recognized as art often because they already have a non-art function.
@@
 
-Modern artist questioned the way of traditional (conventional) way of art making in every dimension.
-Their approach out of the previous methods.
+Modern artist questioned the way of traditional way of art making in every dimension.
+Their approach is out of the previous methods.
 They are looking for the beyond of painting.
 With using different objects they break the pureness of artwork.
-It is not pure anymore, fragmented.
-Boundaries are pushed.
+It is not pure anymore, it is fragmented.
+They push the boundaries of art.
 Using non-art objects in the production of art challenges existing conventions of painting.
 
-Using non-art object can be considered as moving away from the purification of art.
-It is a composition of different fragments and pieces.
+Using non-art object can be considered as moving away from the purification of art which is also significant movement in modern art.
+Purification argues the separation of art and the others.
+Abstract and minimalist works can be given as an example to the purification.
+However, methods such as collage and assemblage are a composition of different fragments and pieces.
 Rather than the traditional way of painting on canvas modern artists composed their work with the combination of various objects from different context.
 With this approach works can be examined in multi-dimensional context.
+This also represents another branch in modern art.
 
-% (Peki neden sanatçılar bunu tercih ettiler, buhran neydi?
-Azıcık öncesindeki kıpırdanmaları anlatmak gerekli.
-Bu apayrı ve uzun bir konu.
-Ama değişmeler yavaş yavaş gelmeye başlamıştı.
-Neye karşıydı, ne getirdi.
-Sanatın var olan kalıplarını yıkıp yerine ne koydu?
-ronesanstan beri gercekligin temsili uzerine kurulan sanat ve estetik anlayis coktan sorgulanmaya baslamistir izlenimcilerle birlikte.)
-
-In the 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
+In 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
 Previously paintings are based on linear perspective and realistic style.
@@
 In impressionist paintings, themes are composed of everyday scenes.
-With Cezanne, the linear perspective is questioned and later this questioning reached to its peak point with cubism.
+With Cezanne, the linear perspective is started to question and later this questioning reached to its peak point with cubism.
 Cubism is developed with the collaboration of Picasso and Braque.
@@
 
-One of the keys to understanding the importance of Cubism of Picasso and Braque, is to consider their actions and how unusual they were for the time.
+One of the keys to understand the importance of Cubism of Picasso and Braque, is to consider their actions and how unusual they were for the time.
 When Braque, and then Picasso placed industrially-produced objects into the realm of fine art they acted as artistic iconoclasts of their age.
@@
 
-% Sanat disi objenin kullanilmasi aslinda sanatin saflasmasininda disinda yer almaktadir.
-Saf oz bir sekilde kurulmasindan ziyade farkli seylerin parcalarin bir araya gelmesiyle birlikte kullanilmasi.
-Tabuların yıkılması.
-Sınırlarının aşılması.
-geleneksel anlamda tuvalin uzerine boya surmekten ziyade farkli teknikler denenmeye baslanmistir.
-20yuzyilda geleneksel sanat tum boyutlariyla yeniden ele alinmistir.
-Resmin konusu, sergileme bicimleri, yenikikler gostermistir.
+Collage originates from the French \textit{coller} is a technique of applying manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting.
+In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to construct compositions.
+Pasting paper is not a new technique but using this technique it in the art making is a revolutionary movement in the language of art \citep{waldman1992collage}.
+Collage was a major turning point in the evolution of Cubism\footnote{It needs to be noted that there is two types of Cubism; analytical and synthetic.
+Analytical one early phase of cubism and based on fragmentary appearance of multiple viewpoints and overlapping planes.
+On the other hand synthetic one is the successor phase of analytical one and formed with various textures and patterns.}, and therefore a major turning point in the whole evolution of modernist art in this century \citep{greenberg1984collage}.
 
-Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions.
-Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \citep{waldman1992collage}.
-Collage was a major turning point in the evolution of Cubism, and therefore a major turning point in the whole evolution of modernist art in this century \citep{greenberg1984collage}.
+Similar to the collage, assemblage is produced by the incorporation of three-dimensional objects.
+In 1961, the exhibition \quotes{The Art of Assemblage} was featured at the New York Museum of Modern Art.
+\cite{seitz1961art}, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.
 
-Similar to the collage, assamblage is produced by the incorporation of three-dimensional elements.
-In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art.
-William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.
-%\todo{ref.}
-
-%Who invented collage--Braque or Picasso--and when is still not settled. because of most of their early works are undated and unsigned. the question of priority is less important rather than
-
-One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting.
+One of the earliest and notable examples of collage is Picasso’s \textit{Still Life with Chair Caning} (Figure \ref{fig:Picasso_Chair}), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting.
 This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture.
@@
 For instance the oval canvas and the rope around it represent the table.
-Pasted chair caning signifies the chair within the table.
+Pasted chair caning signifies the chair near the table.
 On the table folded paper shadow represent newspaper.
 Further there is a cut out lemon painted onto the table.
-The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.
+The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, alluding to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage allowed new possibilities of playfulness.
 This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
-
-% Greenberg
-% The abiding effect is of a constant shuttling between surface and depth, in which the depicted flatness is "infected" by the undepicted.
-Rather than being deceived, the eye is puzzled; instead of seeing objects in space, it sees nothing more than--a picture.
-
-% \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}
 
@@
 Braque and Picasso introduced a fake element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
-They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"
+They inquiry as \quotes{Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?}
 
@@
 Dada artist Kurt Schwitters is one of the productive artists among them.
-In 1918 created his own form of Dada in Hanover called \textit{Merz}, using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions.
-The nonsense word \textit{Merz} is generated from the name of the name of a bank: the Kommerz und Privatbank.
-\textit{Merz} was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt \textit{Merz} Schwitters or simply \textit{Merz}.
+In 1918 he created his own form of Dada in Hanover called \textit{Merz}, using rubbish elements such as labels, bus tickets and bits of broken wood in his collages and constructions.
+The nonsense word \textit{Merz} is generated from the name of a bank: the Kommerz und Privatbank.
+\textit{Merz} was soon to become a kind of brand name for almost all his productions.
+\cite{webster2011kurt} puts significance of Schwitters in the development of art as follows:
 
 \begin{quote}
-The language of Merz now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
+The language of \textit{Merz} now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
 In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism...
@@
 Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.
-\citep{webster2011kurt}
 \end{quote}
 
-In 1937 after Merzbau had been included in the Degenerate Art Exhibition he fled from Germany to Norway.
-There he created a second Merzbau.
-In 1940 he found refuge in England where he started a third Merzbau at Ambleside in the Lake District.
-The first Merzbau was destroyed in the Second World War, the second by fire in 1951 and the third was left unfinished at his death in 1947.
-It is now preserved in the Hatton Gallery of the University of Newcastle upon Tyne.
+He is very insisted on what he did.
+He constructed his room sized construction \textit{Merzbau} several times in different locations.
+First one destroyed in the Second World War, the second by fire in 1951 and the only third one was preserved.
+They are never ending structures not static.
+Through his life he added bits and pieces to them.
+\cite{carroll2011ruin} explains art of Schwitters as follows:
 
-% Yaptığı işte ısrarcı ve üretken. Sürekli inşa ettiği yapılar merzbaular aslında bitmiş bir izlenimi vermiyor. sürekli büyüyor değişiyor. sabit ve bitmiş bir yapısı bulunmamakta.
-
-% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
 \begin{quote}
@@
 \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: ‘It grows more or less according to the principle of a metropolis.’ The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and ‘how’ has surpassed ‘what’ we see.
-The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
-\citep{carroll2011ruin}
+As he wrote: \singlequotes{It grows more or less according to the principle of a metropolis.} The \textit{Merzbau} was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+Material has transformed into information, and \singlequotes{how} has surpassed \singlequotes{what} we see.
+The grottos in the \textit{Merzbau} that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
 \end{quote}
 
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-Jacknis claims that \quotes{like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence.
-Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others} \citep[as cited in][]{cerny1996recycled}
+Jacknis \citep[as cited in][]{cerny1996recycled} claims that \quotes{like collage in art or quotation in literature, the recycled object carries a kind of \singlequotes{memory} of its prior existence.
+Recycling always implies a stance toward time ---between the past and the present--- and often a perspective on cultures ---one's own and others.}
 
-Recycled object contains within it a reference to two or more distinct times.
-Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them".
-%\todo{ref}
+Reused objects contain within them a reference to many separate times.
+Whatever their final design or destination, these reused non-art artifacts are, by definition, impure, inauthentic products of past and present, here and there, us and them \citep{cerny1996recycled}.
 
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
-It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.
+It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their final function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.
 
-Collages and assemblages can be composed of all types of objects such as trash and found object. The notion of found object is researched by many scholars 
-%\todo{ref.}
-, but usage in the art has gained new dimensions with the Duchamp's concept of readymade.
+Collages and assemblages can be composed of all types of objects such as trash and found object.
+The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp's concept of ready-made.
 Industrially manufactured or anything found  anymore can found a place in the art.
-The most famous example is Fountain (1917) (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
-Before that first one is Bicycle Wheel.
-He mounted the bicycle wheel upside down onto a stool.
-% http://www.moma.org/learn/moma_learning/marcel-duchamp-bicycle-wheel-new-york-1951-third-version-after-lost-original-of-1913
-When Bicycle Wheel was first displayed, Duchamp encouraged viewers to spin the wheel.
-Although he claimed to select objects for his readymades without regard to beauty, he said, “To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.”
+The most famous example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+Before that first one is \textit{Bicycle Wheel} (Figure \ref{fig:Duchamp_BicycleWheel}).
+He wrote that the idea of a bicycle wheel upside down onto a stool.
+Although he claimed to select objects for his ready-made without regard to beauty, he said, \quotes{To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.} These samples were the beginning of
+shift from an art that is striving for beauty to a higher complex or hidden meaning beyond what was seen from common artifacts found in everyday living.
 
@@
   \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
-  \caption{Marcel Duchamp, \textit{Bicycle Wheel}, 1913 (authorised reproduction 1951, original lost)}
+  \caption{Marcel Duchamp, \textit{Bicycle Wheel}, 1913 (authorised reproduction 1951)}
   \label{fig:Duchamp_BicycleWheel}
@@
 
-% TODO Bunu sadece referans olarak kullanabilirsin, çünkü zaten çok fazla tekrar var.
-%\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters.
-Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano.
-Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H.
-A.
-Schuldt’s famous “Trash People,” which has traveled around the world since 1996 \cite{tauxe2012encyclopedia}.}
+% Found Object
+Found object originates from the French \textit{objet trouvé}, describing art created from existing, but often modified, artifacts or products that are not commonly regarded as art, often because they already have a non-art function.
+They are generally picked up somewhere and their value for the finder might be aesthetic, symbolic and remembrance.
+\cite[170]{gascoyne1936short} by analyzing found objects in Surrealist art, writes that artist \quotes{discovers a hidden symbolic significance in the [found] object which is preserved when the object is \singlequotes{framed} as art.} In other words, the finder discovers an unrealised significance by removing found object from its previous context and placing it in a new one.
+The meaning of material artifacts was derived from their symbolic relation to another entities such as person, time, place, experience rather than through their physical attributes \citep{camic2010trashed}.
+\cite{camic2010trashed} notes that people's motivation and usage of found objects also occur in various ways.
+Further enjoyment through found objects is different than appreciating art in museums which is isolated and refined activity.
+On the other hand discoveries through found object might happen anywhere at anytime.
+Hence it is not boundaried activity and spread through the daily life.
 
-% TODO rubbish theoryinin başına konulabilir, referans olarak kullanılabilir.
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\comment{Different meanings for everybody.} 
-%\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another.
-Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world.
-It is story of people --- the women, men, children etc.
-one person's trash into another's treasure.}
-
-% TODO MOVE TO COMMON APPROACH
-%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
-
-%
-%
-%\summary{Found Object} 
-Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.
-
-% TODO will not be used. just for rerefence
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors).
-From western trash to tribal treasure.
-\paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods.
-A disposable item becomes imminent desire and profound social consequence.
-(Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}
-
-% TODO will not be used. just for reference
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function.
-It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.
-
-% TODO will not be used. just for reference
-% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\todo{yerlinin fotoğrafı}
-%\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head.
-In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}
-
-%(Summary From Paul M Camic.) 
-%The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder.
-It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes.
-The junk object becomes transformed into the valued found object.
-Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965).
-His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p.
-97) and labeled it a work of art.
-A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996).
-These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.
-
-Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p.
-169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p.
-170).
-The finder discovers an unrealised significance in the object.
-A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object.
-He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context.
-\ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).
-%\todo{parap. ref.}
-
-%How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination.
-(Important points a gap in the literature.
-Although Parsons article analyze practices, it is not very broad and detailed.
-Further what is the importance of it is missing.)
-
-%The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident.
-The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.
-
-%Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater.
-The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements.
-When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object.
-Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder.
-This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.
-
-%An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time.
-Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.
-
-%Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.
-
-% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century.
-To help contextualize the application of found objects, the following section provides an overview of their use by Western artists.
-This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.
-
-%
-%
+%****************************************
 \section{Examples from Contemporary Artists}
-In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed.
-First one is related with found objects.
+In the light of discussions at previous section, some of the main strategies and approaches of artist are analyzed here.
 In this section focus will be shifted to the examples from contemporary artists.
-
-% Neden bu işler, neden bu sıra?
-
-% Neden çöpü kullanıyorlar.
-Bunu belirmek gerekli.
-İlki sanata farklı bir obje sokarak saflığını bozma, hazır yapım ile geleneksel yöntemlere karşı çıkış, fikrin ön plana çıkması.
-Visual uniqueness, aesthetics dimension, Economic reasons
+First one is related with found objects
 
 Photobooths are machines that place crowded places and with affordable cost people can get their photos.
-It is a pheonema that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.
+It is a phenomena that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.
 
@@
 Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away.
-The important part of the film, images of a man are generated who scanvage the photos of another people.
+The important part of the film, images of a man are generated who scavenge the photos of another people.
 There are a lot of artist who collects discarded items but their process is not well documented.
@@
   \includegraphics[height=6cm]{graphics/amelie_01.jpg}
-  \caption{Still image from Amélie}
+  \caption{Still image from Amélie by Jean-Pierre Jeunet}
   \label{fig:Amelie}
@@
 Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them.
-"Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ‘readymades’." His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin.
-Badger describes Found Photos as ‘both a conceptual artwork and a sociological footnote’.
+\quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin.
+Badger describes Found Photos as \quotes{both a conceptual artwork and a sociological footnote.}
 
@@
 
-% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa, http://www.eloisacartonera.com.ar/ENGversion.html
-%\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers.
-\quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets.
-Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
-
-%It reminds me that litreary is also a combination of reused thing. Because to create meanings we reuse words and idioms again and again with different combination.
-
-%\begin{figure}[ht]
-%  \centering
-%  \includegraphics[height=6cm]{graphics/EloisaCartonera_Books2.jpg}
-%  \caption{Books covered by Eloisa Cartonera}
-%  \label{fig:EloisaCartonera_Books}
-%\end{figure}
-
 The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air yet people find it hard to think of plastic bags as things of beauty.
-But as a product -- as something created and then unleashed to become seamlessly integrated into the lives of millions of people around the world -- there is a strange allure to them, just as a pathologist can admire the structure of a particularly virulent and contagious virus.
+However, as a product --as something created and then unleashed to become seamlessly integrated into the lives of millions of people around the world--- there is a strange allure to them, just as a pathologist can admire the structure of a particularly virulent and contagious virus.
 
@@
 
-% Örnek sadece bunlarla sınırlı değil, daha bir çoğu sayılabilir, plastik poşetinde şiirselliğin yakalandığı american beauty filmi, kamusal alanı dönüştüren sanatçılar gibi.
-
 %
@@
 \section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
-"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000.
-The film features various kinds of gleaning.
-According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers".
+\quotes{The Gleaners and I} is a French documentary film directed by Agnès Varda in 2000.
+The film emphasizes diverse types of gleaning from rural to urban.
+According to the Merriam-Webster dictionary gleaning refers \quotes{to gather grain or other produce left by reapers}.
 Varda searches for the historical and current practices of gleaning in rural and urban areas of France.
@@
 Varda discovers and shares with us the disturbing fact that they are taken back to the field where they came from, by following with the camera the trucks that unload mountains of potatoes.
-As Rosello notes that "The ‘good’ potato is not the edible potato but one that will fit into a plastic container to be displayed on the shelf of a supermarket." Varda records few people who glean the rejected potatoes from the field, and also she joins them by collecting heart shaped potatoes that fascinate her.
+As Rosello notes that \quotes{The \singlequotes{good} potato is not the edible potato but one that will fit into a plastic container to be displayed on the shelf of a supermarket.} Varda records few people who glean the rejected potatoes from the field, and also she joins them by collecting heart shaped potatoes that fascinate her.
 Rosello explains that she is collecting not only refused potatoes but also images that are left behind.
@@
 However, Varda forces us to watch it (wants us to pay attention).
-This scene called "the dance of the lens cap".
-Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s \textit{Les Glaneurs et la Glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+This scene called as \quotes{the dance of the lens cap.} Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s \textit{Les Glaneurs et la glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
 Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
@@
 
-%\todo{image}
-
-As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups).
+As Varda indicates, people can be found throughout the French countryside gleaning everything from apples to oysters, potatoes to grapes, much as they did hundreds of years ago (though no longer in organized groups).
 Making use out of something that has been left behind and labeled as obsolete is not unique to potatoes.
 There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely.
-More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have been closed.
-By showing them she shows that once was a common practice of gleaning throughout the years has evolved, but not disappeared.
+More metaphorically, there are also urban gleaners who scavenge scraps from bins, appliances from the side of the street, or vegetables from stalls after the markets have been closed.
+By showing them she explores that once was a common practice of gleaning throughout the years has evolved, but not disappeared.
 She keeps light to the modern life gleaners that are not visible every time.
-One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.
-It can seen that from this example, gleaning becomes also a form of resistance to ruling system ---a way of rejecting to be limited in by conventional expectations.
+One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants and refugees who are also considered as surplus of society.
+It can seen that from this example, gleaning becomes also a form of resistance to ruling system ---a way of rejecting to be limited by mainstream expectations and lifestyle.
 
@@
 
-She talks and investigates artists who are using discarded items in the artworks.
-Which people could not find anything, the artists see countless possibilities.
-There is always alternative ways to see something different: Giving life or finding life from discarded life.
-
-Here another point is that Agnes display images of people picking up things from the ground like their ancestors.
+Here another point is that Agnes records images of people picking up things from the ground like their ancestors.
 Everyone somehow collect things in their life but particularly she selects these people and their images in action.
@@
 
-She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
+She discusses the importance of found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}.
 One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.
 
-Varda's other subjects include artists who include discarded objects into their work.
-Louis Pons is one of them.
-He (born 1927) is a French collage artist.
+She investigates and talks artists who are using discarded items in their works.
+Which people could not find anything, the artists see countless possibilities.
+French collage artist Louis Pons is one of them.
 He specializes in reliefs and assemblages made wholly from refused materials and trash.
-Pons describes his artistic process and understanding of art as what others see \quotes{a cluster of junk,} he sees \quotes{a cluster of possibilities.} By showing these people and their ideas about junk Varda presents alternative ways to see objects and invites people to rethink.
+Pons describes his artistic process and understanding of art as what others see \quotes{a cluster of junk,} he sees \quotes{a cluster of possibilities.} Varda records his studio which contains many scraps, pieces of junk with various shapes and color.
+Combination of these provide countless representations.
+By showing these people and their ideas about junk, Varda presents alternative ways to see objects and invites people to rethink.
+There is always alternative ways to see something different.
+It is like giving life or finding life from discarded object.
+
+% TODO MOVE TO COMMON APPROACH, introduction.
+%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
 
@@
 % Documenting via a blog or a website. (what type of dimension it brings the work? maybe connect them, leave message.)
-% Buying a beverage is a daily event for \ldots
 % Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives. The reason of website.
@@
 
-% Sanatsal bir eylem olduğuna nasıl varacağım peki?
-Çünkü topluyorsun, belli bir yaklaşım geliştiriyorsun.
-Bu eyleme insanları davet ediyorsun.
-Sanatın eylem olma olayı...
-Buna burda değinip, kendi işime geçmeliyim.
-
 % TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
@@
 By juxtaposing different materials changing context and place.
-
-% TODO new comer
-% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\comment{People applies their own perception to interpreted the items.} Human manufactured never envisioned possibilities seen by people.
-It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."

### 2016-01-17 chapter3_final.tex
turnitin fixes
Former-commit-id: 1180ad94f12273274b95105edbcc44ca31b47297

@@
 They collaborated with each other on the development of cubism and collage.
+One of the keys to understand the significance of Cubism of Picasso and Braque, is to view their actions and how unusual they were for the time.
+When they placed mass produced artifacts into the realm of fine art they acted as artistic iconoclasts of their age.
 
-One of the keys to understand the importance of Cubism of Picasso and Braque, is to consider their actions and how unusual they were for the time.
-When Braque, and then Picasso placed industrially-produced objects into the realm of fine art they acted as artistic iconoclasts of their age.
-%\todo{ref}
-
-Collage originates from the French \textit{coller} is a technique of applying manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to construct compositions.
+Collage originates from the French \textit{coller} is a technique of pasting together manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting.
+In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, oil-cloth, and newspapers with oil paint on canvas to construct compositions.
 Pasting paper is not a new technique but using this technique it in the art making is a revolutionary movement in the language of art \citep{waldman1992collage}.
-Collage was a major turning point in the evolution of Cubism\footnote{It needs to be noted that there is two types of Cubism; analytical and synthetic.
+\quotes{Collage was a major turning point in the evolution of Cubism\footnote{It needs to be noted that there is two types of Cubism; analytical and synthetic.
 Analytical one early phase of cubism and based on fragmentary appearance of multiple viewpoints and overlapping planes.
-On the other hand synthetic one is the successor phase of analytical one and formed with various textures and patterns.}, and therefore a major turning point in the whole evolution of modernist art in this century \citep{greenberg1984collage}.
+On the other hand synthetic one is the successor phase of analytical one and formed with various textures and patterns.}, and therefore a major turning point in the whole evolution of modernist art in this century} \citep{greenberg1984collage}.
 
 Similar to the collage, assemblage is produced by the incorporation of three-dimensional objects.
-In 1961, the exhibition \quotes{The Art of Assemblage} was featured at the New York Museum of Modern Art.
-\cite{seitz1961art}, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.
+\cite{seitz1961art}, the curator of the exhibition \quotes{The Art of Assemblage} featured at the New York Museum of Modern Art in 1961, described assemblages as being made up of preformed natural or fabricated materials, objects, or fragments not designed as art materials.
 
@@
 Further there is a cut out lemon painted onto the table.
-The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, alluding to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage allowed new possibilities of playfulness.
-This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.
+The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, referring to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage provided new possibilities of playfulness.
+This was a new way of making art; instead of painting an object or landscape, you could paste whatever it was right onto the canvas.
 
@@
 
-% http://www.nybooks.com/articles/2010/12/09/artist-everything/
-% http://www.artchive.com/artchive/S/schwitters.html
 After Picasso and Baraque, many artists applied collage and assemblage techniques to their works.
 Dada artist Kurt Schwitters is one of the productive artists among them.
-In 1918 he created his own form of Dada in Hanover called \textit{Merz}, using rubbish elements such as labels, bus tickets and bits of broken wood in his collages and constructions.
+In 1918 he created his own form of Dada in Germany named \textit{Merz}, using rubbish elements such as newspapers, bus tickets and pieces of broken wood in his collages and constructions.
 The nonsense word \textit{Merz} is generated from the name of a bank: the Kommerz und Privatbank.
@@
 
-It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their final function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.
+It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their final function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and places.
 
@@
 Industrially manufactured or anything found  anymore can found a place in the art.
-The most famous example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+The most notable example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
 Before that first one is \textit{Bicycle Wheel} (Figure \ref{fig:Duchamp_BicycleWheel}).
@@
 
-Photobooths are machines that place crowded places and with affordable cost people can get their photos.
+Photo booths are machines that place crowded places and with affordable cost people can get their photos.
 It is a phenomena that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.
@@
 There are a lot of artist who collects discarded items but their process is not well documented.
-Therefore we are not aware of the artistic process.
+Therefore we are not fully aware of their artistic process.
 
@@
 Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977.
-It is a collection of photobooth images that had been thrown away or torn up by the people in the photos.
+It is a collection of photo booth images that had been thrown away or torn up by the people in the photos.
 \cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine.
@@
 On the other hand, some of them are very good condition, and it is a mystery that why they are rejected.
-Walker explains that the
+Walker explains that the:
 
@@
 Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them.
-\quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin.
+\quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the photo booths and looking for the nearest waste bin.
 Badger describes Found Photos as \quotes{both a conceptual artwork and a sociological footnote.}
@@
 He notes that it just started as a documentation of his discards, but later it became (part of his life and) an obsession that he can not able to easily quit off.
-He says that "this collection of images intimately displays what I do, what I consume.
-It reveals me." Like in the case of Tracey Emin trash turns to a medium that is used to express oneself.
-People are not only composed of the listed items in the CVs like in the film Fight Club Tyler Durden draws attention to the narrator by saying: "You are not your bank account".
-It is an effective way of looking things left behind rather that things put forward.
+He says that \quotes{this collection of images intimately displays what I do, what I consume.
+It reveals me.} Like in the case of Tracey Emin trash turns to a medium that is used to express oneself.
+People are not only composed of the listed items in the CVs, economical power like pointed out in the book (and also film) Fight Club Tyler Durden draws attention to the narrator by saying: \quotes{You are not your bank account.} It is an effective way of looking things left behind rather that things put forward.
 Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.
@@
 Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement.
-In her photographic series "Road Kill", she captures tiny "trash corpses" that are generally ignored and out of sight.
+In her photographic series \textit{Road Kill}, she captures tiny trash corpses that are generally ignored and out of sight.
 In other words, the skin of city revealed through her photos in micro scale.
-On the skin of city there are lots of trash including "a piece of chewing gum with an "engraved" leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful" as looked through the window of they capture the city life and skin of the city that we touched.
+On the skin of city there are lots of trash including \quotes{a piece of chewing gum with an engraved leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful} as looked through the window of they capture the city life and skin of the city that we touched.
 She shows us tiny details of huge cities.
-(Somehow these trashes for all effort succeeded to stay in the towns.) These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.
+Somehow these trashes for all effort succeeded to stay in the towns.
+These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.
 
@@
 In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump.
-He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millons of people.
+He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millions of people.
 Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump.
-He selects unusual materials and people for potraits rather than the powerful and notable people as commonly encountered at Renaissance.
+He selects unusual materials and people for portraits rather than the powerful and notable people as commonly encountered at Renaissance.
 To create portraits of \textit{catadores} there is any other material than trash because of they are already build up their life in trash of city.
-[Also these image are sold an auction and earned money donated to the \textit{catadores}.
+Also these images are sold an auction and earned money donated to the \textit{catadores}.
 The images of trash moved to beloved places such as homes and museums.
-As stated in the rubbish theory they transformed to a durable object.]
+As stated in the rubbish theory they transformed to a durable object.
 
-% TODO resim yanlış
 \begin{figure}[h!]
   \centering
-  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
+  \includegraphics[height=10cm]{graphics/vik_muniz_marat.jpg}
   \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
@@
 
-Not only monumental portraits extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez.
+Not only monumental portraits are extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez.
 Favio Chávez is a music teacher, and Nicolás Gómez is a garbage picker.
@@
 It is a one of the poorest villages where people live among the sea of garbage.
-"A violin is worth more than a house here," says Favio Chavez in documentary film.
+\quotes{A violin is worth more than a house here,} says Favio Chávez by pointing out their hard conditions.
 The orchestra's director and founder.
-Favio Chavez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez.
+Favio Chávez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez.
 Players of the orchestra are compiled from the children who are hopeless for their future.
-In the midst of such an existence, these musicians have created something both special and truly awe-inspiring.
+In the middle of such an existence, these people and musicians have created something both special and truly awe-inspiring.
 They are given birth to an orchestra that plays the masterpieces of classical music composed by Mozart, Beethoven, and Vivaldi.
-Trash turned to treasure and totally ironic that a signifiers of high culture like classical music can be even played with imperfect instruments.
+Trash turned to treasure and totally ironic that a signifier of high culture like classical music can be even played with imperfect instruments.
 For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music.
 What they create is actually not expected from them, and their success is not limited with their location.
-They have given concerts around the world.
-
-%"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer.
-"Well, we shouldn't throw away people either." \quotes{The world send us garbage.
-We send back music}.
-
-% Resistance to all hard conditions
+They have given concerts around the world and their motto is: \quotes{The world send us garbage.
+We send back music.}
 
@@
 
-As noted that recycling as an economic strategy of survival in developing countries throughout the world.
+As noted that recycling is an economic strategy of survival in developing countries throughout the world \citep[25]{cerny1996recycled}.
 Creative production that is motivated, primarily, by adverse conditions of economic necessity.
 Economic survival and adaptation are influential factors for both the makers, who build an informal business on the making and selling of recycled goods and the local consumers, for whom the market for affordable, utilitarian goods is devised.
-(p25)
 
-They build their musical instruments from what is available around.
-This project can be seen as a bricolage practice.
-Dictionary meaning; something constructed using whatever was available at the time.
-\quotes{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available.
-It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old.
-\citep{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.
-
-\quotes{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}
+Nicolás Gómez builds musical instruments from what is available for him, in this case it is rubbish.
+His practice and works can be seen as an example of \textit{bricolage}.
+Dictionary meaning of it is something constructed by using whatever is available at hand.
+The French word \textit{bricoleur} is someone who works with own hands and construct \textit{bricolage}.
+The term coined by \cite[17]{levi1966savage} and he explains it as:
 
@@
 [He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project.
-His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
+His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with whatever is at hand, that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous construction or destruction.
 \end{quote}
 
-%\begin{quote}
-%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth.
-There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
-%\end{quote}
-
-%\begin{quote}
-%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon.
-In this sense the engineer is a myth.
-A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself.
-The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
-%\end{quote}
-
-% TODO Bunu bitirirken de bir şeyler demek gerekli.
-
-In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical potraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects.
-The people in the figure X is General Jefferson C.
+In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical portraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects.
+The people in the figure \ref{fig:Alsbrooks} is General Jefferson C.
 Davis who was an officer at United States Army in 19th-century.
 Selected persons can be viewed as a member of the higher or ruling class of society.
-Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good.
-Or vice versa.
+Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good or vice verse.
 She probably use trash to criticize social elite of that time.
@@
 
-% Landy'nin yaptığı bir çok iş aslında çöple ilgili olduğu savunulabilir.
-Hepsinin anlatmak mümkün olmasada bir diğer için sahip olduğu tüm eşyaları bozmasıyla ilgili.
-Daha önceden bahsettiğim geri dönüştürme tanımları ile ilgili olarak bu işi downcycling yöntemi arasında görülebilir.
-
 Not all artist transform trash although some deconstruct them.
@@
 
+% TODO burayı da düzeltmek gerek.
 Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
 
-% , as illustrated by the examples cited so far,
-
-%
 %

### 2016-01-17 chapter1_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

@@
 % Change in the production and consumption practices
-\cite[11]{banash2013collage} states that:
-\begin{quote}
-Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption.
-Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.
-\end{quote}
-As a result of it amount of goods boost and the cost of them significantly reduced.
+\citet[11]{banash2013collage} draws attentions to the advancements in the recent history of humankind by stating that \quotes{over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the [Western countries] completed a total transformation of everyday life, reorienting almost every activity toward consumption.} He argues that \quotes{things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As a result of it amount of goods boost and the cost of them significantly reduced.
 Things once reused again and again, now thrown away because it is more affordable to replace with new one.
 As the production increased its by-product material waste is also increased.
-\quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.
+\quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep[ix]{pye2010trashculture}.
 
@@
 In particularly environmental considerations dominates the perceptions of waste.
-\cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.
+\citet[41]{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.
 
 The act of trashing objects and the process of transforming them is not limited with geography, nationality and modern ages.
-It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}.
+It is a very common notion from urban areas to rural ones, from modern societies to ancient ones \citep[33]{rathje1992rubbish}.
 Anyone can encounter with trash in the crowded urban areas \quotes{as well as the remotest corners of the world} \citep[16]{cerny1996recycled}.
@@
 Trash is everywhere and, produced every time.
-It is inseparable from people's activities.
+It is inseparable from people’s activities.
 \quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from} \citep[xxv]{zimring2012encyclopedia} their habitat.
-In other words, refuse is part of people's daily activities.
+In other words, refuse is part of people’s daily activities.
 Production of it never stops.
@@
 
-Trash is in the streets, in people's home, in the sea that people swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
-Even if trash is tried to move away from people's habitat, it is as close as the nearest waste bin.
+Trash is in the streets, in people’s home, in the sea that people swim, rotating around the globe\footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}.
+Even if trash is tried to move away from people’s habitat, it is as close as the nearest waste bin.
 
 People do not think what happens after they throw trash away.
-It exits from people's life but not from the world.
+It exits from people’s life but not from the world.
 It is stacked to another place.
-A project conducted by MIT\footnote{Massachusetts Institute of Technology} in America explores the journey of trash by placing trackers onto the trash \citep{chen2009mit}.
+A project conducted by Massachusetts Institute of Technology in America explores the journey of trash by placing trackers onto the trash \citep{chen2009mit}.
 According to their results trash spreads away across the country and this journey takes month.
@@
 % Different scales
-The scale of trash production is not same for everybody or every country. \cite[2]{chen2015waste} writes that: 
-\begin{quote}
-The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.
-The higher the income level and the rate of urbanization, the greater the amount of solid waste produced.
-OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries.
-Turkey is a member of this organization.} countries produce almost half of the world’s waste.
-Africa and South Asia produce the least waste.
-High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators.
-Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps.
-However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
-\end{quote}
-
-Similar to these as stated by \cite[16]{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.} Moreover from trash many unexpected results can be extracted.
-\cite[xxv]{zimring2012encyclopedia} argues that:
+The scale of trash production is not same for everybody or every country.
+\citet[2]{chen2015waste} writes that by referring to analysis of World Bank \quotes{the amount of solid waste generated in cities is growing faster than the rate of urbanization.} She argues that when the people's income level and the rate of urbanization increased, production of waste also increases.
+Chen notes that nearly half of the world’s waste are produced by OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization mostly composed of the western developed countries.
+Turkey is a member of this organization.} countries.
+On the other hand, Africa and South Asia generate least waste.
+Similar to these as stated by \citet[16]{cerny1996recycled} \quotes{a person’s wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.} Moreover from trash many unexpected results can be extracted because as \citet[xxv]{zimring2012encyclopedia} argues that:
 \begin{quote}
@@
 They are result of different production and consumption practices.
-For example nuclear power generation and applications of nuclear fission or nuclear technology produces not only energy but also radioactive waste which is very dangerous for living creatures.
+As an end product their effect and existence in the nature changes.
+For example power generation through use of nuclear technology and nuclear fission produces not only energy but also radioactive waste which is very dangerous for living creatures and remains unchanged in the nature for thousands years.
 
@@
 Further economical aspect of trash can not ignored.
-\cite[65]{emgin2012trashion} states that there is a huge business based on eco-friendly products and recyclable goods that is increasingly promoted.
+\citet[65]{emgin2012trashion} states that there is a huge business based on eco-friendly products and recyclable goods that is increasingly promoted.
 
@@
 As noted by \cite{pye2010trashculture} \quotes{at least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art}.
-In the beginning of the 20th century objects that are considered as art enter the scope of art making.
+In the beginning of the twentieth century century objects that are considered as art enter the scope of art making.
 Using non-art objects in the art opened new dimensions for the language of art and practice art making.
@@
 Consumption habits of society are criticized through trash.
-\cite[2]{pye2010trashculture} states that \quotes{trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature}.
+\citet[2]{pye2010trashculture} states that \quotes{trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature}.
 
@@
 As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply.
-Artists' methods and approaches to the subject are stated.
+Artists’ methods and approaches to the subject are stated.
 
@@
 \section{A Note on Terminology}
-Many scholars and authors have used broad range of terms to refer the notion.
+Many scholars and authors have used broad range of terms to refer the subject.
 Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them.
-Sometimes these words are used to signify same concept.
-Although there are slight differences between these words.
-This situation signifies that literature of trash is so wide and there is no consensus on terminology.
-Words are used interchangeably.
-The book Rubbish: the Archeology of Garbage gives clearer definition of some these words:
+Sometimes these words are used synonymously in causal speech but in fact there are slight differences between them.
+This situation signifies that the vocabulary of trash is so wide and there is no consensus on terminology.
+The authors of the book \quotes{Rubbish: the Archeology of Garbage} give clearer definition of some these words:
 
 \begin{quote}
-Several words for the things we throw away ---\quotes{garbage}, \quotes{trash}, \quotes{refuse}, \quotes{rubbish}--- are used synonymously in causal speech but in fact have different meanings.
-\textit{Trash} refers specifically to discards that are at least theoretically \quotes{dry} ---newspapers, boxes, cans, and so on.
-\textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal.
-Refuse is an inclusive term for both the wet discards and the dry.
-Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris.
+\textit{Trash} refers specifically to discards that are at least theoretically dry ---newspapers, boxes, cans, and so on.
+\textit{Garbage} refers technically to wet discards ---food remains, yard waste, and offal.
+\textit{Refuse} is an inclusive term for both the wet discards and the dry.
+\textit{Rubbish} is even more inclusive: It refers to all refuse plus construction and demolition debris.
 The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on.
-We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech.
-The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.
 \citep[9]{rathje1992rubbish}
@@
 
-Artist Alice Bradshaw has published a 36 page \quotes{Rubbish Newspaper} which contains these words and illustrates their place in literature and artworks.
+Moreover artist Alice Bradshaw has published a 36 page \quotes{Rubbish Newspaper}.
 It is based on her extensive research on this subject.
+The newspaper contains these words and illustrates their place in literature and artworks.
 
-In this thesis like many scholars I also use these words interchangeably. However mainly in this thesis scope I prefer trash which better signifies dry paper discard.
+In this study like many scholars I also use these words interchangeably. However mainly in this thesis scope I prefer to trash which better defines dry paper discard.
 
 In addition to these there is also a confusion of the terms: reuse and recycling which are the general methods of transforming trash to the another object or concept.
-Both of them are used widely by scholars.
+Both of them are used widely by scholars and artists.
 
@@
 Reusing lengthens the life of the item or material.
-The main purpose is to make the item last as long as it can.
 To reuse is to use something again instead of throwing it away.
@@
 
-On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} In recycling, an object is processed into a totally new product.
+On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} Particularly, through the process of recycling, an object is used as a raw material in the production of new product.
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
@@
 
-\cite[72]{strasser1999waste} explains recycling by referring to the Oxford English Dictionary as:
+\citet[72]{strasser1999waste} explains recycling by referring to the Oxford English Dictionary as:
 \begin{quote}
@@
 Upcycling is a term coined by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
-It is argued that art, in this scope, acts as a tool of transformation and reintroduces into certain orders what was once regarded waste.
+It is argued that art, in this scope, acts as an instrument of transformation and re-presents artifacts what was once regarded waste.
 This approach resists the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
-Some of the scholars and artist uses upcycling for their works.
+Some of the scholars and artist uses the method of upcycling for their works.
 Undertaking thesis project is about those objects that are reproduced from trash through the procedure of upcycling.

### 2016-01-17 chapter2_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

@@
 %****************************************
-\section{Throw Away Culture}
+\section{Throwaway Culture}
 
-Life Magazine (1955: 43) published an article titled \quotes{throw away Living} and proclaimed the arrival of the \quotes{throw away society}.
+Life Magazine (1955: 43) published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society}.
 It is described as behavioral consumption pattern of society based on throwing away objects after use.
@@
 With these items people can spend their time and effort for other activities.
-In fact, the term \quotes{throw away society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
+In fact, the term \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.
 
-According to findings of archaeologist Daniel Ingersoll the age of the throw away world began not in the twentieth century but during the nineteenth \citep[41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throw away society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
+According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[as cited in][41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
 According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
@@
 In this thesis dealt specifically with industrially produced consumer discards and their subsequent transformation.
-This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century.
+This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the post industrial age.
 In its most basic form, consumer culture can be explained, as \quotes{the activities and ethics of a society are determined by patterns of consumption} \citep[2]{mamiya1992pop} rather than production.
@@
 
-\cite[9]{hawkins2001plastic} argues that \quotes{Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
-The capacity for serial replacement is also the capacity to throw away without concern.} It can be understood that both mass production and consumption support each other.
+\citet[9]{hawkins2001plastic} argues that \quotes{Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new.
+The capacity for serial replacement is also the capacity to throwaway without concern.} It can be understood that both mass production and consumption support each other.
 Not only consumerism, but also mass production plays significant role in this phenomena.
@@
 Some of the works of the artist can be examined in the light of discussed phenomena.
-They establish some methods to reflect the throw away culture and its waste generated patterns.
+They establish some methods to reflect the throwaway culture and its waste generated patterns.
 They offer new dimensions to see the subject.
@@
 
-\textit{Caps Seurat} shown in figure \ref{fig:ChrisJordan_Numbers_CapsSeurat} displays 400,000 plastic bottle caps together, equal to the average number of plastic bottles consumed in the United States in every minute.
-It is one of the pieces of Portraits of Global Mass Culture by photographer Chris Jordan.
+\textit{Caps Seurat} shown in figure \ref{fig:ChrisJordan_Numbers_CapsSeurat} displays four hundred thousand plastic bottle caps all together.
+\quotes{It equal[s] to the average number of plastic bottles consumed in the United States in every minute} says Jordan.
+It is one of the piece of Portraits of Global Mass Culture by photographer Chris Jordan.
 In this series, he revisits the statistics of modern societies.
@@
 He argues that \quotes{translating these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension} \citep[as cite in][]{boustead2015impossible}.
-Most of his works are created from photographs of everyday trash and mass consumption leftover.
-He points out the blind unawareness involved in consumerism.
-His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits.
+He creates these works through the combining photographic illustration of everyday trash and mass consumption leftover.
+He draws attention to the blind unawareness entangled in consumerism.
+His work, while often disturbing, is a strong message about ignorant practices in people's everyday lives, leaving it to the viewer to draw conclusions about the unavoidable consequences which will originate from people's daily consumption routines.
 He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
@@
 Gwyneth Leech saves all of her coffee cups to use them as canvases for her abstract illustrations.
-She transforms her coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of throw away caffeine culture.
+She transforms her coffee cups that are no longer junk but a tool for art, ideas, conversation, and memories of a social moment upcycled from the detritus of throwaway caffeine culture.
 Buying a beverage from a coffee shop is a daily event for Leech and also for many other people.
 These coffee shops are located all around the world and busy corners of cities.
-She uses cups as a surface on which to draw and paint.
-Moreover, on the bottom of each one, she records the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a moment.
-The installation shown in figure \ref{fig:GwynethLeech_CoffeeCups} makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away.
-It can be seen as a measure of time gone by, of money spent, of space to be taken up in a dump site.
+She uses cups as a canvas on which to draw and paint.
+Moreover, on the bottom of each one, she records the date, location, occasion and drink consumed so that every hand-made cup artwork becomes the record of a moment.
+The installation shown in figure \ref{fig:GwynethLeech_CoffeeCups} makes visible widely ignorant patterns of consumption; this is what one simple take-away beverage looks like over the course of many years, this is what would usually be thrown away.
+It can be seen as a measure of time gone by, of money spent, of volume to be taken up in a dump site.
 However, as \cite{leech2015cups} \quotes{upcycles each used cup into an artwork, it becomes the measure of other things as well: an artist’s regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.} There are different versions of installations.
-Here paintings on paper coffee cups are displayed in an open window space.
-She publicly draws their cups.
-Public drawing project were showed at many places and date.
+Here paintings on paper coffee cups are displayed in an open window space and she publicly paints them.
+Her public drawing project were showed at many places and date.
 During public drawing projects, she draws with other people.
@@
 
+% FROM drink UP, author: Werthan, Sarah, artist: Leech, Gwyneth. A Year in Cups. http://gwynethleech.com/
+% trash and art collided. Paper and art, actually paper already medium of art, but is there anything different here. Itself is a part of a work, not the drawing, or painting.
+% Documenting via a blog or a website. (what type of dimension it brings the work? maybe connect them, leave message.)
+% Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives. The reason of website.
+% “People see that an artist can make work anywhere, and make creative spaces anywhere,” she asserts.
+
 \begin{figure}[h!]
@@
 
-Figure \ref{fig:SongDong_WasteNot} displays over 10,000 objects owned by Chinese artist Song Dong’s mother.
-She refused to throw anything away if she could possibly reuse it.
+Figure \ref{fig:SongDong_WasteNot} displays over ten thousand objects owned by Chinese artist Song Dong’s mother.
+She declined to discard anything if she could in some way reuse it.
 \textit{Waste Not} is an installation exhibited various museums of the world.
@@
 
-Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of 20th century by the saying \textit{wu jin qi yong} (waste not).
+Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of twentieth century century by the saying \textit{wu jin qi yong} (waste not).
 As a result, all commodities owned or collected items are stockpiled and preserved as protection against for future poverty, even in the times of improving economic conditions.
 
-Like many other Chinese at the time, Zhao developed the habits of frugality and thrift in order to make the best of what limited she had.
-Song recalls that when he was a child, \quotes{my mother always brought scraps of fabric to make clothes, because they did not need to be purchased with the government ---distributed clothing coupons.} She continued to collect them even in prosperity times because she feared that the shortages might some day return.
+In the same way as other Chinese at the time, Zhao developed the habits of frugality and thrift in order to make the best of what limited she had.
+By recalling memories from childhood, Song says that \quotes{my mother always brought scraps of fabric to make clothes, because they did not need to be purchased with the government ---distributed clothing coupons.} She continued to collect them even in prosperity times because she feared that the shortages might some day return.
 The habit of waste not is seen as a \textit{fabao} ---literally a powerful weapon to protect against a return to hardships.
 
-When Song’s father died suddenly in 2002 his mother suffered an emotional collapse and her habit of holding on to matters was taken to extremes.
+When Song’s father died suddenly in 2002 his mother suffered from loneliness and an emotional collapse.
+As a result of it her practice of saving matters was reached to extreme levels.
 Every possible space of her tiny house completely filled with thousands of domestic items.
@@
 In other words, she maintained her habit.
-Song eventually realized that, as he states it:
-
-\begin{quote}
-My mother’s need to fill space with daily-life objects resulted from a need to fill the emptiness after my father’s death.
-I recognised that in this era of transition, a person could live through several different lives in just one lifetime.
-In the wink of an eye, ones life could undergo great changes causing deep divisions between old and young.
-\end{quote}
+Song eventually realized that, as he states that \quotes{my mother’s need to fill space with daily-life objects resulted from a need to fill the emptiness after my father’s death.} He recognizes that \quotes{a person could live through several different lives in just one lifetime.
+In the wink of an eye, ones life could undergo great changes causing deep divisions between old and young.}
 
@@
 
-Jane Alison, senior curator at the Barbican, states that \textit{Waste Not} \quotes{helps us to understand the reality of Chinese history and culture in the 20th century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
+Jane Alison, senior curator at the Barbican, states that \textit{Waste Not} \quotes{helps us to understand the reality of Chinese history and culture in the twentieth century century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
 
@@
 Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people.
-He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away} \citep[as cited in][301]{lukas2012garbage}.
+He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throwaway} \citep[as cited in][301]{lukas2012garbage}.
 The field of garbology involves the study of refuse and waste.
-It enables researchers to document information on the nature and changing patterns of modern rubbish, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}.
+It enables researchers to document information on the dump and changing patterns of modern rubbish, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}.
 According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s.
@@
 Tracey Emin puts her private life to the public.
-The work, which Emin now describes as a portrait of a young woman.
-Around her, there are pieces of junks speared all over the room.
-We can understand from her junk what type of life she has.
-We enter the world of the artist through her trashes.
+This work can be as a portrait of artist in a post-modern fashion.
+Around the bed, there are pieces of junks speared all over the room.
+It can be understood from her junk what type of life she has.
+To put it another way, viewer enter the world of the artist through her trashes.
 
@@
 However, it still exists in reality and waits at somewhere else.
-In other words, it does not disappear, moves away.
+Strictly speaking, it does not disappear, moves away.
 
@@
 
-In \singlequotes{The Social Life of Things} \cite[3]{appadurai1988social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \cite{kopytoff1986cultural} notes that the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different systems of value that are both economically and culturally inscribed.
+In \singlequotes{The Social Life of Things} \citet[3]{appadurai1988social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \cite{kopytoff1986cultural} notes that the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different systems of value that are both economically and culturally inscribed.
 Appadurai focuses on the \quotes{commodity potential} of things and asserts that \quotes{things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant} (1986: 13).
@@
 % http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
-\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in 20th century.
+\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in twentieth century century.
 Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum.
@@
 Committee rejected \textit{Fountain}, even though the rules declared that all works would be accepted from artists who paid the fee.
-It is considered one of the major artworks of the 20th century because of challenging the existing understanding of art.
+It is considered one of the major artworks of the twentieth century century because of challenging the existing understanding of art.
 Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist.
@@
 
-%Firstly trash is created (by the throw away culture).
+%Firstly trash is created (by the throwaway culture).
 Even if there is counter argument about it, the focus is disposable items and their amount is very high.

### 2016-01-17 chapter3_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

@@
 Artists who use discarded items in their work will be analyzed in the light of arguments discussed in the previous chapter.
-Here, the main question is why artists select to use society's debris rather than fresh items.
+Here, the main question is why artists select to use society’s debris rather than fresh items.
 Hence, my research will focus on the place of trash in the world of art by looking at different methods and approaches.
@@
 
-From the beginning of 20th-century non-art objects draw attention of artists.
+From the beginning of twentieth century-century non-art objects draw attention of artists.
 Usage of these objects play significant role in the development of art trough time.
@@
 
-One of the remarkable change in 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
+One of the remarkable change in twentieth century-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
 These objects are not commonly recognized as art often because they already have a non-art function.
-Their place in the society and people's mind commonly have a different meaning.
+Their place in the society and people’s mind commonly have a different meaning.
 Beyond that, artists started to use them for their own purposes.
@@
 
-In 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
+In twentieth century-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
 Previously paintings are based on linear perspective and realistic style.
@@
 Jacknis \citep[as cited in][]{cerny1996recycled} claims that \quotes{like collage in art or quotation in literature, the recycled object carries a kind of \singlequotes{memory} of its prior existence.
-Recycling always implies a stance toward time ---between the past and the present--- and often a perspective on cultures ---one's own and others.}
+Recycling always implies a stance toward time ---between the past and the present--- and often a perspective on cultures ---one’s own and others.}
 
@@
 Collages and assemblages can be composed of all types of objects such as trash and found object.
-The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp's concept of ready-made.
+The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp’s concept of ready-made.
 Industrially manufactured or anything found  anymore can found a place in the art.
@@
 They are generally picked up somewhere and their value for the finder might be aesthetic, symbolic and remembrance.
-\cite[170]{gascoyne1936short} by analyzing found objects in Surrealist art, writes that artist \quotes{discovers a hidden symbolic significance in the [found] object which is preserved when the object is \singlequotes{framed} as art.} In other words, the finder discovers an unrealised significance by removing found object from its previous context and placing it in a new one.
+\citet[170]{gascoyne1936short} by analyzing found objects in Surrealist art, writes that artist \quotes{discovers a hidden symbolic significance in the [found] object which is preserved when the object is \singlequotes{framed} as art.} In other words, the finder discovers an unrealised significance by removing found object from its previous context and placing it in a new one.
 The meaning of material artifacts was derived from their symbolic relation to another entities such as person, time, place, experience rather than through their physical attributes \citep{camic2010trashed}.
-\cite{camic2010trashed} notes that people's motivation and usage of found objects also occur in various ways.
+\cite{camic2010trashed} notes that people’s motivation and usage of found objects also occur in various ways.
 Further enjoyment through found objects is different than appreciating art in museums which is isolated and refined activity.
@@
 
-In the French film Amélie\footnote{Original title: Le fabuleux destin d'Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris.
+In the French film Amélie\footnote{Original title: Le fabuleux destin d’Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris.
 He collects them and glue them together in a photo album.
@@
 In other words, the skin of city revealed through her photos in micro scale.
-On the skin of city there are lots of trash including \quotes{a piece of chewing gum with an engraved leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful} as looked through the window of they capture the city life and skin of the city that we touched.
+On the skin of city there are lots of trash including \quotes{a piece of chewing gum with an engraved leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of \singlequotes{worthlessness} suddenly becoming meaningful} as looked through the window of they capture the city life and skin of the city that we touched.
 She shows us tiny details of huge cities.
@@
 He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millions of people.
-Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump.
+Film documents whole process of development and production of \textit{Pictures of Garbage} made of collected trash from dump.
 He selects unusual materials and people for portraits rather than the powerful and notable people as commonly encountered at Renaissance.
@@
 \quotes{A violin is worth more than a house here,} says Favio Chávez by pointing out their hard conditions.
-The orchestra's director and founder.
 Favio Chávez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez.
@@
 The French word \textit{bricoleur} is someone who works with own hands and construct \textit{bricolage}.
-The term coined by \cite[17]{levi1966savage} and he explains it as:
+The term coined by \citet[17]{levi1966savage} and he explains it as:
 
@@
 Not all the time and every artist turn trash into different objects, sometimes they only trash them.
-Michael Landy's Art Bin is one of them.
+Michael Landy’s Art Bin is one of them.
 It is a room size transparent bin placed inside of the art gallery.
@@
 In this work he break-ups this notion that encouraging the artist reveals their failures to the public.
-Like his words, it is “a monument to creative failure”.
-On the other side, there is a provocative approach to the art and art objects by saying that "Nothing is too good for the art bin." There is no limitation of throwing away even if art.
+Like his words, it is \quotes{a monument to creative failure.} On the other side, there is a provocative approach to the art and art objects by saying that \quotes{Nothing is too good for the art bin.} There is no limitation of throwing away even if art.
 
@@
 Michael Landy is one of them.
-Michael Landy's Break Down Inventory is a two-week show (display) of destruction process of his all possessions on a dissemble line with the help of 10 workers.
+Michael Landy’s Break Down Inventory is a two-week show (display) of destruction process of his all possessions on a dissemble line with the help of 10 workers.
 Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part.
@@
 It can be viewed as the idealization of goods and products (even people).
-At this point, it can be referred back to Žižek's claim that people's false consciousness about balanced and idealized notion of nature.
+At this point, it can be referred back to Žižek’s claim that people’s false consciousness about balanced and idealized notion of nature.
 It can be understood that this type of clarification of objects may result in this false perception.
-What Varda's finding is an excellent exemplification of what Žižek wants to point out.
+What Varda’s finding is an excellent exemplification of what Žižek wants to point out.
 
@@
 She keeps light to the modern life gleaners that are not visible every time.
-One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants and refugees who are also considered as surplus of society.
+One of them is the teacher named Alain, an urban gleaner with a master’s degree who teaches French to immigrants and refugees who are also considered as surplus of society.
 It can seen that from this example, gleaning becomes also a form of resistance to ruling system ---a way of rejecting to be limited by mainstream expectations and lifestyle.
@@
 It is like giving life or finding life from discarded object.
-
-% TODO MOVE TO COMMON APPROACH, introduction.
-%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
-
-%%%
-%%%
-%%%
-%\section{Summary}
-
-% FROM drink UP, author: Werthan, Sarah, artist: Leech, Gwyneth. A Year in Cups. http://gwynethleech.com/
-% trash and art collided. Paper and art, actually paper already medium of art, but is there anything different here. Itself is a part of a work, not the drawing, or painting.
-% Documenting via a blog or a website. (what type of dimension it brings the work? maybe connect them, leave message.)
-% Creating art in public places can demystify the process for passers by, Leech says, making artistic expression more accessible and part of people’s everyday lives. The reason of website.
-% “People see that an artist can make work anywhere, and make creative spaces anywhere,” she asserts.
-
-% TODO PRAP. from rethink, reimagine, reinvent
-%\paraphrase{Recycling art approach to using reclaimed objects in artworks requires rethinking, or examining the affordances of a particular object to explore the possibilities for the object's inclusion in an artwork.
-Assemblage art involves the creation of new and innovative objects from what were once considered objects of waste; that is.
-through their use in assemblage pieces, reclaimed objects are endowed with a new.
-sometimes paradoxical meaning.
-The transformations of the objects used in assemblage pieces ask viewers to reconsider the notion of "valuable" as they are challenged to look at everyday objects with a new perspective (Taylor, 2006).
-Viewers confront issues relating to the functionality of objects during modern processes of production, consumption and distribution.}
-
-%"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
-This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
-
-%
-%
-%\textbf{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
-%\begin{itemize}
-%\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
-%\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
-%\item Try to find a new value and meaning from the discarded material that are useless anymore.
-To explore a new approach, new way.
-Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable).
-Trash to treasure.
-%\item Using discarded item to represent other discarded things by the ruling ideology or approach.
-For example, trash can be used to represent refugees.
-The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential.
-In other words, refugees have potential but we see them as players that will change our current system.
-Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle.
-Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
-%\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
-%\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
-%\item Instead of a world that produce trash, how could it be a world created from trash?
-%\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community.
-It also signifies that trash still has a good quality to used with new materials.
-Creating composite products from new and reused items.
-Using the valuable thing with the invaluable thing.
-It becomes more valuable or less valuable.
-Depends on the perception.
-%\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
-%\end{itemize}
-
-% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
-%Recycling has always been a common practice in the arts at least at a non-material level.
-From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
-Take and put.
-De-contextualize and re-contextualize.
-In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].
-
-% TODO new comer
-% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\summary{Resistance} 
-%\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
-(sahlins 1992, 16)"
-
-% TODO new comer
-% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
-%\summary{Ironic}
-%\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
-the irony is often embodied visually and conceptually.
-opposite of natural use, expected perception.
-for example making something from nothing or turning trash into treasure.
-By juxtaposing different materials changing context and place.

### 2016-01-17 chapter4_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

--- 2016-01-08 chapter4_reduced.tex
@@
 
-% Epigraph
 \begin{singlespace}
-% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
-\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful?
+\epigraph{The first question I ask myself when something doesn’t seem to be beautiful is why do I think it’s not beautiful?
 And very shortly you discover that there is no reason.
 If we can conquer that dislike, or begin to like what we did dislike, then the world is more open.
-That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
+That path ---of increasing one’s enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
 \end{singlespace}
@@
 It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature.
-Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.
+Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man’s trash is another man’s treasure}.
 
@@
 It has a value and part of our games and indispensable source of fun.
-The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously.
+The notion of playing with it can be related with the Picasso’s collage work \quotes{Still Life with Chair Caning} mentioned previously.
 He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials.
@@
 The day after we brought some colorful paper that was bought from stationery store.
-Our papers' shape and color looked same.
+Our papers’ shape and color looked same.
 However her papers were different in every dimension.
@@
 For some people it is a life saving practice.
-It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2).
+It can be seen in the case of artist Song Dong’s mother (mentioned in chapter 2).
 This practice result in establishing stronger and intimate relationship with objects.
@@
 It is the result of inevitable rhythm of modern life style.
-Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard.
+Consuming and wasting is part of people’s daily routine and most of the time they are not aware of what they consume, and what they discard.
 In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines.
@@
 Because it is ignored by discarding and therefore undiscovered.
-It waits us to be discovered and possibly (as Picasso's explanation on his work 'Bull's Head'\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.
+It waits us to be discovered and possibly (as Picasso’s explanation on his work ’Bull’s Head’\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.
 
@@
 
-% TODO Lars Eighner BIB'e eklenecek.
+% TODO Lars Eighner BIB’e eklenecek.
 
@@
 \subsection{Collecting}
-Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that
+Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner’s instructions helped me a lot when collecting objects. He writes that:
 
@@
 \quotes{The question of who owns these discards is not trivial} \citep{zimring2012encyclopedia}.
-This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects.
+This question makes me feel uncomfortable because of thinking that stealing that someone elses’ objects.
 Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
@@
 
-The issue of owner becomes more complicated when owners' social status considered.
+The issue of owner becomes more complicated when owners’ social status considered.
 Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood \citep[as cited in][]{pricano2011trashtalk}.
@@
 Whenever I meet my friends I ask them to save their discard for the project.
-The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}.
+The importance of collaboration with them can be understood the term \quotes{citizen science} which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}.
 I need to note that this is not a scientific project but the notion belongs there.
@@
 
-Collected items reflect my and contributors' consumption practices.
+Collected items reflect my and contributors’ consumption practices.
 People as mentioned previously consumption patterns can be tracked from their leftover.
-From logos of companies onto the packages reveal people's choices and give clues about their social status.
+From logos of companies onto the packages reveal people’s choices and give clues about their social status.
 
@@
 
-\textbf{Burger King packages} are collected from the office where I work.
+\textbf{Burger King packages} (Figure \ref{fig:BurgerKingBag}) are collected from the office where I work.
 At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant.
@@
 Some people think that it is disgusting to use it for other purposes because of oil onto it.
-But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \cite[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}.
-She refers to resolution on dirt of \cite[36]{douglas2003purity}:
+But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \citet[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}.
+She refers to resolution on dirt of \citet[36]{douglas2003purity}:
+
 \begin{quote}
@@
 
-This simply explains that our perceptions to the objects are relative and change in their usage context.
+This simply explains that our perceptions to the objects which are relative and change in their usage context.
+Further it signifies that trash only catches attention of people when it is in wrong place.
+\citet[92]{thompson1979rubbish} argues that people only recognize rubbish when it is in unusual place and condition.
+He also points out rubbish in the wrong place is \quotes{emphatically visible and extremely embarrassing.} \citet[391]{parsons2008thompsons} concludes that rubbish is \quotes{no longer used or loved or cared for and often no longer seen.
+Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.}
 
@@
 
-\textbf{Varuna Gezgin papers} are the pages of obsolete dinner menu.
+\textbf{Varuna Gezgin papers} (Figure \ref{fig:VarunaGezgin}) are the pages of obsolete dinner menu.
 When leaving there I showed my notebooks and asked to the cashier that I could able to present them at Varuna Gezgin.
@@
 
-% I'm collecting the paper that are under the plates.
-When we are leaving this place, I ask the cashier at the desk that \quotes{I am making small notebooks and is it possible to exhibit there?} I asked that is it possible to give them to people.
-Firstly he asked me that did I sell them or not but I said \quotes{no they are free and part of my thesis project.} After that he offered me to give e are a lot of unused papers.
-I can give you.
-they are not used and waiting to be recycling.
-I took some of the papers, and that papers are part the sheets of these papers.
-
-\textbf{The banner} is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates.
+\textbf{The banner} (Figure \ref{fig:Banner_1}) is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates.
 In Middle East Technical University there is a tradition that in graduation ceremony new grads walk through in the stadium and greet to the tribunes.
@@
 They are found on public places.
-They are not personal objects like in the work of Tracey Emin's \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets.
+They are not personal objects like in the work of Tracey Emin’s \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets.
 Identity of owner are not certain.
@@
 
-There are different dimensions of notebooks. Most of them are half of A4 or quarter of it.
+There are different dimensions of notebooks. Most of them are half of A4 (210mm x 297mm) or quarter of it. Collected papers dimensions shape the size of the notebooks.
 
@@
 
-\textbf{Reunion.} These notebook's pages are collected from restaurant Varuna Gezgin, in Ankara.
+\textbf{Reunion.} These notebook’s pages are collected from restaurant Varuna Gezgin, in Ankara.
 We went there to meet some friends after long time.
@@
 
-\textbf{Secondhand.} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.
+\textbf{Secondhand.} It can be thought that these notebooks are second hand objects.
+Used by someone else and still appropriate for reusing.
+Here I wish that these papers and notebooks are used more than twice.
 
-% TODO burada bir isim uydurmak gerekli.
 \textbf{Daro.} For some of the notebooks it is not obvious to name them.
@@
 \subsection{Website}
-Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people's life again, but also it finds another place in the digital space.
+Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people’s life again, but also it finds another place in the digital space.
 
@@
 It contains lots of works from all over the world.
-Full of creativity and showcase of richness of people's expressions on the small notebooks.
+Full of creativity and showcase of richness of people’s expressions on the small notebooks.
 My work can be considered as a sketch book project through trash.

### 2016-01-17 chapter5_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

@@
 
-This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas, theories and people's experiences of things in throw away culture.
+This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas, theories and people’s experiences of things in throw away culture.
 
-People's evaluations of what is trash and treasure are both content and context dependent and are not fixed values.
+People’s evaluations of what is trash and treasure are both content and context dependent and are not fixed values.
 The line between them are blurred in the explored practices and works of art.
-Indeed, temporal value judgements of 'rubbish' and 'art' are often at the core of such art works.
+Indeed, temporal value judgements of ’rubbish’ and ’art’ are often at the core of such art works.
 The analysis of selected works methodologies and approaches show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.
@@
 Different selection of works and their analysis and relation between them will form another thesis which identifies another dimension of trash.
+
+% Bunu landfill orchestrada kullan
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%\summary{Ironic}
+%\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic.
+the irony is often embodied visually and conceptually.
+opposite of natural use, expected perception.
+for example making something from nothing or turning trash into treasure.
+By juxtaposing different materials changing context and place.
+
+% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
+%Recycling has always been a common practice in the arts at least at a non-material level.
+From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole.
+Take and put.
+De-contextualize and re-contextualize.
+In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].
+
+% TODO new comer
+% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
+%\summary{Resistance} 
+%\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins’s assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence.
+(sahlins 1992, 16)"
+
+% TODO MOVE TO COMMON APPROACH, introduction.
+%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}
+
+%"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts.
+This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}
+
+%\item Instead of a world that produce trash, how could it be a world created from trash?

### 2016-01-17 chapter1_final.tex
turnitin fixes
Former-commit-id: 18946952758077b82f1e3365219cc043e9cc2f0d

@@
 \citet[2]{chen2015waste} writes that by referring to analysis of World Bank \quotes{the amount of solid waste generated in cities is growing faster than the rate of urbanization.} She argues that when the people's income level and the rate of urbanization increased, production of waste also increases.
-Chen notes that nearly half of the world’s waste are produced by OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization mostly composed of the western developed countries.
-Turkey is a member of this organization.} countries.
+Chen notes that nearly half of the world’s waste are produced by OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization whose members are mostly western developed countries.} countries.
 On the other hand, Africa and South Asia generate least waste.
 Similar to these as stated by \citet[16]{cerny1996recycled} \quotes{a person’s wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.} Moreover from trash many unexpected results can be extracted because as \citet[xxv]{zimring2012encyclopedia} argues that:
+
 \begin{quote}
@@
 According to dictionary Merriam-Webster, the word reuse means \quotes{to use again especially in a different way or after reclaiming or reprocessing.} Reusing includes usage of the same product unaltered in structure.
-Reusing lengthens the life of the item or material.
+Reusing lengthens the life of the item or material in society.
 To reuse is to use something again instead of throwing it away.
@@
 
-On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} Particularly, through the process of recycling, an object is used as a raw material in the production of new product.
+On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} Particularly, through the systematic process of recycling, an object is used as a raw material in the production of new product.
 Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product.
@@
 
-\citet[72]{strasser1999waste} explains recycling by referring to the Oxford English Dictionary as:
-\begin{quote}
-...
-recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste.
-Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.
-\end{quote}
+\citet[72]{strasser1999waste} by referring to the Oxford English Dictionary notes that \quotes{recycling originated in the oil industry during the 1920s.} Here the main purpose is to reduce the waste of petroleum therefore \quotes{partially refined petroleum sent through the refining cycle again.} She explains that \quotes{the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.}
 
@@
 Creative reuse, inventing new things from discard.
-Upcycling is a term coined by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
-It is argued that art, in this scope, acts as an instrument of transformation and re-presents artifacts what was once regarded waste.
-This approach resists the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
-Some of the scholars and artist uses the method of upcycling for their works.
-Undertaking thesis project is about those objects that are reproduced from trash through the procedure of upcycling.
+The term upcycling is coined by architect and designer William McDonaugh and chemist Michael Braungart.
+It can be explained as \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}.
+Upcycling approach resists the argument that an object is dead once it is disposed of \citep{emgin2012trashion}.
+It can be argued that art, in this scope, acts as an instrument of transformation and re-presents artifacts what was once regarded waste.
+In the light of this argument, methods of analyzed artists in this thesis when producing their artworks can be categorized as upcycling.
+Additionally, undertaking thesis project is about handmade notebooks that are reproduced from discarded papers through the procedure of upcycling.

### 2016-01-17 chapter2_final.tex
turnitin fixes
Former-commit-id: 18946952758077b82f1e3365219cc043e9cc2f0d

@@
 \quotes{The commodities of food and drink must be safe, sterile and private} \citep[70]{kennedy2007ontology}.
+
+%At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene \citep{pye2010trashculture}.
 
@@
 On the other hand, there are examples of saving everything instead of wasting.
-In the work of Song Dong, \textit{Waste Not} thousands of domestic objects are exhibited.
+In the work of Song Dong, \textit{Waste Not}, thousands of domestic objects are exhibited.
 They are owned by his mother and saved for later use.
@@
 
-Jane Alison, senior curator at the Barbican, states that \textit{Waste Not} \quotes{helps us to understand the reality of Chinese history and culture in the twentieth century century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
+Jane Alison, senior curator at the Barbican Art Gallery in London, states that \quotes{\textit{Waste Not} helps us to understand the reality of Chinese history and culture in the twentieth century century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
 
@@
 The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice.
-At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene \citep{pye2010trashculture}.
 With the help of mentioned understanding of trash, what can be understand from the works of art?
@@
 
-Tracey Emin puts her private life to the public.
+Tracey Emin puts her private life to the public via representation of her bed.
 This work can be as a portrait of artist in a post-modern fashion.
@@
 
-% From wiki
-Every detail of her private life is presented through her bed in an uncensored fashion.
-The idea of \textit{My Bed} was result of a depressive period in the artist’s life when she had remained in bed for several days without eating or drinking anything but alcohol.
-The sensation of depression leading to disarray and detritus is not completely unusual to many people, and \textit{My Bed} therefore enforces the communicative power that Tracey Emin seeks with her work.
+Every detail of Emin's private life is presented through her bed in an uncensored fashion.
+The idea of \textit{My Bed} (Figure \ref{fig:TraceyEmin_MyBed}) was result of a depressive period in the artist’s life when she had stayed in bed for a few days without eating or drinking anything except alcohol.
+The feeling of depression resulting in mess and detritus is not completely unusual to many people, and \textit{My Bed} therefore has a bold affect on the viewer.
 The artwork generated great media enthusiasm, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist’s room, such as condoms, underwear with menstrual blood stains, other junks, and functional, everyday objects, including a pair of slippers.
-The bed was presented in the state that Emin claimed it had been after languishing in it for several days; at the time she was suffering suicidal depression brought on by relationship difficulties.
 
-It is a realization what she did during her depression time.
-It perfectly represents her condition during those days.
+It is a realization what she did during her depression time and perfectly represents her condition during those days.
 It can be understood that trash is part of our life.
@@
 The work can be interpreted as a self-portrait of a woman at a time of emotional depression.
-However, it is still a bed and all that a bed symbolizes and covers: sleep, sleeplessness, sex, birth, death and dreams.
+However, it is still a bed and all that a bed symbolizes and covers life events such as sleep, sleeplessness, sex, birth, death and dreams.
+Further bedroom is one of the most personal spaces in the homes.
 Particularly for the ones that have small rooms and spaces bed becomes a life space.
@@
 It is more than sleeping and provide place for other activities.
-
-% tracey emin joseph beuys arasında bir ilişki var. sanatsal eylem ve kalıntı olarak bakıldığında.
-
-% Aslan yattigi yerden belli olur.
 
@@
 Especially these cycles have accelerated with the arrival of consumer culture.
-For instance, most recent technological gadgets become obsolete within two or three years.
+For instance, most recent technological devices become outdated within a few years.
 Firsthand, secondhand and even trash is exchanged among not only people but also countries.
@@
 It can be claimed that the end of an object’s life equates to the moment when it is refused.
-This action might take place in different forms and for various reasons.
-Nonetheless, in the most accurate and common sense, the life of an object ends in a dump in the state of waste.
+As stated by \citet[63]{emgin2012trashion} this action \quotes{might take place in different forms and for [various] reasons.} In common sense it is considered as waste.
 At this moment, the object is left valueless in all the possible meanings of the term value.

### 2016-01-17 chapter1_final.tex
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

@@
 \begin{singlespace}
-\epigraph{One can even shout out through refuse \ldots}{\hfill---Kurt Schwitters, \textit{Kurt Schwitters}, 1985}
+\epigraph{One can even shout out through refuse\ldots}{\hfill---Kurt Schwitters, \textit{Kurt Schwitters}, 1985}
 \end{singlespace}
@@
 % Change in the production and consumption practices
-\citet[11]{banash2013collage} draws attentions to the advancements in the recent history of humankind by stating that \quotes{over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the [Western countries] completed a total transformation of everyday life, reorienting almost every activity toward consumption.} He argues that \quotes{things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As a result of it amount of goods boost and the cost of them significantly reduced.
+\citet[11]{banash2013collage} draws attentions to the advancements in the recent history of humankind by stating that \quotes{over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the [western countries] completed a total transformation of everyday life, reorienting almost every activity toward consumption.} He argues that \quotes{things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line.} As a result of it amount of goods boost and the cost of them significantly reduced.
 Things once reused again and again, now thrown away because it is more affordable to replace with new one.
-As the production increased its by-product material waste is also increased.
+As the production increased, its by-product material waste is also increased.
 \quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep[ix]{pye2010trashculture}.
@@
 The scale of trash production is not same for everybody or every country.
-\citet[2]{chen2015waste} writes that by referring to analysis of World Bank \quotes{the amount of solid waste generated in cities is growing faster than the rate of urbanization.} She argues that when the people's income level and the rate of urbanization increased, production of waste also increases.
+\citet[2]{chen2015waste} writes that by referring to analysis of World Bank \quotes{the amount of solid waste generated in cities is growing faster than the rate of urbanization.} She argues that when the people’s income level and the rate of urbanization increased, production of waste also increases.
 Chen notes that nearly half of the world’s waste are produced by OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization whose members are mostly western developed countries.} countries.
@@
 Trash can be seen as a design and technological problem \citep{mcdonough2010cradle}.
-Further economical aspect of trash can not ignored.
+Further economic aspect of trash can not be ignored.
 \citet[65]{emgin2012trashion} states that there is a huge business based on eco-friendly products and recyclable goods that is increasingly promoted.
@@
 There are people who collects plastics, scraps and papers from waste bins and landfills.
-For the rag-pickers, collecting others excess and discard is significant source of economical income.
+For the rag-pickers, collecting others excess and discard is significant source of economic income.
 They collect and classify recycle materials to sell them.
@@
 Further many people are inside the business of transforming trash through recycling and reusing.
-People has been looking for aluminum cans, glass bottles and plastics on the streets.
-They collect and sell them to survive.
+People has been looking for aluminum cans, glass bottles and plastics on the streets and garbage bins.
+They collect and sell them for economic purposes.
 There are companies that are collect waste materials to regain them to the industry.
@@
 Artist that give attention to the trash and transform them is in the scope of this thesis.
-
-% TODO relocation.
-% MOVE TO Conclusion of art chapter, discussion of transformation.
-% FROM Trashion: The Return of the Disposed by Bahar Emgin
-%\ People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.
 
@@
 This situation signifies that the vocabulary of trash is so wide and there is no consensus on terminology.
-The authors of the book \quotes{Rubbish: the Archeology of Garbage} give clearer definition of some these words:
+The authors of the book \textit{Rubbish: the Archeology of Garbage} give clearer definition of some these words:
 
@@
 
-Moreover artist Alice Bradshaw has published a 36 page \quotes{Rubbish Newspaper}.
+Moreover artist Alice Bradshaw has published a 36 page \textit{Rubbish Newspaper}.
 It is based on her extensive research on this subject.

### 2016-01-17 chapter2_final.tex
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

@@
 Secondly, I looked through the Žižek’s comments on ecological perspectives that dominate the approaches on rubbish.
-Lastly, through \quotes{Rubbish Theory} transformation of trash and its various states as an object category is examined.
+Lastly, through \textit{Rubbish Theory} transformation of trash and its various states as an object category is examined.
 
@@
 
-According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[as cited in][41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
-According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
+According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth century \citep[as cited in][41]{rathje1992rubbish}.
+On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}.
+According to the result of their qualitative research on consumers over two-year, people are not as wasteful as claimed when considering household possessions such as television, furniture and toys.
 However, their research did not include disposable packaging and bottles.
@@
 Disposable items are made to be thrown away after used once or only a few times.
-They are not permanent or durable and not designed to reuse again.
+They are not permanent or durable and not designed to be reused again.
 Packages of beverages, paper cups and tissues are some of them.
@@
 Their lifetime can be measured in minutes in terms of usage.
-However, their usage duration is very short, they continue to exist in nature.
+Although, their usage duration is very short, they continue to exist in nature.
 
@@
 They were designed to decrease in value over time to be used one, or twice and then to be thrown away.
-This applies not only applies packing ---designed containers that protect and promote products--- but to an ever expanding list of products.
+This applies not only packing ---designed containers that protect and promote products--- but to an ever expanding list of products.
 \quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it.
@@
 Technological advancements can be one of the factors that cause over-consumption habits.
-Disposable items with the help of industrialization can be produced easily.
-Disposable items reduce the labor and human resources as compared to the traditional ways.
-For instance, consider napkin(tissue, towel) versus wipes, glass versus paper cup.
+Disposable items with the help of industrialization can be produced easily with low cost and they reduce the labor and human resources as compared to the traditional ways.
+For instance, consider handkerchief versus napkin, glass versus paper cup.
 Another point is that they are more affordable regarding supply chain and cost.
-In other words, people can put new one easily.
+In other words, people can put new one easily after disposing it.
 Therefore, there is no need to save the old one.
@@
 \end{subfigure}
-\caption{Chris Jordan, \textit{Caps Seurat}, 2011, Offset print, 60x90" in one panel, and 88x132" in 3 panels}
+\caption{Chris Jordan, \textit{Caps Seurat}, 2011, Digital pigment print, 60x90" in one panel, and 88x132" in 3 panels}
 \label{fig:ChrisJordan_Numbers_CapsSeurat}
@@
 He draws attention to the blind unawareness entangled in consumerism.
-His work, while often disturbing, is a strong message about ignorant practices in people's everyday lives, leaving it to the viewer to draw conclusions about the unavoidable consequences which will originate from people's daily consumption routines.
+His work, while often disturbing, is a strong message about ignorant practices in people’s everyday lives, leaving it to the viewer to draw conclusions about the unavoidable consequences which will originate from people’s daily consumption routines.
 He recreates the most remarkable artworks with combining bits of trashes as a mosaic.
@@
 \end{subfigure}
-\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
+\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper cups, Dimensions variable}
 \label{fig:GwynethLeech_CoffeeCups}
@@
 
-Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of twentieth century century by the saying \textit{wu jin qi yong} (waste not).
+Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of twentieth century by the saying \textit{wu jin qi yong} (waste not).
 As a result, all commodities owned or collected items are stockpiled and preserved as protection against for future poverty, even in the times of improving economic conditions.
@@
 
-Jane Alison, senior curator at the Barbican Art Gallery in London, states that \quotes{\textit{Waste Not} helps us to understand the reality of Chinese history and culture in the twentieth century century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
+Jane Alison, senior curator at the Barbican Art Gallery in London, states that \quotes{\textit{Waste Not} helps us to understand the reality of Chinese history and culture in the twentieth century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}
 
-As it can be understood trash reflects people's habits.
+As it can be understood trash reflects people’s habits.
 It is like a mirror.
@@
 
-Every detail of Emin's private life is presented through her bed in an uncensored fashion.
+Every detail of Emin’s private life is presented through her bed in an uncensored fashion.
 The idea of \textit{My Bed} (Figure \ref{fig:TraceyEmin_MyBed}) was result of a depressive period in the artist’s life when she had stayed in bed for a few days without eating or drinking anything except alcohol.
@@
 
-% TODO buarada aşağısını toparlamak gerekli.
 In the light of Žižek’s arguments ecology is not an appropriate (or enough) point to approach trash.
-He points out the need for the new approach to trash.
-This new approach should not idealize it.
-At this point where the practices of art gains importance to establish new understanding of trash.
-
+He points out the need for new approaches to trash.
+This new approach should not idealize nature and trash.
+At this point, the practices of art gain importance to establish new understanding of trash.
 Not every act of transforming trash is not related to ecological concerns.
@@
 Beyond ecological concerns, they are attempting to find new ways to look and live with trash.
-
 Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervention.
-Not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it.
-(Converting what we create harmonious with the existing system.
-Because it is not possible to think that nature will live harmoniously with what we created.
-The more reasonable idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together.
+Not discarding but embracing people's trash, they turned them to a something that worth it to watch and think about it.
+They convert what people throw away into objects that are harmonious with the existing system because it is not possible to think that nature will live harmoniously with what people created.
+The more reasonable idea will be people will live harmoniously with what they create.
+Their action can be seen as turning trash to things that can be lived together.
 
@@
 Loving nature is loving it with all dimensions.
-Live with trash.
-Do not see it as trash.
-Then the question is How to love trash?
-How to live with trash?
+His suggestion is to find a way to live with trash instead of seeing it as trash.
+Then the question becomes how to love and live with trash?
 Think beyond the common perception.
@@
 
-It can be claimed that the end of an object’s life equates to the moment when it is refused.
-As stated by \citet[63]{emgin2012trashion} this action \quotes{might take place in different forms and for [various] reasons.} In common sense it is considered as waste.
-At this moment, the object is left valueless in all the possible meanings of the term value.
-It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}.
-However, Thompson’s Rubbish Theory shows us the opposite of it.
+It can be claimed that the end of an object’s life corresponds to the moment when it is refused.
+As stated by \citet[63]{emgin2012trashion} this action \quotes{might take place in different forms and for [various] reasons.} In common sense, trash can or dump is the graveyard of objects.
+In landfills, \quotes{the object is left valueless} in all kinds various value system.
+\quotes{It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values} \citep[63]{emgin2012trashion}.
+However, Thompson’s \textit{Rubbish Theory} shows us the opposite of it.
 Trash can is not an end it is starting point of another life.
 
-In \singlequotes{The Social Life of Things} \citet[3]{appadurai1988social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \cite{kopytoff1986cultural} notes that the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different systems of value that are both economically and culturally inscribed.
+In \textit{The Social Life of Things} \citet[3]{appadurai1986social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \citet[66]{kopytoff1986cultural} notes that the biography of a thing was significantly similar to an account of someone’s life.
+It moves into different positions, and experiences diverse paths in the course of different states and different systems of value that are both economically and culturally defined.
 Appadurai focuses on the \quotes{commodity potential} of things and asserts that \quotes{things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant} (1986: 13).
 However, one can ask that what are these commodity states and does anything exist between them?
-Thompson’s Rubbish Theory fills this gap.
+Thompson’s \textit{Rubbish Theory} fills this gap.
 
-Thompson observes the creation and destruction of value in produced gadgets, cultural artifacts, and ideas.
-He notes that how an object’s economic and cultural value diminishes over time rendering the objects worthless or redundant and how others value increases overtime.
-In his notable Rubbish Theory, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value).
+Thompson observes the creation and destruction of value in products, cultural artifacts, and ideas.
+He notes that how an item’s economic and cultural value lessen through time rendering the objects unprofitable or unnecessary and how others’ value increases.
+In his notable \textit{Rubbish Theory}, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value).
 The transient category falls into the common state of objects that are lessening in value and have limited life period.
 A used car can be an example of transient state.
-On the contrary, the durable objects’ value increase over time and have preferably unlimited life spans.
+On the contrary, the durable objects’ value increase through time and have probably unlimited life spans.
 Antiques and objects in museums can be an example of durable.
@@
 
-Rubbish is, by definition, an object that is not or is no longer, owned by anyone, which falls outside all categories of economics, culture, and social control.
+Rubbish is, by definition, an object state that is not or is no longer, owned by anyone, which falls outside all kinds of economics, culture, and social system.
 As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous.
-The socially constructed value of the object has shifted over time from its limited life span of usefulness and meaning to a infinite and valuable socially accepted rubbish.
+However the socially constructed value of the object can shift through time from its limited life span of usefulness and meaning to a infinite and valuable socially accepted rubbish.
 
@@
 In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty.
-As Michael Thompson’s Rubbish Theory suggests that rubbish is both ready for the disappearance and yet ripe for reinvestment, reinterpretation or revaluing.
-Trash as a state of being flexible is ready to transformation.
+Its value and function open to be reset.
+As Thompson suggests that rubbish is both ripe for disappearance and yet suitable for reinterpretation, reinvestment or revaluing.
+Further rubbish as a state of being flexible is ready to transformation.
 
@@
 Hence, it \quotes{is able to provide the path for the seemingly impossible transfer of an object from transience to durability} (1979: 9) he also puts forward that \quotes{a transient object gradually declining in value and in expected life span may slide across into rubbish} (1979: 9) where it has the chance of being re-discovered, brought to light or admired once again.
-Figure \ref{fig:rubbish_theory} demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable).
-The transitions between these states are defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).
+In other words, he specifies the path between the object categories.
+The path of transitions between transient, rubbish and durable objects are defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).
 
-% TODO
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
-  \caption{Thompson’s Rubbish Theory}
-  \label{fig:rubbish_theory}
-\end{figure}
-
-To illustrate rubbish theory the series of compression by French sculpture César can be analyzed in the context of it.
+To illustrate \textit{Rubbish Theory} the series of compression by French sculpture César can be analyzed in the context of it.
 His early work is composed of soldered and welded metal as well as junk materials.
@@
 % http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
-\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in twentieth century century.
+\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in twentieth century.
 Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum.
 In other words, it switched to durable category by interestingly trashing it.
-
-% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor.
-Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.
 
@@
   \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
-  \caption{César, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
+  \caption{César Baldaccini, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
   \label{fig:Cesar_Zim}
@@
 
-Although Thompson is quite successful describing states of objects, claimed transitions between states in the theory have some problems.
+Although Thompson is quite successful describing states of objects, claimed transitions between object categories in the theory have some problems.
 Thompson label some transitions as possible and the others as impossible.
 He only allows movement of goods from transient to rubbish, and from rubbish to durable.
-Movement in the other directions, from durable to either transient or rubbish, does not exist in this system.
-However, Duchamp’s notable ready-made \textit{Fountain} is one of the examples outside of the defined transitions.
+Movement in the other directions, from durable to either transient or rubbish, does not allowed in this system.
+However, Duchamp’s notable ready-made \textit{Fountain} is one of the examples that fall outside of the given transitions.
 
-\textit{Fountain} (1917) is a artwork produced by Marcel Duchamp, who is notable member of provocative Dada movement.
+\textit{Fountain} (1917) is an artwork produced by Marcel Duchamp, who is notable member of provocative Dada movement.
 The piece was an industrial porcelain urinal, which was signed \quotes{R.Mutt}.
 It is submitted for the exhibition of the Society of Independent Artists in 1917.
-Committee rejected \textit{Fountain}, even though the rules declared that all works would be accepted from artists who paid the fee.
-It is considered one of the major artworks of the twentieth century century because of challenging the existing understanding of art.
+Committee rejected \textit{Fountain}, even though the rules declared that all artworks would be accepted from artists who paid the fee.
+It is considered one of the major artworks of the twentieth century because of challenging the existing understanding of art.
 Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist.

### 2016-01-17 chapter3_final.tex
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

@@
 Several methods and genres are explored.
-Lastly focused on the inspiring documentary of Agnès Varda, The Gleaners and I, which provides a general picture of the subject.
+Lastly focused on the inspiring documentary of Agnès Varda, \textit{The Gleaners and I}, which provides a general picture of the subject.
 
@@
 
-From the beginning of twentieth century-century non-art objects draw attention of artists.
+From the beginning of twentieth century non-art objects draw attention of artists.
 Usage of these objects play significant role in the development of art trough time.
@@
 
-One of the remarkable change in twentieth century-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
-These objects are not commonly recognized as art often because they already have a non-art function.
+One of the remarkable change in twentieth century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art.
+These objects are not commonly recognized as art or art material often because they already have a non-art function and place in society.
 Their place in the society and people’s mind commonly have a different meaning.
@@
 With this approach works can be examined in multi-dimensional context.
-This also represents another branch in modern art.
+This also represents another key branch in modern art.
 
-In twentieth century-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art.
+Artists, in twentieth century, experimented with new ways of seeing and with unusual ideas about the functions of materials and nature of art.
 Previously paintings are based on linear perspective and realistic style.
 Themes are often composed of religious and mythical narratives.
-After the second half of the 19th-century, they started to abandon these themes and painting methods.
+After the second half of the nineteenth century, they started to abandon these themes and painting methods.
 For instance, in the works of impressionist paint brushstrokes can be easily identified.
@@
 They collaborated with each other on the development of cubism and collage.
-One of the keys to understand the significance of Cubism of Picasso and Braque, is to view their actions and how unusual they were for the time.
+One of the keys to understand the significance of Cubism of Picasso and Braque, is to view their methods as unconventional for their time.
 When they placed mass produced artifacts into the realm of fine art they acted as artistic iconoclasts of their age.
 
-Collage originates from the French \textit{coller} is a technique of pasting together manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting.
-In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, oil-cloth, and newspapers with oil paint on canvas to construct compositions.
+Collage originates from the French \textit{coller} is a technique of pasting together manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, usually in combination with drawing and painting.
+In about 1912–13 Pablo Picasso and Georges Braque applied this technique, combining fragments of paper, oil-cloth, and newspapers with oil paint on canvas to construct compositions.
 Pasting paper is not a new technique but using this technique it in the art making is a revolutionary movement in the language of art \citep{waldman1992collage}.
@@
 Similar to the collage, assemblage is produced by the incorporation of three-dimensional objects.
-\cite{seitz1961art}, the curator of the exhibition \quotes{The Art of Assemblage} featured at the New York Museum of Modern Art in 1961, described assemblages as being made up of preformed natural or fabricated materials, objects, or fragments not designed as art materials.
+\cite{seitz1961art}, the curator of the exhibition \quotes{The Art of Assemblage} featured at the New York Museum of Modern Art in 1961, describes assemblages as \quotes{being made up of preformed natural or [fabricated] materials, objects, or fragments not designed as art materials.}
 
@@
 Further there is a cut out lemon painted onto the table.
-The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, referring to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage provided new possibilities of playfulness.
-This was a new way of making art; instead of painting an object or landscape, you could paste whatever it was right onto the canvas.
+The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, referring to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} In essence, the new method; collage provides new possibilities of playfulness to the artists.
+This was a new course of making art; instead of painting an object or landscape, you could paste whatever it was right onto the canvas.
 
@@
   \includegraphics[height=6cm]{graphics/picasso_chair.png}
-  \caption{Pablo Picasso, \textit{Still Life with Chair Caning}, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
+  \caption{Pablo Picasso, \textit{Still Life with Chair Caning}, 1912, Oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
   \label{fig:Picasso_Chair}
@@
 
-Moreover, Braque and Picasso questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the contemplative realm of artistic creation.
-Of equal importance, their work highlighted and separated the role of technical skill from art-making.
-Braque and Picasso introduced a fake element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
-They inquiry as \quotes{Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?}
+Moreover, Braque and Picasso challenged the elitism of the art world, which had constantly forced the separation of ordinary, everyday experience from the sophisticated world of artistic creation.
+At the same time, their work underlined and separated the role of technical skill from art-making.
+Braque and Picasso introduced usage of unoriginal element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects.
+They inquiried as \quotes{Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?}
 
@@
 \textit{Merz} was soon to become a kind of brand name for almost all his productions.
-\cite{webster2011kurt} puts significance of Schwitters in the development of art as follows:
-
-\begin{quote}
-The language of \textit{Merz} now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.
-In his bold and wide-ranging experiments he can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism...
-
-Schwitters’ work inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys, and he is now seen as the grandfather of post-1945 art movements, from Pop Art to Fluxus, Conceptual Art to site-specific art, and the forerunner of present day artists such as Thomas Hirschhorn, Gregor Schneider and Rachel Whiteread.
-\end{quote}
+\cite{webster2011kurt} puts significance of Schwitters in the development of art as \quotes{The language of \textit{Merz} now finds common acceptance and today there is scarcely an artist working with materials other than paint who does not refer to Schwitters in some way.} He notes that \quotes{bold and wide-ranging experiments} of Schwitters \quotes{inspired such post-war pioneers as Jasper Johns, Robert Rauschenberg and Joseph Beuys}.
+Schwitters can be seen as \quotes{can be seen as the grandfather of Pop Art, Happenings, Concept Art, Fluxus, multimedia art and post-modernism.}
 
@@
 \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
-As he wrote: \singlequotes{It grows more or less according to the principle of a metropolis.} The \textit{Merzbau} was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
-Material has transformed into information, and \singlequotes{how} has surpassed \singlequotes{what} we see.
+As he wrote: \quotes{It grows more or less according to the principle of a metropolis.} The \textit{Merzbau} was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
+Material has transformed into information, and \quotes{how} has surpassed \quotes{what} we see.
 The grottos in the \textit{Merzbau} that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.
@@
 Collages and assemblages can be composed of all types of objects such as trash and found object.
-The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp’s concept of ready-made.
+The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1936short}, but usage in the art has gained new dimensions with the Duchamp’s concept of ready-made.
 Industrially manufactured or anything found  anymore can found a place in the art.
-The most notable example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.
+The most notable example is \textit{Fountain} (discussed in the previous chapter), a typical porcelain urinal purchased from a hardware store and displayed on a pedestal, lying on its side.
 Before that first one is \textit{Bicycle Wheel} (Figure \ref{fig:Duchamp_BicycleWheel}).
 He wrote that the idea of a bicycle wheel upside down onto a stool.
-Although he claimed to select objects for his ready-made without regard to beauty, he said, \quotes{To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.} These samples were the beginning of
-shift from an art that is striving for beauty to a higher complex or hidden meaning beyond what was seen from common artifacts found in everyday living.
+Even though he stated to select objects for his ready-made without paying attention to beauty, he wrote, \quotes{To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.} These samples were the beginning of shift from an art that is striving for beauty to a higher complex or hidden meaning beyond what was seen from common artifacts found in everyday living.
 
@@
 
-In the French film Amélie\footnote{Original title: Le fabuleux destin d’Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris.
+In the French film \textit{Amélie}\footnote{Original title: Le fabuleux destin d’Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris.
 He collects them and glue them together in a photo album.
@@
   \includegraphics[height=6cm]{graphics/amelie_01.jpg}
-  \caption{Still image from Amélie by Jean-Pierre Jeunet}
+  \caption{Still image from \textit{Amélie} by Jean-Pierre Jeunet}
   \label{fig:Amelie}
@@
 
-Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977.
-It is a collection of photo booth images that had been thrown away or torn up by the people in the photos.
-\cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine.
+Prior to film \textit{Amélie}, British artist Dick Jewell published a book in title of \textit{Found Photos} in 1977.
+It is a collection of photo booth images that had been thrown away or torn up by owner of the photos.
+\textit{Found Photos} is described by  \citet[222]{badger2014photobook} as \quotes{both a conceptual artwork and a sociological footnote.} \cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine.
 They are scavenged by the artist from the photo booths of London.
@@
 On the other hand, some of them are very good condition, and it is a mystery that why they are rejected.
-Walker explains that the:
+Walker points out that the:
 
 \begin{quote}
-gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in Found Photos, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving.
+gap between our exterior perception of the image and what must have been the internal dissatisfaction of the original subject results in some of the effective moments in \textit{Found Photos}, where the images are not only bizarre and wonderfully funny (as many of them are) but also profoundly moving.
 \end{quote}
@@
 \quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the photo booths and looking for the nearest waste bin.
-Badger describes Found Photos as \quotes{both a conceptual artwork and a sociological footnote.}
 
@@
 On the other side for another artist photographs serve a function to record his daily trash.
-Tim Gaudreau photographed every object that he threw away for one year.
+Tim Gaudreau photographed every object (Figure \ref{fig:TimGaudreau_SelfPotraitRevealedByTrash}) that he threw away for one year.
 At the end around five thousand images are covered all the gallery and opened to visitors.
@@
 It reveals me.} Like in the case of Tracey Emin trash turns to a medium that is used to express oneself.
-People are not only composed of the listed items in the CVs, economical power like pointed out in the book (and also film) Fight Club Tyler Durden draws attention to the narrator by saying: \quotes{You are not your bank account.} It is an effective way of looking things left behind rather that things put forward.
+People are not only composed of the listed items in the CVs, economical power like pointed out in the book (and also film) \textit{Fight Club} Tyler Durden draws attention to the narrator by saying: \quotes{You are not your bank account.} It is an effective way of looking things left behind rather that things put forward.
 Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.
@@
 Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement.
-In her photographic series \textit{Road Kill}, she captures tiny trash corpses that are generally ignored and out of sight.
+In her photographic series \textit{Road Kill} (Figure \ref{fig:FilomenaCruz_RoadKill_ReVista}), she captures tiny trash corpses that are generally ignored and out of sight.
 In other words, the skin of city revealed through her photos in micro scale.
@@
 
-In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump.
+In the documentary film, \textit{Waste Land}, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump.
 He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millions of people.
@@
 
+Figure \ref{fig:VicMuniz_PicturesOfGarbage} is one of the works of Muniz.
+It built up piling trash together in a very large room and later photograph of it taken.
+It is a reproduction of \textit{The Death of Marat} (1793, Oil on canvas, 165 cm x 128 cm) by Jacques-Louis David.
+Painting represents journalist lying dead in his bath and it is one of the most famous images of the French Revolution.
+
 \begin{figure}[h!]
@@
   \includegraphics[height=10cm]{graphics/vik_muniz_marat.jpg}
-  \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
+  \caption{Vik Muniz, \textit{Marat (Sebastiao), Pictures of Garbage}, 2008, Digital C print}
   \label{fig:VicMuniz_PicturesOfGarbage}
@@
 \quotes{A violin is worth more than a house here,} says Favio Chávez by pointing out their hard conditions.
-Favio Chávez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez.
+Favio Chávez director and founder of the orchestra whose instruments such as violins (Figure \ref{fig:landfill_harmonic}), flutes and cellos are built from collected trash by Nicolás Gómez.
 Players of the orchestra are compiled from the children who are hopeless for their future.
@@
     \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
-    \caption{Sax}
+    %\caption{Sax}
     \label{fig:landfill_harmonic-sax}
@@
     \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
-    \caption{Violin}
+    %\caption{Violin}
     \label{fig:landfill_harmonic-violin}
   \end{subfigure}
-  \caption{Instruments of Recycled Orchestra}\label{fig:animals}
+  \caption{Instruments of Recycled Orchestra}
+  \label{fig:landfill_harmonic}
 \end{figure}
@@
 The people in the figure \ref{fig:Alsbrooks} is General Jefferson C.
-Davis who was an officer at United States Army in 19th-century.
+Davis who was an officer at United States Army in nineteenth century.
 Selected persons can be viewed as a member of the higher or ruling class of society.
@@
   \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
-  \caption{Kim Alsbrooks, \textit{Gen. Jefferson Davis}, 2015, oil on aluminum can}
+  \caption{Kim Alsbrooks, \textit{Gen. Jefferson Davis}, 2015, Oil on aluminum can}
   \label{fig:Alsbrooks}
@@
 
-The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air yet people find it hard to think of plastic bags as things of beauty.
-However, as a product --as something created and then unleashed to become seamlessly integrated into the lives of millions of people around the world--- there is a strange allure to them, just as a pathologist can admire the structure of a particularly virulent and contagious virus.
+Examples are not limited with these.
+Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.} The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air yet people find it hard to think of plastic bags as things of beauty.
+On other side, Eloísa Cartonera a cooperative in Buenos Aires, proudly produces handmade books of Latin American literature with cardboard covers picked from the streets.
+Moreover, Turkish artist İpek Duben works with found objects and has a series of head sculpture.
+Examples can be extended but this thesis could not cover all of them.
 
-% TODO burayı da düzeltmek gerek.
-Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}
-
-%
+%****************************************
 \section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
@@
   \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
-  \caption{Still image from The Gleaners and I}
+  \caption{Still image from \textit{The Gleaners and I} by Agnès Varda}
   \label{fig:AgnesVarda_Potatoes}
@@
 However, Varda forces us to watch it (wants us to pay attention).
-This scene called as \quotes{the dance of the lens cap.} Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s \textit{Les Glaneurs et la glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
+This scene called as \quotes{the dance of the lens cap.} Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnès Varda’s \textit{Les Glaneurs et la glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it.
 Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest.
@@
 
-Here another point is that Agnes records images of people picking up things from the ground like their ancestors.
+Here another point is that Agnès records images of people picking up things from the ground like their ancestors.
 Everyone somehow collect things in their life but particularly she selects these people and their images in action.

### 2016-01-17 chapter4_final.tex
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

@@
 The project will be examined in various dimensions.
-The relationship will be established between the previously mentioned artworks.
+The relationship will be established between the previously mentioned artworks and project.
 How this project is related to the discussed concepts and how it can be positioned among the previous works will be explained.
 
-Firstly, brief statement and description of the work is given. Secondly, the development of the project and experiments are explained. Lastly, the final body of the work with its parts is presented.
+Firstly, I briefly state and describe my work. Secondly, the development of the project and experiments are explained. Lastly, the final body of the work with its parts is presented.
 
-%
-%
-% TODO: Be careful on tenses.
+%****************************************
 \section{The Statement}
 Refuse is part of people’s consumption practices.
-It is a very common concept from developed cities to rural areas, from modern societies to ancient societies.
+It is a very common concept from urban areas to rural ones, from modern societies to ancient ones.
 It is not wanted, thrown away, kept away.
 It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature.
-Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man’s trash is another man’s treasure}.
+Contrary to the common approach as \citet[7]{thompson1979rubbish}, author of the book \textit{Rubbish Theory}, stated \quotes{one man’s trash is another man’s treasure}.
 
@@
 
-Through this project trash were re-imagined (re-considered, re-thought), new possibilities and alternatives were seek.
+Through this project, I put all my effort to re-imagine, re-consider and re-think trash for seeking new possibilities and alternatives.
 As it is discarded, missed potentials were discovered.
-This project aims to find new potentials on trash.
+Strictly speaking, this project aims to find new potentials on trash.
 
-The purpose is not to build an object that is produced from discarded material to watch it from distance.
+The purpose is not to build an object that is produced from discarded material in order to watch it from distance.
 The important thing is to interact with it.
-It is already discarded and general behavior avoid from it.
+It is already discarded and general behavior is to avoid from it.
 This work must change it.
 It must call the viewer to interact with it.
-Trash must be accepted by them.
+In other words, trash must be accepted by them.
 This project asks people to readmit the trash to the their life.
@@
 
-%
-%
+%****************************************
 \section{Development Progress of the Project}
@@
 In other words, they lead me during the development of the work.
-
-% This progress also reveals that how this work can be positioned among the other works.
 
@@
 It has a value and part of our games and indispensable source of fun.
-The notion of playing with it can be related with the Picasso’s collage work \quotes{Still Life with Chair Caning} mentioned previously.
+The notion of playing with it can be related with the Picasso’s collage work \textit{Still Life with Chair Caning} mentioned previously.
 He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials.
@@
 They were cut out from packages and advertisements.
-I remember clearly that she suggested that same for us.
-\quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind.
-Can it be reused?
-Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice.
-Further, this practice is also support to the bricolage methodology.
+I remember clearly that she suggested us to do the same: \quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind: Can it be reused?
+Every time it is not obvious that how can it be useful, but at some point it becomes an \quotes{indispensable practice.} Further, this practice also supports to the \textit{bricolage} methodology.
 Keeping many things makes easier to build (or produce) whatever at hand.
@@
 Seeing papers on the waste bin is a disappointment for me.
-As artist Aaron Kramer argues that \quotes{[t]rash is the failure of imagination} \citep[as cited in][]{meyer2007turning}.
+As artist Aaron Kramer argues and I strongly agree with that \quotes{[t]rash is the failure of imagination} \citep[as cited in][16]{meyer2007turning}.
 There is a lot of effort to produce objects and it seems that all this efforts are wasted.
@@
 In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines.
-The use of that object can be decided in the future.
+The usage of that object can be decided in the future.
 
@@
 In other words, it contains eureka moments.
-Because it is ignored by discarding and therefore undiscovered.
-It waits us to be discovered and possibly (as Picasso’s explanation on his work ’Bull’s Head’\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.
+Because it is ignored by discarding and therefore it has undiscovered potentials.
+It waits us to be discovered and possibly (as Picasso’s explanation on his work \textit{Bull’s Head}\footnote{See epigraph in the beginning of chapter 3}, 1942) discovered again and again.
 
@@
 Dormitory is place that living spaces is shared with many people.
-Therefore there is a limited place for you and your possessions.
-There is no space for unused items.
-After I graduated from university I started to living a rented house.
-This give me to opportunity to save the materials to use them later.
-My very first intention is to use them on my painting.
-Instead of white blank canvas I want to experiment with different surfaces.
-I collected boxes and cart boards from my friends.
+Therefore there is a limited place for you and your possessions and there is no space for unused items.
+After I graduated from university I started living in a rented house.
+This gives me to opportunity to save the materials to use them later.
+My very first intention is to use them on my paintings.
+Instead of white blank canvas I have experimented with different surfaces and I have collected boxes and cart boards from my friends.
 My aim is to turn discard materials to the different things.
-Here is some of the my previous works.
+Here are some of my previous works.
 
@@
 At the same time I also gave what I did to my friends as a birthday gift.
-I was experimenting with the material and at some point with the help of my mother I made my first notebook covered by Starbucks package.
+I was experimenting with the material and at some point, with the help of my mother, I made my first notebook covered by a part of Starbucks bag.
 Papers inside of it are blank mimeograph paper which different than white paper.
@@
 
-% NEW PART [collecting] 
+%****************************************
 \subsection{Collecting}
@@
 \begin{quote}
-Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
+Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \quotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
 \end{quote}
@@
 Paper or package must be trash or will be trashed.
-For this project anything must not intentionally bought to use as trash.
+For this project anything must not be intentionally bought to use as trash.
 In other words first rule is to consume less and generate less trash.
@@
 This question makes me feel uncomfortable because of thinking that stealing that someone elses’ objects.
-Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.
+Particularly I felt it when collecting left out papers from Bilkent Computer Laboratory.
 You already know that it owned by somebody else and after a while owner can take them.
@@
 In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select.
-When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.
+When the number of contributors are increased the diversity of the collected material will be increased and this will echo in the notebooks.
 
@@
 the variety of things is increased in time.
-Because people sad me that \quotes{I thought that you can use it.
+Because people said me that \quotes{I thought that you can use it.
 Do you collect also these?}.
@@
 Beyond social status it reveals activities that generate such a waste.It can be also extracted that most of the trashed papers are thrown away from feeding activity.
-On the other hand vastness of some types of disposables reveal the dark side of the enterprises such as Starbucks and Burger King.
+On the other hand vastness of some types of disposables reveal the dark side of enterprises such as Starbucks and Burger King.
 Few people thought that after seeing the project I only collected Starbucks packets.
@@
 
-% TODO see figure appendix.
-Collected items are stored in my room for a long time.
-Most of them are not belong to me.
+Collected items (Figure \ref{fig:CollectedAllTogether}) are stored in my room for a long time.
+Most of them do not belong to me.
 Here the detailed information of the collected materials including the place where it is collected and their previous usage are listed.
@@
 \textbf{Burger King packages} (Figure \ref{fig:BurgerKingBag}) are collected from the office where I work.
-At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant.
+At lunch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant.
 Meals are delivered to the office with paper packages.
@@
 Some people think that it is disgusting to use it for other purposes because of oil onto it.
-But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \citet[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}.
+But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time, what \citet[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}.
 She refers to resolution on dirt of \citet[36]{douglas2003purity}:
@@
 
-\textbf{Starbucks packages} are collected from my supervisor, office where I work and my friend.
+\textbf{Starbucks packages} (Figure \ref{fig:StarbucksBag}) are collected from my supervisor, office where I work and my friend.
 Particularly my friend saved and collected them from her friends.
@@
 There are different types of packets from this category.
-As claimed by the company all of them are build from recycled ---precisely downcycled--- paper.
+As claimed by the company all of them are built from recycled ---precisely downcycled--- paper.
 There is also one category of object that is not paper.
@@
 
-\textbf{Modshifters papers} are used to cover the dinner table.
+\textbf{Modshifters papers} (Figure \ref{fig:Modshifters}) are used to cover the dinner table.
 Beginning of the table there is a big roll of paper to cover the table.
@@
 
-\textbf{Order slips} are collected from bank office located at Technopolis of Middle East Technical University.
+\textbf{Order slips} (Figure \ref{fig:BankSlips}) are collected from bank office located at Technopolis of Middle East Technical University.
 They are used to record the order of customers.
@@
 
-% NEW PART [transforming]
+%****************************************
 \subsection{Transformation}
@@
 There are two main parts of notebooks; cover and pages.
-Papers that are mostly blank(empty) are used inside of the notebooks for writing.
+Papers that are mostly blank (empty) are used inside of the notebooks for writing.
 Others that are solid and colorful are used as a cover for notebooks.
@@
 I try to generate every possible combination.
-The purpose is to create as many alternatives as I can because trash is ignored and people do not give it new alternatives.
+The purpose is to create as many alternatives as I can because trash is ignored and people do not give it alternatives.
 Therefore these notebooks provide many alternatives to show that otherwise is possible.
@@
 
-% TODO starbucks defterlerinin hep yapıştırılmış olmasını da eklemek gerekli.
-
-% TODO muhakkak tekrar kontrol etmek gerekli.
-Size of the paper used inside of the notebooks are mostly equals to the size of an A4 sheet.
+Size of the paper used inside of the notebooks are mostly equal to the size of an A4 sheet (dimensions: 210mm x 297mm).
+There are different dimensions of notebooks.
+Most of them are half of A4 sheet or quarter of it.
+Collected papers' dimension shape the size of the notebooks.
 Usage of papers differs among the notebooks.
 Especially for the papers taken from Varuna Gezgin written part is folded inward by hiding it.
-However for the ones collected from Bilkent Computer Laboratory written side of it leaved open.
+However for the ones collected from Bilkent Computer Laboratory written side of it is left open.
 Their content comes from various students whose departments are also various.
-In other words offers great diversity and they are mixed to allow different interpretations.
-Further it provides what students from other departments works on.
-What other students work on can be understand from these.
-
-There are different dimensions of notebooks. Most of them are half of A4 (210mm x 297mm) or quarter of it. Collected papers dimensions shape the size of the notebooks.
-
-% TODO Dimensions of notebooks. most of them half of A4 or quarte of it. böyle bir fotoğraf eklenmeli. farklı boyutlarda farklı şekillerde ve renklerde.
+In other words, they offer great diversity and they are mixed to allow different interpretations.
+Further they provide what students from other departments work on.
 
@@
 
-While transforming collected materials my method can be explained with the term upcycling mentioned at the end of the Chapter 1.
+While transforming collected materials my method can be explained with the term upcycling mentioned at the end of the chapter 1.
 Further I tried to use objects already at hand.
-In other words I followed the bricolage technique.
+In other words I followed the \textit{bricolage} technique.
 However I have to do buy some tools for my work.
-Therefore it is hard to consider it as bricolage but my intention is to follow it.
+Therefore it is hard to consider it as \textit{bricolage} but my intention is to follow it.
 
 Moreover I have reviewed other notebook projects.
-Notable ones are The Sketchbook Project and myDetour from Moleskine.
+Notable ones are \textit{The Sketchbook Project} and \textit{myDetour} from Moleskine.
 In these projects anyone who bought the notebooks from them can participate and send their notebooks filled with illustrations and paintings.
@@
 
-% NEW PART
+%****************************************
 \subsection{Demonstration}
@@
 Starting point is to stack the notebooks onto the each other, and there are other ideas like putting them inside a waste bin to re-do the action of throwing away.
-After ward somehow they should understand that these notebooks can be taken.
+Afterwards somehow they should understand that these notebooks can be taken.
 I set up models and tried some installations of them.
@@
 They were early interpretations and ideas.
-I imagined an exhibition environment to place notebooks.
+I imagined an exhibition environment to place notebooks (Figure \ref{fig:exhibition}).
 Different placements were tried.
@@
 My purpose is give people.
-Aim is to spread the idea by making something useful from trash.
-Increase diversity, encourage people to embrace the trash.
+Aim is to spread the idea by making something useful from trash and to increase diversity, to encourage people in order to embrace the trash.
 
@@
 
-% TODO boxes and wooden cases
-To hold notebooks together I made several small boxes from discarded card boxes. Notebooks were put inside of them.
-
+To hold notebooks together I made several small boxes from discarded card boxes.
+Notebooks were put inside of them.
 In the production phase of the boxes, I discovered that my folded notebooks are fit into the many card boxes.
@@
 
-%
-%
+%****************************************
 \section{Parts of the Final Work}
@@
 
-%
-%
+%****************************************
 \subsection{Notebooks}
-
 Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memorandum by many artists, scientists, and thinkers through the ages.
-Further same exist for me and people around me.
-Although the digital alternatives of it paper maintains its place in the community.
+Further the same exists for me and people around me.
+Although there are digital alternatives of it paper maintains its place in the community.
 
@@
 I try to record their stories (by photography and taking notes) but some of them were not possible.
-However I still use them in the work because even if I missed their story, with their materiality reveals their history.
-It still has a history but needs to rewritten.
-Maybe forgetting all the history maybe creates different notebook.
+However I still use them in the work because even if I missed their story, with their materiality their history reveal themselves.
+They still have histories but they need to be rewritten.
+Maybe forgetting all the history maybe creates different notebooks.
 
@@
 However for one series I borrowed the idea of nonsense word generation from the Kurt Schwitters.
-Similar to the the production of the nonsense word merz I decided to name some of the notebooks a nonsense word.
+Similar to the the production of the nonsense word \textit{Merz} I decided to name some of the notebooks a nonsense word.
 There are notebook series that have a name.
@@
 At this point approach of Kurt Schwitters provides me a way.
-He generated his frequently used word \quotes{Merz} from an advertisement.
+He generated his frequently used word \textit{Merz} from an advertisement.
 It is a nonsense word and used in most of his works.
 I followed what he did and generated a word from the papers that used inside of the notebooks.
-I use the word \quotes{Daro} extracted from \quotes{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.
+I use the word \textit{Daro} extracted from \textit{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.
+The word found one the of papers collected from near the printer inside of computer laboratory.
 
-%
-%
+%****************************************
 \subsection{Exhibition}
-Especially it is the most hard topic in the development of the thesis. To find an appropriate place for the notebooks is great challenge for me.
+Especially exhibition of notebooks is the most hard topic in the development of project.
+To find an appropriate place for the notebooks is a great challenge for me.
+Main idea is here to find a place that can also be considered as an alternative art space because in every dimension alternative is seek through the project.
+It must not only fit inside of white cube and must reach to audience.
+Therefore frequently visited places is a perfect locations for the project.
 
-\textbf{Public space.} The reason why select library is there are small papers to write down the location of books.
-Libraries are places that things are reused.
-Books are used by many people.
-It is place of sharing culture.
-Books are shared by all the other peoples.
-Public space.
-It is place that students from different department use the same place.
-
-Notebooks are placed where people frequently visit such as computer desks.
+Bilkent library and computer laboratory are one of the places where notebooks are placed inside of boxes made from card boards (Figure \ref{fig:BilkentLibrary}-\ref{fig:BilkentLaboratory}).
+Libraries are places where books are reused and shared among many people.
+It can be viewed as a place of sharing culture.
+Further it is a place that students from several department visit the same location.
+Particularly in Bilkent there are small papers to write down the shelve numbers of books.
+It is a great place to leave notebooks there because people already need something to write.
+They can find notebooks when they need them.
+For the computer laboratory case, the main purpose is to provide an alternative near the place where mostly papers are carelessly wasted.
 
@@
     \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
-    \caption{Library}
+    \caption{Sample placement at Bilkent Library}
     \label{fig:BilkentLibrary}
@@
     \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
-    \caption{Computer Laboratory}
+    \caption{Sample placement at Bilkent Computer Laboratory}
     \label{fig:BilkentLaboratory}
@@
 
-% su anda sadece bilkente yerlestirildi. Odtuye daha koyamadim. Neden koymadim. Nicin koymadim. Koymali miyim?
-
 % bir çok insanın ortaklaşa kullandığı bir alan. kesişim alanı. bir tanesi de özellikle zaten toplanan yer. insanların defterlerle karşılaşmalarını istiyorum.
-
-% Selected places are frequently visited by people. Shared places.
 
@@
 Often they are mass produced imitations and replicas of well-known artists work embedded various objects such as cover on the notebooks.
-At this point I image an art space you can buy these types of items freely.
+At this point I image an art space you can get these types of items freely.
 In other words alternative to the existing approach this types of gadgets.
@@
 For this type of approach Torun is a great place to show my notebooks and give them away.
-Torun describe itself as a place for free place for sharing art.
-Open to everybody.
-Makes open call to the any artist.
+Torun describes itself as a place for free place for sharing art.
+The place is open to everybody and makes open call to any artist.
 There are no security cameras on this gallery therefore no one is watching you at there.
-This idea shared with Torun and they accepted it.
-However Torun will opened after 14th of the January currently I just took some photos at there.
+The project is shared with Torun and it is accepted.
 
@@
 People can get them both.
-Further it reveals the process of the production of the notebooks.
-Shows the previous state of the materials.
+Further it reveals the process of the production of the notebooks and shows the previous state of the materials.
 
@@
 
-These are example placement.
+Figure \ref{fig:SamplePlacementAtTorun} shows the example placements in Torun.
 The exhibition event is not held.
 It is only decided.
-These notebooks are not only exhibited there, but also I will turn it to an workshop that continue to produce notebooks and show people to how to do it.
+These notebooks will not only be exhibited there, but also I will turn it to an workshop that I continue to produce notebooks and show people to how to do it.
 Maybe they will join me in the production of notebooks.
-They can bring their items and transform all together.
+They can bring their items and we can transform them all together.
 We can share our ideas and thoughts with each other.
 
-%
-%
+%****************************************
 \subsection{Website}
@@
 
-Website can be accessible through this address \url{http://kulu.be/notebook-project}.
+Website can be accessible through this address: \url{http://kulu.be/notebook-project}.
 Domain name kulu.be belongs to me and project placed under a directory of it.

### 2016-01-17 main.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30
turnitin fixes
Former-commit-id: 979c7f85b096336823eba6510e83756cbc45169e
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

@@
 \usepackage{apacite}
-\usepackage[a4paper,left=41.2mm,top=25.2mm,right=24.2mm,bottom=35mm]{geometry} % left: 40mm, top: 25mm, right: 25mm, bottom: 25mm
+% left: 40mm, top: 25mm, right: 25mm, bottom: 25mm
+\usepackage[a4paper,left=40.2mm,top=24.2mm,right=25.4mm,bottom=36mm]{geometry}
 \usepackage{epigraph}
@@
 % Remove the next two lines if you want the figures at their place
-\usepackage[figuresonly,nolists,nomarkers]{endfloat}
-\renewcommand{\processdelayedfloats}{}
+%\usepackage[figuresonly,nolists,nomarkers]{endfloat}
+%\renewcommand{\processdelayedfloats}{}
 
@@
 % Chapter title spacing
-\titlespacing{\chapter}{0pt}{13mm}{3\baselineskip} % Centered, Top: 50mm, Next: 3 line after
+% Centered, Top: 50mm, Next: 3 line after
+\titlespacing{\chapter}{0pt}{13mm}{3\baselineskip}
+
 % Bibliography title spacing
-\titlespacing*{name=\chapter,numberless}{0pt}{16mm}{4\baselineskip} % Centered, Top: 50mm, Next: 4 line after
+% Centered, Top: 50mm, Next: 4 line after
+\titlespacing*{name=\chapter,numberless}{0pt}{16mm}{4\baselineskip}
 
@@
   \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
-  \renewcommand{\bibname}{\MakeUppercase{Select Bibliography}}%
+  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
 }
@@
     pdfauthor	= {Mustafa ilhan},
-    pdfsubject			= {Trash, Art},
-    pdfkeywords			= {mfa thesis, trash, art},
+    pdfsubject	= {Trash, Art, Transformation},
+    pdfkeywords	= {mfa thesis, trash, art, transformation},
     colorlinks	= false,
@@
 %\singlespacing
-\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century.
+\par Usage of non-art objects in the artworks can be traced back to the beginning of twentieth century.
 This approach has broken the existing rules and extended the language of art in an unprecedented way.
@@
 %\singlespacing
-\par Sanat işlerinde sanat dışı nesnenin kullanımı 20.
-yüzyılın başına kadar takip edilebilmektedir.
+\par Sanat işlerinde sanat dışı nesnenin kullanımı yirminci yüzyılın başına kadar takip edilebilmektedir.
 Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir.
@@
 İnsanları atığı tekrar kullanmaya davet etmek amacıyla, defterler geleneksel sanat mekanı olarak kabul edilmeyen kütüphane, bilgisayar laboratuvarı gibi sık ziyaret edilen ortak kullanım alanlarına yerleştirilmiştir.
-
-% Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir.
-Ya da en azından proje kapsamında üretilen işin.
-Ya da bu bağlamda ele alınabileceği iddia edilmektedir.
-
-% Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır.
-Çöpün kültürel ve kuramsal olarak nasıl ele alındığı(alınabileceği) araştırılmıştır.
-Çöpü dönüştürmenin nasıl ve ne şekilde mümkün olduğu incelenmiştir.
-Sanatsal üretim yöntemi olarak çöpü (tercih eden)/(kullanan) sanatçıların yaklaşımları ele alınmıştır.
-Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.
-
-% Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır.
-Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır.
-Bu defter hakim sistemin dışındaki mekanlarda konulmuştur.
-(kamusal ortak alan)
-
-% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.).
-Beraberinde pek çok akım ve üretim biçimini tetiklemiştir.
-Hem sanatın dili genişledi hem de objeler sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı.
-Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır.
-Çöpün nasıl sanatta yer bulduğu incelenmiştir.
-
-% Çöp ve sanatsal eylem birlikte alınarak incelenmiştir.
-Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır.
-Teoriler ve methodlar ele alınmıştır.
-Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kazandırmak amaçlanmaktadır.
-
-% Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır.
-Bu atık maddeler dönüştürülerek defter yapılmıştır.
-Renk, doku, biçim ve üretim yöntemi ile endüstriyel defterlere alternatif bir yaklaşım olması amaçlanmıştır.
-Bu defterler insanların ulaşabileceği belirli mekanlara dağıtılmıştır (yerleştirilmiştir).
-Mekanlar da aynı şekilde eleştirel bakış açısına açık yerler arasından seçilmiştir.
-Alternatif bir ortam sunan mekanlar seçilmiştir.
-Defterlerin mekanla belirli bir anlamsal ilişki içine girmesi amaçlanmıştır.
-Bu proje sonunda dönüştürülen şeylerin aynı zamanda dönüşütüğü şeyi de başka bir şeye dönüştürdüğü anlaşılmaktadır.
-Çöpe olan bakış açısının dönüştürülmesi amaç edilmiştir.
 
@@
 \begin{center}
-	\vspace*{13mm}
+	\vspace*{13mm} % Top: 50mm
 	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{ACKNOWLEDGMENTS}}}\\
@@
 Üstündağ, Ayşenur Durgut, Emrah Şamdan, Duygu Ç.
-Şamdan, and Koray Benli for their valuable friendship, and also Ali from METU Technopolis İş Bank Office, Aykut from Modshifters, and Varuna Gezgin for collecting discarded materials for the thesis project.
+Şamdan, and Koray Benli for their valuable friendship, and also Mr.
+Ali from METU Technopolis İş Bank Office, Mr.
+Aykut from Modshifters, and Varuna Gezgin for collecting discarded materials for the thesis project.
 
@@
 \include{chapter1_final}
-\include{chapter2_reduced}
-\include{chapter3_reduced}
-\include{chapter4_reduced}
-\include{chapter5}
+\include{chapter2_final}
+\include{chapter3_final}
+\include{chapter4_final}
+\include{chapter5_final}
 %........................................
@@
 \phantomsection
-\addcontentsline{toc}{chapter}{SELECT BIBLIOGRAPHY}
+\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
 \bibliographystyle{apacite}
@@
 
-%\include{appendix_glossary}
 \include{appendix_materials}
